### 2021-12-21 manuscript_1.0/manuscript_1.0.Rmd
Copies repo from Clean.ActCrit this will be released with manuscript forthcoming

---
title: Combination of field and experimental data together with computational models 
  reveal cognitive mechanisms behind cleaner fish behaviour
#Cognitive and ecological aspects determine cleaner performance
author:
  - name: Andrés E. Quiñones 
    affiliation: "1"
  - name: Zegni Triki
    affiliation: "2"
  - name: Redouan Bshary
    affiliation: "1"
address:
  - code: "1"
    address: Institute of Biology, University of Neuchâtel, Neuchâtel, Switzerland
  - code: "2"
    address: Department of Zoology, Stockholm University, Stockholm, Sweden

corresp_author_name:  "AE. Quiñones"
corresp_author_email: "andreseqp@gmail.com"

subject:
  - "Behavioural ecology"
  - "Cognitive ecology"
  - "Animal behaviour"

keywords:
  - learning   
  - cleaners
  - behaviour
  - bayesian statisitics
  - mutualism

abstract: |
  The same behaviour can be achieved by different mechanistic underpinnings. But the environmental conditions under which the behaviour is triggered might differ between these potential mechanisms. Thus, by analyzing the varitation of expression of a certain behavior across environmental gradients, it is possible to infer which mechanism is behind the behaviour of interest. To do this it is necessary to have clearcut predictions for the different candidate mechanisms. In here, we use experimental data on the behaviour of the cleaner fish *Labroides* *dimidiatus*, as well as enviromental variables from the location of fish, together with a computational model of the learning mechanisms. Using bayesian statistics, we fit key parameters of the computational model that determine the specific learning mechanism. We find that a model where cleaners estimate the long-term consequences of their actions, and use the estimate in their desicion making, explains better under which conditions the fish develop a preference for an ephemeral food source in the context of a biological market. We argue that the combination of computational models with data is powerful tool to infer the mechanistic underpinning behind behaviours of interest.

## Remove this if not required
ethics: |
  The Animal Ethics Committee of the Queensland government (DAFF)
  approved the project (CA 2016/05/970 and CA 2017/05/1063).

data_accessibility: |
  Please provide details on the data availability.

author_contributions: |
  AQ and RB designed the study. ZT collected the data. AQ developed the model and 
  fitted the model parameters to the data. AQ, RB and ZT wrote the manuscript.

## Remove this if not required
conflict_of_interest: |
  The authors declate no conflict of interests.

## Remove this if not required
funding: |
  This work was supported by the Swiss National Science Foundation (grants
  number: 31003A_153067/1 and 310030B_173334/1 to R.B.).

## Remove this if not required
acknowledgements: |
  ZT and RB kindly thank the staff of Lizard Island Research Station, Dominique
  Roche, Sharon Wismer, Olivia Rey,Sandra Ann Binning, Elena Levorato and William McNeely for their
  field support. AQ thanks Florian Hartig for statistical advice.

bibliography: Cleanerlearning.bib

## change to true to add optional line numbering
lineno: true

header-includes: |
  ```{=latex}
  \usepackage{float}
  \usepackage{booktabs}
  \newcommand{\beginsupplement}{ \setcounter{table}{0}     \renewcommand{\thetable}{S\arabic{table}}\setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}}
  ```
site: bookdown::bookdown_site
output: 
  bookdown::pdf_book:
    base_format: rticles::rsos_article
---

## Introduction

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,warning = FALSE,message=FALSE)
library(here)
```

Cooperation among individuals of the same or different species is
ubiquitous in nature. Among individuals of different species it
underlays the biological mechanism for fundamental ecological
interactions such as pollination, nitrogen fixation or parasite removal
[@begon_Ecology_2006]. When partners in these mutualistic interactions
are able to choose their interaction partner, their investment and the
return they obtain can be understood as a biological market
[@hammerstein_Biological_2016; @leimar_Cooperation_2010;
@noe_Biological_1994a;@noe_Biological_1995a]. Thus, we expect supply
and demand of the good and services being exchanged to determine the
action of individuals, at least in an evolutionary time-scale. However,
supply and demand conditions of a biological market, which typically
depend on the abundance of the species involved, certainly vary in time
and space. How do partners adjust their strategy in the face of this
variation? In animals an obvious general candidate mechanism for the
strategic adjustment is the cognitive machinery. However, it is not
clear which specific cognitive mechanisms allow individual to adjust
their behaviour to the varying market conditions.

One example of strategic adjustment in a biological market is the marine
cleaning mutualism involving the cleaner fish *Labroides dimidiatus* and
'client' fish. Clients offer themselves as food patches for cleaners to
remove ectoparasites, which gives the cleaners calories and the clients
improved health [@waldie_LongTerm_2011;
@ros_Does_2011;@triki_Effects_2016]. As cleaners have about 2000
interactions per day [@grutter_Relationship_1995], they regularly face
the situation that two clients seek cleaning simultaneously. In such
conditions, it is important to distinguish between 'resident' and
'visitor' client species [@bshary_Cleaner_2001a]. The residents have
small home ranges and hence access to only the local cleaner, while the
visitors have large home ranges and hence access to two or more
cleaners. Thus, visitors have the option to switch to another cleaner if
being made to wait, while residents must wait for inspection. Indeed,
visitors have been observed to use their partner choice options in that
way [@bshary_Choosy_2002], which may explain why cleaners give
visitors service priority in a field study in the Red Sea
[@bshary_Cleaner_2001a]. More generally, cleaners apparently prefer to
interact with visitors [@triki_Marine_2021]. Such a preference may be
linked to a client's value as a food patch; visitors are on average
larger than residents [ @bshary_Cleaner_2001a], and size is positively
correlated with parasite load [@grutter_Relationship_1995a]. However, 
early laboratory
experiments showed that leaving causes service priority independent of
client value [@bshary_Asymmetric_2002]. The experiments consisted of a
simultaneous two-choice task, where cleaners had to decide which of two
Plexiglas plates, which offered equal amounts of food, to approach first
and eat mashed prawn of it. One plate was made to behave like a
resident, i.e. it would remain until the cleaner had eaten off it. The
other plate was made to behave like a visitor, i.e. it would be removed
if not inspected first. Cleaners learned to prefer the visitor plate and
hence obtained the double amount of food [@bshary_Asymmetric_2002].
Adult cleaner fish outperform various primates as well as rats and
pigeons in this original version of the biological market task
[@salwiczek_Adult_2012; @zentall_Early_2017]; only African grey
parrots solve this task as well [@pepperberg_Can_2014].

Recent research has refined our view on partner choice and priority of
access in the *L. dimidiatus* cleaning mutualism, and as a consequence
performance in the biological market task. First, details of the task
presentation may matter; i.e. what relevant information is encoded in
the design of the two plates (colour versus size;
[@wismer_Cuebased_2019]), or whether the information is in the colour of
the food [@pretot_Comparative_2021; @pretot_Comparing_2016], and
whether the food is visible or hidden/released only when the subjects
made choices on a touch screen [@pretot_Factors_2016]. Second, it
appears that cleaner and client densities in nature affect how cleaners
perform in the original market task: when densities are low, cleaners
are more likely to fail to complete the task [@triki_Biological_2019;
@triki_Decrease_2018; @wismer_Variation_2014]. The apparent explanation
for this failure is that visitor clients are less likely to exert their
choice options (and hence wait for inspection if made to wait) when
cleaner fish densities are low [@triki_Brain_2020]. This change in
behaviour may be due to the fact that when cleaner densities are low,
the cost of switching in terms of distance to swim and time invested
increases. If visitors are not choosy, cleaners should not give them
priority anymore. Interestingly, while cleaners from high-density areas
have larger forebrains harbouring more cells than cleaners from
low-density areas [@triki_Brain_2020], on a local scale those
individuals that perform in the market task in a way that corresponds to
the locally optimal strategy (solving/failing the task when living in
high/low density) have relatively larger forebrains [@triki_Brain_2020].
Taken together, empirical results clearly show major intra- and
inter-specific variation in performance in the market task, warranting
investigation of the underlying cognitive machinery, from perception to
decision-making [@shettleworth_Cognition_2009].

One approach to identify candidate mechanisms underlying performance in
a cognitive task is to develop proximate learning models and to evaluate
their predictions in light of the behavioural data (e.g.
[@dubois_Model_2021]). By varying the cognitive tool kit, one can assess
which minimal kit is necessary to solve the task at hand. This approach
has been used to analyse the market task [@prat_Role_2021;
@quinones_Reinforcement_2019]. Learning models showed that basic
reinforcement learning does not suffice to solve the task, this is
particularly so when models assume the more complex natural situation in
which cleaners not only face resident-visitor pairs but also
visitor-visitor and resident-resident pairs, as well only a resident or
only a visitor. To be able to give visitors priority over residents,
cleaners first need to be able to assess a client's value separately for
the three possible forms of encounter (alone, paired with a fish with
the same strategic option, paired with a fish with the alternative
strategic option) [@quinones_Reinforcement_2019]. In addition, cleaners
need to account for the future consequences of current decisions. In the
model, this could be achieved in two non-mutually exclusive ways
[@quinones_Reinforcement_2019]: through low temporal discounting of
future effects and/or through perceiving a visitor client leaving as
psychological punishment (i.e. as a negative reinforcer). Given that a
negative reinforcer is part of the ubiquitous learning mechanism termed
operant conditioning [@thorndike_Animal_1898; @skinner_Behavior_1938], 
this explanation can be
considered the simpler one. Furthermore, accounting for the future
effects of an action is considered an advanced cognitive ability
[@suddendorf_Evolution_2007]. Here, we fitted our model to the empirical
data on fish densities and cleaner fish performance in the market task
with the aim to determine the likely mechanism used by cleaners to
incorporate future consequences of current decisions.

## Methods

### Overview

We used the data from [@triki_Biological_2019] to fit the parameters of
the model analysed in [@quinones_Reinforcement_2019]. For the bayesian
fitting procedure we used Markov Chain Monte Carlo (MCMC) with a
Metropolis sampler to estimate the posterior distribution of the model
parameters. The data consist a of the number of times that a set of
cleaners chose to feed of a visitor client plate in the context of the
market task. This set of cleaners were collected in different locations
and in each one of those locations environmental variables were
measured. These environmental variables recorded from each location are
used as input for the computational model. Given these inputs, the
computational model produces a time series of choices in the market
task. In the model the preference for the two options changes as the
algorithm learns based on the reward that the two options provide. Thus,
we run the model for 10000 steps and use the last 3000 steps as the
preference developed in the model for visitors given the environmental
variables. We use this preference as the predicted probability in a
binomial distribution to calculate the likelihood that the number of
visitor choices obtained from each cleaner is generated by the model. We
sum over all the cleaners the log-likehoods and use the total for the
acceptance of new parameters in the MCMC.

### The model

The model consist of a set individual-based simulations where
individuals face a series of choices between two options. Individuals in
the model represent cleaners, and the options they face simulate the
natural conditions of a cleaning market. Thus, individuals in the model
choose to prioritize different clients. These clients are classified as
resident and visitors. Residents are those clients that stay in the
cleaning queue when they are not given priority; while visitors leave
the queue (with a certain probability) after they are not given
priority. Individuals obtain a fixed reward from cleaning a client
regardless of the type. Every time individuals face and make a choice
they update the probability of making that same choice. The update is
based on the difference between the expectation of reward and the actual
reward the individual obtains (prediction error)
[@sutton_Reinforcement_2018; @rescorla_Theory_1972]; and it is carried
in the direction that would lead to more reward being obtained, given
the new information. Further details of the model implementation can be
found in the paper [@quinones_Reinforcement_2019]. The model analysis
points to the relevance of two parameters. First, $\gamma$ measures how
much individuals include future rewards in their decision updates. If
$\gamma=0$, individuals only use the immediate reward obtained from a
cleaning interaction. As $\gamma$ increases individuals include more the
reward obtained from the subsequent choices. That amounts to calculating
and using for decision making the future expected rewards in action.
Second, $\eta$ measures how much individuals include in their reward the
fleeing behaviour of visitor clients as a negative component. Both of
these parameters allow individuals to use in their estimates the future
effects of their choices. The model analysis by Quiñones *et al*
[@quinones_Reinforcement_2019] shows that without either of them, learning
individuals cannot develop a preference for the visitor client. The
analysis contrast the effect of these two parameters against variation
in the relative abundance of the two client types. The analysis shows
that under very high client (relative) abundance the presence of future
rewards ($\gamma>0$) no longer favours the preference for the ephemeral
clients, this effect does not occur with negative reward mediated by
client behaviour ($\eta$). Thus, the analysis suggests that future
reward as an explanation for cleaner ability to prefer visitors is
supported by Triki *et al* [@triki_Biological_2019] data. However, a combination of
future and negative rewards, could still be a better explanation for the
data. In the current analysis, we will use the data from
[@triki_Biological_2019] to fit some of the model parameters, particularly
relevant we will fit $\gamma$ and $\eta$ to find out whether each or a
combination of these effects is a better explanation for the pattern
seen in the data. For other parameter values used for the model
simulations and the MCMC see Table \ref{tab:param}

### Data explanation

*Insert here brief description of the data and data collection*

In order to capture with the model the relationship between the
characteristics of the market (environment) and the cleaner's
performance we need to translate the absolute abundances of the data to
to  a measure of relative abundances that captures client visitation patterns.
This is because in the model, relative abundances
of clients define not only the probability of residents and visitors,
but also how often the cleaning station is empty (e.g. there are no
clients to be cleaned). The more cleaners there are, the more options
are available for the clients and hence the higher is the probability of
empty cleaning stations. How often the cleaning stations are empty in
turns influences the value that cleaners can expect from their choices.
The emptier the cleaning stations are, the more beneficial it is to
prioritize a client that will not stay. However, the frequency of empty
spots in the cleaning station does not only depend on cleaner abundances 
but also on the frequency with which clients visit the
station. The client visitation frequency will likely vary among
different clients depending on parasite abundances and loads. These are
variables for which we do not have field estimates. Thus, we computed a
measure of relative cleaner abundance for each site relative to absolute
abundances and multiplied by a scaling constant that changes the range
of the variable. This scaling constant is meant to capture variation in the market 
conditions driven partly by cleaner abundance. We fit the value of the 
scaling constant as part of the
statistical inference. As for the client abundances for residents and
visitors we computed a relative measure with respect to the total client
abundance, and weighted that by the rescaled relative absence of
cleaners (1-relative cleaner abundance). Thus, all three measures of
relative abundance sum up to 1, and can be used in the model as a proxy
for the probability of having different options in the cleaning station.

## Results

```{r post, fig.cap="Posterior distributions for parameter values $\\gamma$, $\\eta$ and the scaling constant. We show the kernel density estimates, below the mode (black point) and the 65\\% (light blue) and 95\\% (grey)  highest posterior density interval for the three paramteres. On the left (panels a, c and c) posterior distributions for a model with   all three parameters; while on the right (b and d) a model without negative reward. Panel f shows a measure of fit for both models, namely the distribution of pseudo-$R^2$ obtained from sampling the posterior distribution of parameter values.",out.width='95%',fig.height=9}
require(data.table)
library(coda)
library(ggplot2)
library(cowplot)
library(ggdist)
source(here("../R_files/posPlots.R"))
source(here("loadData.R"))
library("jsonlite")

# Name of the folders containing the MCMC runs
scen1<-"MCMCclean_gam_nRew_sca_"
scen2<-"MCMCclean_gam_sca_"
scen3<-"MCMCclean_Nrew_sca_"

# NLables names for the three scenarios
labels.Scen<-c("both","gam","Nrew")
labelsPlot.Scen<-c("Full model","Future reward","Negative reward")

## Load files --------------------------------------------------------------

# Defaults for MCMC analysis
burn.in<-1000
thinning<-100

MCMCdata1<-loadMCMCrun(scen1,thinning = thinning,burn.in = burn.in)
MCMCdata2<-loadMCMCrun(scen2,thinning = thinning,burn.in = burn.in)
MCMCdata3<-loadMCMCrun(scen3,thinning = thinning,burn.in = burn.in)

# Create list with the data, convenient to use CODA for diagnostics
mcmcList.1<-mcmc.list(do.call(list,lapply(unique(MCMCdata1$seed), function(repli){
  rundata<-MCMCdata1[seed==repli]
  mcmcRun<-mcmc(rundata[,.(gamma,negReward,scaleConst)],thin = thinning)#
  return(mcmcRun)
})))

mcmcList.2<-mcmc.list(do.call(list,lapply(unique(MCMCdata2$seed), function(repli){
  rundata<-MCMCdata2[seed==repli]
  mcmcRun<-mcmc(rundata[,.(gamma,scaleConst)],thin = thinning)#
  return(mcmcRun)
})))

mcmcList.2<-mcmc.list(do.call(list,lapply(unique(MCMCdata2$seed), function(repli){
  rundata<-MCMCdata2[seed==repli]
  mcmcRun<-mcmc(rundata[,.(negReward,scaleConst)],thin = thinning)#
  return(mcmcRun)
})))

mcmcList.3<-mcmc.list(do.call(list,lapply(unique(MCMCdata3$seed), function(repli){
  rundata<-MCMCdata3[seed==repli]
  mcmcRun<-mcmc(rundata[,.(gamma,negReward,scaleConst)],thin = 100)#
  return(mcmcRun)
})))

## Density plots with gg -------------------------------------------------------

## Define the boundaries for credible intervals using High Density Interval

intervals<-c(0.66,0.95)

cuts.1<-lapply(MCMCdata1[,.(gamma,negReward,scaleConst)],
             function(x){
               c(mode_hdci(x,.width = intervals[c(2,1)])$ymin,
                 mode_hdci(x,.width = intervals)$ymax)  
})

cuts.2<-lapply(MCMCdata2[,.(gamma,scaleConst)],
               function(x){
                 c(mode_hdi(x,.width = intervals[c(2,1)])$ymin,
                   mode_hdi(x,.width = intervals)$ymax)  
               })

cuts.3<-lapply(MCMCdata3[,.(negReward,scaleConst)],
               function(x){
                 c(mode_hdi(x,.width = intervals[c(2,1)])$ymin,
                   mode_hdi(x,.width = intervals)$ymax)  
               })

# get all the likelihoods from the posterior for all models
loglikehoods.all<-data.table(lglikelihood=c(MCMCdata1$fit,MCMCdata2$fit,
                                             MCMCdata3$fit),
                              model=c(rep(labels.Scen[1],length(MCMCdata1$fit)),
                                      rep(labels.Scen[2],length(MCMCdata2$fit)),
                                      rep(labels.Scen[3],length(MCMCdata3$fit))
                                      ))

# Read field data to calculate null log-likelihood
fieldData<-fread(here("Data","data_ABC_cleaner_abs.txt"))

nullLikehood<-sum(dbinom(x=fieldData[,score_visitor],
                         size = 20,prob = 0.5,log = TRUE))

# calculate pseudo R^2
loglikehoods.all[,Rsqrd:=1-lglikelihood/nullLikehood]

panel.rsqr.all<-
  ggplot(data=loglikehoods.all[is.finite(lglikelihood)],
                  aes(y=model,x=Rsqrd,fill=model))+
  stat_halfeye(alpha=0.5,point_size=3)+
  theme_classic()+xlim(-0.5,0.3)+
  scale_fill_manual(values=c("#1b9e77","#d95f02","#7570b3"),
  name = "Model", labels = labelsPlot.Scen)+
  geom_vline(xintercept = 0,color="black",size=1)+
  theme(legend.position = c(.3, .80),legend.key.size = unit(0.4,'cm'),
        axis.text.y = element_blank())

plot_grid(nrow=3,align = "v",byrow = FALSE,
          # Full model - \gamma
          ggplot(data=MCMCdata1,aes(x=gamma)) + 
            stat_halfeye(aes(fill=stat(cut(x,breaks = cuts.1$gamma))),
                         point_interval = mode_hdi, .width = c(.66, .95),point_size=3,
                         show.legend=FALSE) + 
            labs(title=labelsPlot.Scen[1],subtitle = expression(gamma),x="",y="")+
            theme_classic()+scale_fill_manual(values=c("gray85","skyblue","gray85")),
          # \eta
          ggplot(data=MCMCdata1,aes(x=negReward)) + 
            stat_halfeye(aes(fill=stat(cut(x,breaks = cuts.1$negReward))),
                         point_interval = mode_hdi, .width = c(.66, .95),point_size=3,
                         show.legend=FALSE)+theme_classic()+
            scale_fill_manual(values=c("gray85","skyblue","gray85"))+
            labs(subtitle = expression(eta),x="",y="")+xlim(-5,5),
          # Scale Constant
          ggplot(data=MCMCdata1,aes(x=scaleConst)) + 
            stat_halfeye(aes(fill=stat(cut(x,breaks = cuts.1$scaleConst))),
                         point_interval = mode_hdi, .width = c(.66, .95),point_size=3,
                         show.legend=FALSE)+
            theme_classic()+scale_fill_manual(values=c("skyblue","gray85"))+
          labs(subtitle = "Scalling const.",x="",y="")+xlim(-2,1500)+theme_classic(),
          # Future reward only model - \gamma
          ggplot(data=MCMCdata2,aes(x=gamma)) +
            stat_halfeye(aes(fill=stat(cut(x,breaks = cuts.2$gamma))),
                         point_interval = mode_hdi, .width = c(.66, .95),point_size=3,
                         show.legend=FALSE) +
            scale_fill_manual(values=c("gray85","skyblue","gray85"))+
            labs(title=labelsPlot.Scen[2],subtitle = expression(gamma),x="",y="")+
            theme_classic(),
          # Scalling constant
          ggplot(data=MCMCdata2,aes(x=scaleConst)) +
            stat_halfeye(aes(fill=stat(cut(x,breaks = cuts.2$scaleConst))),
                         point_interval = mode_hdi, .width = c(.66, .95),point_size=3,
                         show.legend=FALSE) +
            scale_fill_manual(values=c("gray85","skyblue","gray85"))+
            labs(subtitle = "Scalling const.",x="",y="")+
            theme_classic(),
          # Pseudo R^2
          panel.rsqr.all+labs(subtitle = expression(pseudo-R^2),x="",y=""),
          labels=c('a','b','c','d','e')
)

```

Figure \ref{fig:post} panels a,c and e show the posterior distributions
of the parameter values of the full model, which includes both future
and negative reward. Posterior distributions show the probability
density (y axis) of the estimated parameter values (x axis). Notably,
the bulk of the posterior distribution for the parameter tuning negative
reward ($\eta$ panel e) is around zero. Thus, the shape of the posterior
and its credible intervals suggest the absence of negative reward to be
well supported by the data. As for $\gamma$, the confidence intervals
also includes zero, but the mode of the posterior is around 0.5. Thus,
we run the analysis setting $\eta$ to zero. Figure \ref{fig:post} panels
b and d, show the posterior distributions of the two parameters
estimated. Not surprisingly, under a model without negative reward, the
distribution of $\gamma$ shifts to higher values. Under the new model,
the estimates of $\gamma$ do not include zero, the distribution is
centered around $0.5$. To asses the fit of the two models we calculated
the $pseudo-R^2$ [@mcfadden_Conditional_1974], which is a standard
measure of fit for logistic regression. In that context, $pseudo-R^2$
uses the log-likelihood of the data given the model, relative to the
log-likelihood of the data given a model without covariates, as a
measure of fit. Given that our model is not a logistic regression, we
measure the $pseudo-R^2$ in relation to the log-likelihood of a model
with parameters $\gamma$ and $\eta$ set to zero. This in practice
amounts to a model that has neutral preference between the two options.
In panel f of figure \ref{fig:post} we show the distribution of
$pseudo-R^2$ calculated using samples from the posterior distributions
shown before, as well as from a model with negative reward but without
future reward. Note, $pseudo-R^2$ can have negative values, that is when
the log-likelihood of the model is lower than that of a model that
triggers neutral preferences. Even though, the peak of the three
$pseudo-R^2$ distributions is not very different, the model with only
future reward produces a distribution of $pseudo-R^2$ where more values
are positive (to the right of black line in Fig. \ref{fig:post} f). This
shows that, accounting for variation in the parameter estimates, the
model with only future reward gives a better fit to the data, despite
having one parameter less.

```{r pred, fig.cap="Observed and predicted probability of choosing a visitor. Left-hand side panel: color contour shows the prediction of the learning model using the mode of the posterior distributions of parameters recovered by the statistical analysis. Dots show the frequency of visitor choices for the 12 locations, as well as the corresponding relative cleaner abundance (x axis) and frequency of visitors leaving the station (y axis). Right-hand side panels: scatter plot of the observed and predicted probabilities of choosing a visitor for 12 locations. Line correspond to a perfect match between observed and predicted probabilities. Pseudo $R^2$ shown in the lower right corner corresponds to the fit of a model parameterized with the mode of the posterior distributions. Upper panels show prediction from a model including future and negative reward, lower panels froma  model with only future reward.",out.width='95%',fig.height=8}

source(here("manFigures.R"))
ggarrange(cont.obs.pred.both,scatter.obs.pred.both,
cont.obs.pred.gam,scatter.obs.pred.gam,
          labels=c('a','b','c','d'),common.legend=TRUE,legend = "top")
```

Figure \ref{fig:pred} shows predictions from the two models. On the
left, the colour coded contour shows the prediction of the model for
combinations of cleaner abundance (x axis) and visitor leaving
probability (y axis). Predictions were generated by running the model
using the mode of the posterior distributions as the parameter values,
and varying systematically cleaner abundance and visitor leaving
probability. Colour of the points on top of the contour show the average
frequency with which cleaner fish chose the visitor plate in their last
20 experimental trials. Each point corresponds to a location with a
combination of cleaner abundance and visitor leaving probability. Panels
on the right show how close the observed values for the probability of
choosing the visitor (y axis) are from the predictions of the models (x
axis). The line represents the perfect fit between observed and
predicted values. Predicted values were taken using the mode just as in
the left panels. On the lower right corner of the panel we show the
$pseudo-R^2$ for predictions using the mode of the posterior
distributions. Despite having one more parameter varying, the full model
gives a lower fit to the data than the model without negative reward.
The difference in $pseudo-R^2$ for the point estimates is small, but
using the whole posterior distribution shows the improvement in fit
achieved by eliminating negative reward from the model (Fig.
\ref{fig:post}f). In the supplementary material, we also show that a
model with only negative reward, excluding future rewards ($\gamma=0$,
Fig. \ref{fig:nogamma}), provides a lower fit than either of the ones
presented in the main text.

The main reason for negative and future reward to give different
predictions is the way that cleaner's relative abundance influences the
preference for the visitor clients. Visitor leaving probability has a
similar positive effect on the probability of choosing the visitor
clients on all three models (Fig. \ref{fig:pred}, \ref{fig:nogamma}). In
contrast, cleaner's relative abundance has a different effect in the
model with only future reward, compared to the other two. In the model
with only future reward only intermediate cleaner abundance triggers a
preference for the visitor clients (Fig. \ref{fig:pred} c). In models
with negative reward, both intermediate and low cleaner abundance
trigger a preference for the visitor. (Fig. \ref{fig:pred} a,
\ref{fig:nogamma}).

## Discussion

We have shown that using future rewards in the learning process is the
cognitive strategy that best explains the intra-specific variation in
cleaner performance in the market task. We compared future reward with
the use of visitors behaviour as a primary source of negative reward,
and a combination of both. All three models capture well the positive
relation between visitor leaving behaviour and cleaner performance in
the market task [@triki_Biological_2019]. For both mechanisms it is
indeed necessary to have fleeing behaviour on the side of the visitors
for cleaners to develop a preference for them. The key difference
between future and negative reward emerges in the predicted relation
between cleaner relative abundance and cleaner performance. When cleaner
relative abundance is low a model with only future reward predicts low
performance in the market task regardless of the visitor leaving
probability. In contrast, a model with negative reward predicts the
highest performance with low relative cleaner abundance, particularly
together with high probability of visitor leaving (Fig. \ref{fig:pred}).
Low cleaner abundances mean the market has an excess of demand for
cleaning services. In the model, this translates to a cleaning station
that is frequently full. Thus, when visitors leave, it's likely that the
cleaner will have access to another client, and there will not be much
difference in future reward between choosing a visitor and a resident.
Thus, estimation of future reward will not develop a preference for the
visitor in this conditions, because it matches the state of the market.
On the other hand, the effect of negative reward is unaffected by this
market situation. In a full station, cleaners will get more often the
heterotypic (resident-visitor) option and will develop a preference for
the visitor faster. Note that when cleaner abundance is high situations
with a resident and a visitor will be so rare that neither mechanism
will be very efficient in generating a preference for visitors. When
such choice arises it is still be best to choose the visitor; however,
the learning machinery will not be able to develop this preference
efficiently. Overall, estimation of future reward is then the cognitive
mechanism that allows cleaners to adaptively respond conditions to the
ecological conditions of the biological market.

The cognitive mechanism that our analysis highlights does not require a
direct flow of information between the cleaner and its social
environment. The adaptive responses to local conditions in cleaners is
not only evidenced by their performance in experiments, but also by
changes in their brain anatomy. Indeed, individual cleaners that
performed in the laboratory test according to what is best at the
location in which they were caught had larger forebrains harbouring more
cells than individuals whose performance mismatched locally optimal
decision-rules [@triki_Brain_2020]. This suggests that despite the
overall behavioural adjustment, evidenced here and elsewhere
[@triki_Biological_2019; @triki_Decrease_2018], there are some
cleaners better than others at adjusting their behaviour. Triki *et al.*
[@triki_Brain_2020] refer to these as socially competent cleaners. Social
competence refers to the ability to optimise social behaviour depending
on the available social information [@taborsky_Social_2012a;
@bshary_Cooperation_2015]. However, we have shown here that cleaners
are able to adjust their preference according to the social environment
without using any direct information about the social environment.
Instead cleaners seem to adjust their preference using information from
the visitation patterns of their clients. These patters are of course
determined by the feedback with the cleaner's social environment
(relative abundance). Our models, however, do not include the
possibility of cleaners responding to their relative abundance directly.
The mechanism we present is a general way to learn from the environment
in both asocial and social situations. It would be interesting to
contrast this learning mechanism with one tailored to a social
situation, and see whether such mechanism fits the data better. More
generally, an important challenge ahead is to understand which cognitive
mechanisms evolved exclusively for social life.

One potential difference between cleaners that adjusted adaptively, like
the ones reported in Triki *et al.* [@triki_Brain_2020], is configurational learning or
chunking. The original analysis of the learning model showed that agents
needed two mechanism to solve the market task; to account for the
future, and to assign value to the combination of clients present in the
station [@quinones_Reinforcement_2019]. The latter is referred to as
configurational learning or chunking [@sutherland_Configural_1989;
@miller_Magical_1956]. Theoretical models suggest that the lack of
configurational learning is related to a low frequency with which
stimuli are encountered together [@kolodny_Evolution_2014;
@prat_Role_2021]. Thus, cleaner relative abundance could be related to
this mechanisms as well. Given that the lack of either of these two
mechanisms yields neutral preferences [@quinones_Reinforcement_2019],
we can't, based on the current analysis, distinguish between the two
possibilities. One potential way to distinguish between the two would be
to use an experimental set up designed to test configuration learning on
cleaners with high and low performance in the market task
[@woodbury_Learning_1943; @sutherland_Configural_1989].

Combining mechanistic modelling with empirical data provides a powerful
tool to identify the cognitive processes underlying learning in animals.
The combination overcomes the limitations of the general philosophy in
animal cognition to apply the logic of Lloyd Morgen's canon (Occam's
razor). Excluding basic reinforcement learning explanations (operant
and/or classical conditioning) as a potential explanation in experiments
often warrants animals solving the task on the first possible occasion.
For example, any theory of mind task needs to be solved in the first
trial in order to exclude fast conditioning [@heyes_Theory_1998].
Similarly, subjects need to solve a social learning task on the first
trial to accept imitation as a mechanism over stimulus/local
enhancement. Such strict conditions are virtually never met. For
example, potato washing by Japanese macaques, an iconic example of
social learning, took several years to spread within the group
[@kawamura_Process_1959], meaning that any learner had been repeatedly
exposed to demonstrations before acquisition. Importantly, Galef
[@galef_Question_1992] refuted imitation as mechanism not simply because
of the repeated exposure but because a (rather qualitative) analysis of
the spread of potato washing across individuals did not follow the
prediction based on imitation learning (see also
[@hirata_SweetPotato_2001]). In our case, the number of trials it took
cleaners to learn the solution to the market task would never allow to
exclude an important role of negative reinforcement based on the data
alone. However, fitting model predictions to our data set revealed that
a more complex mechanism (estimation of future reward) fits the data
better.

\newpage

# Supplementary material

```{=tex}
\beginsupplement
```
```{r nogamma, fig.cap="Observed and predicted probability of choosing a visitor for a model without future rewards. Left-hand side panel: color contour shows the prediction of the learning model using the mode of the posterior distributions of parameters recovered by the statistical analysis. Dots show the frequency of visitor choices for the 12 locations, as well as the corresponding relative cleaner abundance (x axis) and frequency of visitors leaving the station (y axis). Right-hand side panel: scatter plot of the observed and predicted probabilities of choosing a visitor for 12 locations. Line correspond to a perfect match between observed and predicted probabilities.",fig.pos = 'H', out.extra = "",out.width='95%',fig.height=8}

ggarrange(cont.obs.pred.Nrew,scatter.obs.pred.Nrew,
          labels=c('a','b'),common.legend=FALSE,legend = "top")

```

```{r param , echo=FALSE,results='asis'}
  cat(' Table: \\label{tab:param} Parameter values with which the model was run 
  in the MCMC. $\\sigma$ refers to the amplitud of the perturbation kernel with the subscript indicating the associated parameter. New values were taken from a uniform distribution. $\\alpha$ refers to the learning rate.

  | Parameter | Value |
|----------:|:-----:|
| Learning rounds | 10000 |
| Reward value | 1 |
| $\\alpha$ | 0.05 |
| $\\sigma_{\\gamma}$ | 0.3 |
| $\\sigma_{\\eta}$ | 4 |
| $\\sigma_{Sca.Const.}$ | 300 |
| Number of chains | 5 |
| Chain lenght | $1^5$ |
')

```

### 2021-12-21 manuscript_1.0/manuscript_1.0.tex
Copies repo from Clean.ActCrit this will be released with manuscript forthcoming

--- 2021-12-21 manuscript_1.0/manuscript_1.0.Rmd
@@
----
-title: Combination of field and experimental data together with computational models 
-  reveal cognitive mechanisms behind cleaner fish behaviour
-#Cognitive and ecological aspects determine cleaner performance
-author:
-  - name: Andrés E. Quiñones 
-    affiliation: "1"
-  - name: Zegni Triki
-    affiliation: "2"
-  - name: Redouan Bshary
-    affiliation: "1"
-address:
-  - code: "1"
-    address: Institute of Biology, University of Neuchâtel, Neuchâtel, Switzerland
-  - code: "2"
-    address: Department of Zoology, Stockholm University, Stockholm, Sweden
+%% Author_tex.tex
+%% V1.0
+%% 2012/13/12
+%% developed by Techset
+%%
+%% This file describes the coding for rsproca.cls
 
-corresp_author_name:  "AE. Quiñones"
-corresp_author_email: "andreseqp@gmail.com"
+\documentclass[]{rsos}%%%%where rsos is the template name
 
-subject:
-  - "Behavioural ecology"
-  - "Cognitive ecology"
-  - "Animal behaviour"
+\usepackage{lineno}
+\linenumbers
 
-keywords:
-  - learning   
-  - cleaners
-  - behaviour
-  - bayesian statisitics
-  - mutualism
+\usepackage[T1]{fontenc}
+\usepackage[utf8]{inputenc}
 
-abstract: |
+% For Pandoc highlighting needs
+
+% Pandoc citation processing
+
+\usepackage{float}
+\usepackage{booktabs}
+\newcommand{\beginsupplement}{ \setcounter{table}{0}     \renewcommand{\thetable}{S\arabic{table}}\setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}}
+
+%%%% *** Do not adjust lengths that control margins, column widths, etc. ***
+
+%%%%%%%%%%% Defining Enunciations  %%%%%%%%%%%
+\newtheorem{theorem}{\bf Theorem}[section]
+\newtheorem{condition}{\bf Condition}[section]
+\newtheorem{corollary}{\bf Corollary}[section]
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{document}
+
+%%%% Article title to be placed here
+\title{Combination of field and experimental data together with computational models reveal cognitive mechanisms behind cleaner fish behaviour}
+
+\author{
+Andrés E. Quiñones$^{1}$,
+Zegni Triki$^{2}$,
+Redouan Bshary$^{1}$}
+
+\address{
+  $^{1}$Institute of Biology, University of Neuchâtel, Neuchâtel, Switzerland\\
+  $^{2}$Department of Zoology, Stockholm University, Stockholm, Sweden}
+%%%% Subject entries to be placed here %%%%
+\subject{
+Behavioural ecology,
+Cognitive ecology,
+Animal behaviour}
+
+%%%% Keyword entries to be placed here %%%%
+\keywords{
+learning,
+cleaners,
+behaviour,
+bayesian statisitics,
+mutualism}
+
+%%%% Insert corresponding author and its email address}
+\corres{
+  AE. Quiñones\\
+  e-mail: \href{mailto:andreseqp@gmail.com}{\nolinkurl{andreseqp@gmail.com}}
+}
+
+%%%% Abstract text to be placed here %%%%%%%%%%%%
+\begin{abstract}
 The same behaviour can be achieved by different mechanistic underpinnings.
@@
 To do this it is necessary to have clearcut predictions for the different candidate mechanisms.
-In here, we use experimental data on the behaviour of the cleaner fish *Labroides* *dimidiatus*, as well as enviromental variables from the location of fish, together with a computational model of the learning mechanisms.
+In here, we use experimental data on the behaviour of the cleaner fish \emph{Labroides} \emph{dimidiatus}, as well as enviromental variables from the location of fish, together with a computational model of the learning mechanisms.
 Using bayesian statistics, we fit key parameters of the computational model that determine the specific learning mechanism.
@@
 We argue that the combination of computational models with data is powerful tool to infer the mechanistic underpinning behind behaviours of interest.
+\end{abstract}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-## Remove this if not required
-ethics: |
-  The Animal Ethics Committee of the Queensland government (DAFF)
-  approved the project (CA 2016/05/970 and CA 2017/05/1063).
+%% Some pieces required from the pandoc template
+\providecommand{\tightlist}{%
+  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
+\providecommand{\EndFirstPage}{%
+}
 
-data_accessibility: |
-  Please provide details on the data availability.
+\maketitle
 
-author_contributions: |
-  AQ and RB designed the study. ZT collected the data. AQ developed the model and 
-  fitted the model parameters to the data. AQ, RB and ZT wrote the manuscript.
-
-## Remove this if not required
-conflict_of_interest: |
-  The authors declate no conflict of interests.
-
-## Remove this if not required
-funding: |
-  This work was supported by the Swiss National Science Foundation (grants
-  number: 31003A_153067/1 and 310030B_173334/1 to R.B.).
-
-## Remove this if not required
-acknowledgements: |
-  ZT and RB kindly thank the staff of Lizard Island Research Station, Dominique
-  Roche, Sharon Wismer, Olivia Rey,Sandra Ann Binning, Elena Levorato and William McNeely for their
-  field support. AQ thanks Florian Hartig for statistical advice.
-
-bibliography: Cleanerlearning.bib
-
-## change to true to add optional line numbering
-lineno: true
-
-header-includes: |
-  ```{=latex}
-  \usepackage{float}
-  \usepackage{booktabs}
-  \newcommand{\beginsupplement}{ \setcounter{table}{0}     \renewcommand{\thetable}{S\arabic{table}}\setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}}
-  ```
-site: bookdown::bookdown_site
-output: 
-  bookdown::pdf_book:
-    base_format: rticles::rsos_article
----
-
-## Introduction
-
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = FALSE,warning = FALSE,message=FALSE)
-library(here)
-```
+\hypertarget{introduction}{%
+\subsection{Introduction}\label{introduction}}
 
@@
 interactions such as pollination, nitrogen fixation or parasite removal
-[@begon_Ecology_2006]. When partners in these mutualistic interactions
+\citep{begon_Ecology_2006}. When partners in these mutualistic interactions
 are able to choose their interaction partner, their investment and the
 return they obtain can be understood as a biological market
-[@hammerstein_Biological_2016; @leimar_Cooperation_2010;
-@noe_Biological_1994a;@noe_Biological_1995a]. Thus, we expect supply
+\citep{hammerstein_Biological_2016, leimar_Cooperation_2010, noe_Biological_1994a, noe_Biological_1995a}. Thus, we expect supply
 and demand of the good and services being exchanged to determine the
@@
 One example of strategic adjustment in a biological market is the marine
-cleaning mutualism involving the cleaner fish *Labroides dimidiatus* and
-'client' fish. Clients offer themselves as food patches for cleaners to
+cleaning mutualism involving the cleaner fish \emph{Labroides dimidiatus} and
+`client' fish. Clients offer themselves as food patches for cleaners to
 remove ectoparasites, which gives the cleaners calories and the clients
-improved health [@waldie_LongTerm_2011;
-@ros_Does_2011;@triki_Effects_2016]. As cleaners have about 2000
-interactions per day [@grutter_Relationship_1995], they regularly face
+improved health \citep{waldie_LongTerm_2011, ros_Does_2011, triki_Effects_2016}. As cleaners have about 2000
+interactions per day \citep{grutter_Relationship_1995}, they regularly face
 the situation that two clients seek cleaning simultaneously. In such
-conditions, it is important to distinguish between 'resident' and
-'visitor' client species [@bshary_Cleaner_2001a]. The residents have
+conditions, it is important to distinguish between `resident' and
+`visitor' client species \citep{bshary_Cleaner_2001a}. The residents have
 small home ranges and hence access to only the local cleaner, while the
@@
 visitors have been observed to use their partner choice options in that
-way [@bshary_Choosy_2002], which may explain why cleaners give
+way \citep{bshary_Choosy_2002}, which may explain why cleaners give
 visitors service priority in a field study in the Red Sea
-[@bshary_Cleaner_2001a]. More generally, cleaners apparently prefer to
-interact with visitors [@triki_Marine_2021]. Such a preference may be
+\citep{bshary_Cleaner_2001a}. More generally, cleaners apparently prefer to
+interact with visitors \citep{triki_Marine_2021}. Such a preference may be
 linked to a client's value as a food patch; visitors are on average
-larger than residents [ @bshary_Cleaner_2001a], and size is positively
-correlated with parasite load [@grutter_Relationship_1995a]. However, 
+larger than residents \citep{bshary_Cleaner_2001a}, and size is positively
+correlated with parasite load \citep{grutter_Relationship_1995a}. However,
 early laboratory
 experiments showed that leaving causes service priority independent of
-client value [@bshary_Asymmetric_2002]. The experiments consisted of a
+client value \citep{bshary_Asymmetric_2002}. The experiments consisted of a
 simultaneous two-choice task, where cleaners had to decide which of two
@@
 and eat mashed prawn of it. One plate was made to behave like a
-resident, i.e. it would remain until the cleaner had eaten off it. The
-other plate was made to behave like a visitor, i.e. it would be removed
+resident, i.e.~it would remain until the cleaner had eaten off it. The
+other plate was made to behave like a visitor, i.e.~it would be removed
 if not inspected first. Cleaners learned to prefer the visitor plate and
-hence obtained the double amount of food [@bshary_Asymmetric_2002].
+hence obtained the double amount of food \citep{bshary_Asymmetric_2002}.
 Adult cleaner fish outperform various primates as well as rats and
 pigeons in this original version of the biological market task
-[@salwiczek_Adult_2012; @zentall_Early_2017]; only African grey
-parrots solve this task as well [@pepperberg_Can_2014].
+\citep{salwiczek_Adult_2012, zentall_Early_2017}; only African grey
+parrots solve this task as well \citep{pepperberg_Can_2014}.
 
 Recent research has refined our view on partner choice and priority of
-access in the *L. dimidiatus* cleaning mutualism, and as a consequence
+access in the \emph{L. dimidiatus} cleaning mutualism, and as a consequence
 performance in the biological market task. First, details of the task
-presentation may matter; i.e. what relevant information is encoded in
+presentation may matter; i.e.~what relevant information is encoded in
 the design of the two plates (colour versus size;
-[@wismer_Cuebased_2019]), or whether the information is in the colour of
-the food [@pretot_Comparative_2021; @pretot_Comparing_2016], and
+\citep{wismer_Cuebased_2019}), or whether the information is in the colour of
+the food \citep{pretot_Comparative_2021, pretot_Comparing_2016}, and
 whether the food is visible or hidden/released only when the subjects
-made choices on a touch screen [@pretot_Factors_2016]. Second, it
+made choices on a touch screen \citep{pretot_Factors_2016}. Second, it
 appears that cleaner and client densities in nature affect how cleaners
 perform in the original market task: when densities are low, cleaners
-are more likely to fail to complete the task [@triki_Biological_2019;
-@triki_Decrease_2018; @wismer_Variation_2014]. The apparent explanation
+are more likely to fail to complete the task \citep{triki_Biological_2019, triki_Decrease_2018, wismer_Variation_2014}. The apparent explanation
 for this failure is that visitor clients are less likely to exert their
 choice options (and hence wait for inspection if made to wait) when
-cleaner fish densities are low [@triki_Brain_2020]. This change in
+cleaner fish densities are low \citep{triki_Brain_2020}. This change in
 behaviour may be due to the fact that when cleaner densities are low,
@@
 have larger forebrains harbouring more cells than cleaners from
-low-density areas [@triki_Brain_2020], on a local scale those
+low-density areas \citep{triki_Brain_2020}, on a local scale those
 individuals that perform in the market task in a way that corresponds to
 the locally optimal strategy (solving/failing the task when living in
-high/low density) have relatively larger forebrains [@triki_Brain_2020].
+high/low density) have relatively larger forebrains \citep{triki_Brain_2020}.
 Taken together, empirical results clearly show major intra- and
@@
 investigation of the underlying cognitive machinery, from perception to
-decision-making [@shettleworth_Cognition_2009].
+decision-making \citep{shettleworth_Cognition_2009}.
 
@@
 their predictions in light of the behavioural data (e.g.
-[@dubois_Model_2021]). By varying the cognitive tool kit, one can assess
+\citep{dubois_Model_2021}). By varying the cognitive tool kit, one can assess
 which minimal kit is necessary to solve the task at hand. This approach
-has been used to analyse the market task [@prat_Role_2021;
-@quinones_Reinforcement_2019]. Learning models showed that basic
+has been used to analyse the market task \citep{prat_Role_2021, quinones_Reinforcement_2019}. Learning models showed that basic
 reinforcement learning does not suffice to solve the task, this is
@@
 the same strategic option, paired with a fish with the alternative
-strategic option) [@quinones_Reinforcement_2019]. In addition, cleaners
+strategic option) \citep{quinones_Reinforcement_2019}. In addition, cleaners
 need to account for the future consequences of current decisions. In the
 model, this could be achieved in two non-mutually exclusive ways
-[@quinones_Reinforcement_2019]: through low temporal discounting of
+\citep{quinones_Reinforcement_2019}: through low temporal discounting of
 future effects and/or through perceiving a visitor client leaving as
-psychological punishment (i.e. as a negative reinforcer). Given that a
+psychological punishment (i.e.~as a negative reinforcer). Given that a
 negative reinforcer is part of the ubiquitous learning mechanism termed
-operant conditioning [@thorndike_Animal_1898; @skinner_Behavior_1938], 
+operant conditioning \citep{thorndike_Animal_1898, skinner_Behavior_1938},
 this explanation can be
@@
 effects of an action is considered an advanced cognitive ability
-[@suddendorf_Evolution_2007]. Here, we fitted our model to the empirical
+\citep{suddendorf_Evolution_2007}. Here, we fitted our model to the empirical
 data on fish densities and cleaner fish performance in the market task
@@
 
-## Methods
+\hypertarget{methods}{%
+\subsection{Methods}\label{methods}}
 
-### Overview
+\hypertarget{overview}{%
+\subsubsection{Overview}\label{overview}}
 
-We used the data from [@triki_Biological_2019] to fit the parameters of
-the model analysed in [@quinones_Reinforcement_2019]. For the bayesian
+We used the data from \citep{triki_Biological_2019} to fit the parameters of
+the model analysed in \citep{quinones_Reinforcement_2019}. For the bayesian
 fitting procedure we used Markov Chain Monte Carlo (MCMC) with a
@@
 
-### The model
+\hypertarget{the-model}{%
+\subsubsection{The model}\label{the-model}}
 
@@
 reward the individual obtains (prediction error)
-[@sutton_Reinforcement_2018; @rescorla_Theory_1972]; and it is carried
+\citep{sutton_Reinforcement_2018, rescorla_Theory_1972}; and it is carried
 in the direction that would lead to more reward being obtained, given
 the new information. Further details of the model implementation can be
-found in the paper [@quinones_Reinforcement_2019]. The model analysis
-points to the relevance of two parameters. First, $\gamma$ measures how
+found in the paper \citep{quinones_Reinforcement_2019}. The model analysis
+points to the relevance of two parameters. First, \(\gamma\) measures how
 much individuals include future rewards in their decision updates. If
-$\gamma=0$, individuals only use the immediate reward obtained from a
-cleaning interaction. As $\gamma$ increases individuals include more the
+\(\gamma=0\), individuals only use the immediate reward obtained from a
+cleaning interaction. As \(\gamma\) increases individuals include more the
 reward obtained from the subsequent choices. That amounts to calculating
 and using for decision making the future expected rewards in action.
-Second, $\eta$ measures how much individuals include in their reward the
+Second, \(\eta\) measures how much individuals include in their reward the
 fleeing behaviour of visitor clients as a negative component. Both of
 these parameters allow individuals to use in their estimates the future
-effects of their choices. The model analysis by Quiñones *et al*
-[@quinones_Reinforcement_2019] shows that without either of them, learning
+effects of their choices. The model analysis by Quiñones \emph{et al}
+\citep{quinones_Reinforcement_2019} shows that without either of them, learning
 individuals cannot develop a preference for the visitor client. The
@@
 that under very high client (relative) abundance the presence of future
-rewards ($\gamma>0$) no longer favours the preference for the ephemeral
+rewards (\(\gamma>0\)) no longer favours the preference for the ephemeral
 clients, this effect does not occur with negative reward mediated by
-client behaviour ($\eta$). Thus, the analysis suggests that future
+client behaviour (\(\eta\)). Thus, the analysis suggests that future
 reward as an explanation for cleaner ability to prefer visitors is
-supported by Triki *et al* [@triki_Biological_2019] data. However, a combination of
+supported by Triki \emph{et al} \citep{triki_Biological_2019} data. However, a combination of
 future and negative rewards, could still be a better explanation for the
 data. In the current analysis, we will use the data from
-[@triki_Biological_2019] to fit some of the model parameters, particularly
-relevant we will fit $\gamma$ and $\eta$ to find out whether each or a
+\citep{triki_Biological_2019} to fit some of the model parameters, particularly
+relevant we will fit \(\gamma\) and \(\eta\) to find out whether each or a
 combination of these effects is a better explanation for the pattern
@@
 
-### Data explanation
+\hypertarget{data-explanation}{%
+\subsubsection{Data explanation}\label{data-explanation}}
 
-*Insert here brief description of the data and data collection*
+\emph{Insert here brief description of the data and data collection}
 
@@
 of clients define not only the probability of residents and visitors,
-but also how often the cleaning station is empty (e.g. there are no
+but also how often the cleaning station is empty (e.g.~there are no
 clients to be cleaned). The more cleaners there are, the more options
@@
 
-## Results
+\hypertarget{results}{%
+\subsection{Results}\label{results}}
 
-```{r post, fig.cap="Posterior distributions for parameter values $\\gamma$, $\\eta$ and the scaling constant.
-We show the kernel density estimates, below the mode (black point) and the 65\\% (light blue) and 95\\% (grey)  highest posterior density interval for the three paramteres.
+\begin{figure}
+
+{\centering \includegraphics[width=0.95\linewidth]{manuscript_1.0_files/figure-latex/post-1}
+
+}
+
+\caption{Posterior distributions for parameter values $\gamma$, $\eta$ and the scaling constant.
+We show the kernel density estimates, below the mode (black point) and the 65\% (light blue) and 95\% (grey)  highest posterior density interval for the three paramteres.
 On the left (panels a, c and c) posterior distributions for a model with   all three parameters; while on the right (b and d) a model without negative reward.
-Panel f shows a measure of fit for both models, namely the distribution of pseudo-$R^2$ obtained from sampling the posterior distribution of parameter values.",out.width='95%',fig.height=9}
-require(data.table)
-library(coda)
-library(ggplot2)
-library(cowplot)
-library(ggdist)
-source(here("../R_files/posPlots.R"))
-source(here("loadData.R"))
-library("jsonlite")
-
-# Name of the folders containing the MCMC runs
-scen1<-"MCMCclean_gam_nRew_sca_"
-scen2<-"MCMCclean_gam_sca_"
-scen3<-"MCMCclean_Nrew_sca_"
-
-# NLables names for the three scenarios
-labels.Scen<-c("both","gam","Nrew")
-labelsPlot.Scen<-c("Full model","Future reward","Negative reward")
-
-## Load files --------------------------------------------------------------
-
-# Defaults for MCMC analysis
-burn.in<-1000
-thinning<-100
-
-MCMCdata1<-loadMCMCrun(scen1,thinning = thinning,burn.in = burn.in)
-MCMCdata2<-loadMCMCrun(scen2,thinning = thinning,burn.in = burn.in)
-MCMCdata3<-loadMCMCrun(scen3,thinning = thinning,burn.in = burn.in)
-
-# Create list with the data, convenient to use CODA for diagnostics
-mcmcList.1<-mcmc.list(do.call(list,lapply(unique(MCMCdata1$seed), function(repli){
-  rundata<-MCMCdata1[seed==repli]
-  mcmcRun<-mcmc(rundata[,.(gamma,negReward,scaleConst)],thin = thinning)#
-  return(mcmcRun)
-})))
-
-mcmcList.2<-mcmc.list(do.call(list,lapply(unique(MCMCdata2$seed), function(repli){
-  rundata<-MCMCdata2[seed==repli]
-  mcmcRun<-mcmc(rundata[,.(gamma,scaleConst)],thin = thinning)#
-  return(mcmcRun)
-})))
-
-mcmcList.2<-mcmc.list(do.call(list,lapply(unique(MCMCdata2$seed), function(repli){
-  rundata<-MCMCdata2[seed==repli]
-  mcmcRun<-mcmc(rundata[,.(negReward,scaleConst)],thin = thinning)#
-  return(mcmcRun)
-})))
-
-mcmcList.3<-mcmc.list(do.call(list,lapply(unique(MCMCdata3$seed), function(repli){
-  rundata<-MCMCdata3[seed==repli]
-  mcmcRun<-mcmc(rundata[,.(gamma,negReward,scaleConst)],thin = 100)#
-  return(mcmcRun)
-})))
-
-## Density plots with gg -------------------------------------------------------
-
-## Define the boundaries for credible intervals using High Density Interval
-
-intervals<-c(0.66,0.95)
-
-cuts.1<-lapply(MCMCdata1[,.(gamma,negReward,scaleConst)],
-             function(x){
-               c(mode_hdci(x,.width = intervals[c(2,1)])$ymin,
-                 mode_hdci(x,.width = intervals)$ymax)  
-})
-
-cuts.2<-lapply(MCMCdata2[,.(gamma,scaleConst)],
-               function(x){
-                 c(mode_hdi(x,.width = intervals[c(2,1)])$ymin,
-                   mode_hdi(x,.width = intervals)$ymax)  
-               })
-
-cuts.3<-lapply(MCMCdata3[,.(negReward,scaleConst)],
-               function(x){
-                 c(mode_hdi(x,.width = intervals[c(2,1)])$ymin,
-                   mode_hdi(x,.width = intervals)$ymax)  
-               })
-
-# get all the likelihoods from the posterior for all models
-loglikehoods.all<-data.table(lglikelihood=c(MCMCdata1$fit,MCMCdata2$fit,
-                                             MCMCdata3$fit),
-                              model=c(rep(labels.Scen[1],length(MCMCdata1$fit)),
-                                      rep(labels.Scen[2],length(MCMCdata2$fit)),
-                                      rep(labels.Scen[3],length(MCMCdata3$fit))
-                                      ))
-
-# Read field data to calculate null log-likelihood
-fieldData<-fread(here("Data","data_ABC_cleaner_abs.txt"))
-
-nullLikehood<-sum(dbinom(x=fieldData[,score_visitor],
-                         size = 20,prob = 0.5,log = TRUE))
-
-# calculate pseudo R^2
-loglikehoods.all[,Rsqrd:=1-lglikelihood/nullLikehood]
-
-panel.rsqr.all<-
-  ggplot(data=loglikehoods.all[is.finite(lglikelihood)],
-                  aes(y=model,x=Rsqrd,fill=model))+
-  stat_halfeye(alpha=0.5,point_size=3)+
-  theme_classic()+xlim(-0.5,0.3)+
-  scale_fill_manual(values=c("#1b9e77","#d95f02","#7570b3"),
-  name = "Model", labels = labelsPlot.Scen)+
-  geom_vline(xintercept = 0,color="black",size=1)+
-  theme(legend.position = c(.3, .80),legend.key.size = unit(0.4,'cm'),
-        axis.text.y = element_blank())
-
-plot_grid(nrow=3,align = "v",byrow = FALSE,
-          # Full model - \gamma
-          ggplot(data=MCMCdata1,aes(x=gamma)) + 
-            stat_halfeye(aes(fill=stat(cut(x,breaks = cuts.1$gamma))),
-                         point_interval = mode_hdi, .width = c(.66, .95),point_size=3,
-                         show.legend=FALSE) + 
-            labs(title=labelsPlot.Scen[1],subtitle = expression(gamma),x="",y="")+
-            theme_classic()+scale_fill_manual(values=c("gray85","skyblue","gray85")),
-          # \eta
-          ggplot(data=MCMCdata1,aes(x=negReward)) + 
-            stat_halfeye(aes(fill=stat(cut(x,breaks = cuts.1$negReward))),
-                         point_interval = mode_hdi, .width = c(.66, .95),point_size=3,
-                         show.legend=FALSE)+theme_classic()+
-            scale_fill_manual(values=c("gray85","skyblue","gray85"))+
-            labs(subtitle = expression(eta),x="",y="")+xlim(-5,5),
-          # Scale Constant
-          ggplot(data=MCMCdata1,aes(x=scaleConst)) + 
-            stat_halfeye(aes(fill=stat(cut(x,breaks = cuts.1$scaleConst))),
-                         point_interval = mode_hdi, .width = c(.66, .95),point_size=3,
-                         show.legend=FALSE)+
-            theme_classic()+scale_fill_manual(values=c("skyblue","gray85"))+
-          labs(subtitle = "Scalling const.",x="",y="")+xlim(-2,1500)+theme_classic(),
-          # Future reward only model - \gamma
-          ggplot(data=MCMCdata2,aes(x=gamma)) +
-            stat_halfeye(aes(fill=stat(cut(x,breaks = cuts.2$gamma))),
-                         point_interval = mode_hdi, .width = c(.66, .95),point_size=3,
-                         show.legend=FALSE) +
-            scale_fill_manual(values=c("gray85","skyblue","gray85"))+
-            labs(title=labelsPlot.Scen[2],subtitle = expression(gamma),x="",y="")+
-            theme_classic(),
-          # Scalling constant
-          ggplot(data=MCMCdata2,aes(x=scaleConst)) +
-            stat_halfeye(aes(fill=stat(cut(x,breaks = cuts.2$scaleConst))),
-                         point_interval = mode_hdi, .width = c(.66, .95),point_size=3,
-                         show.legend=FALSE) +
-            scale_fill_manual(values=c("gray85","skyblue","gray85"))+
-            labs(subtitle = "Scalling const.",x="",y="")+
-            theme_classic(),
-          # Pseudo R^2
-          panel.rsqr.all+labs(subtitle = expression(pseudo-R^2),x="",y=""),
-          labels=c('a','b','c','d','e')
-)
-
-```
+Panel f shows a measure of fit for both models, namely the distribution of pseudo-$R^2$ obtained from sampling the posterior distribution of parameter values.}\label{fig:post}
+\end{figure}
 
@@
 the bulk of the posterior distribution for the parameter tuning negative
-reward ($\eta$ panel e) is around zero. Thus, the shape of the posterior
+reward (\(\eta\) panel e) is around zero. Thus, the shape of the posterior
 and its credible intervals suggest the absence of negative reward to be
-well supported by the data. As for $\gamma$, the confidence intervals
+well supported by the data. As for \(\gamma\), the confidence intervals
 also includes zero, but the mode of the posterior is around 0.5. Thus,
-we run the analysis setting $\eta$ to zero. Figure \ref{fig:post} panels
+we run the analysis setting \(\eta\) to zero. Figure \ref{fig:post} panels
 b and d, show the posterior distributions of the two parameters
 estimated. Not surprisingly, under a model without negative reward, the
-distribution of $\gamma$ shifts to higher values. Under the new model,
-the estimates of $\gamma$ do not include zero, the distribution is
-centered around $0.5$. To asses the fit of the two models we calculated
-the $pseudo-R^2$ [@mcfadden_Conditional_1974], which is a standard
-measure of fit for logistic regression. In that context, $pseudo-R^2$
+distribution of \(\gamma\) shifts to higher values. Under the new model,
+the estimates of \(\gamma\) do not include zero, the distribution is
+centered around \(0.5\). To asses the fit of the two models we calculated
+the \(pseudo-R^2\) \citep{mcfadden_Conditional_1974}, which is a standard
+measure of fit for logistic regression. In that context, \(pseudo-R^2\)
 uses the log-likelihood of the data given the model, relative to the
@@
 measure of fit. Given that our model is not a logistic regression, we
-measure the $pseudo-R^2$ in relation to the log-likelihood of a model
-with parameters $\gamma$ and $\eta$ set to zero. This in practice
+measure the \(pseudo-R^2\) in relation to the log-likelihood of a model
+with parameters \(\gamma\) and \(\eta\) set to zero. This in practice
 amounts to a model that has neutral preference between the two options.
 In panel f of figure \ref{fig:post} we show the distribution of
-$pseudo-R^2$ calculated using samples from the posterior distributions
+\(pseudo-R^2\) calculated using samples from the posterior distributions
 shown before, as well as from a model with negative reward but without
-future reward. Note, $pseudo-R^2$ can have negative values, that is when
+future reward. Note, \(pseudo-R^2\) can have negative values, that is when
 the log-likelihood of the model is lower than that of a model that
 triggers neutral preferences. Even though, the peak of the three
-$pseudo-R^2$ distributions is not very different, the model with only
-future reward produces a distribution of $pseudo-R^2$ where more values
+\(pseudo-R^2\) distributions is not very different, the model with only
+future reward produces a distribution of \(pseudo-R^2\) where more values
 are positive (to the right of black line in Fig. \ref{fig:post} f). This
@@
 
-```{r pred, fig.cap="Observed and predicted probability of choosing a visitor.
+\begin{figure}
+
+{\centering \includegraphics[width=0.95\linewidth]{manuscript_1.0_files/figure-latex/pred-1}
+
+}
+
+\caption{Observed and predicted probability of choosing a visitor.
 Left-hand side panel: color contour shows the prediction of the learning model using the mode of the posterior distributions of parameters recovered by the statistical analysis.
@@
 Pseudo $R^2$ shown in the lower right corner corresponds to the fit of a model parameterized with the mode of the posterior distributions.
-Upper panels show prediction from a model including future and negative reward, lower panels froma  model with only future reward.",out.width='95%',fig.height=8}
-
-source(here("manFigures.R"))
-ggarrange(cont.obs.pred.both,scatter.obs.pred.both,
-cont.obs.pred.gam,scatter.obs.pred.gam,
-          labels=c('a','b','c','d'),common.legend=TRUE,legend = "top")
-```
+Upper panels show prediction from a model including future and negative reward, lower panels froma  model with only future reward.}\label{fig:pred}
+\end{figure}
 
@@
 the left panels. On the lower right corner of the panel we show the
-$pseudo-R^2$ for predictions using the mode of the posterior
+\(pseudo-R^2\) for predictions using the mode of the posterior
 distributions. Despite having one more parameter varying, the full model
 gives a lower fit to the data than the model without negative reward.
-The difference in $pseudo-R^2$ for the point estimates is small, but
+The difference in \(pseudo-R^2\) for the point estimates is small, but
 using the whole posterior distribution shows the improvement in fit
@@
 \ref{fig:post}f). In the supplementary material, we also show that a
-model with only negative reward, excluding future rewards ($\gamma=0$,
+model with only negative reward, excluding future rewards (\(\gamma=0\),
 Fig. \ref{fig:nogamma}), provides a lower fit than either of the ones
@@
 
-## Discussion
+\hypertarget{discussion}{%
+\subsection{Discussion}\label{discussion}}
 
@@
 relation between visitor leaving behaviour and cleaner performance in
-the market task [@triki_Biological_2019]. For both mechanisms it is
+the market task \citep{triki_Biological_2019}. For both mechanisms it is
 indeed necessary to have fleeing behaviour on the side of the visitors
@@
 cells than individuals whose performance mismatched locally optimal
-decision-rules [@triki_Brain_2020]. This suggests that despite the
+decision-rules \citep{triki_Brain_2020}. This suggests that despite the
 overall behavioural adjustment, evidenced here and elsewhere
-[@triki_Biological_2019; @triki_Decrease_2018], there are some
-cleaners better than others at adjusting their behaviour. Triki *et al.*
-[@triki_Brain_2020] refer to these as socially competent cleaners. Social
+\citep{triki_Biological_2019, triki_Decrease_2018}, there are some
+cleaners better than others at adjusting their behaviour. Triki \emph{et al.}
+\citep{triki_Brain_2020} refer to these as socially competent cleaners. Social
 competence refers to the ability to optimise social behaviour depending
-on the available social information [@taborsky_Social_2012a;
-@bshary_Cooperation_2015]. However, we have shown here that cleaners
+on the available social information \citep{taborsky_Social_2012a, bshary_Cooperation_2015}. However, we have shown here that cleaners
 are able to adjust their preference according to the social environment
@@
 One potential difference between cleaners that adjusted adaptively, like
-the ones reported in Triki *et al.* [@triki_Brain_2020], is configurational learning or
+the ones reported in Triki \emph{et al.} \citep{triki_Brain_2020}, is configurational learning or
 chunking. The original analysis of the learning model showed that agents
@@
 future, and to assign value to the combination of clients present in the
-station [@quinones_Reinforcement_2019]. The latter is referred to as
-configurational learning or chunking [@sutherland_Configural_1989;
-@miller_Magical_1956]. Theoretical models suggest that the lack of
+station \citep{quinones_Reinforcement_2019}. The latter is referred to as
+configurational learning or chunking \citep{sutherland_Configural_1989, miller_Magical_1956}. Theoretical models suggest that the lack of
 configurational learning is related to a low frequency with which
-stimuli are encountered together [@kolodny_Evolution_2014;
-@prat_Role_2021]. Thus, cleaner relative abundance could be related to
+stimuli are encountered together \citep{kolodny_Evolution_2014, prat_Role_2021}. Thus, cleaner relative abundance could be related to
 this mechanisms as well. Given that the lack of either of these two
-mechanisms yields neutral preferences [@quinones_Reinforcement_2019],
+mechanisms yields neutral preferences \citep{quinones_Reinforcement_2019},
 we can't, based on the current analysis, distinguish between the two
@@
 cleaners with high and low performance in the market task
-[@woodbury_Learning_1943; @sutherland_Configural_1989].
+\citep{woodbury_Learning_1943, sutherland_Configural_1989}.
 
@@
 For example, any theory of mind task needs to be solved in the first
-trial in order to exclude fast conditioning [@heyes_Theory_1998].
+trial in order to exclude fast conditioning \citep{heyes_Theory_1998}.
 Similarly, subjects need to solve a social learning task on the first
@@
 social learning, took several years to spread within the group
-[@kawamura_Process_1959], meaning that any learner had been repeatedly
+\citep{kawamura_Process_1959}, meaning that any learner had been repeatedly
 exposed to demonstrations before acquisition. Importantly, Galef
-[@galef_Question_1992] refuted imitation as mechanism not simply because
+\citep{galef_Question_1992} refuted imitation as mechanism not simply because
 of the repeated exposure but because a (rather qualitative) analysis of
@@
 prediction based on imitation learning (see also
-[@hirata_SweetPotato_2001]). In our case, the number of trials it took
+\citep{hirata_SweetPotato_2001}). In our case, the number of trials it took
 cleaners to learn the solution to the market task would never allow to
@@
 
-# Supplementary material
+\hypertarget{supplementary-material}{%
+\section{Supplementary material}\label{supplementary-material}}
 
-```{=tex}
 \beginsupplement
-```
-```{r nogamma, fig.cap="Observed and predicted probability of choosing a visitor for a model without future rewards.
+
+\begin{figure}[H]
+
+{\centering \includegraphics[width=0.95\linewidth,]{manuscript_1.0_files/figure-latex/nogamma-1}
+
+}
+
+\caption{Observed and predicted probability of choosing a visitor for a model without future rewards.
 Left-hand side panel: color contour shows the prediction of the learning model using the mode of the posterior distributions of parameters recovered by the statistical analysis.
@@
 Right-hand side panel: scatter plot of the observed and predicted probabilities of choosing a visitor for 12 locations.
-Line correspond to a perfect match between observed and predicted probabilities.",fig.pos = 'H', out.extra = "",out.width='95%',fig.height=8}
+Line correspond to a perfect match between observed and predicted probabilities.}\label{fig:nogamma}
+\end{figure}
 
-ggarrange(cont.obs.pred.Nrew,scatter.obs.pred.Nrew,
-          labels=c('a','b'),common.legend=FALSE,legend = "top")
+\begin{longtable}[]{@{}rc@{}}
+\caption{\label{tab:param} Parameter values with which the model was run
+in the MCMC.
+\(\sigma\) refers to the amplitud of the perturbation kernel with the subscript indicating the associated parameter.
+New values were taken from a uniform distribution.
+\(\alpha\) refers to the learning rate.}\tabularnewline
+\toprule
+Parameter & Value \\
+\midrule
+\endfirsthead
+\toprule
+Parameter & Value \\
+\midrule
+\endhead
+Learning rounds & 10000 \\
+Reward value & 1 \\
+\(\alpha\) & 0.05 \\
+\(\sigma_{\gamma}\) & 0.3 \\
+\(\sigma_{\eta}\) & 4 \\
+\(\sigma_{Sca.Const.}\) & 300 \\
+Number of chains & 5 \\
+Chain lenght & \(1^5\) \\
+\bottomrule
+\end{longtable}
 
-```
+\ethics{The Animal Ethics Committee of the Queensland government (DAFF)
+approved the project (CA 2016/05/970 and CA 2017/05/1063).}
 
-```{r param , echo=FALSE,results='asis'}
-  cat(' Table: \\label{tab:param} Parameter values with which the model was run 
-  in the MCMC.
-$\\sigma$ refers to the amplitud of the perturbation kernel with the subscript indicating the associated parameter.
-New values were taken from a uniform distribution.
-$\\alpha$ refers to the learning rate.
+\dataccess{Please provide details on the data availability.}
 
-  | Parameter | Value |
-|----------:|:-----:|
-| Learning rounds | 10000 |
-| Reward value | 1 |
-| $\\alpha$ | 0.05 |
-| $\\sigma_{\\gamma}$ | 0.3 |
-| $\\sigma_{\\eta}$ | 4 |
-| $\\sigma_{Sca.Const.}$ | 300 |
-| Number of chains | 5 |
-| Chain lenght | $1^5$ |
-')
+\aucontribute{AQ and RB designed the study. ZT collected the data. AQ developed the model and
+fitted the model parameters to the data. AQ, RB and ZT wrote the manuscript.}
 
-```
+\competing{The authors declate no conflict of interests.}
+
+\funding{This work was supported by the Swiss National Science Foundation (grants
+number: 31003A\_153067/1 and 310030B\_173334/1 to R.B.).}
+
+\ack{ZT and RB kindly thank the staff of Lizard Island Research Station, Dominique
+Roche, Sharon Wismer, Olivia Rey,Sandra Ann Binning, Elena Levorato and William McNeely for their
+field support. AQ thanks Florian Hartig for statistical advice.}
+
+\bibliographystyle{RS}
+\bibliography{Cleanerlearning.bib}
+
+\end{document}

### 2021-12-21 ActCrit.cpp

@@ -1,0 +1,775 @@
+// ActCrit.cpp : Defines the entry point for the console application.
+//
+/*=============================================================================
+ActCrit.cpp
+===============================================================================
+
+This is the main file of the project exploring a simple learning model in the
+context of the cleaner wrasse mutualism. 
+The model uses the actor-critic methods from reinforcement learning, 
+to teach an agent to solve the market experiment that cleaners face in 
+experimental trials. In the market experiment individuals are offered two 
+options of clients to clean. This options can be a visitor, a resident, or 
+the absence of clients. The difference between the two types of 
+clients is that visitors leave the cleaning station when they are not served, 
+while residents wait; thus, are available in the next time step.There are two 
+types of agent. Fully Aware Agents (FAA) estimate value for 
+9 state-action pairs. In contrast, partially Aware agents 
+(PAA) estimate value for 3 potential actions. 
+
+
+
+
+Written by:
+
+Andr?s E. Qui?ones
+Posdoctoral researcher
+Behavioural Ecology Group
+Institute of Biology
+University of Neuch?tel
+Switzerland
+
+Start date:
+5 April 2017
+
+=============================================================================*/
+
+#include <stdio.h>
+#include <cstdlib>
+#include <math.h>
+#include <iostream>
+#include <fstream>
+#include <omp.h>
+#include "random.h"
+#include "json.hpp"       
+// Header for reading and using JSON files see https://github.com/nlohmann/json
+
+
+#define GET_VARIABLE_NAME(Variable) (#Variable)
+
+using namespace std;
+using json = nlohmann::json;
+
+// General parameters
+
+// Classes
+
+enum client { resident, visitor, absence };																		
+// clients can be resident, visitors, or be absent
+enum learPar { alphaPar, gammaPar, netaPar , alphathPar};
+
+enum learnScenario {nature, experiment, marketExperiment, ExtendedMarket};
+
+class agent													// Learning agent
+{
+public:
+	agent(double alphaI, double gammaI, bool netaI, 
+		double alphathI, double initVal);
[…]

### 2021-12-21 aesth_par.R

@@ -1,0 +1,25 @@
+# ----------- Aesthetic paramters ------------------#
+
+# Define Colours -------------------------------------------------------
+
+library("wesanderson")
+
+colours <- c(rgb(red = .0, green = 0, blue = 0.8, alpha = 0.5),
+             rgb(red = .8, green = 0.8, blue = 0, alpha = 0.5))
+
+colboxes<- c('#d7191c','#fdae61','#2b83ba',"black")
+
+palette('default')
+
+colorValues <- c("#1b9e77","#d95f02","#7570b3",
+                 "#e7298a","#66a61e","#e6ab02")[6:1]
+
+paletteMeans <- colorRampPalette(c('#d73027','#fc8d59','#fee090',
+                                   '#e0f3f8','#91bfdb','#4575b4')[6:1],
+                                 alpha=TRUE)
+
+paletteVar <- colorRampPalette(c('#d8b365','#f5f5f5','#5ab4ac'),alpha=TRUE)
+
+
+zegniPal <- wes_palette("Zissou1",100, type = "continuous")
+

### 2021-12-21 analysisMCMC.R

@@ -1,0 +1,563 @@
+##### Analysis of the Aproximate Bayesian Computation to estimating learning
+##### parameters in the AC models using data from experiments and the field
+
+## Libraries
+require(here)
+require(data.table)
+library(coda)
+library(ggplot2)
+library(cowplot)
+library(ggdist)
+source(here("../R_files/posPlots.R"))
+source(here("loadData.R"))
+library("jsonlite")
+
+# Name of the folders containing the MCMC runs
+scen1<-"MCMCclean_gam_nRew_sca_"
+scen2<-"MCMCclean_gam_sca_"
+scen3<-"MCMCclean_Nrew_sca_"
+
+# NLables names for the three scenarios
+labels.Scen<-c("both","gam","Nrew")
+labelsPlot.Scen<-c("Full model","Future reward","Negative reward")
+
+## Load files --------------------------------------------------------------
+
+# Defaults for MCMC analysis
+burn.in<-1000
+thinning<-100
+
+
+MCMCdata1<-loadMCMCrun(scen1,thinning = thinning,burn.in = burn.in)
+MCMCdata2<-loadMCMCrun(scen2,thinning = thinning,burn.in = burn.in)
+MCMCdata3<-loadMCMCrun(scen3,thinning = thinning,burn.in = burn.in)
+
+
+# Create list with the data, convenient to use CODA for diagnostics
+mcmcList.1<-mcmc.list(do.call(list,lapply(unique(MCMCdata1$seed), function(repli){
+  rundata<-MCMCdata1[seed==repli]
+  mcmcRun<-mcmc(rundata[,.(gamma,negReward,scaleConst)],thin = thinning)#
+  return(mcmcRun)
+})))
+
+mcmcList.2<-mcmc.list(do.call(list,lapply(unique(MCMCdata2$seed), function(repli){
+  rundata<-MCMCdata2[seed==repli]
+  mcmcRun<-mcmc(rundata[,.(gamma,scaleConst)],thin = thinning)#
+  return(mcmcRun)
+})))
+
+
+mcmcList.2<-mcmc.list(do.call(list,lapply(unique(MCMCdata2$seed), function(repli){
+  rundata<-MCMCdata2[seed==repli]
+  mcmcRun<-mcmc(rundata[,.(gamma,scaleConst)],thin = thinning)#
+  return(mcmcRun)
+})))
+
+
+mcmcList.3<-mcmc.list(do.call(list,lapply(unique(MCMCdata3$seed), function(repli){
[…]

### 2021-12-21 data2interp.R

@@ -1,0 +1,57 @@
+######################### Abundance functions ##################################
+
+# Function to create the interpolation -----------------------------------------
+
+AbundData2interp<-function(dataAbun,
+                           npoints=100, # size of the interpolations
+                           Var2int      # variable to interpolate
+                           ){
+
+  # interpolate real data
+  interpData<-with(dataAbun,
+                      {interp(x=pR,y=pV,z=get(Var2int),duplicate = "mean",
+                              nx=npoints,ny=npoints)})
+  # Create structure to transpose interpolated data
+  interpDataTrans<-data.table(matrix(0,nrow = npoints*npoints,ncol = 4))
+  names(interpDataTrans)<-c("resProb","visProb",Var2int,"notProb")
+  # Transpose interpolated data
+  for (i in 1:npoints) {
+    for (j in 1:npoints) {
+      interpDataTrans[(i-1)*npoints+j,resProb:=interpData$x[i]]
+      interpDataTrans[(i-1)*npoints+j,visProb:=interpData$y[j]]
+      interpDataTrans[(i-1)*npoints+j,eval(Var2int):=interpData$z[i,j]]
+    }
+  }
+  # Complementary probability - "absence"
+  interpDataTrans[,4]<-1-interpDataTrans[,1]-interpDataTrans[,2]
+  # Select relavant data
+  interpDataTrans<-interpDataTrans[resProb+visProb<1]
+  return(interpDataTrans)
+}
+
+# Function to interpolate abundance vs leaving probability --------------------- 
+
+AbundLeavData2interp<-function(dataAbun,
+                           npoints=100, # size of the interpolations
+                           Var2int ){     # variable to interpolate
+
+  
+  # interpolate real data
+  interpData<-with(dataAbun,
+                   {interp(x=pA,y=Vlp,z=get(Var2int),duplicate = "mean",
+                           nx=npoints,ny=npoints)})
+  # Create structure to transpose interpolated data
+  interpDataTrans<-data.table(matrix(0,nrow = npoints*npoints,ncol = 3))
+  names(interpDataTrans)<-c("pAbs","VLeavProb",Var2int)
+  # Transpose interpolated data
+  for (i in 1:npoints) {
+    for (j in 1:npoints) {
+      interpDataTrans[(i-1)*npoints+j,pAbs:=interpData$x[i]]
[…]

### 2021-12-21 loadData.R

@@ -1,0 +1,229 @@
+# ------------------------ Load data ------------------------------------------#
+
+# Libraries
+
+require("data.table")
+require("jsonlite")
+require("rlist")
+
+# get files --------------------------------------------------------------------
+
+getFilelist<-
+  # reads de list of files and filters it according to a list of parameters
+  # and values of interest
+  function(folder, # folder where the files are
+           listparam=NULL, 
+           # list strings providing the parameters 
+           # of interest
+           values=NULL, 
+           # list of values matching the list in 
+           # listparam
+           fullNam=FALSE # Boolean. Append full path name
+           ){
+  posAgen<-c("PAA","FAA","DP","p1")
+  listRaw<-list.files(folder,recursive = TRUE,full.names = fullNam)
+  if(length(listRaw)<1)warning("No files in such location",immediate. = TRUE)
+  listRaw<-grep(".txt",listRaw,value = TRUE)
+  fullList<-vector("list",4)
+  names(fullList)<-posAgen
+  if(length(listparam)!=length(values)){
+    # parameter and value lists must be the same length
+    warning("Parameter list and values don't match",immediate. = TRUE)
+  }
+  else{
+      if(is.null(listparam)){
+        # if there is no list, use all the data
+        paramList<-listRaw
+  }
+    else{
+      # if there is list, filter the data
+      #regExpList<-paste0(listparam,values,"_",sep="")
+      for (param in unique(listparam)){
+        valsparam<-values[grep(param,listparam)]
+        listRaw<-do.call(list.append,lapply(paste(param,valsparam,"_",sep=""),
+                                           grep,x=listRaw,value=TRUE))
+      }
+      
+      paramList<-listRaw
+    }
+      for(agent in posAgen){
+        # Create a list with the lists separated by type of agents
+        listAgent<-grep(agent,paramList,value = TRUE)
+        fullList[[agent]]<-listAgent
+      }
+      return(fullList)
+    }
+}
+
+
[…]

### 2021-12-21 loadFieldData.R

@@ -1,0 +1,96 @@
+## Merge field and experimental data to use in the bayesian analysis
+
+library("data.table")
+library("here")
+library("readxl")
+library('dplyr')
+library('ggplot2')
+
+## Load field data based on the market experiment performance criteria
+fieldData<-fread(here("Data","market_model.csv"))
+
+
+str(fieldData)
+## Summarize ecological data by site
+
+fieldData[,unique(site_year)]
+names(fieldData)
+
+# Summarize field data by location
+fieldData.site<-fieldData[,lapply(.SD,max),by=site_year,
+                          .SDcols=c("abundance_large_100m2","abundance_small_100m2",
+                                   "abundance_cleaners_100m2","percentage_swim_off")]
+
+
+## Load the experimental data
+fieldData.cleaner<-data.table(read_xlsx(here("Data","market_raw_data.xlsx"),sheet = "round_data"))
+
+# Choose data from the last 20 experimental choices
+fieldData.cleaner[,use_sims:=ifelse(is.na(use_sims),0,1)]
+fieldData.cleaner[,use_sims:=as.logical(use_sims)]
+
+fieldData.filt<-fieldData.cleaner[use_sims==T,]
+fieldData.filt[,score_visitor:=as.numeric(score_visitor)]
+fieldData.filt[,stage:=as.factor(stage)]
+
+str(fieldData.filt)
+
+# Sum choices for each location and experimental subject
+fieldData.sum<-fieldData.filt[,sum(score_visitor),
+                              by=.(site_year,cleaner_ID)]
+
+str(fieldData.sum)
+
+# Rename columns for convenience
+names(fieldData.sum)[3]<-"score_visitor"
+names(fieldData.sum)[1]<-"site.year"
+
+fieldData.sum[,unique(site.year)]
+fieldData.site$site_year
+
+# Fix mistake in location code name
+fieldData.sum[site.year=="NHS2017",site.year:="NHS 2017"]
+
+# Get environmental variables from field data
+fieldData.sum[,abund.cleaners:=
+                fieldData.site[match(site.year,site_year),abundance_cleaners_100m2]]
+
+# Check the location names coincide
+fieldData.sum[order(abund.cleaners),max(abund.cleaners),by=site.year]$site.year==
+  
+  fieldData.site[order(abundance_cleaners_100m2),.(site_year,abundance_cleaners_100m2)]$site_year
+
[…]

### 2021-12-21 manFigures.R

@@ -1,0 +1,282 @@
+#### Figures showing the fit between model and data ############################
+#----------- Figure 2 
+##
+library(data.table)
+library(ggplot2)
+library("RColorBrewer")
+library("patchwork") 
+library(ggpubr)
+library(here)
+library(cowplot)
+source(here("loadData.R"))
+source(here("data2interp.R"))
+require('akima')
+source(here("aesth_par.R"))
+source(here("../R_files/posPlots.R"))
+
+# Folder where the three models are
+scenario<-"MCMCclean_gam_Nrew_sca"
+scenario2<-"MCMCclean_gam_sca"
+scenario3<-"MCMCclean_Nrew_sca"
+
+# Get file with the predictions using the mode of the posterior
+predfileMode.both<-grep(".txt",grep("round",list.files(here("Simulations",paste0(scenario,"_"))),value = T),
+                    value = T)
+predfileMode.gam<-grep(".txt",grep("round",list.files(here("Simulations",paste0(scenario2,"_"))),value = T),
+                   value = T)
+predfileMode.Nrew<-grep(".txt",grep("round",list.files(here("Simulations",paste0(scenario3,"_"))),value = T),
+                       value = T)
+
+# Get predictions from sampling the posterior 
+predfileSamples.both<-grep(".txt",grep("round",list.files(here("Simulations",
+                                  paste0(scenario,"_"),"samplesPost_"),
+                                  full.names = TRUE),value = T), value = T)
+predfileSamples.gam<-grep(".txt",grep("round",list.files(here("Simulations",
+                                paste0(scenario2,"_"),"samplesPost_"),
+                                full.names = TRUE),value = T),value = T)
+predfileSamples.Nrew<-grep(".txt",grep("round",list.files(here("Simulations",
+                                paste0(scenario3,"_"),"samplesPost_"),
+                               full.names = TRUE),value = T),value = T)
+
+# Load predictions with the mode of the posterior
+predictDataMode.both<-fread(here("Simulations",paste0(scenario,"_"),
+                      predfileMode.both))
[…]

### 2021-12-21 parTOjson.R

@@ -1,0 +1,304 @@
+# -------------- generate json files with parameters------------------------------------------ #
+
+library("jsonlite")
+library("here")
+source(here("loadData.R"))
+
+simsDir<-"Simulations"
+
+exedir<-'/./ActCrit.exe'
+
+fileName<-"parameters.json"
+
+scenario<-"MCMCclean_gam_nRew_sca_group_"
+
+
+# MCMC fit - Generate json parameter files for -------------------------------------
+
+scenario<-"MCMCclean_gam_sca_group"
+
+# For running MCMC with model generated data
+
+# filesList<-list.files(here("Simulations",scenario),full.names = TRUE)
+# 
+# fake.data.pred<-fread(grep("round",filesList,value = TRUE))
+# 
+# fake.data.pred<-fake.data.pred[,.(site_year,CleanerID,
+#                                   score_visitor=sapply(visitorChoices_pred,
+#                                                        rbinom,n = 1,size = 20),
+#                                   rel.abund.cleaners,rel.abund.visitors,
+#                                   rel.abund.residents,prob.Vis.Leav)]
+# 
+# fake.data.pred<-fake.data.pred[fakeData,on=.(site_year=site.year,CleanerID=cleaner_ID)]
+# 
+# fake.data.pred<-fake.data.pred[,.(site_year,CleanerID,score_visitor,abund.cleaners,
+#                                   abund.visitors,abund.residents,prob.Vis.Leav),]
+# 
+# fwrite(fake.data.pred,file = here("Simulations",scenario,"data_MCMC_fake.txt"),
+#        row.names = FALSE,sep = "\t")
+# 
+# scenario<-"MCMCfakedata2"
+# for MCMC
+param_mcmc<-list(totRounds=10000,ResReward=1,VisReward=1,
+                 ResProbLeav=0,scenario=0, 
+                 #nature, experiment, marketExperiment, ExtendedMarket
+                 inbr=0,outbr=0,forRat=0.0,
+                 seed=1, propfullPrint = 0.7,sdPert=c(0.05,0.05,0.3,2,200),
+                 chain_length=100000,
+                 init=c(0.05,0.05,0,0,30),# alphaA,AlphaC, Gamma, NegRew, scalConst
[…]

### 2021-12-21 random.cpp

@@ -1,0 +1,374 @@
+/*=============================================================================================================
+                                                random.cpp
+===============================================================================================================
+
+ Routines for the generation of pseudo-random numbers
+ 
+ Written originally by:
+ G. Sander van Doorn
+ Centre for Ecological and Evolutionary Studies - Theoretical Biology Group
+ University of Groningen
+ the Netherlands
+
+ Program version
+		xx/xx/xxxx	:
+
+=============================================================================================================*/
+
+//#include "stdafx.h"
+#include <chrono>
+#include <sstream>
+#include <iomanip>
+#include "random.h"
+
+namespace rnd {
+	std::mt19937 rng;
+	const double BINOMIALCOST = 7.0;	//time cost of drawing a binomial() deviate relative to drawing a uniform() deviate
+
+	void set_seed(const unsigned& seed) {
+		std::ostringstream oss;
+		oss << "random seed set to " << seed;
+		echo(oss.str());
+		rng.seed(seed);
+	}
+
+	void set_seed() {
+		unsigned seed = static_cast<unsigned>(std::chrono::high_resolution_clock::now().time_since_epoch().count());
+		set_seed(seed);
+	}
+
+	int integer(const int& n) {
+		typedef std::uniform_int_distribution<int> distribution;
+		static int k = n;
+		static distribution distr(0, k - 1);
+		if (k != n) {
+			k = n;
+			distr = distribution(0, k - 1);
+		}
+		return distr(rng);
+	}
+
+	bool bernoulli(const double& p) {
+		typedef std::bernoulli_distribution distribution;
+		static double z = p;
+		static distribution distr(z);
+		if (p > 0.0 && p < 1.0) {
+			if (z != p) {
+				z = p;
+				distr = distribution(z);
+			}
+		}
+		else if (p == 0.0) return false;
+		else if (p == 1.0) return true;
+		else error("argument out of range", CURRENT_FUNCTION);
+		return distr(rng);
+	}
+
+	int binomial(const int& n, const double& p)
+	{
+		typedef std::binomial_distribution<int> distribution;
+		static int k = n;
+		static double z = p;
[…]

### 2021-12-21 random.h

@@ -1,0 +1,62 @@
+/*=============================================================================================================
+                                                   random.h
+===============================================================================================================
+ 
+ Routines for the generation of pseudo-random numbers
+ 
+ Written originally by:
+    G. Sander van Doorn
+    Centre for Ecological and Evolutionary Studies - Theoretical Biology Group
+    University of Groningen
+    the Netherlands
+ 
+ Program version
+        xx/xx/xxxx	:
+ 
+ =============================================================================================================*/
+
+#ifndef random_h
+#define random_h
+#include <random>
+#include <vector>
+#include "utils.h"
+
+namespace rnd
+{
+    class discrete_distribution {
+    public:
+        discrete_distribution(const int&);
+        double& operator[](const int &i) { is_accumulated = false; return pdf[i]; }
+        double operator()(const int &i) const { return pdf[i]; }
+        int sample();//int sample(std::mt19937 rng);
+        std::vector<int> sample(int);
+        int size() const { return n;}
+    private:
+        void accumulate();
+        const int n;
+        bool is_accumulated;
+        std::vector<double> pdf, cdf;
+    };
+
+	//extern std::mt19937 rng_d;    
+    void set_seed();
+	void set_seed(const unsigned int&);
+    int integer(const int&);
+	bool bernoulli(const double& = 0.5);
+	int binomial(const int&, const double& = 0.5);
+	double pdf_binomial(const int& k, const int& n, const double& p= 0.5);
+	int poisson(const double& = 1.0);
+	double uniform(const double  min=0, const double  max=1);
+    double normal(const double& = 0.0, const double& = 1.0);
+    double exponential(const double& = 1.0);
+ 
+	extern std::mt19937 rng;
+	double gamma(const double& shape, const double& scale);
+	double beta(const double&, const double&);
+	double pdf_gamma(const double&, const double&, const double&);
+	//double pdf_beta(const double& x, const double& shapeL, const double& shapeR);
+	double r8_beta(double x, double y);
+	double beta_pdf(double x, double a, double b);
+}
+
+#endif //#ifndef random_h

### 2021-12-21 utils.cpp

@@ -1,0 +1,128 @@
+/*=============================================================================================================
+                                                 utils.cpp
+===============================================================================================================
+ 
+ Miscellaneous utility routines
+ 
+ Written originally by:
+        G. Sander van Doorn
+        Centre for Ecological and Evolutionary Studies - Theoretical Biology Group
+        University of Groningen
+        the Netherlands
+ 
+ Program version
+        xx/xx/xxxx	:
+ 
+=============================================================================================================*/
+
+//#include "stdafx.h"
+#include <fstream>
+#include <sstream>
+#include <chrono>
+#include <ctime>
+#include "utils.h"
+#pragma warning(disable : 4996)
+
+
+/*=============================================================================================================
+                                    frequently used mathematical constants
+=============================================================================================================*/
+
+const double	PI2		= 6.28318530717958;
+const double	PI		= 3.14159265358979;
+const double    SQRT2   = 1.41421356237309;
+
+/*=============================================================================================================
+                                                (error) logging
+=============================================================================================================*/
+ 
+bool echo_stdclog = true;
+
+void echo(const std::string &message, const bool &write_to_clog)
+{
+	//writes messages to the log file
+	static std::ofstream fp_out;
+	static bool init = true;
+	if(init)
+	{
+		fp_out.open("messages.txt");
+		verify(fp_out.is_open());
+		init = false;
+	}
+    std::time_t the_time = std::chrono::system_clock::to_time_t(std::chrono::system_clock::now());
+    std::string log_entry(std::ctime(&the_time));
+	log_entry.insert(log_entry.length() - 1," : " + message);
+	fp_out << log_entry;
+	fp_out.flush();
+    if(write_to_clog) std::clog << log_entry;
+}
+
+void error(const std::string &function, const std::string &message)
+{
+    std::ostringstream oss;
+	oss << "error! in function " << function << (message.empty() ? "().\n" :  "() -> " + message + ".\n");
+	echo(oss.str(), true);
+	wait_for_return();
+	exit(1);
+}
+
+void warning(const std::string &function, const std::string &message)
+{
+    std::ostringstream oss;
+	oss << "warning! in function " << function << (message.empty() ? "().\n" :  "() -> " + message + ".\n");
+	echo(oss.str());
+}
+
[…]

### 2021-12-21 utils.h

@@ -1,0 +1,71 @@
+/*=============================================================================================================
+                                                 utils.h
+===============================================================================================================
+ 
+ Miscellaneous utility routines
+ 
+ Written originally by:
+        G. Sander van Doorn
+        Centre for Ecological and Evolutionary Studies - Theoretical Biology Group
+        University of Groningen
+        the Netherlands
+ 
+ Program version
+        xx/xx/xxxx	:
+ 
+=============================================================================================================*/
+
+
+#ifndef utils_h
+#define utils_h
+
+#include <iostream>
+#include <sstream>
+#include <string>
+#include <cstdlib>
+#include <string>
+
+extern const double	PI2;
+extern const double	PI;
+extern const double SQRT2;
+extern bool echo_stdclog;
+
+void echo(const std::string&, const bool& = echo_stdclog);
+void error(const std::string&, const std::string& = "");
+void warning(const std::string&, const std::string& = "");
+
+void dot();
+void mark_time(const bool& = false);
+void wait_for_return();
+std::string itos(int j);
+std::string douts(double j);
+
+
+void clip_range(double&, const double&, const double&);
+void clip_low(double&, const double&);
+void clip_high(double&, const double&);
+template <class T> inline double sqr(const T &x) { return x * x; };
+
+#if defined(__GNUC__) || (defined(__MWERKS__) && (__MWERKS__ >= 0x3000)) || (defined(__ICC) && (__ICC >= 600)) || (defined(__DMC__) && (__DMC__ >= 0x810))
+# define CURRENT_FUNCTION __PRETTY_FUNCTION__
+#elif defined(__FUNCSIG__)
+# define CURRENT_FUNCTION __FUNCSIG__
+#elif (defined(__INTEL_COMPILER) && (__INTEL_COMPILER >= 600)) || (defined(__IBMCPP__) && (__IBMCPP__ >= 500)) || (defined(_MSC_VER) && (_MSC_VER >= 1020))
+# define CURRENT_FUNCTION __FUNCTION__
+#elif defined(__BORLANDC__) && (__BORLANDC__ >= 0x550)
+# define CURRENT_FUNCTION __FUNC__
+#elif defined(__STDC_VERSION__) && (__STDC_VERSION__ >= 199901)
+# define CURRENT_FUNCTION __func__
+#else
+# define CURRENT_FUNCTION "(unknown)"
+#endif
+
+#define verify(condition) \
[…]

### 2022-01-06 manuscript_1.0/manuscript_1.0.Rmd
Fix issues with the size of figures in the formatted version

@@
 On the left (panels a, c and c) posterior distributions for a model with   all three parameters; while on the right (b and d) a model without negative reward.
-Panel f shows a measure of fit for both models, namely the distribution of pseudo-$R^2$ obtained from sampling the posterior distribution of parameter values.",out.width='95%',fig.height=9}
-require(data.table)
+Panel f shows a measure of fit for both models, namely the distribution of pseudo-$R^2$ obtained from sampling the posterior distribution of parameter values.",out.width='100%',fig.height=7}
+library(data.table)
 library(coda)
@@
 labels.Scen<-c("both","gam","Nrew")
-labelsPlot.Scen<-c("Full model","Future reward","Negative reward")
+labelsPlot.Scen<-c("Full \n model","Future \n reward","Negative \n reward")
 
@@
   stat_halfeye(alpha=0.5,point_size=3)+
-  theme_classic()+xlim(-0.5,0.3)+
+  theme_classic()+xlim(-0.6,0.2)+
   scale_fill_manual(values=c("#1b9e77","#d95f02","#7570b3"),
@@
   geom_vline(xintercept = 0,color="black",size=1)+
-  theme(legend.position = c(.3, .80),legend.key.size = unit(0.4,'cm'),
+  theme(legend.position = c(.3, .75),legend.key.size = unit(0.25,'cm'),
         axis.text.y = element_blank())
@@
             labs(title=labelsPlot.Scen[1],subtitle = expression(gamma),x="",y="")+
-            theme_classic()+scale_fill_manual(values=c("gray85","skyblue","gray85")),
+            theme_classic()+scale_fill_manual(values=c("gray85","skyblue","gray85"))+
+            theme(plot.margin = unit(rep(0.5,4), "lines")),
           # \eta
@@
             scale_fill_manual(values=c("gray85","skyblue","gray85"))+
-            labs(subtitle = expression(eta),x="",y="")+xlim(-5,5),
+            labs(subtitle = expression(eta),x="",y="")+xlim(-5,5)+
+            theme(plot.margin = unit(rep(0.5,4), "lines")),
           # Scale Constant
@@
             theme_classic()+scale_fill_manual(values=c("skyblue","gray85"))+
-          labs(subtitle = "Scalling const.",x="",y="")+xlim(-2,1500)+theme_classic(),
+          labs(subtitle = "Scalling const.",x="",y="")+xlim(-2,1500)+theme_classic()+
+          theme(plot.margin = unit(rep(0.5,4), "lines")),
           # Future reward only model - \gamma
@@
             labs(title=labelsPlot.Scen[2],subtitle = expression(gamma),x="",y="")+
-            theme_classic(),
+            theme_classic()+theme(plot.margin = unit(rep(0.5,4), "lines")),
           # Scalling constant
@@
             labs(subtitle = "Scalling const.",x="",y="")+
-            theme_classic(),
+            theme_classic()+theme(plot.margin = unit(rep(0.5,4), "lines")),
           # Pseudo R^2
@@
 Pseudo $R^2$ shown in the lower right corner corresponds to the fit of a model parameterized with the mode of the posterior distributions.
-Upper panels show prediction from a model including future and negative reward, lower panels froma  model with only future reward.",out.width='95%',fig.height=8}
+Upper panels show prediction from a model including future and negative reward, lower panels froma  model with only future reward.",out.width='100%',fig.height=6}
 
@@
 Right-hand side panel: scatter plot of the observed and predicted probabilities of choosing a visitor for 12 locations.
-Line correspond to a perfect match between observed and predicted probabilities.",fig.pos = 'H', out.extra = "",out.width='95%',fig.height=8}
+Line correspond to a perfect match between observed and predicted probabilities.",fig.pos = 'H', out.extra = "",out.width='95%',fig.height=4}
 

### 2022-01-06 manuscript_1.0/manuscript_1.0.tex
Fix issues with the size of figures in the formatted version

@@
 
-{\centering \includegraphics[width=0.95\linewidth]{manuscript_1.0_files/figure-latex/post-1}
+{\centering \includegraphics[width=1\linewidth]{manuscript_1.0_files/figure-latex/post-1}
 
@@
 
-{\centering \includegraphics[width=0.95\linewidth]{manuscript_1.0_files/figure-latex/pred-1}
+{\centering \includegraphics[width=1\linewidth]{manuscript_1.0_files/figure-latex/pred-1}
 

### 2022-01-06 manFigures.R

@@ -196,6 +196,8 @@ rsqr.gam.McFadden<-1-predictDataMode.gam[,sum(log.like)]/
 rsqr.Nrew.McFadden<-1-predictDataMode.Nrew[,sum(log.like)]/
   sum(dbinom(x=predictDataMode.Nrew[,visitorChoices],size = 20,prob = 0.5,log = TRUE))
 
+axislabSize<-10
+axisSize<-12
 # Panel full model contour
 cont.obs.pred.both<- ggplot(data = FIAinterpData.both,aes(x=rel.abund.cleaners,y=prob.Vis.Leav,
                                                 fill=market_binomial_data))+
@@ -205,8 +207,8 @@ cont.obs.pred.both<- ggplot(data = FIAinterpData.both,aes(x=rel.abund.cleaners,y
              shape=21,color="black")+sc+xlab("")+
   ylab("Probability of visitor leaving")+
   labs(fill="Probability \n of choosing \n a visitor")+
-  theme(axis.text = element_text(size=12),
-axis.title.x = element_text(size=12),axis.title.y = element_text(size=12))
+  theme(axis.text = element_text(size=axisSize),
+axis.title.x = element_text(size=axislabSize),axis.title.y = element_text(size=axislabSize))
 
 # Panel full model scatter
 scatter.obs.pred.both<-ggplot(data = fieldatabyLoc.both,aes(y=market_binomial_data,x=probvisitor.pred))+
@@ -217,11 +219,11 @@ scatter.obs.pred.both<-ggplot(data = fieldatabyLoc.both,aes(y=market_binomial_da
   ggtitle("")+
   theme_classic()+
   theme(plot.title = element_text(hjust = 0.5),
-      axis.title.x = element_text(size=12),axis.title.y = element_text(size=12),
+      axis.title.x = element_text(size=axisSize),axis.title.y = element_text(size=axislabSize),
       axis.text = element_text(size=14))+
-  geom_text(x = 0.8, y = 0.85, label = expression(y==x), parse = TRUE,size=4)+
+  geom_text(x = 0.8, y = 0.85, label = expression(y==x), parse = TRUE,size=3)+
   geom_text(x = 0.8, y = 0.5, label = deparse(bquote(R^2==.(round(rsqr.both.McFadden,4)))), 
-            parse = TRUE,size=4)
+            parse = TRUE,size=3)
 
 # Panel future reward contour
[…]

### 2022-01-14 manuscript_1.0/manuscript_1.0.tex
New Rmd file to produce the manuscript in word format. Abstract and intro have been edited as well as figures. In the process of editing methods and discussion.

@@
 \begin{abstract}
-The same behaviour can be achieved by different mechanistic underpinnings.
-But the environmental conditions under which the behaviour is triggered might differ between these potential mechanisms.
-Thus, by analyzing the varitation of expression of a certain behavior across environmental gradients, it is possible to infer which mechanism is behind the behaviour of interest.
-To do this it is necessary to have clearcut predictions for the different candidate mechanisms.
-In here, we use experimental data on the behaviour of the cleaner fish \emph{Labroides} \emph{dimidiatus}, as well as enviromental variables from the location of fish, together with a computational model of the learning mechanisms.
-Using bayesian statistics, we fit key parameters of the computational model that determine the specific learning mechanism.
-We find that a model where cleaners estimate the long-term consequences of their actions, and use the estimate in their desicion making, explains better under which conditions the fish develop a preference for an ephemeral food source in the context of a biological market.
-We argue that the combination of computational models with data is powerful tool to infer the mechanistic underpinning behind behaviours of interest.
+While it is generally straightforward to quantify individual performance in cognitive experiments, identifying the underlying cognitive processes remains a major challenge.
+Often, different mechanistic underpinnings may yield similar performances, and Lloyd Morgan's cannon warrants acceptance of the simpler explanation.
+Alternatively, when the different mechanisms interact with environmental conditions, variation in performance across environments might allow to statistically infer the mechanism responsible.
+However, to do this it is necessary to have quantitative predictions for the different candidate mechanisms.
+Here, we use a set of computational models to get quantitative predictions from alternative learning mechanisms, and using Bayesian statistics fit the model parameters to performance data.
+We used experimental data on performance in an ephemeral reward task by wild-caught cleaner fish Labroides dimidiatus, as well as cleaner and client fish densities from the locations of capture.
+The task can in principle be solved by estimating future consequences of an action, or by perceiving the removal of the ephemeral reward as psychological punishment (negative reinforcement).
+We found that a model where cleaners only estimate the future consequences of their actions explains best which cleaner relative abundances cause the fish to develop a preference for an ephemeral food source.
+This model also yields performances that can be considered the result of locally optimal decision-rules, in contrast to the negative reinforcement model.
+We argue that the combination of computational models with data is a powerful tool to infer the mechanistic underpinning behind cognitive performance.
 \end{abstract}
@@
 Cooperation among individuals of the same or different species is
-ubiquitous in nature. Among individuals of different species it
-underlays the biological mechanism for fundamental ecological
-interactions such as pollination, nitrogen fixation or parasite removal
-\citep{begon_Ecology_2006}. When partners in these mutualistic interactions
-are able to choose their interaction partner, their investment and the
-return they obtain can be understood as a biological market
-\citep{hammerstein_Biological_2016, leimar_Cooperation_2010, noe_Biological_1994a, noe_Biological_1995a}. Thus, we expect supply
-and demand of the good and services being exchanged to determine the
-action of individuals, at least in an evolutionary time-scale. However,
-supply and demand conditions of a biological market, which typically
+ubiquitous in nature. Whenever such interactions involve some degree
+of partner choice, biological market theory predicts that the exchange
+rate of goods and/or services traded adjusts to the law of supply and demand
+\citep{noe_Biological_1995a}. While biological market models have largely focused
+on evolutionary time scales \citep{noe_Biological_1994a, johnstone_Mutualism_2008a}
+\(\color{red}{\text{Hoekstra xxxx}}\), supply and demand conditions, which typically
 depend on the abundance of the species involved, certainly vary in time
-and space. How do partners adjust their strategy in the face of this
-variation? In animals an obvious general candidate mechanism for the
-strategic adjustment is the cognitive machinery. However, it is not
-clear which specific cognitive mechanisms allow individual to adjust
-their behaviour to the varying market conditions.
+and space within ecological time scales. Therefore, natural selection should
+favour the ability to flexibly adjust decisions and behavioural output to
+current market conditions. Indeed, such adjustments have been repeatedly
+documented \citep{axen_Signalling_1996}. In animals, an obvious general candidate
+mechanism for the strategic adjustment is the cognitive machinery. However,
+it is not clear which cognitive mechanisms allow individuals to adjust their
+behaviour to the varying market conditions. As adjustments to changes in
+market conditions have been documented in a great variety of species with
+highly variable brain anatomies, the question arises to what extent mechanisms
+beyond basic associative learning may be involved.
 
@@
 correlated with parasite load \citep{grutter_Relationship_1995a}. However,
-early laboratory
-experiments showed that leaving causes service priority independent of
-client value \citep{bshary_Asymmetric_2002}. The experiments consisted of a
-simultaneous two-choice task, where cleaners had to decide which of two
+early laboratory experiments showed that leaving causes service
+priority independent of client value \citep{bshary_Asymmetric_2002}.
+The experiments consisted of asimultaneous two-choice task,
+where cleaners had to decide which of two
 Plexiglas plates, which offered equal amounts of food, to approach first
@@
 \citep{salwiczek_Adult_2012, zentall_Early_2017}; only African grey
-parrots solve this task as well \citep{pepperberg_Can_2014}.
+parrots solve this task as well \citep{pepperberg_Can_2014}. As the correct
+solution must be learned, and primates are known to readily distinguish
+between one and two reward units if presented in more conventional ways
+\(\color{red}{\text{ref}}\), what makes the task difficult for most non-cleaners?
 
-Recent research has refined our view on partner choice and priority of
-access in the \emph{L. dimidiatus} cleaning mutualism, and as a consequence
-performance in the biological market task. First, details of the task
-presentation may matter; i.e.~what relevant information is encoded in
-the design of the two plates (colour versus size;
-\citep{wismer_Cuebased_2019}), or whether the information is in the colour of
+Recent research on the cognitive tool kit needed to solve an ephemeral
+reward task has used a broad approach as proposed by Shettleworth
+\citep{shettleworth_Cognition_2009},
+who defined cognition as includes all ways in which animals take in information
+through the senses, process, retain and decide to act on it. Indeed, perception
+of relevant cues is of major importance for individual performance;
+i.e.~what relevant information is encoded in the design of the two
+plates (colour versus size; \citep{wismer_Cuebased_2019}), or whether
+the information is in the colour of
 the food \citep{pretot_Comparative_2021, pretot_Comparing_2016}, and
 whether the food is visible or hidden/released only when the subjects
-made choices on a touch screen \citep{pretot_Factors_2016}. Second, it
-appears that cleaner and client densities in nature affect how cleaners
-perform in the original market task: when densities are low, cleaners
-are more likely to fail to complete the task \citep{triki_Biological_2019, triki_Decrease_2018, wismer_Variation_2014}. The apparent explanation
-for this failure is that visitor clients are less likely to exert their
-choice options (and hence wait for inspection if made to wait) when
-cleaner fish densities are low \citep{triki_Brain_2020}. This change in
-behaviour may be due to the fact that when cleaner densities are low,
-the cost of switching in terms of distance to swim and time invested
-increases. If visitors are not choosy, cleaners should not give them
-priority anymore. Interestingly, while cleaners from high-density areas
-have larger forebrains harbouring more cells than cleaners from
-low-density areas \citep{triki_Brain_2020}, on a local scale those
-individuals that perform in the market task in a way that corresponds to
-the locally optimal strategy (solving/failing the task when living in
-high/low density) have relatively larger forebrains \citep{triki_Brain_2020}.
-Taken together, empirical results clearly show major intra- and
-inter-specific variation in performance in the market task, warranting
-investigation of the underlying cognitive machinery, from perception to
-decision-making \citep{shettleworth_Cognition_2009}.
-
-One approach to identify candidate mechanisms underlying performance in
-a cognitive task is to develop proximate learning models and to evaluate
-their predictions in light of the behavioural data (e.g.
-\citep{dubois_Model_2021}). By varying the cognitive tool kit, one can assess
-which minimal kit is necessary to solve the task at hand. This approach
-has been used to analyse the market task \citep{prat_Role_2021, quinones_Reinforcement_2019}. Learning models showed that basic
-reinforcement learning does not suffice to solve the task, this is
-particularly so when models assume the more complex natural situation in
-which cleaners not only face resident-visitor pairs but also
+made choices on a touch screen \citep{pretot_Factors_2016}. However, identifying
+cues as salient is not the only challenge of the ephemeral reward task,
+as revealed by proximate learning models. Such models allow varying the
+cognitive tool kit and to evaluate which minimal kit is necessary to solve
+the task at hand (e.g. \citep{dubois_Model_2021}). Applied to the ephemeral
+reward task, learning models showed that basic reinforcement learning does
+not suffice to solve the task \citep{prat_Modelling_2022, quinones_Reinforcement_2019}.
+This is particularly so when models assume the more complex natural
+situation in which cleaners not only face resident-visitor pairs but also
 visitor-visitor and resident-resident pairs, as well only a resident or
 only a visitor. To be able to give visitors priority over residents,
-cleaners first need to be able to assess a client's value separately for
-the three possible forms of encounter (alone, paired with a fish with
-the same strategic option, paired with a fish with the alternative
-strategic option) \citep{quinones_Reinforcement_2019}. In addition, cleaners
-need to account for the future consequences of current decisions. In the
-model, this could be achieved in two non-mutually exclusive ways
-\citep{quinones_Reinforcement_2019}: through low temporal discounting of
-future effects and/or through perceiving a visitor client leaving as
-psychological punishment (i.e.~as a negative reinforcer). Given that a
-negative reinforcer is part of the ubiquitous learning mechanism termed
-operant conditioning \citep{thorndike_Animal_1898, skinner_Behavior_1938},
-this explanation can be
-considered the simpler one. Furthermore, accounting for the future
-effects of an action is considered an advanced cognitive ability
-\citep{suddendorf_Evolution_2007}. Here, we fitted our model to the empirical
-data on fish densities and cleaner fish performance in the market task
-with the aim to determine the likely mechanism used by cleaners to
-incorporate future consequences of current decisions.
+cleaners need to be able to assess a client's value separately for the
+three possible forms of encounter (alone, paired with a fish with the
+same strategic option, paired with a fish with the alternative strategic option)
+\citep{quinones_Reinforcement_2019}. The ability to keep such separate scores
+for the same stimulus has been termed configurational learning,
+or chunking, or segmentation (see references in \citep{prat_Modelling_2022}).
+
+To solve the ephemeral reward task, cleaners also need to account for
+the future consequences of current decisions. In the model by
+Quiñones et al. \citep{quinones_Reinforcement_2019}, this could be achieved in
+two non-mutually exclusive ways: through low temporal discounting of
+future effects, also termed `chaining' \citep{enquist_Power_2016}; and/or
+through perceiving a visitor client leaving as psychological punishment
+(i.e.~as a negative reinforcer). Given that a negative reinforcer is part
+of the ubiquitous learning mechanism termed operant conditioning
+\citep{thorndike_Animal_1898, skinner_Behavior_1938}, this explanation
+could be considered the simpler one. Furthermore, accounting for the
+future effects of an action is considered an advanced cognitive
+ability \citep{suddendorf_Evolution_2007}. Thus, standard logic of
+Lloyd Morgan's cannon demands that operant conditioning as the simpler
+explanation is to be accepted by default. Here, we explore the
+possibility that fitting a model in which the action of these two
+mechanisms, operant conditioning and chaining, depends
+on model parameters may reveal which process cleaners actually use.
+This is because one process may be better at predicting the observed
+variation in cleaner fish performance as a function of ecological conditions.
+
+Various repetitions of the ephemeral reward task in different years and
+with cleaners caught from various locations around Lizard Island,
+Great Barrier Reef, revealed that cleaner and client densities in
+nature affect how cleaners perform in the original market task:
+when relative densities are low, cleaners are more likely to fail to
+complete the task \citep{triki_Biological_2019, triki_Decrease_2018, wismer_Variation_2014}. The explanation for this pattern
+is twofold. First, low cleaner abundances implies low supply and high demand
+of cleaning services. Under this conditions, there will be less occasions under
+which failing to give priority to a visitor translates to an empty
+cleaning station. Secondly and also related to the state of the cleaning market,
+visitor clients are less likely to exert their choice options
+(and hence wait for inspection if made to wait) when
+cleaner fish densities are low \citep{triki_Brain_2020}. If visitors are not choosy,
+cleaners should not give them priority anymore. Thus, the underling
+cognitive machinery and ecological variables apparently interact to produce
+such variable performance. By fitting our model to the empirical data on
+fish densities and cleaner fish performance in the ephemeral reward task
+we aimed to address two questions. First, we aimed to determine the likely
+mechanism used by cleaners to incorporate future consequences of current
+decisions by testing whether operant conditioning, chaining, or a combination
+of both best explains performance. Second and related to the first
+question, we aimed to determine whether the two mechanisms differed
+with respect to the ecological conditions that are likely to cause high
+versus low performance in the ephemeral reward task. If that were the case,
+we would assess which mechanism would yield more appropriate performance
+patterns. Relying on the logic of biological market theory, we predicted
+that appropriate performance is to show low preference for visitors under high
+local client-to-cleaner ratio as visitor leaving rates should be low
+and any leaving visitor will be readily replaced by another client. In contrast,
+cleaners should show high performance if the local client-to-cleaner
+ratio favours clients.
 

### 2022-01-14 manuscript_1.0/manuscript_word.Rmd
New Rmd file to produce the manuscript in word format. Abstract and intro have been edited as well as figures. In the process of editing methods and discussion.

--- 2022-01-06 manuscript_1.0/manuscript_1.0.Rmd
@@
   reveal cognitive mechanisms behind cleaner fish behaviour
-#Cognitive and ecological aspects determine cleaner performance
 author:
-  - name: Andrés E. Quiñones 
-    affiliation: "1"
-  - name: Zegni Triki
-    affiliation: "2"
-  - name: Redouan Bshary
-    affiliation: "1"
-address:
-  - code: "1"
-    address: Institute of Biology, University of Neuchâtel, Neuchâtel, Switzerland
-  - code: "2"
-    address: Department of Zoology, Stockholm University, Stockholm, Sweden
-
-corresp_author_name:  "AE. Quiñones"
-corresp_author_email: "andreseqp@gmail.com"
-
-subject:
-  - "Behavioural ecology"
-  - "Cognitive ecology"
-  - "Animal behaviour"
-
-keywords:
-  - learning   
-  - cleaners
-  - behaviour
-  - bayesian statisitics
-  - mutualism
-
-abstract: |
-  The same behaviour can be achieved by different mechanistic underpinnings.
-But the environmental conditions under which the behaviour is triggered might differ between these potential mechanisms.
-Thus, by analyzing the varitation of expression of a certain behavior across environmental gradients, it is possible to infer which mechanism is behind the behaviour of interest.
-To do this it is necessary to have clearcut predictions for the different candidate mechanisms.
-In here, we use experimental data on the behaviour of the cleaner fish *Labroides* *dimidiatus*, as well as enviromental variables from the location of fish, together with a computational model of the learning mechanisms.
-Using bayesian statistics, we fit key parameters of the computational model that determine the specific learning mechanism.
-We find that a model where cleaners estimate the long-term consequences of their actions, and use the estimate in their desicion making, explains better under which conditions the fish develop a preference for an ephemeral food source in the context of a biological market.
-We argue that the combination of computational models with data is powerful tool to infer the mechanistic underpinning behind behaviours of interest.
-
-## Remove this if not required
-ethics: |
-  The Animal Ethics Committee of the Queensland government (DAFF)
-  approved the project (CA 2016/05/970 and CA 2017/05/1063).
-
-data_accessibility: |
-  Please provide details on the data availability.
-
-author_contributions: |
-  AQ and RB designed the study. ZT collected the data. AQ developed the model and 
-  fitted the model parameters to the data. AQ, RB and ZT wrote the manuscript.
-
-## Remove this if not required
-conflict_of_interest: |
-  The authors declate no conflict of interests.
-
-## Remove this if not required
-funding: |
-  This work was supported by the Swiss National Science Foundation (grants
-  number: 31003A_153067/1 and 310030B_173334/1 to R.B.).
-
-## Remove this if not required
-acknowledgements: |
-  ZT and RB kindly thank the staff of Lizard Island Research Station, Dominique
-  Roche, Sharon Wismer, Olivia Rey,Sandra Ann Binning, Elena Levorato and William McNeely for their
-  field support. AQ thanks Florian Hartig for statistical advice.
-
+- Andrés E. Quiñones^[Institute of Biology, University of Neuchâtel, Neuchâtel, Switzerland
+  - andresqp@gmail.com]
+date: "`r format(Sys.time(), '%B %d, %Y')`"
+output:
+  word_document: default
+  pdf_document: default
+fig_caption: yes
+fontsize: 12pt
+header-includes:
+- \usepackage{float}
+- \usepackage{setspace}\doublespacing
+- \linespread{2}
+- \usepackage{lineno}
+- \linenumbers
+- \newcommand{\beginsupplement}{ \setcounter{table}{0} \renewcommand{\thetable}{S\arabic{table}}
+  \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}}
+keep_tex: yes
+linespread: 2
 bibliography: Cleanerlearning.bib
-
-## change to true to add optional line numbering
-lineno: true
-
-header-includes: |
-  ```{=latex}
-  \usepackage{float}
-  \usepackage{booktabs}
-  \newcommand{\beginsupplement}{ \setcounter{table}{0}     \renewcommand{\thetable}{S\arabic{table}}\setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}}
-  ```
-site: bookdown::bookdown_site
-output: 
-  bookdown::pdf_book:
-    base_format: rticles::rsos_article
+style: M:\Zotero\styles\behavioral-ecology-and-sociobiology.csl
+spacing: double
+abstract: "While it is generally straightforward to quantify individual performance
+  in cognitive experiments, identifying the underlying cognitive processes remains
+  a major challenge. Often, different mechanistic underpinnings may yield similar
+  performances, and Lloyd Morgan’s cannon warrants acceptance of the simpler explanation.
+  Alternatively, when the different mechanisms interact with environmental conditions,
+  variation in performance across environments might allow to statistically infer
+  the mechanism responsible. However, to do this it is necessary to have quantitative
+  predictions for the different candidate mechanisms. Here, we use a set of computational
+  models to get quantitative predictions from alternative learning mechanisms, and
+  using Bayesian statistics fit the model parameters to performance data. We used
+  experimental data on performance in an ephemeral reward task by wild-caught cleaner
+  fish Labroides dimidiatus, as well as cleaner and client fish densities from the
+  locations of capture. The task can in principle be solved by estimating future consequences
+  of an action, or by perceiving the removal of the ephemeral reward as psychological
+  punishment (negative reinforcement). We found that a model where cleaners only estimate
+  the future consequences of their actions explains best which cleaner relative abundances
+  cause the fish to develop a preference for an ephemeral food source. This model
+  also yields performances that can be considered the result of locally optimal decision-rules,
+  in contrast to the negative reinforcement model.  We argue that the combination
+  of computational models with data is a powerful tool to infer the mechanistic underpinning
+  behind cognitive performance. \n"
+keywords: learning, behaviour, cleaners, bayesian statisitics
 ---
@@
 Cooperation among individuals of the same or different species is
-ubiquitous in nature. Among individuals of different species it
-underlays the biological mechanism for fundamental ecological
-interactions such as pollination, nitrogen fixation or parasite removal
-[@begon_Ecology_2006]. When partners in these mutualistic interactions
-are able to choose their interaction partner, their investment and the
-return they obtain can be understood as a biological market
-[@hammerstein_Biological_2016; @leimar_Cooperation_2010;
-@noe_Biological_1994a;@noe_Biological_1995a]. Thus, we expect supply
-and demand of the good and services being exchanged to determine the
-action of individuals, at least in an evolutionary time-scale. However,
-supply and demand conditions of a biological market, which typically
+ubiquitous in nature. Whenever such interactions involve some degree 
+of partner choice, biological market theory predicts that the exchange 
+rate of goods and/or services traded adjusts to the law of supply and demand 
+[@noe_Biological_1995a]. While biological market models have largely focused 
+on evolutionary time scales [@noe_Biological_1994a;@johnstone_Mutualism_2008a] 
+$\color{red}{\text{Hoekstra xxxx}}$, supply and demand conditions, which typically 
 depend on the abundance of the species involved, certainly vary in time 
-and space. How do partners adjust their strategy in the face of this
-variation? In animals an obvious general candidate mechanism for the
-strategic adjustment is the cognitive machinery. However, it is not
-clear which specific cognitive mechanisms allow individual to adjust
-their behaviour to the varying market conditions.
+and space within ecological time scales. Therefore, natural selection should 
+favour the ability to flexibly adjust decisions and behavioural output to 
+current market conditions. Indeed, such adjustments have been repeatedly 
+documented [@axen_signalling_1996]. In animals, an obvious general candidate 
+mechanism for the strategic adjustment is the cognitive machinery. However, 
+it is not clear which cognitive mechanisms allow individuals to adjust their 
+behaviour to the varying market conditions. As adjustments to changes in 
+market conditions have been documented in a great variety of species with 
+highly variable brain anatomies, the question arises to what extent mechanisms 
+beyond basic associative learning may be involved.
 
@@
 correlated with parasite load [@grutter_Relationship_1995a]. However, 
-early laboratory
-experiments showed that leaving causes service priority independent of
-client value [@bshary_Asymmetric_2002]. The experiments consisted of a
-simultaneous two-choice task, where cleaners had to decide which of two
+early laboratory experiments showed that leaving causes service 
+priority independent of client value [@bshary_Asymmetric_2002]. 
+The experiments consisted of asimultaneous two-choice task, 
+where cleaners had to decide which of two
 Plexiglas plates, which offered equal amounts of food, to approach first
@@
 [@salwiczek_Adult_2012; @zentall_Early_2017]; only African grey
-parrots solve this task as well [@pepperberg_Can_2014].
+parrots solve this task as well [@pepperberg_Can_2014]. As the correct 
+solution must be learned, and primates are known to readily distinguish 
+between one and two reward units if presented in more conventional ways 
+$\color{red}{\text{ref}}$, what makes the task difficult for most non-cleaners?
 
-Recent research has refined our view on partner choice and priority of
-access in the *L. dimidiatus* cleaning mutualism, and as a consequence
-performance in the biological market task. First, details of the task
-presentation may matter; i.e. what relevant information is encoded in
-the design of the two plates (colour versus size;
-[@wismer_Cuebased_2019]), or whether the information is in the colour of
+Recent research on the cognitive tool kit needed to solve an ephemeral 
+reward task has used a broad approach as proposed by @shettleworth_Cognition_2009, 
+who defined cognition as includes all ways in which animals take in information 
+through the senses, process, retain and decide to act on it. Indeed, perception 
+of relevant cues is of major importance for individual performance; 
+i.e. what relevant information is encoded in the design of the two 
+plates (colour versus size; [@wismer_Cuebased_2019]), or whether 
+the information is in the colour of
 the food [@pretot_Comparative_2021; @pretot_Comparing_2016], and
 whether the food is visible or hidden/released only when the subjects
-made choices on a touch screen [@pretot_Factors_2016]. Second, it
-appears that cleaner and client densities in nature affect how cleaners
-perform in the original market task: when densities are low, cleaners
-are more likely to fail to complete the task [@triki_Biological_2019;
-@triki_Decrease_2018; @wismer_Variation_2014]. The apparent explanation
-for this failure is that visitor clients are less likely to exert their
-choice options (and hence wait for inspection if made to wait) when
-cleaner fish densities are low [@triki_Brain_2020]. This change in
-behaviour may be due to the fact that when cleaner densities are low,
-the cost of switching in terms of distance to swim and time invested
-increases. If visitors are not choosy, cleaners should not give them
-priority anymore. Interestingly, while cleaners from high-density areas
-have larger forebrains harbouring more cells than cleaners from
-low-density areas [@triki_Brain_2020], on a local scale those
-individuals that perform in the market task in a way that corresponds to
-the locally optimal strategy (solving/failing the task when living in
-high/low density) have relatively larger forebrains [@triki_Brain_2020].
-Taken together, empirical results clearly show major intra- and
-inter-specific variation in performance in the market task, warranting
-investigation of the underlying cognitive machinery, from perception to
-decision-making [@shettleworth_Cognition_2009].
-
-One approach to identify candidate mechanisms underlying performance in
-a cognitive task is to develop proximate learning models and to evaluate
-their predictions in light of the behavioural data (e.g.
-[@dubois_Model_2021]). By varying the cognitive tool kit, one can assess
-which minimal kit is necessary to solve the task at hand. This approach
-has been used to analyse the market task [@prat_Role_2021;
-@quinones_Reinforcement_2019]. Learning models showed that basic
-reinforcement learning does not suffice to solve the task, this is
-particularly so when models assume the more complex natural situation in
-which cleaners not only face resident-visitor pairs but also
+made choices on a touch screen [@pretot_Factors_2016]. However, identifying 
+cues as salient is not the only challenge of the ephemeral reward task, 
+as revealed by proximate learning models. Such models allow varying the 
+cognitive tool kit and to evaluate which minimal kit is necessary to solve 
+the task at hand (e.g. [@dubois_Model_2021]). Applied to the ephemeral 
+reward task, learning models showed that basic reinforcement learning does 
+not suffice to solve the task [@prat_Modelling_2022; @quinones_Reinforcement_2019]. 
+This is particularly so when models assume the more complex natural 
+situation in which cleaners not only face resident-visitor pairs but also 
 visitor-visitor and resident-resident pairs, as well only a resident or 
 only a visitor. To be able to give visitors priority over residents, 
-cleaners first need to be able to assess a client's value separately for
-the three possible forms of encounter (alone, paired with a fish with
-the same strategic option, paired with a fish with the alternative
-strategic option) [@quinones_Reinforcement_2019]. In addition, cleaners
-need to account for the future consequences of current decisions. In the
-model, this could be achieved in two non-mutually exclusive ways
-[@quinones_Reinforcement_2019]: through low temporal discounting of
-future effects and/or through perceiving a visitor client leaving as
-psychological punishment (i.e. as a negative reinforcer). Given that a
-negative reinforcer is part of the ubiquitous learning mechanism termed
-operant conditioning [@thorndike_Animal_1898; @skinner_Behavior_1938], 
-this explanation can be
-considered the simpler one. Furthermore, accounting for the future
-effects of an action is considered an advanced cognitive ability
-[@suddendorf_Evolution_2007]. Here, we fitted our model to the empirical
-data on fish densities and cleaner fish performance in the market task
-with the aim to determine the likely mechanism used by cleaners to
-incorporate future consequences of current decisions.
+cleaners need to be able to assess a client’s value separately for the 
+three possible forms of encounter (alone, paired with a fish with the 
+same strategic option, paired with a fish with the alternative strategic option) 
+[@quinones_Reinforcement_2019]. The ability to keep such separate scores 
+for the same stimulus has been termed configurational learning, 
+or chunking, or segmentation (see references in @prat_Modelling_2022).
+
+To solve the ephemeral reward task, cleaners also need to account for 
+the future consequences of current decisions. In the model by 
+Quiñones et al. @quinones_Reinforcement_2019, this could be achieved in 
+two non-mutually exclusive ways: through low temporal discounting of 
+future effects, also termed ‘chaining’ [@enquist_Power_2016]; and/or 
+through perceiving a visitor client leaving as psychological punishment 
+(i.e. as a negative reinforcer). Given that a negative reinforcer is part 
+of the ubiquitous learning mechanism termed operant conditioning 
+[@thorndike_Animal_1898; @skinner_Behavior_1938], this explanation 
+could be considered the simpler one. Furthermore, accounting for the 
+future effects of an action is considered an advanced cognitive 
+ability [@suddendorf_Evolution_2007]. Thus, standard logic of 
+Lloyd Morgan’s cannon demands that operant conditioning as the simpler 
+explanation is to be accepted by default. Here, we explore the 
+possibility that fitting a model in which the action of these two 
+mechanisms, operant conditioning and chaining, depends 
+on model parameters may reveal which process cleaners actually use. 
+This is because one process may be better at predicting the observed 
+variation in cleaner fish performance as a function of ecological conditions.
+
+Various repetitions of the ephemeral reward task in different years and 
+with cleaners caught from various locations around Lizard Island, 
+Great Barrier Reef, revealed that cleaner and client densities in 
+nature affect how cleaners perform in the original market task: 
+when relative densities are low, cleaners are more likely to fail to 
+complete the task [@triki_Biological_2019;
+@triki_Decrease_2018; @wismer_Variation_2014]. The explanation for this pattern
+is twofold. First, low cleaner abundances implies low supply and high demand 
+of cleaning services. Under this conditions, there will be less occasions under 
+which failing to give priority to a visitor translates to an empty 
+cleaning station. Secondly and also related to the state of the cleaning market,
+visitor clients are less likely to exert their choice options 
+(and hence wait for inspection if made to wait) when
+cleaner fish densities are low [@triki_Brain_2020]. If visitors are not choosy, 
+cleaners should not give them priority anymore. Thus, the underling 
+cognitive machinery and ecological variables apparently interact to produce 
+such variable performance. By fitting our model to the empirical data on 
+fish densities and cleaner fish performance in the ephemeral reward task 
+we aimed to address two questions. First, we aimed to determine the likely 
+mechanism used by cleaners to incorporate future consequences of current 
+decisions by testing whether operant conditioning, chaining, or a combination 
+of both best explains performance. Second and related to the first 
+question, we aimed to determine whether the two mechanisms differed 
+with respect to the ecological conditions that are likely to cause high 
+versus low performance in the ephemeral reward task. If that were the case, 
+we would assess which mechanism would yield more appropriate performance 
+patterns. Relying on the logic of biological market theory, we predicted 
+that appropriate performance is to show low preference for visitors under high
+local client-to-cleaner ratio as visitor leaving rates should be low 
+and any leaving visitor will be readily replaced by another client. In contrast, 
+cleaners should show high performance if the local client-to-cleaner 
+ratio favours clients.
 

### 2022-01-14 aesth_par.R

@@ -20,6 +20,19 @@ paletteMeans <- colorRampPalette(c('#d73027','#fc8d59','#fee090',
 
 paletteVar <- colorRampPalette(c('#d8b365','#f5f5f5','#5ab4ac'),alpha=TRUE)
 
-
-zegniPal <- wes_palette("Zissou1",100, type = "continuous")
+multDiscrPallet <- c(
+  "dodgerblue2", "#E31A1C", # red
+  "green4",
+  "#6A3D9A", # purple
+  "#FF7F00", # orange
+  "black", "gold1",
+  "skyblue2", "#FB9A99", # lt pink
+  "palegreen2",
+  "#CAB2D6", # lt purple
+  "#FDBF6F", # lt orange
+  "gray70", "khaki2",
+  "maroon", "orchid1", "deeppink1", "blue1", "steelblue4",
+  "darkturquoise", "green1", "yellow4", "yellow3",
+  "darkorange4", "brown"
+)
 

### 2022-01-14 manFigures.R

@@ -6,6 +6,7 @@ library(ggplot2)
 library("RColorBrewer")
 library("patchwork") 
 library(ggpubr)
+library(ggdist)
 library(here)
 library(cowplot)
 source(here("loadData.R"))
@@ -207,23 +208,40 @@ cont.obs.pred.both<- ggplot(data = FIAinterpData.both,aes(x=rel.abund.cleaners,y
              shape=21,color="black")+sc+xlab("")+
   ylab("Probability of visitor leaving")+
   labs(fill="Probability \n of choosing \n a visitor")+
-  theme(axis.text = element_text(size=axisSize),
-axis.title.x = element_text(size=axislabSize),axis.title.y = element_text(size=axislabSize))
+  theme(legend.position ="top",
+        axis.text = element_text(size=axisSize),
+        axis.title.x = element_text(size=axislabSize),
+        axis.title.y = element_text(size=axislabSize))
 
 # Panel full model scatter
-scatter.obs.pred.both<-ggplot(data = fieldatabyLoc.both,aes(y=market_binomial_data,x=probvisitor.pred))+
-  geom_point(data = fieldatabyLocSamps.both,aes(x=probvisitor.pred,y=probVisi.data),
-             color='grey')+
-  geom_point(size=4)+ylim(0.4,0.9)+xlim(0.4,0.9)+
+scatter.obs.pred.both<-ggplot(data=fieldatabyLocSamps.both,
+                              aes(y=probVisi.data,colour=site_year,x=probvisitor.pred))+
+  stat_gradientinterval(aes(slab_alpha=F),point_interval = mode_hdi,point_size=2)+
   geom_abline(slope=1)+ylab("Observed")+xlab("Predicted")+
-  ggtitle("")+
-  theme_classic()+
-  theme(plot.title = element_text(hjust = 0.5),
-      axis.title.x = element_text(size=axisSize),axis.title.y = element_text(size=axislabSize),
-      axis.text = element_text(size=14))+
-  geom_text(x = 0.8, y = 0.85, label = expression(y==x), parse = TRUE,size=3)+
-  geom_text(x = 0.8, y = 0.5, label = deparse(bquote(R^2==.(round(rsqr.both.McFadden,4)))), 
-            parse = TRUE,size=3)
+  geom_point(data = fieldatabyLoc.both,aes(y=market_binomial_data,x=probvisitor.pred),
[…]

### 2022-02-03 manuscript_1.0/manuscript_1.0.Rmd
Edit's related to Redouan's comments

@@
 abstract: |
-  The same behaviour can be achieved by different mechanistic underpinnings.
-But the environmental conditions under which the behaviour is triggered might differ between these potential mechanisms.
-Thus, by analyzing the varitation of expression of a certain behavior across environmental gradients, it is possible to infer which mechanism is behind the behaviour of interest.
-To do this it is necessary to have clearcut predictions for the different candidate mechanisms.
-In here, we use experimental data on the behaviour of the cleaner fish *Labroides* *dimidiatus*, as well as enviromental variables from the location of fish, together with a computational model of the learning mechanisms.
-Using bayesian statistics, we fit key parameters of the computational model that determine the specific learning mechanism.
-We find that a model where cleaners estimate the long-term consequences of their actions, and use the estimate in their desicion making, explains better under which conditions the fish develop a preference for an ephemeral food source in the context of a biological market.
-We argue that the combination of computational models with data is powerful tool to infer the mechanistic underpinning behind behaviours of interest.
+  While it is generally straightforward to quantify individual performance in cognitive experiments, identifying the underlying cognitive processes remains a major challenge.
+Often, different mechanistic underpinnings may yield similar performances, and Lloyd Morgan’s cannon warrants acceptance of the simpler explanation.
+Alternatively, when the different mechanisms interact with environmental conditions, variation in performance across environments might allow to statistically infer the mechanism responsible.
+However, to do this it is necessary to have quantitative predictions for the different candidate mechanisms.
+Here, we use a set of computational models to get quantitative predictions from alternative learning mechanisms, and using Bayesian statistics fit the model parameters to performance data.
+We used experimental data on performance in an ephemeral reward task by wild-caught cleaner fish *Labroides dimidiatus*, as well as cleaner and client fish densities from the locations of capture.
+The task can in principle be solved by estimating future consequences of an action, or by perceiving the removal of the ephemeral reward as psychological punishment (negative reinforcement).
+We found that a model where cleaners only estimate the future consequences of their actions explains best which cleaner relative abundances cause the fish to develop a preference for an ephemeral food source.
+This model also yields performances that can be considered the result of locally optimal decision-rules, in contrast to the negative reinforcement model.
+We argue that the combination of computational models with data is a powerful tool to infer the mechanistic underpinning behind cognitive performance.
 
@@
 Cooperation among individuals of the same or different species is
-ubiquitous in nature. Among individuals of different species it
-underlays the biological mechanism for fundamental ecological
-interactions such as pollination, nitrogen fixation or parasite removal
-[@begon_Ecology_2006]. When partners in these mutualistic interactions
-are able to choose their interaction partner, their investment and the
-return they obtain can be understood as a biological market
-[@hammerstein_Biological_2016; @leimar_Cooperation_2010;
-@noe_Biological_1994a;@noe_Biological_1995a]. Thus, we expect supply
-and demand of the good and services being exchanged to determine the
-action of individuals, at least in an evolutionary time-scale. However,
-supply and demand conditions of a biological market, which typically
+ubiquitous in nature. Whenever such interactions involve some degree 
+of partner choice, biological market theory predicts that the exchange 
+rate of goods and/or services traded adjusts to the law of supply and demand 
+[@noe_Biological_1995a]. While biological market models have largely focused 
+on evolutionary time scales [@noe_Biological_1994a;@johnstone_Mutualism_2008a] 
+$\color{red}{\text{Hoekstra xxxx}}$, supply and demand conditions, which typically 
 depend on the abundance of the species involved, certainly vary in time 
-and space. How do partners adjust their strategy in the face of this
-variation? In animals an obvious general candidate mechanism for the
-strategic adjustment is the cognitive machinery. However, it is not
-clear which specific cognitive mechanisms allow individual to adjust
-their behaviour to the varying market conditions.
+and space. Therefore, natural selection should 
+favour the ability to flexibly adjust decisions and behavioural output to 
+current market conditions. Indeed, such adjustments have been repeatedly 
+documented [@axen_Signalling_1996]. In animals, an obvious general candidate 
+mechanism for the strategic adjustment is the cognitive machinery. However, 
+it is not clear which cognitive mechanisms allow individuals to adjust their 
+behaviour to the varying market conditions. As adjustments to changes in 
+market conditions have been documented in a great variety of species with 
+highly variable brain anatomies, the question arises to what extent mechanisms 
+beyond basic associative learning may be involved.
 
@@
 larger than residents [ @bshary_Cleaner_2001a], and size is positively
-correlated with parasite load [@grutter_Relationship_1995a]. However, 
-early laboratory
-experiments showed that leaving causes service priority independent of
-client value [@bshary_Asymmetric_2002]. The experiments consisted of a
-simultaneous two-choice task, where cleaners had to decide which of two
+correlated with parasite load [@grutter_Relationship_1995]. However, 
+early laboratory experiments showed that leaving causes service 
+priority independent of client value [@bshary_Asymmetric_2002]. 
+The experiments consisted of asimultaneous two-choice task, 
+where cleaners had to decide which of two
 Plexiglas plates, which offered equal amounts of food, to approach first
@@
 [@salwiczek_Adult_2012; @zentall_Early_2017]; only African grey
-parrots solve this task as well [@pepperberg_Can_2014].
+parrots solve this task as well [@pepperberg_Can_2014]. As the correct 
+solution must be learned, and primates are known to readily distinguish 
+between one and two reward units if presented in more conventional ways 
+$\color{red}{\text{ref}}$, what makes the task difficult for most non-cleaners?
 
-Recent research has refined our view on partner choice and priority of
-access in the *L. dimidiatus* cleaning mutualism, and as a consequence
-performance in the biological market task. First, details of the task
-presentation may matter; i.e. what relevant information is encoded in
-the design of the two plates (colour versus size;
-[@wismer_Cuebased_2019]), or whether the information is in the colour of
+Recent research on the cognitive tool kit needed to solve an ephemeral 
+reward task has used a broad approach as proposed by Shettleworth 
+[@shettleworth_Cognition_2009], 
+who defined cognition as including all ways in which animals take in information 
+through the senses, process, retain and decide to act on it. Indeed, perception 
+of relevant cues is of major importance for individual performance; 
+i.e. what relevant information is encoded in the design of the two 
+plates (colour versus size; [@wismer_Cuebased_2019]), or whether 
+the information is in the colour of
 the food [@pretot_Comparative_2021; @pretot_Comparing_2016], and
 whether the food is visible or hidden/released only when the subjects
-made choices on a touch screen [@pretot_Factors_2016]. Second, it
-appears that cleaner and client densities in nature affect how cleaners
-perform in the original market task: when densities are low, cleaners
-are more likely to fail to complete the task [@triki_Biological_2019;
-@triki_Decrease_2018; @wismer_Variation_2014]. The apparent explanation
-for this failure is that visitor clients are less likely to exert their
-choice options (and hence wait for inspection if made to wait) when
-cleaner fish densities are low [@triki_Brain_2020]. This change in
-behaviour may be due to the fact that when cleaner densities are low,
-the cost of switching in terms of distance to swim and time invested
-increases. If visitors are not choosy, cleaners should not give them
-priority anymore. Interestingly, while cleaners from high-density areas
-have larger forebrains harbouring more cells than cleaners from
-low-density areas [@triki_Brain_2020], on a local scale those
-individuals that perform in the market task in a way that corresponds to
-the locally optimal strategy (solving/failing the task when living in
-high/low density) have relatively larger forebrains [@triki_Brain_2020].
-Taken together, empirical results clearly show major intra- and
-inter-specific variation in performance in the market task, warranting
-investigation of the underlying cognitive machinery, from perception to
-decision-making [@shettleworth_Cognition_2009].
-
-One approach to identify candidate mechanisms underlying performance in
-a cognitive task is to develop proximate learning models and to evaluate
-their predictions in light of the behavioural data (e.g.
-[@dubois_Model_2021]). By varying the cognitive tool kit, one can assess
-which minimal kit is necessary to solve the task at hand. This approach
-has been used to analyse the market task [@prat_Role_2021;
-@quinones_Reinforcement_2019]. Learning models showed that basic
-reinforcement learning does not suffice to solve the task, this is
-particularly so when models assume the more complex natural situation in
-which cleaners not only face resident-visitor pairs but also
+made choices on a touch screen [@pretot_Factors_2016]. However, identifying 
+cues as salient is not the only challenge of the ephemeral reward task, 
+as revealed by proximate learning models. Such models allow varying the 
+cognitive tool kit and to evaluate which minimal kit is necessary to solve 
+the task at hand (e.g. [@dubois_Model_2021]). Applied to the ephemeral 
+reward task, learning models showed that basic reinforcement learning does 
+not suffice to solve the task [@prat_Modelling_2022; @quinones_Reinforcement_2019]. 
+This is particularly so when models assume the more complex natural 
+situation in which cleaners not only face resident-visitor pairs but also 
 visitor-visitor and resident-resident pairs, as well only a resident or 
 only a visitor. To be able to give visitors priority over residents, 
-cleaners first need to be able to assess a client's value separately for
-the three possible forms of encounter (alone, paired with a fish with
-the same strategic option, paired with a fish with the alternative
-strategic option) [@quinones_Reinforcement_2019]. In addition, cleaners
-need to account for the future consequences of current decisions. In the
-model, this could be achieved in two non-mutually exclusive ways
-[@quinones_Reinforcement_2019]: through low temporal discounting of
-future effects and/or through perceiving a visitor client leaving as
-psychological punishment (i.e. as a negative reinforcer). Given that a
-negative reinforcer is part of the ubiquitous learning mechanism termed
-operant conditioning [@thorndike_Animal_1898; @skinner_Behavior_1938], 
-this explanation can be
-considered the simpler one. Furthermore, accounting for the future
-effects of an action is considered an advanced cognitive ability
-[@suddendorf_Evolution_2007]. Here, we fitted our model to the empirical
-data on fish densities and cleaner fish performance in the market task
-with the aim to determine the likely mechanism used by cleaners to
-incorporate future consequences of current decisions.
+cleaners need to be able to assess a client’s value separately for the 
+three possible forms of encounter (alone, paired with a fish with the 
+same strategic option, paired with a fish with the alternative strategic option) 
+[@quinones_Reinforcement_2019]. The ability to keep such separate scores 
+for the same stimulus has been termed configurational learning, 
+or chunking, or segmentation (see references in [@prat_Modelling_2022]).
+
+To solve the ephemeral reward task, cleaners also need to account for 
+the future consequences of current decisions. In the model by 
+Quiñones *et al.* [@quinones_Reinforcement_2019], this could be achieved in 
+two non-mutually exclusive ways: through low temporal discounting of 
+future effects, also termed ‘chaining’ [@enquist_Power_2016]; and/or 
+through perceiving a visitor client leaving as psychological punishment 
+(i.e. as a negative reinforcer). Given that a negative reinforcer is part 
+of the ubiquitous learning mechanism termed operant conditioning 
+[@thorndike_Animal_1898; @skinner_Behavior_1938], this explanation 
+could be considered the simpler one. Furthermore, accounting for the 
+future effects of an action is considered an advanced cognitive 
+ability [@suddendorf_Evolution_2007]. Thus, standard logic of 
+Lloyd Morgan’s cannon demands that operant conditioning as the simpler 
+explanation is to be accepted by default. Here, we explore the 
+possibility that fitting a model in which the action of these two 
+mechanisms, operant conditioning and chaining, depends 
+on model parameters may reveal which process cleaners actually use. 
+This is because one process may be better at predicting the observed 
+variation in cleaner fish performance as a function of ecological conditions.
+
+Various repetitions of the ephemeral reward task in different years and 
+with cleaners caught from various locations around Lizard Island, 
+Great Barrier Reef, revealed that cleaner and client densities in 
+nature affect how cleaners perform in the original market task: 
+when relative densities are low, cleaners are more likely to fail to 
+complete the task [@triki_Biological_2019;
+@triki_Decrease_2018; @wismer_Variation_2014]. The explanation for this pattern
+is twofold. First, low cleaner abundances implies low supply and high demand 
+of cleaning services. Under this conditions, there will be less occasions under 
+which failing to give priority to a visitor translates to an empty 
+cleaning station. Secondly and also related to the state of the cleaning market,
+visitor clients are less likely to exert their choice options 
+(and hence wait for inspection if made to wait) when
+cleaner fish densities are low [@triki_Brain_2020]. If visitors are not choosy, 
+cleaners should not give them priority anymore. Thus, the underling 
+cognitive machinery and ecological variables apparently interact to produce 
+such variable performance. By fitting our model to the empirical data on 
+fish densities and cleaner fish performance in the ephemeral reward task 
+we aimed to address two questions. First, we aimed to determine the likely 
+mechanism used by cleaners to incorporate future consequences of current 
+decisions by testing whether operant conditioning, chaining, or a combination 
+of both best explains performance. Second and related to the first 
+question, we aimed to determine whether the two mechanisms differed 
+with respect to the ecological conditions that are likely to cause high 
+versus low performance in the ephemeral reward task. If that were the case, 
+we would assess which mechanism would yield more appropriate performance 
+patterns. Relying on the logic of biological market theory, we predicted 
+that appropriate performance is to show low preference for visitors under high
+local client-to-cleaner ratio as visitor leaving rates should be low 
+and any leaving visitor will be readily replaced by another client. In contrast, 
+cleaners should show high performance if the local client-to-cleaner 
+ratio favours clients.
 
@@
 
-We used the data from [@triki_Biological_2019] to fit the parameters of
-the model analysed in [@quinones_Reinforcement_2019]. For the bayesian
-fitting procedure we used Markov Chain Monte Carlo (MCMC) with a
-Metropolis sampler to estimate the posterior distribution of the model
-parameters. The data consist a of the number of times that a set of
-cleaners chose to feed of a visitor client plate in the context of the
-market task. This set of cleaners were collected in different locations
-and in each one of those locations environmental variables were
-measured. These environmental variables recorded from each location are
-used as input for the computational model. Given these inputs, the
-computational model produces a time series of choices in the market
-task. In the model the preference for the two options changes as the
-algorithm learns based on the reward that the two options provide. Thus,
-we run the model for 10000 steps and use the last 3000 steps as the
-preference developed in the model for visitors given the environmental
-variables. We use this preference as the predicted probability in a
-binomial distribution to calculate the likelihood that the number of
-visitor choices obtained from each cleaner is generated by the model. We
-sum over all the cleaners the log-likehoods and use the total for the
-acceptance of new parameters in the MCMC.
+To test the relative validity of chaining versus negative reinforcement as 
+mechanisms to account for future consequences of current choices, 
+we combined empirical data from Triki *et. al* 
+[@triki_Biological_2019;@triki_Brain_2020]. with the computational 
+model analysed in Quiñones *et al.*[@quinones_Reinforcement_2019]. In order to 
+compare the explanatory power of the different hypothesis, we estimate the 
+parameter values of three versions of the model that best fit the data. 
+Particularly, we fit the parameter that determines how important 
+future rewards are ($\gamma$), the magnitude of the negative reward 
+($\eta$) and a scaling constant that translates absolute to relative 
+abundances (see following sections for details). We obtained model 
+predictions using a set of stochastic individual-based
+simulations. Thus, each parameter combination of the model yields not one 
+prediction for the data set, but a distribution of them. Thus, for the 
+fitting procedure, we use one of the most common algorithms in bayesian inference,
+the Markov Chain Monte Carlo (MCMC). MCMC is a stochastic algorithm that allows
+to sample from the posterior distribution of model parameter values. The posterior
+distribution represents the most likely parameter values given the data. 
+Due to the stochastic nature of MCMC, which repeatedly samples parameter values
+and evaluates their likelihood, the distribution of likelihoods from the 
+stochastic model is also explored. This makes MCMC and bayesian inference
+particularly suitable for the computational models we evaluate. Bellow, 
+we explain first the computational model and the data collection, and later 
+how the MCMC was used to estimate parameter values.
 
@@
 the model represent cleaners, and the options they face simulate the
-natural conditions of a cleaning market. Thus, individuals in the model
-choose to prioritize different clients. These clients are classified as
-resident and visitors. Residents are those clients that stay in the
-cleaning queue when they are not given priority; while visitors leave
+natural conditions of a cleaning market. Cleaners experience a series 
+of discrete time points in which they face different ‘states’, which 
+are defined by the number and type of clients inviting for service. 
+There are six possible states: zero clients, one resident, one visitor, 
+two residents, two visitors, and a mix of one resident and one visitor. 
+The probability of each state is largely determined by the relative 
+abundance of cleaners, residents and visitors, but to some degree by a 
+cleaner’s choices when it faces the resident-visitor combination. 
+This is because residents are those clients that stay in the
+cleaning queue when they are not given priority and hence would 
+still be available in the next time point; while visitors leave
 the queue (with a certain probability) after they are not given
@@
 in the direction that would lead to more reward being obtained, given
-the new information. Further details of the model implementation can be
-found in the paper [@quinones_Reinforcement_2019]. The model analysis
-points to the relevance of two parameters. First, $\gamma$ measures how
+the new information. In the long run, the probability of choosing a visitor 
+over a resident converges in the model. To which probability the model 
+will converge depends on the relative abundance of cleaners, visitors 
+and resident; as well as on the probability of visitors leaving the station
+when unattended. Further details of the model implementation can be
+found in the paper [@quinones_Reinforcement_2019].
+
+The model shows that only agents that calculate rewards separately for 
+the different states (termed ‘fully aware agents’) can potentially 
+prioritise visitors of residents in nature, and hence also solve the 
+ephemeral reward task. This is because pooling rewards for the two 
+clients from all states by ‘partially aware agents’ 
+(that only recognize the two clients as different) cancels out 
+all differences (see [@quinones_Reinforcement_2019]). However, 
+such *chunking* by fully aware agents is not enough to develop a 
+preference for visitors. In addition, agents need to find a mean 
+to incorporate future consequences of current choices. In the model, 
+this could be achieved with either of two parameters that could 
+also work together.  First, $\gamma$ measures how
 much individuals include future rewards in their decision updates. If
@@
 reward obtained from the subsequent choices. That amounts to calculating
-and using for decision making the future expected rewards in action.
+and using for decision making the future expected rewards of an action.
 Second, $\eta$ measures how much individuals include in their reward the
@@
 these parameters allow individuals to use in their estimates the future
-effects of their choices. The model analysis by Quiñones *et al*
-[@quinones_Reinforcement_2019] shows that without either of them, learning
-individuals cannot develop a preference for the visitor client. The
-analysis contrast the effect of these two parameters against variation
-in the relative abundance of the two client types. The analysis shows
-that under very high client (relative) abundance the presence of future
-rewards ($\gamma>0$) no longer favours the preference for the ephemeral
-clients, this effect does not occur with negative reward mediated by
-client behaviour ($\eta$). Thus, the analysis suggests that future
-reward as an explanation for cleaner ability to prefer visitors is
-supported by Triki *et al* [@triki_Biological_2019] data. However, a combination of
-future and negative rewards, could still be a better explanation for the
-data. In the current analysis, we will use the data from
-[@triki_Biological_2019] to fit some of the model parameters, particularly
-relevant we will fit $\gamma$ and $\eta$ to find out whether each or a
-combination of these effects is a better explanation for the pattern
-seen in the data. For other parameter values used for the model
-simulations and the MCMC see Table \ref{tab:param}
+effects of their choices.
 
-### Data explanation
+A further model analysis contrast the effect of these two 
+parameters against variation in the relative abundance of cleaners 
+and the two client types. Assuming certainty that visitors leave, the 
+two parameters yield different 
+predictions when relative client abundance is very high. Under such 
+conditions, the analysis shows that under very high client (relative) 
+abundance the presence of future rewards ($\gamma>0$) no longer favours 
+the preference for the ephemeral clients, while the preference persists 
+when the negative reward mediated by client behaviour ($\eta>0$) is 
+included. Thus, the analysis suggests that future reward as an 
+explanation for cleaner ability to prefer visitors is supported. 
+At first sight, empirical data seem to support future rewards as 
+the mechanism used by cleaners, as the statistical analysis  by 
+Triki *et al.* [@triki_Biological_2019] data revealed that low 
+cleaner-to-client ratios predict low preference for visitors and hence 
+low performance in the ephemeral reward task. However, low cleaner-to-client 
+ratios may also lead to low probabilities of visitors leaving, which would 
+cause low preferences for visitors independently of the underlying 
+mechanism [@quinones_Reinforcement_2019]. Furthermore, a combination 
+of future and negative rewards, could still be yield a better explanation 
+for the data than any single factor.
 
-*Insert here brief description of the data and data collection*
+### Empirical data
 
-In order to capture with the model the relationship between the
-characteristics of the market (environment) and the cleaner's
-performance we need to translate the absolute abundances of the data to
-to  a measure of relative abundances that captures client visitation patterns.
-This is because in the model, relative abundances
-of clients define not only the probability of residents and visitors,
+The empirical data were collected between 2010 and 2018 always during 
+the austral winter months June to August at Lizard Island 
+($14.6682° S, 145.4604° E$), Great Barrier Reef, Australia. 
+They consist of three sets: fish densities from a total of five study 
+reef sites (Corner Beach-CB, Horseshoe-HS, 
+Mermaid Cove-MC, Northern Horseshoe-NHS, and The Crest-TC), 
+natural observations of cleaners to quantify the probability 
+of visitors leaving if initially ignored in favour of another client, and the 
+performance of individuals caught from these sites in the ephemeral reward test. 
+In total, we have twelve site/year data sets for fish densities and 
+corresponding performance in the test. Thus, some sites were sampled more 
+than once. Due to major environmental perturbations during the study period 
+($\color{red}{\text{refs}}$), fish densities changed significantly even 
+within sites [@triki_Decrease_2018;@triki_Fluctuations_2019]. To estimate 
+the population density of cleaner fish and their clients at a given site in 
+a given year, Triki *et al.* [@triki_Biological_2019] used a series of ten 
+transects of $30m$ each. Observers swam along the transect lines placed on 
+the reef and first counted the visible large-bodied adult fish 
+(species with total length TL > $10cm$) on a width of $5m$, and then on the 
+return individuals of small-bodied fish species (TL < $10 cm$) on a width 
+of $1 m$. We included cleaner fish in the $5 m$ transect. Based on the 
+classification by Bshary [@bshary_Cleaner_2001a] and Wismer *et al.* 
+[@wismer_Variation_2014], all visitor client species ($n = 124$) were 
+large-bodied. Resident clients comprised all small-bodied species 
+($n = 30$) but also some large-bodied ones ($n = 15$). Overall, 
+large-bodied species are highly correlated with being a visitor, 
+and small-bodied species are a good correlate of residents. Based on the 
+transect data, Triki *et al.* [@triki_Biological_2019;@triki_Brain_2020] 
+estimated cleaner fish, small-bodied client, large-bodied client and total 
+client fish densities per $100 m^2$. LASSO analyses revealed that cleaner and
+large-bodied client densities were highly correlated, and only the former 
+was hence kept in the analyses as representative of both [@triki_Biological_2019]. 
+Cleaner densities, in interaction with visitor client leaving probability, 
+explained best individual performance in the ephemeral reward task 
+[@triki_Biological_2019], while cleaner-to-client ratio was not a significant 
+factor. This creates a certain mismatch with the model by Quiñones *et al.* 
+[@quinones_Reinforcement_2019], which focused on abundance of cleaners relative 
+to overall client abundance in order to capture the characteristics 
+of the market. Importantly, relative abundances of clients define not only 
+the probability of interactions with residents and visitors, but also affect 
+how often the cleaning station is empty (e.g. there are no clients to be cleaned). 
+The higher the relative abundance of cleaners is, the higher is the probability 
+of cleaning stations being empty at a given time point. How often the 
+cleaning stations are empty in turns influences the value that cleaners can 
+expect from their choices. The emptier the cleaning stations are, the more 
+beneficial it is to prioritize a client that will not stay. On the other hand, 
+situations where cleaners have to choose will be rare if cleaner relative 
+abundance is high, which reduces the total value of prioritizing visitors 
+over residents and makes it more difficult to learn a preference for visitors. 
+Given the model structure, we used the empirical data to calculate relative 
+abundances of cleaners, residents and visitors for the current analyses. 
+To incorporate the empirical finding that absolute densities matter, we 
+introduced a new scaling constant (see section on model fitting).
+
+To collect data on the visitor clients’ probability of leaving if not serviced 
+immediately, eight cleaners per site/year were each filmed for $30 min$. 
+From the videos, all events in which a visitor client was made to wait in 
+favour of another (visitor or resident) client were identified, and noted 
+whether or not the visitor left [@triki_Biological_2019;@triki_Brain_2020]. 
+A total of 120 cleaners (10 individuals per 12 site/year) were tested in the 
+ephemeral reward task [@triki_Biological_2019;@triki_Brain_2020]. Authors 
+housed all captured cleaners individually in glass aquaria 
+( $62cm \times 27cm \times 37 cm$ ) and provided them 
+with PVC pipes ($10 cm \times 1 cm$) as shelters. 
+The task consisted of exposing the cleaner fish to substitute 
+models of client fish in the form of two *Plexiglas* plates offering the 
+same amount of food (one item of mashed prawn).  The two plates differed 
+in colour and pattern (horizontal green stripes or vertical pink stripes) 
+but had equal size ($10 cm \times 7 cm$). Importantly, the two plates played 
+different roles as either a visitor (ephemeral food source) or 
+resident (permanent food source). That is, if a cleaner inspected the 
+resident plate first, the experimenter withdrew the visitor plate out of 
+the aquarium as a consequence.  Choosing first the visitor plate, 
+however, granted access to both plates. The equal size of the plates 
+forced cleaner fish to learn to give service priority to the visitor plate 
+based solely on the behaviour-cue of the plates rather than size-cue 
+[@wismer_Cuebased_2019]. Triki *et al.* [@triki_Biological_2019;@triki_Brain_2020] 
+tested the fish for a maximum of 200 trials with 20 trials a day, 10 trials 
+in the morning and 10 trials in the afternoon. They randomized and 
+counterbalanced the plates’ spatial location (i.e. left or right) 
+between trials. Similarly, they counterbalanced the plates’ decoration 
+(colour and pattern) and the plates’ role (visitor or resident) between the 
+tested fish. The data was originally collected to assess which variables are 
+good predictors of the capacity to solve the ephemeral food task. Thus, previous 
+analysis  use specific statistical criteria to classify individual cleaners'
+performance as successful or failure [@triki_Biological_2019]. Because the model 
+predicts the preference of cleaners given the set of environmental variable, 
+we instead use the raw data of individuals cleaners' decisions.
+We use 20 choices from each cleaner as the preference they develop 
+for the visitor plate. Which these 20 choices were vary for each cleaner depending 
+on the performance that was originally assessed. For cleaners that did not 
+succeed, the 20 choices correspond to the last two sessions. Cleaners that 
+succeeded in solving the task were tested on a reversal task. That is, the 
+pattern in plates was switched to the opposite role they played in the 
+initial test. For those cleaners, we used the last session before they succeeded 
+in the initial, and the last session of the reversal, completing the 20 choices.
+We did not distinguish between individuals that reached the criterion early 
+or late during the 200 trials.
+
+### Statistical analysis
+
+The aim of the analysis is to fit the key model parameters that allow 
+individuals to incorporate future consequences of current actions, 
+$\gamma$ and $\eta$, to the data from Triki *et al.* 
+[@triki_Biological_2019;@triki_Brain_2020] to find out whether each or 
+a combination of these effects is a better explanation for the pattern 
+seen in the data. In particular, we are interested in the relation between the 
+ecological variables: cleaners, visitor clients, resident clients abundances and
+visitor clients leaving probability; and cleaners' preference for visitor clients
+over residents. Thus, the four ecological variables are given as input to 
+the models. The preference for visitors gotten from the simulations of the model 
+is used as the prediction for the response variable, while the number of visitors 
+chosen out of the 20 choices of each cleaner as the observed response variable. 
+We kept all  other parameter values used for the model simulations constant, 
+see Table \ref{tab:param}.
+
+In order to capture with the model the relationship between the characteristics 
+of the market (environment) and the cleaner’s preference we need to translate 
+the absolute abundances of the data to to a measure of relative abundances 
+that captures client visitation patterns. This is because in the model, relative 
+abundances of clients define not only the probability of residents and visitors, 
 but also how often the cleaning station is empty (e.g. there are no 
-clients to be cleaned). The more cleaners there are, the more options
-are available for the clients and hence the higher is the probability of
-empty cleaning stations. How often the cleaning stations are empty in
-turns influences the value that cleaners can expect from their choices.
-The emptier the cleaning stations are, the more beneficial it is to
-prioritize a client that will not stay. However, the frequency of empty
-spots in the cleaning station does not only depend on cleaner abundances 
-but also on the frequency with which clients visit the
-station. The client visitation frequency will likely vary among
-different clients depending on parasite abundances and loads. These are
-variables for which we do not have field estimates. Thus, we computed a
-measure of relative cleaner abundance for each site relative to absolute
-abundances and multiplied by a scaling constant that changes the range
-of the variable. This scaling constant is meant to capture variation in the market 
-conditions driven partly by cleaner abundance. We fit the value of the 
-scaling constant as part of the
-statistical inference. As for the client abundances for residents and
-visitors we computed a relative measure with respect to the total client
-abundance, and weighted that by the rescaled relative absence of
-cleaners (1-relative cleaner abundance). Thus, all three measures of
-relative abundance sum up to 1, and can be used in the model as a proxy
+clients to be cleaned). The frequency with which clients visit the station 
+is another variable, which will likely vary among different client species 
+depending on parasite abundances and loads. We do not have field estimates 
+for species specific parasite loads, especially not as a function of site. 
+In order to control for these aspects, we computed a measure of relative 
+cleaner abundance for each site relative to absolute abundances and multiplied 
+by a scaling constant that changes the range of the variable. This scaling 
+constant is hence meant to capture variation in the market conditions driven 
+partly by cleaner abundance. We fit the value of the scaling constant as 
+part of the statistical inference. As for the client abundances for 
+residents and visitors we computed a relative measure with respect to the 
+total client abundance, and weighted that by the rescaled relative absence 
+of cleaners ($1-\text{relative cleaner abundance}$). Thus, all three measures 
+of relative abundance sum up to 1, and can be used in the model as a proxy 
 for the probability of having different options in the cleaning station. 
+Note that the scaling constant was introduced to control for variation that 
+is not captured by the model; its parameter distribution does not offer 
+biological insights.
+
+Once we calculate the relative abundances, we can obtain predictions from 
+the model for each one of the locations and run the Markov Chain. We start the
+chain with random values for the parameters of interest, then run the 
+computational model once for every location using as input the ecological 
+explanatory variables. The model outputs the probability of choosing the visitor
+for each location $p_i$, where $i$ is the index for the 12 locations. Assuming a 
+binomial distribution, the probability that each of the cleaners' 20 choices was 
+generated by the model is given by $\binom{n}{k_ij}p^{k_{ij}}_i (1-p_i)^{n-k_{ij}}$;
+where $k_{ij}$ is the number of times that cleaner $j$ in location $i$ chose the 
+visitor over the resident; and $n=20$ (due to our choice of using 20 
+choices per cleaner). By taking the natural logarithm and summing over all 
+the cleaners and locations we obtain the log-likelihood of the data 
+given the model and parameters. We then propose a new set of parameters drawn 
+from a uniform distribution centred around the old parameter set. The amplitude 
+of the uniform distribution used for each parameter can be found in Table 
+\ref{tab:param}. Subsequently, we ran the model and calculated the likelihood 
+with the new parameter set. We then use the ratio of the two likelihoods to 
+choose which parameter set to keep. New parameter sets with a higher likelihood 
+than the old set replace old ones, and those with a lower likelihood are replace 
+current ones  with a probability equals to the log-likelihood ratio. 
+Given that we only use the likelihoods in the decision, we are using a 
+uninformative prior. Once we decide whether the new parameter set replaces 
+the old one, we ran the model again to sample to the likelihood 
+distribution of the parameter set. We then start 
+the cycle again by proposing a new set of parameters, and repeat the process for 
+$1e^5$ steps. We ran 5 independent chains, discarded the first 
+$100$ samples of each chain as burn in, and after that we keep 1 in every 
+100 samples to avoid autocorrelation. The collection of parameters sets kept in 
+all chains approximates the posterior distribution. The model as well as the 
+fitting algorithm were coded in *c++*, the diagnostics and visualization were 
+coded in R [@rcoreteam_Language_2021] of the  all code can be found at 
+$\color{red}{\text{include citation}}$
+
+In order to compare the fit that the three alternative models give we use the 
+distribution of pseudo $R^2$ proposed by Mcfadden [@mcfadden_Conditional_1974].
+Mcfadden's pseudo $R^2$ is a standard measure of fit for logistic regression. 
+In that context, $pseudo-R^2$ uses the log-likelihood of the data given 
+the model, relative to the log-likelihood of the data given a 
+model without covariates, as a measure of fit. Given that our 
+model is not a logistic regression, we measure the $pseudo-R^2$ in
+relation to the log-likelihood of a model
+with parameters $\gamma$ and $\eta$ set to zero. This in practice
+amounts to a model that has neutral preference between the two options. 
+Pseudo $R^2$ was calculated for all the samples of the posterior gotten from
+the MCMC. Thus, we use these distributions of pseudo $R^2$'s as a measure of
+fit.
 
@@
 On the left (panels a, c and c) posterior distributions for a model with all three parameters; while on the right (b and d) a model without negative reward.
-Panel f shows a measure of fit for both models, namely the distribution of pseudo-$R^2$ obtained from sampling the posterior distribution of parameter values.",out.width='100%',fig.height=7}
+Panel f shows a measure of fit for both models, namely the distribution of pseudo-$R^2$ obtained from sampling the posterior distribution of parameter values.",out.width='100%',fig.height=6}
 library(data.table)
@@
 distribution of $\gamma$ shifts to higher values. Under the new model,
-the estimates of $\gamma$ do not include zero, the distribution is
-centered around $0.5$. To asses the fit of the two models we calculated
-the $pseudo-R^2$ [@mcfadden_Conditional_1974], which is a standard
-measure of fit for logistic regression. In that context, $pseudo-R^2$
-uses the log-likelihood of the data given the model, relative to the
-log-likelihood of the data given a model without covariates, as a
-measure of fit. Given that our model is not a logistic regression, we
-measure the $pseudo-R^2$ in relation to the log-likelihood of a model
-with parameters $\gamma$ and $\eta$ set to zero. This in practice
-amounts to a model that has neutral preference between the two options.
-In panel f of figure \ref{fig:post} we show the distribution of
-$pseudo-R^2$ calculated using samples from the posterior distributions
-shown before, as well as from a model with negative reward but without
+the estimates of $\gamma$ do not include zero and the distribution is
+centered around $0.5$. In panel f of figure \ref{fig:post} 
+we show the distribution of $pseudo-R^2$ calculated using 
+samples from the posterior distributions shown before, 
+as well as from a model with negative reward but without
 future reward. Note, $pseudo-R^2$ can have negative values, that is when
@@
 Dots show the frequency of visitor choices for the 12 locations, as well as the corresponding relative cleaner abundance (x axis) and frequency of visitors leaving the station (y axis).
-Right-hand side panels: scatter plot of the observed and predicted probabilities of choosing a visitor for 12 locations.
-Line correspond to a perfect match between observed and predicted probabilities.
-Pseudo $R^2$ shown in the lower right corner corresponds to the fit of a model parameterized with the mode of the posterior distributions.
-Upper panels show prediction from a model including future and negative reward, lower panels froma  model with only future reward.",out.width='100%',fig.height=6}
+Right-hand side panels: Variation of the predicted probabilites  of choosing a visitor and their observed values for 12 locations.
+Circles show the mean prediction for each location from 100 samples taking from the posterior distribution.
+Thick and thin bars show the 66 and 95\\% credible interval taken from those posterior samples.
+Squares show the predictions used for panel on the righ-hand side.
+Colour denotes different locations (see Empirical data section).
+Black line correspond to a perfect match between observed and predicted probabilities.
+Upper panels show prediction from a model including future and negative reward, lower panels from a  model with only future reward.",out.width='100%',fig.height=5}
 
@@
 cont.obs.pred.gam,scatter.obs.pred.gam,
-          labels=c('a','b','c','d'),common.legend=TRUE,legend = "top")
+          labels=c('a','b','c','d'),common.legend = F,
+  heights=c(1.25,1))
+
 ```
@@
 choosing the visitor (y axis) are from the predictions of the models (x
-axis). The line represents the perfect fit between observed and
-predicted values. Predicted values were taken using the mode just as in
-the left panels. On the lower right corner of the panel we show the
-$pseudo-R^2$ for predictions using the mode of the posterior
-distributions. Despite having one more parameter varying, the full model
+axis). The black line represents the perfect fit between observed and
+predicted values. Bars show the variation in predicted values using 100 
+samples from the posterior distribution. Despite having one more 
+parameter varying, the full model
 gives a lower fit to the data than the model without negative reward.
-The difference in $pseudo-R^2$ for the point estimates is small, but
-using the whole posterior distribution shows the improvement in fit
-achieved by eliminating negative reward from the model (Fig.
-\ref{fig:post}f). In the supplementary material, we also show that a
+In the supplementary material, we also show predictions from 
 model with only negative reward, excluding future rewards ($\gamma=0$,
@@
 
-We have shown that using future rewards in the learning process is the
-cognitive strategy that best explains the intra-specific variation in
-cleaner performance in the market task. We compared future reward with
-the use of visitors behaviour as a primary source of negative reward,
-and a combination of both. All three models capture well the positive
-relation between visitor leaving behaviour and cleaner performance in
-the market task [@triki_Biological_2019]. For both mechanisms it is
-indeed necessary to have fleeing behaviour on the side of the visitors
-for cleaners to develop a preference for them. The key difference
-between future and negative reward emerges in the predicted relation
-between cleaner relative abundance and cleaner performance. When cleaner
-relative abundance is low a model with only future reward predicts low
-performance in the market task regardless of the visitor leaving
+We asked which if two potential cognitive mechanisms 
+– chaining of events, negative reinforcement, or a combination of both – 
+is the more likely mechanism to explain intra-specific variation in cleaner 
+performance in the ephemeral reward task as a function of ecological 
+conditions in the wild. To evaluate the merits of the alternative mechanisms, 
+we considered performance in the task to depend on decision-rules that 
+cleaners had developed in their natural environment: individuals that 
+solved the task did so because they already had a general preference for 
+visitors, and applied this rule once being familiar with the task.  
+While all three models capture well the positive relation between visitor 
+leaving behaviour and cleaner performance in
+the market task [@triki_Biological_2019], only the chaining mechanism 
+predicts that cleaner performance in the task should be low if their 
+local abundance in the wild relative to clients is low. Indeed, such low 
+performance is predicted regardless of the visitor leaving
 probability. In contrast, a model with negative reward predicts the
-highest performance with low relative cleaner abundance, particularly
+highest performance in the ephemeral reward task when relative 
+cleaner abundance is low, particularly
 together with high probability of visitor leaving (Fig. \ref{fig:pred}).
@@
 that is frequently full. Thus, when visitors leave, it's likely that the
-cleaner will have access to another client, and there will not be much
-difference in future reward between choosing a visitor and a resident.
-Thus, estimation of future reward will not develop a preference for the
-visitor in this conditions, because it matches the state of the market.
-On the other hand, the effect of negative reward is unaffected by this
-market situation. In a full station, cleaners will get more often the
+cleaner will have access to another client in the next step. Therefore, 
+there will not be much difference in future reward between choosing 
+a visitor and a resident, and cleaners will not develop a preference for the
+visitor in these conditions. On the other hand, the effect of negative reward 
+would be opposite as in a full station, cleaners will get more often the
 heterotypic (resident-visitor) option and will develop a preference for
@@
 efficiently. Overall, estimation of future reward is then the cognitive
-mechanism that allows cleaners to adaptively respond conditions to the
+mechanism that allows cleaners to adaptively respond to the
 ecological conditions of the biological market.
 
-The cognitive mechanism that our analysis highlights does not require a
-direct flow of information between the cleaner and its social
-environment. The adaptive responses to local conditions in cleaners is
-not only evidenced by their performance in experiments, but also by
-changes in their brain anatomy. Indeed, individual cleaners that
-performed in the laboratory test according to what is best at the
-location in which they were caught had larger forebrains harbouring more
-cells than individuals whose performance mismatched locally optimal
-decision-rules [@triki_Brain_2020]. This suggests that despite the
-overall behavioural adjustment, evidenced here and elsewhere
-[@triki_Biological_2019; @triki_Decrease_2018], there are some
-cleaners better than others at adjusting their behaviour. Triki *et al.*
-[@triki_Brain_2020] refer to these as socially competent cleaners. Social
-competence refers to the ability to optimise social behaviour depending
-on the available social information [@taborsky_Social_2012a;
-@bshary_Cooperation_2015]. However, we have shown here that cleaners
-are able to adjust their preference according to the social environment
-without using any direct information about the social environment.
-Instead cleaners seem to adjust their preference using information from
-the visitation patterns of their clients. These patters are of course
-determined by the feedback with the cleaner's social environment
-(relative abundance). Our models, however, do not include the
-possibility of cleaners responding to their relative abundance directly.
-The mechanism we present is a general way to learn from the environment
-in both asocial and social situations. It would be interesting to
-contrast this learning mechanism with one tailored to a social
-situation, and see whether such mechanism fits the data better. More
-generally, an important challenge ahead is to understand which cognitive
-mechanisms evolved exclusively for social life.
+Our results support chaining as the more plausible mechanism behind the 
+inter-specific variation in cleaners' performance, which is also 
+the mechanism that allows them to respond more adaptively. This could
+suggest chaining to be under positive selection. In the standard ephemeral
+reward task, however, food amount and quality are equal between the 
+two plates. An given that models resemble this, choosing visitors over 
+residents in low cleaner abundances does not diminish the 
+amount of food/reward in the the models. 
+On the other hand, a cleaner committed to visitors might find more difficult 
+to include in the decision making other variables, like parasite load 
+and/or mucus quality, that do predict the amount of food in the field 
+[@roche_Client_2021]. In nature and in laboratory experiments, cleaners prefer 
+higher quality mucus and more food in the absence of market effects 
+(i.e. in simultaneous 2-choice options, 
+[@triki_Fluctuations_2019;@grutter_Cleaner_2004]), and they use size as a 
+proxy for food availability [@wismer_Cuebased_2019;@grutter_Does_2005]. 
+How important this limitation is will determine whether chaining yields a higher
+fitness for cleaners.
 
-One potential difference between cleaners that adjusted adaptively, like
-the ones reported in Triki *et al.* [@triki_Brain_2020], is configurational learning or
-chunking. The original analysis of the learning model showed that agents
-needed two mechanism to solve the market task; to account for the
-future, and to assign value to the combination of clients present in the
-station [@quinones_Reinforcement_2019]. The latter is referred to as
-configurational learning or chunking [@sutherland_Configural_1989;
-@miller_Magical_1956]. Theoretical models suggest that the lack of
-configurational learning is related to a low frequency with which
-stimuli are encountered together [@kolodny_Evolution_2014;
-@prat_Role_2021]. Thus, cleaner relative abundance could be related to
-this mechanisms as well. Given that the lack of either of these two
-mechanisms yields neutral preferences [@quinones_Reinforcement_2019],
-we can't, based on the current analysis, distinguish between the two
-possibilities. One potential way to distinguish between the two would be
-to use an experimental set up designed to test configuration learning on
-cleaners with high and low performance in the market task
-[@woodbury_Learning_1943; @sutherland_Configural_1989].
+Individual cleaners that performed in the laboratory test according to what 
+is best at their site of capture (low performance when living at low densities, 
+high performance when living at high densities) had larger forebrains 
+harbouring more cells than individuals whose performance mismatched locally 
+optimal decision-rules [@triki_Brain_2020]. Triki *et al.*  refer to the 
+former as socially competent cleaners. Social competence refers to the 
+ability to optimise social behaviour depending on the available social 
+information [@taborsky_Social_2012a;
+@bshary_Cooperation_2015;@varela_Correlated_2020]. Our analyses yielded no 
+evidence that the difference in social competence with respect to the local 
+market conditions and associated brain morphology are due to the mechanism 
+used to incorporate future consequences. It could have been conceivable that 
+high performing individuals from low-density sites might use negative 
+reinforcement instead of chaining, but in that case negative reinforcement 
+should have explained part of the data. Configurational learning or 
+chunking [@sutherland_Configural_1989;@miller_Magical_1956], the second component 
+necessary to solve the ephemeral reward task [@quinones_Reinforcement_2019], was 
+not varied in the models analized here. However, while chunking tendencies 
+should vary to allow individuals to adapt to local conditions 
+[@prat_Modelling_2022;@kolodny_Evolution_2014], systematic differences 
+in individual chunking tendencies would not explain how socially 
+competent decisions vary as a function of relative abundance. 
+Therefore, it remains currently unclear what cell-demanding 
+mechanisms may cause variation in social competence that 
+translates into site-specific variation in performance in the 
+ephemeral reward task.
 
-Combining mechanistic modelling with empirical data provides a powerful
-tool to identify the cognitive processes underlying learning in animals.
-The combination overcomes the limitations of the general philosophy in
-animal cognition to apply the logic of Lloyd Morgen's canon (Occam's
-razor). Excluding basic reinforcement learning explanations (operant
-and/or classical conditioning) as a potential explanation in experiments
+The model is inspired by the general processes of associative learning
+where short term rewards are translated to decision making; thus, it 
+ignores alternative channels of information that could be relevant in 
+market-like situations. For example, the model does not investigate whether 
+cleaners actually assess the frequency of client visits or a mean frequency 
+of visitors leaving. The updating learning mechanism for the development 
+of preferences works on a trial by trial basis. In the model, cleaners 
+do not need to assess the actual state of the market, *i.e.* their density, 
+the density of residents and visitors, and client visitation rate as an 
+indicator of demand. They only need to assess short-term consequences of 
+own decisions on food intake and chain them. Also, for the sake of 
+simplicity, the model ignores the process by which cleaners discriminate 
+residents and visitor clients. A model that accounts for this discrimination
+probably involves the development of preferences for morphological or 
+behavioural features that are statistically associated with visitors 
+or residents. For example, visitors are on average larger larger 
+than residents [@bshary_Cleaner_2001a], and are less likely to chase 
+cleaners in response to the latter cheating by taking a bite of 
+mucus [@bshary_Asymmetric_2002]. Given these associations, chaining might 
+produce the decision-rule “chose the larger client and/or less aggressive 
+client”, which does not help in the standard ephemeral reward task.
+
+In conclusion, our study shows that variation in cognitive performance as 
+a function of ecological factors may set the stage for the use of 
+mechanistic modelling to identify the cognitive processes underlying 
+learning in animals. The combination overcomes the limitations 
+of the general philosophy in animal cognition to apply the logic of 
+Lloyd Morgen's canon (Occam's razor). Excluding basic 
+reinforcement learning explanations (operant and/or classical conditioning) 
+as a potential explanation in experiments
 often warrants animals solving the task on the first possible occasion.
@@
 Dots show the frequency of visitor choices for the 12 locations, as well as the corresponding relative cleaner abundance (x axis) and frequency of visitors leaving the station (y axis).
-Right-hand side panel: scatter plot of the observed and predicted probabilities of choosing a visitor for 12 locations.
-Line correspond to a perfect match between observed and predicted probabilities.",fig.pos = 'H', out.extra = "",out.width='95%',fig.height=4}
+Right-hand side panel: Right-hand side panels: Variation of the predicted probabilites  of choosing a visitor and their observed values for 12 locations.
+Circles show the mean prediction for each location from 100 samples taking from the posterior distribution.
+Thick and thin bars show the 66 and 95\\% credible interval taken from those posterior samples.
+Squares show the predictions used for panel on the righ-hand side.
+Colour denotes different locations (see Empirical data section).
+Black line correspond to a perfect match between observed and predicted probabilities.",fig.pos = 'H', out.extra = "",out.width='95%',fig.height=4}
 
 ggarrange(cont.obs.pred.Nrew,scatter.obs.pred.Nrew,
-          labels=c('a','b'),common.legend=FALSE,legend = "top")
+          labels=c('a','b'),common.legend=FALSE)
 

### 2022-02-03 manuscript_1.0/manuscript_1.0.tex
Edit's related to Redouan's comments

@@
 Here, we use a set of computational models to get quantitative predictions from alternative learning mechanisms, and using Bayesian statistics fit the model parameters to performance data.
-We used experimental data on performance in an ephemeral reward task by wild-caught cleaner fish Labroides dimidiatus, as well as cleaner and client fish densities from the locations of capture.
+We used experimental data on performance in an ephemeral reward task by wild-caught cleaner fish \emph{Labroides dimidiatus}, as well as cleaner and client fish densities from the locations of capture.
 The task can in principle be solved by estimating future consequences of an action, or by perceiving the removal of the ephemeral reward as psychological punishment (negative reinforcement).
@@
 depend on the abundance of the species involved, certainly vary in time
-and space within ecological time scales. Therefore, natural selection should
+and space. Therefore, natural selection should
 favour the ability to flexibly adjust decisions and behavioural output to
@@
 larger than residents \citep{bshary_Cleaner_2001a}, and size is positively
-correlated with parasite load \citep{grutter_Relationship_1995a}. However,
+correlated with parasite load \citep{grutter_Relationship_1995}. However,
 early laboratory experiments showed that leaving causes service
@@
 \citep{shettleworth_Cognition_2009},
-who defined cognition as includes all ways in which animals take in information
+who defined cognition as including all ways in which animals take in information
 through the senses, process, retain and decide to act on it. Indeed, perception
@@
 the future consequences of current decisions. In the model by
-Quiñones et al. \citep{quinones_Reinforcement_2019}, this could be achieved in
+Quiñones \emph{et al.} \citep{quinones_Reinforcement_2019}, this could be achieved in
 two non-mutually exclusive ways: through low temporal discounting of
@@
 
-We used the data from \citep{triki_Biological_2019} to fit the parameters of
-the model analysed in \citep{quinones_Reinforcement_2019}. For the bayesian
-fitting procedure we used Markov Chain Monte Carlo (MCMC) with a
-Metropolis sampler to estimate the posterior distribution of the model
-parameters. The data consist a of the number of times that a set of
-cleaners chose to feed of a visitor client plate in the context of the
-market task. This set of cleaners were collected in different locations
-and in each one of those locations environmental variables were
-measured. These environmental variables recorded from each location are
-used as input for the computational model. Given these inputs, the
-computational model produces a time series of choices in the market
-task. In the model the preference for the two options changes as the
-algorithm learns based on the reward that the two options provide. Thus,
-we run the model for 10000 steps and use the last 3000 steps as the
-preference developed in the model for visitors given the environmental
-variables. We use this preference as the predicted probability in a
-binomial distribution to calculate the likelihood that the number of
-visitor choices obtained from each cleaner is generated by the model. We
-sum over all the cleaners the log-likehoods and use the total for the
-acceptance of new parameters in the MCMC.
+To test the relative validity of chaining versus negative reinforcement as
+mechanisms to account for future consequences of current choices,
+we combined empirical data from Triki \emph{et. al}
+\citep{triki_Biological_2019, triki_Brain_2020}. with the computational
+model analysed in Quiñones \emph{et al.}\citep{quinones_Reinforcement_2019}. In order to
+compare the explanatory power of the different hypothesis, we estimate the
+parameter values of three versions of the model that best fit the data.
+Particularly, we fit the parameter that determines how important
+future rewards are (\(\gamma\)), the magnitude of the negative reward
+(\(\eta\)) and a scaling constant that translates absolute to relative
+abundances (see following sections for details). We obtained model
+predictions using a set of stochastic individual-based
+simulations. Thus, each parameter combination of the model yields not one
+prediction for the data set, but a distribution of them. Thus, for the
+fitting procedure, we use one of the most common algorithms in bayesian inference,
+the Markov Chain Monte Carlo (MCMC). MCMC is a stochastic algorithm that allows
+to sample from the posterior distribution of model parameter values. The posterior
+distribution represents the most likely parameter values given the data.
+Due to the stochastic nature of MCMC, which repeatedly samples parameter values
+and evaluates their likelihood, the distribution of likelihoods from the
+stochastic model is also explored. This makes MCMC and bayesian inference
+particularly suitable for the computational models we evaluate. Bellow,
+we explain first the computational model and the data collection, and later
+how the MCMC was used to estimate parameter values.
 
@@
 the model represent cleaners, and the options they face simulate the
-natural conditions of a cleaning market. Thus, individuals in the model
-choose to prioritize different clients. These clients are classified as
-resident and visitors. Residents are those clients that stay in the
-cleaning queue when they are not given priority; while visitors leave
+natural conditions of a cleaning market. Cleaners experience a series
+of discrete time points in which they face different `states', which
+are defined by the number and type of clients inviting for service.
+There are six possible states: zero clients, one resident, one visitor,
+two residents, two visitors, and a mix of one resident and one visitor.
+The probability of each state is largely determined by the relative
+abundance of cleaners, residents and visitors, but to some degree by a
+cleaner's choices when it faces the resident-visitor combination.
+This is because residents are those clients that stay in the
+cleaning queue when they are not given priority and hence would
+still be available in the next time point; while visitors leave
 the queue (with a certain probability) after they are not given
@@
 in the direction that would lead to more reward being obtained, given
-the new information. Further details of the model implementation can be
-found in the paper \citep{quinones_Reinforcement_2019}. The model analysis
-points to the relevance of two parameters. First, \(\gamma\) measures how
+the new information. In the long run, the probability of choosing a visitor
+over a resident converges in the model. To which probability the model
+will converge depends on the relative abundance of cleaners, visitors
+and resident; as well as on the probability of visitors leaving the station
+when unattended. Further details of the model implementation can be
+found in the paper \citep{quinones_Reinforcement_2019}.
+
+The model shows that only agents that calculate rewards separately for
+the different states (termed `fully aware agents') can potentially
+prioritise visitors of residents in nature, and hence also solve the
+ephemeral reward task. This is because pooling rewards for the two
+clients from all states by `partially aware agents'
+(that only recognize the two clients as different) cancels out
+all differences (see \citep{quinones_Reinforcement_2019}). However,
+such \emph{chunking} by fully aware agents is not enough to develop a
+preference for visitors. In addition, agents need to find a mean
+to incorporate future consequences of current choices. In the model,
+this could be achieved with either of two parameters that could
+also work together. First, \(\gamma\) measures how
 much individuals include future rewards in their decision updates. If
@@
 reward obtained from the subsequent choices. That amounts to calculating
-and using for decision making the future expected rewards in action.
+and using for decision making the future expected rewards of an action.
 Second, \(\eta\) measures how much individuals include in their reward the
@@
 these parameters allow individuals to use in their estimates the future
-effects of their choices. The model analysis by Quiñones \emph{et al}
-\citep{quinones_Reinforcement_2019} shows that without either of them, learning
-individuals cannot develop a preference for the visitor client. The
-analysis contrast the effect of these two parameters against variation
-in the relative abundance of the two client types. The analysis shows
-that under very high client (relative) abundance the presence of future
-rewards (\(\gamma>0\)) no longer favours the preference for the ephemeral
-clients, this effect does not occur with negative reward mediated by
-client behaviour (\(\eta\)). Thus, the analysis suggests that future
-reward as an explanation for cleaner ability to prefer visitors is
-supported by Triki \emph{et al} \citep{triki_Biological_2019} data. However, a combination of
-future and negative rewards, could still be a better explanation for the
-data. In the current analysis, we will use the data from
-\citep{triki_Biological_2019} to fit some of the model parameters, particularly
-relevant we will fit \(\gamma\) and \(\eta\) to find out whether each or a
-combination of these effects is a better explanation for the pattern
-seen in the data. For other parameter values used for the model
-simulations and the MCMC see Table \ref{tab:param}
+effects of their choices.
 
-\hypertarget{data-explanation}{%
-\subsubsection{Data explanation}\label{data-explanation}}
+A further model analysis contrast the effect of these two
+parameters against variation in the relative abundance of cleaners
+and the two client types. Assuming certainty that visitors leave, the
+two parameters yield different
+predictions when relative client abundance is very high. Under such
+conditions, the analysis shows that under very high client (relative)
+abundance the presence of future rewards (\(\gamma>0\)) no longer favours
+the preference for the ephemeral clients, while the preference persists
+when the negative reward mediated by client behaviour (\(\eta>0\)) is
+included. Thus, the analysis suggests that future reward as an
+explanation for cleaner ability to prefer visitors is supported.
+At first sight, empirical data seem to support future rewards as
+the mechanism used by cleaners, as the statistical analysis by
+Triki \emph{et al.} \citep{triki_Biological_2019} data revealed that low
+cleaner-to-client ratios predict low preference for visitors and hence
+low performance in the ephemeral reward task. However, low cleaner-to-client
+ratios may also lead to low probabilities of visitors leaving, which would
+cause low preferences for visitors independently of the underlying
+mechanism \citep{quinones_Reinforcement_2019}. Furthermore, a combination
+of future and negative rewards, could still be yield a better explanation
+for the data than any single factor.
 
-\emph{Insert here brief description of the data and data collection}
+\hypertarget{empirical-data}{%
+\subsubsection{Empirical data}\label{empirical-data}}
 
-In order to capture with the model the relationship between the
-characteristics of the market (environment) and the cleaner's
-performance we need to translate the absolute abundances of the data to
-to a measure of relative abundances that captures client visitation patterns.
-This is because in the model, relative abundances
-of clients define not only the probability of residents and visitors,
+The empirical data were collected between 2010 and 2018 always during
+the austral winter months June to August at Lizard Island
+(\(14.6682° S, 145.4604° E\)), Great Barrier Reef, Australia.
+They consist of three sets: fish densities from a total of five study
+reef sites (Corner Beach-CB, Horseshoe-HS,
+Mermaid Cove-MC, Northern Horseshoe-NHS, and The Crest-TC),
+natural observations of cleaners to quantify the probability
+of visitors leaving if initially ignored in favour of another client, and the
+performance of individuals caught from these sites in the ephemeral reward test.
+In total, we have twelve site/year data sets for fish densities and
+corresponding performance in the test. Thus, some sites were sampled more
+than once. Due to major environmental perturbations during the study period
+(\(\color{red}{\text{refs}}\)), fish densities changed significantly even
+within sites \citep{triki_Decrease_2018, triki_Fluctuations_2019}. To estimate
+the population density of cleaner fish and their clients at a given site in
+a given year, Triki \emph{et al.} \citep{triki_Biological_2019} used a series of ten
+transects of \(30m\) each. Observers swam along the transect lines placed on
+the reef and first counted the visible large-bodied adult fish
+(species with total length TL \textgreater{} \(10cm\)) on a width of \(5m\), and then on the
+return individuals of small-bodied fish species (TL \textless{} \(10 cm\)) on a width
+of \(1 m\). We included cleaner fish in the \(5 m\) transect. Based on the
+classification by Bshary \citep{bshary_Cleaner_2001a} and Wismer \emph{et al.}
+\citep{wismer_Variation_2014}, all visitor client species (\(n = 124\)) were
+large-bodied. Resident clients comprised all small-bodied species
+(\(n = 30\)) but also some large-bodied ones (\(n = 15\)). Overall,
+large-bodied species are highly correlated with being a visitor,
+and small-bodied species are a good correlate of residents. Based on the
+transect data, Triki \emph{et al.} \citep{triki_Biological_2019, triki_Brain_2020}
+estimated cleaner fish, small-bodied client, large-bodied client and total
+client fish densities per \(100 m^2\). LASSO analyses revealed that cleaner and
+large-bodied client densities were highly correlated, and only the former
+was hence kept in the analyses as representative of both \citep{triki_Biological_2019}.
+Cleaner densities, in interaction with visitor client leaving probability,
+explained best individual performance in the ephemeral reward task
+\citep{triki_Biological_2019}, while cleaner-to-client ratio was not a significant
+factor. This creates a certain mismatch with the model by Quiñones \emph{et al.}
+\citep{quinones_Reinforcement_2019}, which focused on abundance of cleaners relative
+to overall client abundance in order to capture the characteristics
+of the market. Importantly, relative abundances of clients define not only
+the probability of interactions with residents and visitors, but also affect
+how often the cleaning station is empty (e.g.~there are no clients to be cleaned).
+The higher the relative abundance of cleaners is, the higher is the probability
+of cleaning stations being empty at a given time point. How often the
+cleaning stations are empty in turns influences the value that cleaners can
+expect from their choices. The emptier the cleaning stations are, the more
+beneficial it is to prioritize a client that will not stay. On the other hand,
+situations where cleaners have to choose will be rare if cleaner relative
+abundance is high, which reduces the total value of prioritizing visitors
+over residents and makes it more difficult to learn a preference for visitors.
+Given the model structure, we used the empirical data to calculate relative
+abundances of cleaners, residents and visitors for the current analyses.
+To incorporate the empirical finding that absolute densities matter, we
+introduced a new scaling constant (see section on model fitting).
+
+To collect data on the visitor clients' probability of leaving if not serviced
+immediately, eight cleaners per site/year were each filmed for \(30 min\).
+From the videos, all events in which a visitor client was made to wait in
+favour of another (visitor or resident) client were identified, and noted
+whether or not the visitor left \citep{triki_Biological_2019, triki_Brain_2020}.
+A total of 120 cleaners (10 individuals per 12 site/year) were tested in the
+ephemeral reward task \citep{triki_Biological_2019, triki_Brain_2020}. Authors
+housed all captured cleaners individually in glass aquaria
+( \(62cm \times 27cm \times 37 cm\) ) and provided them
+with PVC pipes (\(10 cm \times 1 cm\)) as shelters.
+The task consisted of exposing the cleaner fish to substitute
+models of client fish in the form of two \emph{Plexiglas} plates offering the
+same amount of food (one item of mashed prawn). The two plates differed
+in colour and pattern (horizontal green stripes or vertical pink stripes)
+but had equal size (\(10 cm \times 7 cm\)). Importantly, the two plates played
+different roles as either a visitor (ephemeral food source) or
+resident (permanent food source). That is, if a cleaner inspected the
+resident plate first, the experimenter withdrew the visitor plate out of
+the aquarium as a consequence. Choosing first the visitor plate,
+however, granted access to both plates. The equal size of the plates
+forced cleaner fish to learn to give service priority to the visitor plate
+based solely on the behaviour-cue of the plates rather than size-cue
+\citep{wismer_Cuebased_2019}. Triki \emph{et al.} \citep{triki_Biological_2019, triki_Brain_2020}
+tested the fish for a maximum of 200 trials with 20 trials a day, 10 trials
+in the morning and 10 trials in the afternoon. They randomized and
+counterbalanced the plates' spatial location (i.e.~left or right)
+between trials. Similarly, they counterbalanced the plates' decoration
+(colour and pattern) and the plates' role (visitor or resident) between the
+tested fish. The data was originally collected to assess which variables are
+good predictors of the capacity to solve the ephemeral food task. Thus, previous
+analysis use specific statistical criteria to classify individual cleaners'
+performance as successful or failure \citep{triki_Biological_2019}. Because the model
+predicts the preference of cleaners given the set of environmental variable,
+we instead use the raw data of individuals cleaners' decisions.
+We use 20 choices from each cleaner as the preference they develop
+for the visitor plate. Which these 20 choices were vary for each cleaner depending
+on the performance that was originally assessed. For cleaners that did not
+succeed, the 20 choices correspond to the last two sessions. Cleaners that
+succeeded in solving the task were tested on a reversal task. That is, the
+pattern in plates was switched to the opposite role they played in the
+initial test. For those cleaners, we used the last session before they succeeded
+in the initial, and the last session of the reversal, completing the 20 choices.
+We did not distinguish between individuals that reached the criterion early
+or late during the 200 trials.
+
+\hypertarget{statistical-analysis}{%
+\subsubsection{Statistical analysis}\label{statistical-analysis}}
+
+The aim of the analysis is to fit the key model parameters that allow
+individuals to incorporate future consequences of current actions,
+\(\gamma\) and \(\eta\), to the data from Triki \emph{et al.}
+\citep{triki_Biological_2019, triki_Brain_2020} to find out whether each or
+a combination of these effects is a better explanation for the pattern
+seen in the data. In particular, we are interested in the relation between the
+ecological variables: cleaners, visitor clients, resident clients abundances and
+visitor clients leaving probability; and cleaners' preference for visitor clients
+over residents. Thus, the four ecological variables are given as input to
+the models. The preference for visitors gotten from the simulations of the model
+is used as the prediction for the response variable, while the number of visitors
+chosen out of the 20 choices of each cleaner as the observed response variable.
+We kept all other parameter values used for the model simulations constant,
+see Table \ref{tab:param}.
+
+In order to capture with the model the relationship between the characteristics
+of the market (environment) and the cleaner's preference we need to translate
+the absolute abundances of the data to to a measure of relative abundances
+that captures client visitation patterns. This is because in the model, relative
+abundances of clients define not only the probability of residents and visitors,
 but also how often the cleaning station is empty (e.g.~there are no
-clients to be cleaned). The more cleaners there are, the more options
-are available for the clients and hence the higher is the probability of
-empty cleaning stations. How often the cleaning stations are empty in
-turns influences the value that cleaners can expect from their choices.
-The emptier the cleaning stations are, the more beneficial it is to
-prioritize a client that will not stay. However, the frequency of empty
-spots in the cleaning station does not only depend on cleaner abundances
-but also on the frequency with which clients visit the
-station. The client visitation frequency will likely vary among
-different clients depending on parasite abundances and loads. These are
-variables for which we do not have field estimates. Thus, we computed a
-measure of relative cleaner abundance for each site relative to absolute
-abundances and multiplied by a scaling constant that changes the range
-of the variable. This scaling constant is meant to capture variation in the market
-conditions driven partly by cleaner abundance. We fit the value of the
-scaling constant as part of the
-statistical inference. As for the client abundances for residents and
-visitors we computed a relative measure with respect to the total client
-abundance, and weighted that by the rescaled relative absence of
-cleaners (1-relative cleaner abundance). Thus, all three measures of
-relative abundance sum up to 1, and can be used in the model as a proxy
+clients to be cleaned). The frequency with which clients visit the station
+is another variable, which will likely vary among different client species
+depending on parasite abundances and loads. We do not have field estimates
+for species specific parasite loads, especially not as a function of site.
+In order to control for these aspects, we computed a measure of relative
+cleaner abundance for each site relative to absolute abundances and multiplied
+by a scaling constant that changes the range of the variable. This scaling
+constant is hence meant to capture variation in the market conditions driven
+partly by cleaner abundance. We fit the value of the scaling constant as
+part of the statistical inference. As for the client abundances for
+residents and visitors we computed a relative measure with respect to the
+total client abundance, and weighted that by the rescaled relative absence
+of cleaners (\(1-\text{relative cleaner abundance}\)). Thus, all three measures
+of relative abundance sum up to 1, and can be used in the model as a proxy
 for the probability of having different options in the cleaning station.
+Note that the scaling constant was introduced to control for variation that
+is not captured by the model; its parameter distribution does not offer
+biological insights.
+
+Once we calculate the relative abundances, we can obtain predictions from
+the model for each one of the locations and run the Markov Chain. We start the
+chain with random values for the parameters of interest, then run the
+computational model once for every location using as input the ecological
+explanatory variables. The model outputs the probability of choosing the visitor
+for each location \(p_i\), where \(i\) is the index for the 12 locations. Assuming a
+binomial distribution, the probability that each of the cleaners' 20 choices was
+generated by the model is given by \(\binom{n}{k_ij}p^{k_{ij}}_i (1-p_i)^{n-k_{ij}}\);
+where \(k_{ij}\) is the number of times that cleaner \(j\) in location \(i\) chose the
+visitor over the resident; and \(n=20\) (due to our choice of using 20
+choices per cleaner). By taking the natural logarithm and summing over all
+the cleaners and locations we obtain the log-likelihood of the data
+given the model and parameters. We then propose a new set of parameters drawn
+from a uniform distribution centred around the old parameter set. The amplitude
+of the uniform distribution used for each parameter can be found in Table
+\ref{tab:param}. Subsequently, we ran the model and calculated the likelihood
+with the new parameter set. We then use the ratio of the two likelihoods to
+choose which parameter set to keep. New parameter sets with a higher likelihood
+than the old set replace old ones, and those with a lower likelihood are replace
+current ones with a probability equals to the log-likelihood ratio.
+Given that we only use the likelihoods in the decision, we are using a
+uninformative prior. Once we decide whether the new parameter set replaces
+the old one, we ran the model again to sample to the likelihood
+distribution of the parameter set. We then start
+the cycle again by proposing a new set of parameters, and repeat the process for
+\(1e^5\) steps. We ran 5 independent chains, discarded the first
+\(100\) samples of each chain as burn in, and after that we keep 1 in every
+100 samples to avoid autocorrelation. The collection of parameters sets kept in
+all chains approximates the posterior distribution. The model as well as the
+fitting algorithm were coded in \emph{c++}, the diagnostics and visualization were
+coded in R \citep{rcoreteam_Language_2021} of the all code can be found at
+\(\color{red}{\text{include citation}}\)
+
+In order to compare the fit that the three alternative models give we use the
+distribution of pseudo \(R^2\) proposed by Mcfadden \citep{mcfadden_Conditional_1974}.
+Mcfadden's pseudo \(R^2\) is a standard measure of fit for logistic regression.
+In that context, \(pseudo-R^2\) uses the log-likelihood of the data given
+the model, relative to the log-likelihood of the data given a
+model without covariates, as a measure of fit. Given that our
+model is not a logistic regression, we measure the \(pseudo-R^2\) in
+relation to the log-likelihood of a model
+with parameters \(\gamma\) and \(\eta\) set to zero. This in practice
+amounts to a model that has neutral preference between the two options.
+Pseudo \(R^2\) was calculated for all the samples of the posterior gotten from
+the MCMC. Thus, we use these distributions of pseudo \(R^2\)'s as a measure of
+fit.
 
@@
 distribution of \(\gamma\) shifts to higher values. Under the new model,
-the estimates of \(\gamma\) do not include zero, the distribution is
-centered around \(0.5\). To asses the fit of the two models we calculated
-the \(pseudo-R^2\) \citep{mcfadden_Conditional_1974}, which is a standard
-measure of fit for logistic regression. In that context, \(pseudo-R^2\)
-uses the log-likelihood of the data given the model, relative to the
-log-likelihood of the data given a model without covariates, as a
-measure of fit. Given that our model is not a logistic regression, we
-measure the \(pseudo-R^2\) in relation to the log-likelihood of a model
-with parameters \(\gamma\) and \(\eta\) set to zero. This in practice
-amounts to a model that has neutral preference between the two options.
-In panel f of figure \ref{fig:post} we show the distribution of
-\(pseudo-R^2\) calculated using samples from the posterior distributions
-shown before, as well as from a model with negative reward but without
+the estimates of \(\gamma\) do not include zero and the distribution is
+centered around \(0.5\). In panel f of figure \ref{fig:post}
+we show the distribution of \(pseudo-R^2\) calculated using
+samples from the posterior distributions shown before,
+as well as from a model with negative reward but without
 future reward. Note, \(pseudo-R^2\) can have negative values, that is when
@@
 Dots show the frequency of visitor choices for the 12 locations, as well as the corresponding relative cleaner abundance (x axis) and frequency of visitors leaving the station (y axis).
-Right-hand side panels: scatter plot of the observed and predicted probabilities of choosing a visitor for 12 locations.
-Line correspond to a perfect match between observed and predicted probabilities.
-Pseudo $R^2$ shown in the lower right corner corresponds to the fit of a model parameterized with the mode of the posterior distributions.
-Upper panels show prediction from a model including future and negative reward, lower panels froma  model with only future reward.}\label{fig:pred}
+Right-hand side panels: Variation of the predicted probabilites  of choosing a visitor and their observed values for 12 locations.
+Circles show the mean prediction for each location from 100 samples taking from the posterior distribution.
+Thick and thin bars show the 66 and 95\% credible interval taken from those posterior samples.
+Squares show the predictions used for panel on the righ-hand side.
+Colour denotes different locations (see Empirical data section).
+Black line correspond to a perfect match between observed and predicted probabilities.
+Upper panels show prediction from a model including future and negative reward, lower panels from a  model with only future reward.}\label{fig:pred}
 \end{figure}
@@
 choosing the visitor (y axis) are from the predictions of the models (x
-axis). The line represents the perfect fit between observed and
-predicted values. Predicted values were taken using the mode just as in
-the left panels. On the lower right corner of the panel we show the
-\(pseudo-R^2\) for predictions using the mode of the posterior
-distributions. Despite having one more parameter varying, the full model
+axis). The black line represents the perfect fit between observed and
+predicted values. Bars show the variation in predicted values using 100
+samples from the posterior distribution. Despite having one more
+parameter varying, the full model
 gives a lower fit to the data than the model without negative reward.
-The difference in \(pseudo-R^2\) for the point estimates is small, but
-using the whole posterior distribution shows the improvement in fit
-achieved by eliminating negative reward from the model (Fig.
-\ref{fig:post}f). In the supplementary material, we also show that a
+In the supplementary material, we also show predictions from
 model with only negative reward, excluding future rewards (\(\gamma=0\),
@@
 
-We have shown that using future rewards in the learning process is the
-cognitive strategy that best explains the intra-specific variation in
-cleaner performance in the market task. We compared future reward with
-the use of visitors behaviour as a primary source of negative reward,
-and a combination of both. All three models capture well the positive
-relation between visitor leaving behaviour and cleaner performance in
-the market task \citep{triki_Biological_2019}. For both mechanisms it is
-indeed necessary to have fleeing behaviour on the side of the visitors
-for cleaners to develop a preference for them. The key difference
-between future and negative reward emerges in the predicted relation
-between cleaner relative abundance and cleaner performance. When cleaner
-relative abundance is low a model with only future reward predicts low
-performance in the market task regardless of the visitor leaving
+We asked which if two potential cognitive mechanisms
+-- chaining of events, negative reinforcement, or a combination of both --
+is the more likely mechanism to explain intra-specific variation in cleaner
+performance in the ephemeral reward task as a function of ecological
+conditions in the wild. To evaluate the merits of the alternative mechanisms,
+we considered performance in the task to depend on decision-rules that
+cleaners had developed in their natural environment: individuals that
+solved the task did so because they already had a general preference for
+visitors, and applied this rule once being familiar with the task.\\
+While all three models capture well the positive relation between visitor
+leaving behaviour and cleaner performance in
+the market task \citep{triki_Biological_2019}, only the chaining mechanism
+predicts that cleaner performance in the task should be low if their
+local abundance in the wild relative to clients is low. Indeed, such low
+performance is predicted regardless of the visitor leaving
 probability. In contrast, a model with negative reward predicts the
-highest performance with low relative cleaner abundance, particularly
+highest performance in the ephemeral reward task when relative
+cleaner abundance is low, particularly
 together with high probability of visitor leaving (Fig. \ref{fig:pred}).
@@
 that is frequently full. Thus, when visitors leave, it's likely that the
-cleaner will have access to another client, and there will not be much
-difference in future reward between choosing a visitor and a resident.
-Thus, estimation of future reward will not develop a preference for the
-visitor in this conditions, because it matches the state of the market.
-On the other hand, the effect of negative reward is unaffected by this
-market situation. In a full station, cleaners will get more often the
+cleaner will have access to another client in the next step. Therefore,
+there will not be much difference in future reward between choosing
+a visitor and a resident, and cleaners will not develop a preference for the
+visitor in these conditions. On the other hand, the effect of negative reward
+would be opposite as in a full station, cleaners will get more often the
 heterotypic (resident-visitor) option and will develop a preference for
@@
 efficiently. Overall, estimation of future reward is then the cognitive
-mechanism that allows cleaners to adaptively respond conditions to the
+mechanism that allows cleaners to adaptively respond to the
 ecological conditions of the biological market.
 
-The cognitive mechanism that our analysis highlights does not require a
-direct flow of information between the cleaner and its social
-environment. The adaptive responses to local conditions in cleaners is
-not only evidenced by their performance in experiments, but also by
-changes in their brain anatomy. Indeed, individual cleaners that
-performed in the laboratory test according to what is best at the
-location in which they were caught had larger forebrains harbouring more
-cells than individuals whose performance mismatched locally optimal
-decision-rules \citep{triki_Brain_2020}. This suggests that despite the
-overall behavioural adjustment, evidenced here and elsewhere
-\citep{triki_Biological_2019, triki_Decrease_2018}, there are some
-cleaners better than others at adjusting their behaviour. Triki \emph{et al.}
-\citep{triki_Brain_2020} refer to these as socially competent cleaners. Social
-competence refers to the ability to optimise social behaviour depending
-on the available social information \citep{taborsky_Social_2012a, bshary_Cooperation_2015}. However, we have shown here that cleaners
-are able to adjust their preference according to the social environment
-without using any direct information about the social environment.
-Instead cleaners seem to adjust their preference using information from
-the visitation patterns of their clients. These patters are of course
-determined by the feedback with the cleaner's social environment
-(relative abundance). Our models, however, do not include the
-possibility of cleaners responding to their relative abundance directly.
-The mechanism we present is a general way to learn from the environment
-in both asocial and social situations. It would be interesting to
-contrast this learning mechanism with one tailored to a social
-situation, and see whether such mechanism fits the data better. More
-generally, an important challenge ahead is to understand which cognitive
-mechanisms evolved exclusively for social life.
+Our results support chaining as the more plausible mechanism behind the
+inter-specific variation in cleaners' performance, which is also
+the mechanism that allows them to respond more adaptively. This could
+suggest chaining to be under positive selection. In the standard ephemeral
+reward task, however, food amount and quality are equal between the
+two plates. An given that models resemble this, choosing visitors over
+residents in low cleaner abundances does not diminish the
+amount of food/reward in the the models.
+On the other hand, a cleaner committed to visitors might find more difficult
+to include in the decision making other variables, like parasite load
+and/or mucus quality, that do predict the amount of food in the field
+\citep{roche_Client_2021}. In nature and in laboratory experiments, cleaners prefer
+higher quality mucus and more food in the absence of market effects
+(i.e.~in simultaneous 2-choice options,
+\citep{triki_Fluctuations_2019, grutter_Cleaner_2004}), and they use size as a
+proxy for food availability \citep{wismer_Cuebased_2019, grutter_Does_2005}.
+How important this limitation is will determine whether chaining yields a higher
+fitness for cleaners.
 
-One potential difference between cleaners that adjusted adaptively, like
-the ones reported in Triki \emph{et al.} \citep{triki_Brain_2020}, is configurational learning or
-chunking. The original analysis of the learning model showed that agents
-needed two mechanism to solve the market task; to account for the
-future, and to assign value to the combination of clients present in the
-station \citep{quinones_Reinforcement_2019}. The latter is referred to as
-configurational learning or chunking \citep{sutherland_Configural_1989, miller_Magical_1956}. Theoretical models suggest that the lack of
-configurational learning is related to a low frequency with which
-stimuli are encountered together \citep{kolodny_Evolution_2014, prat_Role_2021}. Thus, cleaner relative abundance could be related to
-this mechanisms as well. Given that the lack of either of these two
-mechanisms yields neutral preferences \citep{quinones_Reinforcement_2019},
-we can't, based on the current analysis, distinguish between the two
-possibilities. One potential way to distinguish between the two would be
-to use an experimental set up designed to test configuration learning on
-cleaners with high and low performance in the market task
-\citep{woodbury_Learning_1943, sutherland_Configural_1989}.
+Individual cleaners that performed in the laboratory test according to what
+is best at their site of capture (low performance when living at low densities,
+high performance when living at high densities) had larger forebrains
+harbouring more cells than individuals whose performance mismatched locally
+optimal decision-rules \citep{triki_Brain_2020}. Triki \emph{et al.} refer to the
+former as socially competent cleaners. Social competence refers to the
+ability to optimise social behaviour depending on the available social
+information \citep{taborsky_Social_2012a, bshary_Cooperation_2015, varela_Correlated_2020}. Our analyses yielded no
+evidence that the difference in social competence with respect to the local
+market conditions and associated brain morphology are due to the mechanism
+used to incorporate future consequences. It could have been conceivable that
+high performing individuals from low-density sites might use negative
+reinforcement instead of chaining, but in that case negative reinforcement
+should have explained part of the data. Configurational learning or
+chunking \citep{sutherland_Configural_1989, miller_Magical_1956}, the second component
+necessary to solve the ephemeral reward task \citep{quinones_Reinforcement_2019}, was
+not varied in the models analized here. However, while chunking tendencies
+should vary to allow individuals to adapt to local conditions
+\citep{prat_Modelling_2022, kolodny_Evolution_2014}, systematic differences
+in individual chunking tendencies would not explain how socially
+competent decisions vary as a function of relative abundance.
+Therefore, it remains currently unclear what cell-demanding
+mechanisms may cause variation in social competence that
+translates into site-specific variation in performance in the
+ephemeral reward task.
 
-Combining mechanistic modelling with empirical data provides a powerful
-tool to identify the cognitive processes underlying learning in animals.
-The combination overcomes the limitations of the general philosophy in
-animal cognition to apply the logic of Lloyd Morgen's canon (Occam's
-razor). Excluding basic reinforcement learning explanations (operant
-and/or classical conditioning) as a potential explanation in experiments
+The model is inspired by the general processes of associative learning
+where short term rewards are translated to decision making; thus, it
+ignores alternative channels of information that could be relevant in
+market-like situations. For example, the model does not investigate whether
+cleaners actually assess the frequency of client visits or a mean frequency
+of visitors leaving. The updating learning mechanism for the development
+of preferences works on a trial by trial basis. In the model, cleaners
+do not need to assess the actual state of the market, \emph{i.e.} their density,
+the density of residents and visitors, and client visitation rate as an
+indicator of demand. They only need to assess short-term consequences of
+own decisions on food intake and chain them. Also, for the sake of
+simplicity, the model ignores the process by which cleaners discriminate
+residents and visitor clients. A model that accounts for this discrimination
+probably involves the development of preferences for morphological or
+behavioural features that are statistically associated with visitors
+or residents. For example, visitors are on average larger larger
+than residents \citep{bshary_Cleaner_2001a}, and are less likely to chase
+cleaners in response to the latter cheating by taking a bite of
+mucus \citep{bshary_Asymmetric_2002}. Given these associations, chaining might
+produce the decision-rule ``chose the larger client and/or less aggressive
+client'', which does not help in the standard ephemeral reward task.
+
+In conclusion, our study shows that variation in cognitive performance as
+a function of ecological factors may set the stage for the use of
+mechanistic modelling to identify the cognitive processes underlying
+learning in animals. The combination overcomes the limitations
+of the general philosophy in animal cognition to apply the logic of
+Lloyd Morgen's canon (Occam's razor). Excluding basic
+reinforcement learning explanations (operant and/or classical conditioning)
+as a potential explanation in experiments
 often warrants animals solving the task on the first possible occasion.
@@
 Dots show the frequency of visitor choices for the 12 locations, as well as the corresponding relative cleaner abundance (x axis) and frequency of visitors leaving the station (y axis).
-Right-hand side panel: scatter plot of the observed and predicted probabilities of choosing a visitor for 12 locations.
-Line correspond to a perfect match between observed and predicted probabilities.}\label{fig:nogamma}
+Right-hand side panel: Right-hand side panels: Variation of the predicted probabilites  of choosing a visitor and their observed values for 12 locations.
+Circles show the mean prediction for each location from 100 samples taking from the posterior distribution.
+Thick and thin bars show the 66 and 95\% credible interval taken from those posterior samples.
+Squares show the predictions used for panel on the righ-hand side.
+Colour denotes different locations (see Empirical data section).
+Black line correspond to a perfect match between observed and predicted probabilities.}\label{fig:nogamma}
 \end{figure}

### 2022-02-03 manuscript_1.0/manuscript_word.Rmd
Edit's related to Redouan's comments

@@
 spacing: double
-abstract: "While it is generally straightforward to quantify individual performance
-  in cognitive experiments, identifying the underlying cognitive processes remains
-  a major challenge. Often, different mechanistic underpinnings may yield similar
-  performances, and Lloyd Morgan’s cannon warrants acceptance of the simpler explanation.
-  Alternatively, when the different mechanisms interact with environmental conditions,
-  variation in performance across environments might allow to statistically infer
-  the mechanism responsible. However, to do this it is necessary to have quantitative
-  predictions for the different candidate mechanisms. Here, we use a set of computational
-  models to get quantitative predictions from alternative learning mechanisms, and
-  using Bayesian statistics fit the model parameters to performance data. We used
-  experimental data on performance in an ephemeral reward task by wild-caught cleaner
-  fish Labroides dimidiatus, as well as cleaner and client fish densities from the
-  locations of capture. The task can in principle be solved by estimating future consequences
-  of an action, or by perceiving the removal of the ephemeral reward as psychological
-  punishment (negative reinforcement). We found that a model where cleaners only estimate
-  the future consequences of their actions explains best which cleaner relative abundances
-  cause the fish to develop a preference for an ephemeral food source. This model
-  also yields performances that can be considered the result of locally optimal decision-rules,
-  in contrast to the negative reinforcement model.  We argue that the combination
-  of computational models with data is a powerful tool to infer the mechanistic underpinning
-  behind cognitive performance. \n"
+abstract: |
+  While it is generally straightforward to quantify individual performance in cognitive experiments, identifying the underlying cognitive processes remains a major challenge.
+Often, different mechanistic underpinnings may yield similar performances, and Lloyd Morgan’s cannon warrants acceptance of the simpler explanation.
+Alternatively, when the different mechanisms interact with environmental conditions, variation in performance across environments might allow to statistically infer the mechanism responsible.
+However, to do this it is necessary to have quantitative predictions for the different candidate mechanisms.
+Here, we use a set of computational models to get quantitative predictions from alternative learning mechanisms, and using Bayesian statistics fit the model parameters to performance data.
+We used experimental data on performance in an ephemeral reward task by wild-caught cleaner fish *Labroides dimidiatus*, as well as cleaner and client fish densities from the locations of capture.
+The task can in principle be solved by estimating future consequences of an action, or by perceiving the removal of the ephemeral reward as psychological punishment (negative reinforcement).
+We found that a model where cleaners only estimate the future consequences of their actions explains best which cleaner relative abundances cause the fish to develop a preference for an ephemeral food source.
+This model also yields performances that can be considered the result of locally optimal decision-rules, in contrast to the negative reinforcement model.
+We argue that the combination of computational models with data is a powerful tool to infer the mechanistic underpinning behind cognitive performance.
 keywords: learning, behaviour, cleaners, bayesian statisitics
@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = FALSE,warning = FALSE,message=FALSE)
+knitr::opts_chunk$set(echo = FALSE,warning = FALSE,message=FALSE,cache=TRUE)
 library(here)
@@
 depend on the abundance of the species involved, certainly vary in time 
-and space within ecological time scales. Therefore, natural selection should 
+and space. Therefore, natural selection should 
 favour the ability to flexibly adjust decisions and behavioural output to 
 current market conditions. Indeed, such adjustments have been repeatedly 
-documented [@axen_signalling_1996]. In animals, an obvious general candidate 
+documented [@axen_Signalling_1996]. In animals, an obvious general candidate 
 mechanism for the strategic adjustment is the cognitive machinery. However, 
@@
 larger than residents [ @bshary_Cleaner_2001a], and size is positively
-correlated with parasite load [@grutter_Relationship_1995a]. However, 
+correlated with parasite load [@grutter_Relationship_1995]. However, 
 early laboratory experiments showed that leaving causes service 
@@
 Recent research on the cognitive tool kit needed to solve an ephemeral 
-reward task has used a broad approach as proposed by @shettleworth_Cognition_2009, 
-who defined cognition as includes all ways in which animals take in information 
+reward task has used a broad approach as proposed by Shettleworth 
+[@shettleworth_Cognition_2009], 
+who defined cognition as including all ways in which animals take in information 
 through the senses, process, retain and decide to act on it. Indeed, perception 
@@
 for the same stimulus has been termed configurational learning, 
-or chunking, or segmentation (see references in @prat_Modelling_2022).
+or chunking, or segmentation (see references in [@prat_Modelling_2022]).
 
@@
 the future consequences of current decisions. In the model by 
-Quiñones et al. @quinones_Reinforcement_2019, this could be achieved in 
+Quiñones *et al.* [@quinones_Reinforcement_2019], this could be achieved in 
 two non-mutually exclusive ways: through low temporal discounting of 

### 2022-02-03 manFigures.R

@@ -197,7 +197,7 @@ rsqr.gam.McFadden<-1-predictDataMode.gam[,sum(log.like)]/
 rsqr.Nrew.McFadden<-1-predictDataMode.Nrew[,sum(log.like)]/
   sum(dbinom(x=predictDataMode.Nrew[,visitorChoices],size = 20,prob = 0.5,log = TRUE))
 
-axislabSize<-10
+axislabSize<-8
 axisSize<-12
 # Panel full model contour
 cont.obs.pred.both<- ggplot(data = FIAinterpData.both,aes(x=rel.abund.cleaners,y=prob.Vis.Leav,
@@ -207,7 +207,7 @@ cont.obs.pred.both<- ggplot(data = FIAinterpData.both,aes(x=rel.abund.cleaners,y
   geom_point(data = fieldatabyLoc.both,aes(fill=market_binomial_data),size=5,
              shape=21,color="black")+sc+xlab("")+
   ylab("Probability of visitor leaving")+
-  labs(fill="Probability \n of choosing \n a visitor")+
+  labs(fill="")+#Probability \n of choosing \n a visitor
   theme(legend.position ="top",
         axis.text = element_text(size=axisSize),
         axis.title.x = element_text(size=axislabSize),
@@ -217,17 +217,20 @@ cont.obs.pred.both<- ggplot(data = FIAinterpData.both,aes(x=rel.abund.cleaners,y
 scatter.obs.pred.both<-ggplot(data=fieldatabyLocSamps.both,
                               aes(y=probVisi.data,colour=site_year,x=probvisitor.pred))+
   stat_gradientinterval(aes(slab_alpha=F),point_interval = mode_hdi,point_size=2)+
-  geom_abline(slope=1)+ylab("Observed")+xlab("Predicted")+
+  geom_abline(slope=1)+ylab("Observed")+xlab("")+
   geom_point(data = fieldatabyLoc.both,aes(y=market_binomial_data,x=probvisitor.pred),
              shape=15,size=2)+
   ylim(0.45,0.85)+xlim(0.45,0.85)+
-  guides(color=guide_legend(title="Location"))+
+  guides(color=guide_legend(title=""))+
   scale_color_manual(values = multDiscrPallet[1:12])+
-  theme_classic()+theme(legend.position ="none",#c(.9, .4),
+  theme_classic()+theme(legend.position ="top",#c(.9, .4),
         axis.text = element_text(size=axisSize),
         axis.title.x = element_text(size=axislabSize),
[…]

### 2022-02-09 manuscript_1.0/manuscript_1.0.Rmd
Changes addressing Zegni's comment in the ms

@@
   While it is generally straightforward to quantify individual performance in cognitive experiments, identifying the underlying cognitive processes remains a major challenge.
-Often, different mechanistic underpinnings may yield similar performances, and Lloyd Morgan’s cannon warrants acceptance of the simpler explanation.
+Often, different mechanistic underpinnings yield similar performances, and Lloyd Morgan’s cannon warrants acceptance of the simpler explanation.
 Alternatively, when the different mechanisms interact with environmental conditions, variation in performance across environments might allow to statistically infer the mechanism responsible.
@@
 
-Cooperation among individuals of the same or different species is
-ubiquitous in nature. Whenever such interactions involve some degree 
-of partner choice, biological market theory predicts that the exchange 
-rate of goods and/or services traded adjusts to the law of supply and demand 
-[@noe_Biological_1995a]. While biological market models have largely focused 
-on evolutionary time scales [@noe_Biological_1994a;@johnstone_Mutualism_2008a] 
-$\color{red}{\text{Hoekstra xxxx}}$, supply and demand conditions, which typically 
+Disentangling the mechanistic underpinnings of behaviour 
+is typically done under controlled conditions in a laboratory setting. However, 
+controlled laboratory conditions often mask the inter and intra-specific 
+variation that arises in the interaction between mechanisms and 
+environmental variation. From a evolutionary perspective, mechanisms 
+are likely selected because of how they allow individuals to respond to 
+environmental variation. For example, biological market theory predicts that 
+the exchange rate of goods and/or services traded between cooperative 
+partners adjusts to the law of supply and demand, when individuals have 
+some degree of partner choice [@noe_Biological_1995a]. 
+Supply and demand conditions, which typically 
 depend on the abundance of the species involved, certainly vary in time 
@@
 it is not clear which cognitive mechanisms allow individuals to adjust their 
-behaviour to the varying market conditions. As adjustments to changes in 
+behaviour to the varying conditions. As adjustments to changes in 
 market conditions have been documented in a great variety of species with 
@@
 cleaning mutualism involving the cleaner fish *Labroides dimidiatus* and
-'client' fish. Clients offer themselves as food patches for cleaners to
-remove ectoparasites, which gives the cleaners calories and the clients
-improved health [@waldie_LongTerm_2011;
-@ros_Does_2011;@triki_Effects_2016]. As cleaners have about 2000
-interactions per day [@grutter_Relationship_1995], they regularly face
-the situation that two clients seek cleaning simultaneously. In such
-conditions, it is important to distinguish between 'resident' and
-'visitor' client species [@bshary_Cleaner_2001a]. The residents have
-small home ranges and hence access to only the local cleaner, while the
-visitors have large home ranges and hence access to two or more
-cleaners. Thus, visitors have the option to switch to another cleaner if
-being made to wait, while residents must wait for inspection. Indeed,
-visitors have been observed to use their partner choice options in that
+'client' fish. Client fish seek cleaner fish services at their territory 
+(so-called “cleaning station”) and offer themselves as food patches 
+to get their ectoparasites removed, which provides cleaners 
+with food and clients with improved health [@waldie_LongTerm_2011;
+@ros_Does_2011;@triki_Effects_2016;@demaire_Reduced_2020]. 
+Given the capacity of some client fish to swim larger distances and 
+access multiple cleaning stations while others access the only cleaning 
+station at their territory, it is crucial to categorize clients as 
+either “visitors” or “residents”, respectively. During cleaning interactions, 
+a cleaner fish often face a choice between a visitor and a resident client 
+seeking its cleaning services simultaneously. Visitors have the option 
+to switch to another cleaner fish if being made to wait, while residents 
+must wait for inspection. Indeed,
+visitors have been observed to use their partner choice option in that
 way [@bshary_Choosy_2002], which may explain why cleaners give
 visitors service priority in a field study in the Red Sea
-[@bshary_Cleaner_2001a]. More generally, cleaners apparently prefer to
-interact with visitors [@triki_Marine_2021]. Such a preference may be
-linked to a client's value as a food patch; visitors are on average
-larger than residents [ @bshary_Cleaner_2001a], and size is positively
-correlated with parasite load [@grutter_Relationship_1995]. However, 
-early laboratory experiments showed that leaving causes service 
-priority independent of client value [@bshary_Asymmetric_2002]. 
-The experiments consisted of asimultaneous two-choice task, 
-where cleaners had to decide which of two
-Plexiglas plates, which offered equal amounts of food, to approach first
-and eat mashed prawn of it. One plate was made to behave like a
-resident, i.e. it would remain until the cleaner had eaten off it. The
-other plate was made to behave like a visitor, i.e. it would be removed
-if not inspected first. Cleaners learned to prefer the visitor plate and
+[@bshary_Cleaner_2001a].
+
+When researchers aimed at testing wild-caught cleaner fish, as 
+well as individuals from other species, abilities 
+to prioritize visitor over resident clients in a lab-based paradigm, 
+they used Plexiglas plates of different colours and shapes offering same 
+amount of food as surrogates for visitor and resident clients.
+One plate is made to behave like a resident, i.e. it remains until 
+the cleaner had eaten off it. The other plate was made to behave 
+like a visitor, i.e. it is removed if not inspected first.
+Cleaners learned to prefer the visitor plate and
 hence obtained the double amount of food [@bshary_Asymmetric_2002].
-Adult cleaner fish outperform various primates as well as rats and
+Furthermore, adult cleaner fish outperformed various primates as well as rats and
 pigeons in this original version of the biological market task
-[@salwiczek_Adult_2012; @zentall_Early_2017]; only African grey
-parrots solve this task as well [@pepperberg_Can_2014]. As the correct 
-solution must be learned, and primates are known to readily distinguish 
+[@salwiczek_Adult_2012; @zentall_Early_2017]; yet the African grey
+parrots solve this task as well [@pepperberg_Can_2014]. Given that primates 
+are known to readily distinguish 
 between one and two reward units if presented in more conventional ways 
-$\color{red}{\text{ref}}$, what makes the task difficult for most non-cleaners?
+$\color{red}{\text{ref}}$, this raises the question:
+what makes the task difficult for most non-cleaners?
 
-Recent research on the cognitive tool kit needed to solve an ephemeral 
+Recent research on the cognitive tool kit needed to solve the ephemeral 
 reward task has used a broad approach as proposed by Shettleworth 
-[@shettleworth_Cognition_2009], 
-who defined cognition as including all ways in which animals take in information 
-through the senses, process, retain and decide to act on it. Indeed, perception 
-of relevant cues is of major importance for individual performance; 
-i.e. what relevant information is encoded in the design of the two 
-plates (colour versus size; [@wismer_Cuebased_2019]), or whether 
-the information is in the colour of
-the food [@pretot_Comparative_2021; @pretot_Comparing_2016], and
-whether the food is visible or hidden/released only when the subjects
-made choices on a touch screen [@pretot_Factors_2016]. However, identifying 
+[@shettleworth_Cognition_2009], who defined cognition as including 
+all ways in which animals acquire information 
+through the senses, process, retain and decide to act on it. 
+Indeed, perception of relevant cues is of major importance 
+for individual performance. For example, some animals find relevant 
+information in the plates 
+ [@wismer_Cuebased_2019] while others find it in the food 
+[@pretot_Comparative_2021; @pretot_Comparing_2016]. However, identifying 
 cues as salient is not the only challenge of the ephemeral reward task, 
@@
 reward task, learning models showed that basic reinforcement learning does 
-not suffice to solve the task [@prat_Modelling_2022; @quinones_Reinforcement_2019]. 
+not suffice to solve the ephemeral reward task [@prat_Modelling_2022;
+@quinones_Reinforcement_2019]. 
 This is particularly so when models assume the more complex natural 
-situation in which cleaners not only face resident-visitor pairs but also 
-visitor-visitor and resident-resident pairs, as well only a resident or 
-only a visitor. To be able to give visitors priority over residents, 
+situation in which cleaner fish not only face resident-visitor pairs but also 
+visitor-visitor and resident-resident pairs, as well a resident alone or 
+a visitor alone. To be able to give visitors priority over residents, 
 cleaners need to be able to assess a client’s value separately for the 
-three possible forms of encounter (alone, paired with a fish with the 
+three possible scenarios (alone, paired with a fish with the 
 same strategic option, paired with a fish with the alternative strategic option) 
-[@quinones_Reinforcement_2019]. The ability to keep such separate scores 
-for the same stimulus has been termed configurational learning, 
-or chunking, or segmentation (see references in [@prat_Modelling_2022]).
+[@quinones_Reinforcement_2019]. The ability to distinguish and value differently
+one stimulus alone from compound versions of it has been termed 
+configurational learning, or chunking, 
+or segmentation (see references in [@prat_Modelling_2022]).
 
-To solve the ephemeral reward task, cleaners also need to account for 
+To solve the ephemeral reward task, cleaners need to account for 
 the future consequences of current decisions. In the model by 
@@
 through perceiving a visitor client leaving as psychological punishment 
-(i.e. as a negative reinforcer). Given that a negative reinforcer is part 
-of the ubiquitous learning mechanism termed operant conditioning 
-[@thorndike_Animal_1898; @skinner_Behavior_1938], this explanation 
-could be considered the simpler one. Furthermore, accounting for the 
-future effects of an action is considered an advanced cognitive 
-ability [@suddendorf_Evolution_2007]. Thus, standard logic of 
+(i.e. as a negative reinforcer). Low temporal discounting is when 
+individuals include in their valuation of an action the reward effects 
+that this will have in the future. This is done by combining in a single 
+valuation the reward obtained in the current time with all the reward that 
+comes after, discounting for how far in the future reward 
+is accrued. 'Chaining' the reward of these different time steps allows 
+individuals to take actions that increase the long-term reward at the sacrifice
+of short term considerations [@enquist_Power_2016]. Even though, 'chaining' 
+can be readily implemented computationally in learning models 
+[@enquist_Power_2016;@sutton_Reinforcement_2018], cognitively it seems to be 
+a complex adaptation [@suddendorf_Evolution_2007]. On the other hand,
+using client behaviour as a negative reinforcer is in principle 
+easier to implement. Negative reinforcement is part of the ubiquitous 
+learning mechanism termed operant conditioning [@thorndike_Animal_1898; 
+@skinner_Behavior_1938]. Thus, standard logic of 
 Lloyd Morgan’s cannon demands that operant conditioning as the simpler 
-explanation is to be accepted by default. Here, we explore the 
-possibility that fitting a model in which the action of these two 
-mechanisms, operant conditioning and chaining, depends 
-on model parameters may reveal which process cleaners actually use. 
-This is because one process may be better at predicting the observed 
-variation in cleaner fish performance as a function of ecological conditions.
+explanation is to be accepted by default. Ideally, the two mechanisms should 
+be evaluated in light of how well they explain the available data.
 
-Various repetitions of the ephemeral reward task in different years and 
-with cleaners caught from various locations around Lizard Island, 
-Great Barrier Reef, revealed that cleaner and client densities in 
-nature affect how cleaners perform in the original market task: 
-when relative densities are low, cleaners are more likely to fail to 
-complete the task [@triki_Biological_2019;
+Over the last decade, our team tested over a hundred of wild-caught 
+cleaner fish in the exact same paradigm of  of the ephemeral reward 
+task [@salwiczek_Adult_2012;@wismer_Variation_2014;@triki_Decrease_2018;
+@triki_Biological_2019;@triki_Brain_2020]. These fish often come from 
+different reef locations around the study field site at Lizard Island, 
+Great Barrier Reef in Australia. Further investigation of the local 
+eco-sociological conditions revealed that cleaner and client 
+fish population densities have a substantial impact on cleaner fish 
+performance in the task. Cleaner fish from reef sites with relatively 
+low densities were more likely to fail at solving the task [@triki_Biological_2019;
 @triki_Decrease_2018; @wismer_Variation_2014]. The explanation for this pattern
-is twofold. First, low cleaner abundances implies low supply and high demand 
-of cleaning services. Under this conditions, there will be less occasions under 
+is twofold. First, low cleaner fish population densities imply 
+low supply and high demand for cleaning services. 
+Under such conditions, there are fewer occasions under 
 which failing to give priority to a visitor translates to an empty 
-cleaning station. Secondly and also related to the state of the cleaning market,
-visitor clients are less likely to exert their choice options 
-(and hence wait for inspection if made to wait) when
-cleaner fish densities are low [@triki_Brain_2020]. If visitors are not choosy, 
-cleaners should not give them priority anymore. Thus, the underling 
-cognitive machinery and ecological variables apparently interact to produce 
-such variable performance. By fitting our model to the empirical data on 
-fish densities and cleaner fish performance in the ephemeral reward task 
-we aimed to address two questions. First, we aimed to determine the likely 
-mechanism used by cleaners to incorporate future consequences of current 
+cleaning station. Second and also related to the state of the cleaning market,
+visitor clients at low cleaner fish population densities 
+are less likely to exert their partner choice options 
+and are hence more likely to wait for inspection if not given cleaning 
+priority [@triki_Brain_2020]. In the absence of partner choice 
+cleaners should not give priority to visitors any more.
+
+The interplay between the underling cognitive machinery and 
+local ecological conditions apparently generate the documented variable 
+performance among individuals of the same species. 
+Our approach of fitting the computational model to the empirical data on 
+fish densities and cleaner fish censuses and performance
+in the ephemeral reward task aimed at: (i), determining which 
+mechanism cleaner fish use to incorporate future consequences of current 
 decisions by testing whether operant conditioning, chaining, or a combination 
-of both best explains performance. Second and related to the first 
-question, we aimed to determine whether the two mechanisms differed 
-with respect to the ecological conditions that are likely to cause high 
-versus low performance in the ephemeral reward task. If that were the case, 
-we would assess which mechanism would yield more appropriate performance 
-patterns. Relying on the logic of biological market theory, we predicted 
-that appropriate performance is to show low preference for visitors under high
-local client-to-cleaner ratio as visitor leaving rates should be low 
-and any leaving visitor will be readily replaced by another client. In contrast, 
-cleaners should show high performance if the local client-to-cleaner 
-ratio favours clients.
+of both best explains their performance; (ii)  determining whether the 
+two mechanisms differed with respect to the ecological conditions 
+that are likely to cause high versus low performance in the 
+ephemeral reward task. Additionally, we assessed which mechanism 
+yields optimal performance patterns. Relying on the logic of 
+biological market theory, we predicted 
+that appropriate performance is to show low preference for visitors under low
+local cleaner-to-client ratio. 
+<!-- In this case, as visitor leaving rates  -->
+<!-- should be low as well and any leaving visitor will be readily  -->
+<!-- replaced by another client in the queue. In contrast,  -->
+<!-- cleaners should show high performance in the ephemeral reward task -->
+<!-- if the local cleaner-to-client ratio favours clients.  -->
 
@@
 
-To test the relative validity of chaining versus negative reinforcement as 
-mechanisms to account for future consequences of current choices, 
-we combined empirical data from Triki *et. al* 
-[@triki_Biological_2019;@triki_Brain_2020]. with the computational 
-model analysed in Quiñones *et al.*[@quinones_Reinforcement_2019]. In order to 
-compare the explanatory power of the different hypothesis, we estimate the 
-parameter values of three versions of the model that best fit the data. 
-Particularly, we fit the parameter that determines how important 
-future rewards are ($\gamma$), the magnitude of the negative reward 
-($\eta$) and a scaling constant that translates absolute to relative 
-abundances (see following sections for details). We obtained model 
-predictions using a set of stochastic individual-based
-simulations. Thus, each parameter combination of the model yields not one 
-prediction for the data set, but a distribution of them. Thus, for the 
-fitting procedure, we use one of the most common algorithms in bayesian inference,
-the Markov Chain Monte Carlo (MCMC). MCMC is a stochastic algorithm that allows
+In this study, we combined empirical data from Triki *et. al* 
+[@triki_Biological_2019;@triki_Brain_2020] and the computational 
+model analysed in Quiñones *et al.*[@quinones_Reinforcement_2019] 
+to test the relative validity of chaining versus operant conditioning as 
+mechanisms to account for future consequences of cleaner fish desicion-making.
+In order to compare the explanatory power of the different hypotheses, 
+we estimated the parameter values of three versions of 
+the model that best fit the empirical data. 
+Particularly, we fitted the parameter that determines how important 
+future reward is ($\gamma$), the magnitude of the negative reward 
+($\eta$) and a scaling constant that translates cleaner fish absolute 
+to relative population abundances (see following sections for details). 
+We obtained the model predictions using a set of stochastic individual-based
+simulations. Thus, each parameter combination of the model yielded not one 
+but a distribution of predictions. For the 
+fitting procedure, we used the bayesian inference algorithm: 
+Markov Chain Monte Carlo (MCMC). MCMC is a stochastic algorithm that allows
 to sample from the posterior distribution of model parameter values. The posterior
@@
 
-The model consist of a set individual-based simulations where
-individuals face a series of choices between two options. Individuals in
-the model represent cleaners, and the options they face simulate the
-natural conditions of a cleaning market. Cleaners experience a series 
-of discrete time points in which they face different ‘states’, which 
-are defined by the number and type of clients inviting for service. 
-There are six possible states: zero clients, one resident, one visitor, 
-two residents, two visitors, and a mix of one resident and one visitor. 
+The model consists of a set individual-based simulations where
+individuals, representing cleaners, face a series of choices 
+between two options, which simulate the natural conditions 
+of the cleaning market. Individuals experience a series 
+of discrete time points in which they face different ‘states’, 
+defined by the number and category of client fish (visitor or residents) 
+inviting for cleaning services. There are six possible states: 
+zero clients, one resident, one visitor, 
+resident-resident, visitor-visitor, and resident-visitor. 
 The probability of each state is largely determined by the relative 
-abundance of cleaners, residents and visitors, but to some degree by a 
-cleaner’s choices when it faces the resident-visitor combination. 
-This is because residents are those clients that stay in the
-cleaning queue when they are not given priority and hence would 
-still be available in the next time point; while visitors leave
-the queue (with a certain probability) after they are not given
-priority. Individuals obtain a fixed reward from cleaning a client
-regardless of the type. Every time individuals face and make a choice
+abundance of cleaner fish, residents and visitors, but to some degree by
+cleaner fish choices when it faces the resident-visitor combination. 
+This is because residents are willing to queue for cleaning service; 
+while visitors leave the queue (with a certain probability) when made to wait. 
+Individuals obtain a fixed reward from cleaning a client fish
+regardless of the category. Every time individuals face and make a choice
 they update the probability of making that same choice. The update is
-based on the difference between the expectation of reward and the actual
-reward the individual obtains (prediction error)
-[@sutton_Reinforcement_2018; @rescorla_Theory_1972]; and it is carried
-in the direction that would lead to more reward being obtained, given
+based on the difference between the expected reward and the obtained
+reward (prediction error) [@sutton_Reinforcement_2018; 
+@rescorla_Theory_1972]. Given the new information, the update is carried
+in the direction that leads to more reward being obtained, given
 the new information. In the long run, the probability of choosing a visitor 
@@
 will converge depends on the relative abundance of cleaners, visitors 
-and resident; as well as on the probability of visitors leaving the station
-when unattended. Further details of the model implementation can be
-found in the paper [@quinones_Reinforcement_2019].
+and resident; as well as on the probability of visitors leaving the 
+cleaning station when made to wait. Further details of the model 
+implementation can be found in Quiñones *et al* [@quinones_Reinforcement_2019].
 
-The model shows that only agents that calculate rewards separately for 
-the different states (termed ‘fully aware agents’) can potentially 
-prioritise visitors of residents in nature, and hence also solve the 
-ephemeral reward task. This is because pooling rewards for the two 
-clients from all states by ‘partially aware agents’ 
-(that only recognize the two clients as different) cancels out 
-all differences (see [@quinones_Reinforcement_2019]). However, 
-such *chunking* by fully aware agents is not enough to develop a 
-preference for visitors. In addition, agents need to find a mean 
+The model shows that agents need to find a mean 
 to incorporate future consequences of current choices. In the model, 
@@
 Second, $\eta$ measures how much individuals include in their reward the
-fleeing behaviour of visitor clients as a negative component. Both of
+fleeing behaviour of visitor as a negative component. Both of
 these parameters allow individuals to use in their estimates the future
@@
 
-A further model analysis contrast the effect of these two 
-parameters against variation in the relative abundance of cleaners 
-and the two client types. Assuming certainty that visitors leave, the 
-two parameters yield different 
-predictions when relative client abundance is very high. Under such 
-conditions, the analysis shows that under very high client (relative) 
-abundance the presence of future rewards ($\gamma>0$) no longer favours 
-the preference for the ephemeral clients, while the preference persists 
-when the negative reward mediated by client behaviour ($\eta>0$) is 
-included. Thus, the analysis suggests that future reward as an 
-explanation for cleaner ability to prefer visitors is supported. 
-At first sight, empirical data seem to support future rewards as 
-the mechanism used by cleaners, as the statistical analysis  by 
-Triki *et al.* [@triki_Biological_2019] data revealed that low 
-cleaner-to-client ratios predict low preference for visitors and hence 
-low performance in the ephemeral reward task. However, low cleaner-to-client 
-ratios may also lead to low probabilities of visitors leaving, which would 
-cause low preferences for visitors independently of the underlying 
-mechanism [@quinones_Reinforcement_2019]. Furthermore, a combination 
-of future and negative rewards, could still be yield a better explanation 
-for the data than any single factor.
+<!-- A further model analysis contrast the effect of these two  -->
+<!-- parameters against variation in the relative abundance of cleaners  -->
+<!-- and the two client types. Assuming certainty that visitors leave, the  -->
+<!-- two parameters yield different  -->
+<!-- predictions when relative client abundance is very high. Under such  -->
+<!-- conditions, the analysis shows that under very high client (relative)  -->
+<!-- abundance the presence of future rewards ($\gamma>0$) no longer favours  -->
+<!-- the preference for the ephemeral clients, while the preference persists  -->
+<!-- when the negative reward mediated by client behaviour ($\eta>0$) is  -->
+<!-- included. Thus, the analysis suggests that future reward as an  -->
+<!-- explanation for cleaner ability to prefer visitors is supported.  -->
+<!-- At first sight, empirical data seem to support future rewards as  -->
+<!-- the mechanism used by cleaners, as the statistical analysis  by  -->
+<!-- Triki *et al.* [@triki_Biological_2019] data revealed that low  -->
+<!-- cleaner-to-client ratios predict low preference for visitors and hence  -->
+<!-- low performance in the ephemeral reward task. However, low cleaner-to-client  -->
+<!-- ratios may also lead to low probabilities of visitors leaving, which would  -->
+<!-- cause low preferences for visitors independently of the underlying  -->
+<!-- mechanism [@quinones_Reinforcement_2019]. Furthermore, a combination  -->
+<!-- of future and negative rewards, could still be yield a better explanation  -->
+<!-- for the data than any single factor.  -->
 
@@
 
-The empirical data were collected between 2010 and 2018 always during 
-the austral winter months June to August at Lizard Island 
+The empirical data were collected between 2010 and 2019 always during 
+the austral winter months June to August from a total of five 
+study reef sites (Corner Beach-CB, Horseshoe-HS, Mermaid Cove-MC, 
+Northern Horseshoe-NHS, and The Crest-TC)  at Lizard Island 
 ($14.6682° S, 145.4604° E$), Great Barrier Reef, Australia. 
-They consist of three sets: fish densities from a total of five study 
-reef sites (Corner Beach-CB, Horseshoe-HS, 
-Mermaid Cove-MC, Northern Horseshoe-NHS, and The Crest-TC), 
-natural observations of cleaners to quantify the probability 
-of visitors leaving if initially ignored in favour of another client, and the 
-performance of individuals caught from these sites in the ephemeral reward test. 
-In total, we have twelve site/year data sets for fish densities and 
-corresponding performance in the test. Thus, some sites were sampled more 
-than once. Due to major environmental perturbations during the study period 
-($\color{red}{\text{refs}}$), fish densities changed significantly even 
-within sites [@triki_Decrease_2018;@triki_Fluctuations_2019]. To estimate 
-the population density of cleaner fish and their clients at a given site in 
+The data consist of three sets: fish censuses, field 
+observations of cleaner-client interactions to quantify the probability 
+of visitors leaving if made to wait, and the 
+performance of wild-caught cleaner fish in the ephemeral reward test. 
+In total, we have twelve site/year data sets for fish censuses and 
+corresponding performance in the lab test. Thus, some sites were sampled more 
+than once. To estimate the population density of cleaner fish 
+and their clients at a given site in 
 a given year, Triki *et al.* [@triki_Biological_2019] used a series of ten 
@@
 the reef and first counted the visible large-bodied adult fish 
-(species with total length TL > $10cm$) on a width of $5m$, and then on the 
-return individuals of small-bodied fish species (TL < $10 cm$) on a width 
-of $1 m$. We included cleaner fish in the $5 m$ transect. Based on the 
-classification by Bshary [@bshary_Cleaner_2001a] and Wismer *et al.* 
-[@wismer_Variation_2014], all visitor client species ($n = 124$) were 
-large-bodied. Resident clients comprised all small-bodied species 
-($n = 30$) but also some large-bodied ones ($n = 15$). Overall, 
-large-bodied species are highly correlated with being a visitor, 
-and small-bodied species are a good correlate of residents. Based on the 
-transect data, Triki *et al.* [@triki_Biological_2019;@triki_Brain_2020] 
-estimated cleaner fish, small-bodied client, large-bodied client and total 
-client fish densities per $100 m^2$. LASSO analyses revealed that cleaner and
-large-bodied client densities were highly correlated, and only the former 
-was hence kept in the analyses as representative of both [@triki_Biological_2019]. 
-Cleaner densities, in interaction with visitor client leaving probability, 
-explained best individual performance in the ephemeral reward task 
-[@triki_Biological_2019], while cleaner-to-client ratio was not a significant 
-factor. This creates a certain mismatch with the model by Quiñones *et al.* 
-[@quinones_Reinforcement_2019], which focused on abundance of cleaners relative 
-to overall client abundance in order to capture the characteristics 
-of the market. Importantly, relative abundances of clients define not only 
-the probability of interactions with residents and visitors, but also affect 
-how often the cleaning station is empty (e.g. there are no clients to be cleaned). 
-The higher the relative abundance of cleaners is, the higher is the probability 
-of cleaning stations being empty at a given time point. How often the 
-cleaning stations are empty in turns influences the value that cleaners can 
-expect from their choices. The emptier the cleaning stations are, the more 
-beneficial it is to prioritize a client that will not stay. On the other hand, 
-situations where cleaners have to choose will be rare if cleaner relative 
-abundance is high, which reduces the total value of prioritizing visitors 
-over residents and makes it more difficult to learn a preference for visitors. 
-Given the model structure, we used the empirical data to calculate relative 
-abundances of cleaners, residents and visitors for the current analyses. 
-To incorporate the empirical finding that absolute densities matter, we 
-introduced a new scaling constant (see section on model fitting).
+(species with total length $TL \geq 10cm$) including cleaner fish 
+on a width of $5m$, and then on the 
+return individuals of small-bodied fish species ($TL < 10 cm$) \
+on a width of $1 m$
+(see Triki et al. 2018 for further details on fish censuses data collection). 
+We then scaled the counts of cleaner fish, small-bodied, 
+and  large-bodied  clients fish densities per $100 m^2$. 
+From the study by Triki *et al* [@triki_Biological_2019] 
+cleaner fish and large-bodied client populations densities were 
+highly correlated, and only the former 
+was hence used in the analyses as representative of both measures.
 
-To collect data on the visitor clients’ probability of leaving if not serviced 
-immediately, eight cleaners per site/year were each filmed for $30 min$. 
-From the videos, all events in which a visitor client was made to wait in 
-favour of another (visitor or resident) client were identified, and noted 
-whether or not the visitor left [@triki_Biological_2019;@triki_Brain_2020]. 
-A total of 120 cleaners (10 individuals per 12 site/year) were tested in the 
+<!-- Cleaner densities, in interaction with visitor client leaving probability,  -->
+<!-- explained best individual performance in the ephemeral reward task  -->
+<!-- [@triki_Biological_2019], while cleaner-to-client ratio was not a significant  -->
+<!-- factor. This creates a certain mismatch with the model by Quiñones *et al.*  -->
+<!-- [@quinones_Reinforcement_2019], which focused on abundance of cleaners relative  -->
+<!-- to overall client abundance in order to capture the characteristics  -->
+<!-- of the market. Importantly, relative abundances of clients define not only  -->
+<!-- the probability of interactions with residents and visitors, but also affect  -->
+<!-- how often the cleaning station is empty (e.g. there are no clients to be cleaned).  -->
+<!-- The higher the relative abundance of cleaners is, the higher is the probability  -->
+<!-- of cleaning stations being empty at a given time point. How often the  -->
+<!-- cleaning stations are empty in turns influences the value that cleaners can  -->
+<!-- expect from their choices. The emptier the cleaning stations are, the more  -->
+<!-- beneficial it is to prioritize a client that will not stay. On the other hand,  -->
+<!-- situations where cleaners have to choose will be rare if cleaner relative  -->
+<!-- abundance is high, which reduces the total value of prioritizing visitors  -->
+<!-- over residents and makes it more difficult to learn a preference for visitors.  -->
+<!-- Given the model structure, we used the empirical data to calculate relative  -->
+<!-- abundances of cleaners, residents and visitors for the current analyses.  -->
+<!-- To incorporate the empirical finding that absolute densities matter, we  -->
+<!-- introduced a new scaling constant (see section on model fitting).  -->
+
+The field observation data consisted of video recordings/encodings of the 
+cleaner-client cleaning interactions. There were videos from eight 
+cleaners per site/year of a duration of $30 min$ each. Triki *et al* 
+extracted information from every event wherein a visitor client 
+was made to wait in favour of another client (visitor or resident), and noted 
+whether or not the visitor left or queued for the cleaning service
+[@triki_Biological_2019;@triki_Brain_2020].
+
+The cognitive performance data was from a total of 120 cleaners 
+(10 individuals per 12 site/year) tested in the 
 ephemeral reward task [@triki_Biological_2019;@triki_Brain_2020]. Authors 
@@
 (colour and pattern) and the plates’ role (visitor or resident) between the 
-tested fish. The data was originally collected to assess which variables are 
-good predictors of the capacity to solve the ephemeral food task. Thus, previous 
-analysis  use specific statistical criteria to classify individual cleaners'
-performance as successful or failure [@triki_Biological_2019]. Because the model 
-predicts the preference of cleaners given the set of environmental variable, 
-we instead use the raw data of individuals cleaners' decisions.
-We use 20 choices from each cleaner as the preference they develop 
-for the visitor plate. Which these 20 choices were vary for each cleaner depending 
-on the performance that was originally assessed. For cleaners that did not 
-succeed, the 20 choices correspond to the last two sessions. Cleaners that 
-succeeded in solving the task were tested on a reversal task. That is, the 
-pattern in plates was switched to the opposite role they played in the 
-initial test. For those cleaners, we used the last session before they succeeded 
-in the initial, and the last session of the reversal, completing the 20 choices.
-We did not distinguish between individuals that reached the criterion early 
-or late during the 200 trials.
+tested fish. In the original studies, once a fish reach a learning criterion, 
+that is, performing significantly above chance level ($> 50%$, $p-value ≥ 0.05$),
+they passed to a reversal version of the task where the roles of the 
+visitor/resident Plexiglas plates were swapped (see Triki et al. 2019, 2020). 
+Here, we used instead a subset of these data in order to have an idea on 
+cleaner fish preferences for the visitor plate, even if they do not reach 
+the learning criterion within 200 trials. To do so, we first extracted the 
+trial-by-trial outcomes from the last two session (20 trials) of those who 
+never reached the learning criterion for visitor plate 
+$\color{red}{\text{(N = XX cleaner fish)}}$. 
+For those who reached the learning criterion at some point during the 
+test and passed to a reversal phase, we extracted the trials-by-trial 
+outcomes from the last session (10 trials) before passing to reversal 
+and the last 10 trials they were exposed to in the test 
+$\color{red}{\text{(N = XX cleaner fish)}}$.
 
@@
 
-The aim of the analysis is to fit the key model parameters that allow 
-individuals to incorporate future consequences of current actions, 
-$\gamma$ and $\eta$, to the data from Triki *et al.* 
-[@triki_Biological_2019;@triki_Brain_2020] to find out whether each or 
+The aim of the analyses is to fit the key model parameters 
+$\gamma$ and $\eta$, to the empirical data from Triki *et al.* 
+[@triki_Biological_2019;@triki_Brain_2020] to test whether each or 
 a combination of these effects is a better explanation for the pattern 
-seen in the data. In particular, we are interested in the relation between the 
-ecological variables: cleaners, visitor clients, resident clients abundances and
-visitor clients leaving probability; and cleaners' preference for visitor clients
-over residents. Thus, the four ecological variables are given as input to 
-the models. The preference for visitors gotten from the simulations of the model 
-is used as the prediction for the response variable, while the number of visitors 
-chosen out of the 20 choices of each cleaner as the observed response variable. 
+seen in the data. We used the 
+ecological variables: cleaners, visitor clients, 
+resident clients abundances and
+visitor clients leaving probability,  as input to the models. 
+As response variable we used cleaners' preference for visitor 
+over residents in the ephemeral reward task. 
+Finally, we used the preference for visitors resulting from the 
+model simulations as the prediction for the response variable. 
 We kept all other parameter values used for the model simulations constant, 
@@
 
-In order to capture with the model the relationship between the characteristics 
-of the market (environment) and the cleaner’s preference we need to translate 
-the absolute abundances of the data to to a measure of relative abundances 
-that captures client visitation patterns. This is because in the model, relative 
+To capture with the model the relationship between the ecological 
+variables and cleaner fish preferences for visitors we need to scale 
+the absolute population densities of cleaner fish from the empirical data
+to a measure of relative abundances that captures 
+client visitation patterns. This is because in the model, relative 
 abundances of clients define not only the probability of residents and visitors, 
@@
 clients to be cleaned). The frequency with which clients visit the station 
-is another variable, which will likely vary among different client species 
-depending on parasite abundances and loads. We do not have field estimates 
-for species specific parasite loads, especially not as a function of site. 
+is another variable, which in nature may vary among different client species 
+depending on their ectoparasite loads. We do not have field estimates 
+for species-specific parasite loads, especially not as a function of site. 
 In order to control for these aspects, we computed a measure of relative 
-cleaner abundance for each site relative to absolute abundances and multiplied 
+cleaner fish abundance for each reef site relative to 
+absolute abundances and multiplied it
 by a scaling constant that changes the range of the variable. This scaling 
 constant is hence meant to capture variation in the market conditions driven 
-partly by cleaner abundance. We fit the value of the scaling constant as 
-part of the statistical inference. As for the client abundances for 
-residents and visitors we computed a relative measure with respect to the 
+partly by cleaner abundance. We fitted the value of the scaling constant as 
+part of the statistical inference. As for the visitor and resident 
+abundances we computed a relative measure with respect to the 
 total client abundance, and weighted that by the rescaled relative absence 
@@
 for the probability of having different options in the cleaning station. 
-Note that the scaling constant was introduced to control for variation that 
+Note that we introduced the scaling constant to control for variation that 
 is not captured by the model; its parameter distribution does not offer 
@@
 
-Once we calculate the relative abundances, we can obtain predictions from 
-the model for each one of the locations and run the Markov Chain. We start the
-chain with random values for the parameters of interest, then run the 
-computational model once for every location using as input the ecological 
+Once we calculated the relative abundances, we obtained predictions from 
+the model for each one of the locations and ran the Markov Chain. We started the
+chain with random values for the parameters of interest, then ran the 
+computational model once for every reef site using as input the ecological 
 explanatory variables. The model outputs the probability of choosing the visitor
 for each location $p_i$, where $i$ is the index for the 12 locations. Assuming a 
-binomial distribution, the probability that each of the cleaners' 20 choices was 
-generated by the model is given by $\binom{n}{k_ij}p^{k_{ij}}_i (1-p_i)^{n-k_{ij}}$;
-where $k_{ij}$ is the number of times that cleaner $j$ in location $i$ chose the 
-visitor over the resident; and $n=20$ (due to our choice of using 20 
-choices per cleaner). By taking the natural logarithm and summing over all 
-the cleaners and locations we obtain the log-likelihood of the data 
-given the model and parameters. We then propose a new set of parameters drawn 
+binomial distribution, the probability that each of the cleaner fish 20 choices 
+in the ephemeral reward task was generated by the model 
+is given by $\binom{n}{k_ij}p^{k_{ij}}_i (1-p_i)^{n-k_{ij}}$;
+where $k_{ij}$ is the number of times that cleaner fish $j$ in reef site $i$ 
+chose the visitor over the resident; and $n=20$ (due to our choice of using 20 
+choices per cleaner fish). By taking the natural logarithm and summing over all 
+the cleaner fish and reef sites we obtained the log-likelihood of the data 
+given the model and parameters. We then proposed a new set of parameters drawn 
 from a uniform distribution centred around the old parameter set. The amplitude 
@@
 \ref{tab:param}. Subsequently, we ran the model and calculated the likelihood 
-with the new parameter set. We then use the ratio of the two likelihoods to 
+with the new parameter set. We then used the ratio of the two likelihoods to 
 choose which parameter set to keep. New parameter sets with a higher likelihood 
-than the old set replace old ones, and those with a lower likelihood are replace 
+than the old set replaced old ones, and those with a lower likelihood replaced 
 current ones  with a probability equals to the log-likelihood ratio. 
-Given that we only use the likelihoods in the decision, we are using a 
-uninformative prior. Once we decide whether the new parameter set replaces 
-the old one, we ran the model again to sample to the likelihood 
-distribution of the parameter set. We then start 
-the cycle again by proposing a new set of parameters, and repeat the process for 
-$1e^5$ steps. We ran 5 independent chains, discarded the first 
-$100$ samples of each chain as burn in, and after that we keep 1 in every 
-100 samples to avoid autocorrelation. The collection of parameters sets kept in 
-all chains approximates the posterior distribution. The model as well as the 
-fitting algorithm were coded in *c++*, the diagnostics and visualization were 
-coded in R [@rcoreteam_Language_2021] of the  all code can be found at 
+Given that we only used the likelihoods in the decision, we used a 
+uninformative prior. Once we decided whether the new parameter set replaces 
+the old one, we ran the model again to sample the likelihood 
+distribution of the parameter set. We then started 
+the cycle again by proposing a new set of parameters, and repeated
+the process for $1e^5$ steps. We ran 5 independent chains, 
+discarded the first $100$ samples of each chain as burn in, 
+and after that we kept 1 in every 100 samples to avoid autocorrelation. 
+The collection of parameters sets kept in 
+all chains approximates the posterior distribution. We coded the model 
+as well as the fitting algorithm in *c++*, the diagnostics and visualization 
+in R [@rcoreteam_Language_2021]. All codes are accessible at 
 $\color{red}{\text{include citation}}$

### 2022-02-09 manuscript_1.0/manuscript_1.0.tex
Changes addressing Zegni's comment in the ms

@@
 
-% For Pandoc highlighting needs
+% tightlist command for lists without linebreak
+\providecommand{\tightlist}{%
+  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
 
-% Pandoc citation processing
+% From pandoc table feature
+\usepackage{longtable,booktabs,array}
+\usepackage{calc} % for calculating minipage widths
+% Correct order of tables after \paragraph or \subparagraph
+\usepackage{etoolbox}
+\makeatletter
+\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
+\makeatother
+% Allow footnotes in longtable head/foot
+\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
+\makesavenoteenv{longtable}
 
@@
 While it is generally straightforward to quantify individual performance in cognitive experiments, identifying the underlying cognitive processes remains a major challenge.
-Often, different mechanistic underpinnings may yield similar performances, and Lloyd Morgan's cannon warrants acceptance of the simpler explanation.
+Often, different mechanistic underpinnings yield similar performances, and Lloyd Morgan's cannon warrants acceptance of the simpler explanation.
 Alternatively, when the different mechanisms interact with environmental conditions, variation in performance across environments might allow to statistically infer the mechanism responsible.
@@
 
-%% Some pieces required from the pandoc template
-\providecommand{\tightlist}{%
-  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
 \providecommand{\EndFirstPage}{%
@@
 
-Cooperation among individuals of the same or different species is
-ubiquitous in nature. Whenever such interactions involve some degree
-of partner choice, biological market theory predicts that the exchange
-rate of goods and/or services traded adjusts to the law of supply and demand
-\citep{noe_Biological_1995a}. While biological market models have largely focused
-on evolutionary time scales \citep{noe_Biological_1994a, johnstone_Mutualism_2008a}
-\(\color{red}{\text{Hoekstra xxxx}}\), supply and demand conditions, which typically
+Disentangling the mechanistic underpinnings of behaviour
+is typically done under controlled conditions in a laboratory setting. However,
+controlled laboratory conditions often mask the inter and intra-specific
+variation that arises in the interaction between mechanisms and
+environmental variation. From a evolutionary perspective, mechanisms
+are likely selected because of how they allow individuals to respond to
+environmental variation. For example, biological market theory predicts that
+the exchange rate of goods and/or services traded between cooperative
+partners adjusts to the law of supply and demand, when individuals have
+some degree of partner choice \citep{noe_Biological_1995a}.
+Supply and demand conditions, which typically
 depend on the abundance of the species involved, certainly vary in time
@@
 cleaning mutualism involving the cleaner fish \emph{Labroides dimidiatus} and
-`client' fish. Clients offer themselves as food patches for cleaners to
-remove ectoparasites, which gives the cleaners calories and the clients
-improved health \citep{waldie_LongTerm_2011, ros_Does_2011, triki_Effects_2016}. As cleaners have about 2000
-interactions per day \citep{grutter_Relationship_1995}, they regularly face
-the situation that two clients seek cleaning simultaneously. In such
-conditions, it is important to distinguish between `resident' and
-`visitor' client species \citep{bshary_Cleaner_2001a}. The residents have
-small home ranges and hence access to only the local cleaner, while the
-visitors have large home ranges and hence access to two or more
-cleaners. Thus, visitors have the option to switch to another cleaner if
-being made to wait, while residents must wait for inspection. Indeed,
-visitors have been observed to use their partner choice options in that
+`client' fish. Client fish seek cleaner fish services at their territory
+(so-called ``cleaning station'') and offer themselves as food patches
+to get their ectoparasites removed, which provides cleaners
+with food and clients with improved health \citep{waldie_LongTerm_2011, ros_Does_2011, triki_Effects_2016, demaire_Reduced_2020}.
+Given the capacity of some client fish to swim larger distances and
+access multiple cleaning stations while others access the only cleaning
+station at their territory, it is crucial to categorize clients as
+either ``visitors'' or ``residents'', respectively. During cleaning interactions,
+a cleaner fish often face a choice between a visitor and a resident client
+seeking its cleaning services simultaneously. Visitors have the option
+to switch to another cleaner fish if being made to wait, while residents
+must wait for inspection. Indeed,
+visitors have been observed to use their partner choice option in that
 way \citep{bshary_Choosy_2002}, which may explain why cleaners give
 visitors service priority in a field study in the Red Sea
-\citep{bshary_Cleaner_2001a}. More generally, cleaners apparently prefer to
-interact with visitors \citep{triki_Marine_2021}. Such a preference may be
-linked to a client's value as a food patch; visitors are on average
-larger than residents \citep{bshary_Cleaner_2001a}, and size is positively
-correlated with parasite load \citep{grutter_Relationship_1995}. However,
-early laboratory experiments showed that leaving causes service
-priority independent of client value \citep{bshary_Asymmetric_2002}.
-The experiments consisted of asimultaneous two-choice task,
-where cleaners had to decide which of two
-Plexiglas plates, which offered equal amounts of food, to approach first
-and eat mashed prawn of it. One plate was made to behave like a
-resident, i.e.~it would remain until the cleaner had eaten off it. The
-other plate was made to behave like a visitor, i.e.~it would be removed
-if not inspected first. Cleaners learned to prefer the visitor plate and
+\citep{bshary_Cleaner_2001a}.
+
+When researchers aimed at testing wild-caught cleaner fish, as
+well as individuals from other species, abilities
+to prioritize visitor over resident clients in a lab-based paradigm,
+they used Plexiglas plates of different colours and shapes offering same
+amount of food as surrogates for visitor and resident clients.
+One plate is made to behave like a resident, i.e.~it remains until
+the cleaner had eaten off it. The other plate was made to behave
+like a visitor, i.e.~it is removed if not inspected first.
+Cleaners learned to prefer the visitor plate and
 hence obtained the double amount of food \citep{bshary_Asymmetric_2002}.
-Adult cleaner fish outperform various primates as well as rats and
+Furthermore, adult cleaner fish outperformed various primates as well as rats and
 pigeons in this original version of the biological market task
-\citep{salwiczek_Adult_2012, zentall_Early_2017}; only African grey
-parrots solve this task as well \citep{pepperberg_Can_2014}. As the correct
-solution must be learned, and primates are known to readily distinguish
+\citep{salwiczek_Adult_2012, zentall_Early_2017}; yet the African grey
+parrots solve this task as well \citep{pepperberg_Can_2014}. Given that primates
+are known to readily distinguish
 between one and two reward units if presented in more conventional ways
-\(\color{red}{\text{ref}}\), what makes the task difficult for most non-cleaners?
+\(\color{red}{\text{ref}}\), this raises the question:
+what makes the task difficult for most non-cleaners?
 
-Recent research on the cognitive tool kit needed to solve an ephemeral
+Recent research on the cognitive tool kit needed to solve the ephemeral
 reward task has used a broad approach as proposed by Shettleworth
-\citep{shettleworth_Cognition_2009},
-who defined cognition as including all ways in which animals take in information
-through the senses, process, retain and decide to act on it. Indeed, perception
-of relevant cues is of major importance for individual performance;
-i.e.~what relevant information is encoded in the design of the two
-plates (colour versus size; \citep{wismer_Cuebased_2019}), or whether
-the information is in the colour of
-the food \citep{pretot_Comparative_2021, pretot_Comparing_2016}, and
-whether the food is visible or hidden/released only when the subjects
-made choices on a touch screen \citep{pretot_Factors_2016}. However, identifying
+\citep{shettleworth_Cognition_2009}, who defined cognition as including
+all ways in which animals acquire information
+through the senses, process, retain and decide to act on it.
+Indeed, perception of relevant cues is of major importance
+for individual performance. For example, some animals find relevant
+information in the plates
+\citep{wismer_Cuebased_2019}) while others find it in the food
+\citep{pretot_Comparative_2021, pretot_Comparing_2016}. However, identifying
 cues as salient is not the only challenge of the ephemeral reward task,
@@
 reward task, learning models showed that basic reinforcement learning does
-not suffice to solve the task \citep{prat_Modelling_2022, quinones_Reinforcement_2019}.
+not suffice to solve the ephemeral reward task \citep{prat_Modelling_2022, quinones_Reinforcement_2019}.
 This is particularly so when models assume the more complex natural
-situation in which cleaners not only face resident-visitor pairs but also
-visitor-visitor and resident-resident pairs, as well only a resident or
-only a visitor. To be able to give visitors priority over residents,
+situation in which cleaner fish not only face resident-visitor pairs but also
+visitor-visitor and resident-resident pairs, as well a resident alone or
+a visitor alone. To be able to give visitors priority over residents,
 cleaners need to be able to assess a client's value separately for the
-three possible forms of encounter (alone, paired with a fish with the
+three possible scenarios (alone, paired with a fish with the
 same strategic option, paired with a fish with the alternative strategic option)
-\citep{quinones_Reinforcement_2019}. The ability to keep such separate scores
-for the same stimulus has been termed configurational learning,
-or chunking, or segmentation (see references in \citep{prat_Modelling_2022}).
+\citep{quinones_Reinforcement_2019}. The ability to distinguish and value differently
+one stimulus alone from compound versions of it has been termed
+configurational learning, or chunking,
+or segmentation (see references in \citep{prat_Modelling_2022}).
 
-To solve the ephemeral reward task, cleaners also need to account for
+To solve the ephemeral reward task, cleaners need to account for
 the future consequences of current decisions. In the model by
@@
 through perceiving a visitor client leaving as psychological punishment
-(i.e.~as a negative reinforcer). Given that a negative reinforcer is part
-of the ubiquitous learning mechanism termed operant conditioning
-\citep{thorndike_Animal_1898, skinner_Behavior_1938}, this explanation
-could be considered the simpler one. Furthermore, accounting for the
-future effects of an action is considered an advanced cognitive
-ability \citep{suddendorf_Evolution_2007}. Thus, standard logic of
+(i.e.~as a negative reinforcer). Low temporal discounting is when
+individuals include in their valuation of an action the reward effects
+that this will have in the future. This is done by combining in a single
+valuation the reward obtained in the current time with all the reward that
+comes after, discounting for how far in the future the future reward
+is accrued. `Chaining' the reward of these different time steps allows
+individuals to take actions that increase the long-term reward at the sacrifice
+of short term considerations \citep{enquist_Power_2016}. Even though, `chaining'
+can be readily implemented computationally in learning models
+\citep{enquist_Power_2016, sutton_Reinforcement_2018}, cognitively it seems to be
+a complex adaptation \citep{suddendorf_Evolution_2007}. On the other hand,
+using client behaviour as a negative reinforcer is in principle
+easier to implement. Negative reinforcement is part of the ubiquitous
+learning mechanism termed operant conditioning \citep{thorndike_Animal_1898, skinner_Behavior_1938}. Thus, standard logic of
 Lloyd Morgan's cannon demands that operant conditioning as the simpler
-explanation is to be accepted by default. Here, we explore the
-possibility that fitting a model in which the action of these two
-mechanisms, operant conditioning and chaining, depends
-on model parameters may reveal which process cleaners actually use.
-This is because one process may be better at predicting the observed
-variation in cleaner fish performance as a function of ecological conditions.
+explanation is to be accepted by default. Ideally, the two mechanisms should
+be evaluated in light of how well they explain the available data.
 
-Various repetitions of the ephemeral reward task in different years and
-with cleaners caught from various locations around Lizard Island,
-Great Barrier Reef, revealed that cleaner and client densities in
-nature affect how cleaners perform in the original market task:
-when relative densities are low, cleaners are more likely to fail to
-complete the task \citep{triki_Biological_2019, triki_Decrease_2018, wismer_Variation_2014}. The explanation for this pattern
-is twofold. First, low cleaner abundances implies low supply and high demand
-of cleaning services. Under this conditions, there will be less occasions under
+Over the last decade, our team tested over a hundred of wild-caught
+cleaner fish in the exact same paradigm of of the ephemeral reward
+task \citep{salwiczek_Adult_2012, wismer_Variation_2014, triki_Decrease_2018, triki_Biological_2019, triki_Brain_2020}. These fish often come from
+different reef locations around the study field site at Lizard Island,
+Great Barrier Reef in Australia. Further investigation of the local
+eco-sociological conditions revealed that cleaner and client
+fish population densities have a substantial impact on cleaner fish
+performance in the task. Cleaner fish from reef sites with relatively
+low densities were more likely to fail solving the task \citep{triki_Biological_2019, triki_Decrease_2018, wismer_Variation_2014}. The explanation for this pattern
+is twofold. First, low cleaner fish population densities imply
+low supply and high demand for cleaning services.
+Under such conditions, there are fewer occasions under
 which failing to give priority to a visitor translates to an empty
-cleaning station. Secondly and also related to the state of the cleaning market,
-visitor clients are less likely to exert their choice options
-(and hence wait for inspection if made to wait) when
-cleaner fish densities are low \citep{triki_Brain_2020}. If visitors are not choosy,
-cleaners should not give them priority anymore. Thus, the underling
-cognitive machinery and ecological variables apparently interact to produce
-such variable performance. By fitting our model to the empirical data on
-fish densities and cleaner fish performance in the ephemeral reward task
-we aimed to address two questions. First, we aimed to determine the likely
-mechanism used by cleaners to incorporate future consequences of current
+cleaning station. Second and also related to the state of the cleaning market,
+visitor clients at low cleaner fish population densities
+are less likely to exert their partner choice options
+and are hence more likely to wait for inspection if not given cleaning
+priority \citep{triki_Brain_2020}. In the absence of partner choice
+cleaners should not give priority to visitors any more.
+
+The interplay between the underling cognitive machinery and
+local ecological conditions apparently generate the documented variable
+performance among individuals of the same species.
+Our approach of fitting the computational model to the empirical data on
+fish densities and cleaner fish censuses and cleaner fish performance
+in the ephemeral reward task aimed at: (i), determining which
+mechanism cleaner fish use to incorporate future consequences of current
 decisions by testing whether operant conditioning, chaining, or a combination
-of both best explains performance. Second and related to the first
-question, we aimed to determine whether the two mechanisms differed
-with respect to the ecological conditions that are likely to cause high
-versus low performance in the ephemeral reward task. If that were the case,
-we would assess which mechanism would yield more appropriate performance
-patterns. Relying on the logic of biological market theory, we predicted
-that appropriate performance is to show low preference for visitors under high
-local client-to-cleaner ratio as visitor leaving rates should be low
-and any leaving visitor will be readily replaced by another client. In contrast,
-cleaners should show high performance if the local client-to-cleaner
-ratio favours clients.
+of both best explains their performance; (ii) determining whether the
+two mechanisms differed with respect to the ecological conditions
+that are likely to cause high versus low performance in the
+ephemeral reward task. Additionally, we assessed which mechanism
+yields optimal performance patterns. Relying on the logic of
+biological market theory, we predicted
+that appropriate performance is to show low preference for visitors under low
+local cleaner-to-client ratio. In this case, as visitor leaving rates
+should be low as well and any leaving visitor will be readily
+replaced by another client in the queue. In contrast,
+cleaners should show high performance in the ephemeral reward task
+if the local cleaner-to-client ratio favours clients.
 

### 2022-02-09 manuscript_1.0/manuscript_word.Rmd
Changes addressing Zegni's comment in the ms

@@
 ---
-title: Combination of field and experimental data together with computational models
-  reveal cognitive mechanisms behind cleaner fish behaviour
+title: Field and experimental data together with computational models
+  reveal key cognitive mechanisms behind cleaner fish behaviour
 author:

### 2022-02-16 manuscript_1.0/manuscript_1.0.Rmd
Fixed data files. Updated the cpp to g++ compilation. new parameter files to run chains with the fixed data files. Update figures in the manuscript

@@
 
-### Overview
+<!-- ### Overview -->
 
-In this study, we combined empirical data from Triki *et. al* 
-[@triki_Biological_2019;@triki_Brain_2020] and the computational 
-model analysed in Quiñones *et al.*[@quinones_Reinforcement_2019] 
-to test the relative validity of chaining versus operant conditioning as 
-mechanisms to account for future consequences of cleaner fish desicion-making.
-In order to compare the explanatory power of the different hypotheses, 
-we estimated the parameter values of three versions of 
-the model that best fit the empirical data. 
-Particularly, we fitted the parameter that determines how important 
-future reward is ($\gamma$), the magnitude of the negative reward 
-($\eta$) and a scaling constant that translates cleaner fish absolute 
-to relative population abundances (see following sections for details). 
-We obtained the model predictions using a set of stochastic individual-based
-simulations. Thus, each parameter combination of the model yielded not one 
-but a distribution of predictions. For the 
-fitting procedure, we used the bayesian inference algorithm: 
-Markov Chain Monte Carlo (MCMC). MCMC is a stochastic algorithm that allows
-to sample from the posterior distribution of model parameter values. The posterior
-distribution represents the most likely parameter values given the data. 
-Due to the stochastic nature of MCMC, which repeatedly samples parameter values
-and evaluates their likelihood, the distribution of likelihoods from the 
-stochastic model is also explored. This makes MCMC and bayesian inference
-particularly suitable for the computational models we evaluate. Bellow, 
-we explain first the computational model and the data collection, and later 
-how the MCMC was used to estimate parameter values.
+<!-- In this study, we combined empirical data from Triki *et. al*  -->
+<!-- [@triki_Biological_2019;@triki_Brain_2020] and the computational  -->
+<!-- model analysed in Quiñones *et al.*[@quinones_Reinforcement_2019]  -->
+<!-- to test the relative validity of chaining versus operant conditioning as  -->
+<!-- mechanisms to account for future consequences of cleaner fish desicion-making. -->
+<!-- In order to compare the explanatory power of the different hypotheses,  -->
+<!-- we estimated the parameter values of three versions of  -->
+<!-- the model that best fit the empirical data.  -->
+<!-- Particularly, we fitted the parameter that determines how important  -->
+<!-- future reward is ($\gamma$), the magnitude of the negative reward  -->
+<!-- ($\eta$) and a scaling constant that translates cleaner fish absolute  -->
+<!-- to relative population abundances (see following sections for details).  -->
+<!-- We obtained the model predictions using a set of stochastic individual-based -->
+<!-- simulations. Thus, each parameter combination of the model yielded not one  -->
+<!-- but a distribution of predictions. For the  -->
+<!-- fitting procedure, we used the bayesian inference algorithm:  -->
+<!-- Markov Chain Monte Carlo (MCMC). MCMC is a stochastic algorithm that allows -->
+<!-- to sample from the posterior distribution of model parameter values. The posterior -->
+<!-- distribution represents the most likely parameter values given the data.  -->
+<!-- Due to the stochastic nature of MCMC, which repeatedly samples parameter values -->
+<!-- and evaluates their likelihood, the distribution of likelihoods from the  -->
+<!-- stochastic model is also explored. This makes MCMC and bayesian inference -->
+<!-- particularly suitable for the computational models we evaluate. Bellow,  -->
+<!-- we explain first the computational model and the data collection, and later  -->
+<!-- how the MCMC was used to estimate parameter values. -->
 
@@
 
-In order to compare the fit that the three alternative models give we use the 
+To compare the fit of the three alternative models, we used the 
 distribution of pseudo $R^2$ proposed by Mcfadden [@mcfadden_Conditional_1974].
@@
 the model, relative to the log-likelihood of the data given a 
-model without covariates, as a measure of fit. Given that our 
-model is not a logistic regression, we measure the $pseudo-R^2$ in
+model without covariates, as a measure of fit. Our 
+model is not a logistic regression, therefore we measured the $pseudo-R^2$ in
 relation to the log-likelihood of a model
@@
 amounts to a model that has neutral preference between the two options. 
-Pseudo $R^2$ was calculated for all the samples of the posterior gotten from
-the MCMC. Thus, we use these distributions of pseudo $R^2$'s as a measure of
+We computed the pseudo $R^2$ for all the samples of the posterior from
+the MCMC. Thus, we used these distributions of pseudo $R^2$'s as a measure of
 fit.
@@
 ```{r post, fig.cap="Posterior distributions for parameter values $\\gamma$, $\\eta$ and the scaling constant.
-We show the kernel density estimates, below the mode (black point) and the 65\\% (light blue) and 95\\% (grey)  highest posterior density interval for the three paramteres.
-On the left (panels a, c and c) posterior distributions for a model with all three parameters; while on the right (b and d) a model without negative reward.
+We show the kernel density estimates, below the mode (black dot) and the 65\\% (light blue shade) and 95\\% (grey shade)  highest posterior density interval for the three paramteres.
+On the left, panels a, b and c show posterior distributions for a model with all three parameters; while on the right, d and e, show a model with only chaining.
 Panel f shows a measure of fit for both models, namely the distribution of pseudo-$R^2$ obtained from sampling the posterior distribution of parameter values.",out.width='100%',fig.height=6}
@@
 labels.Scen<-c("both","gam","Nrew")
-labelsPlot.Scen<-c("Full \n model","Future \n reward","Negative \n reward")
+labelsPlot.Scen<-c("FM","C","OC")
 
@@
   stat_halfeye(alpha=0.5,point_size=3)+
-  theme_classic()+xlim(-0.6,0.2)+
+  theme_classic()+xlim(-0.5,0.25)+
   scale_fill_manual(values=c("#1b9e77","#d95f02","#7570b3"),
   name = "Model", labels = labelsPlot.Scen)+
-  geom_vline(xintercept = 0,color="black",size=1)+
-  theme(legend.position = c(.3, .75),legend.key.size = unit(0.25,'cm'),
-        axis.text.y = element_blank())
+  scale_y_discrete(labels=labelsPlot.Scen)+
+  geom_vline(xintercept = 0,color="black",size=0.5)+
+  theme(legend.position = 'none')
+          # c(.32, .65)
+        # ,legend.key.size = unit(0.22,'cm'),
+        # axis.text.y = element_blank(),
+        # legend.text = element_text(size=7))
 
-plot_grid(nrow=3,align = "v",byrow = FALSE,
-          # Full model - \gamma
-          ggplot(data=MCMCdata1,aes(x=gamma)) + 
+gam.both.post<-ggplot(data=MCMCdata1,aes(x=gamma)) + 
   stat_halfeye(aes(fill=stat(cut(x,breaks = cuts.1$gamma))),
-                         point_interval = mode_hdi, .width = c(.66, .95),point_size=3,
-                         show.legend=FALSE) + 
-            labs(title=labelsPlot.Scen[1],subtitle = expression(gamma),x="",y="")+
-            theme_classic()+scale_fill_manual(values=c("gray85","skyblue","gray85"))+
-            theme(plot.margin = unit(rep(0.5,4), "lines")),
-          # \eta
-          ggplot(data=MCMCdata1,aes(x=negReward)) + 
+               point_interval = mode_hdi, .width = c(.66, .95),
+               point_size=3,show.legend=FALSE) + 
+  labs(title=labelsPlot.Scen[1],
+       subtitle = expression(gamma),x="",y="")+
+  theme_classic()+
+  scale_fill_manual(values=c("gray85","skyblue","gray85"))
+nrew.both.post<-ggplot(data=MCMCdata1,aes(x=negReward)) + 
   stat_halfeye(aes(fill=stat(cut(x,breaks = cuts.1$negReward))),
-                         point_interval = mode_hdi, .width = c(.66, .95),point_size=3,
+               point_interval = mode_hdi, 
+               .width = c(.66, .95),point_size=3,
                show.legend=FALSE)+theme_classic()+
   scale_fill_manual(values=c("gray85","skyblue","gray85"))+
-            labs(subtitle = expression(eta),x="",y="")+xlim(-5,5)+
-            theme(plot.margin = unit(rep(0.5,4), "lines")),
-          # Scale Constant
-          ggplot(data=MCMCdata1,aes(x=scaleConst)) + 
-            stat_halfeye(aes(fill=stat(cut(x,breaks = cuts.1$scaleConst))),
-                         point_interval = mode_hdi, .width = c(.66, .95),point_size=3,
-                         show.legend=FALSE)+
-            theme_classic()+scale_fill_manual(values=c("skyblue","gray85"))+
-          labs(subtitle = "Scalling const.",x="",y="")+xlim(-2,1500)+theme_classic()+
-          theme(plot.margin = unit(rep(0.5,4), "lines")),
-          # Future reward only model - \gamma
-          ggplot(data=MCMCdata2,aes(x=gamma)) +
+  labs(title="",subtitle = expression(eta),x="",y="")+
+  xlim(-2,2)
+gam.gam.post<-ggplot(data=MCMCdata2,aes(x=gamma)) +
   stat_halfeye(aes(fill=stat(cut(x,breaks = cuts.2$gamma))),
-                         point_interval = mode_hdi, .width = c(.66, .95),point_size=3,
+               point_interval = mode_hdi, .width = c(.66, .95),
+               point_size=3,
                show.legend=FALSE) +
   scale_fill_manual(values=c("gray85","skyblue","gray85"))+
-            labs(title=labelsPlot.Scen[2],subtitle = expression(gamma),x="",y="")+
-            theme_classic()+theme(plot.margin = unit(rep(0.5,4), "lines")),
-          # Scalling constant
-          ggplot(data=MCMCdata2,aes(x=scaleConst)) +
-            stat_halfeye(aes(fill=stat(cut(x,breaks = cuts.2$scaleConst))),
-                         point_interval = mode_hdi, .width = c(.66, .95),point_size=3,
+  labs(title=labelsPlot.Scen[2],
+       subtitle = expression(gamma),x="",y="")+
+  theme_classic()
+nrew.nrew.post<-ggplot(data=MCMCdata3,aes(x=negReward)) +
+  stat_halfeye(aes(fill=stat(cut(x,breaks = cuts.3$negReward))),
+               point_interval = mode_hdi, .width = c(.66, .95),
+               point_size=3,
                show.legend=FALSE) +
   scale_fill_manual(values=c("gray85","skyblue","gray85"))+
-            labs(subtitle = "Scalling const.",x="",y="")+
-            theme_classic()+theme(plot.margin = unit(rep(0.5,4), "lines")),
-          # Pseudo R^2
-          panel.rsqr.all+labs(subtitle = expression(pseudo-R^2),x="",y=""),
-          labels=c('a','b','c','d','e')
-)
+  labs(title=labelsPlot.Scen[3],
+       subtitle = expression(gamma),x="",y="")+
+  theme_classic()+xlim(-2,2)
+
+first.col<-plot_grid(nrow=3,align = "v",byrow = TRUE,
+          gam.both.post,gam.gam.post,nrew.nrew.post,           
+          labels=c('a','c','d'))
+second.col<-plot_grid(nrow = 2,align = "v",byrow = TRUE,
+          nrew.both.post,rsqr.both,rel_heights = c(1,2),
+          labels = c('b','e'))
+plot_grid(ncol = 2,first.col,second.col)
 
@@
 
-Figure \ref{fig:post} panels a,c and e show the posterior distributions
-of the parameter values of the full model, which includes both future
-and negative reward. Posterior distributions show the probability
+Figure \ref{fig:post} panels a,b and c show the posterior distributions
+of the parameter values of the full model, which includes both chaining
+and operant conditioning (negative reward). Posterior distributions show the probability
 density (y axis) of the estimated parameter values (x axis). Notably,
 the bulk of the posterior distribution for the parameter tuning negative
-reward ($\eta$ panel e) is around zero. Thus, the shape of the posterior
+reward ($\eta$ panel b) was around zero. Thus, the shape of the posterior
 and its credible intervals suggest the absence of negative reward to be
@@
 also includes zero, but the mode of the posterior is around 0.5. Thus,
-we run the analysis setting $\eta$ to zero. Figure \ref{fig:post} panels
-b and d, show the posterior distributions of the two parameters
+we ran the analysis setting $\eta$ to zero. Figure \ref{fig:post} panels
+d and e, show the posterior distributions of the two parameters
 estimated. Not surprisingly, under a model without negative reward, the
-distribution of $\gamma$ shifts to higher values. Under the new model,
-the estimates of $\gamma$ do not include zero and the distribution is
-centered around $0.5$. In panel f of figure \ref{fig:post} 
+distribution of $\gamma$ shifted to higher values. Under the new model,
+the estimates of $\gamma$ did not include zero and the distribution was
+centred around $0.5$. In panel f of figure \ref{fig:post} 
 we show the distribution of $pseudo-R^2$ calculated using 
@@
 as well as from a model with negative reward but without
-future reward. Note, $pseudo-R^2$ can have negative values, that is when
+future reward. Note, $pseudo-R^2$ can have negative values, which is when
 the log-likelihood of the model is lower than that of a model that
 triggers neutral preferences. Even though, the peak of the three
-$pseudo-R^2$ distributions is not very different, the model with only
-future reward produces a distribution of $pseudo-R^2$ where more values
-are positive (to the right of black line in Fig. \ref{fig:post} f). This
+$pseudo-R^2$ distributions was not very different, the model with only
+future reward produced a distribution of $pseudo-R^2$ where more values
+were positive (to the right of black line in Fig. \ref{fig:post} f). This
 shows that, accounting for variation in the parameter estimates, the
@@
 Left-hand side panel: color contour shows the prediction of the learning model using the mode of the posterior distributions of parameters recovered by the statistical analysis.
-Dots show the frequency of visitor choices for the 12 locations, as well as the corresponding relative cleaner abundance (x axis) and frequency of visitors leaving the station (y axis).
-Right-hand side panels: Variation of the predicted probabilites  of choosing a visitor and their observed values for 12 locations.
-Circles show the mean prediction for each location from 100 samples taking from the posterior distribution.
-Thick and thin bars show the 66 and 95\\% credible interval taken from those posterior samples.
+Dots show the frequency of visitor choices for the 12 reef sites, as well as the corresponding relative cleaner fish abundance (x axis) and frequency of visitors clients leaving the cleaning station (y axis).
+Right-hand side panels: Variation of the predicted probabilites  of choosing a visitor over a resident and their observed values for 12 locations.
+Circles show the mean prediction for each location from 100 samples taken from the posterior distribution.
+Thick and thin bars show the 66 and 95\\% credible interval, respectively, taken from those posterior samples.
 Squares show the predictions used for panel on the righ-hand side.
-Colour denotes different locations (see Empirical data section).
-Black line correspond to a perfect match between observed and predicted probabilities.
-Upper panels show prediction from a model including future and negative reward, lower panels from a  model with only future reward.",out.width='100%',fig.height=5}
+Colour coding denotes different reef sites/year of the data collection (see Empirical data section).
+Black line corresponds to a perfect match between observed and predicted probabilities.
+Upper panels show prediction from a model including chaining and operant conditioning, lower panels from a  model with only chaining.",out.width='100%',fig.height=5}
 
@@
 
-Figure \ref{fig:pred} shows predictions from the two models. On the
+Figure \ref{fig:pred} shows predictions from the two models, 
+one including chaining and operant conditioning (upper panels) and 
+one with only chaining (lower panels). On the
 left, the colour coded contour shows the prediction of the model for
-combinations of cleaner abundance (x axis) and visitor leaving
+combinations of cleaner fish abundance (x axis) and visitor leaving
 probability (y axis). Predictions were generated by running the model
 using the mode of the posterior distributions as the parameter values,
-and varying systematically cleaner abundance and visitor leaving
-probability. Colour of the points on top of the contour show the average
+and varying systematically cleaner fish abundance and visitor leaving
+probability. Colour of the dots on top of the contour show the average
 frequency with which cleaner fish chose the visitor plate in their last
-20 experimental trials. Each point corresponds to a location with a
-combination of cleaner abundance and visitor leaving probability. Panels
+20 experimental trials. Each dot corresponds to a reef-site/year of 
+data collection with a combination of cleaner fish abundance 
+and visitor leaving probability. Panels
 on the right show how close the observed values for the probability of
-choosing the visitor (y axis) are from the predictions of the models (x
+choosing the visitor (y axis) were from the predictions of the models (x
 axis). The black line represents the perfect fit between observed and
@@
 parameter varying, the full model
-gives a lower fit to the data than the model without negative reward.
+gave a lower fit to the data than the model without negative reward.
 In the supplementary material, we also show predictions from 
@@
 
-The main reason for negative and future reward to give different
-predictions is the way that cleaner's relative abundance influences the
+The main reason for chaining and operant conditioning to give different
+predictions is the way that cleaner fish relative abundance influences the
 preference for the visitor clients. Visitor leaving probability has a
@@
 clients on all three models (Fig. \ref{fig:pred}, \ref{fig:nogamma}). In
-contrast, cleaner's relative abundance has a different effect in the
-model with only future reward, compared to the other two. In the model
-with only future reward only intermediate cleaner abundance triggers a
+contrast, cleaner fish relative abundance has a different effect in the
+model with only chaining, compared to the other two models, 
+full model and only operant conditioning. In the model
+with only chaining, only intermediate cleaner fish abundance triggers a
 preference for the visitor clients (Fig. \ref{fig:pred} c). In models
 with negative reward, both intermediate and low cleaner abundance
-trigger a preference for the visitor. (Fig. \ref{fig:pred} a,
+triggered a preference for the visitor. (Fig. \ref{fig:pred} a,
 \ref{fig:nogamma}).
@@
 
-We asked which if two potential cognitive mechanisms 
-– chaining of events, negative reinforcement, or a combination of both – 
-is the more likely mechanism to explain intra-specific variation in cleaner 
-performance in the ephemeral reward task as a function of ecological 
-conditions in the wild. To evaluate the merits of the alternative mechanisms, 
-we considered performance in the task to depend on decision-rules that 
-cleaners had developed in their natural environment: individuals that 
-solved the task did so because they already had a general preference for 
-visitors, and applied this rule once being familiar with the task.  
-While all three models capture well the positive relation between visitor 
+In this study, our main aim was to unravel which of two potential 
+cognitive mechanisms, chaining of events, operant conditioning, 
+or their combination, best explains wild-caught cleaner fish 
+performance in the ephemeral reward task, while accounting for their
+ecological conditions. To evaluate the merits of each of these two mechanisms
+separately and combined, we considered cleaner fish performance 
+in the lab test to have its origin from the these fish apply 
+in their natural environment. That is, individuals that 
+solved the task already had a preference for 
+visitors clients, and generalized this rule to the lab conditions 
+once being familiar with the task.
+
+While all three models captured well the positive relation between visitor 
 leaving behaviour and cleaner performance in
 the market task [@triki_Biological_2019], only the chaining mechanism 
-predicts that cleaner performance in the task should be low if their 
-local abundance in the wild relative to clients is low. Indeed, such low 
-performance is predicted regardless of the visitor leaving
-probability. In contrast, a model with negative reward predicts the
-highest performance in the ephemeral reward task when relative 
-cleaner abundance is low, particularly
+predicted that cleaner fish performance in the task should be low in 
+habitats with low cleaner-to-client ratios, regardless of the 
+visitor leaving probability. In contrast, models including 
+negative reward predicted the highest performance in the ephemeral 
+reward task when relative cleaner abundance is low, particularly 
 together with high probability of visitor leaving (Fig. \ref{fig:pred}).
-Low cleaner abundances mean the market has an excess of demand for
-cleaning services. In the model, this translates to a cleaning station
-that is frequently full. Thus, when visitors leave, it's likely that the
-cleaner will have access to another client in the next step. Therefore, 
+Low relative cleaner fish abundances mean the market has an excess of demand for
+cleaning services. In the models, this translates to a cleaning station
+that is frequently full. Thus, when a visitors leaves, it is likely that the
+cleaner fish will have access to another client in the next step. Therefore, 
 there will not be much difference in future reward between choosing 
@@
 visitor in these conditions. On the other hand, the effect of negative reward 
-would be opposite as in a full station, cleaners will get more often the
-heterotypic (resident-visitor) option and will develop a preference for
-the visitor faster. Note that when cleaner abundance is high situations
-with a resident and a visitor will be so rare that neither mechanism
-will be very efficient in generating a preference for visitors. When
-such choice arises it is still be best to choose the visitor; however,
+on cleaner fish preference is the opposite, as in a busy cleaning station, to
+that of chaining. cleaner fish will get more often the resident-visitor
+state and will develop a preference for the visitor faster. 
+At high cleaner fish abundances, the resident-visitor state
+becomes so rare that neither mechanism is very efficient 
+at generating a preference for visitors. When facing the resident 
+visitor choice it is still be best to choose the visitor; however,
 the learning machinery will not be able to develop this preference
-efficiently. Overall, estimation of future reward is then the cognitive
-mechanism that allows cleaners to adaptively respond to the
-ecological conditions of the biological market.
+efficiently. Overall, the models suggest that chaining is the cognitive
+mechanism that allows cleaner fish to adaptively adjust to their 
+biological market ecological conditions.
 
 Our results support chaining as the more plausible mechanism behind the 
-inter-specific variation in cleaners' performance, which is also 
-the mechanism that allows them to respond more adaptively. This could
-suggest chaining to be under positive selection. In the standard ephemeral
-reward task, however, food amount and quality are equal between the 
-two plates. An given that models resemble this, choosing visitors over 
-residents in low cleaner abundances does not diminish the 
-amount of food/reward in the the models. 
-On the other hand, a cleaner committed to visitors might find more difficult 
-to include in the decision making other variables, like parasite load 
-and/or mucus quality, that do predict the amount of food in the field 
-[@roche_Client_2021]. In nature and in laboratory experiments, cleaners prefer 
-higher quality mucus and more food in the absence of market effects 
-(i.e. in simultaneous 2-choice options, 
-[@triki_Fluctuations_2019;@grutter_Cleaner_2004]), and they use size as a 
-proxy for food availability [@wismer_Cuebased_2019;@grutter_Does_2005]. 
+inter-specific variation in cleaners' performance. This suggest
+that chaining could be under positive selection. In the standard ephemeral
+reward task, however, food amount and quality are equal in the 
+two Plexiglas plates. Since our computational models simulate this aspect of
+the task, choosing visitors over residents at low cleaner fish abundances 
+does not diminish the amount of food/reward in the models. 
+On the other hand, a cleaner fish committed to visitors might find it more difficult 
+to include in its decision making other variables, like parasite load 
+and/or mucus quality [@roche_Client_2021]. Indeed, in the absence of 
+market effects, both field observations and aboratory experiments also 
+using simultaneous two choice options, show that cleaner fish base their 
+decision-making on other cues such as the mucus quality and the amount of food.  
+[@triki_Fluctuations_2019;@grutter_Cleaner_2004], as well as client size 
+as a proxy for food quantity [@wismer_Cuebased_2019;@grutter_Does_2005]. 
 How important this limitation is will determine whether chaining yields a higher
@@
 
-Individual cleaners that performed in the laboratory test according to what 
-is best at their site of capture (low performance when living at low densities, 
-high performance when living at high densities) had larger forebrains 
-harbouring more cells than individuals whose performance mismatched locally 
-optimal decision-rules [@triki_Brain_2020]. Triki *et al.*  refer to the 
-former as socially competent cleaners. Social competence refers to the 
-ability to optimise social behaviour depending on the available social 
-information [@taborsky_Social_2012a;
+Previous research showed that cleaner fish living at high population 
+densities and giving service priority to the visitor plate in the 
+ephemeral reward task, as well as cleaner fish living at low 
+densities but denying service priority to the visitor plate possess 
+larger forebrains; a key teleost brain region associated with 
+behavioral flexibility and social intelligence. Those failing to 
+show optimized decision-rules given their local ecological 
+conditions had relatively smaller forebrains  [@triki_Brain_2020]. 
+Triki *et al.*  refer to the former as socially competent cleaner fish,
+while the second group as socially incompetent cleaner fish. 
+Social competence is the ability to optimise social behaviour 
+to the available social information [@taborsky_Social_2012a;
 @bshary_Cooperation_2015;@varela_Correlated_2020]. Our analyses yielded no 
 evidence that the difference in social competence with respect to the local 
-market conditions and associated brain morphology are due to the mechanism 
+ecological conditions and associated brain morphology, 
+found by Triki *et al* [@triki_Brain_2020], are due to the mechanism 
 used to incorporate future consequences. It could have been conceivable that 
-high performing individuals from low-density sites might use negative 
-reinforcement instead of chaining, but in that case negative reinforcement 
-should have explained part of the data. Configurational learning or 
-chunking [@sutherland_Configural_1989;@miller_Magical_1956], the second component 
-necessary to solve the ephemeral reward task [@quinones_Reinforcement_2019], was 
-not varied in the models analized here. However, while chunking tendencies 
-should vary to allow individuals to adapt to local conditions 
+high performing individuals from low population densities reef sites 
+might use negative reinforcement instead of chaining, but in that 
+case negative reinforcement should have explained at least 
+part of the data. Configurational learning or 
+chunking [@sutherland_Configural_1989;@miller_Magical_1956], 
+the second component necessary to solve the ephemeral 
+reward task [@quinones_Reinforcement_2019], was 
+not varied in the models we analized here. However, while chunking tendencies 
+should vary to allow individuals to adapt to their local conditions 
 [@prat_Modelling_2022;@kolodny_Evolution_2014], systematic differences 
@@
 
-The model is inspired by the general processes of associative learning
-where short term rewards are translated to decision making; thus, it 
+Our models are inspired by the general processes of associative learning
+where short term rewards are translated into decision making; thus, it 
 ignores alternative channels of information that could be relevant in 
 market-like situations. For example, the model does not investigate whether 
-cleaners actually assess the frequency of client visits or a mean frequency 
+cleaner fish actually assess the frequency of client visits or a mean frequency 
 of visitors leaving. The updating learning mechanism for the development 
-of preferences works on a trial by trial basis. In the model, cleaners 
-do not need to assess the actual state of the market, *i.e.* their density, 
-the density of residents and visitors, and client visitation rate as an 
-indicator of demand. They only need to assess short-term consequences of 
-own decisions on food intake and chain them. Also, for the sake of 
-simplicity, the model ignores the process by which cleaners discriminate 
+of preferences works on a trial-by-trial basis. In the model, cleaner fish 
+do not need to assess the actual state of the market, *i.e.* their abundance, 
+the abundance of residents and visitors, and client visitation rate as an 
+indicator of demand. They only need to assess short-term consequences of their
+own decisions on food intake, and chain them. Also, for the sake of 
+simplicity, the model ignores the process by which cleaner fish discriminate 
 residents and visitor clients. A model that accounts for this discrimination
-probably involves the development of preferences for morphological or 
+probably would involve the development of preferences for morphological or 
 behavioural features that are statistically associated with visitors 
-or residents. For example, visitors are on average larger larger 
-than residents [@bshary_Cleaner_2001a], and are less likely to chase 
-cleaners in response to the latter cheating by taking a bite of 
-mucus [@bshary_Asymmetric_2002]. Given these associations, chaining might 
-produce the decision-rule “chose the larger client and/or less aggressive 
-client”, which does not help in the standard ephemeral reward task.
+or residents. For example, visitors are on average larger 
+than residents in body size [@bshary_Cleaner_2001a], and contrary to 
+resindents, are less likely to chase a cleaner fish that fails to cooperate
+and intead cheats its client by taking a bite of mucus 
+[@bshary_Asymmetric_2002]. Given these associations, chaining might 
+produce the decision-rule “choose the larger client and/or the less aggressive 
+client”, which is not a useful rule in the standard ephemeral reward task.
 
 In conclusion, our study shows that variation in cognitive performance as 
-a function of ecological factors may set the stage for the use of 
+a function of the local ecological conditions may set the stage for the use of 
 mechanistic modelling to identify the cognitive processes underlying 
@@
 of the general philosophy in animal cognition to apply the logic of 
-Lloyd Morgen's canon (Occam's razor). Excluding basic 
-reinforcement learning explanations (operant and/or classical conditioning) 
-as a potential explanation in experiments
-often warrants animals solving the task on the first possible occasion.
+Lloyd Morgen's canon (Occam's razor). Cognitive experiments with the 
+aim of excluding basic reinforcement learning as a potential 
+explanation (operant and/or classical conditioning) of performance 
+often employ one trial experiments requiring animals to solve the 
+task on the first possible occasion. 
 For example, any theory of mind task needs to be solved in the first
@@
 [@hirata_SweetPotato_2001]). In our case, the number of trials it took
-cleaners to learn the solution to the market task would never allow to
-exclude an important role of negative reinforcement based on the data
-alone. However, fitting model predictions to our data set revealed that
-a more complex mechanism (estimation of future reward) fits the data
-better.
+cleaners to learn the solution to the ephemeral rewards task 
+would never allow to exclude an important role of 
+negative reinforcement based on the data
+alone. However, fitting model predictions to our comprehensive empirical 
+data set revealed that a more complex mechanism, estimation of future reward,
+fits the data better.
 
@@
 ```
-```{r nogamma, fig.cap="Observed and predicted probability of choosing a visitor for a model without future rewards.
+```{r nogamma, fig.cap="Observed and predicted probability of choosing a visitor for a model without chaining.
 Left-hand side panel: color contour shows the prediction of the learning model using the mode of the posterior distributions of parameters recovered by the statistical analysis.
-Dots show the frequency of visitor choices for the 12 locations, as well as the corresponding relative cleaner abundance (x axis) and frequency of visitors leaving the station (y axis).
-Right-hand side panel: Right-hand side panels: Variation of the predicted probabilites  of choosing a visitor and their observed values for 12 locations.
+Dots show the frequency of visitor choices for the 12 reef sites, as well as the corresponding relative cleaner fish abundance (x axis) and frequency of visitors leaving the station if being made to wait (y axis).
+Right-hand side panel: Right-hand side panels: Variation of the predicted probabilites  of choosing a visitor and their observed values for 12 reef sited.
 Circles show the mean prediction for each location from 100 samples taking from the posterior distribution.

### 2022-02-16 manuscript_1.0/manuscript_1.0.tex
Fixed data files. Updated the cpp to g++ compilation. new parameter files to run chains with the fixed data files. Update figures in the manuscript

@@
 it is not clear which cognitive mechanisms allow individuals to adjust their
-behaviour to the varying market conditions. As adjustments to changes in
+behaviour to the varying conditions. As adjustments to changes in
 market conditions have been documented in a great variety of species with
@@
 information in the plates
-\citep{wismer_Cuebased_2019}) while others find it in the food
+\citep{wismer_Cuebased_2019} while others find it in the food
 \citep{pretot_Comparative_2021, pretot_Comparing_2016}. However, identifying
@@
 valuation the reward obtained in the current time with all the reward that
-comes after, discounting for how far in the future the future reward
+comes after, discounting for how far in the future reward
 is accrued. `Chaining' the reward of these different time steps allows
@@
 performance in the task. Cleaner fish from reef sites with relatively
-low densities were more likely to fail solving the task \citep{triki_Biological_2019, triki_Decrease_2018, wismer_Variation_2014}. The explanation for this pattern
+low densities were more likely to fail at solving the task \citep{triki_Biological_2019, triki_Decrease_2018, wismer_Variation_2014}. The explanation for this pattern
 is twofold. First, low cleaner fish population densities imply
@@
 Our approach of fitting the computational model to the empirical data on
-fish densities and cleaner fish censuses and cleaner fish performance
+fish densities and cleaner fish censuses and performance
 in the ephemeral reward task aimed at: (i), determining which
@@
 that appropriate performance is to show low preference for visitors under low
-local cleaner-to-client ratio. In this case, as visitor leaving rates
-should be low as well and any leaving visitor will be readily
-replaced by another client in the queue. In contrast,
-cleaners should show high performance in the ephemeral reward task
-if the local cleaner-to-client ratio favours clients.
+local cleaner-to-client ratio.
 
@@
 
-\hypertarget{overview}{%
-\subsubsection{Overview}\label{overview}}
-
-To test the relative validity of chaining versus negative reinforcement as
-mechanisms to account for future consequences of current choices,
-we combined empirical data from Triki \emph{et. al}
-\citep{triki_Biological_2019, triki_Brain_2020}. with the computational
-model analysed in Quiñones \emph{et al.}\citep{quinones_Reinforcement_2019}. In order to
-compare the explanatory power of the different hypothesis, we estimate the
-parameter values of three versions of the model that best fit the data.
-Particularly, we fit the parameter that determines how important
-future rewards are (\(\gamma\)), the magnitude of the negative reward
-(\(\eta\)) and a scaling constant that translates absolute to relative
-abundances (see following sections for details). We obtained model
-predictions using a set of stochastic individual-based
-simulations. Thus, each parameter combination of the model yields not one
-prediction for the data set, but a distribution of them. Thus, for the
-fitting procedure, we use one of the most common algorithms in bayesian inference,
-the Markov Chain Monte Carlo (MCMC). MCMC is a stochastic algorithm that allows
-to sample from the posterior distribution of model parameter values. The posterior
-distribution represents the most likely parameter values given the data.
-Due to the stochastic nature of MCMC, which repeatedly samples parameter values
-and evaluates their likelihood, the distribution of likelihoods from the
-stochastic model is also explored. This makes MCMC and bayesian inference
-particularly suitable for the computational models we evaluate. Bellow,
-we explain first the computational model and the data collection, and later
-how the MCMC was used to estimate parameter values.
-
 \hypertarget{the-model}{%
@@
 
-The model consist of a set individual-based simulations where
-individuals face a series of choices between two options. Individuals in
-the model represent cleaners, and the options they face simulate the
-natural conditions of a cleaning market. Cleaners experience a series
-of discrete time points in which they face different `states', which
-are defined by the number and type of clients inviting for service.
-There are six possible states: zero clients, one resident, one visitor,
-two residents, two visitors, and a mix of one resident and one visitor.
+The model consists of a set individual-based simulations where
+individuals, representing cleaners, face a series of choices
+between two options, which simulate the natural conditions
+of the cleaning market. Individuals experience a series
+of discrete time points in which they face different `states',
+defined by the number and category of client fish (visitor or residents)
+inviting for cleaning services. There are six possible states:
+zero clients, one resident, one visitor,
+resident-resident, visitor-visitor, and resident-visitor.
 The probability of each state is largely determined by the relative
-abundance of cleaners, residents and visitors, but to some degree by a
-cleaner's choices when it faces the resident-visitor combination.
-This is because residents are those clients that stay in the
-cleaning queue when they are not given priority and hence would
-still be available in the next time point; while visitors leave
-the queue (with a certain probability) after they are not given
-priority. Individuals obtain a fixed reward from cleaning a client
-regardless of the type. Every time individuals face and make a choice
+abundance of cleaner fish, residents and visitors, but to some degree by
+cleaner fish choices when it faces the resident-visitor combination.
+This is because residents are willing to queue for cleaning service;
+while visitors leave the queue (with a certain probability) when made to wait.
+Individuals obtain a fixed reward from cleaning a client fish
+regardless of the category. Every time individuals face and make a choice
 they update the probability of making that same choice. The update is
-based on the difference between the expectation of reward and the actual
-reward the individual obtains (prediction error)
-\citep{sutton_Reinforcement_2018, rescorla_Theory_1972}; and it is carried
-in the direction that would lead to more reward being obtained, given
+based on the difference between the expected reward and the obtained
+reward (prediction error) \citep{sutton_Reinforcement_2018, rescorla_Theory_1972}. Given the new information, the update is carried
+in the direction that leads to more reward being obtained, given
 the new information. In the long run, the probability of choosing a visitor
@@
 will converge depends on the relative abundance of cleaners, visitors
-and resident; as well as on the probability of visitors leaving the station
-when unattended. Further details of the model implementation can be
-found in the paper \citep{quinones_Reinforcement_2019}.
+and resident; as well as on the probability of visitors leaving the
+cleaning station when made to wait. Further details of the model
+implementation can be found in Quiñones \emph{et al} \citep{quinones_Reinforcement_2019}.
 
-The model shows that only agents that calculate rewards separately for
-the different states (termed `fully aware agents') can potentially
-prioritise visitors of residents in nature, and hence also solve the
-ephemeral reward task. This is because pooling rewards for the two
-clients from all states by `partially aware agents'
-(that only recognize the two clients as different) cancels out
-all differences (see \citep{quinones_Reinforcement_2019}). However,
-such \emph{chunking} by fully aware agents is not enough to develop a
-preference for visitors. In addition, agents need to find a mean
+The model shows that agents need to find a mean
 to incorporate future consequences of current choices. In the model,
@@
 Second, \(\eta\) measures how much individuals include in their reward the
-fleeing behaviour of visitor clients as a negative component. Both of
+fleeing behaviour of visitor as a negative component. Both of
 these parameters allow individuals to use in their estimates the future
 effects of their choices.
-
-A further model analysis contrast the effect of these two
-parameters against variation in the relative abundance of cleaners
-and the two client types. Assuming certainty that visitors leave, the
-two parameters yield different
-predictions when relative client abundance is very high. Under such
-conditions, the analysis shows that under very high client (relative)
-abundance the presence of future rewards (\(\gamma>0\)) no longer favours
-the preference for the ephemeral clients, while the preference persists
-when the negative reward mediated by client behaviour (\(\eta>0\)) is
-included. Thus, the analysis suggests that future reward as an
-explanation for cleaner ability to prefer visitors is supported.
-At first sight, empirical data seem to support future rewards as
-the mechanism used by cleaners, as the statistical analysis by
-Triki \emph{et al.} \citep{triki_Biological_2019} data revealed that low
-cleaner-to-client ratios predict low preference for visitors and hence
-low performance in the ephemeral reward task. However, low cleaner-to-client
-ratios may also lead to low probabilities of visitors leaving, which would
-cause low preferences for visitors independently of the underlying
-mechanism \citep{quinones_Reinforcement_2019}. Furthermore, a combination
-of future and negative rewards, could still be yield a better explanation
-for the data than any single factor.
 
@@
 
-The empirical data were collected between 2010 and 2018 always during
-the austral winter months June to August at Lizard Island
+The empirical data were collected between 2010 and 2019 always during
+the austral winter months June to August from a total of five
+study reef sites (Corner Beach-CB, Horseshoe-HS, Mermaid Cove-MC,
+Northern Horseshoe-NHS, and The Crest-TC) at Lizard Island
 (\(14.6682° S, 145.4604° E\)), Great Barrier Reef, Australia.
-They consist of three sets: fish densities from a total of five study
-reef sites (Corner Beach-CB, Horseshoe-HS,
-Mermaid Cove-MC, Northern Horseshoe-NHS, and The Crest-TC),
-natural observations of cleaners to quantify the probability
-of visitors leaving if initially ignored in favour of another client, and the
-performance of individuals caught from these sites in the ephemeral reward test.
-In total, we have twelve site/year data sets for fish densities and
-corresponding performance in the test. Thus, some sites were sampled more
-than once. Due to major environmental perturbations during the study period
-(\(\color{red}{\text{refs}}\)), fish densities changed significantly even
-within sites \citep{triki_Decrease_2018, triki_Fluctuations_2019}. To estimate
-the population density of cleaner fish and their clients at a given site in
+The data consist of three sets: fish censuses, field
+observations of cleaner-client interactions to quantify the probability
+of visitors leaving if made to wait, and the
+performance of wild-caught cleaner fish in the ephemeral reward test.
+In total, we have twelve site/year data sets for fish censuses and
+corresponding performance in the lab test. Thus, some sites were sampled more
+than once. To estimate the population density of cleaner fish
+and their clients at a given site in
 a given year, Triki \emph{et al.} \citep{triki_Biological_2019} used a series of ten
@@
 the reef and first counted the visible large-bodied adult fish
-(species with total length TL \textgreater{} \(10cm\)) on a width of \(5m\), and then on the
-return individuals of small-bodied fish species (TL \textless{} \(10 cm\)) on a width
-of \(1 m\). We included cleaner fish in the \(5 m\) transect. Based on the
-classification by Bshary \citep{bshary_Cleaner_2001a} and Wismer \emph{et al.}
-\citep{wismer_Variation_2014}, all visitor client species (\(n = 124\)) were
-large-bodied. Resident clients comprised all small-bodied species
-(\(n = 30\)) but also some large-bodied ones (\(n = 15\)). Overall,
-large-bodied species are highly correlated with being a visitor,
-and small-bodied species are a good correlate of residents. Based on the
-transect data, Triki \emph{et al.} \citep{triki_Biological_2019, triki_Brain_2020}
-estimated cleaner fish, small-bodied client, large-bodied client and total
-client fish densities per \(100 m^2\). LASSO analyses revealed that cleaner and
-large-bodied client densities were highly correlated, and only the former
-was hence kept in the analyses as representative of both \citep{triki_Biological_2019}.
-Cleaner densities, in interaction with visitor client leaving probability,
-explained best individual performance in the ephemeral reward task
-\citep{triki_Biological_2019}, while cleaner-to-client ratio was not a significant
-factor. This creates a certain mismatch with the model by Quiñones \emph{et al.}
-\citep{quinones_Reinforcement_2019}, which focused on abundance of cleaners relative
-to overall client abundance in order to capture the characteristics
-of the market. Importantly, relative abundances of clients define not only
-the probability of interactions with residents and visitors, but also affect
-how often the cleaning station is empty (e.g.~there are no clients to be cleaned).
-The higher the relative abundance of cleaners is, the higher is the probability
-of cleaning stations being empty at a given time point. How often the
-cleaning stations are empty in turns influences the value that cleaners can
-expect from their choices. The emptier the cleaning stations are, the more
-beneficial it is to prioritize a client that will not stay. On the other hand,
-situations where cleaners have to choose will be rare if cleaner relative
-abundance is high, which reduces the total value of prioritizing visitors
-over residents and makes it more difficult to learn a preference for visitors.
-Given the model structure, we used the empirical data to calculate relative
-abundances of cleaners, residents and visitors for the current analyses.
-To incorporate the empirical finding that absolute densities matter, we
-introduced a new scaling constant (see section on model fitting).
+(species with total length \(TL \geq 10cm\)) including cleaner fish
+on a width of \(5m\), and then on the
+return individuals of small-bodied fish species (\(TL < 10 cm\))\\
+on a width of \(1 m\)
+(see Triki et al.~2018 for further details on fish censuses data collection).
+We then scaled the counts of cleaner fish, small-bodied,
+and large-bodied clients fish densities per \(100 m^2\).
+From the study by Triki \emph{et al} \citep{triki_Biological_2019}
+cleaner fish and large-bodied client populations densities were
+highly correlated, and only the former
+was hence used in the analyses as representative of both measures.
 
-To collect data on the visitor clients' probability of leaving if not serviced
-immediately, eight cleaners per site/year were each filmed for \(30 min\).
-From the videos, all events in which a visitor client was made to wait in
-favour of another (visitor or resident) client were identified, and noted
-whether or not the visitor left \citep{triki_Biological_2019, triki_Brain_2020}.
-A total of 120 cleaners (10 individuals per 12 site/year) were tested in the
+The field observation data consisted of video recordings/encodings of the
+cleaner-client cleaning interactions. There were videos from eight
+cleaners per site/year of a duration of \(30 min\) each. Triki \emph{et al}
+extracted information from every event wherein a visitor client
+was made to wait in favour of another client (visitor or resident), and noted
+whether or not the visitor left or queued for the cleaning service
+\citep{triki_Biological_2019, triki_Brain_2020}.
+
+The cognitive performance data was from a total of 120 cleaners
+(10 individuals per 12 site/year) tested in the
 ephemeral reward task \citep{triki_Biological_2019, triki_Brain_2020}. Authors
@@
 (colour and pattern) and the plates' role (visitor or resident) between the
-tested fish. The data was originally collected to assess which variables are
-good predictors of the capacity to solve the ephemeral food task. Thus, previous
-analysis use specific statistical criteria to classify individual cleaners'
-performance as successful or failure \citep{triki_Biological_2019}. Because the model
-predicts the preference of cleaners given the set of environmental variable,
-we instead use the raw data of individuals cleaners' decisions.
-We use 20 choices from each cleaner as the preference they develop
-for the visitor plate. Which these 20 choices were vary for each cleaner depending
-on the performance that was originally assessed. For cleaners that did not
-succeed, the 20 choices correspond to the last two sessions. Cleaners that
-succeeded in solving the task were tested on a reversal task. That is, the
-pattern in plates was switched to the opposite role they played in the
-initial test. For those cleaners, we used the last session before they succeeded
-in the initial, and the last session of the reversal, completing the 20 choices.
-We did not distinguish between individuals that reached the criterion early
-or late during the 200 trials.
+tested fish. In the original studies, once a fish reach a learning criterion,
+that is, performing significantly above chance level (\(> 50%
+\), \(p-value ≥ 0.05\)),
+they passed to a reversal version of the task where the roles of the
+visitor/resident Plexiglas plates were swapped (see Triki et al.~2019, 2020).
+Here, we used instead a subset of these data in order to have an idea on
+cleaner fish preferences for the visitor plate, even if they do not reach
+the learning criterion within 200 trials. To do so, we first extracted the
+trial-by-trial outcomes from the last two session (20 trials) of those who
+never reached the learning criterion for visitor plate
+\(\color{red}{\text{(N = XX cleaner fish)}}\).
+For those who reached the learning criterion at some point during the
+test and passed to a reversal phase, we extracted the trials-by-trial
+outcomes from the last session (10 trials) before passing to reversal
+and the last 10 trials they were exposed to in the test
+\(\color{red}{\text{(N = XX cleaner fish)}}\).
 
@@
 
-The aim of the analysis is to fit the key model parameters that allow
-individuals to incorporate future consequences of current actions,
-\(\gamma\) and \(\eta\), to the data from Triki \emph{et al.}
-\citep{triki_Biological_2019, triki_Brain_2020} to find out whether each or
+The aim of the analyses is to fit the key model parameters
+\(\gamma\) and \(\eta\), to the empirical data from Triki \emph{et al.}
+\citep{triki_Biological_2019, triki_Brain_2020} to test whether each or
 a combination of these effects is a better explanation for the pattern
-seen in the data. In particular, we are interested in the relation between the
-ecological variables: cleaners, visitor clients, resident clients abundances and
-visitor clients leaving probability; and cleaners' preference for visitor clients
-over residents. Thus, the four ecological variables are given as input to
-the models. The preference for visitors gotten from the simulations of the model
-is used as the prediction for the response variable, while the number of visitors
-chosen out of the 20 choices of each cleaner as the observed response variable.
+seen in the data. We used the
+ecological variables: cleaners, visitor clients,
+resident clients abundances and
+visitor clients leaving probability, as input to the models.
+As response variable we used cleaners' preference for visitor
+over residents in the ephemeral reward task.
+Finally, we used the preference for visitors resulting from the
+model simulations as the prediction for the response variable.
 We kept all other parameter values used for the model simulations constant,
@@
 
-In order to capture with the model the relationship between the characteristics
-of the market (environment) and the cleaner's preference we need to translate
-the absolute abundances of the data to to a measure of relative abundances
-that captures client visitation patterns. This is because in the model, relative
+To capture with the model the relationship between the ecological
+variables and cleaner fish preferences for visitors we need to scale
+the absolute population densities of cleaner fish from the empirical data
+to a measure of relative abundances that captures
+client visitation patterns. This is because in the model, relative
 abundances of clients define not only the probability of residents and visitors,
@@
 clients to be cleaned). The frequency with which clients visit the station
-is another variable, which will likely vary among different client species
-depending on parasite abundances and loads. We do not have field estimates
-for species specific parasite loads, especially not as a function of site.
+is another variable, which in nature may vary among different client species
+depending on their ectoparasite loads. We do not have field estimates
+for species-specific parasite loads, especially not as a function of site.
 In order to control for these aspects, we computed a measure of relative
-cleaner abundance for each site relative to absolute abundances and multiplied
+cleaner fish abundance for each reef site relative to
+absolute abundances and multiplied it
 by a scaling constant that changes the range of the variable. This scaling
 constant is hence meant to capture variation in the market conditions driven
-partly by cleaner abundance. We fit the value of the scaling constant as
-part of the statistical inference. As for the client abundances for
-residents and visitors we computed a relative measure with respect to the
+partly by cleaner abundance. We fitted the value of the scaling constant as
+part of the statistical inference. As for the visitor and resident
+abundances we computed a relative measure with respect to the
 total client abundance, and weighted that by the rescaled relative absence
@@
 for the probability of having different options in the cleaning station.
-Note that the scaling constant was introduced to control for variation that
+Note that we introduced the scaling constant to control for variation that
 is not captured by the model; its parameter distribution does not offer
@@
 
-Once we calculate the relative abundances, we can obtain predictions from
-the model for each one of the locations and run the Markov Chain. We start the
-chain with random values for the parameters of interest, then run the
-computational model once for every location using as input the ecological
+Once we calculated the relative abundances, we obtained predictions from
+the model for each one of the locations and ran the Markov Chain. We started the
+chain with random values for the parameters of interest, then ran the
+computational model once for every reef site using as input the ecological
 explanatory variables. The model outputs the probability of choosing the visitor
 for each location \(p_i\), where \(i\) is the index for the 12 locations. Assuming a
-binomial distribution, the probability that each of the cleaners' 20 choices was
-generated by the model is given by \(\binom{n}{k_ij}p^{k_{ij}}_i (1-p_i)^{n-k_{ij}}\);
-where \(k_{ij}\) is the number of times that cleaner \(j\) in location \(i\) chose the
-visitor over the resident; and \(n=20\) (due to our choice of using 20
-choices per cleaner). By taking the natural logarithm and summing over all
-the cleaners and locations we obtain the log-likelihood of the data
-given the model and parameters. We then propose a new set of parameters drawn
+binomial distribution, the probability that each of the cleaner fish 20 choices
+in the ephemeral reward task was generated by the model
+is given by \(\binom{n}{k_ij}p^{k_{ij}}_i (1-p_i)^{n-k_{ij}}\);
+where \(k_{ij}\) is the number of times that cleaner fish \(j\) in reef site \(i\)
+chose the visitor over the resident; and \(n=20\) (due to our choice of using 20
+choices per cleaner fish). By taking the natural logarithm and summing over all
+the cleaner fish and reef sites we obtained the log-likelihood of the data
+given the model and parameters. We then proposed a new set of parameters drawn
 from a uniform distribution centred around the old parameter set. The amplitude
@@
 \ref{tab:param}. Subsequently, we ran the model and calculated the likelihood
-with the new parameter set. We then use the ratio of the two likelihoods to
+with the new parameter set. We then used the ratio of the two likelihoods to
 choose which parameter set to keep. New parameter sets with a higher likelihood
-than the old set replace old ones, and those with a lower likelihood are replace
+than the old set replaced old ones, and those with a lower likelihood replaced
 current ones with a probability equals to the log-likelihood ratio.
-Given that we only use the likelihoods in the decision, we are using a
-uninformative prior. Once we decide whether the new parameter set replaces
-the old one, we ran the model again to sample to the likelihood
-distribution of the parameter set. We then start
-the cycle again by proposing a new set of parameters, and repeat the process for
-\(1e^5\) steps. We ran 5 independent chains, discarded the first
-\(100\) samples of each chain as burn in, and after that we keep 1 in every
-100 samples to avoid autocorrelation. The collection of parameters sets kept in
-all chains approximates the posterior distribution. The model as well as the
-fitting algorithm were coded in \emph{c++}, the diagnostics and visualization were
-coded in R \citep{rcoreteam_Language_2021} of the all code can be found at
+Given that we only used the likelihoods in the decision, we used a
+uninformative prior. Once we decided whether the new parameter set replaces
+the old one, we ran the model again to sample the likelihood
+distribution of the parameter set. We then started
+the cycle again by proposing a new set of parameters, and repeated
+the process for \(1e^5\) steps. We ran 5 independent chains,
+discarded the first \(100\) samples of each chain as burn in,
+and after that we kept 1 in every 100 samples to avoid autocorrelation.
+The collection of parameters sets kept in
+all chains approximates the posterior distribution. We coded the model
+as well as the fitting algorithm in \emph{c++}, the diagnostics and visualization
+in R \citep{rcoreteam_Language_2021}. All codes are accessible at
 \(\color{red}{\text{include citation}}\)
 
-In order to compare the fit that the three alternative models give we use the
+To compare the fit of the three alternative models, we used the
 distribution of pseudo \(R^2\) proposed by Mcfadden \citep{mcfadden_Conditional_1974}.
@@
 the model, relative to the log-likelihood of the data given a
-model without covariates, as a measure of fit. Given that our
-model is not a logistic regression, we measure the \(pseudo-R^2\) in
+model without covariates, as a measure of fit. Our
+model is not a logistic regression, therefore we measured the \(pseudo-R^2\) in
 relation to the log-likelihood of a model
@@
 amounts to a model that has neutral preference between the two options.
-Pseudo \(R^2\) was calculated for all the samples of the posterior gotten from
-the MCMC. Thus, we use these distributions of pseudo \(R^2\)'s as a measure of
+We computed the pseudo \(R^2\) for all the samples of the posterior from
+the MCMC. Thus, we used these distributions of pseudo \(R^2\)'s as a measure of
 fit.
@@
 \caption{Posterior distributions for parameter values $\gamma$, $\eta$ and the scaling constant.
-We show the kernel density estimates, below the mode (black point) and the 65\% (light blue) and 95\% (grey)  highest posterior density interval for the three paramteres.
-On the left (panels a, c and c) posterior distributions for a model with all three parameters; while on the right (b and d) a model without negative reward.
+We show the kernel density estimates, below the mode (black dot) and the 65\% (light blue shade) and 95\% (grey shade)  highest posterior density interval for the three paramteres.
+On the left, panels a, b and c show posterior distributions for a model with all three parameters; while on the right, d and e, show a model with only chaining.
 Panel f shows a measure of fit for both models, namely the distribution of pseudo-$R^2$ obtained from sampling the posterior distribution of parameter values.}\label{fig:post}
@@
 
-Figure \ref{fig:post} panels a,c and e show the posterior distributions
-of the parameter values of the full model, which includes both future
-and negative reward. Posterior distributions show the probability
+Figure \ref{fig:post} panels a,b and c show the posterior distributions
+of the parameter values of the full model, which includes both chaining
+and operant conditioning (negative reward). Posterior distributions show the probability
 density (y axis) of the estimated parameter values (x axis). Notably,
 the bulk of the posterior distribution for the parameter tuning negative
-reward (\(\eta\) panel e) is around zero. Thus, the shape of the posterior
+reward (\(\eta\) panel b) was around zero. Thus, the shape of the posterior
 and its credible intervals suggest the absence of negative reward to be
@@
 also includes zero, but the mode of the posterior is around 0.5. Thus,
-we run the analysis setting \(\eta\) to zero. Figure \ref{fig:post} panels
-b and d, show the posterior distributions of the two parameters
+we ran the analysis setting \(\eta\) to zero. Figure \ref{fig:post} panels
+d and e, show the posterior distributions of the two parameters
 estimated. Not surprisingly, under a model without negative reward, the
-distribution of \(\gamma\) shifts to higher values. Under the new model,
-the estimates of \(\gamma\) do not include zero and the distribution is
-centered around \(0.5\). In panel f of figure \ref{fig:post}
+distribution of \(\gamma\) shifted to higher values. Under the new model,
+the estimates of \(\gamma\) did not include zero and the distribution was
+centred around \(0.5\). In panel f of figure \ref{fig:post}
 we show the distribution of \(pseudo-R^2\) calculated using
@@
 as well as from a model with negative reward but without
-future reward. Note, \(pseudo-R^2\) can have negative values, that is when
+future reward. Note, \(pseudo-R^2\) can have negative values, which is when
 the log-likelihood of the model is lower than that of a model that
 triggers neutral preferences. Even though, the peak of the three
-\(pseudo-R^2\) distributions is not very different, the model with only
-future reward produces a distribution of \(pseudo-R^2\) where more values
-are positive (to the right of black line in Fig. \ref{fig:post} f). This
+\(pseudo-R^2\) distributions was not very different, the model with only
+future reward produced a distribution of \(pseudo-R^2\) where more values
+were positive (to the right of black line in Fig. \ref{fig:post} f). This
 shows that, accounting for variation in the parameter estimates, the
@@
 Left-hand side panel: color contour shows the prediction of the learning model using the mode of the posterior distributions of parameters recovered by the statistical analysis.
-Dots show the frequency of visitor choices for the 12 locations, as well as the corresponding relative cleaner abundance (x axis) and frequency of visitors leaving the station (y axis).
-Right-hand side panels: Variation of the predicted probabilites  of choosing a visitor and their observed values for 12 locations.
-Circles show the mean prediction for each location from 100 samples taking from the posterior distribution.
-Thick and thin bars show the 66 and 95\% credible interval taken from those posterior samples.
+Dots show the frequency of visitor choices for the 12 reef sites, as well as the corresponding relative cleaner fish abundance (x axis) and frequency of visitors clients leaving the cleaning station (y axis).
+Right-hand side panels: Variation of the predicted probabilites  of choosing a visitor over a resident and their observed values for 12 locations.
+Circles show the mean prediction for each location from 100 samples taken from the posterior distribution.
+Thick and thin bars show the 66 and 95\% credible interval, respectively, taken from those posterior samples.
 Squares show the predictions used for panel on the righ-hand side.
-Colour denotes different locations (see Empirical data section).
-Black line correspond to a perfect match between observed and predicted probabilities.
-Upper panels show prediction from a model including future and negative reward, lower panels from a  model with only future reward.}\label{fig:pred}
+Colour coding denotes different reef sites/year of the data collection (see Empirical data section).
+Black line corresponds to a perfect match between observed and predicted probabilities.
+Upper panels show prediction from a model including chaining and operant conditioning, lower panels from a  model with only chaining.}\label{fig:pred}
 \end{figure}
 
-Figure \ref{fig:pred} shows predictions from the two models. On the
+Figure \ref{fig:pred} shows predictions from the two models,
+one including chaining and operant conditioning (upper panels) and
+one with only chaining (lower panels). On the
 left, the colour coded contour shows the prediction of the model for
-combinations of cleaner abundance (x axis) and visitor leaving
+combinations of cleaner fish abundance (x axis) and visitor leaving
 probability (y axis). Predictions were generated by running the model
 using the mode of the posterior distributions as the parameter values,
-and varying systematically cleaner abundance and visitor leaving
-probability. Colour of the points on top of the contour show the average
+and varying systematically cleaner fish abundance and visitor leaving
+probability. Colour of the dots on top of the contour show the average
 frequency with which cleaner fish chose the visitor plate in their last
-20 experimental trials. Each point corresponds to a location with a
-combination of cleaner abundance and visitor leaving probability. Panels
+20 experimental trials. Each dot corresponds to a reef-site/year of
+data collection with a combination of cleaner fish abundance
+and visitor leaving probability. Panels
 on the right show how close the observed values for the probability of
-choosing the visitor (y axis) are from the predictions of the models (x
+choosing the visitor (y axis) were from the predictions of the models (x
 axis). The black line represents the perfect fit between observed and
@@
 parameter varying, the full model
-gives a lower fit to the data than the model without negative reward.
+gave a lower fit to the data than the model without negative reward.
 In the supplementary material, we also show predictions from
@@
 clients on all three models (Fig. \ref{fig:pred}, \ref{fig:nogamma}). In
-contrast, cleaner's relative abundance has a different effect in the
-model with only future reward, compared to the other two. In the model
-with only future reward only intermediate cleaner abundance triggers a
+contrast, cleaner fish relative abundance has a different effect in the
+model with only chaining, compared to the other two models,
+full model and only operant conditioning. In the model
+with only chaining, only intermediate cleaner fish abundance triggers a
 preference for the visitor clients (Fig. \ref{fig:pred} c). In models
 with negative reward, both intermediate and low cleaner abundance
-trigger a preference for the visitor. (Fig. \ref{fig:pred} a,
+triggered a preference for the visitor. (Fig. \ref{fig:pred} a,
 \ref{fig:nogamma}).
@@
 
-We asked which if two potential cognitive mechanisms
--- chaining of events, negative reinforcement, or a combination of both --
-is the more likely mechanism to explain intra-specific variation in cleaner
-performance in the ephemeral reward task as a function of ecological
-conditions in the wild. To evaluate the merits of the alternative mechanisms,
-we considered performance in the task to depend on decision-rules that
-cleaners had developed in their natural environment: individuals that
-solved the task did so because they already had a general preference for
-visitors, and applied this rule once being familiar with the task.\\
-While all three models capture well the positive relation between visitor
+In this study, our main aim was to unravel which of two potential
+cognitive mechanisms, chaining of events, operant conditioning,
+or their combination, best explains wild-caught cleaner fish
+performance in the ephemeral reward task, while accounting for their
+ecological conditions. To evaluate the merits of each of these two mechanisms
+separately and combined, we considered cleaner fish performance
+in the lab test to have its origin from the these fish apply
+in their natural environment. That is, individuals that
+solved the task already had a preference for
+visitors clients, and generalized this rule to the lab conditions
+once being familiar with the task.
+
+While all three models captured well the positive relation between visitor
 leaving behaviour and cleaner performance in
 the market task \citep{triki_Biological_2019}, only the chaining mechanism
-predicts that cleaner performance in the task should be low if their
-local abundance in the wild relative to clients is low. Indeed, such low
-performance is predicted regardless of the visitor leaving
-probability. In contrast, a model with negative reward predicts the
-highest performance in the ephemeral reward task when relative
-cleaner abundance is low, particularly
+predicted that cleaner fish performance in the task should be low in
+habitats with low cleaner-to-client ratios, regardless of the
+visitor leaving probability. In contrast, models including
+negative reward predicted the highest performance in the ephemeral
+reward task when relative cleaner abundance is low, particularly
 together with high probability of visitor leaving (Fig. \ref{fig:pred}).
-Low cleaner abundances mean the market has an excess of demand for
-cleaning services. In the model, this translates to a cleaning station
-that is frequently full. Thus, when visitors leave, it's likely that the
-cleaner will have access to another client in the next step. Therefore,
+Low relative cleaner fish abundances mean the market has an excess of demand for
+cleaning services. In the models, this translates to a cleaning station
+that is frequently full. Thus, when a visitors leaves, it is likely that the
+cleaner fish will have access to another client in the next step. Therefore,
 there will not be much difference in future reward between choosing
@@
 visitor in these conditions. On the other hand, the effect of negative reward
-would be opposite as in a full station, cleaners will get more often the
-heterotypic (resident-visitor) option and will develop a preference for
-the visitor faster. Note that when cleaner abundance is high situations
-with a resident and a visitor will be so rare that neither mechanism
-will be very efficient in generating a preference for visitors. When
-such choice arises it is still be best to choose the visitor; however,
+on cleaner fish preference is the opposite, as in a busy cleaning station, to
+that of chaining. cleaner fish will get more often the resident-visitor
+state and will develop a preference for the visitor faster.
+At high cleaner fish abundances, the resident-visitor state
+becomes so rare that neither mechanism is very efficient
+at generating a preference for visitors. When facing the resident
+visitor choice it is still be best to choose the visitor; however,
 the learning machinery will not be able to develop this preference
-efficiently. Overall, estimation of future reward is then the cognitive
-mechanism that allows cleaners to adaptively respond to the
-ecological conditions of the biological market.
+efficiently. Overall, the models suggest that chaining is the cognitive
+mechanism that allows cleaner fish to adaptively adjust to their
+biological market ecological conditions.
 
 Our results support chaining as the more plausible mechanism behind the
-inter-specific variation in cleaners' performance, which is also
-the mechanism that allows them to respond more adaptively. This could
-suggest chaining to be under positive selection. In the standard ephemeral
-reward task, however, food amount and quality are equal between the
-two plates. An given that models resemble this, choosing visitors over
-residents in low cleaner abundances does not diminish the
-amount of food/reward in the the models.
-On the other hand, a cleaner committed to visitors might find more difficult
-to include in the decision making other variables, like parasite load
-and/or mucus quality, that do predict the amount of food in the field
-\citep{roche_Client_2021}. In nature and in laboratory experiments, cleaners prefer
-higher quality mucus and more food in the absence of market effects
-(i.e.~in simultaneous 2-choice options,
-\citep{triki_Fluctuations_2019, grutter_Cleaner_2004}), and they use size as a
-proxy for food availability \citep{wismer_Cuebased_2019, grutter_Does_2005}.
+inter-specific variation in cleaners' performance. This suggest
+that chaining could be under positive selection. In the standard ephemeral
+reward task, however, food amount and quality are equal in the
+two Plexiglas plates. Since our computational models simulate this aspect of
+the task, choosing visitors over residents at low cleaner fish abundances
+does not diminish the amount of food/reward in the models.
+On the other hand, a cleaner fish committed to visitors might find it more difficult
+to include in its decision making other variables, like parasite load
+and/or mucus quality \citep{roche_Client_2021}. Indeed, in the absence of
+market effects, both field observations and aboratory experiments also
+using simultaneous two choice options, show that cleaner fish base their
+decision-making on other cues such as the mucus quality and the amount of food.\\
+\citep{triki_Fluctuations_2019, grutter_Cleaner_2004}, as well as client size
+as a proxy for food quantity \citep{wismer_Cuebased_2019, grutter_Does_2005}.
 How important this limitation is will determine whether chaining yields a higher
@@
 
-Individual cleaners that performed in the laboratory test according to what
-is best at their site of capture (low performance when living at low densities,
-high performance when living at high densities) had larger forebrains
-harbouring more cells than individuals whose performance mismatched locally
-optimal decision-rules \citep{triki_Brain_2020}. Triki \emph{et al.} refer to the
-former as socially competent cleaners. Social competence refers to the
-ability to optimise social behaviour depending on the available social
-information \citep{taborsky_Social_2012a, bshary_Cooperation_2015, varela_Correlated_2020}. Our analyses yielded no
+Previous research showed that cleaner fish living at high population
+densities and giving service priority to the visitor plate in the
+ephemeral reward task, as well as cleaner fish living at low
+densities but denying service priority to the visitor plate possess
+larger forebrains; a key teleost brain region associated with
+behavioral flexibility and social intelligence. Those failing to
+show optimized decision-rules given their local ecological
+conditions had relatively smaller forebrains \citep{triki_Brain_2020}.
+Triki \emph{et al.} refer to the former as socially competent cleaner fish,
+while the second group as socially incompetent cleaner fish.
+Social competence is the ability to optimise social behaviour
+to the available social information \citep{taborsky_Social_2012a, bshary_Cooperation_2015, varela_Correlated_2020}. Our analyses yielded no
 evidence that the difference in social competence with respect to the local
-market conditions and associated brain morphology are due to the mechanism
+ecological conditions and associated brain morphology,
+found by Triki \emph{et al} \citep{triki_Brain_2020}, are due to the mechanism
 used to incorporate future consequences. It could have been conceivable that
-high performing individuals from low-density sites might use negative
-reinforcement instead of chaining, but in that case negative reinforcement
-should have explained part of the data. Configurational learning or
-chunking \citep{sutherland_Configural_1989, miller_Magical_1956}, the second component
-necessary to solve the ephemeral reward task \citep{quinones_Reinforcement_2019}, was
-not varied in the models analized here. However, while chunking tendencies
-should vary to allow individuals to adapt to local conditions
+high performing individuals from low population densities reef sites
+might use negative reinforcement instead of chaining, but in that
+case negative reinforcement should have explained at least
+part of the data. Configurational learning or
+chunking \citep{sutherland_Configural_1989, miller_Magical_1956},
+the second component necessary to solve the ephemeral
+reward task \citep{quinones_Reinforcement_2019}, was
+not varied in the models we analized here. However, while chunking tendencies
+should vary to allow individuals to adapt to their local conditions
 \citep{prat_Modelling_2022, kolodny_Evolution_2014}, systematic differences
@@
 
-The model is inspired by the general processes of associative learning
-where short term rewards are translated to decision making; thus, it
+Our models are inspired by the general processes of associative learning
+where short term rewards are translated into decision making; thus, it
 ignores alternative channels of information that could be relevant in
 market-like situations. For example, the model does not investigate whether
-cleaners actually assess the frequency of client visits or a mean frequency
+cleaner fish actually assess the frequency of client visits or a mean frequency
 of visitors leaving. The updating learning mechanism for the development
-of preferences works on a trial by trial basis. In the model, cleaners
-do not need to assess the actual state of the market, \emph{i.e.} their density,
-the density of residents and visitors, and client visitation rate as an
-indicator of demand. They only need to assess short-term consequences of
-own decisions on food intake and chain them. Also, for the sake of
-simplicity, the model ignores the process by which cleaners discriminate
+of preferences works on a trial-by-trial basis. In the model, cleaner fish
+do not need to assess the actual state of the market, \emph{i.e.} their abundance,
+the abundance of residents and visitors, and client visitation rate as an
+indicator of demand. They only need to assess short-term consequences of their
+own decisions on food intake, and chain them. Also, for the sake of
+simplicity, the model ignores the process by which cleaner fish discriminate
 residents and visitor clients. A model that accounts for this discrimination
-probably involves the development of preferences for morphological or
+probably would involve the development of preferences for morphological or
 behavioural features that are statistically associated with visitors
-or residents. For example, visitors are on average larger larger
-than residents \citep{bshary_Cleaner_2001a}, and are less likely to chase
-cleaners in response to the latter cheating by taking a bite of
-mucus \citep{bshary_Asymmetric_2002}. Given these associations, chaining might
-produce the decision-rule ``chose the larger client and/or less aggressive
-client'', which does not help in the standard ephemeral reward task.
+or residents. For example, visitors are on average larger
+than residents in body size \citep{bshary_Cleaner_2001a}, and contrary to
+resindents, are less likely to chase a cleaner fish that fails to cooperate
+and intead cheats its client by taking a bite of mucus
+\citep{bshary_Asymmetric_2002}. Given these associations, chaining might
+produce the decision-rule ``choose the larger client and/or the less aggressive
+client'', which is not a useful rule in the standard ephemeral reward task.
 
 In conclusion, our study shows that variation in cognitive performance as
-a function of ecological factors may set the stage for the use of
+a function of the local ecological conditions may set the stage for the use of
 mechanistic modelling to identify the cognitive processes underlying
@@
 of the general philosophy in animal cognition to apply the logic of
-Lloyd Morgen's canon (Occam's razor). Excluding basic
-reinforcement learning explanations (operant and/or classical conditioning)
-as a potential explanation in experiments
-often warrants animals solving the task on the first possible occasion.
+Lloyd Morgen's canon (Occam's razor). Cognitive experiments with the
+aim of excluding basic reinforcement learning as a potential
+explanation (operant and/or classical conditioning) of performance
+often employ one trial experiments requiring animals to solve the
+task on the first possible occasion.
 For example, any theory of mind task needs to be solved in the first
@@
 \citep{hirata_SweetPotato_2001}). In our case, the number of trials it took
-cleaners to learn the solution to the market task would never allow to
-exclude an important role of negative reinforcement based on the data
-alone. However, fitting model predictions to our data set revealed that
-a more complex mechanism (estimation of future reward) fits the data
-better.
+cleaners to learn the solution to the ephemeral rewards task
+would never allow to exclude an important role of
+negative reinforcement based on the data
+alone. However, fitting model predictions to our comprehensive empirical
+data set revealed that a more complex mechanism, estimation of future reward,
+fits the data better.
 
@@
 
-\caption{Observed and predicted probability of choosing a visitor for a model without future rewards.
+\caption{Observed and predicted probability of choosing a visitor for a model without chaining.
 Left-hand side panel: color contour shows the prediction of the learning model using the mode of the posterior distributions of parameters recovered by the statistical analysis.
-Dots show the frequency of visitor choices for the 12 locations, as well as the corresponding relative cleaner abundance (x axis) and frequency of visitors leaving the station (y axis).
-Right-hand side panel: Right-hand side panels: Variation of the predicted probabilites  of choosing a visitor and their observed values for 12 locations.
+Dots show the frequency of visitor choices for the 12 reef sites, as well as the corresponding relative cleaner fish abundance (x axis) and frequency of visitors leaving the station if being made to wait (y axis).
+Right-hand side panel: Right-hand side panels: Variation of the predicted probabilites  of choosing a visitor and their observed values for 12 reef sited.
 Circles show the mean prediction for each location from 100 samples taking from the posterior distribution.

### 2022-02-16 manuscript_1.0/manuscript_word.Rmd
Fixed data files. Updated the cpp to g++ compilation. new parameter files to run chains with the fixed data files. Update figures in the manuscript

--- 2022-01-14 manuscript_1.0/manuscript_word.Rmd
@@
 spacing: double
-abstract: "While it is generally straightforward to quantify individual performance
-  in cognitive experiments, identifying the underlying cognitive processes remains
-  a major challenge. Often, different mechanistic underpinnings may yield similar
-  performances, and Lloyd Morgan’s cannon warrants acceptance of the simpler explanation.
-  Alternatively, when the different mechanisms interact with environmental conditions,
-  variation in performance across environments might allow to statistically infer
-  the mechanism responsible. However, to do this it is necessary to have quantitative
-  predictions for the different candidate mechanisms. Here, we use a set of computational
-  models to get quantitative predictions from alternative learning mechanisms, and
-  using Bayesian statistics fit the model parameters to performance data. We used
-  experimental data on performance in an ephemeral reward task by wild-caught cleaner
-  fish Labroides dimidiatus, as well as cleaner and client fish densities from the
-  locations of capture. The task can in principle be solved by estimating future consequences
-  of an action, or by perceiving the removal of the ephemeral reward as psychological
-  punishment (negative reinforcement). We found that a model where cleaners only estimate
-  the future consequences of their actions explains best which cleaner relative abundances
-  cause the fish to develop a preference for an ephemeral food source. This model
-  also yields performances that can be considered the result of locally optimal decision-rules,
-  in contrast to the negative reinforcement model.  We argue that the combination
-  of computational models with data is a powerful tool to infer the mechanistic underpinning
-  behind cognitive performance. \n"
+abstract: |
+  While it is generally straightforward to quantify individual performance in cognitive experiments, identifying the underlying cognitive processes remains a major challenge.
+Often, different mechanistic underpinnings yield similar performances, and Lloyd Morgan’s cannon warrants acceptance of the simpler explanation.
+Alternatively, when the different mechanisms interact with environmental conditions, variation in performance across environments might allow to statistically infer the mechanism responsible.
+However, to do this it is necessary to have quantitative predictions for the different candidate mechanisms.
+Here, we use a set of computational models to get quantitative predictions from alternative learning mechanisms, and using Bayesian statistics fit the model parameters to performance data.
+We used experimental data on performance in an ephemeral reward task by wild-caught cleaner fish *Labroides dimidiatus*, as well as cleaner and client fish densities from the locations of capture.
+The task can in principle be solved by estimating future consequences of an action, or by perceiving the removal of the ephemeral reward as psychological punishment (negative reinforcement).
+We found that a model where cleaners only estimate the future consequences of their actions explains best which cleaner relative abundances cause the fish to develop a preference for an ephemeral food source.
+This model also yields performances that can be considered the result of locally optimal decision-rules, in contrast to the negative reinforcement model.
+We argue that the combination of computational models with data is a powerful tool to infer the mechanistic underpinning behind cognitive performance.
 keywords: learning, behaviour, cleaners, bayesian statisitics
@@
 
-Cooperation among individuals of the same or different species is
-ubiquitous in nature. Whenever such interactions involve some degree 
-of partner choice, biological market theory predicts that the exchange 
-rate of goods and/or services traded adjusts to the law of supply and demand 
-[@noe_Biological_1995a]. While biological market models have largely focused 
-on evolutionary time scales [@noe_Biological_1994a;@johnstone_Mutualism_2008a] 
-$\color{red}{\text{Hoekstra xxxx}}$, supply and demand conditions, which typically 
+Disentangling the mechanistic underpinnings of behaviour 
+is typically done under controlled conditions in a laboratory setting. However, 
+controlled laboratory conditions often mask the inter and intra-specific 
+variation that arises in the interaction between mechanisms and 
+environmental variation. From a evolutionary perspective, mechanisms 
+are likely selected because of how they allow individuals to respond to 
+environmental variation. For example, biological market theory predicts that 
+the exchange rate of goods and/or services traded between cooperative 
+partners adjusts to the law of supply and demand, when individuals have 
+some degree of partner choice [@noe_Biological_1995a]. 
+Supply and demand conditions, which typically 
 depend on the abundance of the species involved, certainly vary in time 
-and space within ecological time scales. Therefore, natural selection should 
+and space. Therefore, natural selection should 
 favour the ability to flexibly adjust decisions and behavioural output to 
 current market conditions. Indeed, such adjustments have been repeatedly 
-documented [@axen_signalling_1996]. In animals, an obvious general candidate 
+documented [@axen_Signalling_1996]. In animals, an obvious general candidate 
 mechanism for the strategic adjustment is the cognitive machinery. However, 
 it is not clear which cognitive mechanisms allow individuals to adjust their 
-behaviour to the varying market conditions. As adjustments to changes in 
+behaviour to the varying conditions. As adjustments to changes in 
 market conditions have been documented in a great variety of species with 
@@
 cleaning mutualism involving the cleaner fish *Labroides dimidiatus* and
-'client' fish. Clients offer themselves as food patches for cleaners to
-remove ectoparasites, which gives the cleaners calories and the clients
-improved health [@waldie_LongTerm_2011;
-@ros_Does_2011;@triki_Effects_2016]. As cleaners have about 2000
-interactions per day [@grutter_Relationship_1995], they regularly face
-the situation that two clients seek cleaning simultaneously. In such
-conditions, it is important to distinguish between 'resident' and
-'visitor' client species [@bshary_Cleaner_2001a]. The residents have
-small home ranges and hence access to only the local cleaner, while the
-visitors have large home ranges and hence access to two or more
-cleaners. Thus, visitors have the option to switch to another cleaner if
-being made to wait, while residents must wait for inspection. Indeed,
-visitors have been observed to use their partner choice options in that
+'client' fish. Client fish seek cleaner fish services at their territory 
+(so-called “cleaning station”) and offer themselves as food patches 
+to get their ectoparasites removed, which provides cleaners 
+with food and clients with improved health [@waldie_LongTerm_2011;
+@ros_Does_2011;@triki_Effects_2016;@demaire_Reduced_2020]. 
+Given the capacity of some client fish to swim larger distances and 
+access multiple cleaning stations while others access the only cleaning 
+station at their territory, it is crucial to categorize clients as 
+either “visitors” or “residents”, respectively. During cleaning interactions, 
+a cleaner fish often face a choice between a visitor and a resident client 
+seeking its cleaning services simultaneously. Visitors have the option 
+to switch to another cleaner fish if being made to wait, while residents 
+must wait for inspection. Indeed,
+visitors have been observed to use their partner choice option in that
 way [@bshary_Choosy_2002], which may explain why cleaners give
 visitors service priority in a field study in the Red Sea
-[@bshary_Cleaner_2001a]. More generally, cleaners apparently prefer to
-interact with visitors [@triki_Marine_2021]. Such a preference may be
-linked to a client's value as a food patch; visitors are on average
-larger than residents [ @bshary_Cleaner_2001a], and size is positively
-correlated with parasite load [@grutter_Relationship_1995a]. However, 
-early laboratory experiments showed that leaving causes service 
-priority independent of client value [@bshary_Asymmetric_2002]. 
-The experiments consisted of asimultaneous two-choice task, 
-where cleaners had to decide which of two
-Plexiglas plates, which offered equal amounts of food, to approach first
-and eat mashed prawn of it. One plate was made to behave like a
-resident, i.e. it would remain until the cleaner had eaten off it. The
-other plate was made to behave like a visitor, i.e. it would be removed
-if not inspected first. Cleaners learned to prefer the visitor plate and
+[@bshary_Cleaner_2001a].
+
+When researchers aimed at testing wild-caught cleaner fish, as 
+well as individuals from other species, abilities 
+to prioritize visitor over resident clients in a lab-based paradigm, 
+they used Plexiglas plates of different colours and shapes offering same 
+amount of food as surrogates for visitor and resident clients.
+One plate is made to behave like a resident, i.e. it remains until 
+the cleaner had eaten off it. The other plate was made to behave 
+like a visitor, i.e. it is removed if not inspected first.
+Cleaners learned to prefer the visitor plate and
 hence obtained the double amount of food [@bshary_Asymmetric_2002].
-Adult cleaner fish outperform various primates as well as rats and
+Furthermore, adult cleaner fish outperformed various primates as well as rats and
 pigeons in this original version of the biological market task
-[@salwiczek_Adult_2012; @zentall_Early_2017]; only African grey
-parrots solve this task as well [@pepperberg_Can_2014]. As the correct 
-solution must be learned, and primates are known to readily distinguish 
+[@salwiczek_Adult_2012; @zentall_Early_2017]; yet the African grey
+parrots solve this task as well [@pepperberg_Can_2014]. Given that primates 
+are known to readily distinguish 
 between one and two reward units if presented in more conventional ways 
-$\color{red}{\text{ref}}$, what makes the task difficult for most non-cleaners?
+$\color{red}{\text{ref}}$, this raises the question:
+what makes the task difficult for most non-cleaners?
 
-Recent research on the cognitive tool kit needed to solve an ephemeral 
-reward task has used a broad approach as proposed by @shettleworth_Cognition_2009, 
-who defined cognition as includes all ways in which animals take in information 
-through the senses, process, retain and decide to act on it. Indeed, perception 
-of relevant cues is of major importance for individual performance; 
-i.e. what relevant information is encoded in the design of the two 
-plates (colour versus size; [@wismer_Cuebased_2019]), or whether 
-the information is in the colour of
-the food [@pretot_Comparative_2021; @pretot_Comparing_2016], and
-whether the food is visible or hidden/released only when the subjects
-made choices on a touch screen [@pretot_Factors_2016]. However, identifying 
+Recent research on the cognitive tool kit needed to solve the ephemeral 
+reward task has used a broad approach as proposed by Shettleworth 
+[@shettleworth_Cognition_2009], who defined cognition as including 
+all ways in which animals acquire information 
+through the senses, process, retain and decide to act on it. 
+Indeed, perception of relevant cues is of major importance 
+for individual performance. For example, some animals find relevant 
+information in the plates 
+ [@wismer_Cuebased_2019] while others find it in the food 
+[@pretot_Comparative_2021; @pretot_Comparing_2016]. However, identifying 
 cues as salient is not the only challenge of the ephemeral reward task, 
@@
 reward task, learning models showed that basic reinforcement learning does 
-not suffice to solve the task [@prat_Modelling_2022; @quinones_Reinforcement_2019]. 
+not suffice to solve the ephemeral reward task [@prat_Modelling_2022;
+@quinones_Reinforcement_2019]. 
 This is particularly so when models assume the more complex natural 
-situation in which cleaners not only face resident-visitor pairs but also 
-visitor-visitor and resident-resident pairs, as well only a resident or 
-only a visitor. To be able to give visitors priority over residents, 
+situation in which cleaner fish not only face resident-visitor pairs but also 
+visitor-visitor and resident-resident pairs, as well a resident alone or 
+a visitor alone. To be able to give visitors priority over residents, 
 cleaners need to be able to assess a client’s value separately for the 
-three possible forms of encounter (alone, paired with a fish with the 
+three possible scenarios (alone, paired with a fish with the 
 same strategic option, paired with a fish with the alternative strategic option) 
-[@quinones_Reinforcement_2019]. The ability to keep such separate scores 
-for the same stimulus has been termed configurational learning, 
-or chunking, or segmentation (see references in @prat_Modelling_2022).
+[@quinones_Reinforcement_2019]. The ability to distinguish and value differently
+one stimulus alone from compound versions of it has been termed 
+configurational learning, or chunking, 
+or segmentation (see references in [@prat_Modelling_2022]).
 
-To solve the ephemeral reward task, cleaners also need to account for 
+To solve the ephemeral reward task, cleaners need to account for 
 the future consequences of current decisions. In the model by 
-Quiñones et al. @quinones_Reinforcement_2019, this could be achieved in 
+Quiñones *et al.* [@quinones_Reinforcement_2019], this could be achieved in 
 two non-mutually exclusive ways: through low temporal discounting of 
@@
 
-### Overview
+<!-- ### Overview -->
 
-We used the data from [@triki_Biological_2019] to fit the parameters of
-the model analysed in [@quinones_Reinforcement_2019]. For the bayesian
-fitting procedure we used Markov Chain Monte Carlo (MCMC) with a
-Metropolis sampler to estimate the posterior distribution of the model
-parameters. The data consist a of the number of times that a set of
-cleaners chose to feed of a visitor client plate in the context of the
-market task. This set of cleaners were collected in different locations
-and in each one of those locations environmental variables were
-measured. These environmental variables recorded from each location are
-used as input for the computational model. Given these inputs, the
-computational model produces a time series of choices in the market
-task. In the model the preference for the two options changes as the
-algorithm learns based on the reward that the two options provide. Thus,
-we run the model for 10000 steps and use the last 3000 steps as the
-preference developed in the model for visitors given the environmental
-variables. We use this preference as the predicted probability in a
-binomial distribution to calculate the likelihood that the number of
-visitor choices obtained from each cleaner is generated by the model. We
-sum over all the cleaners the log-likehoods and use the total for the
-acceptance of new parameters in the MCMC.
+<!-- In this study, we combined empirical data from Triki *et. al*  -->
+<!-- [@triki_Biological_2019;@triki_Brain_2020] and the computational  -->
+<!-- model analysed in Quiñones *et al.*[@quinones_Reinforcement_2019]  -->
+<!-- to test the relative validity of chaining versus operant conditioning as  -->
+<!-- mechanisms to account for future consequences of cleaner fish desicion-making. -->
+<!-- In order to compare the explanatory power of the different hypotheses,  -->
+<!-- we estimated the parameter values of three versions of  -->
+<!-- the model that best fit the empirical data.  -->
+<!-- Particularly, we fitted the parameter that determines how important  -->
+<!-- future reward is ($\gamma$), the magnitude of the negative reward  -->
+<!-- ($\eta$) and a scaling constant that translates cleaner fish absolute  -->
+<!-- to relative population abundances (see following sections for details).  -->
+<!-- We obtained the model predictions using a set of stochastic individual-based -->
+<!-- simulations. Thus, each parameter combination of the model yielded not one  -->
+<!-- but a distribution of predictions. For the  -->
+<!-- fitting procedure, we used the bayesian inference algorithm:  -->
+<!-- Markov Chain Monte Carlo (MCMC). MCMC is a stochastic algorithm that allows -->
+<!-- to sample from the posterior distribution of model parameter values. The posterior -->
+<!-- distribution represents the most likely parameter values given the data.  -->
+<!-- Due to the stochastic nature of MCMC, which repeatedly samples parameter values -->
+<!-- and evaluates their likelihood, the distribution of likelihoods from the  -->
+<!-- stochastic model is also explored. This makes MCMC and bayesian inference -->
+<!-- particularly suitable for the computational models we evaluate. Bellow,  -->
+<!-- we explain first the computational model and the data collection, and later  -->
+<!-- how the MCMC was used to estimate parameter values. -->
 
@@
 
-The model consist of a set individual-based simulations where
-individuals face a series of choices between two options. Individuals in
-the model represent cleaners, and the options they face simulate the
-natural conditions of a cleaning market. Thus, individuals in the model
-choose to prioritize different clients. These clients are classified as
-resident and visitors. Residents are those clients that stay in the
-cleaning queue when they are not given priority; while visitors leave
-the queue (with a certain probability) after they are not given
-priority. Individuals obtain a fixed reward from cleaning a client
-regardless of the type. Every time individuals face and make a choice
+The model consists of a set individual-based simulations where
+individuals, representing cleaners, face a series of choices 
+between two options, which simulate the natural conditions 
+of the cleaning market. Individuals experience a series 
+of discrete time points in which they face different ‘states’, 
+defined by the number and category of client fish (visitor or residents) 
+inviting for cleaning services. There are six possible states: 
+zero clients, one resident, one visitor, 
+resident-resident, visitor-visitor, and resident-visitor. 
+The probability of each state is largely determined by the relative 
+abundance of cleaner fish, residents and visitors, but to some degree by
+cleaner fish choices when it faces the resident-visitor combination. 
+This is because residents are willing to queue for cleaning service; 
+while visitors leave the queue (with a certain probability) when made to wait. 
+Individuals obtain a fixed reward from cleaning a client fish
+regardless of the category. Every time individuals face and make a choice
 they update the probability of making that same choice. The update is
-based on the difference between the expectation of reward and the actual
-reward the individual obtains (prediction error)
-[@sutton_Reinforcement_2018; @rescorla_Theory_1972]; and it is carried
-in the direction that would lead to more reward being obtained, given
-the new information. Further details of the model implementation can be
-found in the paper [@quinones_Reinforcement_2019]. The model analysis
-points to the relevance of two parameters. First, $\gamma$ measures how
+based on the difference between the expected reward and the obtained
+reward (prediction error) [@sutton_Reinforcement_2018; 
+@rescorla_Theory_1972]. Given the new information, the update is carried
+in the direction that leads to more reward being obtained, given
+the new information. In the long run, the probability of choosing a visitor 
+over a resident converges in the model. To which probability the model 
+will converge depends on the relative abundance of cleaners, visitors 
+and resident; as well as on the probability of visitors leaving the 
+cleaning station when made to wait. Further details of the model 
+implementation can be found in Quiñones *et al* [@quinones_Reinforcement_2019].
+
+The model shows that agents need to find a mean 
+to incorporate future consequences of current choices. In the model, 
+this could be achieved with either of two parameters that could 
+also work together.  First, $\gamma$ measures how
 much individuals include future rewards in their decision updates. If
@@
 reward obtained from the subsequent choices. That amounts to calculating
-and using for decision making the future expected rewards in action.
+and using for decision making the future expected rewards of an action.
 Second, $\eta$ measures how much individuals include in their reward the
-fleeing behaviour of visitor clients as a negative component. Both of
+fleeing behaviour of visitor as a negative component. Both of
 these parameters allow individuals to use in their estimates the future
-effects of their choices. The model analysis by Quiñones *et al*
-[@quinones_Reinforcement_2019] shows that without either of them, learning
-individuals cannot develop a preference for the visitor client. The
-analysis contrast the effect of these two parameters against variation
-in the relative abundance of the two client types. The analysis shows
-that under very high client (relative) abundance the presence of future
-rewards ($\gamma>0$) no longer favours the preference for the ephemeral
-clients, this effect does not occur with negative reward mediated by
-client behaviour ($\eta$). Thus, the analysis suggests that future
-reward as an explanation for cleaner ability to prefer visitors is
-supported by Triki *et al* [@triki_Biological_2019] data. However, a combination of
-future and negative rewards, could still be a better explanation for the
-data. In the current analysis, we will use the data from
-[@triki_Biological_2019] to fit some of the model parameters, particularly
-relevant we will fit $\gamma$ and $\eta$ to find out whether each or a
-combination of these effects is a better explanation for the pattern
-seen in the data. For other parameter values used for the model
-simulations and the MCMC see Table \ref{tab:param}
+effects of their choices.
 
-### Data explanation
+<!-- A further model analysis contrast the effect of these two  -->
+<!-- parameters against variation in the relative abundance of cleaners  -->
+<!-- and the two client types. Assuming certainty that visitors leave, the  -->
+<!-- two parameters yield different  -->
+<!-- predictions when relative client abundance is very high. Under such  -->
+<!-- conditions, the analysis shows that under very high client (relative)  -->
+<!-- abundance the presence of future rewards ($\gamma>0$) no longer favours  -->
+<!-- the preference for the ephemeral clients, while the preference persists  -->
+<!-- when the negative reward mediated by client behaviour ($\eta>0$) is  -->
+<!-- included. Thus, the analysis suggests that future reward as an  -->
+<!-- explanation for cleaner ability to prefer visitors is supported.  -->
+<!-- At first sight, empirical data seem to support future rewards as  -->
+<!-- the mechanism used by cleaners, as the statistical analysis  by  -->
+<!-- Triki *et al.* [@triki_Biological_2019] data revealed that low  -->
+<!-- cleaner-to-client ratios predict low preference for visitors and hence  -->
+<!-- low performance in the ephemeral reward task. However, low cleaner-to-client  -->
+<!-- ratios may also lead to low probabilities of visitors leaving, which would  -->
+<!-- cause low preferences for visitors independently of the underlying  -->
+<!-- mechanism [@quinones_Reinforcement_2019]. Furthermore, a combination  -->
+<!-- of future and negative rewards, could still be yield a better explanation  -->
+<!-- for the data than any single factor.  -->
 
-*Insert here brief description of the data and data collection*
+### Empirical data
 
-In order to capture with the model the relationship between the
-characteristics of the market (environment) and the cleaner's
-performance we need to translate the absolute abundances of the data to
-to  a measure of relative abundances that captures client visitation patterns.
-This is because in the model, relative abundances
-of clients define not only the probability of residents and visitors,
+The empirical data were collected between 2010 and 2019 always during 
+the austral winter months June to August from a total of five 
+study reef sites (Corner Beach-CB, Horseshoe-HS, Mermaid Cove-MC, 
+Northern Horseshoe-NHS, and The Crest-TC)  at Lizard Island 
+($14.6682° S, 145.4604° E$), Great Barrier Reef, Australia. 
+The data consist of three sets: fish censuses, field 
+observations of cleaner-client interactions to quantify the probability 
+of visitors leaving if made to wait, and the 
+performance of wild-caught cleaner fish in the ephemeral reward test. 
+In total, we have twelve site/year data sets for fish censuses and 
+corresponding performance in the lab test. Thus, some sites were sampled more 
+than once. To estimate the population density of cleaner fish 
+and their clients at a given site in 
+a given year, Triki *et al.* [@triki_Biological_2019] used a series of ten 
+transects of $30m$ each. Observers swam along the transect lines placed on 
+the reef and first counted the visible large-bodied adult fish 
+(species with total length $TL \geq 10cm$) including cleaner fish 
+on a width of $5m$, and then on the 
+return individuals of small-bodied fish species ($TL < 10 cm$) \
+on a width of $1 m$
+(see Triki et al. 2018 for further details on fish censuses data collection). 
+We then scaled the counts of cleaner fish, small-bodied, 
+and  large-bodied  clients fish densities per $100 m^2$. 
+From the study by Triki *et al* [@triki_Biological_2019] 
+cleaner fish and large-bodied client populations densities were 
+highly correlated, and only the former 
+was hence used in the analyses as representative of both measures.
+
+<!-- Cleaner densities, in interaction with visitor client leaving probability,  -->
+<!-- explained best individual performance in the ephemeral reward task  -->
+<!-- [@triki_Biological_2019], while cleaner-to-client ratio was not a significant  -->
+<!-- factor. This creates a certain mismatch with the model by Quiñones *et al.*  -->
+<!-- [@quinones_Reinforcement_2019], which focused on abundance of cleaners relative  -->
+<!-- to overall client abundance in order to capture the characteristics  -->
+<!-- of the market. Importantly, relative abundances of clients define not only  -->
+<!-- the probability of interactions with residents and visitors, but also affect  -->
+<!-- how often the cleaning station is empty (e.g. there are no clients to be cleaned).  -->
+<!-- The higher the relative abundance of cleaners is, the higher is the probability  -->
+<!-- of cleaning stations being empty at a given time point. How often the  -->
+<!-- cleaning stations are empty in turns influences the value that cleaners can  -->
+<!-- expect from their choices. The emptier the cleaning stations are, the more  -->
+<!-- beneficial it is to prioritize a client that will not stay. On the other hand,  -->
+<!-- situations where cleaners have to choose will be rare if cleaner relative  -->
+<!-- abundance is high, which reduces the total value of prioritizing visitors  -->
+<!-- over residents and makes it more difficult to learn a preference for visitors.  -->
+<!-- Given the model structure, we used the empirical data to calculate relative  -->
+<!-- abundances of cleaners, residents and visitors for the current analyses.  -->
+<!-- To incorporate the empirical finding that absolute densities matter, we  -->
+<!-- introduced a new scaling constant (see section on model fitting).  -->
+
+The field observation data consisted of video recordings/encodings of the 
+cleaner-client cleaning interactions. There were videos from eight 
+cleaners per site/year of a duration of $30 min$ each. Triki *et al* 
+extracted information from every event wherein a visitor client 
+was made to wait in favour of another client (visitor or resident), and noted 
+whether or not the visitor left or queued for the cleaning service
+[@triki_Biological_2019;@triki_Brain_2020].
+
+The cognitive performance data was from a total of 120 cleaners 
+(10 individuals per 12 site/year) tested in the 
+ephemeral reward task [@triki_Biological_2019;@triki_Brain_2020]. Authors 
+housed all captured cleaners individually in glass aquaria 
+( $62cm \times 27cm \times 37 cm$ ) and provided them 
+with PVC pipes ($10 cm \times 1 cm$) as shelters. 
+The task consisted of exposing the cleaner fish to substitute 
+models of client fish in the form of two *Plexiglas* plates offering the 
+same amount of food (one item of mashed prawn).  The two plates differed 
+in colour and pattern (horizontal green stripes or vertical pink stripes) 
+but had equal size ($10 cm \times 7 cm$). Importantly, the two plates played 
+different roles as either a visitor (ephemeral food source) or 
+resident (permanent food source). That is, if a cleaner inspected the 
+resident plate first, the experimenter withdrew the visitor plate out of 
+the aquarium as a consequence.  Choosing first the visitor plate, 
+however, granted access to both plates. The equal size of the plates 
+forced cleaner fish to learn to give service priority to the visitor plate 
+based solely on the behaviour-cue of the plates rather than size-cue 
+[@wismer_Cuebased_2019]. Triki *et al.* [@triki_Biological_2019;@triki_Brain_2020] 
+tested the fish for a maximum of 200 trials with 20 trials a day, 10 trials 
+in the morning and 10 trials in the afternoon. They randomized and 
+counterbalanced the plates’ spatial location (i.e. left or right) 
+between trials. Similarly, they counterbalanced the plates’ decoration 
+(colour and pattern) and the plates’ role (visitor or resident) between the 
+tested fish. In the original studies, once a fish reach a learning criterion, 
+that is, performing significantly above chance level ($> 50%$, $p-value ≥ 0.05$),
+they passed to a reversal version of the task where the roles of the 
+visitor/resident Plexiglas plates were swapped (see Triki et al. 2019, 2020). 
+Here, we used instead a subset of these data in order to have an idea on 
+cleaner fish preferences for the visitor plate, even if they do not reach 
+the learning criterion within 200 trials. To do so, we first extracted the 
+trial-by-trial outcomes from the last two session (20 trials) of those who 
+never reached the learning criterion for visitor plate 
+$\color{red}{\text{(N = XX cleaner fish)}}$. 
+For those who reached the learning criterion at some point during the 
+test and passed to a reversal phase, we extracted the trials-by-trial 
+outcomes from the last session (10 trials) before passing to reversal 
+and the last 10 trials they were exposed to in the test 
+$\color{red}{\text{(N = XX cleaner fish)}}$.
+
+### Statistical analysis
+
+The aim of the analyses is to fit the key model parameters 
+$\gamma$ and $\eta$, to the empirical data from Triki *et al.* 
+[@triki_Biological_2019;@triki_Brain_2020] to test whether each or 
+a combination of these effects is a better explanation for the pattern 
+seen in the data. We used the 
+ecological variables: cleaners, visitor clients, 
+resident clients abundances and
+visitor clients leaving probability,  as input to the models. 
+As response variable we used cleaners' preference for visitor 
+over residents in the ephemeral reward task. 
+Finally, we used the preference for visitors resulting from the 
+model simulations as the prediction for the response variable. 
+We kept all other parameter values used for the model simulations constant, 
+see Table \ref{tab:param}.
+
+To capture with the model the relationship between the ecological 
+variables and cleaner fish preferences for visitors we need to scale 
+the absolute population densities of cleaner fish from the empirical data
+to a measure of relative abundances that captures 
+client visitation patterns. This is because in the model, relative 
+abundances of clients define not only the probability of residents and visitors, 
 but also how often the cleaning station is empty (e.g. there are no 
-clients to be cleaned). The more cleaners there are, the more options
-are available for the clients and hence the higher is the probability of
-empty cleaning stations. How often the cleaning stations are empty in
-turns influences the value that cleaners can expect from their choices.
-The emptier the cleaning stations are, the more beneficial it is to
-prioritize a client that will not stay. However, the frequency of empty
-spots in the cleaning station does not only depend on cleaner abundances 
-but also on the frequency with which clients visit the
-station. The client visitation frequency will likely vary among
-different clients depending on parasite abundances and loads. These are
-variables for which we do not have field estimates. Thus, we computed a
-measure of relative cleaner abundance for each site relative to absolute
-abundances and multiplied by a scaling constant that changes the range
-of the variable. This scaling constant is meant to capture variation in the market 
-conditions driven partly by cleaner abundance. We fit the value of the 
-scaling constant as part of the
-statistical inference. As for the client abundances for residents and
-visitors we computed a relative measure with respect to the total client
-abundance, and weighted that by the rescaled relative absence of
-cleaners (1-relative cleaner abundance). Thus, all three measures of
-relative abundance sum up to 1, and can be used in the model as a proxy
+clients to be cleaned). The frequency with which clients visit the station 
+is another variable, which in nature may vary among different client species 
+depending on their ectoparasite loads. We do not have field estimates 
+for species-specific parasite loads, especially not as a function of site. 
+In order to control for these aspects, we computed a measure of relative 
+cleaner fish abundance for each reef site relative to 
+absolute abundances and multiplied it
+by a scaling constant that changes the range of the variable. This scaling 
+constant is hence meant to capture variation in the market conditions driven 
+partly by cleaner abundance. We fitted the value of the scaling constant as 
+part of the statistical inference. As for the visitor and resident 
+abundances we computed a relative measure with respect to the 
+total client abundance, and weighted that by the rescaled relative absence 
+of cleaners ($1-\text{relative cleaner abundance}$). Thus, all three measures 
+of relative abundance sum up to 1, and can be used in the model as a proxy 
 for the probability of having different options in the cleaning station. 
+Note that we introduced the scaling constant to control for variation that 
+is not captured by the model; its parameter distribution does not offer 
+biological insights.
+
+Once we calculated the relative abundances, we obtained predictions from 
+the model for each one of the locations and ran the Markov Chain. We started the
+chain with random values for the parameters of interest, then ran the 
+computational model once for every reef site using as input the ecological 
+explanatory variables. The model outputs the probability of choosing the visitor
+for each location $p_i$, where $i$ is the index for the 12 locations. Assuming a 
+binomial distribution, the probability that each of the cleaner fish 20 choices 
+in the ephemeral reward task was generated by the model 
+is given by $\binom{n}{k_ij}p^{k_{ij}}_i (1-p_i)^{n-k_{ij}}$;
+where $k_{ij}$ is the number of times that cleaner fish $j$ in reef site $i$ 
+chose the visitor over the resident; and $n=20$ (due to our choice of using 20 
+choices per cleaner fish). By taking the natural logarithm and summing over all 
+the cleaner fish and reef sites we obtained the log-likelihood of the data 
+given the model and parameters. We then proposed a new set of parameters drawn 
+from a uniform distribution centred around the old parameter set. The amplitude 
+of the uniform distribution used for each parameter can be found in Table 
+\ref{tab:param}. Subsequently, we ran the model and calculated the likelihood 
+with the new parameter set. We then used the ratio of the two likelihoods to 
+choose which parameter set to keep. New parameter sets with a higher likelihood 
+than the old set replaced old ones, and those with a lower likelihood replaced 
+current ones  with a probability equals to the log-likelihood ratio. 
+Given that we only used the likelihoods in the decision, we used a 
+uninformative prior. Once we decided whether the new parameter set replaces 
+the old one, we ran the model again to sample the likelihood 
+distribution of the parameter set. We then started 
+the cycle again by proposing a new set of parameters, and repeated
+the process for $1e^5$ steps. We ran 5 independent chains, 
+discarded the first $100$ samples of each chain as burn in, 
+and after that we kept 1 in every 100 samples to avoid autocorrelation. 
+The collection of parameters sets kept in 
+all chains approximates the posterior distribution. We coded the model 
+as well as the fitting algorithm in *c++*, the diagnostics and visualization 
+in R [@rcoreteam_Language_2021]. All codes are accessible at 
+$\color{red}{\text{include citation}}$
+
+To compare the fit of the three alternative models, we used the 
+distribution of pseudo $R^2$ proposed by Mcfadden [@mcfadden_Conditional_1974].
+Mcfadden's pseudo $R^2$ is a standard measure of fit for logistic regression. 
+In that context, $pseudo-R^2$ uses the log-likelihood of the data given 
+the model, relative to the log-likelihood of the data given a 
+model without covariates, as a measure of fit. Our 
+model is not a logistic regression, therefore we measured the $pseudo-R^2$ in
+relation to the log-likelihood of a model
+with parameters $\gamma$ and $\eta$ set to zero. This in practice
+amounts to a model that has neutral preference between the two options. 
+We computed the pseudo $R^2$ for all the samples of the posterior from
+the MCMC. Thus, we used these distributions of pseudo $R^2$'s as a measure of
+fit.
 
@@
 ```{r post, fig.cap="Posterior distributions for parameter values $\\gamma$, $\\eta$ and the scaling constant.
-We show the kernel density estimates, below the mode (black point) and the 65\\% (light blue) and 95\\% (grey)  highest posterior density interval for the three paramteres.
-On the left (panels a, c and c) posterior distributions for a model with   all three parameters; while on the right (b and d) a model without negative reward.
-Panel f shows a measure of fit for both models, namely the distribution of pseudo-$R^2$ obtained from sampling the posterior distribution of parameter values.",out.width='100%',fig.height=7}
+We show the kernel density estimates, below the mode (black dot) and the 65\\% (light blue shade) and 95\\% (grey shade)  highest posterior density interval for the three paramteres.
+On the left, panels a, b and c show posterior distributions for a model with all three parameters; while on the right, d and e, show a model with only chaining.
+Panel f shows a measure of fit for both models, namely the distribution of pseudo-$R^2$ obtained from sampling the posterior distribution of parameter values.",out.width='100%',fig.height=6}
 library(data.table)
@@
   stat_halfeye(alpha=0.5,point_size=3)+
-  theme_classic()+xlim(-0.6,0.2)+
+  theme_classic()+xlim(-0.4,0.2)+
   scale_fill_manual(values=c("#1b9e77","#d95f02","#7570b3"),
   name = "Model", labels = labelsPlot.Scen)+
-  geom_vline(xintercept = 0,color="black",size=1)+
-  theme(legend.position = c(.3, .75),legend.key.size = unit(0.25,'cm'),
-        axis.text.y = element_blank())
+  scale_y_discrete(labels=labelsPlot.Scen)+
+  geom_vline(xintercept = 0,color="black",size=0.5)+
+  theme(legend.position = 'none')
+          # c(.32, .65)
+        # ,legend.key.size = unit(0.22,'cm'),
+        # axis.text.y = element_blank(),
+        # legend.text = element_text(size=7))
 
@@
           # Pseudo R^2
-          panel.rsqr.all+labs(subtitle = expression(pseudo-R^2),x="",y=""),
-          labels=c('a','b','c','d','e')
+          panel.rsqr.all+labs(subtitle = expression(pseudo-R^2),x="",y="")+
+            theme(legend.position = 'none'),
+          labels=c('a','d','b','e','c','f')
 )
@@
 also includes zero, but the mode of the posterior is around 0.5. Thus,
-we run the analysis setting $\eta$ to zero. Figure \ref{fig:post} panels
-b and d, show the posterior distributions of the two parameters
+we ran the analysis setting $\eta$ to zero. Figure \ref{fig:post} panels
+d and e, show the posterior distributions of the two parameters
 estimated. Not surprisingly, under a model without negative reward, the
-distribution of $\gamma$ shifts to higher values. Under the new model,
-the estimates of $\gamma$ do not include zero, the distribution is
-centered around $0.5$. To asses the fit of the two models we calculated
-the $pseudo-R^2$ [@mcfadden_Conditional_1974], which is a standard
-measure of fit for logistic regression. In that context, $pseudo-R^2$
-uses the log-likelihood of the data given the model, relative to the
-log-likelihood of the data given a model without covariates, as a
-measure of fit. Given that our model is not a logistic regression, we
-measure the $pseudo-R^2$ in relation to the log-likelihood of a model
-with parameters $\gamma$ and $\eta$ set to zero. This in practice
-amounts to a model that has neutral preference between the two options.
-In panel f of figure \ref{fig:post} we show the distribution of
-$pseudo-R^2$ calculated using samples from the posterior distributions
-shown before, as well as from a model with negative reward but without
-future reward. Note, $pseudo-R^2$ can have negative values, that is when
+distribution of $\gamma$ shifted to higher values. Under the new model,
+the estimates of $\gamma$ did not include zero and the distribution was
+centred around $0.5$. In panel f of figure \ref{fig:post} 
+we show the distribution of $pseudo-R^2$ calculated using 
+samples from the posterior distributions shown before, 
+as well as from a model with negative reward but without
+future reward. Note, $pseudo-R^2$ can have negative values, which is when
 the log-likelihood of the model is lower than that of a model that
 triggers neutral preferences. Even though, the peak of the three
-$pseudo-R^2$ distributions is not very different, the model with only
-future reward produces a distribution of $pseudo-R^2$ where more values
-are positive (to the right of black line in Fig. \ref{fig:post} f). This
+$pseudo-R^2$ distributions was not very different, the model with only
+future reward produced a distribution of $pseudo-R^2$ where more values
+were positive (to the right of black line in Fig. \ref{fig:post} f). This
 shows that, accounting for variation in the parameter estimates, the
@@
 Left-hand side panel: color contour shows the prediction of the learning model using the mode of the posterior distributions of parameters recovered by the statistical analysis.
-Dots show the frequency of visitor choices for the 12 locations, as well as the corresponding relative cleaner abundance (x axis) and frequency of visitors leaving the station (y axis).
-Right-hand side panels: scatter plot of the observed and predicted probabilities of choosing a visitor for 12 locations.
-Line correspond to a perfect match between observed and predicted probabilities.
-Pseudo $R^2$ shown in the lower right corner corresponds to the fit of a model parameterized with the mode of the posterior distributions.
-Upper panels show prediction from a model including future and negative reward, lower panels froma  model with only future reward.",out.width='100%',fig.height=6}
+Dots show the frequency of visitor choices for the 12 reef sites, as well as the corresponding relative cleaner fish abundance (x axis) and frequency of visitors clients leaving the cleaning station (y axis).
+Right-hand side panels: Variation of the predicted probabilites  of choosing a visitor over a resident and their observed values for 12 locations.
+Circles show the mean prediction for each location from 100 samples taken from the posterior distribution.
+Thick and thin bars show the 66 and 95\\% credible interval, respectively, taken from those posterior samples.
+Squares show the predictions used for panel on the righ-hand side.
+Colour coding denotes different reef sites/year of the data collection (see Empirical data section).
+Black line corresponds to a perfect match between observed and predicted probabilities.
+Upper panels show prediction from a model including chaining and operant conditioning, lower panels from a  model with only chaining.",out.width='100%',fig.height=5}
 
@@
 cont.obs.pred.gam,scatter.obs.pred.gam,
-          labels=c('a','b','c','d'),common.legend=TRUE,legend = "top")
+          labels=c('a','b','c','d'),common.legend = F,
+  heights=c(1.25,1))
+
 ```
 
-Figure \ref{fig:pred} shows predictions from the two models. On the
+Figure \ref{fig:pred} shows predictions from the two models, 
+one including chaining and operant conditioning (upper panels) and 
+one with only chaining (lower panels). On the
 left, the colour coded contour shows the prediction of the model for
-combinations of cleaner abundance (x axis) and visitor leaving
+combinations of cleaner fish abundance (x axis) and visitor leaving
 probability (y axis). Predictions were generated by running the model
 using the mode of the posterior distributions as the parameter values,
-and varying systematically cleaner abundance and visitor leaving
-probability. Colour of the points on top of the contour show the average
+and varying systematically cleaner fish abundance and visitor leaving
+probability. Colour of the dots on top of the contour show the average
 frequency with which cleaner fish chose the visitor plate in their last
-20 experimental trials. Each point corresponds to a location with a
-combination of cleaner abundance and visitor leaving probability. Panels
+20 experimental trials. Each dot corresponds to a reef-site/year of 
+data collection with a combination of cleaner fish abundance 
+and visitor leaving probability. Panels
 on the right show how close the observed values for the probability of
-choosing the visitor (y axis) are from the predictions of the models (x
-axis). The line represents the perfect fit between observed and
-predicted values. Predicted values were taken using the mode just as in
-the left panels. On the lower right corner of the panel we show the
-$pseudo-R^2$ for predictions using the mode of the posterior
-distributions. Despite having one more parameter varying, the full model
-gives a lower fit to the data than the model without negative reward.
-The difference in $pseudo-R^2$ for the point estimates is small, but
-using the whole posterior distribution shows the improvement in fit
-achieved by eliminating negative reward from the model (Fig.
-\ref{fig:post}f). In the supplementary material, we also show that a
+choosing the visitor (y axis) were from the predictions of the models (x
+axis). The black line represents the perfect fit between observed and
+predicted values. Bars show the variation in predicted values using 100 
+samples from the posterior distribution. Despite having one more 
+parameter varying, the full model
+gave a lower fit to the data than the model without negative reward.
+In the supplementary material, we also show predictions from 
 model with only negative reward, excluding future rewards ($\gamma=0$,
@@
 
-We have shown that using future rewards in the learning process is the
-cognitive strategy that best explains the intra-specific variation in
-cleaner performance in the market task. We compared future reward with
-the use of visitors behaviour as a primary source of negative reward,
-and a combination of both. All three models capture well the positive
-relation between visitor leaving behaviour and cleaner performance in
-the market task [@triki_Biological_2019]. For both mechanisms it is
-indeed necessary to have fleeing behaviour on the side of the visitors
-for cleaners to develop a preference for them. The key difference
-between future and negative reward emerges in the predicted relation
-between cleaner relative abundance and cleaner performance. When cleaner
-relative abundance is low a model with only future reward predicts low
-performance in the market task regardless of the visitor leaving
-probability. In contrast, a model with negative reward predicts the
-highest performance with low relative cleaner abundance, particularly
+In this study, our main aim was to unravel which of two potential 
+cognitive mechanisms, chaining of events, operant conditioning, 
+or their combination, best explains wild-caught cleaner fish 
+performance in the ephemeral reward task, while accounting for their
+ecological conditions. To evaluate the merits of each of these two mechanisms
+separately and combined, we considered cleaner fish performance 
+in the lab test to have its origin from the these fish apply 
+in their natural environment. That is, individuals that 
+solved the task already had a preference for 
+visitors clients, and generalized this rule to the lab conditions 
+once being familiar with the task.
+
+While all three models captured well the positive relation between visitor 
+leaving behaviour and cleaner performance in
+the market task [@triki_Biological_2019], only the chaining mechanism 
+predicted that cleaner fish performance in the task should be low in 
+habitats with low cleaner-to-client ratios, regardless of the 
+visitor leaving probability. In contrast, models including 
+negative reward predicted the highest performance in the ephemeral 
+reward task when relative cleaner abundance is low, particularly 
 together with high probability of visitor leaving (Fig. \ref{fig:pred}).
-Low cleaner abundances mean the market has an excess of demand for
-cleaning services. In the model, this translates to a cleaning station
-that is frequently full. Thus, when visitors leave, it's likely that the
-cleaner will have access to another client, and there will not be much
-difference in future reward between choosing a visitor and a resident.
-Thus, estimation of future reward will not develop a preference for the
-visitor in this conditions, because it matches the state of the market.
-On the other hand, the effect of negative reward is unaffected by this
-market situation. In a full station, cleaners will get more often the
-heterotypic (resident-visitor) option and will develop a preference for
-the visitor faster. Note that when cleaner abundance is high situations
-with a resident and a visitor will be so rare that neither mechanism
-will be very efficient in generating a preference for visitors. When
-such choice arises it is still be best to choose the visitor; however,
+Low relative cleaner fish abundances mean the market has an excess of demand for
+cleaning services. In the models, this translates to a cleaning station
+that is frequently full. Thus, when a visitors leaves, it is likely that the
+cleaner fish will have access to another client in the next step. Therefore, 
+there will not be much difference in future reward between choosing 
+a visitor and a resident, and cleaners will not develop a preference for the
+visitor in these conditions. On the other hand, the effect of negative reward 
+on cleaner fish preference is the opposite, as in a busy cleaning station, to
+that of chaining. cleaner fish will get more often the resident-visitor
+state and will develop a preference for the visitor faster. 
+At high cleaner fish abundances, the resident-visitor state
+becomes so rare that neither mechanism is very efficient 
+at generating a preference for visitors. When facing the resident 
+visitor choice it is still be best to choose the visitor; however,
 the learning machinery will not be able to develop this preference
-efficiently. Overall, estimation of future reward is then the cognitive
-mechanism that allows cleaners to adaptively respond conditions to the
-ecological conditions of the biological market.
+efficiently. Overall, the models suggest that chaining is the cognitive
+mechanism that allows cleaner fish to adaptively adjust to their 
+biological market ecological conditions.
 
-The cognitive mechanism that our analysis highlights does not require a
-direct flow of information between the cleaner and its social
-environment. The adaptive responses to local conditions in cleaners is
-not only evidenced by their performance in experiments, but also by
-changes in their brain anatomy. Indeed, individual cleaners that
-performed in the laboratory test according to what is best at the
-location in which they were caught had larger forebrains harbouring more
-cells than individuals whose performance mismatched locally optimal
-decision-rules [@triki_Brain_2020]. This suggests that despite the
-overall behavioural adjustment, evidenced here and elsewhere
-[@triki_Biological_2019; @triki_Decrease_2018], there are some
-cleaners better than others at adjusting their behaviour. Triki *et al.*
-[@triki_Brain_2020] refer to these as socially competent cleaners. Social
-competence refers to the ability to optimise social behaviour depending
-on the available social information [@taborsky_Social_2012a;
-@bshary_Cooperation_2015]. However, we have shown here that cleaners
-are able to adjust their preference according to the social environment
-without using any direct information about the social environment.
-Instead cleaners seem to adjust their preference using information from
-the visitation patterns of their clients. These patters are of course
-determined by the feedback with the cleaner's social environment
-(relative abundance). Our models, however, do not include the
-possibility of cleaners responding to their relative abundance directly.
-The mechanism we present is a general way to learn from the environment
-in both asocial and social situations. It would be interesting to
-contrast this learning mechanism with one tailored to a social
-situation, and see whether such mechanism fits the data better. More
-generally, an important challenge ahead is to understand which cognitive
-mechanisms evolved exclusively for social life.
+Our results support chaining as the more plausible mechanism behind the 
+inter-specific variation in cleaners' performance. This suggest
+that chaining could be under positive selection. In the standard ephemeral
+reward task, however, food amount and quality are equal in the 
+two Plexiglas plates. Since our computational models simulate this aspect of
+the task, choosing visitors over residents at low cleaner fish abundances 
+does not diminish the amount of food/reward in the models. 
+On the other hand, a cleaner fish committed to visitors might find it more difficult 
+to include in its decision making other variables, like parasite load 
+and/or mucus quality [@roche_Client_2021]. Indeed, in the absence of 
+market effects, both field observations and aboratory experiments also 
+using simultaneous two choice options, show that cleaner fish base their 
+decision-making on other cues such as the mucus quality and the amount of food.  
+[@triki_Fluctuations_2019;@grutter_Cleaner_2004], as well as client size 
+as a proxy for food quantity [@wismer_Cuebased_2019;@grutter_Does_2005]. 
+How important this limitation is will determine whether chaining yields a higher
+fitness for cleaners.
 
-One potential difference between cleaners that adjusted adaptively, like
-the ones reported in Triki *et al.* [@triki_Brain_2020], is configurational learning or
-chunking. The original analysis of the learning model showed that agents
-needed two mechanism to solve the market task; to account for the
-future, and to assign value to the combination of clients present in the
-station [@quinones_Reinforcement_2019]. The latter is referred to as
-configurational learning or chunking [@sutherland_Configural_1989;
-@miller_Magical_1956]. Theoretical models suggest that the lack of
-configurational learning is related to a low frequency with which
-stimuli are encountered together [@kolodny_Evolution_2014;
-@prat_Role_2021]. Thus, cleaner relative abundance could be related to
-this mechanisms as well. Given that the lack of either of these two
-mechanisms yields neutral preferences [@quinones_Reinforcement_2019],
-we can't, based on the current analysis, distinguish between the two
-possibilities. One potential way to distinguish between the two would be
-to use an experimental set up designed to test configuration learning on
-cleaners with high and low performance in the market task
-[@woodbury_Learning_1943; @sutherland_Configural_1989].
+Previous research showed that cleaner fish living at high population 
+densities and giving service priority to the visitor plate in the 
+ephemeral reward task, as well as cleaner fish living at low 
+densities but denying service priority to the visitor plate possess 
+larger forebrains; a key teleost brain region associated with 
+behavioral flexibility and social intelligence. Those failing to 
+show optimized decision-rules given their local ecological 
+conditions had relatively smaller forebrains  [@triki_Brain_2020]. 
+Triki *et al.*  refer to the former as socially competent cleaner fish,
+while the second group as socially incompetent cleaner fish. 
+Social competence is the ability to optimise social behaviour 
+to the available social information [@taborsky_Social_2012a;
+@bshary_Cooperation_2015;@varela_Correlated_2020]. Our analyses yielded no 
+evidence that the difference in social competence with respect to the local 
+ecological conditions and associated brain morphology, 
+found by Triki *et al* [@triki_Brain_2020], are due to the mechanism 
+used to incorporate future consequences. It could have been conceivable that 
+high performing individuals from low population densities reef sites 
+might use negative reinforcement instead of chaining, but in that 
+case negative reinforcement should have explained at least 
+part of the data. Configurational learning or 
+chunking [@sutherland_Configural_1989;@miller_Magical_1956], 
+the second component necessary to solve the ephemeral 
+reward task [@quinones_Reinforcement_2019], was 
+not varied in the models we analized here. However, while chunking tendencies 
+should vary to allow individuals to adapt to their local conditions 
+[@prat_Modelling_2022;@kolodny_Evolution_2014], systematic differences 
+in individual chunking tendencies would not explain how socially 
+competent decisions vary as a function of relative abundance. 
+Therefore, it remains currently unclear what cell-demanding 
+mechanisms may cause variation in social competence that 
+translates into site-specific variation in performance in the 
+ephemeral reward task.
 
-Combining mechanistic modelling with empirical data provides a powerful
-tool to identify the cognitive processes underlying learning in animals.
-The combination overcomes the limitations of the general philosophy in
-animal cognition to apply the logic of Lloyd Morgen's canon (Occam's
-razor). Excluding basic reinforcement learning explanations (operant
-and/or classical conditioning) as a potential explanation in experiments
-often warrants animals solving the task on the first possible occasion.
+Our models are inspired by the general processes of associative learning
+where short term rewards are translated into decision making; thus, it 
+ignores alternative channels of information that could be relevant in 
+market-like situations. For example, the model does not investigate whether 
+cleaner fish actually assess the frequency of client visits or a mean frequency 
+of visitors leaving. The updating learning mechanism for the development 
+of preferences works on a trial-by-trial basis. In the model, cleaner fish 
+do not need to assess the actual state of the market, *i.e.* their abundance, 
+the abundance of residents and visitors, and client visitation rate as an 
+indicator of demand. They only need to assess short-term consequences of their
+own decisions on food intake, and chain them. Also, for the sake of 
+simplicity, the model ignores the process by which cleaner fish discriminate 
+residents and visitor clients. A model that accounts for this discrimination
+probably would involve the development of preferences for morphological or 
+behavioural features that are statistically associated with visitors 
+or residents. For example, visitors are on average larger 
+than residents in body size [@bshary_Cleaner_2001a], and contrary to 
+resindents, are less likely to chase a cleaner fish that fails to cooperate
+and intead cheats its client by taking a bite of mucus 
+[@bshary_Asymmetric_2002]. Given these associations, chaining might 
+produce the decision-rule “choose the larger client and/or the less aggressive 
+client”, which is not a useful rule in the standard ephemeral reward task.
+
+In conclusion, our study shows that variation in cognitive performance as 
+a function of the local ecological conditions may set the stage for the use of 
+mechanistic modelling to identify the cognitive processes underlying 
+learning in animals. The combination overcomes the limitations 
+of the general philosophy in animal cognition to apply the logic of 
+Lloyd Morgen's canon (Occam's razor). Cognitive experiments with the 
+aim of excluding basic reinforcement learning as a potential 
+explanation (operant and/or classical conditioning) of performance 
+often employ one trial experiments requiring animals to solve the 
+task on the first possible occasion. 
 For example, any theory of mind task needs to be solved in the first
@@
 ```
-```{r nogamma, fig.cap="Observed and predicted probability of choosing a visitor for a model without future rewards.
+```{r nogamma, fig.cap="Observed and predicted probability of choosing a visitor for a model without chaining.
 Left-hand side panel: color contour shows the prediction of the learning model using the mode of the posterior distributions of parameters recovered by the statistical analysis.
-Dots show the frequency of visitor choices for the 12 locations, as well as the corresponding relative cleaner abundance (x axis) and frequency of visitors leaving the station (y axis).
-Right-hand side panel: scatter plot of the observed and predicted probabilities of choosing a visitor for 12 locations.
-Line correspond to a perfect match between observed and predicted probabilities.",fig.pos = 'H', out.extra = "",out.width='95%',fig.height=4}
+Dots show the frequency of visitor choices for the 12 reef sites, as well as the corresponding relative cleaner fish abundance (x axis) and frequency of visitors leaving the station if being made to wait (y axis).
+Right-hand side panel: Right-hand side panels: Variation of the predicted probabilites  of choosing a visitor and their observed values for 12 reef sited.
+Circles show the mean prediction for each location from 100 samples taking from the posterior distribution.
+Thick and thin bars show the 66 and 95\\% credible interval taken from those posterior samples.
+Squares show the predictions used for panel on the righ-hand side.
+Colour denotes different locations (see Empirical data section).
+Black line correspond to a perfect match between observed and predicted probabilities.",fig.pos = 'H', out.extra = "",out.width='95%',fig.height=4}
 
 ggarrange(cont.obs.pred.Nrew,scatter.obs.pred.Nrew,
-          labels=c('a','b'),common.legend=FALSE,legend = "top")
+          labels=c('a','b'),common.legend=FALSE)
 

### 2022-02-16 ActCritMCMC.cpp

@@ -1114,8 +1114,8 @@ int main(int argc, char* argv[]){
 	//sim_param["MCMC"] = 0;
 	//sim_param["data"] = "clean"; // "loc", "clean"
 	//sim_param["nRep"] = 30 ;
-	//sim_param["folder"]       = "M:/Projects/Clean.ActCrit/Simulations/ABCtest_/";
-	//sim_param["dataFile"] = "M:/Projects/Clean.ActCrit/Data/data_ABC_cleaner_abs_threa1.5.txt";
+	//sim_param["folder"] = "M:/Projects/LearnDataModel/Simulations/test_/";
+	//sim_param["dataFile"] = "M:/Projects/LearnDataModel/Data/data_cleaner_abs_threa1.5.txt";
 	//sim_param["Group"] = true;
 
 	////ifstream marketData ("E:/Projects/Clean.ActCrit/Data/data_ABC.txt");
@@ -1255,7 +1255,8 @@ int main(int argc, char* argv[]){
 				}
 			}
 			for (int j = 0; j < emp_data_loc.size(); ++j)
-				emp_data_loc[j].marketPred = average_prediction[j] / sim_param["nRep"];
+				emp_data_loc[j].marketPred = 
+				  average_prediction[j] / double(sim_param["nRep"]);
 			printRoundFile(roundOut, emp_data_loc);
 			roundOut.close();
 		}
@@ -1273,7 +1274,8 @@ int main(int argc, char* argv[]){
 				}
 			}
 			for (int j = 0; j < emp_data_clean.size(); ++j) 
-				emp_data_clean[j].marketPred = average_prediction[j]/sim_param["nRep"];
+				emp_data_clean[j].marketPred = 
+				  average_prediction[j]/double(sim_param["nRep"]);
 			printRoundFile(roundOut, emp_data_clean);
 			roundOut.close();
 		}

### 2022-02-16 loadFieldData.R

@@ -25,6 +25,13 @@ fieldData.site<-fieldData[,lapply(.SD,max),by=site_year,
 ## Load the experimental data
 fieldData.cleaner<-data.table(read_xlsx(here("Data","market_raw_data.xlsx"),sheet = "round_data"))
 
+fieldData.cleaner[,unique(site_year)]
+
+# Fix mistake in location code name
+fieldData.cleaner[site_year=="NHS2017",site_year:="NHS 2017"]
+
+
+
 # Choose data from the last 20 experimental choices
 fieldData.cleaner[,use_sims:=ifelse(is.na(use_sims),0,1)]
 fieldData.cleaner[,use_sims:=as.logical(use_sims)]
@@ -32,6 +39,7 @@ fieldData.cleaner[,use_sims:=as.logical(use_sims)]
 fieldData.filt<-fieldData.cleaner[use_sims==T,]
 fieldData.filt[,score_visitor:=as.numeric(score_visitor)]
 fieldData.filt[,stage:=as.factor(stage)]
+
 
 str(fieldData.filt)
 
@@ -48,8 +56,7 @@ names(fieldData.sum)[1]<-"site.year"
 fieldData.sum[,unique(site.year)]
 fieldData.site$site_year
 
-# Fix mistake in location code name
-fieldData.sum[site.year=="NHS2017",site.year:="NHS 2017"]
+
 
 # Get environmental variables from field data
 fieldData.sum[,abund.cleaners:=
@@ -88,9 +95,12 @@ setorder(fieldData.sum,site.year)
 fieldData.sum[,`:=`(highDens=NULL,visPref=NULL,competence=as.integer(competence))]
 
 # Print dataset with both sources of information with competence grouping
-fwrite(fieldData.sum,here("data",paste0("data_ABC_cleaner_abs_threa",threashold,".txt")),
+fwrite(fieldData.sum,here("data",paste0("data_cleaner_abs_threa",threashold,".txt")),
        row.names = FALSE,sep = "\t")
 
 # Print dataset with both sources of information without competence grouping
-fwrite(fieldData.sum,here("data","data_ABC_cleaner_abs.txt"),
+fieldData.sum[,competence:=NULL]
+fwrite(fieldData.sum,here("data","data_ABC_cleaner_absolute.txt"),
        row.names = FALSE,sep = "\t")
+
+## 

### 2022-02-16 parTOjson.R

@@ -6,58 +6,53 @@ source(here("loadData.R"))
 
 simsDir<-"Simulations"
 
-exedir<-'/./ActCrit.exe'
-
 fileName<-"parameters.json"
-
-scenario<-"MCMCclean_gam_nRew_sca_group_"
 
 
 # MCMC fit - Generate json parameter files for -------------------------------------
 
-scenario<-"MCMCclean_gam_sca_group"
+# name of the scenariofor which parameter files will be produces
+# format used for the name: MCMCclean_*parameter1_paramerter2_parameter3
+scenario<-"MCMCclean_nRew_sca"
 
-# For running MCMC with model generated data
-
-# filesList<-list.files(here("Simulations",scenario),full.names = TRUE)
-# 
-# fake.data.pred<-fread(grep("round",filesList,value = TRUE))
-# 
-# fake.data.pred<-fake.data.pred[,.(site_year,CleanerID,
-#                                   score_visitor=sapply(visitorChoices_pred,
-#                                                        rbinom,n = 1,size = 20),
-#                                   rel.abund.cleaners,rel.abund.visitors,
-#                                   rel.abund.residents,prob.Vis.Leav)]
-# 
-# fake.data.pred<-fake.data.pred[fakeData,on=.(site_year=site.year,CleanerID=cleaner_ID)]
-# 
-# fake.data.pred<-fake.data.pred[,.(site_year,CleanerID,score_visitor,abund.cleaners,
-#                                   abund.visitors,abund.residents,prob.Vis.Leav),]
-# 
-# fwrite(fake.data.pred,file = here("Simulations",scenario,"data_MCMC_fake.txt"),
-#        row.names = FALSE,sep = "\t")
-# 
-# scenario<-"MCMCfakedata2"
 # for MCMC
-param_mcmc<-list(totRounds=10000,ResReward=1,VisReward=1,
-                 ResProbLeav=0,scenario=0, 
-                 #nature, experiment, marketExperiment, ExtendedMarket
-                 inbr=0,outbr=0,forRat=0.0,
-                 seed=1, propfullPrint = 0.7,sdPert=c(0.05,0.05,0.3,2,200),
-                 chain_length=100000,
-                 init=c(0.05,0.05,0,0,30),# alphaA,AlphaC, Gamma, NegRew, scalConst
-                 pertScen = c(FALSE,FALSE,TRUE,FALSE,TRUE), 
-                 MCMC =1, data="clean",nRep=1,
-                 Group = TRUE,
[…]

### 2022-02-22 manuscript_1.0/manuscript_1.0.Rmd
Error found in the manual coding of the cleaner entries used to compute visitor preference. In loadFieldData.R a programatic way of coding cleaner entries was done. Now that the manual and programatic results coincide I can re-run the chains. New figure configurations were implemented. Among those supplementary figures showing the diagnostics of the MCMC. A new result section was written.

@@
 The task can in principle be solved by estimating future consequences of an action, or by perceiving the removal of the ephemeral reward as psychological punishment (negative reinforcement).
-We found that a model where cleaners only estimate the future consequences of their actions explains best which cleaner relative abundances cause the fish to develop a preference for an ephemeral food source.
+We found that a model where cleaners only estimate the future consequences of their actions explains best which cleaner fish relative abundances cause the fish to develop a preference for an ephemeral food source.
 This model also yields performances that can be considered the result of locally optimal decision-rules, in contrast to the negative reinforcement model.
@@
 library(here)
+source(file=here("loadFieldData.R"))
 ```
@@
 One plate is made to behave like a resident, i.e. it remains until 
-the cleaner had eaten off it. The other plate was made to behave 
+the cleaner fish had eaten off it. The other plate was made to behave 
 like a visitor, i.e. it is removed if not inspected first.
@@
 <!-- included. Thus, the analysis suggests that future reward as an  -->
-<!-- explanation for cleaner ability to prefer visitors is supported.  -->
+<!-- explanation for cleaner fish ability to prefer visitors is supported.  -->
 <!-- At first sight, empirical data seem to support future rewards as  -->
@@
 <!-- beneficial it is to prioritize a client that will not stay. On the other hand,  -->
-<!-- situations where cleaners have to choose will be rare if cleaner relative  -->
+<!-- situations where cleaners have to choose will be rare if cleaner fidh relative  -->
 <!-- abundance is high, which reduces the total value of prioritizing visitors  -->
@@
 different roles as either a visitor (ephemeral food source) or 
-resident (permanent food source). That is, if a cleaner inspected the 
+resident (permanent food source). That is, if a cleaner fish inspected the 
 resident plate first, the experimenter withdrew the visitor plate out of 
@@
 never reached the learning criterion for visitor plate 
-$\color{red}{\text{(N = XX cleaner fish)}}$. 
+($N = `r fieldData.cleaner.filt.sum[V1==2,length(V1)]`$ cleaner fish). 
 For those who reached the learning criterion at some point during the 
@@
 and the last 10 trials they were exposed to in the test 
-$\color{red}{\text{(N = XX cleaner fish)}}$.
+($N = `r fieldData.cleaner.filt.sum[V1>2,length(V1)]`$ cleaner fish).
 
@@
 a combination of these effects is a better explanation for the pattern 
-seen in the data. We used the 
-ecological variables: cleaners, visitor clients, 
-resident clients abundances and
-visitor clients leaving probability,  as input to the models. 
-As response variable we used cleaners' preference for visitor 
-over residents in the ephemeral reward task. 
+seen in the data. We used the ecological variables: cleaners, visitor clients, 
+resident clients abundances and visitor clients leaving probability,  
+as input to the models. As response variable we used cleaners' 
+preference for visitor over residents in the ephemeral reward task. 
 Finally, we used the preference for visitors resulting from the 
@@
 the absolute population densities of cleaner fish from the empirical data
-to a measure of relative abundances that captures 
-client visitation patterns. This is because in the model, relative 
-abundances of clients define not only the probability of residents and visitors, 
+to a measure of relative abundances that captures client visitation patterns. 
+This is because in the model, relative abundances of clients 
+define not only the probability of residents and visitors, 
 but also how often the cleaning station is empty (e.g. there are no 
@@
 constant is hence meant to capture variation in the market conditions driven 
-partly by cleaner abundance. We fitted the value of the scaling constant as 
+partly by cleaner fish abundance. We fitted the value of the scaling constant as 
 part of the statistical inference. As for the visitor and resident 
@@
 the process for $1e^5$ steps. We ran 5 independent chains, 
-discarded the first $100$ samples of each chain as burn in, 
+discarded the first $1000$ samples of each chain as burn in, 
 and after that we kept 1 in every 100 samples to avoid autocorrelation. 
@@
 
-```{r post, fig.cap="Posterior distributions for parameter values $\\gamma$, $\\eta$ and the scaling constant.
-We show the kernel density estimates, below the mode (black dot) and the 65\\% (light blue shade) and 95\\% (grey shade)  highest posterior density interval for the three paramteres.
-On the left, panels a, b and c show posterior distributions for a model with all three parameters; while on the right, d and e, show a model with only chaining.
-Panel f shows a measure of fit for both models, namely the distribution of pseudo-$R^2$ obtained from sampling the posterior distribution of parameter values.",out.width='100%',fig.height=6}
+(ref:post) Posterior distributions for parameter values $\gamma$ and $\eta$ for 
+the three model ("Full model", "chaining only" and "penalty only"). We show 
+the kernel density estimates, below the mode (black dot) and the 65% 
+(light blue shade) and 95% (grey shade)  highest posterior density interval 
+for the two parameters. On the top, panels a and b show posterior 
+distributions for a full model, including chaining ($\gamma$) and penalty 
+($\eta$). Panel c, shows the $\gamma$ estimate from model with only chaining. 
+Panel d shows the $\\eta$ estimate from a model with only penalty. Panel e, 
+shows a measure of fit for all models, namely the distribution of pseudo-$R^2$ 
+obtained from sampling the posterior distribution of parameter values.
+
+```{r post, fig.cap='(ref:post)',out.width='100%',fig.height=6}
 library(data.table)
@@
 library(ggdist)
+library(ggpubr)
 source(here("../R_files/posPlots.R"))
@@
 labels.Scen<-c("both","gam","Nrew")
-labelsPlot.Scen<-c("FM","C","OC")
+labelsPlot.Scen<-c("Full Model","Chaining","Penalty")
 
@@
 MCMCdata2<-loadMCMCrun(scen2,thinning = thinning,burn.in = burn.in)
-MCMCdata3<-loadMCMCrun(scen3,thinning = thinning,burn.in = burn.in)
+# MCMCdata3<-loadMCMCrun(scen3,thinning = thinning,burn.in = burn.in)
 
@@
   rundata<-MCMCdata2[seed==repli]
-  mcmcRun<-mcmc(rundata[,.(gamma,scaleConst)],thin = thinning)#
+  mcmcRun<-mcmc(rundata[,.(gamma,scaleConst)],thin = thinning)
   return(mcmcRun)
@@
 
-mcmcList.2<-mcmc.list(do.call(list,lapply(unique(MCMCdata2$seed), function(repli){
-  rundata<-MCMCdata2[seed==repli]
-  mcmcRun<-mcmc(rundata[,.(negReward,scaleConst)],thin = thinning)#
-  return(mcmcRun)
-})))
-
-mcmcList.3<-mcmc.list(do.call(list,lapply(unique(MCMCdata3$seed), function(repli){
-  rundata<-MCMCdata3[seed==repli]
-  mcmcRun<-mcmc(rundata[,.(gamma,negReward,scaleConst)],thin = 100)#
-  return(mcmcRun)
-})))
+# mcmcList.3<-mcmc.list(do.call(list,lapply(unique(MCMCdata3$seed), function(repli){
+#   rundata<-MCMCdata3[seed==repli]
+#   mcmcRun<-mcmc(rundata[,.(gamma,scaleConst)],thin = thinning)#
+#   return(mcmcRun)
+# })))
 
@@
                function(x){
-                 c(mode_hdi(x,.width = intervals[c(2,1)])$ymin,
-                   mode_hdi(x,.width = intervals)$ymax)  
+                 c(mode_hdci(x,.width = intervals[c(2,1)])$ymin,
+                   mode_hdci(x,.width = intervals)$ymax)
                })
 
-cuts.3<-lapply(MCMCdata3[,.(negReward,scaleConst)],
-               function(x){
-                 c(mode_hdi(x,.width = intervals[c(2,1)])$ymin,
-                   mode_hdi(x,.width = intervals)$ymax)  
-               })
+# cuts.3<-lapply(MCMCdata3[,.(negReward,scaleConst)],
+#                function(x){
+#                  c(mode_hdci(x,.width = intervals[c(2,1)])$ymin,
+#                    mode_hdci(x,.width = intervals)$ymax)
+#                })
 
 # get all the likelihoods from the posterior for all models
-loglikehoods.all<-data.table(lglikelihood=c(MCMCdata1$fit,MCMCdata2$fit,
-                                             MCMCdata3$fit),
-                              model=c(rep(labels.Scen[1],length(MCMCdata1$fit)),
-                                      rep(labels.Scen[2],length(MCMCdata2$fit)),
-                                      rep(labels.Scen[3],length(MCMCdata3$fit))
-                                      ))
-
-# Read field data to calculate null log-likelihood
-fieldData<-fread(here("Data","data_ABC_cleaner_abs.txt"))
-
-nullLikehood<-sum(dbinom(x=fieldData[,score_visitor],
-                         size = 20,prob = 0.5,log = TRUE))
-
-# calculate pseudo R^2
-loglikehoods.all[,Rsqrd:=1-lglikelihood/nullLikehood]
-
-panel.rsqr.all<-
-  ggplot(data=loglikehoods.all[is.finite(lglikelihood)],
-                  aes(y=model,x=Rsqrd,fill=model))+
-  stat_halfeye(alpha=0.5,point_size=3)+
-  theme_classic()+xlim(-0.5,0.25)+
-  scale_fill_manual(values=c("#1b9e77","#d95f02","#7570b3"),
-  name = "Model", labels = labelsPlot.Scen)+
-  scale_y_discrete(labels=labelsPlot.Scen)+
-  geom_vline(xintercept = 0,color="black",size=0.5)+
-  theme(legend.position = 'none')
-          # c(.32, .65)
-        # ,legend.key.size = unit(0.22,'cm'),
-        # axis.text.y = element_blank(),
-        # legend.text = element_text(size=7))
-
-gam.both.post<-ggplot(data=MCMCdata1,aes(x=gamma)) + 
-  stat_halfeye(aes(fill=stat(cut(x,breaks = cuts.1$gamma))),
-               point_interval = mode_hdi, .width = c(.66, .95),
-               point_size=3,show.legend=FALSE) + 
-  labs(title=labelsPlot.Scen[1],
-       subtitle = expression(gamma),x="",y="")+
-  theme_classic()+
-  scale_fill_manual(values=c("gray85","skyblue","gray85"))
-nrew.both.post<-ggplot(data=MCMCdata1,aes(x=negReward)) + 
-  stat_halfeye(aes(fill=stat(cut(x,breaks = cuts.1$negReward))),
-               point_interval = mode_hdi, 
-               .width = c(.66, .95),point_size=3,
-               show.legend=FALSE)+theme_classic()+
-  scale_fill_manual(values=c("gray85","skyblue","gray85"))+
-  labs(title="",subtitle = expression(eta),x="",y="")+
-  xlim(-2,2)
-gam.gam.post<-ggplot(data=MCMCdata2,aes(x=gamma)) +
-  stat_halfeye(aes(fill=stat(cut(x,breaks = cuts.2$gamma))),
-               point_interval = mode_hdi, .width = c(.66, .95),
-               point_size=3,
-               show.legend=FALSE) +
-  scale_fill_manual(values=c("gray85","skyblue","gray85"))+
-  labs(title=labelsPlot.Scen[2],
-       subtitle = expression(gamma),x="",y="")+
-  theme_classic()
-nrew.nrew.post<-ggplot(data=MCMCdata3,aes(x=negReward)) +
-  stat_halfeye(aes(fill=stat(cut(x,breaks = cuts.3$negReward))),
-               point_interval = mode_hdi, .width = c(.66, .95),
-               point_size=3,
-               show.legend=FALSE) +
-  scale_fill_manual(values=c("gray85","skyblue","gray85"))+
-  labs(title=labelsPlot.Scen[3],
-       subtitle = expression(gamma),x="",y="")+
-  theme_classic()+xlim(-2,2)
-
-first.col<-plot_grid(nrow=3,align = "v",byrow = TRUE,
-          gam.both.post,gam.gam.post,nrew.nrew.post,           
-          labels=c('a','c','d'))
-second.col<-plot_grid(nrow = 2,align = "v",byrow = TRUE,
-          nrew.both.post,rsqr.both,rel_heights = c(1,2),
-          labels = c('b','e'))
-plot_grid(ncol = 2,first.col,second.col)
+# loglikehoods.all<-data.table(lglikelihood=c(MCMCdata1$fit,MCMCdata2$fit,
+#                                              MCMCdata3$fit),
+#                               model=c(rep(labels.Scen[1],length(MCMCdata1$fit)),
+#                                       rep(labels.Scen[2],length(MCMCdata2$fit)),
+#                                       rep(labels.Scen[3],length(MCMCdata3$fit))
+#                                       ))
+# 
+# # Read field data to calculate null log-likelihood
+# fieldData<-fread(here("Data","data_cleaner_abs_threa1.5.txt"))
+# 
+# nullLikehood<-sum(dbinom(x=fieldData[,score_visitor],
+#                          size = 20,prob = 0.5,log = TRUE))
+# 
+# # calculate pseudo R^2
+# loglikehoods.all[,Rsqrd:=1-lglikelihood/nullLikehood]
+# 
+# 
+# panel.rsqr.all<-
+#   ggplot(data=loglikehoods.all[is.finite(lglikelihood)],
+#                   aes(y=model,x=Rsqrd,fill=model))+
+#   stat_halfeye(alpha=0.5,point_size=3)+
+#   theme_classic()+#xlim(-0.5,0.25)+
+#   scale_fill_manual(values=c("#1b9e77","#d95f02","#7570b3"),
+#   name = "Model", labels = labelsPlot.Scen)+
+#   scale_y_discrete(labels=labelsPlot.Scen)+
+#   geom_vline(xintercept = 0,color="black",size=0.5)+
+#   theme(legend.position = 'none')
+#           # c(.32, .65)
+#         # ,legend.key.size = unit(0.22,'cm'),
+#         # axis.text.y = element_blank(),
+#         # legend.text = element_text(size=7))
+# 
+# gam.both.post<-ggplot(data=MCMCdata1,aes(x=gamma)) +
+#   stat_halfeye(aes(fill=stat(cut(x,breaks = cuts.1$gamma))),
+#                point_interval = mode_hdi, .width = c(.66, .95),
+#                point_size=3,show.legend=FALSE) +
+#   labs(title=labelsPlot.Scen[1],
+#        subtitle = expression(gamma),x="",y="")+
+#   theme_classic()+
+#   scale_fill_manual(values=c("gray85","skyblue","gray85"))
+# 
+# nrew.both.post<-ggplot(data=MCMCdata1,aes(x=negReward)) +
+#   stat_halfeye(aes(fill=stat(cut(x,breaks = cuts.1$negReward))),
+#                point_interval = mode_hdi,
+#                .width = c(.66, .95),point_size=3,
+#                show.legend=FALSE)+theme_classic()+
+#   scale_fill_manual(values=c("gray85","skyblue","gray85"))+
+#   labs(title="",subtitle = expression(eta),x="",y="")+
+#   xlim(-2,2)
+# gam.gam.post<-ggplot(data=MCMCdata2,aes(x=gamma)) +
+#   stat_halfeye(aes(fill=stat(cut(x,breaks = cuts.2$gamma))),
+#                point_interval = mode_hdi, .width = c(.66, .95),
+#                point_size=3,
+#                show.legend=FALSE) +
+#   scale_fill_manual(values=c("gray85","skyblue","gray85"))+
+#   labs(title=labelsPlot.Scen[2],
+#        subtitle = expression(gamma),x="",y="")+
+#   theme_classic()
+# nrew.nrew.post<-ggplot(data=MCMCdata3,aes(x=negReward)) +
+#   stat_halfeye(aes(fill=stat(cut(x,breaks = cuts.3$negReward))),
+#                point_interval = mode_hdi, .width = c(.66, .95),
+#                point_size=3,
+#                show.legend=FALSE) +
+#   scale_fill_manual(values=c("gray85","skyblue","gray85"))+
+#   labs(title=labelsPlot.Scen[3],
+#        subtitle = expression(gamma),x="",y="")+
+#   theme_classic()+xlim(-2,2)
+# 
+# first.col<-plot_grid(nrow=3,align = "v",byrow = TRUE,
+#           gam.both.post,gam.gam.post,nrew.nrew.post,
+#           labels=c('a','c','d'))
+# second.col<-plot_grid(nrow = 2,align = "v",byrow = TRUE,
+#           nrew.both.post,panel.rsqr.all,rel_heights = c(1,2),
+#           labels = c('b','e'))
+# plot_grid(ncol = 2,first.col,second.col)
 
@@
 
-Figure \ref{fig:post} panels a,b and c show the posterior distributions
-of the parameter values of the full model, which includes both chaining
-and operant conditioning (negative reward). Posterior distributions show the probability
-density (y axis) of the estimated parameter values (x axis). Notably,
-the bulk of the posterior distribution for the parameter tuning negative
-reward ($\eta$ panel b) was around zero. Thus, the shape of the posterior
-and its credible intervals suggest the absence of negative reward to be
-well supported by the data. As for $\gamma$, the confidence intervals
-also includes zero, but the mode of the posterior is around 0.5. Thus,
-we ran the analysis setting $\eta$ to zero. Figure \ref{fig:post} panels
-d and e, show the posterior distributions of the two parameters
-estimated. Not surprisingly, under a model without negative reward, the
-distribution of $\gamma$ shifted to higher values. Under the new model,
-the estimates of $\gamma$ did not include zero and the distribution was
-centred around $0.5$. In panel f of figure \ref{fig:post} 
+Estimation of parameter values for the three models (full model,
+chaining and penalty), support chaining as the only mechanism 
+cleaners use to account for the future effects of their actions;
+and thus to solve the ephemeral reward task. In the estimation of the 
+parameter values of the full model, which includes both chaining and
+penalty, the bulk of the marginal posterior distribution of $\eta$ which 
+controls the strength of penalty is around 0 (Fig. \ref{fig:post}). 
+As for $\gamma$, controlling chaining, the 95% confidence 
+intervals also includes zero, but the mode of the posterior 
+is around 0.5 (Fig. \ref{fig:post}, a). In the chaining model, 
+where $\eta$ is set to zero, the distribution of $\gamma$ shifted 
+to higher values, zero is no longer part of the 95% credible interval
+of the parameter (Fig. \ref{fig:post}, c). In contrast, when we 
+look at the model with only penalty, the posterior distribution 
+of $\eta$ is still centred around zero (Fig. \ref{fig:post}, d). 
+Thus, the analysis of the estimates of individual parameter 
+values in the three models only supports a strong 
+effect of chaining. Furthermore, the comparison of the models` fit 
+favours the chaining model. In panel e of figure \ref{fig:post} 
 we show the distribution of $pseudo-R^2$ calculated using 
-samples from the posterior distributions shown before, 
-as well as from a model with negative reward but without
-future reward. Note, $pseudo-R^2$ can have negative values, which is when
+samples from the posterior distributions shown before. 
+Note, $pseudo-R^2$ can have negative values, which is when
 the log-likelihood of the model is lower than that of a model that
@@
 $pseudo-R^2$ distributions was not very different, the model with only
-future reward produced a distribution of $pseudo-R^2$ where more values
+chaining produced a distribution of $pseudo-R^2$ where more values
 were positive (to the right of black line in Fig. \ref{fig:post} f). This
 shows that, accounting for variation in the parameter estimates, the
-model with only future reward gives a better fit to the data, despite
-having one parameter less.
-
-```{r pred, fig.cap="Observed and predicted probability of choosing a visitor.
-Left-hand side panel: color contour shows the prediction of the learning model using the mode of the posterior distributions of parameters recovered by the statistical analysis.
-Dots show the frequency of visitor choices for the 12 reef sites, as well as the corresponding relative cleaner fish abundance (x axis) and frequency of visitors clients leaving the cleaning station (y axis).
-Right-hand side panels: Variation of the predicted probabilites  of choosing a visitor over a resident and their observed values for 12 locations.
-Circles show the mean prediction for each location from 100 samples taken from the posterior distribution.
-Thick and thin bars show the 66 and 95\\% credible interval, respectively, taken from those posterior samples.
-Squares show the predictions used for panel on the righ-hand side.
-Colour coding denotes different reef sites/year of the data collection (see Empirical data section).
-Black line corresponds to a perfect match between observed and predicted probabilities.
-Upper panels show prediction from a model including chaining and operant conditioning, lower panels from a  model with only chaining.",out.width='100%',fig.height=5}
-
-source(here("manFigures.R"))
-ggarrange(cont.obs.pred.both,scatter.obs.pred.both,
-cont.obs.pred.gam,scatter.obs.pred.gam,
-          labels=c('a','b','c','d'),common.legend = F,
-  heights=c(1.25,1))
-
-```
-
-Figure \ref{fig:pred} shows predictions from the two models, 
-one including chaining and operant conditioning (upper panels) and 
-one with only chaining (lower panels). On the
-left, the colour coded contour shows the prediction of the model for
-combinations of cleaner fish abundance (x axis) and visitor leaving
-probability (y axis). Predictions were generated by running the model
-using the mode of the posterior distributions as the parameter values,
-and varying systematically cleaner fish abundance and visitor leaving
-probability. Colour of the dots on top of the contour show the average
-frequency with which cleaner fish chose the visitor plate in their last
-20 experimental trials. Each dot corresponds to a reef-site/year of 
-data collection with a combination of cleaner fish abundance 
-and visitor leaving probability. Panels
-on the right show how close the observed values for the probability of
-choosing the visitor (y axis) were from the predictions of the models (x
-axis). The black line represents the perfect fit between observed and
-predicted values. Bars show the variation in predicted values using 100 
-samples from the posterior distribution. Despite having one more 
-parameter varying, the full model
-gave a lower fit to the data than the model without negative reward.
-In the supplementary material, we also show predictions from 
-model with only negative reward, excluding future rewards ($\gamma=0$,
-Fig. \ref{fig:nogamma}), provides a lower fit than either of the ones
-presented in the main text.
-
-The main reason for chaining and operant conditioning to give different
+model with chaining gives a better fit to the data, despite
+having one parameter less than the full model. We have not shown 
+here the marginal posterior distributions, given that they do not bring 
+biological insight. Their visualizations can be found in the supplementary 
+material (Fig. \ref{fig:scaConst}), as well as the diagnostics of the MCMCs
+(Figs. \ref{fig:diagnosticsfull},\ref{fig:diaggam},\ref{fig:diagneg}).
+
+(ref:pred) Observed and predicted probability of choosing a visitor. 
+Left-hand side panel: colour contour shows the prediction from the 
+learning model using the mode of the posterior distributions of parameters 
+recovered by the statistical analysis. Dots show the frequency of visitor 
+choices for the 12 reef sites, as well as the corresponding relative 
+cleaner fish abundance (x axis) and frequency of visitors clients leaving 
+the cleaning station (y axis). Right-hand side panels: Variation of the 
+predicted probabilities  of choosing a visitor over a resident and their 
+observed values for 12 locations. Circles show the mean prediction for 
+each location from 100 samples taken from the posterior distribution. 
+Thick and thin bars show the 66 and 95% credible interval, respectively, 
+taken from those posterior samples. Squares show the predictions used for 
+panel on the right-hand side. Colour coding denotes different reef sites/year 
+of the data collection (see Empirical data section). Black line corresponds 
+to a perfect match between observed and predicted probabilities. Upper 
+panels (a and b) show predictions from a model including chaining and 
+penalty; middle panels (c and d) from a  model with only chaining; lower 
+panel (e and f) from a model with only penalty.
+
+<!-- # ```{r pred, fig.cap='(ref:pred)',out.width='100%',fig.height=5} -->
+<!-- #  -->
+<!-- # source(here("manFigures.R")) -->
+<!-- # ggarrange(cont.obs.pred.both,scatter.obs.pred.both, -->
+<!-- # cont.obs.pred.gam,scatter.obs.pred.gam, -->
+<!-- # cont.obs.pred.Nrew,scatter.obs.pred.Nrew, -->
+<!-- #           labels=c('a','b','c','d'),common.legend = F, -->
+<!-- #   heights=c(1.25,1)) -->
+<!-- #  -->
+<!-- # ``` -->
+
+The main reason for chaining and penalty to give different
 predictions is the way that cleaner fish relative abundance influences the
@@
 similar positive effect on the probability of choosing the visitor
-clients on all three models (Fig. \ref{fig:pred}, \ref{fig:nogamma}). In
-contrast, cleaner fish relative abundance has a different effect in the
+clients on all three models, they all predict an increase preference 
+for visitors as the visitor probability increases  (Fig. \ref{fig:pred}).
+In contrast, cleaner fish relative abundance has a different effect in the
 model with only chaining, compared to the other two models,
-full model and only operant conditioning. In the model
-with only chaining, only intermediate cleaner fish abundance triggers a
-preference for the visitor clients (Fig. \ref{fig:pred} c). In models
-with negative reward, both intermediate and low cleaner abundance
-triggered a preference for the visitor. (Fig. \ref{fig:pred} a,
-\ref{fig:nogamma}).
+full model and penalty. In the model with only chaining, only intermediate 
+cleaner fish abundance triggers a preference for the visitor 
+clients (Fig. \ref{fig:pred} c). In both models with penalty, 
+both intermediate and low cleaner abundance triggered a preference 
+for the visitor (Fig. \ref{fig:pred} a,e). Note, however, we calculated 
+preferences shown in figure \ref{fig:pred} left panels by using only the mode 
+of the posterior distributions, and by holding constant the balance between 
+resident and visitors´s abundances. Panels on the right, show how close 
+predictions are from the observed data, allowing the balance between 
+client types to vary, and using a set of samples from the posterior 
+distribution.
 
@@
 While all three models captured well the positive relation between visitor 
-leaving behaviour and cleaner performance in
+leaving behaviour and cleaner fish performance in
 the market task [@triki_Biological_2019], only the chaining mechanism 
@@
 negative reward predicted the highest performance in the ephemeral 
-reward task when relative cleaner abundance is low, particularly 
+reward task when relative cleaner fish abundance is low, particularly 
 together with high probability of visitor leaving (Fig. \ref{fig:pred}).
@@
 
-Our results support chaining as the more plausible mechanism behind the 
-inter-specific variation in cleaners' performance. This suggest
-that chaining could be under positive selection. In the standard ephemeral
-reward task, however, food amount and quality are equal in the 
-two Plexiglas plates. Since our computational models simulate this aspect of
-the task, choosing visitors over residents at low cleaner fish abundances 
-does not diminish the amount of food/reward in the models. 
-On the other hand, a cleaner fish committed to visitors might find it more difficult 
-to include in its decision making other variables, like parasite load 
-and/or mucus quality [@roche_Client_2021]. Indeed, in the absence of 
-market effects, both field observations and aboratory experiments also 
-using simultaneous two choice options, show that cleaner fish base their 
-decision-making on other cues such as the mucus quality and the amount of food.  
-[@triki_Fluctuations_2019;@grutter_Cleaner_2004], as well as client size 
-as a proxy for food quantity [@wismer_Cuebased_2019;@grutter_Does_2005]. 
-How important this limitation is will determine whether chaining yields a higher
-fitness for cleaners.
-
 Previous research showed that cleaner fish living at high population 
@@
 larger forebrains; a key teleost brain region associated with 
-behavioral flexibility and social intelligence. Those failing to 
+behavioural flexibility and social intelligence. Those failing to 
 show optimized decision-rules given their local ecological 
@@
 ```
-```{r nogamma, fig.cap="Observed and predicted probability of choosing a visitor for a model without chaining.
-Left-hand side panel: color contour shows the prediction of the learning model using the mode of the posterior distributions of parameters recovered by the statistical analysis.
-Dots show the frequency of visitor choices for the 12 reef sites, as well as the corresponding relative cleaner fish abundance (x axis) and frequency of visitors leaving the station if being made to wait (y axis).
-Right-hand side panel: Right-hand side panels: Variation of the predicted probabilites  of choosing a visitor and their observed values for 12 reef sited.
-Circles show the mean prediction for each location from 100 samples taking from the posterior distribution.
-Thick and thin bars show the 66 and 95\\% credible interval taken from those posterior samples.
-Squares show the predictions used for panel on the righ-hand side.
-Colour denotes different locations (see Empirical data section).
-Black line correspond to a perfect match between observed and predicted probabilities.",fig.pos = 'H', out.extra = "",out.width='95%',fig.height=4}
-
-ggarrange(cont.obs.pred.Nrew,scatter.obs.pred.Nrew,
-          labels=c('a','b'),common.legend=FALSE)
+
+(ref:rawdata) Relation between the response variable used in this study and the 
+criteria used in previous studies to assess performance in the ephemeral reward 
+task. In the x axis, we classified the performance of cleaner fish according to 
+whether they developed a preference for the visitor in the initial round, 
+in the initial and reversal, or none of them. In the y axis, we add the choices
+of two experimental sessions: panel on the left uses one session from the initial 
+round and one from the reversal round when possible 
+(as described in the main text); panel on the right uses two sessions from the 
+initial round for all fish.
+
+```{r rawdata,fig.cap='(ref:rawdata)'}
+plot_grid(initANDRev,init,ncol = 2)
+
+```
+
+(ref:scaConst) Posterior distributions for scaling constant for the three model 
+("Full model", chaining only" and "penalty only"). We show the kernel 
+density estimates, below the mode (black dot) and the 65% (light blue shade) 
+and 95% (grey shade)  highest posterior density interval. On the top, 
+panel a shows the posterior distribution from the full model; panel b from 
+the model with only chaining; and panel c from a model with only penalty.
+
+```{r scaConst, fig.cap='(ref:scaConst)',fig.pos = 'H', out.extra = "",out.width='95%',fig.height=4}
+
+sca.both.post<-ggplot(data=MCMCdata1,aes(x=scaleConst)) + 
+  stat_halfeye(aes(fill=stat(cut(x,breaks = cuts.1$scaleConst))),
+               point_interval = mode_hdi, .width = c(.66, .95),
+               point_size=3,show.legend=FALSE) + 
+  labs(title=labelsPlot.Scen[1],x="",y="")+
+  theme_classic()+
+  scale_fill_manual(values=c("gray85","skyblue","gray85"))
+sca.gam.post<-ggplot(data=MCMCdata2,aes(x=scaleConst)) + 
+  stat_halfeye(aes(fill=stat(cut(x,breaks = cuts.2$scaleConst))),
+               point_interval = mode_hdi, 
+               .width = c(.66, .95),point_size=3,
+               show.legend=FALSE)+theme_classic()+
+  scale_fill_manual(values=c("gray85","skyblue","gray85"))+
+  labs(title=labelsPlot.Scen[2],x="",y="")
+# sca.nRew.post<-ggplot(data=MCMCdata3,aes(x=scaleConst)) +
+#   stat_halfeye(aes(fill=stat(cut(x,breaks = cuts.3$scaleConst))),
+#                point_interval = mode_hdi, .width = c(.66, .95),
+#                point_size=3,
+#                show.legend=FALSE) +
+#   scale_fill_manual(values=c("gray85","skyblue","gray85"))+
+#   labs(title=labelsPlot.Scen[3],x="",y="")+
+#   theme_classic()
+ggarrange(sca.both.post,sca.gam.post,
+          # sca.nRew.post,
+          labels=c('a','b','c'),common.legend = F)
 
@@
 ```
+
+(ref:diagnosticsfull) MCMC convergence diagnostics for the full model. 
+On the left trace-plots, on the right changes along the chain of the 
+Gelman and Rubin's shrink factor [@brooks_General_1998].
+
+```{r diagnosticsfull, fig.cap='(ref:diagnosticsfull)',echo=FALSE,fig.height=5}
+
+longMCMCdata1<-melt(MCMCdata1,id.vars = c("iteration","seed"),
+                    variable.name = "parameter",
+                    measure.vars = c("gamma","negReward","scaleConst"))
+
+parlab<-list(`gamma` =expression(gamma),
+          `negReward`=expression(eta),
+          `scaleConst`="Scaling constant")
+
+traces.full<-ggplot(longMCMCdata1,aes(x=iteration,y=value,colour=as.factor(seed)))+
+  geom_line()+
+  scale_color_manual(values = multDiscrPallet)+
+  labs(color="Chain")+
+  facet_grid(rows=vars(parameter),scales = "free",switch = "y",
+             labeller = function(variable,value){
+  return(parlab[value])})+
+  theme_classic()+
+  theme(legend.position = 'top')
+
+gel.full<-as.data.table(gelman.diag(mcmcList.1)$psrf)
+gel.full[,parameter:=c("gamma","negReward","scalConst")]
+
+pdf(file = NULL)
+gp.dat<-gelman.plot(mcmcList.1)
+dev.off()
+
+gp.dat.frame <- data.table(rbind(as.data.frame(gp.dat[["shrink"]][,,1]), 
+                          as.data.frame(gp.dat[["shrink"]][,,2])), 
+                q=rep(dimnames(gp.dat[["shrink"]])[[3]], each=nrow(gp.dat[["shrink"]][,,1])),
+                last.iter=rep(gp.dat[["last.iter"]], length(gp.dat)))
+
+gelman.full<-ggplot(melt(gp.dat.frame, c("q","last.iter"), value.name="shrink_factor"), 
+       aes(last.iter, shrink_factor, colour=q, linetype=q)) + 
+  geom_hline(yintercept=1, colour="grey30", lwd=0.2) +
+  geom_line() +
+  facet_grid(rows = vars(variable), labeller= labeller(function(var,value){
+  return(parlab[value])})) +
+  labs(x="Last Iteration in Chain", y="Shrink Factor",
+       colour="Quantile", linetype="Quantile") +
+  scale_linetype_manual(values=c(2,1))+
+  theme_classic()+
+  theme(legend.position = 'top')
+
+ggarrange(traces.full,gelman.full)
+
+```
+
+(ref:diagnosticsGam) MCMC convergence diagnostics for the chaining model. 
+On the left trace-plots, on the right changes along the chain of the 
+Gelman and Rubin's shrink factor [@brooks_General_1998]
+
+```{r diaggam,fig.cap='(ref:diagnosticsGam)',echo=FALSE}
+longMCMCdata2<-melt(MCMCdata2,id.vars = c("iteration","seed"),
+                    variable.name = "parameter",
+                    measure.vars = c("gamma","scaleConst"))
+
+parlab<-list(`gamma` =expression(gamma),
+          `scaleConst`="Scaling constant")
+
+traces.gam<-ggplot(longMCMCdata2,aes(x=iteration,y=value,colour=as.factor(seed)))+
+  geom_line()+
+  scale_color_manual(values = multDiscrPallet)+
+  labs(color="Chain")+
+  facet_grid(rows=vars(parameter),scales = "free",switch = "y",
+             labeller = function(variable,value){
+  return(parlab[value])})+
+  theme_classic()+
+  theme(legend.position = 'top')
+
+gel.gam<-as.data.table(gelman.diag(mcmcList.2)$psrf)
+gel.gam[,parameter:=c("gamma","scalConst")]
+
+pdf(file = NULL)
+gp.dat.gam<-gelman.plot(mcmcList.2)
+dev.off()
+
+gp.dat.frame.gam <- data.table(rbind(as.data.frame(gp.dat.gam[["shrink"]][,,1]), 
+                          as.data.frame(gp.dat.gam[["shrink"]][,,2])), 
+                q=rep(dimnames(gp.dat.gam[["shrink"]])[[3]], each=nrow(gp.dat.gam[["shrink"]][,,1])),
+                last.iter=rep(gp.dat.gam[["last.iter"]], length(gp.dat.gam)))
+
+gelman.gam<-ggplot(melt(gp.dat.frame.gam, c("q","last.iter"), value.name="shrink_factor"), 
+       aes(last.iter, shrink_factor, colour=q, linetype=q)) + 
+  geom_hline(yintercept=1, colour="grey30", lwd=0.2) +
+  geom_line() +
+  facet_grid(rows = vars(variable), labeller= labeller(function(var,value){
+  return(parlab[value])})) +
+  labs(x="Last Iteration in Chain", y="Shrink Factor",
+       colour="Quantile", linetype="Quantile") +
+  scale_linetype_manual(values=c(2,1))+
+  theme_classic()+
+  theme(legend.position = 'top')
+
+ggarrange(traces.gam,gelman.gam)
+```
+
+<!-- (ref:diagNeg) MCMC convergence diagnostics for the penalty model.  -->
+<!-- On the left trace-plots, on the right changes along the chain of the  -->
+<!-- Gelman and Rubin's shrink factor [@brooks_General_1998] -->
+
+<!-- ```{r diag.neg,fig.cap='(ref:diag.neg)'} -->
+<!-- longMCMCdata3<-melt(MCMCdata3,id.vars = c("iteration","seed"), -->
+<!--                     variable.name = "parameter", -->
+<!--                     measure.vars = c("negReward","scaleConst")) -->
+
+<!-- parlab<-list(`negReward` =expression(eta), -->
+<!--           `scaleConst`="Scaling constant") -->
+
+<!-- traces.neg<-ggplot(longMCMCdata3,aes(x=iteration,y=value,colour=as.factor(seed)))+ -->
+<!--   geom_line()+ -->
+<!--   scale_color_manual(values = multDiscrPallet)+ -->
+<!--   labs(color="Chain")+ -->
+<!--   facet_grid(rows=vars(parameter),scales = "free",switch = "y", -->
+<!--              labeller = function(variable,value){ -->
+<!--   return(parlab[value])})+ -->
+<!--   theme_classic()+ -->
+<!--   theme(legend.position = 'top') -->
+
+<!-- pdf(file = NULL) -->
+<!-- gp.dat.neg<-gelman.plot(mcmcList.3) -->
+<!-- dev.off() -->
+
+<!-- gp.dat.frame.neg <- data.table(rbind(as.data.frame(gp.dat.neg[["shrink"]][,,1]),  -->
+<!--                           as.data.frame(gp.dat.neg[["shrink"]][,,2])),  -->
+<!--                 q=rep(dimnames(gp.dat.neg[["shrink"]])[[3]], each=nrow(gp.dat.neg[["shrink"]][,,1])), -->
+<!--                 last.iter=rep(gp.dat.neg[["last.iter"]], length(gp.dat.neg))) -->
+
+<!-- gelman.neg<-ggplot(melt(gp.dat.frame.neg, c("q","last.iter"), value.name="shrink_factor"),  -->
+<!--        aes(last.iter, shrink_factor, colour=q, linetype=q)) +  -->
+<!--   geom_hline(yintercept=1, colour="grey30", lwd=0.2) + -->
+<!--   geom_line() + -->
+<!--   facet_grid(rows = vars(variable), labeller= labeller(function(var,value){ -->
+<!--   return(parlab[value])})) + -->
+<!--   labs(x="Last Iteration in Chain", y="Shrink Factor", -->
+<!--        colour="Quantile", linetype="Quantile") + -->
+<!--   scale_linetype_manual(values=c(2,1))+ -->
+<!--   theme_classic()+ -->
+<!--   theme(legend.position = 'top') -->
+
+<!-- ggarrange(traces.neg,gelman.neg) -->
+<!-- ``` -->

### 2022-02-22 manuscript_1.0/manuscript_1.0.tex
Error found in the manual coding of the cleaner entries used to compute visitor preference. In loadFieldData.R a programatic way of coding cleaner entries was done. Now that the manual and programatic results coincide I can re-run the chains. New figure configurations were implemented. Among those supplementary figures showing the diagnostics of the MCMC. A new result section was written.

@@
 One plate is made to behave like a resident, i.e.~it remains until
-the cleaner had eaten off it. The other plate was made to behave
+the cleaner fish had eaten off it. The other plate was made to behave
 like a visitor, i.e.~it is removed if not inspected first.
@@
 different roles as either a visitor (ephemeral food source) or
-resident (permanent food source). That is, if a cleaner inspected the
+resident (permanent food source). That is, if a cleaner fish inspected the
 resident plate first, the experimenter withdrew the visitor plate out of
@@
 never reached the learning criterion for visitor plate
-\(\color{red}{\text{(N = XX cleaner fish)}}\).
+(\(N = 45\) cleaner fish).
 For those who reached the learning criterion at some point during the
@@
 and the last 10 trials they were exposed to in the test
-\(\color{red}{\text{(N = XX cleaner fish)}}\).
+(\(N = 75\) cleaner fish).
 
@@
 a combination of these effects is a better explanation for the pattern
-seen in the data. We used the
-ecological variables: cleaners, visitor clients,
-resident clients abundances and
-visitor clients leaving probability, as input to the models.
-As response variable we used cleaners' preference for visitor
-over residents in the ephemeral reward task.
+seen in the data. We used the ecological variables: cleaners, visitor clients,
+resident clients abundances and visitor clients leaving probability,\\
+as input to the models. As response variable we used cleaners'
+preference for visitor over residents in the ephemeral reward task.
 Finally, we used the preference for visitors resulting from the
@@
 the absolute population densities of cleaner fish from the empirical data
-to a measure of relative abundances that captures
-client visitation patterns. This is because in the model, relative
-abundances of clients define not only the probability of residents and visitors,
+to a measure of relative abundances that captures client visitation patterns.
+This is because in the model, relative abundances of clients
+define not only the probability of residents and visitors,
 but also how often the cleaning station is empty (e.g.~there are no
@@
 constant is hence meant to capture variation in the market conditions driven
-partly by cleaner abundance. We fitted the value of the scaling constant as
+partly by cleaner fish abundance. We fitted the value of the scaling constant as
 part of the statistical inference. As for the visitor and resident
@@
 the process for \(1e^5\) steps. We ran 5 independent chains,
-discarded the first \(100\) samples of each chain as burn in,
+discarded the first \(1000\) samples of each chain as burn in,
 and after that we kept 1 in every 100 samples to avoid autocorrelation.
@@
 \subsection{Results}\label{results}}
-
-\begin{figure}
-
-{\centering \includegraphics[width=1\linewidth]{manuscript_1.0_files/figure-latex/post-1}
-
-}
-
-\caption{Posterior distributions for parameter values $\gamma$, $\eta$ and the scaling constant.
-We show the kernel density estimates, below the mode (black dot) and the 65\% (light blue shade) and 95\% (grey shade)  highest posterior density interval for the three paramteres.
-On the left, panels a, b and c show posterior distributions for a model with all three parameters; while on the right, d and e, show a model with only chaining.
-Panel f shows a measure of fit for both models, namely the distribution of pseudo-$R^2$ obtained from sampling the posterior distribution of parameter values.}\label{fig:post}
-\end{figure}
 
@@
 having one parameter less.
-
-\begin{figure}
-
-{\centering \includegraphics[width=1\linewidth]{manuscript_1.0_files/figure-latex/pred-1}
-
-}
-
-\caption{Observed and predicted probability of choosing a visitor.
-Left-hand side panel: color contour shows the prediction of the learning model using the mode of the posterior distributions of parameters recovered by the statistical analysis.
-Dots show the frequency of visitor choices for the 12 reef sites, as well as the corresponding relative cleaner fish abundance (x axis) and frequency of visitors clients leaving the cleaning station (y axis).
-Right-hand side panels: Variation of the predicted probabilites  of choosing a visitor over a resident and their observed values for 12 locations.
-Circles show the mean prediction for each location from 100 samples taken from the posterior distribution.
-Thick and thin bars show the 66 and 95\% credible interval, respectively, taken from those posterior samples.
-Squares show the predictions used for panel on the righ-hand side.
-Colour coding denotes different reef sites/year of the data collection (see Empirical data section).
-Black line corresponds to a perfect match between observed and predicted probabilities.
-Upper panels show prediction from a model including chaining and operant conditioning, lower panels from a  model with only chaining.}\label{fig:pred}
-\end{figure}
 
@@
 While all three models captured well the positive relation between visitor
-leaving behaviour and cleaner performance in
+leaving behaviour and cleaner fish performance in
 the market task \citep{triki_Biological_2019}, only the chaining mechanism
@@
 negative reward predicted the highest performance in the ephemeral
-reward task when relative cleaner abundance is low, particularly
+reward task when relative cleaner fish abundance is low, particularly
 together with high probability of visitor leaving (Fig. \ref{fig:pred}).
@@
 Our results support chaining as the more plausible mechanism behind the
-inter-specific variation in cleaners' performance. This suggest
+intra-specific variation in cleaners' performance. This suggest
 that chaining could be under positive selection. In the standard ephemeral
@@
 and/or mucus quality \citep{roche_Client_2021}. Indeed, in the absence of
-market effects, both field observations and aboratory experiments also
+market effects, both field observations and laboratory experiments also
 using simultaneous two choice options, show that cleaner fish base their
@@
 larger forebrains; a key teleost brain region associated with
-behavioral flexibility and social intelligence. Those failing to
+behavioural flexibility and social intelligence. Those failing to
 show optimized decision-rules given their local ecological
@@
 
-\begin{figure}[H]
+\begin{figure}
 
-{\centering \includegraphics[width=0.95\linewidth,]{manuscript_1.0_files/figure-latex/nogamma-1}
+{\centering \includegraphics{manuscript_1.0_files/figure-latex/rawdata-1}
 
@@
 
-\caption{Observed and predicted probability of choosing a visitor for a model without chaining.
-Left-hand side panel: color contour shows the prediction of the learning model using the mode of the posterior distributions of parameters recovered by the statistical analysis.
-Dots show the frequency of visitor choices for the 12 reef sites, as well as the corresponding relative cleaner fish abundance (x axis) and frequency of visitors leaving the station if being made to wait (y axis).
-Right-hand side panel: Right-hand side panels: Variation of the predicted probabilites  of choosing a visitor and their observed values for 12 reef sited.
-Circles show the mean prediction for each location from 100 samples taking from the posterior distribution.
-Thick and thin bars show the 66 and 95\% credible interval taken from those posterior samples.
-Squares show the predictions used for panel on the righ-hand side.
-Colour denotes different locations (see Empirical data section).
-Black line correspond to a perfect match between observed and predicted probabilities.}\label{fig:nogamma}
+\caption{Relation between the response variable used in this study and the
+criteria used in previous studies to assess performance in the ephemeral reward
+task. In the x axis, we classified the performance of cleaner fish according to
+whether they developed a preference for the visitor in the initial round,
+in the initial and reversal, or none of them. In the y axis, we add the choices
+of two experimental sessions: panel on the left uses one session from the initial
+round and one from the reversal round when possible
+(as described in the main text); panel on the right uses two sessions from the
+initial round for all fish.}\label{fig:rawdata}
+\end{figure}
+
+\begin{figure}[H]
+
+{\centering \includegraphics[width=0.95\linewidth,]{manuscript_1.0_files/figure-latex/scaConst-1}
+
+}
+
+\caption{Posterior distributions for scaling constant for the three model
+(``Full model'', chaining only'' and ``penalty only''). We show the kernel
+density estimates, below the mode (black dot) and the 65\% (light blue shade)
+and 95\% (grey shade) highest posterior density interval. On the top,
+panel a shows the posterior distribution from the full model; panel b from
+the model with only chaining; and panel c from a model with only penalty.}\label{fig:scaConst}
 \end{figure}
@@
 
+\begin{verbatim}
+## pdf 
+##   2
+\end{verbatim}
+
+\begin{figure}
+
+{\centering \includegraphics{manuscript_1.0_files/figure-latex/diagnosticsfull-1}
+
+}
+
+\caption{MCMC convergence diagnostics for the full model.
+On the left trace-plots, on the right changes along the chain of the
+Gelman and Rubin's shrink factor \citep{brooks_General_1998}.}\label{fig:diagnosticsfull}
+\end{figure}
+
+\begin{verbatim}
+## pdf 
+##   2
+\end{verbatim}
+
+\begin{figure}
+
+{\centering \includegraphics{manuscript_1.0_files/figure-latex/diaggam-1}
+
+}
+
+\caption{MCMC convergence diagnostics for the chaining model.
+On the left trace-plots, on the right changes along the chain of the
+Gelman and Rubin's shrink factor \citep{brooks_General_1998}}\label{fig:diaggam}
+\end{figure}
+
 \ethics{The Animal Ethics Committee of the Queensland government (DAFF)

### 2022-02-22 ActCritMCMC.cpp

@@ -1092,39 +1092,39 @@ int main(int argc, char* argv[]){
 	// Only for debugging 
 	// input parameters provided by a JSON file with the following
 	// structure:
-	//json sim_param;
-	//sim_param["totRounds"]    = 5000;
-	//sim_param["ResReward"]    = 1;
-	//sim_param["VisReward"]    = 1;
-	//sim_param["ResProbLeav"]  = 0;
-	//sim_param["scenario"]  = 0;
-	//sim_param["inbr"]         = 0;
-	//sim_param["outbr"]        = 0;
-	//sim_param["seed"]         = 3;
-	//sim_param["forRat"]       = 0.0;
-	//sim_param["propfullPrint"]       = 0.7;
-	//sim_param["sdPert"]       = {0.05, 0.05 ,0.15 ,0.1, 10}; 
-	//// alphaA, alphaC, Gamma, NegRew,scaleConst
-	//sim_param["chain_length"] = 100;
-	//sim_param["init"]       = {0.05, 0.05 , 0.93,0.02, 58};
-	//sim_param["init2"] =	{ 0.05, 0.05 , 0.93,0.02, 58 };
-	// //alphaA, alphaC, gamma, NegRew, scaleConst
-	//sim_param["pertScen"] = {false,false,true,true,true};
-	////enum perturnScen {all,  bothFut, justGam, justNegRew};
-	//sim_param["MCMC"] = 0;
-	//sim_param["data"] = "clean"; // "loc", "clean"
-	//sim_param["nRep"] = 30 ;
-	//sim_param["folder"] = "M:/Projects/LearnDataModel/Simulations/test_/";
-	//sim_param["dataFile"] = "M:/Projects/LearnDataModel/Data/data_cleaner_abs_threa1.5.txt";
-	//sim_param["Group"] = true;
+	json sim_param;
+	sim_param["totRounds"]    = 5000;
+	sim_param["ResReward"]    = 1;
+	sim_param["VisReward"]    = 1;
+	sim_param["ResProbLeav"]  = 0;
+	sim_param["scenario"]  = 0;
+	sim_param["inbr"]         = 0;
+	sim_param["outbr"]        = 0;
+	sim_param["seed"]         = 3;
+	sim_param["forRat"]       = 0.0;
+	sim_param["propfullPrint"]       = 0.7;
+	sim_param["sdPert"]       = {0.05, 0.05 ,0.15 ,0.1, 10}; 
[…]

### 2022-02-22 analysisMCMC.R

@@ -8,6 +8,7 @@ library(coda)
 library(ggplot2)
 library(cowplot)
 library(ggdist)
+library(ggpubr)
 source(here("../R_files/posPlots.R"))
 source(here("loadData.R"))
 library("jsonlite")
@@ -19,7 +20,7 @@ scen3<-"MCMCclean_Nrew_sca_"
 
 # NLables names for the three scenarios
 labels.Scen<-c("both","gam","Nrew")
-labelsPlot.Scen<-c("Full model","Future reward","Negative reward")
+labelsPlot.Scen<-c("Full model","Chaining","Penalty")
 
 ## Load files --------------------------------------------------------------
 
@@ -47,16 +48,10 @@ mcmcList.2<-mcmc.list(do.call(list,lapply(unique(MCMCdata2$seed), function(repli
 })))
 
 
-mcmcList.2<-mcmc.list(do.call(list,lapply(unique(MCMCdata2$seed), function(repli){
-  rundata<-MCMCdata2[seed==repli]
-  mcmcRun<-mcmc(rundata[,.(gamma,scaleConst)],thin = thinning)#
-  return(mcmcRun)
-})))
-
 
 mcmcList.3<-mcmc.list(do.call(list,lapply(unique(MCMCdata3$seed), function(repli){
   rundata<-MCMCdata3[seed==repli]
-  mcmcRun<-mcmc(rundata[,.(negReward,scaleConst)],thin = 100)#
+  mcmcRun<-mcmc(rundata[,.(negReward,scaleConst)],thin =thinning)#
   return(mcmcRun)
 })))
 
@@ -66,97 +61,99 @@ mcmcList.3<-mcmc.list(do.call(list,lapply(unique(MCMCdata3$seed), function(repli
 
 
 
-# ABC.gamma.time.short<-dcast(MCMCdata1,iteration~seed,value.var = c("gamma"))
-# ABC.nRew.time.short<-dcast(MCMCdata1,iteration~seed,value.var = "negReward")
-# ABC.sca.time.short<-dcast(MCMCdata1,iteration~seed,value.var = "scaleConst")
-# ABC.logLike.time.short<-dcast(MCMCdata1,iteration~seed,value.var = "fit")
-# 
-# par(plt=posPlot(numploty = 4,idploty = 4,numplotx = 2,idplotx = 1)-c(0.05,0.05,0,0),
-#     mfrow=c(1,1),las=1)
[…]

### 2022-02-22 loadFieldData.R

@@ -5,6 +5,9 @@ library("here")
 library("readxl")
 library('dplyr')
 library('ggplot2')
+library('cowplot')
+library("ggbeeswarm")
+source(here("aesth_par.R"))
 
 ## Load field data based on the market experiment performance criteria
 fieldData<-fread(here("Data","market_model.csv"))
@@ -23,84 +26,202 @@ fieldData.site<-fieldData[,lapply(.SD,max),by=site_year,
 
 
 ## Load the experimental data
-fieldData.cleaner<-data.table(read_xlsx(here("Data","market_raw_data.xlsx"),sheet = "round_data"))
+fieldData.cleaner<-data.table(read_xlsx(here("Data","market_raw_data.xlsx"),
+                                        sheet = "round_data"))
 
 fieldData.cleaner[,unique(site_year)]
 
 # Fix mistake in location code name
 fieldData.cleaner[site_year=="NHS2017",site_year:="NHS 2017"]
 
+# standarize cleaner IDs and reef-year sites
+fieldData.cleaner[,cleaner_ID:=gsub(" ",replacement = "",x = cleaner_ID)]
+fieldData.cleaner[,cleaner_ID:=gsub("c",replacement = "C",x = cleaner_ID)]
+fieldData.cleaner[,cleaner_ID:=gsub("l",replacement = "L",x = cleaner_ID)]
+fieldData.cleaner[,site_year:=gsub(" ",replacement = "_",x = site_year)]
+
+# get scores from last two session, both initial and reversal
+fieldData.cleaner.filt<-fieldData.cleaner[,.SD[c(.N-1,.N)],
+                                          by=.(site_year,cleaner_ID,
+                                               stage)]
+fieldData.cleaner.filt<-fieldData.cleaner.filt[stage!="NA"]
+fieldData.cleaner.filt[,score_visitor:=as.numeric(score_visitor)]
 
 
-# Choose data from the last 20 experimental choices
-fieldData.cleaner[,use_sims:=ifelse(is.na(use_sims),0,1)]
-fieldData.cleaner[,use_sims:=as.logical(use_sims)]
+fieldData.cleaner.filt.sum<-fieldData.cleaner.filt[,length(score_visitor),
+                       by=.(site_year,cleaner_ID)]
 
-fieldData.filt<-fieldData.cleaner[use_sims==T,]
-fieldData.filt[,score_visitor:=as.numeric(score_visitor)]
[…]

### 2022-02-22 manFigures.R

@@ -302,7 +302,7 @@ cont.obs.pred.Nrew<- ggplot(data = FIAinterpData.Nrew,aes(x=rel.abund.cleaners,y
              shape=21,color="black")+sc+xlab("Relative cleaner abundance")+
   ylab("Probability of visitor leaving")+
   labs(fill="Probability \n of choosing \n a visitor")+
-  theme(legend.position = "top",
+  theme(legend.position = "none",
     axis.text = element_text(size=axisSize),
     axis.title.x = element_text(size=axislabSize),
     axis.title.y = element_text(size=axislabSize))
@@ -320,7 +320,7 @@ scatter.obs.pred.Nrew<-ggplot(data=fieldatabyLocSamps.Nrew,
   guides(color=guide_legend(title="Location"))+
   scale_color_manual(values = multDiscrPallet[1:12],
                      name = "Location")+
-  theme_classic()+theme(legend.position ="top",#c(.9, .4),
+  theme_classic()+theme(legend.position ="none",#c(.9, .4),
                       axis.text = element_text(size=axisSize),
                       axis.title.x = element_text(size=axislabSize),
                       axis.title.y = element_text(size=axislabSize),

### 2022-02-22 parTOjson.R

@@ -6,6 +6,8 @@ source(here("loadData.R"))
 
 simsDir<-"Simulations"
 
+clusterHome<-"/home/ubuntu"
+
 fileName<-"parameters.json"
 
 
@@ -13,7 +15,7 @@ fileName<-"parameters.json"
 
 # name of the scenariofor which parameter files will be produces
 # format used for the name: MCMCclean_*parameter1_paramerter2_parameter3
-scenario<-"MCMCclean_nRew_sca"
+scenario<-"MCMCclean_gam_nRew_sca2"
 
 # for MCMC
 param_mcmc<-list(totRounds=10000, # Number of rounds in the learning model
@@ -31,14 +33,17 @@ param_mcmc<-list(totRounds=10000, # Number of rounds in the learning model
                  chain_length=100000, # Chain length
                  init=c(0.05,0.05,0,0,30), # Initial values for each of the parameters
                  # alphaA,AlphaC, Gamma, NegRew, scalConst
-                 pertScen = c(FALSE,FALSE,FALSE,TRUE,TRUE), # boolean controlling which
+                 pertScen = c(FALSE,FALSE,TRUE,TRUE,TRUE), # boolean controlling which
                  # parameter is perturbed
                  MCMC =1, # run chain=1, run prediction for one parameter set = 0
                  data="clean", # use all cleaner data = 1, use data by reef sites
                  nRep=1, # number of replicate simulations
                  Group = FALSE, # grouped data according to social competence
                  # from triki et al. 2020
-                 dataFile = here("Data","data_cleaner_abs_threa1.5.txt"),
+                 dataFile =
+                 # paste(clusterHome,"Data","data_cleaner_abs_threa1.5.txt",
+                 #                  sep="/"),
+                   here("Data","data_cleaner_abs_threa1.5.txt"),
                  # location of the data file
                  # here("Simulations",
                  #                 paste0(scenario,"_"),"data_MCMC_fake.txt"))
@@ -56,8 +61,10 @@ check_create.dir(here(simsDir),param = rep(scenario,1),
[…]

### 2022-02-28 manuscript_1.0/manuscript_1.0.Rmd
New version of the manuscript. Using figure from the old data.

@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = FALSE,warning = FALSE,message=FALSE)
+knitr::opts_chunk$set(echo = FALSE,warning = FALSE,message=FALSE,cache = TRUE)
 library(here)
@@
 
-Disentangling the mechanistic underpinnings of behaviour 
-is typically done under controlled conditions in a laboratory setting. However, 
-controlled laboratory conditions often mask the inter and intra-specific 
-variation that arises in the interaction between mechanisms and 
-environmental variation. From a evolutionary perspective, mechanisms 
-are likely selected because of how they allow individuals to respond to 
-environmental variation. For example, biological market theory predicts that 
-the exchange rate of goods and/or services traded between cooperative 
-partners adjusts to the law of supply and demand, when individuals have 
-some degree of partner choice [@noe_Biological_1995a]. 
-Supply and demand conditions, which typically 
+Often alternative cognitive mechanisms yield similar behaviour and/or cognitive
+performances. This poses a problem for disentangling the mechanistic 
+underpinnings of behaviour. This is particularly clear in research aimed at
+discovering interspecific variation in *higher* cognitive abilities; or 
+in other words, research on whether non-human animals show cognitive 
+abilities believed to be uniquely human. For instance, when researchers 
+try to find *mental time travel-like* behaviour, they usually come up with 
+clever experiments showing the behaviour displayed requires inferences made 
+through past events[@dally_Foodcaching_2006]. However, they often face challenges proposing alternative scenarios where simple associations can bring about the 
+predicted behavioural outcome [@suddendorf_Evolution_2007]. Similarly, attempts 
+to show *theory of mind* in non-human animals face objections 
+justified by alternative mechanisms that bring about similar behavioural 
+results [@heyes_Theory_1998]. Such controversies are usually settled by 
+using the principle of parsimony, and it's cognitive version, 
+Lloyd Morgan’s cannon. Which states that the simpler explanation (mechanism)
+must be accepted. Ideally, however, alternative hypothesis should be evaluated 
+in light of their explanatory power. One potential dimension that could allow
+the variation necessary among distinct cognitive mechanisms is environmental
+variation. Controlled laboratory conditions often mask the inter and 
+intra-specific variation that arises in the interaction between mechanisms and 
+environments. Thus, if predictions from the alternative mechanisms change
+with environmental conditions, it is possible to asses the explanatory power 
+of the different hypothesis by performing behavioural test in the context of
+different environmental conditions.
+
+From a evolutionary perspective, mechanisms are likely selected because 
+of how they allow individuals to respond to environmental variation. 
+For example, biological market theory predicts that the exchange rate of goods 
+and/or services traded between cooperative partners adjusts to the 
+law of supply and demand, when individuals have some degree of partner choice
+[@noe_Biological_1995]. Supply and demand conditions, which typically 
 depend on the abundance of the species involved, certainly vary in time 
-and space. Therefore, natural selection should 
-favour the ability to flexibly adjust decisions and behavioural output to 
+and space. Therefore, natural selection should favour the ability 
+to flexibly adjust decisions and behavioural output to 
 current market conditions. Indeed, such adjustments have been repeatedly 
@@
 market conditions have been documented in a great variety of species with 
-highly variable brain anatomies, the question arises to what extent mechanisms 
-beyond basic associative learning may be involved.
+highly variable brain anatomies, the question arises to what extent 
+mechanisms beyond basic associative learning may be involved.
 
@@
 visitors service priority in a field study in the Red Sea
-[@bshary_Cleaner_2001a].
+[@bshary_Cleaner_2001].
 
@@
 like a visitor, i.e. it is removed if not inspected first. 
+This laboratory paradigm originally inspired by the cleaning market 
+of cleaner fish is more generally refered as the ephemeral reward task. 
+Individuals are assesed in their capacity to develop a preference for the 
+ephemeral option, which gives them access to two reward units.
 Cleaners learned to prefer the visitor plate and
@@
 Furthermore, adult cleaner fish outperformed various primates as well as rats and
-pigeons in this original version of the biological market task
+pigeons in this original version of the ephemeral reward task
 [@salwiczek_Adult_2012; @zentall_Early_2017]; yet the African grey
-parrots solve this task as well [@pepperberg_Can_2014]. Given that primates 
-are known to readily distinguish 
-between one and two reward units if presented in more conventional ways 
-$\color{red}{\text{ref}}$, this raises the question:
-what makes the task difficult for most non-cleaners?
+parrots solve this task as well [@pepperberg_Can_2014]. This interspecific
+variation in performance, and primates' known cognitive abilities $\color{red}{\text{ref}}$, shows that performane in the task
+cannot be readily explained by classifying species as having high and 
+low cognitive abilities. Instead, this inter-spefic variation suggest
+that solving the ephemeral reward task requires a set of cognitive 
+mechanisms that are not present in all the tested taxa, or were not used 
+under the experimental set-up.
 
@@
 for individual performance. For example, some animals find relevant 
-information in the plates 
- [@wismer_Cuebased_2019] while others find it in the food 
-[@pretot_Comparative_2021; @pretot_Comparing_2016]. However, identifying 
-cues as salient is not the only challenge of the ephemeral reward task, 
-as revealed by proximate learning models. Such models allow varying the 
-cognitive tool kit and to evaluate which minimal kit is necessary to solve 
+information in the plates  [@wismer_Cuebased_2019] while others find 
+it in the food [@pretot_Comparative_2021; @pretot_Comparing_2016]. 
+However, identifying cues as salient is not the only challenge 
+of the ephemeral reward task, as revealed by proximate learning models. 
+Such models allow varying the cognitive tool kit and to evaluate 
+which minimal kit is necessary to solve 
 the task at hand (e.g. [@dubois_Model_2021]). Applied to the ephemeral 
@@
 Lloyd Morgan’s cannon demands that operant conditioning as the simpler 
-explanation is to be accepted by default. Ideally, the two mechanisms should 
-be evaluated in light of how well they explain the available data.
+explanation is to be accepted by default. Ideally, however, the two 
+mechanisms should be evaluated in light of how well 
+they explain the available data. Note that different fields interested in
+cognition and desicion making use different words to refer to negative 
+reinforcers [@quinones_Reinforcement_2019;@sutton_Reinforcement_2018]. 
+In here, for the sake of simplicity and clarity, we will use the word 
+'penalty' to refer to this mechanism which includes a negative reinforcer.
 
@@
 mechanism cleaner fish use to incorporate future consequences of current 
-decisions by testing whether operant conditioning, chaining, or a combination 
+decisions by testing whether chaining, penalty, or a combination 
 of both best explains their performance; (ii)  determining whether the 
@@
 local cleaner-to-client ratio.
-<!-- In this case, as visitor leaving rates  -->
-<!-- should be low as well and any leaving visitor will be readily  -->
-<!-- replaced by another client in the queue. In contrast,  -->
-<!-- cleaners should show high performance in the ephemeral reward task -->
-<!-- if the local cleaner-to-client ratio favours clients.  -->
 
@@
 also work together.  First, $\gamma$ measures how
-much individuals include future rewards in their decision updates. If
-$\gamma=0$, individuals only use the immediate reward obtained from a
+much individuals include future rewards in their decision updates. 
+If $\gamma=0$, individuals only use the immediate reward obtained from a
 cleaning interaction. As $\gamma$ increases individuals include more the
 reward obtained from the subsequent choices. That amounts to calculating
-and using for decision making the future expected rewards of an action.
+and using for decision making the future expected rewards of an action (chaining).
 Second, $\eta$ measures how much individuals include in their reward the
-fleeing behaviour of visitor as a negative component. Both of
+fleeing behaviour of visitor as a negative component (penalty). Both of
 these parameters allow individuals to use in their estimates the future
@@
 was hence used in the analyses as representative of both measures.
-
-<!-- Cleaner densities, in interaction with visitor client leaving probability,  -->
-<!-- explained best individual performance in the ephemeral reward task  -->
-<!-- [@triki_Biological_2019], while cleaner-to-client ratio was not a significant  -->
-<!-- factor. This creates a certain mismatch with the model by Quiñones *et al.*  -->
-<!-- [@quinones_Reinforcement_2019], which focused on abundance of cleaners relative  -->
-<!-- to overall client abundance in order to capture the characteristics  -->
-<!-- of the market. Importantly, relative abundances of clients define not only  -->
-<!-- the probability of interactions with residents and visitors, but also affect  -->
-<!-- how often the cleaning station is empty (e.g. there are no clients to be cleaned).  -->
-<!-- The higher the relative abundance of cleaners is, the higher is the probability  -->
-<!-- of cleaning stations being empty at a given time point. How often the  -->
-<!-- cleaning stations are empty in turns influences the value that cleaners can  -->
-<!-- expect from their choices. The emptier the cleaning stations are, the more  -->
-<!-- beneficial it is to prioritize a client that will not stay. On the other hand,  -->
-<!-- situations where cleaners have to choose will be rare if cleaner fidh relative  -->
-<!-- abundance is high, which reduces the total value of prioritizing visitors  -->
-<!-- over residents and makes it more difficult to learn a preference for visitors.  -->
-<!-- Given the model structure, we used the empirical data to calculate relative  -->
-<!-- abundances of cleaners, residents and visitors for the current analyses.  -->
-<!-- To incorporate the empirical finding that absolute densities matter, we  -->
-<!-- introduced a new scaling constant (see section on model fitting).  -->
 
@@
 ($N = `r fieldData.cleaner.filt.sum[V1>2,length(V1)]`$ cleaner fish). 
+We chose a combination of initial and reversal to quantify preference 
+for the visitor client, given that it matches well the criteria chosen 
+in previous analysis of the ephemeral reward task experimental set-up
+[@triki_Biological_2019;@triki_Brain_2020]. In the 
+suplementaty material (Fig. \ref{fig:rawdata}) we show how our choice maps
+to the previously used criteria. For comparison, we also show a quantification 
+of visitor preference based only on the initial phase of the experiments.
 
@@
 (ref:post) Posterior distributions for parameter values $\gamma$ and $\eta$ for 
-the three model ("Full model", "chaining only" and "penalty only"). We show 
+the three models ("Full model", "chaining only" and "penalty only"). We show 
 the kernel density estimates, below the mode (black dot) and the 65% 
@@
 # Name of the folders containing the MCMC runs
-scen1<-"MCMCclean_gam_nRew_sca_"
-scen2<-"MCMCclean_gam_sca_"
-scen3<-"MCMCclean_Nrew_sca_"
+# scen1<-"MCMCclean_gam_nRew_sca_"
+# scen2<-"MCMCclean_gam_sca_"
+# scen3<-"MCMCclean_Nrew_sca_"
+
+scen1<-"MCMCclean_gam_Nrew_sca_old_"
+scen2<-"MCMCclean_gam_sca_old_"
+scen3<-"MCMCclean_Nrew_sca_old_"
 
@@
 MCMCdata2<-loadMCMCrun(scen2,thinning = thinning,burn.in = burn.in)
-# MCMCdata3<-loadMCMCrun(scen3,thinning = thinning,burn.in = burn.in)
+MCMCdata3<-loadMCMCrun(scen3,thinning = thinning,burn.in = burn.in)
 
@@
 
-# mcmcList.3<-mcmc.list(do.call(list,lapply(unique(MCMCdata3$seed), function(repli){
-#   rundata<-MCMCdata3[seed==repli]
-#   mcmcRun<-mcmc(rundata[,.(gamma,scaleConst)],thin = thinning)#
-#   return(mcmcRun)
-# })))
+mcmcList.3<-mcmc.list(do.call(list,lapply(unique(MCMCdata3$seed), function(repli){
+  rundata<-MCMCdata3[seed==repli]
+  mcmcRun<-mcmc(rundata[,.(negReward,scaleConst)],thin = thinning)#
+  return(mcmcRun)
+})))
 
@@
 
-# cuts.3<-lapply(MCMCdata3[,.(negReward,scaleConst)],
-#                function(x){
-#                  c(mode_hdci(x,.width = intervals[c(2,1)])$ymin,
-#                    mode_hdci(x,.width = intervals)$ymax)
-#                })
+cuts.3<-lapply(MCMCdata3[,.(negReward,scaleConst)],
+               function(x){
+                 c(mode_hdci(x,.width = intervals[c(2,1)])$ymin,
+                   mode_hdci(x,.width = intervals)$ymax)
+               })
 
 # get all the likelihoods from the posterior for all models
-# loglikehoods.all<-data.table(lglikelihood=c(MCMCdata1$fit,MCMCdata2$fit,
-#                                              MCMCdata3$fit),
-#                               model=c(rep(labels.Scen[1],length(MCMCdata1$fit)),
-#                                       rep(labels.Scen[2],length(MCMCdata2$fit)),
-#                                       rep(labels.Scen[3],length(MCMCdata3$fit))
-#                                       ))
-# 
-# # Read field data to calculate null log-likelihood
-# fieldData<-fread(here("Data","data_cleaner_abs_threa1.5.txt"))
-# 
-# nullLikehood<-sum(dbinom(x=fieldData[,score_visitor],
-#                          size = 20,prob = 0.5,log = TRUE))
-# 
-# # calculate pseudo R^2
-# loglikehoods.all[,Rsqrd:=1-lglikelihood/nullLikehood]
-# 
-# 
-# panel.rsqr.all<-
-#   ggplot(data=loglikehoods.all[is.finite(lglikelihood)],
-#                   aes(y=model,x=Rsqrd,fill=model))+
-#   stat_halfeye(alpha=0.5,point_size=3)+
-#   theme_classic()+#xlim(-0.5,0.25)+
-#   scale_fill_manual(values=c("#1b9e77","#d95f02","#7570b3"),
-#   name = "Model", labels = labelsPlot.Scen)+
-#   scale_y_discrete(labels=labelsPlot.Scen)+
-#   geom_vline(xintercept = 0,color="black",size=0.5)+
-#   theme(legend.position = 'none')
-#           # c(.32, .65)
-#         # ,legend.key.size = unit(0.22,'cm'),
-#         # axis.text.y = element_blank(),
-#         # legend.text = element_text(size=7))
-# 
-# gam.both.post<-ggplot(data=MCMCdata1,aes(x=gamma)) +
-#   stat_halfeye(aes(fill=stat(cut(x,breaks = cuts.1$gamma))),
-#                point_interval = mode_hdi, .width = c(.66, .95),
-#                point_size=3,show.legend=FALSE) +
-#   labs(title=labelsPlot.Scen[1],
-#        subtitle = expression(gamma),x="",y="")+
-#   theme_classic()+
-#   scale_fill_manual(values=c("gray85","skyblue","gray85"))
-# 
-# nrew.both.post<-ggplot(data=MCMCdata1,aes(x=negReward)) +
-#   stat_halfeye(aes(fill=stat(cut(x,breaks = cuts.1$negReward))),
-#                point_interval = mode_hdi,
-#                .width = c(.66, .95),point_size=3,
-#                show.legend=FALSE)+theme_classic()+
-#   scale_fill_manual(values=c("gray85","skyblue","gray85"))+
-#   labs(title="",subtitle = expression(eta),x="",y="")+
-#   xlim(-2,2)
-# gam.gam.post<-ggplot(data=MCMCdata2,aes(x=gamma)) +
-#   stat_halfeye(aes(fill=stat(cut(x,breaks = cuts.2$gamma))),
-#                point_interval = mode_hdi, .width = c(.66, .95),
-#                point_size=3,
-#                show.legend=FALSE) +
-#   scale_fill_manual(values=c("gray85","skyblue","gray85"))+
-#   labs(title=labelsPlot.Scen[2],
-#        subtitle = expression(gamma),x="",y="")+
-#   theme_classic()
-# nrew.nrew.post<-ggplot(data=MCMCdata3,aes(x=negReward)) +
-#   stat_halfeye(aes(fill=stat(cut(x,breaks = cuts.3$negReward))),
-#                point_interval = mode_hdi, .width = c(.66, .95),
-#                point_size=3,
-#                show.legend=FALSE) +
-#   scale_fill_manual(values=c("gray85","skyblue","gray85"))+
-#   labs(title=labelsPlot.Scen[3],
-#        subtitle = expression(gamma),x="",y="")+
-#   theme_classic()+xlim(-2,2)
-# 
-# first.col<-plot_grid(nrow=3,align = "v",byrow = TRUE,
-#           gam.both.post,gam.gam.post,nrew.nrew.post,
-#           labels=c('a','c','d'))
-# second.col<-plot_grid(nrow = 2,align = "v",byrow = TRUE,
-#           nrew.both.post,panel.rsqr.all,rel_heights = c(1,2),
-#           labels = c('b','e'))
-# plot_grid(ncol = 2,first.col,second.col)
+loglikehoods.all<-data.table(lglikelihood=c(MCMCdata1$fit,MCMCdata2$fit,
+                                             MCMCdata3$fit),
+                              model=c(rep(labels.Scen[1],length(MCMCdata1$fit)),
+                                      rep(labels.Scen[2],length(MCMCdata2$fit)),
+                                      rep(labels.Scen[3],length(MCMCdata3$fit))
+                                      ))
+
+# Read field data to calculate null log-likelihood
+fieldData<-fread(here("Data","data_cleaner_abs_threa1.5.txt"))
+
+nullLikehood<-sum(dbinom(x=fieldData[,score_visitor],
+                         size = 20,prob = 0.5,log = TRUE))
+
+# calculate pseudo R^2
+loglikehoods.all[,Rsqrd:=1-lglikelihood/nullLikehood]
+
+panel.rsqr.all<-
+  ggplot(data=loglikehoods.all[is.finite(lglikelihood)],
+                  aes(y=model,x=Rsqrd,fill=model))+
+  stat_halfeye(alpha=0.5,point_size=3)+
+  theme_classic()+xlim(-0.5,0.25)+
+  scale_fill_manual(values=c("#1b9e77","#d95f02","#7570b3"),
+  name = "Model", labels = labelsPlot.Scen)+
+  scale_y_discrete(labels=labelsPlot.Scen)+
+  geom_vline(xintercept = 0,color="black",size=0.5)+
+  theme(legend.position = 'none')
+          # c(.32, .65)
+        # ,legend.key.size = unit(0.22,'cm'),
+        # axis.text.y = element_blank(),
+        # legend.text = element_text(size=7))
+
+gam.both.post<-ggplot(data=MCMCdata1,aes(x=gamma)) +
+  stat_halfeye(aes(fill=stat(cut(x,breaks = cuts.1$gamma))),
+               point_interval = mode_hdi, .width = c(.66, .95),
+               point_size=3,show.legend=FALSE) +
+  labs(title=labelsPlot.Scen[1],
+       subtitle = expression(gamma),x="",y="")+
+  theme_classic()+
+  scale_fill_manual(values=c("gray85","skyblue","gray85"))
+
+nrew.both.post<-ggplot(data=MCMCdata1,aes(x=negReward)) +
+  stat_halfeye(aes(fill=stat(cut(x,breaks = cuts.1$negReward))),
+               point_interval = mode_hdi,
+               .width = c(.66, .95),point_size=3,
+               show.legend=FALSE)+theme_classic()+
+  scale_fill_manual(values=c("gray85","skyblue","gray85"))+
+  labs(title="",subtitle = expression(eta),x="",y="")+
+  xlim(-2,2)
+gam.gam.post<-ggplot(data=MCMCdata2,aes(x=gamma)) +
+  stat_halfeye(aes(fill=stat(cut(x,breaks = cuts.2$gamma))),
+               point_interval = mode_hdi, .width = c(.66, .95),
+               point_size=3,
+               show.legend=FALSE) +
+  scale_fill_manual(values=c("gray85","skyblue","gray85"))+
+  labs(title=labelsPlot.Scen[2],
+       subtitle = expression(gamma),x="",y="")+
+  theme_classic()
+nrew.nrew.post<-ggplot(data=MCMCdata3,aes(x=negReward)) +
+  stat_halfeye(aes(fill=stat(cut(x,breaks = cuts.3$negReward))),
+               point_interval = mode_hdi, .width = c(.66, .95),
+               point_size=3,
+               show.legend=FALSE) +
+  scale_fill_manual(values=c("gray85","skyblue","gray85"))+
+  labs(title=labelsPlot.Scen[3],
+       subtitle = expression(gamma),x="",y="")+
+  theme_classic()+xlim(-2,2)
+
+first.col<-plot_grid(nrow=3,align = "v",byrow = TRUE,
+          gam.both.post,gam.gam.post,nrew.nrew.post,
+          labels=c('a','c','d'))
+second.col<-plot_grid(nrow = 2,align = "v",byrow = TRUE,
+          nrew.both.post,panel.rsqr.all,rel_heights = c(1,2),
+          labels = c('b','e'))
+plot_grid(ncol = 2,first.col,second.col)
 
@@
 having one parameter less than the full model. We have not shown 
-here the marginal posterior distributions, given that they do not bring 
-biological insight. Their visualizations can be found in the supplementary 
+here the marginal posterior distributions of the scaling constant, 
+given that they do not bring biological insight. 
+Their visualizations can be found in the supplementary 
 material (Fig. \ref{fig:scaConst}), as well as the diagnostics of the MCMCs
-(Figs. \ref{fig:diagnosticsfull},\ref{fig:diaggam},\ref{fig:diagneg}).
+(Figs. \ref{fig:diagnosticsfull},\ref{fig:diaggam},\ref{fig:diagNeg}).
 
@@
 
-<!-- # ```{r pred, fig.cap='(ref:pred)',out.width='100%',fig.height=5} -->
-<!-- #  -->
-<!-- # source(here("manFigures.R")) -->
-<!-- # ggarrange(cont.obs.pred.both,scatter.obs.pred.both, -->
-<!-- # cont.obs.pred.gam,scatter.obs.pred.gam, -->
-<!-- # cont.obs.pred.Nrew,scatter.obs.pred.Nrew, -->
-<!-- #           labels=c('a','b','c','d'),common.legend = F, -->
-<!-- #   heights=c(1.25,1)) -->
-<!-- #  -->
-<!-- # ``` -->
+```{r pred, fig.cap='(ref:pred)',out.width='100%',fig.height=5}
+
+ source(here("manFigures.R"))
+ ggarrange(cont.obs.pred.both,scatter.obs.pred.both,
+ cont.obs.pred.gam,scatter.obs.pred.gam,
+ cont.obs.pred.Nrew,scatter.obs.pred.Nrew,
+           labels=c('a','b','c','d','e','f'),common.legend = F,
+   heights=c(1.4,1,1),nrow = 3,ncol = 2)
+
+```
 
@@
 In this study, our main aim was to unravel which of two potential 
-cognitive mechanisms, chaining of events, operant conditioning, 
+cognitive mechanisms, chaining of events, penalty, 
 or their combination, best explains wild-caught cleaner fish 
@@
 Social competence is the ability to optimise social behaviour 
-to the available social information [@taborsky_Social_2012a;
+to the available social information [@taborsky_Social_2012;
 @bshary_Cooperation_2015;@varela_Correlated_2020]. Our analyses yielded no 
@@
 found by Triki *et al* [@triki_Brain_2020], are due to the mechanism 
-used to incorporate future consequences. It could have been conceivable that 
+used to incorporate future consequences. It is conceivable that 
 high performing individuals from low population densities reef sites 
-might use negative reinforcement instead of chaining, but in that 
+use negative reinforcement instead of chaining, but in that 
 case negative reinforcement should have explained at least 
@@
 or residents. For example, visitors are on average larger 
-than residents in body size [@bshary_Cleaner_2001a], and contrary to 
+than residents in body size [@bshary_Cleaner_2001], and contrary to 
 resindents, are less likely to chase a cleaner fish that fails to cooperate
@@
 would never allow to exclude an important role of 
-negative reinforcement based on the data
+penalty based on the data
 alone. However, fitting model predictions to our comprehensive empirical 
@@
   theme_classic()+
-  scale_fill_manual(values=c("gray85","skyblue","gray85"))
+  scale_fill_manual(values=c("skyblue","gray85"))
 sca.gam.post<-ggplot(data=MCMCdata2,aes(x=scaleConst)) + 
@@
   labs(title=labelsPlot.Scen[2],x="",y="")
-# sca.nRew.post<-ggplot(data=MCMCdata3,aes(x=scaleConst)) +
-#   stat_halfeye(aes(fill=stat(cut(x,breaks = cuts.3$scaleConst))),
-#                point_interval = mode_hdi, .width = c(.66, .95),
-#                point_size=3,
-#                show.legend=FALSE) +
-#   scale_fill_manual(values=c("gray85","skyblue","gray85"))+
-#   labs(title=labelsPlot.Scen[3],x="",y="")+
-#   theme_classic()
+sca.nRew.post<-ggplot(data=MCMCdata3,aes(x=scaleConst)) +
+  stat_halfeye(aes(fill=stat(cut(x,breaks = cuts.3$scaleConst[2:4]))),
+               point_interval = mode_hdi, .width = c(.66, .95),
+               point_size=3,
+               show.legend=FALSE) +
+  scale_fill_manual(values=c("skyblue","gray85"))+
+  labs(title=labelsPlot.Scen[3],x="",y="")+
+  theme_classic()
 ggarrange(sca.both.post,sca.gam.post,
-          # sca.nRew.post,
+          sca.nRew.post,
           labels=c('a','b','c'),common.legend = F)
@@
 
-```{r diagnosticsfull, fig.cap='(ref:diagnosticsfull)',echo=FALSE,fig.height=5}
+```{r diagnosticsfull, fig.cap='(ref:diagnosticsfull)',message=FALSE,echo=FALSE,fig.height=5}
 
@@
 gp.dat<-gelman.plot(mcmcList.1)
-dev.off()
+rubbish <- dev.off()
 
@@
 
-```{r diaggam,fig.cap='(ref:diagnosticsGam)',echo=FALSE}
+```{r diaggam,fig.cap='(ref:diagnosticsGam)',echo=FALSE,message=FALSE}
 longMCMCdata2<-melt(MCMCdata2,id.vars = c("iteration","seed"),
@@
 gp.dat.gam<-gelman.plot(mcmcList.2)
-dev.off()
+rubbish <- dev.off()
 
@@
 
-<!-- (ref:diagNeg) MCMC convergence diagnostics for the penalty model.  -->
-<!-- On the left trace-plots, on the right changes along the chain of the  -->
-<!-- Gelman and Rubin's shrink factor [@brooks_General_1998] -->
-
-<!-- ```{r diag.neg,fig.cap='(ref:diag.neg)'} -->
-<!-- longMCMCdata3<-melt(MCMCdata3,id.vars = c("iteration","seed"), -->
-<!--                     variable.name = "parameter", -->
-<!--                     measure.vars = c("negReward","scaleConst")) -->
-
-<!-- parlab<-list(`negReward` =expression(eta), -->
-<!--           `scaleConst`="Scaling constant") -->
-
-<!-- traces.neg<-ggplot(longMCMCdata3,aes(x=iteration,y=value,colour=as.factor(seed)))+ -->
-<!--   geom_line()+ -->
-<!--   scale_color_manual(values = multDiscrPallet)+ -->
-<!--   labs(color="Chain")+ -->
-<!--   facet_grid(rows=vars(parameter),scales = "free",switch = "y", -->
-<!--              labeller = function(variable,value){ -->
-<!--   return(parlab[value])})+ -->
-<!--   theme_classic()+ -->
-<!--   theme(legend.position = 'top') -->
-
-<!-- pdf(file = NULL) -->
-<!-- gp.dat.neg<-gelman.plot(mcmcList.3) -->
-<!-- dev.off() -->
-
-<!-- gp.dat.frame.neg <- data.table(rbind(as.data.frame(gp.dat.neg[["shrink"]][,,1]),  -->
-<!--                           as.data.frame(gp.dat.neg[["shrink"]][,,2])),  -->
-<!--                 q=rep(dimnames(gp.dat.neg[["shrink"]])[[3]], each=nrow(gp.dat.neg[["shrink"]][,,1])), -->
-<!--                 last.iter=rep(gp.dat.neg[["last.iter"]], length(gp.dat.neg))) -->
-
-<!-- gelman.neg<-ggplot(melt(gp.dat.frame.neg, c("q","last.iter"), value.name="shrink_factor"),  -->
-<!--        aes(last.iter, shrink_factor, colour=q, linetype=q)) +  -->
-<!--   geom_hline(yintercept=1, colour="grey30", lwd=0.2) + -->
-<!--   geom_line() + -->
-<!--   facet_grid(rows = vars(variable), labeller= labeller(function(var,value){ -->
-<!--   return(parlab[value])})) + -->
-<!--   labs(x="Last Iteration in Chain", y="Shrink Factor", -->
-<!--        colour="Quantile", linetype="Quantile") + -->
-<!--   scale_linetype_manual(values=c(2,1))+ -->
-<!--   theme_classic()+ -->
-<!--   theme(legend.position = 'top') -->
-
-<!-- ggarrange(traces.neg,gelman.neg) -->
-<!-- ``` -->
+(ref:diagNeg) MCMC convergence diagnostics for the penalty model.
+On the left trace-plots, on the right changes along the chain of the
+Gelman and Rubin's shrink factor [@brooks_General_1998]
+
+```{r diagNeg,fig.cap='(ref:diagNeg)',message=FALSE}
+longMCMCdata3<-melt(MCMCdata3,id.vars = c("iteration","seed"),
+                    variable.name = "parameter",
+                    measure.vars = c("negReward","scaleConst"))
+
+parlab<-list(`negReward` =expression(eta),
+          `scaleConst`="Scaling constant")
+
+traces.neg<-ggplot(longMCMCdata3,aes(x=iteration,y=value,colour=as.factor(seed)))+
+  geom_line()+
+  scale_color_manual(values = multDiscrPallet)+
+  labs(color="Chain")+
+  facet_grid(rows=vars(parameter),scales = "free",switch = "y",
+             labeller = function(variable,value){
+  return(parlab[value])})+
+  theme_classic()+
+  theme(legend.position = 'top')
+
+pdf(file = NULL)
+gp.dat.neg<-gelman.plot(mcmcList.3)
+rubbish <- dev.off()
+
+gp.dat.frame.neg <- data.table(rbind(as.data.frame(gp.dat.neg[["shrink"]][,,1]),
+                          as.data.frame(gp.dat.neg[["shrink"]][,,2])),
+                q=rep(dimnames(gp.dat.neg[["shrink"]])[[3]], each=nrow(gp.dat.neg[["shrink"]][,,1])),
+                last.iter=rep(gp.dat.neg[["last.iter"]], length(gp.dat.neg)))
+
+gelman.neg<-ggplot(melt(gp.dat.frame.neg, c("q","last.iter"), value.name="shrink_factor"),
+       aes(last.iter, shrink_factor, colour=q, linetype=q)) +
+  geom_hline(yintercept=1, colour="grey30", lwd=0.2) +
+  geom_line() +
+  facet_grid(rows = vars(variable), labeller= labeller(function(var,value){
+  return(parlab[value])})) +
+  labs(x="Last Iteration in Chain", y="Shrink Factor",
+       colour="Quantile", linetype="Quantile") +
+  scale_linetype_manual(values=c(2,1))+
+  theme_classic()+
+  theme(legend.position = 'top')
+
+ggarrange(traces.neg,gelman.neg)
+```

### 2022-02-28 manuscript_1.0/manuscript_1.0.tex
New version of the manuscript. Using figure from the old data.

@@
 
-Disentangling the mechanistic underpinnings of behaviour
-is typically done under controlled conditions in a laboratory setting. However,
-controlled laboratory conditions often mask the inter and intra-specific
-variation that arises in the interaction between mechanisms and
-environmental variation. From a evolutionary perspective, mechanisms
-are likely selected because of how they allow individuals to respond to
-environmental variation. For example, biological market theory predicts that
-the exchange rate of goods and/or services traded between cooperative
-partners adjusts to the law of supply and demand, when individuals have
-some degree of partner choice \citep{noe_Biological_1995a}.
-Supply and demand conditions, which typically
+Often alternative cognitive mechanisms yield similar behaviour and/or cognitive
+performances. This poses a problem for disentangling the mechanistic
+underpinnings of behaviour. This is particularly clear in research aimed at
+discovering interspecific variation in \emph{higher} cognitive abilities; or
+in other words, research on whether non-human animals show cognitive
+abilities believed to be uniquely human. For instance, when researchers
+try to find \emph{mental time travel-like} behaviour, they usually come up with
+clever experiments showing the behaviour displayed requires inferences made
+through past events\citep{dally_Foodcaching_2006}. However, they often face challenges proposing alternative scenarios where simple associations can bring about the
+predicted behavioural outcome \citep{suddendorf_Evolution_2007}. Similarly, attempts
+to show \emph{theory of mind} in non-human animals face objections
+justified by alternative mechanisms that bring about similar behavioural
+results \citep{heyes_Theory_1998}. Such controversies are usually settled by
+using the principle of parsimony, and it's cognitive version,
+Lloyd Morgan's cannon. Which states that the simpler explanation (mechanism)
+must be accepted. Ideally, however, alternative hypothesis should be evaluated
+in light of their explanatory power. One potential dimension that could allow
+the variation necessary among distinct cognitive mechanisms is environmental
+variation. Controlled laboratory conditions often mask the inter and
+intra-specific variation that arises in the interaction between mechanisms and
+environments. Thus, if predictions from the alternative mechanisms change
+with environmental conditions, it is possible to asses the explanatory power
+of the different hypothesis by performing behavioural test in the context of
+different environmental conditions.
+
+From a evolutionary perspective, mechanisms are likely selected because
+of how they allow individuals to respond to environmental variation.
+For example, biological market theory predicts that the exchange rate of goods
+and/or services traded between cooperative partners adjusts to the
+law of supply and demand, when individuals have some degree of partner choice
+\citep{noe_Biological_1995}. Supply and demand conditions, which typically
 depend on the abundance of the species involved, certainly vary in time
-and space. Therefore, natural selection should
-favour the ability to flexibly adjust decisions and behavioural output to
+and space. Therefore, natural selection should favour the ability
+to flexibly adjust decisions and behavioural output to
 current market conditions. Indeed, such adjustments have been repeatedly
@@
 market conditions have been documented in a great variety of species with
-highly variable brain anatomies, the question arises to what extent mechanisms
-beyond basic associative learning may be involved.
+highly variable brain anatomies, the question arises to what extent
+mechanisms beyond basic associative learning may be involved.
 
@@
 visitors service priority in a field study in the Red Sea
-\citep{bshary_Cleaner_2001a}.
+\citep{bshary_Cleaner_2001}.
 
@@
 like a visitor, i.e.~it is removed if not inspected first.
+This laboratory paradigm originally inspired by the cleaning market
+of cleaner fish is more generally refered as the ephemeral reward task.
+Individuals are assesed in their capacity to develop a preference for the
+ephemeral option, which gives them access to two reward units.
 Cleaners learned to prefer the visitor plate and
@@
 Furthermore, adult cleaner fish outperformed various primates as well as rats and
-pigeons in this original version of the biological market task
+pigeons in this original version of the ephemeral reward task
 \citep{salwiczek_Adult_2012, zentall_Early_2017}; yet the African grey
-parrots solve this task as well \citep{pepperberg_Can_2014}. Given that primates
-are known to readily distinguish
-between one and two reward units if presented in more conventional ways
-\(\color{red}{\text{ref}}\), this raises the question:
-what makes the task difficult for most non-cleaners?
+parrots solve this task as well \citep{pepperberg_Can_2014}. This interspecific
+variation in performance, and primates' known cognitive abilities \(\color{red}{\text{ref}}\), shows that performane in the task
+cannot be readily explained by classifying species as having high and
+low cognitive abilities. Instead, this inter-spefic variation suggest
+that solving the ephemeral reward task requires a set of cognitive
+mechanisms that are not present in all the tested taxa, or were not used
+under the experimental set-up.
 
@@
 for individual performance. For example, some animals find relevant
-information in the plates
-\citep{wismer_Cuebased_2019} while others find it in the food
-\citep{pretot_Comparative_2021, pretot_Comparing_2016}. However, identifying
-cues as salient is not the only challenge of the ephemeral reward task,
-as revealed by proximate learning models. Such models allow varying the
-cognitive tool kit and to evaluate which minimal kit is necessary to solve
+information in the plates \citep{wismer_Cuebased_2019} while others find
+it in the food \citep{pretot_Comparative_2021, pretot_Comparing_2016}.
+However, identifying cues as salient is not the only challenge
+of the ephemeral reward task, as revealed by proximate learning models.
+Such models allow varying the cognitive tool kit and to evaluate
+which minimal kit is necessary to solve
 the task at hand (e.g. \citep{dubois_Model_2021}). Applied to the ephemeral
@@
 Lloyd Morgan's cannon demands that operant conditioning as the simpler
-explanation is to be accepted by default. Ideally, the two mechanisms should
-be evaluated in light of how well they explain the available data.
+explanation is to be accepted by default. Ideally, however, the two
+mechanisms should be evaluated in light of how well
+they explain the available data. Note that different fields interested in
+cognition and desicion making use different words to refer to negative
+reinforcers \citep{quinones_Reinforcement_2019, sutton_Reinforcement_2018}.
+In here, for the sake of simplicity and clarity, we will use the word
+`penalty' to refer to this mechanism which includes a negative reinforcer.
 
@@
 mechanism cleaner fish use to incorporate future consequences of current
-decisions by testing whether operant conditioning, chaining, or a combination
+decisions by testing whether chaining, penalty, or a combination
 of both best explains their performance; (ii) determining whether the
@@
 also work together. First, \(\gamma\) measures how
-much individuals include future rewards in their decision updates. If
-\(\gamma=0\), individuals only use the immediate reward obtained from a
+much individuals include future rewards in their decision updates.
+If \(\gamma=0\), individuals only use the immediate reward obtained from a
 cleaning interaction. As \(\gamma\) increases individuals include more the
 reward obtained from the subsequent choices. That amounts to calculating
-and using for decision making the future expected rewards of an action.
+and using for decision making the future expected rewards of an action (chaining).
 Second, \(\eta\) measures how much individuals include in their reward the
-fleeing behaviour of visitor as a negative component. Both of
+fleeing behaviour of visitor as a negative component (penalty). Both of
 these parameters allow individuals to use in their estimates the future
@@
 (\(N = 75\) cleaner fish).
+We chose a combination of initial and reversal to quantify preference
+for the visitor client, given that it matches well the criteria chosen
+in previous analysis of the ephemeral reward task experimental set-up
+\citep{triki_Biological_2019, triki_Brain_2020}. In the
+suplementaty material (Fig. \ref{fig:rawdata}) we show how our choice maps
+to the previously used criteria. For comparison, we also show a quantification
+of visitor preference based only on the initial phase of the experiments.
 
@@
 
-Figure \ref{fig:post} panels a,b and c show the posterior distributions
-of the parameter values of the full model, which includes both chaining
-and operant conditioning (negative reward). Posterior distributions show the probability
-density (y axis) of the estimated parameter values (x axis). Notably,
-the bulk of the posterior distribution for the parameter tuning negative
-reward (\(\eta\) panel b) was around zero. Thus, the shape of the posterior
-and its credible intervals suggest the absence of negative reward to be
-well supported by the data. As for \(\gamma\), the confidence intervals
-also includes zero, but the mode of the posterior is around 0.5. Thus,
-we ran the analysis setting \(\eta\) to zero. Figure \ref{fig:post} panels
-d and e, show the posterior distributions of the two parameters
-estimated. Not surprisingly, under a model without negative reward, the
-distribution of \(\gamma\) shifted to higher values. Under the new model,
-the estimates of \(\gamma\) did not include zero and the distribution was
-centred around \(0.5\). In panel f of figure \ref{fig:post}
+\begin{figure}
+
+{\centering \includegraphics[width=1\linewidth]{manuscript_1.0_files/figure-latex/post-1}
+
+}
+
+\caption{Posterior distributions for parameter values \(\gamma\) and \(\eta\) for
+the three models (``Full model'', ``chaining only'' and ``penalty only''). We show
+the kernel density estimates, below the mode (black dot) and the 65\%
+(light blue shade) and 95\% (grey shade) highest posterior density interval
+for the two parameters. On the top, panels a and b show posterior
+distributions for a full model, including chaining (\(\gamma\)) and penalty
+(\(\eta\)). Panel c, shows the \(\gamma\) estimate from model with only chaining.
+Panel d shows the \(\\eta\) estimate from a model with only penalty. Panel e,
+shows a measure of fit for all models, namely the distribution of pseudo-\(R^2\)
+obtained from sampling the posterior distribution of parameter values.}\label{fig:post}
+\end{figure}
+
+Estimation of parameter values for the three models (full model,
+chaining and penalty), support chaining as the only mechanism
+cleaners use to account for the future effects of their actions;
+and thus to solve the ephemeral reward task. In the estimation of the
+parameter values of the full model, which includes both chaining and
+penalty, the bulk of the marginal posterior distribution of \(\eta\) which
+controls the strength of penalty is around 0 (Fig. \ref{fig:post}).
+As for \(\gamma\), controlling chaining, the 95\% confidence
+intervals also includes zero, but the mode of the posterior
+is around 0.5 (Fig. \ref{fig:post}, a). In the chaining model,
+where \(\eta\) is set to zero, the distribution of \(\gamma\) shifted
+to higher values, zero is no longer part of the 95\% credible interval
+of the parameter (Fig. \ref{fig:post}, c). In contrast, when we
+look at the model with only penalty, the posterior distribution
+of \(\eta\) is still centred around zero (Fig. \ref{fig:post}, d).
+Thus, the analysis of the estimates of individual parameter
+values in the three models only supports a strong
+effect of chaining. Furthermore, the comparison of the models` fit
+favours the chaining model. In panel e of figure \ref{fig:post}
 we show the distribution of \(pseudo-R^2\) calculated using
-samples from the posterior distributions shown before,
-as well as from a model with negative reward but without
-future reward. Note, \(pseudo-R^2\) can have negative values, which is when
+samples from the posterior distributions shown before.
+Note, \(pseudo-R^2\) can have negative values, which is when
 the log-likelihood of the model is lower than that of a model that
@@
 \(pseudo-R^2\) distributions was not very different, the model with only
-future reward produced a distribution of \(pseudo-R^2\) where more values
+chaining produced a distribution of \(pseudo-R^2\) where more values
 were positive (to the right of black line in Fig. \ref{fig:post} f). This
 shows that, accounting for variation in the parameter estimates, the
-model with only future reward gives a better fit to the data, despite
-having one parameter less.
+model with chaining gives a better fit to the data, despite
+having one parameter less than the full model. We have not shown
+here the marginal posterior distributions of the scaling constant,
+given that they do not bring biological insight.
+Their visualizations can be found in the supplementary
+material (Fig. \ref{fig:scaConst}), as well as the diagnostics of the MCMCs
+(Figs. \ref{fig:diagnosticsfull},\ref{fig:diaggam},\ref{fig:diagNeg}).
 
-Figure \ref{fig:pred} shows predictions from the two models,
-one including chaining and operant conditioning (upper panels) and
-one with only chaining (lower panels). On the
-left, the colour coded contour shows the prediction of the model for
-combinations of cleaner fish abundance (x axis) and visitor leaving
-probability (y axis). Predictions were generated by running the model
-using the mode of the posterior distributions as the parameter values,
-and varying systematically cleaner fish abundance and visitor leaving
-probability. Colour of the dots on top of the contour show the average
-frequency with which cleaner fish chose the visitor plate in their last
-20 experimental trials. Each dot corresponds to a reef-site/year of
-data collection with a combination of cleaner fish abundance
-and visitor leaving probability. Panels
-on the right show how close the observed values for the probability of
-choosing the visitor (y axis) were from the predictions of the models (x
-axis). The black line represents the perfect fit between observed and
-predicted values. Bars show the variation in predicted values using 100
-samples from the posterior distribution. Despite having one more
-parameter varying, the full model
-gave a lower fit to the data than the model without negative reward.
-In the supplementary material, we also show predictions from
-model with only negative reward, excluding future rewards (\(\gamma=0\),
-Fig. \ref{fig:nogamma}), provides a lower fit than either of the ones
-presented in the main text.
+\begin{figure}
 
-The main reason for chaining and operant conditioning to give different
+{\centering \includegraphics[width=1\linewidth]{manuscript_1.0_files/figure-latex/pred-1}
+
+}
+
+\caption{Observed and predicted probability of choosing a visitor.
+Left-hand side panel: colour contour shows the prediction from the
+learning model using the mode of the posterior distributions of parameters
+recovered by the statistical analysis. Dots show the frequency of visitor
+choices for the 12 reef sites, as well as the corresponding relative
+cleaner fish abundance (x axis) and frequency of visitors clients leaving
+the cleaning station (y axis). Right-hand side panels: Variation of the
+predicted probabilities of choosing a visitor over a resident and their
+observed values for 12 locations. Circles show the mean prediction for
+each location from 100 samples taken from the posterior distribution.
+Thick and thin bars show the 66 and 95\% credible interval, respectively,
+taken from those posterior samples. Squares show the predictions used for
+panel on the right-hand side. Colour coding denotes different reef sites/year
+of the data collection (see Empirical data section). Black line corresponds
+to a perfect match between observed and predicted probabilities. Upper
+panels (a and b) show predictions from a model including chaining and
+penalty; middle panels (c and d) from a model with only chaining; lower
+panel (e and f) from a model with only penalty.}\label{fig:pred}
+\end{figure}
+
+The main reason for chaining and penalty to give different
 predictions is the way that cleaner fish relative abundance influences the
@@
 similar positive effect on the probability of choosing the visitor
-clients on all three models (Fig. \ref{fig:pred}, \ref{fig:nogamma}). In
-contrast, cleaner fish relative abundance has a different effect in the
+clients on all three models, they all predict an increase preference
+for visitors as the visitor probability increases (Fig. \ref{fig:pred}).
+In contrast, cleaner fish relative abundance has a different effect in the
 model with only chaining, compared to the other two models,
-full model and only operant conditioning. In the model
-with only chaining, only intermediate cleaner fish abundance triggers a
-preference for the visitor clients (Fig. \ref{fig:pred} c). In models
-with negative reward, both intermediate and low cleaner abundance
-triggered a preference for the visitor. (Fig. \ref{fig:pred} a,
-\ref{fig:nogamma}).
+full model and penalty. In the model with only chaining, only intermediate
+cleaner fish abundance triggers a preference for the visitor
+clients (Fig. \ref{fig:pred} c). In both models with penalty,
+both intermediate and low cleaner abundance triggered a preference
+for the visitor (Fig. \ref{fig:pred} a,e). Note, however, we calculated
+preferences shown in figure \ref{fig:pred} left panels by using only the mode
+of the posterior distributions, and by holding constant the balance between
+resident and visitors´s abundances. Panels on the right, show how close
+predictions are from the observed data, allowing the balance between
+client types to vary, and using a set of samples from the posterior
+distribution.
 
@@
 In this study, our main aim was to unravel which of two potential
-cognitive mechanisms, chaining of events, operant conditioning,
+cognitive mechanisms, chaining of events, penalty,
 or their combination, best explains wild-caught cleaner fish
@@
 
-Our results support chaining as the more plausible mechanism behind the
-intra-specific variation in cleaners' performance. This suggest
-that chaining could be under positive selection. In the standard ephemeral
-reward task, however, food amount and quality are equal in the
-two Plexiglas plates. Since our computational models simulate this aspect of
-the task, choosing visitors over residents at low cleaner fish abundances
-does not diminish the amount of food/reward in the models.
-On the other hand, a cleaner fish committed to visitors might find it more difficult
-to include in its decision making other variables, like parasite load
-and/or mucus quality \citep{roche_Client_2021}. Indeed, in the absence of
-market effects, both field observations and laboratory experiments also
-using simultaneous two choice options, show that cleaner fish base their
-decision-making on other cues such as the mucus quality and the amount of food.\\
-\citep{triki_Fluctuations_2019, grutter_Cleaner_2004}, as well as client size
-as a proxy for food quantity \citep{wismer_Cuebased_2019, grutter_Does_2005}.
-How important this limitation is will determine whether chaining yields a higher
-fitness for cleaners.
-
 Previous research showed that cleaner fish living at high population
@@
 Social competence is the ability to optimise social behaviour
-to the available social information \citep{taborsky_Social_2012a, bshary_Cooperation_2015, varela_Correlated_2020}. Our analyses yielded no
+to the available social information \citep{taborsky_Social_2012, bshary_Cooperation_2015, varela_Correlated_2020}. Our analyses yielded no
 evidence that the difference in social competence with respect to the local
@@
 found by Triki \emph{et al} \citep{triki_Brain_2020}, are due to the mechanism
-used to incorporate future consequences. It could have been conceivable that
+used to incorporate future consequences. It is conceivable that
 high performing individuals from low population densities reef sites
-might use negative reinforcement instead of chaining, but in that
+use negative reinforcement instead of chaining, but in that
 case negative reinforcement should have explained at least
@@
 or residents. For example, visitors are on average larger
-than residents in body size \citep{bshary_Cleaner_2001a}, and contrary to
+than residents in body size \citep{bshary_Cleaner_2001}, and contrary to
 resindents, are less likely to chase a cleaner fish that fails to cooperate
@@
 would never allow to exclude an important role of
-negative reinforcement based on the data
+penalty based on the data
 alone. However, fitting model predictions to our comprehensive empirical
@@
 
-\begin{verbatim}
-## pdf 
-##   2
-\end{verbatim}
-
 \begin{figure}
@@
 Gelman and Rubin's shrink factor \citep{brooks_General_1998}}\label{fig:diaggam}
+\end{figure}
+
+\begin{figure}
+
+{\centering \includegraphics{manuscript_1.0_files/figure-latex/diagNeg-1}
+
+}
+
+\caption{MCMC convergence diagnostics for the penalty model.
+On the left trace-plots, on the right changes along the chain of the
+Gelman and Rubin's shrink factor \citep{brooks_General_1998}}\label{fig:diagNeg}
 \end{figure}

### 2022-02-28 manuscript_1.0/manuscript_word.Rmd
New version of the manuscript. Using figure from the old data.

@@
   word_document: default
-  pdf_document: default
 fig_caption: yes
@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = FALSE,warning = FALSE,message=FALSE)
+knitr::opts_chunk$set(echo = FALSE,warning = FALSE,message=FALSE,cache = TRUE)
 library(here)
+source(file=here("loadFieldData.R"))
 ```
 
-Disentangling the mechanistic underpinnings of behaviour 
-is typically done under controlled conditions in a laboratory setting. However, 
-controlled laboratory conditions often mask the inter and intra-specific 
-variation that arises in the interaction between mechanisms and 
-environmental variation. From a evolutionary perspective, mechanisms 
-are likely selected because of how they allow individuals to respond to 
-environmental variation. For example, biological market theory predicts that 
-the exchange rate of goods and/or services traded between cooperative 
-partners adjusts to the law of supply and demand, when individuals have 
-some degree of partner choice [@noe_Biological_1995a]. 
-Supply and demand conditions, which typically 
+Often alternative cognitive mechanisms yield similar behaviour and/or cognitive
+performances. This poses a problem for disentangling the mechanistic 
+underpinnings of behaviour. This is particularly clear in research aimed at
+discovering interspecific variation in *higher* cognitive abilities; or 
+in other words, research on whether non-human animals show cognitive 
+abilities believed to be uniquely human. For instance, when researchers 
+try to find *mental time travel-like* behaviour, they usually come up with 
+clever experiments showing the behaviour displayed requires inferences made 
+through past events[@dally_Foodcaching_2006]. However, they often face challenges proposing alternative scenarios where simple associations can bring about the 
+predicted behavioural outcome [@suddendorf_Evolution_2007]. Similarly, attempts 
+to show *theory of mind* in non-human animals face objections 
+justified by alternative mechanisms that bring about similar behavioural 
+results [@heyes_Theory_1998]. Such controversies are usually settled by 
+using the principle of parsimony, and it's cognitive version, 
+Lloyd Morgan’s cannon. Which states that the simpler explanation (mechanism)
+must be accepted. Ideally, however, alternative hypothesis should be evaluated 
+in light of their explanatory power. One potential dimension that could allow
+the variation necessary among distinct cognitive mechanisms is environmental
+variation. Controlled laboratory conditions often mask the inter and 
+intra-specific variation that arises in the interaction between mechanisms and 
+environments. Thus, if predictions from the alternative mechanisms change
+with environmental conditions, it is possible to asses the explanatory power 
+of the different hypothesis by performing behavioural test in the context of
+different environmental conditions.
+
+From a evolutionary perspective, mechanisms are likely selected because 
+of how they allow individuals to respond to environmental variation. 
+For example, biological market theory predicts that the exchange rate of goods 
+and/or services traded between cooperative partners adjusts to the 
+law of supply and demand, when individuals have some degree of partner choice
+[@noe_Biological_1995]. Supply and demand conditions, which typically 
 depend on the abundance of the species involved, certainly vary in time 
-and space. Therefore, natural selection should 
-favour the ability to flexibly adjust decisions and behavioural output to 
+and space. Therefore, natural selection should favour the ability 
+to flexibly adjust decisions and behavioural output to 
 current market conditions. Indeed, such adjustments have been repeatedly 
@@
 One plate is made to behave like a resident, i.e. it remains until 
-the cleaner had eaten off it. The other plate was made to behave 
+the cleaner fish had eaten off it. The other plate was made to behave 
 like a visitor, i.e. it is removed if not inspected first. 
+This laboratory paradigm originally inspired by the cleaning market 
+of cleaner fish is more generally refered as the ephemeral reward task. 
+Individuals are assesed in their capacity to develop a preference for the 
+ephemeral option, which gives them access to two reward units.
 Cleaners learned to prefer the visitor plate and
@@
 
-<!-- Cleaner densities, in interaction with visitor client leaving probability,  -->
-<!-- explained best individual performance in the ephemeral reward task  -->
-<!-- [@triki_Biological_2019], while cleaner-to-client ratio was not a significant  -->
-<!-- factor. This creates a certain mismatch with the model by Quiñones *et al.*  -->
-<!-- [@quinones_Reinforcement_2019], which focused on abundance of cleaners relative  -->
-<!-- to overall client abundance in order to capture the characteristics  -->
-<!-- of the market. Importantly, relative abundances of clients define not only  -->
-<!-- the probability of interactions with residents and visitors, but also affect  -->
-<!-- how often the cleaning station is empty (e.g. there are no clients to be cleaned).  -->
-<!-- The higher the relative abundance of cleaners is, the higher is the probability  -->
-<!-- of cleaning stations being empty at a given time point. How often the  -->
-<!-- cleaning stations are empty in turns influences the value that cleaners can  -->
-<!-- expect from their choices. The emptier the cleaning stations are, the more  -->
-<!-- beneficial it is to prioritize a client that will not stay. On the other hand,  -->
-<!-- situations where cleaners have to choose will be rare if cleaner relative  -->
-<!-- abundance is high, which reduces the total value of prioritizing visitors  -->
-<!-- over residents and makes it more difficult to learn a preference for visitors.  -->
-<!-- Given the model structure, we used the empirical data to calculate relative  -->
-<!-- abundances of cleaners, residents and visitors for the current analyses.  -->
-<!-- To incorporate the empirical finding that absolute densities matter, we  -->
-<!-- introduced a new scaling constant (see section on model fitting).  -->
-
 The field observation data consisted of video recordings/encodings of the 
@@
 and the last 10 trials they were exposed to in the test 
-$\color{red}{\text{(N = XX cleaner fish)}}$.
+($N = `r fieldData.cleaner.filt.sum[V1>2,length(V1)]`$ cleaner fish). 
+We chose a combination of initial and reversal to quantify preference 
+for the visitor client, given that it matches well the criteria chosen 
+in previous analysis of the ephemeral reward task experimental set-up
+[@triki_Biological_2019;@triki_Brain_2020]. In the 
+suplementaty material (Fig. \ref{fig:rawdata}) we show how our choice maps
+to the previously used criteria. For comparison, we also show a quantification 
+of visitor preference based only on the initial phase of the experiments.
 
@@
 
-```{r post, fig.cap="Posterior distributions for parameter values $\\gamma$, $\\eta$ and the scaling constant.
-We show the kernel density estimates, below the mode (black dot) and the 65\\% (light blue shade) and 95\\% (grey shade)  highest posterior density interval for the three paramteres.
-On the left, panels a, b and c show posterior distributions for a model with all three parameters; while on the right, d and e, show a model with only chaining.
-Panel f shows a measure of fit for both models, namely the distribution of pseudo-$R^2$ obtained from sampling the posterior distribution of parameter values.",out.width='100%',fig.height=6}
+(ref:post) Posterior distributions for parameter values $\gamma$ and $\eta$ for 
+the three models ("Full model", "chaining only" and "penalty only"). We show 
+the kernel density estimates, below the mode (black dot) and the 65% 
+(light blue shade) and 95% (grey shade)  highest posterior density interval 
+for the two parameters. On the top, panels a and b show posterior 
+distributions for a full model, including chai %>% ning ($\gamma$) and penalty 
+($\eta$). Panel c, shows the $\gamma$ estimate from model with only chaining. 
+Panel d shows the $\\eta$ estimate from a model with only penalty. Panel e, 
+shows a measure of fit for all models, namely the distribution of pseudo-$R^2$ 
+obtained from sampling the posterior distribution of parameter values.
+
+```{r post, fig.cap='(ref:post)',out.width='100%',fig.height=6}
 library(data.table)
@@
 
-mcmcList.2<-mcmc.list(do.call(list,lapply(unique(MCMCdata2$seed), function(repli){
-  rundata<-MCMCdata2[seed==repli]
-  mcmcRun<-mcmc(rundata[,.(negReward,scaleConst)],thin = thinning)#
-  return(mcmcRun)
-})))
-
 mcmcList.3<-mcmc.list(do.call(list,lapply(unique(MCMCdata3$seed), function(repli){
   rundata<-MCMCdata3[seed==repli]
-  mcmcRun<-mcmc(rundata[,.(gamma,negReward,scaleConst)],thin = 100)#
+  mcmcRun<-mcmc(rundata[,.(negReward,scaleConst)],thin = thinning)#
   return(mcmcRun)
@@
                function(x){
-                 c(mode_hdi(x,.width = intervals[c(2,1)])$ymin,
-                   mode_hdi(x,.width = intervals)$ymax)  
+                 c(mode_hdci(x,.width = intervals[c(2,1)])$ymin,
+                   mode_hdci(x,.width = intervals)$ymax)
                })
@@
 # Read field data to calculate null log-likelihood
-fieldData<-fread(here("Data","data_ABC_cleaner_abs.txt"))
+fieldData<-fread(here("Data","data_cleaner_abs_threa1.5.txt"))
 
@@
   stat_halfeye(alpha=0.5,point_size=3)+
-  theme_classic()+xlim(-0.4,0.2)+
+  theme_classic()+xlim(-0.5,0.25)+
   scale_fill_manual(values=c("#1b9e77","#d95f02","#7570b3"),
@@
 
-plot_grid(nrow=3,align = "v",byrow = FALSE,
-          # Full model - \gamma
-          ggplot(data=MCMCdata1,aes(x=gamma)) + 
+gam.both.post<-ggplot(data=MCMCdata1,aes(x=gamma)) +
   stat_halfeye(aes(fill=stat(cut(x,breaks = cuts.1$gamma))),
-                         point_interval = mode_hdi, .width = c(.66, .95),point_size=3,
-                         show.legend=FALSE) + 
-            labs(title=labelsPlot.Scen[1],subtitle = expression(gamma),x="",y="")+
-            theme_classic()+scale_fill_manual(values=c("gray85","skyblue","gray85"))+
-            theme(plot.margin = unit(rep(0.5,4), "lines")),
-          # \eta
-          ggplot(data=MCMCdata1,aes(x=negReward)) + 
+               point_interval = mode_hdi, .width = c(.66, .95),
+               point_size=3,show.legend=FALSE) +
+  labs(title=labelsPlot.Scen[1],
+       subtitle = expression(gamma),x="",y="")+
+  theme_classic()+
+  scale_fill_manual(values=c("gray85","skyblue","gray85"))
+
+nrew.both.post<-ggplot(data=MCMCdata1,aes(x=negReward)) +
   stat_halfeye(aes(fill=stat(cut(x,breaks = cuts.1$negReward))),
-                         point_interval = mode_hdi, .width = c(.66, .95),point_size=3,
+               point_interval = mode_hdi,
+               .width = c(.66, .95),point_size=3,
                show.legend=FALSE)+theme_classic()+
   scale_fill_manual(values=c("gray85","skyblue","gray85"))+
-            labs(subtitle = expression(eta),x="",y="")+xlim(-5,5)+
-            theme(plot.margin = unit(rep(0.5,4), "lines")),
-          # Scale Constant
-          ggplot(data=MCMCdata1,aes(x=scaleConst)) + 
-            stat_halfeye(aes(fill=stat(cut(x,breaks = cuts.1$scaleConst))),
-                         point_interval = mode_hdi, .width = c(.66, .95),point_size=3,
-                         show.legend=FALSE)+
-            theme_classic()+scale_fill_manual(values=c("skyblue","gray85"))+
-          labs(subtitle = "Scalling const.",x="",y="")+xlim(-2,1500)+theme_classic()+
-          theme(plot.margin = unit(rep(0.5,4), "lines")),
-          # Future reward only model - \gamma
-          ggplot(data=MCMCdata2,aes(x=gamma)) +
+  labs(title="",subtitle = expression(eta),x="",y="")+
+  xlim(-2,2)
+gam.gam.post<-ggplot(data=MCMCdata2,aes(x=gamma)) +
   stat_halfeye(aes(fill=stat(cut(x,breaks = cuts.2$gamma))),
-                         point_interval = mode_hdi, .width = c(.66, .95),point_size=3,
+               point_interval = mode_hdi, .width = c(.66, .95),
+               point_size=3,
                show.legend=FALSE) +
   scale_fill_manual(values=c("gray85","skyblue","gray85"))+
-            labs(title=labelsPlot.Scen[2],subtitle = expression(gamma),x="",y="")+
-            theme_classic()+theme(plot.margin = unit(rep(0.5,4), "lines")),
-          # Scalling constant
-          ggplot(data=MCMCdata2,aes(x=scaleConst)) +
-            stat_halfeye(aes(fill=stat(cut(x,breaks = cuts.2$scaleConst))),
-                         point_interval = mode_hdi, .width = c(.66, .95),point_size=3,
+  labs(title=labelsPlot.Scen[2],
+       subtitle = expression(gamma),x="",y="")+
+  theme_classic()
+nrew.nrew.post<-ggplot(data=MCMCdata3,aes(x=negReward)) +
+  stat_halfeye(aes(fill=stat(cut(x,breaks = cuts.3$negReward))),
+               point_interval = mode_hdi, .width = c(.66, .95),
+               point_size=3,
                show.legend=FALSE) +
   scale_fill_manual(values=c("gray85","skyblue","gray85"))+
-            labs(subtitle = "Scalling const.",x="",y="")+
-            theme_classic()+theme(plot.margin = unit(rep(0.5,4), "lines")),
-          # Pseudo R^2
-          panel.rsqr.all+labs(subtitle = expression(pseudo-R^2),x="",y="")+
-            theme(legend.position = 'none'),
-          labels=c('a','d','b','e','c','f')
-)
+  labs(title=labelsPlot.Scen[3],
+       subtitle = expression(gamma),x="",y="")+
+  theme_classic()+xlim(-2,2)
+
+first.col<-plot_grid(nrow=3,align = "v",byrow = TRUE,
+          gam.both.post,gam.gam.post,nrew.nrew.post,
+          labels=c('a','c','d'))
+second.col<-plot_grid(nrow = 2,align = "v",byrow = TRUE,
+          nrew.both.post,panel.rsqr.all,rel_heights = c(1,2),
+          labels = c('b','e'))
+plot_grid(ncol = 2,first.col,second.col)
 
@@
 $pseudo-R^2$ distributions was not very different, the model with only
-future reward produced a distribution of $pseudo-R^2$ where more values
+chaining produced a distribution of $pseudo-R^2$ where more values
 were positive (to the right of black line in Fig. \ref{fig:post} f). This
 shows that, accounting for variation in the parameter estimates, the
-model with only future reward gives a better fit to the data, despite
-having one parameter less.
-
-```{r pred, fig.cap="Observed and predicted probability of choosing a visitor.
-Left-hand side panel: color contour shows the prediction of the learning model using the mode of the posterior distributions of parameters recovered by the statistical analysis.
-Dots show the frequency of visitor choices for the 12 reef sites, as well as the corresponding relative cleaner fish abundance (x axis) and frequency of visitors clients leaving the cleaning station (y axis).
-Right-hand side panels: Variation of the predicted probabilites  of choosing a visitor over a resident and their observed values for 12 locations.
-Circles show the mean prediction for each location from 100 samples taken from the posterior distribution.
-Thick and thin bars show the 66 and 95\\% credible interval, respectively, taken from those posterior samples.
-Squares show the predictions used for panel on the righ-hand side.
-Colour coding denotes different reef sites/year of the data collection (see Empirical data section).
-Black line corresponds to a perfect match between observed and predicted probabilities.
-Upper panels show prediction from a model including chaining and operant conditioning, lower panels from a  model with only chaining.",out.width='100%',fig.height=5}
+model with chaining gives a better fit to the data, despite
+having one parameter less than the full model. We have not shown 
+here the marginal posterior distributions of the scaling constant, 
+given that they do not bring biological insight. 
+Their visualizations can be found in the supplementary 
+material (Fig. \ref{fig:scaConst}), as well as the diagnostics of the MCMCs
+(Figs. \ref{fig:diagnosticsfull},\ref{fig:diaggam},\ref{fig:diagNeg}).
+
+(ref:pred) Observed and predicted probability of choosing a visitor. 
+Left-hand side panel: colour contour shows the prediction from the 
+learning model using the mode of the posterior distributions of parameters 
+recovered by the statistical analysis. Dots show the frequency of visitor 
+choices for the 12 reef sites, as well as the corresponding relative 
+cleaner fish abundance (x axis) and frequency of visitors clients leaving 
+the cleaning station (y axis). Right-hand side panels: Variation of the 
+predicted probabilities  of choosing a visitor over a resident and their 
+observed values for 12 locations. Circles show the mean prediction for 
+each location from 100 samples taken from the posterior distribution. 
+Thick and thin bars show the 66 and 95% credible interval, respectively, 
+taken from those posterior samples. Squares show the predictions used for 
+panel on the right-hand side. Colour coding denotes different reef sites/year 
+of the data collection (see Empirical data section). Black line corresponds 
+to a perfect match between observed and predicted probabilities. Upper 
+panels (a and b) show predictions from a model including chaining and 
+penalty; middle panels (c and d) from a  model with only chaining; lower 
+panel (e and f) from a model with only penalty.
+
+```{r pred, fig.cap='(ref:pred)',out.width='100%',fig.height=5}
 
@@
  cont.obs.pred.gam,scatter.obs.pred.gam,
-          labels=c('a','b','c','d'),common.legend = F,
-  heights=c(1.25,1))
+ cont.obs.pred.Nrew,scatter.obs.pred.Nrew,
+           labels=c('a','b','c','d','e','f'),common.legend = F,
+   heights=c(1.4,1,1),nrow = 3,ncol = 2)
 
@@
 
-Figure \ref{fig:pred} shows predictions from the two models, 
-one including chaining and operant conditioning (upper panels) and 
-one with only chaining (lower panels). On the
-left, the colour coded contour shows the prediction of the model for
-combinations of cleaner fish abundance (x axis) and visitor leaving
-probability (y axis). Predictions were generated by running the model
-using the mode of the posterior distributions as the parameter values,
-and varying systematically cleaner fish abundance and visitor leaving
-probability. Colour of the dots on top of the contour show the average
-frequency with which cleaner fish chose the visitor plate in their last
-20 experimental trials. Each dot corresponds to a reef-site/year of 
-data collection with a combination of cleaner fish abundance 
-and visitor leaving probability. Panels
-on the right show how close the observed values for the probability of
-choosing the visitor (y axis) were from the predictions of the models (x
-axis). The black line represents the perfect fit between observed and
-predicted values. Bars show the variation in predicted values using 100 
-samples from the posterior distribution. Despite having one more 
-parameter varying, the full model
-gave a lower fit to the data than the model without negative reward.
-In the supplementary material, we also show predictions from 
-model with only negative reward, excluding future rewards ($\gamma=0$,
-Fig. \ref{fig:nogamma}), provides a lower fit than either of the ones
-presented in the main text.
-
-The main reason for chaining and operant conditioning to give different
+The main reason for chaining and penalty to give different
 predictions is the way that cleaner fish relative abundance influences the
@@
 ```
-```{r nogamma, fig.cap="Observed and predicted probability of choosing a visitor for a model without chaining.
-Left-hand side panel: color contour shows the prediction of the learning model using the mode of the posterior distributions of parameters recovered by the statistical analysis.
-Dots show the frequency of visitor choices for the 12 reef sites, as well as the corresponding relative cleaner fish abundance (x axis) and frequency of visitors leaving the station if being made to wait (y axis).
-Right-hand side panel: Right-hand side panels: Variation of the predicted probabilites  of choosing a visitor and their observed values for 12 reef sited.
-Circles show the mean prediction for each location from 100 samples taking from the posterior distribution.
-Thick and thin bars show the 66 and 95\\% credible interval taken from those posterior samples.
-Squares show the predictions used for panel on the righ-hand side.
-Colour denotes different locations (see Empirical data section).
-Black line correspond to a perfect match between observed and predicted probabilities.",fig.pos = 'H', out.extra = "",out.width='95%',fig.height=4}
-
-ggarrange(cont.obs.pred.Nrew,scatter.obs.pred.Nrew,
-          labels=c('a','b'),common.legend=FALSE)
+
+(ref:rawdata) Relation between the response variable used in this study and the 
+criteria used in previous studies to assess performance in the ephemeral reward 
+task. In the x axis, we classified the performance of cleaner fish according to 
+whether they developed a preference for the visitor in the initial round, 
+in the initial and reversal, or none of them. In the y axis, we add the choices
+of two experimental sessions: panel on the left uses one session from the initial 
+round and one from the reversal round when possible 
+(as described in the main text); panel on the right uses two sessions from the 
+initial round for all fish.
+
+```{r rawdata,fig.cap='(ref:rawdata)'}
+plot_grid(initANDRev,init,ncol = 2)
+
+```
+
+(ref:scaConst) Posterior distributions for scaling constant for the three model 
+("Full model", chaining only" and "penalty only"). We show the kernel 
+density estimates, below the mode (black dot) and the 65% (light blue shade) 
+and 95% (grey shade)  highest posterior density interval. On the top, 
+panel a shows the posterior distribution from the full model; panel b from 
+the model with only chaining; and panel c from a model with only penalty.
+
+```{r scaConst, fig.cap='(ref:scaConst)',fig.pos = 'H', out.extra = "",out.width='95%',fig.height=4}
+
+sca.both.post<-ggplot(data=MCMCdata1,aes(x=scaleConst)) + 
+  stat_halfeye(aes(fill=stat(cut(x,breaks = cuts.1$scaleConst))),
+               point_interval = mode_hdi, .width = c(.66, .95),
+               point_size=3,show.legend=FALSE) + 
+  labs(title=labelsPlot.Scen[1],x="",y="")+
+  theme_classic()+
+  scale_fill_manual(values=c("skyblue","gray85"))
+sca.gam.post<-ggplot(data=MCMCdata2,aes(x=scaleConst)) + 
+  stat_halfeye(aes(fill=stat(cut(x,breaks = cuts.2$scaleConst))),
+               point_interval = mode_hdi, 
+               .width = c(.66, .95),point_size=3,
+               show.legend=FALSE)+theme_classic()+
+  scale_fill_manual(values=c("gray85","skyblue","gray85"))+
+  labs(title=labelsPlot.Scen[2],x="",y="")
+sca.nRew.post<-ggplot(data=MCMCdata3,aes(x=scaleConst)) +
+  stat_halfeye(aes(fill=stat(cut(x,breaks = cuts.3$scaleConst[2:4]))),
+               point_interval = mode_hdi, .width = c(.66, .95),
+               point_size=3,
+               show.legend=FALSE) +
+  scale_fill_manual(values=c("skyblue","gray85"))+
+  labs(title=labelsPlot.Scen[3],x="",y="")+
+  theme_classic()
+ggarrange(sca.both.post,sca.gam.post,
+          sca.nRew.post,
+          labels=c('a','b','c'),common.legend = F)
 
@@
 ```
+
+(ref:diagnosticsfull) MCMC convergence diagnostics for the full model. 
+On the left trace-plots, on the right changes along the chain of the 
+Gelman and Rubin's shrink factor [@brooks_General_1998].
+
+```{r diagnosticsfull, fig.cap='(ref:diagnosticsfull)',message=FALSE,echo=FALSE,fig.height=5}
+
+longMCMCdata1<-melt(MCMCdata1,id.vars = c("iteration","seed"),
+                    variable.name = "parameter",
+                    measure.vars = c("gamma","negReward","scaleConst"))
+
+parlab<-list(`gamma` =expression(gamma),
+          `negReward`=expression(eta),
+          `scaleConst`="Scaling constant")
+
+traces.full<-ggplot(longMCMCdata1,aes(x=iteration,y=value,colour=as.factor(seed)))+
+  geom_line()+
+  scale_color_manual(values = multDiscrPallet)+
+  labs(color="Chain")+
+  facet_grid(rows=vars(parameter),scales = "free",switch = "y",
+             labeller = function(variable,value){
+  return(parlab[value])})+
+  theme_classic()+
+  theme(legend.position = 'top')
+
+gel.full<-as.data.table(gelman.diag(mcmcList.1)$psrf)
+gel.full[,parameter:=c("gamma","negReward","scalConst")]
+
+pdf(file = NULL)
+gp.dat<-gelman.plot(mcmcList.1)
+rubbish <- dev.off()
+
+gp.dat.frame <- data.table(rbind(as.data.frame(gp.dat[["shrink"]][,,1]), 
+                          as.data.frame(gp.dat[["shrink"]][,,2])), 
+                q=rep(dimnames(gp.dat[["shrink"]])[[3]], each=nrow(gp.dat[["shrink"]][,,1])),
+                last.iter=rep(gp.dat[["last.iter"]], length(gp.dat)))
+
+gelman.full<-ggplot(melt(gp.dat.frame, c("q","last.iter"), value.name="shrink_factor"), 
+       aes(last.iter, shrink_factor, colour=q, linetype=q)) + 
+  geom_hline(yintercept=1, colour="grey30", lwd=0.2) +
+  geom_line() +
+  facet_grid(rows = vars(variable), labeller= labeller(function(var,value){
+  return(parlab[value])})) +
+  labs(x="Last Iteration in Chain", y="Shrink Factor",
+       colour="Quantile", linetype="Quantile") +
+  scale_linetype_manual(values=c(2,1))+
+  theme_classic()+
+  theme(legend.position = 'top')
+
+ggarrange(traces.full,gelman.full)
+
+```
+
+(ref:diagnosticsGam) MCMC convergence diagnostics for the chaining model. 
+On the left trace-plots, on the right changes along the chain of the 
+Gelman and Rubin's shrink factor [@brooks_General_1998]
+
+```{r diaggam,fig.cap='(ref:diagnosticsGam)',echo=FALSE,message=FALSE}
+longMCMCdata2<-melt(MCMCdata2,id.vars = c("iteration","seed"),
+                    variable.name = "parameter",
+                    measure.vars = c("gamma","scaleConst"))
+
+parlab<-list(`gamma` =expression(gamma),
+          `scaleConst`="Scaling constant")
+
+traces.gam<-ggplot(longMCMCdata2,aes(x=iteration,y=value,colour=as.factor(seed)))+
+  geom_line()+
+  scale_color_manual(values = multDiscrPallet)+
+  labs(color="Chain")+
+  facet_grid(rows=vars(parameter),scales = "free",switch = "y",
+             labeller = function(variable,value){
+  return(parlab[value])})+
+  theme_classic()+
+  theme(legend.position = 'top')
+
+gel.gam<-as.data.table(gelman.diag(mcmcList.2)$psrf)
+gel.gam[,parameter:=c("gamma","scalConst")]
+
+pdf(file = NULL)
+gp.dat.gam<-gelman.plot(mcmcList.2)
+rubbish <- dev.off()
+
+gp.dat.frame.gam <- data.table(rbind(as.data.frame(gp.dat.gam[["shrink"]][,,1]), 
+                          as.data.frame(gp.dat.gam[["shrink"]][,,2])), 
+                q=rep(dimnames(gp.dat.gam[["shrink"]])[[3]], each=nrow(gp.dat.gam[["shrink"]][,,1])),
+                last.iter=rep(gp.dat.gam[["last.iter"]], length(gp.dat.gam)))
+
+gelman.gam<-ggplot(melt(gp.dat.frame.gam, c("q","last.iter"), value.name="shrink_factor"), 
+       aes(last.iter, shrink_factor, colour=q, linetype=q)) + 
+  geom_hline(yintercept=1, colour="grey30", lwd=0.2) +
+  geom_line() +
+  facet_grid(rows = vars(variable), labeller= labeller(function(var,value){
+  return(parlab[value])})) +
+  labs(x="Last Iteration in Chain", y="Shrink Factor",
+       colour="Quantile", linetype="Quantile") +
+  scale_linetype_manual(values=c(2,1))+
+  theme_classic()+
+  theme(legend.position = 'top')
+
+ggarrange(traces.gam,gelman.gam)
+```
+
+(ref:diagNeg) MCMC convergence diagnostics for the penalty model.
+On the left trace-plots, on the right changes along the chain of the
+Gelman and Rubin's shrink factor [@brooks_General_1998]
+
+```{r diagNeg,fig.cap='(ref:diagNeg)',message=FALSE}
+longMCMCdata3<-melt(MCMCdata3,id.vars = c("iteration","seed"),
+                    variable.name = "parameter",
+                    measure.vars = c("negReward","scaleConst"))
+
+parlab<-list(`negReward` =expression(eta),
+          `scaleConst`="Scaling constant")
+
+traces.neg<-ggplot(longMCMCdata3,aes(x=iteration,y=value,colour=as.factor(seed)))+
+  geom_line()+
+  scale_color_manual(values = multDiscrPallet)+
+  labs(color="Chain")+
+  facet_grid(rows=vars(parameter),scales = "free",switch = "y",
+             labeller = function(variable,value){
+  return(parlab[value])})+
+  theme_classic()+
+  theme(legend.position = 'top')
+
+pdf(file = NULL)
+gp.dat.neg<-gelman.plot(mcmcList.3)
+rubbish <- dev.off()
+
+gp.dat.frame.neg <- data.table(rbind(as.data.frame(gp.dat.neg[["shrink"]][,,1]),
+                          as.data.frame(gp.dat.neg[["shrink"]][,,2])),
+                q=rep(dimnames(gp.dat.neg[["shrink"]])[[3]], each=nrow(gp.dat.neg[["shrink"]][,,1])),
+                last.iter=rep(gp.dat.neg[["last.iter"]], length(gp.dat.neg)))
+
+gelman.neg<-ggplot(melt(gp.dat.frame.neg, c("q","last.iter"), value.name="shrink_factor"),
+       aes(last.iter, shrink_factor, colour=q, linetype=q)) +
+  geom_hline(yintercept=1, colour="grey30", lwd=0.2) +
+  geom_line() +
+  facet_grid(rows = vars(variable), labeller= labeller(function(var,value){
+  return(parlab[value])})) +
+  labs(x="Last Iteration in Chain", y="Shrink Factor",
+       colour="Quantile", linetype="Quantile") +
+  scale_linetype_manual(values=c(2,1))+
+  theme_classic()+
+  theme(legend.position = 'top')
+
+ggarrange(traces.neg,gelman.neg)
+```

### 2022-02-28 aesth_par.R

@@ -1,8 +1,7 @@
-# ----------- Aesthetic paramters ------------------#
+# ----------- Aesthetic parameters ------------------#
 
 # Define Colours -------------------------------------------------------
 
-library("wesanderson")
 
 colours <- c(rgb(red = .0, green = 0, blue = 0.8, alpha = 0.5),
              rgb(red = .8, green = 0.8, blue = 0, alpha = 0.5))

### 2022-02-28 manFigures.R

@@ -16,35 +16,35 @@ source(here("aesth_par.R"))
 source(here("../R_files/posPlots.R"))
 
 # Folder where the three models are
-scenario<-"MCMCclean_gam_Nrew_sca"
-scenario2<-"MCMCclean_gam_sca"
-scenario3<-"MCMCclean_Nrew_sca"
+# scen1<-"MCMCclean_gam_Nrew_sca"
+# scen2<-"MCMCclean_gam_sca"
+# scen3<-"MCMCclean_Nrew_sca"
 
 # Get file with the predictions using the mode of the posterior
-predfileMode.both<-grep(".txt",grep("round",list.files(here("Simulations",paste0(scenario,"_"))),value = T),
-                    value = T)
-predfileMode.gam<-grep(".txt",grep("round",list.files(here("Simulations",paste0(scenario2,"_"))),value = T),
-                   value = T)
-predfileMode.Nrew<-grep(".txt",grep("round",list.files(here("Simulations",paste0(scenario3,"_"))),value = T),
-                       value = T)
+predfileMode.both<-grep(".txt",grep("round",list.files(here("Simulations",
+                    scen1)),value = T),value = T)
+predfileMode.gam<-grep(".txt",grep("round",list.files(here("Simulations",
+                    scen2)),value = T),value = T)
+predfileMode.Nrew<-grep(".txt",grep("round",list.files(here("Simulations",
+                    scen3)),value = T),value = T)
 
 # Get predictions from sampling the posterior 
 predfileSamples.both<-grep(".txt",grep("round",list.files(here("Simulations",
-                                  paste0(scenario,"_"),"samplesPost_"),
+                                  scen1,"samplesPost_"),
                                   full.names = TRUE),value = T), value = T)
 predfileSamples.gam<-grep(".txt",grep("round",list.files(here("Simulations",
-                                paste0(scenario2,"_"),"samplesPost_"),
+                                scen2,"samplesPost_"),
                                 full.names = TRUE),value = T),value = T)
 predfileSamples.Nrew<-grep(".txt",grep("round",list.files(here("Simulations",
-                                paste0(scenario3,"_"),"samplesPost_"),
+                                scen3,"samplesPost_"),
[…]

### 2022-03-01 manuscript_1.0/manuscript_1.0.Rmd
Edited the manuscript according to Red1 comments. Readme.md file to facilitate reproducibility.

@@
 ---
-title: Combination of field and experimental data together with computational models 
-  reveal cognitive mechanisms behind cleaner fish behaviour
-#Cognitive and ecological aspects determine cleaner performance
+title: Field and experimental data together with computational 
+  models reveal how cleaner fish adjust decisions  in a biological market
 author:
@@
 Alternatively, when the different mechanisms interact with environmental conditions, variation in performance across environments might allow to statistically infer the mechanism responsible.
-However, to do this it is necessary to have quantitative predictions for the different candidate mechanisms.
-Here, we use a set of computational models to get quantitative predictions from alternative learning mechanisms, and using Bayesian statistics fit the model parameters to performance data.
-We used experimental data on performance in an ephemeral reward task by wild-caught cleaner fish *Labroides dimidiatus*, as well as cleaner and client fish densities from the locations of capture.
-The task can in principle be solved by estimating future consequences of an action, or by perceiving the removal of the ephemeral reward as psychological punishment (negative reinforcement).
-We found that a model where cleaners only estimate the future consequences of their actions explains best which cleaner fish relative abundances cause the fish to develop a preference for an ephemeral food source.
-This model also yields performances that can be considered the result of locally optimal decision-rules, in contrast to the negative reinforcement model.
-We argue that the combination of computational models with data is a powerful tool to infer the mechanistic underpinning behind cognitive performance.
+We illustrate this point by fitting computational models to experimental data on performance by wild-caught cleaner fish Labroides dimidiatus in an ephemeral reward task, as well as cleaner and client fish densities from the locations of capture.
+Using Bayesian statistics to fit the model parameters to performance data revealed that cleaner fish most likely estimate future consequences of an action, while it appears unlikely that the removal of the ephemeral reward acts as psychological punishment (negative reinforcement).
+Incorporating future consequences also yields performances that can be considered the result of locally optimal decision-rules, in contrast to the negative reinforcement mechanism.
+We argue that the combination of computational models with data is a powerful tool to infer the mechanistic underpinnings of cognitive performance.
 
@@
 underpinnings of behaviour. This is particularly clear in research aimed at
-discovering interspecific variation in *higher* cognitive abilities; or 
+discovering between species variation in *higher* cognitive abilities; or 
 in other words, research on whether non-human animals show cognitive 
@@
 try to find *mental time travel-like* behaviour, they usually come up with 
-clever experiments showing the behaviour displayed requires inferences made 
-through past events[@dally_Foodcaching_2006]. However, they often face challenges proposing alternative scenarios where simple associations can bring about the 
-predicted behavioural outcome [@suddendorf_Evolution_2007]. Similarly, attempts 
-to show *theory of mind* in non-human animals face objections 
-justified by alternative mechanisms that bring about similar behavioural 
-results [@heyes_Theory_1998]. Such controversies are usually settled by 
-using the principle of parsimony, and it's cognitive version, 
-Lloyd Morgan’s cannon. Which states that the simpler explanation (mechanism)
-must be accepted. Ideally, however, alternative hypothesis should be evaluated 
+clever experiments to show the behaviour displayed requires inferences made 
+through past events[@dally_Foodcaching_2006]. However, they often face the
+challenge of alternative scenarios where simpler explanations, 
+like classic associative learning, can bring about the 
+observed behavioural outcome [@suddendorf_Evolution_2007]. Similarly, attempts 
+to demonstrate the presence of *theory of mind* in non-human animals 
+face objections justified by alternative mechanisms underpinning 
+similar behavioural results [@heyes_Theory_1998]. 
+Such controversies are usually settled by using the principle 
+of parsimony and its cognitive version, 
+Lloyd Morgan’s cannon, which states that the simpler explanation (mechanism)
+should be accepted. Ideally, however, alternative hypotheses should be evaluated 
 in light of their explanatory power. One potential dimension that could allow
 the variation necessary among distinct cognitive mechanisms is environmental
-variation. Controlled laboratory conditions often mask the inter and 
-intra-specific variation that arises in the interaction between mechanisms and 
-environments. Thus, if predictions from the alternative mechanisms change
-with environmental conditions, it is possible to asses the explanatory power 
-of the different hypothesis by performing behavioural test in the context of
+variation. Controlled laboratory conditions often mask between and within 
+species variation that arises among different environments. Thus, if 
+predictions from the alternative mechanisms depend on environmental 
+conditions, it is possible to assess their relative explanatory power 
+by performing cognitive test in the context of
 different environmental conditions.
 
-From a evolutionary perspective, mechanisms are likely selected because 
+From an evolutionary perspective, mechanisms are likely selected because 
 of how they allow individuals to respond to environmental variation. 
@@
 it is not clear which cognitive mechanisms allow individuals to adjust their 
-behaviour to the varying conditions. As adjustments to changes in 
-market conditions have been documented in a great variety of species with 
-highly variable brain anatomies, the question arises to what extent 
-mechanisms beyond basic associative learning may be involved.
+behaviour to the varying conditions. More specifically the question arises 
+to what extent mechanisms beyond basic associative learning may be involved.
 
@@
 access multiple cleaning stations while others access the only cleaning 
-station at their territory, it is crucial to categorize clients as 
+station in their territory, it is crucial to categorize clients as 
 either “visitors” or “residents”, respectively. During cleaning interactions, 
@@
 to prioritize visitor over resident clients in a lab-based paradigm, 
-they used Plexiglas plates of different colours and shapes offering same 
+they used Plexiglas plates of different colours and shapes offering the same 
 amount of food as surrogates for visitor and resident clients.
 One plate is made to behave like a resident, i.e. it remains until 
-the cleaner fish had eaten off it. The other plate was made to behave 
+the cleaner fish has eaten off it. The other plate was made to behave 
 like a visitor, i.e. it is removed if not inspected first. 
 This laboratory paradigm originally inspired by the cleaning market 
-of cleaner fish is more generally refered as the ephemeral reward task. 
-Individuals are assesed in their capacity to develop a preference for the 
+of cleaner fish is more generally referred as the ephemeral reward task. 
+Individuals are assessed in their capacity to develop a preference for the 
 ephemeral option, which gives them access to two reward units.
@@
 [@salwiczek_Adult_2012; @zentall_Early_2017]; yet the African grey
-parrots solve this task as well [@pepperberg_Can_2014]. This interspecific
-variation in performance, and primates' known cognitive abilities $\color{red}{\text{ref}}$, shows that performane in the task
+parrots solve this task as well [@pepperberg_Can_2014]. 
+This between variation in performance, and primates' known cognitive abilities
+$\color{red}{\text{ref}}$, shows that performance in the task
 cannot be readily explained by classifying species as having high and 
-low cognitive abilities. Instead, this inter-spefic variation suggest
+low cognitive abilities. Instead, this between species variation suggests
 that solving the ephemeral reward task requires a set of cognitive 
@@
 
-Recent research on the cognitive tool kit needed to solve the ephemeral 
+Recent research on the cognitive abilities needed to solve the ephemeral 
 reward task has used a broad approach as proposed by Shettleworth 
@@
 of the ephemeral reward task, as revealed by proximate learning models. 
-Such models allow varying the cognitive tool kit and to evaluate 
+Such models allow varying the cognitive tool kit and evaluating 
 which minimal kit is necessary to solve 
@@
 This is particularly so when models assume the more complex natural 
-situation in which cleaner fish not only face resident-visitor pairs but also 
+situation in which cleaner fish face not only resident-visitor pairs but also 
 visitor-visitor and resident-resident pairs, as well a resident alone or 
@@
 same strategic option, paired with a fish with the alternative strategic option) 
-[@quinones_Reinforcement_2019]. The ability to distinguish and value differently
-one stimulus alone from compound versions of it has been termed 
-configurational learning, or chunking, 
+[@quinones_Reinforcement_2019]. The ability to distinguish and value 
+one stimulus differently alone from compound versions of it has been termed 
+configurational learning, chunking, 
 or segmentation (see references in [@prat_Modelling_2022]).
 
-To solve the ephemeral reward task, cleaners need to account for 
+In addition to configurational learning, cleaners also need to account for 
 the future consequences of current decisions. In the model by 
@@
 a complex adaptation [@suddendorf_Evolution_2007]. On the other hand,
-using client behaviour as a negative reinforcer is in principle 
+using client behaviour as a negative reinforcer is, in principle, 
 easier to implement. Negative reinforcement is part of the ubiquitous 
 learning mechanism termed operant conditioning [@thorndike_Animal_1898; 
-@skinner_Behavior_1938]. Thus, standard logic of 
+@skinner_Behavior_1938]. Thus, the standard logic of 
 Lloyd Morgan’s cannon demands that operant conditioning as the simpler 
@@
 they explain the available data. Note that different fields interested in
-cognition and desicion making use different words to refer to negative 
+cognition and decision making use different words to refer to negative 
 reinforcers [@quinones_Reinforcement_2019;@sutton_Reinforcement_2018]. 
-In here, for the sake of simplicity and clarity, we will use the word 
+Here, for the sake of simplicity and clarity, we will use the word 
 'penalty' to refer to this mechanism which includes a negative reinforcer.
 
-Over the last decade, our team tested over a hundred of wild-caught 
-cleaner fish in the exact same paradigm of  of the ephemeral reward 
+Over the last decade, our team tested over a hundred wild-caught 
+cleaner fish in the exact same paradigm of the ephemeral reward 
 task [@salwiczek_Adult_2012;@wismer_Variation_2014;@triki_Decrease_2018;
@@
 priority [@triki_Brain_2020]. In the absence of partner choice 
-cleaners should not give priority to visitors any more.
-
-The interplay between the underling cognitive machinery and 
+cleaner fish should not give priority to visitors anymore.
+
+The interplay between the underlying cognitive machinery and 
 local ecological conditions apparently generate the documented variable 
@@
 biological market theory, we predicted 
-that appropriate performance is to show low preference for visitors under low
+that appropriate performance is to show a low preference for visitors under low
 local cleaner-to-client ratio.
@@
 
-The model consists of a set individual-based simulations where
-individuals, representing cleaners, face a series of choices 
+The model consists of a set of individual-based simulations where
+individuals, representing cleaner fish, face a series of choices 
 between two options, which simulate the natural conditions 
@@
 will converge depends on the relative abundance of cleaners, visitors 
-and resident; as well as on the probability of visitors leaving the 
+and residents; as well as on the probability of visitors leaving the 
 cleaning station when made to wait. Further details of the model 
@@
 
-The model shows that agents need to find a mean 
+The model shows that agents need to find a way 
 to incorporate future consequences of current choices. In the model, 
@@
 If $\gamma=0$, individuals only use the immediate reward obtained from a
-cleaning interaction. As $\gamma$ increases individuals include more the
+cleaning interaction. As $\gamma$ increases, individuals include more the
 reward obtained from the subsequent choices. That amounts to calculating
@@
 Second, $\eta$ measures how much individuals include in their reward the
-fleeing behaviour of visitor as a negative component (penalty). Both of
+fleeing behaviour of visitors as a negative component (penalty). Both of
 these parameters allow individuals to use in their estimates the future
@@
 visitor/resident Plexiglas plates were swapped (see Triki et al. 2019, 2020). 
-Here, we used instead a subset of these data in order to have an idea on 
+Here, we used instead a subset of these data in order to have an idea of 
 cleaner fish preferences for the visitor plate, even if they do not reach 
 the learning criterion within 200 trials. To do so, we first extracted the 
-trial-by-trial outcomes from the last two session (20 trials) of those who 
+trial-by-trial outcomes from the last two sessions (20 trials) of those who 
 never reached the learning criterion for visitor plate 
@@
 For those who reached the learning criterion at some point during the 
-test and passed to a reversal phase, we extracted the trials-by-trial 
+test and passed to a reversal phase, we extracted the trial-by-trial 
 outcomes from the last session (10 trials) before passing to reversal 
@@
 [@triki_Biological_2019;@triki_Brain_2020]. In the 
-suplementaty material (Fig. \ref{fig:rawdata}) we show how our choice maps
+supplementary material (Fig. \ref{fig:rawdata}) we show how our choice maps
 to the previously used criteria. For comparison, we also show a quantification 
-of visitor preference based only on the initial phase of the experiments.
+of visitor preference based only on the initial phase of the task.
 
@@
 resident clients abundances and visitor clients leaving probability,  
-as input to the models. As response variable we used cleaners' 
-preference for visitor over residents in the ephemeral reward task. 
+as input to the models. As the response variable, we used cleaners' 
+preference for visitors over residents in the ephemeral reward task. 
 Finally, we used the preference for visitors resulting from the 
@@
 To capture with the model the relationship between the ecological 
-variables and cleaner fish preferences for visitors we need to scale 
+variables and cleaner fish preferences for visitors, we needed to scale 
 the absolute population densities of cleaner fish from the empirical data
 to a measure of relative abundances that captures client visitation patterns. 
-This is because in the model, relative abundances of clients 
-define not only the probability of residents and visitors, 
+This is because, in the model, relative abundances of clients 
+define not only the probability of residents and visitors 
 but also how often the cleaning station is empty (e.g. there are no 
@@
 depending on their ectoparasite loads. We do not have field estimates 
-for species-specific parasite loads, especially not as a function of site. 
+for species-specific parasite loads, especially not as a function of the site. 
 In order to control for these aspects, we computed a measure of relative 
@@
 part of the statistical inference. As for the visitor and resident 
-abundances we computed a relative measure with respect to the 
+abundances, we computed a relative measure with respect to the 
 total client abundance, and weighted that by the rescaled relative absence 
@@
 choices per cleaner fish). By taking the natural logarithm and summing over all 
-the cleaner fish and reef sites we obtained the log-likelihood of the data 
+the cleaner fish and reef sites, we obtained the log-likelihood of the data 
 given the model and parameters. We then proposed a new set of parameters drawn 
@@
 than the old set replaced old ones, and those with a lower likelihood replaced 
-current ones  with a probability equals to the log-likelihood ratio. 
-Given that we only used the likelihoods in the decision, we used a 
-uninformative prior. Once we decided whether the new parameter set replaces 
-the old one, we ran the model again to sample the likelihood 
+current ones  with a probability equal to the log-likelihood ratio. 
+Given that we only used the likelihoods in the decision, we used an 
+uninformative prior. Once we decided whether the new parameter set 
+would replace the old one, we ran the model again to sample the likelihood 
 distribution of the parameter set. We then started 
-the cycle again by proposing a new set of parameters, and repeated
+the cycle again by proposing a new set of parameters and repeated
 the process for $1e^5$ steps. We ran 5 independent chains, 
 discarded the first $1000$ samples of each chain as burn in, 
-and after that we kept 1 in every 100 samples to avoid autocorrelation. 
+and after that, we kept 1 in every 100 samples to avoid autocorrelation. 
 The collection of parameters sets kept in 
@@
 relation to the log-likelihood of a model
-with parameters $\gamma$ and $\eta$ set to zero. This in practice
-amounts to a model that has neutral preference between the two options. 
+with parameters $\gamma$ and $\eta$ set to zero. This, in practice,
+amounts to a model that has a neutral preference between the two options. 
 We computed the pseudo $R^2$ for all the samples of the posterior from
@@
   scale_fill_manual(values=c("#1b9e77","#d95f02","#7570b3"),
-  name = "Model", labels = labelsPlot.Scen)+
+  name = "", labels = labelsPlot.Scen)+
+  ylab("")+
   scale_y_discrete(labels=labelsPlot.Scen)+
@@
 the log-likelihood of the model is lower than that of a model that
-triggers neutral preferences. Even though, the peak of the three
-$pseudo-R^2$ distributions was not very different, the model with only
+triggers neutral preferences. Even though the peak of the three
+$pseudo-R^2$ distributions were not very different, the model with only
 chaining produced a distribution of $pseudo-R^2$ where more values
-were positive (to the right of black line in Fig. \ref{fig:post} f). This
-shows that, accounting for variation in the parameter estimates, the
+were positive (to the right of the black line in Fig. \ref{fig:post} f). This
+shows that accounting for variation in the parameter estimates the
 model with chaining gives a better fit to the data, despite
@@
 Thick and thin bars show the 66 and 95% credible interval, respectively, 
-taken from those posterior samples. Squares show the predictions used for 
-panel on the right-hand side. Colour coding denotes different reef sites/year 
-of the data collection (see Empirical data section). Black line corresponds 
+taken from those posterior samples. Squares show the predictions used for the
+panel on the right-hand side. Colour coding denotes different reef site/year 
+of the data collection (see Empirical data section). The black line corresponds 
 to a perfect match between observed and predicted probabilities. Upper 
@@
 penalty; middle panels (c and d) from a  model with only chaining; lower 
-panel (e and f) from a model with only penalty.
-
-```{r pred, fig.cap='(ref:pred)',out.width='100%',fig.height=5}
+panels (e and f) from a model with penalty only.
+
+```{r pred, fig.cap='(ref:pred)',out.width='100%',fig.height=5,cache=FALSE}
 
@@
 of the posterior distributions, and by holding constant the balance between 
-resident and visitors´s abundances. Panels on the right, show how close 
+resident and visitors´ abundances. Panels on the right, show how close 
 predictions are from the observed data, allowing the balance between 
-client types to vary, and using a set of samples from the posterior 
+client types to vary and using a set of samples from the posterior 
 distribution.
@@
 separately and combined, we considered cleaner fish performance 
-in the lab test to have its origin from the these fish apply 
+in the lab test to have its origin from the rule these fish applied 
 in their natural environment. That is, individuals that 
 solved the task already had a preference for 
-visitors clients, and generalized this rule to the lab conditions 
+visitors clients and generalized this rule to the lab conditions 
 once being familiar with the task.
 
-While all three models captured well the positive relation between visitor 
+While all three models captured well the positive relationship between visitor 
 leaving behaviour and cleaner fish performance in
@@
 reward task when relative cleaner fish abundance is low, particularly 
-together with high probability of visitor leaving (Fig. \ref{fig:pred}).
+together with a high probability of visitor leaving (Fig. \ref{fig:pred}).
 Low relative cleaner fish abundances mean the market has an excess of demand for
 cleaning services. In the models, this translates to a cleaning station
-that is frequently full. Thus, when a visitors leaves, it is likely that the
+that is frequently full. Thus, when a visitor leaves, it is likely that the
 cleaner fish will have access to another client in the next step. Therefore, 
@@
 becomes so rare that neither mechanism is very efficient 
-at generating a preference for visitors. When facing the resident 
-visitor choice it is still be best to choose the visitor; however,
+at generating a preference for visitors. When facing the 
+resident-visitor choice, it is still best to choose the visitor; however,
 the learning machinery will not be able to develop this preference
@@
 ecological conditions and associated brain morphology, 
-found by Triki *et al* [@triki_Brain_2020], are due to the mechanism 
+found by Triki *et al* [@triki_Brain_2020], is due to the mechanism 
 used to incorporate future consequences. It is conceivable that 
@@
 use negative reinforcement instead of chaining, but in that 
-case negative reinforcement should have explained at least 
+case, negative reinforcement should have explained at least 
 part of the data. Configurational learning or 
@@
 reward task [@quinones_Reinforcement_2019], was 
-not varied in the models we analized here. However, while chunking tendencies 
+not varied in the models we analyzed here. However, while chunking tendencies 
 should vary to allow individuals to adapt to their local conditions 
@@
 the abundance of residents and visitors, and client visitation rate as an 
-indicator of demand. They only need to assess short-term consequences of their
-own decisions on food intake, and chain them. Also, for the sake of 
-simplicity, the model ignores the process by which cleaner fish discriminate 
+indicator of demand. They only need to assess the short-term 
+consequences of their own decisions on food intake and chain them. 
+Also, for the sake of simplicity, the model ignores 
+the process by which cleaner fish discriminate 
 residents and visitor clients. A model that accounts for this discrimination
@@
 than residents in body size [@bshary_Cleaner_2001], and contrary to 
-resindents, are less likely to chase a cleaner fish that fails to cooperate
-and intead cheats its client by taking a bite of mucus 
+residents, they are less likely to chase a cleaner fish that fails to cooperate
+and instead cheats its client by taking a bite of mucus 
 [@bshary_Asymmetric_2002]. Given these associations, chaining might 
@@
 exposed to demonstrations before acquisition. Importantly, Galef
-[@galef_Question_1992] refuted imitation as mechanism not simply because
+[@galef_Question_1992] refuted imitation as a mechanism not simply because
 of the repeated exposure but because a (rather qualitative) analysis of
@@
 cleaners to learn the solution to the ephemeral rewards task 
-would never allow to exclude an important role of 
+would never allow excluding an important role of 
 penalty based on the data
@@
 
-(ref:scaConst) Posterior distributions for scaling constant for the three model 
+(ref:scaConst) Posterior distributions for scaling constant for the three models 
 ("Full model", chaining only" and "penalty only"). We show the kernel 
@@
   in the MCMC.
-$\\sigma$ refers to the amplitud of the perturbation kernel with the subscript indicating the associated parameter.
+$\\sigma$ refers to the amplitude of the perturbation kernel with the subscript indicating the associated parameter.
 New values were taken from a uniform distribution.
@@
 | Number of chains | 5 |
-| Chain lenght | $1^5$ |
+| Chain length | $1^5$ |
 ')
@@
   geom_line() +
-  facet_grid(rows = vars(variable), labeller= labeller(function(var,value){
-  return(parlab[value])})) +
+  facet_grid(rows = vars(variable)) +
   labs(x="Last Iteration in Chain", y="Shrink Factor",
@@
   theme_classic()+
-  theme(legend.position = 'top')
+  theme(legend.position = 'top',strip.text.y  = element_blank())
 
@@
   theme_classic()+
-  theme(legend.position = 'top')
+  theme(legend.position = 'top',strip.text.y = element_blank())
 

### 2022-03-01 manuscript_1.0/manuscript_1.0.tex
Edited the manuscript according to Red1 comments. Readme.md file to facilitate reproducibility.

@@
 %%%% Article title to be placed here
-\title{Combination of field and experimental data together with computational models reveal cognitive mechanisms behind cleaner fish behaviour}
+\title{Field and experimental data together with computational models reveal how cleaner fish adjust decisions in a biological market}
 
@@
 Alternatively, when the different mechanisms interact with environmental conditions, variation in performance across environments might allow to statistically infer the mechanism responsible.
-However, to do this it is necessary to have quantitative predictions for the different candidate mechanisms.
-Here, we use a set of computational models to get quantitative predictions from alternative learning mechanisms, and using Bayesian statistics fit the model parameters to performance data.
-We used experimental data on performance in an ephemeral reward task by wild-caught cleaner fish \emph{Labroides dimidiatus}, as well as cleaner and client fish densities from the locations of capture.
-The task can in principle be solved by estimating future consequences of an action, or by perceiving the removal of the ephemeral reward as psychological punishment (negative reinforcement).
-We found that a model where cleaners only estimate the future consequences of their actions explains best which cleaner fish relative abundances cause the fish to develop a preference for an ephemeral food source.
-This model also yields performances that can be considered the result of locally optimal decision-rules, in contrast to the negative reinforcement model.
-We argue that the combination of computational models with data is a powerful tool to infer the mechanistic underpinning behind cognitive performance.
+We illustrate this point by fitting computational models to experimental data on performance by wild-caught cleaner fish Labroides dimidiatus in an ephemeral reward task, as well as cleaner and client fish densities from the locations of capture.
+Using Bayesian statistics to fit the model parameters to performance data revealed that cleaner fish most likely estimate future consequences of an action, while it appears unlikely that the removal of the ephemeral reward acts as psychological punishment (negative reinforcement).
+Incorporating future consequences also yields performances that can be considered the result of locally optimal decision-rules, in contrast to the negative reinforcement mechanism.
+We argue that the combination of computational models with data is a powerful tool to infer the mechanistic underpinnings of cognitive performance.
 \end{abstract}
@@
 underpinnings of behaviour. This is particularly clear in research aimed at
-discovering interspecific variation in \emph{higher} cognitive abilities; or
+discovering between species variation in \emph{higher} cognitive abilities; or
 in other words, research on whether non-human animals show cognitive
@@
 try to find \emph{mental time travel-like} behaviour, they usually come up with
-clever experiments showing the behaviour displayed requires inferences made
-through past events\citep{dally_Foodcaching_2006}. However, they often face challenges proposing alternative scenarios where simple associations can bring about the
-predicted behavioural outcome \citep{suddendorf_Evolution_2007}. Similarly, attempts
-to show \emph{theory of mind} in non-human animals face objections
-justified by alternative mechanisms that bring about similar behavioural
-results \citep{heyes_Theory_1998}. Such controversies are usually settled by
-using the principle of parsimony, and it's cognitive version,
-Lloyd Morgan's cannon. Which states that the simpler explanation (mechanism)
-must be accepted. Ideally, however, alternative hypothesis should be evaluated
+clever experiments to show the behaviour displayed requires inferences made
+through past events\citep{dally_Foodcaching_2006}. However, they often face the
+challenge of alternative scenarios where simpler explanations,
+like classic associative learning, can bring about the
+observed behavioural outcome \citep{suddendorf_Evolution_2007}. Similarly, attempts
+to demonstrate the presence of \emph{theory of mind} in non-human animals
+face objections justified by alternative mechanisms underpinning
+similar behavioural results \citep{heyes_Theory_1998}.
+Such controversies are usually settled by using the principle
+of parsimony and its cognitive version,
+Lloyd Morgan's cannon, which states that the simpler explanation (mechanism)
+should be accepted. Ideally, however, alternative hypotheses should be evaluated
 in light of their explanatory power. One potential dimension that could allow
 the variation necessary among distinct cognitive mechanisms is environmental
-variation. Controlled laboratory conditions often mask the inter and
-intra-specific variation that arises in the interaction between mechanisms and
-environments. Thus, if predictions from the alternative mechanisms change
-with environmental conditions, it is possible to asses the explanatory power
-of the different hypothesis by performing behavioural test in the context of
+variation. Controlled laboratory conditions often mask between and within
+species variation that arises among different environments. Thus, if
+predictions from the alternative mechanisms depend on environmental
+conditions, it is possible to assess their relative explanatory power
+by performing cognitive test in the context of
 different environmental conditions.
 
-From a evolutionary perspective, mechanisms are likely selected because
+From an evolutionary perspective, mechanisms are likely selected because
 of how they allow individuals to respond to environmental variation.
@@
 it is not clear which cognitive mechanisms allow individuals to adjust their
-behaviour to the varying conditions. As adjustments to changes in
-market conditions have been documented in a great variety of species with
-highly variable brain anatomies, the question arises to what extent
-mechanisms beyond basic associative learning may be involved.
+behaviour to the varying conditions. More specifically the question arises
+to what extent mechanisms beyond basic associative learning may be involved.
 
@@
 access multiple cleaning stations while others access the only cleaning
-station at their territory, it is crucial to categorize clients as
+station in their territory, it is crucial to categorize clients as
 either ``visitors'' or ``residents'', respectively. During cleaning interactions,
@@
 to prioritize visitor over resident clients in a lab-based paradigm,
-they used Plexiglas plates of different colours and shapes offering same
+they used Plexiglas plates of different colours and shapes offering the same
 amount of food as surrogates for visitor and resident clients.
 One plate is made to behave like a resident, i.e.~it remains until
-the cleaner fish had eaten off it. The other plate was made to behave
+the cleaner fish has eaten off it. The other plate was made to behave
 like a visitor, i.e.~it is removed if not inspected first.
 This laboratory paradigm originally inspired by the cleaning market
-of cleaner fish is more generally refered as the ephemeral reward task.
-Individuals are assesed in their capacity to develop a preference for the
+of cleaner fish is more generally referred as the ephemeral reward task.
+Individuals are assessed in their capacity to develop a preference for the
 ephemeral option, which gives them access to two reward units.
@@
 \citep{salwiczek_Adult_2012, zentall_Early_2017}; yet the African grey
-parrots solve this task as well \citep{pepperberg_Can_2014}. This interspecific
-variation in performance, and primates' known cognitive abilities \(\color{red}{\text{ref}}\), shows that performane in the task
+parrots solve this task as well \citep{pepperberg_Can_2014}.
+This between variation in performance, and primates' known cognitive abilities
+\(\color{red}{\text{ref}}\), shows that performance in the task
 cannot be readily explained by classifying species as having high and
-low cognitive abilities. Instead, this inter-spefic variation suggest
+low cognitive abilities. Instead, this between species variation suggests
 that solving the ephemeral reward task requires a set of cognitive
@@
 
-Recent research on the cognitive tool kit needed to solve the ephemeral
+Recent research on the cognitive abilities needed to solve the ephemeral
 reward task has used a broad approach as proposed by Shettleworth
@@
 of the ephemeral reward task, as revealed by proximate learning models.
-Such models allow varying the cognitive tool kit and to evaluate
+Such models allow varying the cognitive tool kit and evaluating
 which minimal kit is necessary to solve
@@
 This is particularly so when models assume the more complex natural
-situation in which cleaner fish not only face resident-visitor pairs but also
+situation in which cleaner fish face not only resident-visitor pairs but also
 visitor-visitor and resident-resident pairs, as well a resident alone or
@@
 same strategic option, paired with a fish with the alternative strategic option)
-\citep{quinones_Reinforcement_2019}. The ability to distinguish and value differently
-one stimulus alone from compound versions of it has been termed
-configurational learning, or chunking,
+\citep{quinones_Reinforcement_2019}. The ability to distinguish and value
+one stimulus differently alone from compound versions of it has been termed
+configurational learning, chunking,
 or segmentation (see references in \citep{prat_Modelling_2022}).
 
-To solve the ephemeral reward task, cleaners need to account for
+In addition to configurational learning, cleaners also need to account for
 the future consequences of current decisions. In the model by
@@
 a complex adaptation \citep{suddendorf_Evolution_2007}. On the other hand,
-using client behaviour as a negative reinforcer is in principle
+using client behaviour as a negative reinforcer is, in principle,
 easier to implement. Negative reinforcement is part of the ubiquitous
-learning mechanism termed operant conditioning \citep{thorndike_Animal_1898, skinner_Behavior_1938}. Thus, standard logic of
+learning mechanism termed operant conditioning \citep{thorndike_Animal_1898, skinner_Behavior_1938}. Thus, the standard logic of
 Lloyd Morgan's cannon demands that operant conditioning as the simpler
@@
 they explain the available data. Note that different fields interested in
-cognition and desicion making use different words to refer to negative
+cognition and decision making use different words to refer to negative
 reinforcers \citep{quinones_Reinforcement_2019, sutton_Reinforcement_2018}.
-In here, for the sake of simplicity and clarity, we will use the word
+Here, for the sake of simplicity and clarity, we will use the word
 `penalty' to refer to this mechanism which includes a negative reinforcer.
 
-Over the last decade, our team tested over a hundred of wild-caught
-cleaner fish in the exact same paradigm of of the ephemeral reward
+Over the last decade, our team tested over a hundred wild-caught
+cleaner fish in the exact same paradigm of the ephemeral reward
 task \citep{salwiczek_Adult_2012, wismer_Variation_2014, triki_Decrease_2018, triki_Biological_2019, triki_Brain_2020}. These fish often come from
@@
 priority \citep{triki_Brain_2020}. In the absence of partner choice
-cleaners should not give priority to visitors any more.
+cleaner fish should not give priority to visitors anymore.
 
-The interplay between the underling cognitive machinery and
+The interplay between the underlying cognitive machinery and
 local ecological conditions apparently generate the documented variable
@@
 biological market theory, we predicted
-that appropriate performance is to show low preference for visitors under low
+that appropriate performance is to show a low preference for visitors under low
 local cleaner-to-client ratio.
@@
 
-The model consists of a set individual-based simulations where
-individuals, representing cleaners, face a series of choices
+The model consists of a set of individual-based simulations where
+individuals, representing cleaner fish, face a series of choices
 between two options, which simulate the natural conditions
@@
 will converge depends on the relative abundance of cleaners, visitors
-and resident; as well as on the probability of visitors leaving the
+and residents; as well as on the probability of visitors leaving the
 cleaning station when made to wait. Further details of the model
@@
 
-The model shows that agents need to find a mean
+The model shows that agents need to find a way
 to incorporate future consequences of current choices. In the model,
@@
 If \(\gamma=0\), individuals only use the immediate reward obtained from a
-cleaning interaction. As \(\gamma\) increases individuals include more the
+cleaning interaction. As \(\gamma\) increases, individuals include more the
 reward obtained from the subsequent choices. That amounts to calculating
@@
 Second, \(\eta\) measures how much individuals include in their reward the
-fleeing behaviour of visitor as a negative component (penalty). Both of
+fleeing behaviour of visitors as a negative component (penalty). Both of
 these parameters allow individuals to use in their estimates the future
@@
 visitor/resident Plexiglas plates were swapped (see Triki et al.~2019, 2020).
-Here, we used instead a subset of these data in order to have an idea on
+Here, we used instead a subset of these data in order to have an idea of
 cleaner fish preferences for the visitor plate, even if they do not reach
 the learning criterion within 200 trials. To do so, we first extracted the
-trial-by-trial outcomes from the last two session (20 trials) of those who
+trial-by-trial outcomes from the last two sessions (20 trials) of those who
 never reached the learning criterion for visitor plate
@@
 For those who reached the learning criterion at some point during the
-test and passed to a reversal phase, we extracted the trials-by-trial
+test and passed to a reversal phase, we extracted the trial-by-trial
 outcomes from the last session (10 trials) before passing to reversal
@@
 \citep{triki_Biological_2019, triki_Brain_2020}. In the
-suplementaty material (Fig. \ref{fig:rawdata}) we show how our choice maps
+supplementary material (Fig. \ref{fig:rawdata}) we show how our choice maps
 to the previously used criteria. For comparison, we also show a quantification
-of visitor preference based only on the initial phase of the experiments.
+of visitor preference based only on the initial phase of the task.
 
@@
 resident clients abundances and visitor clients leaving probability,\\
-as input to the models. As response variable we used cleaners'
-preference for visitor over residents in the ephemeral reward task.
+as input to the models. As the response variable, we used cleaners'
+preference for visitors over residents in the ephemeral reward task.
 Finally, we used the preference for visitors resulting from the
@@
 To capture with the model the relationship between the ecological
-variables and cleaner fish preferences for visitors we need to scale
+variables and cleaner fish preferences for visitors, we needed to scale
 the absolute population densities of cleaner fish from the empirical data
 to a measure of relative abundances that captures client visitation patterns.
-This is because in the model, relative abundances of clients
-define not only the probability of residents and visitors,
+This is because, in the model, relative abundances of clients
+define not only the probability of residents and visitors
 but also how often the cleaning station is empty (e.g.~there are no
@@
 depending on their ectoparasite loads. We do not have field estimates
-for species-specific parasite loads, especially not as a function of site.
+for species-specific parasite loads, especially not as a function of the site.
 In order to control for these aspects, we computed a measure of relative
@@
 part of the statistical inference. As for the visitor and resident
-abundances we computed a relative measure with respect to the
+abundances, we computed a relative measure with respect to the
 total client abundance, and weighted that by the rescaled relative absence
@@
 choices per cleaner fish). By taking the natural logarithm and summing over all
-the cleaner fish and reef sites we obtained the log-likelihood of the data
+the cleaner fish and reef sites, we obtained the log-likelihood of the data
 given the model and parameters. We then proposed a new set of parameters drawn
@@
 than the old set replaced old ones, and those with a lower likelihood replaced
-current ones with a probability equals to the log-likelihood ratio.
-Given that we only used the likelihoods in the decision, we used a
-uninformative prior. Once we decided whether the new parameter set replaces
-the old one, we ran the model again to sample the likelihood
+current ones with a probability equal to the log-likelihood ratio.
+Given that we only used the likelihoods in the decision, we used an
+uninformative prior. Once we decided whether the new parameter set
+would replace the old one, we ran the model again to sample the likelihood
 distribution of the parameter set. We then started
-the cycle again by proposing a new set of parameters, and repeated
+the cycle again by proposing a new set of parameters and repeated
 the process for \(1e^5\) steps. We ran 5 independent chains,
 discarded the first \(1000\) samples of each chain as burn in,
-and after that we kept 1 in every 100 samples to avoid autocorrelation.
+and after that, we kept 1 in every 100 samples to avoid autocorrelation.
 The collection of parameters sets kept in
@@
 relation to the log-likelihood of a model
-with parameters \(\gamma\) and \(\eta\) set to zero. This in practice
-amounts to a model that has neutral preference between the two options.
+with parameters \(\gamma\) and \(\eta\) set to zero. This, in practice,
+amounts to a model that has a neutral preference between the two options.
 We computed the pseudo \(R^2\) for all the samples of the posterior from
@@
 the log-likelihood of the model is lower than that of a model that
-triggers neutral preferences. Even though, the peak of the three
-\(pseudo-R^2\) distributions was not very different, the model with only
+triggers neutral preferences. Even though the peak of the three
+\(pseudo-R^2\) distributions were not very different, the model with only
 chaining produced a distribution of \(pseudo-R^2\) where more values
-were positive (to the right of black line in Fig. \ref{fig:post} f). This
-shows that, accounting for variation in the parameter estimates, the
+were positive (to the right of the black line in Fig. \ref{fig:post} f). This
+shows that accounting for variation in the parameter estimates the
 model with chaining gives a better fit to the data, despite
@@
 Thick and thin bars show the 66 and 95\% credible interval, respectively,
-taken from those posterior samples. Squares show the predictions used for
-panel on the right-hand side. Colour coding denotes different reef sites/year
-of the data collection (see Empirical data section). Black line corresponds
+taken from those posterior samples. Squares show the predictions used for the
+panel on the right-hand side. Colour coding denotes different reef site/year
+of the data collection (see Empirical data section). The black line corresponds
 to a perfect match between observed and predicted probabilities. Upper
@@
 penalty; middle panels (c and d) from a model with only chaining; lower
-panel (e and f) from a model with only penalty.}\label{fig:pred}
+panels (e and f) from a model with penalty only.}\label{fig:pred}
 \end{figure}
@@
 of the posterior distributions, and by holding constant the balance between
-resident and visitors´s abundances. Panels on the right, show how close
+resident and visitors´ abundances. Panels on the right, show how close
 predictions are from the observed data, allowing the balance between
-client types to vary, and using a set of samples from the posterior
+client types to vary and using a set of samples from the posterior
 distribution.
@@
 separately and combined, we considered cleaner fish performance
-in the lab test to have its origin from the these fish apply
+in the lab test to have its origin from the rule these fish applied
 in their natural environment. That is, individuals that
 solved the task already had a preference for
-visitors clients, and generalized this rule to the lab conditions
+visitors clients and generalized this rule to the lab conditions
 once being familiar with the task.
 
-While all three models captured well the positive relation between visitor
+While all three models captured well the positive relationship between visitor
 leaving behaviour and cleaner fish performance in
@@
 reward task when relative cleaner fish abundance is low, particularly
-together with high probability of visitor leaving (Fig. \ref{fig:pred}).
+together with a high probability of visitor leaving (Fig. \ref{fig:pred}).
 Low relative cleaner fish abundances mean the market has an excess of demand for
 cleaning services. In the models, this translates to a cleaning station
-that is frequently full. Thus, when a visitors leaves, it is likely that the
+that is frequently full. Thus, when a visitor leaves, it is likely that the
 cleaner fish will have access to another client in the next step. Therefore,
@@
 becomes so rare that neither mechanism is very efficient
-at generating a preference for visitors. When facing the resident
-visitor choice it is still be best to choose the visitor; however,
+at generating a preference for visitors. When facing the
+resident-visitor choice, it is still best to choose the visitor; however,
 the learning machinery will not be able to develop this preference
@@
 ecological conditions and associated brain morphology,
-found by Triki \emph{et al} \citep{triki_Brain_2020}, are due to the mechanism
+found by Triki \emph{et al} \citep{triki_Brain_2020}, is due to the mechanism
 used to incorporate future consequences. It is conceivable that
@@
 use negative reinforcement instead of chaining, but in that
-case negative reinforcement should have explained at least
+case, negative reinforcement should have explained at least
 part of the data. Configurational learning or
@@
 reward task \citep{quinones_Reinforcement_2019}, was
-not varied in the models we analized here. However, while chunking tendencies
+not varied in the models we analyzed here. However, while chunking tendencies
 should vary to allow individuals to adapt to their local conditions
@@
 the abundance of residents and visitors, and client visitation rate as an
-indicator of demand. They only need to assess short-term consequences of their
-own decisions on food intake, and chain them. Also, for the sake of
-simplicity, the model ignores the process by which cleaner fish discriminate
+indicator of demand. They only need to assess the short-term
+consequences of their own decisions on food intake and chain them.
+Also, for the sake of simplicity, the model ignores
+the process by which cleaner fish discriminate
 residents and visitor clients. A model that accounts for this discrimination
@@
 than residents in body size \citep{bshary_Cleaner_2001}, and contrary to
-resindents, are less likely to chase a cleaner fish that fails to cooperate
-and intead cheats its client by taking a bite of mucus
+residents, they are less likely to chase a cleaner fish that fails to cooperate
+and instead cheats its client by taking a bite of mucus
 \citep{bshary_Asymmetric_2002}. Given these associations, chaining might
@@
 exposed to demonstrations before acquisition. Importantly, Galef
-\citep{galef_Question_1992} refuted imitation as mechanism not simply because
+\citep{galef_Question_1992} refuted imitation as a mechanism not simply because
 of the repeated exposure but because a (rather qualitative) analysis of
@@
 cleaners to learn the solution to the ephemeral rewards task
-would never allow to exclude an important role of
+would never allow excluding an important role of
 penalty based on the data
@@
 
-\caption{Posterior distributions for scaling constant for the three model
+\caption{Posterior distributions for scaling constant for the three models
 (``Full model'', chaining only'' and ``penalty only''). We show the kernel
@@
 in the MCMC.
-\(\sigma\) refers to the amplitud of the perturbation kernel with the subscript indicating the associated parameter.
+\(\sigma\) refers to the amplitude of the perturbation kernel with the subscript indicating the associated parameter.
 New values were taken from a uniform distribution.
@@
 Number of chains & 5 \\
-Chain lenght & \(1^5\) \\
+Chain length & \(1^5\) \\
 \bottomrule

### 2022-03-01 manuscript_1.0/manuscript_word.Rmd
Edited the manuscript according to Red1 comments. Readme.md file to facilitate reproducibility.

@@
 try to find *mental time travel-like* behaviour, they usually come up with 
-clever experiments showing the behaviour displayed requires inferences made 
-through past events[@dally_Foodcaching_2006]. However, they often face challenges proposing alternative scenarios where simple associations can bring about the 
-predicted behavioural outcome [@suddendorf_Evolution_2007]. Similarly, attempts 
-to show *theory of mind* in non-human animals face objections 
-justified by alternative mechanisms that bring about similar behavioural 
-results [@heyes_Theory_1998]. Such controversies are usually settled by 
-using the principle of parsimony, and it's cognitive version, 
-Lloyd Morgan’s cannon. Which states that the simpler explanation (mechanism)
-must be accepted. Ideally, however, alternative hypothesis should be evaluated 
+clever experiments to show the behaviour displayed requires inferences made 
+through past events[@dally_Foodcaching_2006]. However, they often face the
+challenge of alternative scenarios where simpler explanations, 
+like classic associative learning, can bring about the 
+observed behavioural outcome [@suddendorf_Evolution_2007]. Similarly, attempts 
+to demonstrate the presence of *theory of mind* in non-human animals 
+face objections justified by alternative mechanisms underpinning 
+similar behavioural results [@heyes_Theory_1998]. 
+Such controversies are usually settled by using the principle 
+of parsimony and its cognitive version, 
+Lloyd Morgan’s cannon, which states that the simpler explanation (mechanism)
+should be accepted. Ideally, however, alternative hypotheses should be evaluated 
 in light of their explanatory power. One potential dimension that could allow
 the variation necessary among distinct cognitive mechanisms is environmental
-variation. Controlled laboratory conditions often mask the inter and 
-intra-specific variation that arises in the interaction between mechanisms and 
-environments. Thus, if predictions from the alternative mechanisms change
-with environmental conditions, it is possible to asses the explanatory power 
-of the different hypothesis by performing behavioural test in the context of
+variation. Controlled laboratory conditions often mask between and within 
+species variation that arises among different environments. Thus, if 
+predictions from the alternative mechanisms depend on environmental 
+conditions, it is possible to assess the explanatory power 
+of the different hypotheses by performing behavioural test in the context of
 different environmental conditions.
 
-From a evolutionary perspective, mechanisms are likely selected because 
+From an evolutionary perspective, mechanisms are likely selected because 
 of how they allow individuals to respond to environmental variation. 
@@
 same strategic option, paired with a fish with the alternative strategic option) 
-[@quinones_Reinforcement_2019]. The ability to distinguish and value differently
-one stimulus alone from compound versions of it has been termed 
-configurational learning, or chunking, 
+[@quinones_Reinforcement_2019]. The ability to distinguish and value 
+one stimulus differently alone from compound versions of it has been termed 
+configurational learning, chunking, 
 or segmentation (see references in [@prat_Modelling_2022]).
@@
 for the two parameters. On the top, panels a and b show posterior 
-distributions for a full model, including chai %>% ning ($\gamma$) and penalty 
+distributions for a full model, including chaining ($\gamma$) and penalty 
 ($\eta$). Panel c, shows the $\gamma$ estimate from model with only chaining. 

### 2022-03-01 manFigures.R

@@ -206,7 +206,7 @@ cont.obs.pred.both<- ggplot(data = FIAinterpData.both,aes(x=rel.abund.cleaners,y
   scale_fill_gradientn(limits=c(0.3,1),colours= myPalette(100))+theme_classic()+
   geom_point(data = fieldatabyLoc.both,aes(fill=market_binomial_data),size=5,
              shape=21,color="black")+sc+xlab("")+
-  ylab("")+
+  ylab("Prob. of visitor leaving")+
   labs(fill="Probability \n of choosing \n a visitor")+#
   theme(legend.position ="top",
         axis.text = element_text(size=axisSize),
@@ -343,17 +343,9 @@ scatter.obs.pred.Nrew<-ggplot(data=fieldatabyLocSamps.Nrew,
 #   geom_text(x = 0.8, y = 0.5, label = deparse(bquote(R^2==.(round(rsqr.Nrew.McFadden,4)))), 
 #             parse = TRUE,size=3)
 
-# ggarrange(cont.obs.pred.Nrew,scatter.obs.pred.Nrew,
-#           labels=c('a','b'),common.legend=FALSE,legend = "top")
-# 
 # ggarrange(cont.obs.pred.both,scatter.obs.pred.both,
 #           cont.obs.pred.gam,scatter.obs.pred.gam,
-#           labels=c('a','b','c','d'))
-
-# ggarrange(cont.obs.pred.Nrew,scatter.obs.pred.Nrew,
-#           labels=c('a','b'),common.legend=FALSE,legend = "top")
-# 
-# ggarrange(cont.obs.pred.both,scatter.obs.pred.both,
-#           cont.obs.pred.gam,scatter.obs.pred.gam,
-#           labels=c('a','b','c','d'))
+#           cont.obs.pred.Nrew,scatter.obs.pred.Nrew,
+#           labels=c('a','b','c','d','e','f'),common.legend = F,
+#           heights=c(1.4,1,1),nrow = 3,ncol = 2)
 

### 2022-03-01 parTOjson.R

@@ -13,8 +13,8 @@ fileName<-"parameters.json"
 
 # MCMC fit - Generate json parameter files for -------------------------------------
 
-# name of the scenariofor which parameter files will be produces
-# format used for the name: MCMCclean_*parameter1_paramerter2_parameter3
+# name of the scenario for which parameter files will be produces
+# format used for the name: MCMCclean_*parameter1_paramerter2_parameter3.....
 scenario<-"MCMCclean_gam_nRew_sca2"
 
 # for MCMC
@@ -99,6 +99,8 @@ for(seed in 1:5){
 # Predicted values -------------------------------------------------------------
 
 # Run the learning model with parameters estimated through the MCMC
+
+## Using the mode of the marginal posterior distributions
 
 scenario<-"MCMCclean_Nrew_sca"
 

### 2022-03-08 manuscript_1.0/manuscript_1.0.tex
Updated manuscript tp the PLOS Comp. Biol. Updated figures with new figures.

@@
 priority \citep{triki_Brain_2020}. In the absence of partner choice
-cleaner fish should not give priority to visitors anymore.
+cleaner fish should not give priority to visitors any more.
 
@@
 Northern Horseshoe-NHS, and The Crest-TC) at Lizard Island
-(\(14.6682° S, 145.4604° E\)), Great Barrier Reef, Australia.
+(\(14.6682^\circ S, 145.4604^\circ E\)), Great Barrier Reef, Australia.
 The data consist of three sets: fish censuses, field
@@
 reward task \citep{quinones_Reinforcement_2019}, was
-not varied in the models we analyzed here. However, while chunking tendencies
+not varied in the models we analysed here. However, while chunking tendencies
 should vary to allow individuals to adapt to their local conditions

### 2022-03-08 manuscript_1.0/manuscript_word.Rmd
Updated manuscript tp the PLOS Comp. Biol. Updated figures with new figures.

@@
 ---
-title: Field and experimental data together with computational models
-  reveal key cognitive mechanisms behind cleaner fish behaviour
+title: Field and experimental data together with computational 
+  models reveal how cleaner fish adjust decisions  in a biological market
 author:
@@
 Alternatively, when the different mechanisms interact with environmental conditions, variation in performance across environments might allow to statistically infer the mechanism responsible.
-However, to do this it is necessary to have quantitative predictions for the different candidate mechanisms.
-Here, we use a set of computational models to get quantitative predictions from alternative learning mechanisms, and using Bayesian statistics fit the model parameters to performance data.
-We used experimental data on performance in an ephemeral reward task by wild-caught cleaner fish *Labroides dimidiatus*, as well as cleaner and client fish densities from the locations of capture.
-The task can in principle be solved by estimating future consequences of an action, or by perceiving the removal of the ephemeral reward as psychological punishment (negative reinforcement).
-We found that a model where cleaners only estimate the future consequences of their actions explains best which cleaner relative abundances cause the fish to develop a preference for an ephemeral food source.
-This model also yields performances that can be considered the result of locally optimal decision-rules, in contrast to the negative reinforcement model.
-We argue that the combination of computational models with data is a powerful tool to infer the mechanistic underpinning behind cognitive performance.
+We illustrate this point by fitting computational models to experimental data on performance by wild-caught cleaner fish *Labroides dimidiatus* in an ephemeral reward task, as well as cleaner and client fish densities from the locations of capture.
+Using Bayesian statistics to fit the model parameters to performance data revealed that cleaner fish most likely estimate future consequences of an action, while it appears unlikely that the removal of the ephemeral reward acts as psychological punishment (negative reinforcement).
+Incorporating future consequences also yields performances that can be considered the result of locally optimal decision-rules, in contrast to the negative reinforcement mechanism.
+We argue that the combination of computational models with data is a powerful tool to infer the mechanistic underpinnings of cognitive performance.
+author_summary: |
+  Performance in behavioural experiments is often used to assess the cognitive abilities of animals.
+However, animals can get to the same outcome in alternative ways.
+Thus, the outcome of the experiments does not tell us how animals achieve their performance.
+In order to overcome this limitation, we used a set of computational models, which provide predictions on how alternative cognitive mechanisms perform in the face of varying environmental conditions, and compare their predictions to performance data from individuals that experienced different conditions throughout their life.
+Our study system is the cleaner fish *Labroides dimidiatus*, a coral reef fish that feeds off ectoparasites and dead tissue from the skin of other reef fishes.
+Cleaner fish often have to choose among alternative clients seeking their cleaning service, and the optimal choice is often hard to achieve.
+Our performance experiments mimic the natural choices the cleaner fish make.
+The combination of experiments and computational models points to cleaner fish abilities to account for the future effect of their choices by estimating the long term expected value of those choices.
+Estimating long term value is a mechanism involved in human foresight.
 keywords: learning, behaviour, cleaners, bayesian statisitics
@@
 predictions from the alternative mechanisms depend on environmental 
-conditions, it is possible to assess the explanatory power 
-of the different hypotheses by performing behavioural test in the context of
+conditions, it is possible to assess their relative explanatory power 
+by performing cognitive test in the context of
 different environmental conditions.
@@
 
-To solve the ephemeral reward task, cleaners need to account for 
+In addition to configurational learning, cleaners also need to account for 
 the future consequences of current decisions. In the model by 
@@
 priority [@triki_Brain_2020]. In the absence of partner choice 
-cleaner fish should not give priority to visitors anymore.
+cleaner fish should not give priority to visitors any more.
 
@@
 ## Methods
-
-<!-- ### Overview -->
-
-<!-- In this study, we combined empirical data from Triki *et. al*  -->
-<!-- [@triki_Biological_2019;@triki_Brain_2020] and the computational  -->
-<!-- model analysed in Quiñones *et al.*[@quinones_Reinforcement_2019]  -->
-<!-- to test the relative validity of chaining versus operant conditioning as  -->
-<!-- mechanisms to account for future consequences of cleaner fish desicion-making. -->
-<!-- In order to compare the explanatory power of the different hypotheses,  -->
-<!-- we estimated the parameter values of three versions of  -->
-<!-- the model that best fit the empirical data.  -->
-<!-- Particularly, we fitted the parameter that determines how important  -->
-<!-- future reward is ($\gamma$), the magnitude of the negative reward  -->
-<!-- ($\eta$) and a scaling constant that translates cleaner fish absolute  -->
-<!-- to relative population abundances (see following sections for details).  -->
-<!-- We obtained the model predictions using a set of stochastic individual-based -->
-<!-- simulations. Thus, each parameter combination of the model yielded not one  -->
-<!-- but a distribution of predictions. For the  -->
-<!-- fitting procedure, we used the bayesian inference algorithm:  -->
-<!-- Markov Chain Monte Carlo (MCMC). MCMC is a stochastic algorithm that allows -->
-<!-- to sample from the posterior distribution of model parameter values. The posterior -->
-<!-- distribution represents the most likely parameter values given the data.  -->
-<!-- Due to the stochastic nature of MCMC, which repeatedly samples parameter values -->
-<!-- and evaluates their likelihood, the distribution of likelihoods from the  -->
-<!-- stochastic model is also explored. This makes MCMC and bayesian inference -->
-<!-- particularly suitable for the computational models we evaluate. Bellow,  -->
-<!-- we explain first the computational model and the data collection, and later  -->
-<!-- how the MCMC was used to estimate parameter values. -->
 
@@
 
-<!-- A further model analysis contrast the effect of these two  -->
-<!-- parameters against variation in the relative abundance of cleaners  -->
-<!-- and the two client types. Assuming certainty that visitors leave, the  -->
-<!-- two parameters yield different  -->
-<!-- predictions when relative client abundance is very high. Under such  -->
-<!-- conditions, the analysis shows that under very high client (relative)  -->
-<!-- abundance the presence of future rewards ($\gamma>0$) no longer favours  -->
-<!-- the preference for the ephemeral clients, while the preference persists  -->
-<!-- when the negative reward mediated by client behaviour ($\eta>0$) is  -->
-<!-- included. Thus, the analysis suggests that future reward as an  -->
-<!-- explanation for cleaner fish ability to prefer visitors is supported.  -->
-<!-- At first sight, empirical data seem to support future rewards as  -->
-<!-- the mechanism used by cleaners, as the statistical analysis  by  -->
-<!-- Triki *et al.* [@triki_Biological_2019] data revealed that low  -->
-<!-- cleaner-to-client ratios predict low preference for visitors and hence  -->
-<!-- low performance in the ephemeral reward task. However, low cleaner-to-client  -->
-<!-- ratios may also lead to low probabilities of visitors leaving, which would  -->
-<!-- cause low preferences for visitors independently of the underlying  -->
-<!-- mechanism [@quinones_Reinforcement_2019]. Furthermore, a combination  -->
-<!-- of future and negative rewards, could still be yield a better explanation  -->
-<!-- for the data than any single factor.  -->
-
 ### Empirical data
@@
 Northern Horseshoe-NHS, and The Crest-TC)  at Lizard Island 
-($14.6682° S, 145.4604° E$), Great Barrier Reef, Australia. 
+($14.6682^\circ S, 145.4604^\circ E$), Great Barrier Reef, Australia. 
 The data consist of three sets: fish censuses, field 
@@
 
-(ref:post) Posterior distributions for parameter values $\gamma$ and $\eta$ for 
-the three models ("Full model", "chaining only" and "penalty only"). We show 
-the kernel density estimates, below the mode (black dot) and the 65% 
-(light blue shade) and 95% (grey shade)  highest posterior density interval 
-for the two parameters. On the top, panels a and b show posterior 
-distributions for a full model, including chaining ($\gamma$) and penalty 
-($\eta$). Panel c, shows the $\gamma$ estimate from model with only chaining. 
-Panel d shows the $\\eta$ estimate from a model with only penalty. Panel e, 
-shows a measure of fit for all models, namely the distribution of pseudo-$R^2$ 
-obtained from sampling the posterior distribution of parameter values.
-
-```{r post, fig.cap='(ref:post)',out.width='100%',fig.height=6}
-library(data.table)
-library(coda)
-library(ggplot2)
-library(cowplot)
-library(ggdist)
-library(ggpubr)
-source(here("../R_files/posPlots.R"))
-source(here("loadData.R"))
-library("jsonlite")
-
-# Name of the folders containing the MCMC runs
-# scen1<-"MCMCclean_gam_nRew_sca_"
-# scen2<-"MCMCclean_gam_sca_"
-# scen3<-"MCMCclean_Nrew_sca_"
-
-scen1<-"MCMCclean_gam_Nrew_sca_old_"
-scen2<-"MCMCclean_gam_sca_old_"
-scen3<-"MCMCclean_Nrew_sca_old_"
-
-# NLables names for the three scenarios
-labels.Scen<-c("both","gam","Nrew")
-labelsPlot.Scen<-c("Full Model","Chaining","Penalty")
-
-## Load files --------------------------------------------------------------
-
-# Defaults for MCMC analysis
-burn.in<-1000
-thinning<-100
-
-MCMCdata1<-loadMCMCrun(scen1,thinning = thinning,burn.in = burn.in)
-MCMCdata2<-loadMCMCrun(scen2,thinning = thinning,burn.in = burn.in)
-MCMCdata3<-loadMCMCrun(scen3,thinning = thinning,burn.in = burn.in)
-
-# Create list with the data, convenient to use CODA for diagnostics
-mcmcList.1<-mcmc.list(do.call(list,lapply(unique(MCMCdata1$seed), function(repli){
-  rundata<-MCMCdata1[seed==repli]
-  mcmcRun<-mcmc(rundata[,.(gamma,negReward,scaleConst)],thin = thinning)#
-  return(mcmcRun)
-})))
-
-mcmcList.2<-mcmc.list(do.call(list,lapply(unique(MCMCdata2$seed), function(repli){
-  rundata<-MCMCdata2[seed==repli]
-  mcmcRun<-mcmc(rundata[,.(gamma,scaleConst)],thin = thinning)
-  return(mcmcRun)
-})))
-
-mcmcList.3<-mcmc.list(do.call(list,lapply(unique(MCMCdata3$seed), function(repli){
-  rundata<-MCMCdata3[seed==repli]
-  mcmcRun<-mcmc(rundata[,.(negReward,scaleConst)],thin = thinning)#
-  return(mcmcRun)
-})))
-
-## Density plots with gg -------------------------------------------------------
-
-## Define the boundaries for credible intervals using High Density Interval
-
-intervals<-c(0.66,0.95)
-
-cuts.1<-lapply(MCMCdata1[,.(gamma,negReward,scaleConst)],
-             function(x){
-               c(mode_hdci(x,.width = intervals[c(2,1)])$ymin,
-                 mode_hdci(x,.width = intervals)$ymax)
-})
-
-cuts.2<-lapply(MCMCdata2[,.(gamma,scaleConst)],
-               function(x){
-                 c(mode_hdci(x,.width = intervals[c(2,1)])$ymin,
-                   mode_hdci(x,.width = intervals)$ymax)
-               })
-
-cuts.3<-lapply(MCMCdata3[,.(negReward,scaleConst)],
-               function(x){
-                 c(mode_hdci(x,.width = intervals[c(2,1)])$ymin,
-                   mode_hdci(x,.width = intervals)$ymax)
-               })
-
-# get all the likelihoods from the posterior for all models
-loglikehoods.all<-data.table(lglikelihood=c(MCMCdata1$fit,MCMCdata2$fit,
-                                             MCMCdata3$fit),
-                              model=c(rep(labels.Scen[1],length(MCMCdata1$fit)),
-                                      rep(labels.Scen[2],length(MCMCdata2$fit)),
-                                      rep(labels.Scen[3],length(MCMCdata3$fit))
-                                      ))
-
-# Read field data to calculate null log-likelihood
-fieldData<-fread(here("Data","data_cleaner_abs_threa1.5.txt"))
-
-nullLikehood<-sum(dbinom(x=fieldData[,score_visitor],
-                         size = 20,prob = 0.5,log = TRUE))
-
-# calculate pseudo R^2
-loglikehoods.all[,Rsqrd:=1-lglikelihood/nullLikehood]
-
-panel.rsqr.all<-
-  ggplot(data=loglikehoods.all[is.finite(lglikelihood)],
-                  aes(y=model,x=Rsqrd,fill=model))+
-  stat_halfeye(alpha=0.5,point_size=3)+
-  theme_classic()+xlim(-0.5,0.25)+
-  scale_fill_manual(values=c("#1b9e77","#d95f02","#7570b3"),
-  name = "", labels = labelsPlot.Scen)+
-  ylab("")+
-  scale_y_discrete(labels=labelsPlot.Scen)+
-  geom_vline(xintercept = 0,color="black",size=0.5)+
-  theme(legend.position = 'none')
-          # c(.32, .65)
-        # ,legend.key.size = unit(0.22,'cm'),
-        # axis.text.y = element_blank(),
-        # legend.text = element_text(size=7))
-
-gam.both.post<-ggplot(data=MCMCdata1,aes(x=gamma)) +
-  stat_halfeye(aes(fill=stat(cut(x,breaks = cuts.1$gamma))),
-               point_interval = mode_hdi, .width = c(.66, .95),
-               point_size=3,show.legend=FALSE) +
-  labs(title=labelsPlot.Scen[1],
-       subtitle = expression(gamma),x="",y="")+
-  theme_classic()+
-  scale_fill_manual(values=c("gray85","skyblue","gray85"))
-
-nrew.both.post<-ggplot(data=MCMCdata1,aes(x=negReward)) +
-  stat_halfeye(aes(fill=stat(cut(x,breaks = cuts.1$negReward))),
-               point_interval = mode_hdi,
-               .width = c(.66, .95),point_size=3,
-               show.legend=FALSE)+theme_classic()+
-  scale_fill_manual(values=c("gray85","skyblue","gray85"))+
-  labs(title="",subtitle = expression(eta),x="",y="")+
-  xlim(-2,2)
-gam.gam.post<-ggplot(data=MCMCdata2,aes(x=gamma)) +
-  stat_halfeye(aes(fill=stat(cut(x,breaks = cuts.2$gamma))),
-               point_interval = mode_hdi, .width = c(.66, .95),
-               point_size=3,
-               show.legend=FALSE) +
-  scale_fill_manual(values=c("gray85","skyblue","gray85"))+
-  labs(title=labelsPlot.Scen[2],
-       subtitle = expression(gamma),x="",y="")+
-  theme_classic()
-nrew.nrew.post<-ggplot(data=MCMCdata3,aes(x=negReward)) +
-  stat_halfeye(aes(fill=stat(cut(x,breaks = cuts.3$negReward))),
-               point_interval = mode_hdi, .width = c(.66, .95),
-               point_size=3,
-               show.legend=FALSE) +
-  scale_fill_manual(values=c("gray85","skyblue","gray85"))+
-  labs(title=labelsPlot.Scen[3],
-       subtitle = expression(gamma),x="",y="")+
-  theme_classic()+xlim(-2,2)
-
+<!-- (ref:post) Posterior distributions for parameter values $\gamma$ and $\eta$ for  -->
+<!-- the three models ("Full model", "chaining only" and "penalty only"). We show  -->
+<!-- the kernel density estimates, below the mode (black dot) and the 65%  -->
+<!-- (light blue shade) and 95% (grey shade)  highest posterior density interval  -->
+<!-- for the two parameters. On the top, panels a and b show posterior  -->
+<!-- distributions for a full model, including chaining ($\gamma$) and penalty  -->
+<!-- ($\eta$). Panel c, shows the $\gamma$ estimate from model with only chaining.  -->
+<!-- Panel d shows the $\eta$ estimate from a model with only penalty. Panel e,  -->
+<!-- shows a measure of fit for all models, namely the distribution of pseudo-$R^2$  -->
+<!-- obtained from sampling the posterior distribution of parameter values. -->
+
+```{r post, fig.cap='Posterior distributions for parameter values $\\gamma$ and $\\eta$ for the three models (Full model, chaining only and penalty only).
+We show the kernel density estimates, below the mode (black dot) and the 65 (light blue shade) and 95\\% (grey shade)  highest posterior density interval for the two parameters.
+On the top, panels a and b show posterior distributions for a full model, including chaining ($\\gamma$) and penalty ($\\eta$).
+Panel c, shows the $\\gamma$ estimate from model with only chaining.
+Panel d shows the $\\eta$ estimate from a model with only penalty.
+Panel e, shows a measure of fit for all models, namely the distribution of pseudo-$R^2$ obtained from sampling the posterior distribution of parameter values.',out.width='100%',fig.height=6,cache=FALSE}
+
+source(here("analysisMCMC.R"))
 first.col<-plot_grid(nrow=3,align = "v",byrow = TRUE,
@@
 
-(ref:pred) Observed and predicted probability of choosing a visitor. 
-Left-hand side panel: colour contour shows the prediction from the 
-learning model using the mode of the posterior distributions of parameters 
-recovered by the statistical analysis. Dots show the frequency of visitor 
-choices for the 12 reef sites, as well as the corresponding relative 
-cleaner fish abundance (x axis) and frequency of visitors clients leaving 
-the cleaning station (y axis). Right-hand side panels: Variation of the 
-predicted probabilities  of choosing a visitor over a resident and their 
-observed values for 12 locations. Circles show the mean prediction for 
-each location from 100 samples taken from the posterior distribution. 
-Thick and thin bars show the 66 and 95% credible interval, respectively, 
-taken from those posterior samples. Squares show the predictions used for the
-panel on the right-hand side. Colour coding denotes different reef site/year 
-of the data collection (see Empirical data section). The black line corresponds 
-to a perfect match between observed and predicted probabilities. Upper 
-panels (a and b) show predictions from a model including chaining and 
-penalty; middle panels (c and d) from a  model with only chaining; lower 
-panels (e and f) from a model with penalty only.
-
-```{r pred, fig.cap='(ref:pred)',out.width='100%',fig.height=5,cache=FALSE}
-
- source(here("manFigures.R"))
+<!-- (ref:pred) Observed and predicted probability of choosing a visitor.  -->
+<!-- Left-hand side panel: colour contour shows the prediction from the  -->
+<!-- learning model using the mode of the posterior distributions of parameters  -->
+<!-- recovered by the statistical analysis. Dots show the frequency of visitor  -->
+<!-- choices for the 12 reef sites, as well as the corresponding relative  -->
+<!-- cleaner fish abundance (x axis) and frequency of visitors clients leaving  -->
+<!-- the cleaning station (y axis). Right-hand side panels: Variation of the  -->
+<!-- predicted probabilities  of choosing a visitor over a resident and their  -->
+<!-- observed values for 12 locations. Circles show the mean prediction for  -->
+<!-- each location from 100 samples taken from the posterior distribution.  -->
+<!-- Thick and thin bars show the 66 and 95% credible interval, respectively,  -->
+<!-- taken from those posterior samples. Squares show the predictions used for the -->
+<!-- panel on the right-hand side. Colour coding denotes different reef site/year  -->
+<!-- of the data collection (see Empirical data section). The black line corresponds  -->
+<!-- to a perfect match between observed and predicted probabilities. Upper  -->
+<!-- panels (a and b) show predictions from a model including chaining and  -->
+<!-- penalty; middle panels (c and d) from a  model with only chaining; lower  -->
+<!-- panels (e and f) from a model with penalty only. -->
+
+```{r pred, fig.cap='Observed and predicted probability of choosing a visitor.
+Left-hand side panel: colour contour shows the prediction from the learning model using the mode of the posterior distributions of parameters recovered by the statistical analysis.
+Dots show the frequency of visitor choices for the 12 reef sites, as well as the corresponding relative cleaner fish abundance (x axis) and frequency of visitors clients leaving the cleaning station (y axis).
+Right-hand side panels: Variation of the predicted probabilities  of choosing a visitor over a resident and their observed values for 12 locations.
+Circles show the mean prediction for each location from 100 samples taken from the posterior distribution.
+Thick and thin bars show the 66 and 95\\% credible interval, respectively, taken from those posterior samples.
+Squares show the predictions used for the panel on the right-hand side.
+Colour coding denotes different reef site/year of the data collection (see Empirical data section).
+The black line corresponds to a perfect match between observed and predicted probabilities.
+Upper panels (a and b) show predictions from a model including chaining and penalty; middle panels (c and d) from a  model with only chaining; lower panels (e and f) from a model with penalty only.',out.width='100%',fig.height=5,cache=FALSE}
+
+ source(here("predictions.R"))
  ggarrange(cont.obs.pred.both,scatter.obs.pred.both,
@@
 reward task [@quinones_Reinforcement_2019], was 
-not varied in the models we analyzed here. However, while chunking tendencies 
+not varied in the models we analysed here. However, while chunking tendencies 
 should vary to allow individuals to adapt to their local conditions 
@@
 
-(ref:rawdata) Relation between the response variable used in this study and the 
-criteria used in previous studies to assess performance in the ephemeral reward 
-task. In the x axis, we classified the performance of cleaner fish according to 
-whether they developed a preference for the visitor in the initial round, 
-in the initial and reversal, or none of them. In the y axis, we add the choices
-of two experimental sessions: panel on the left uses one session from the initial 
-round and one from the reversal round when possible 
-(as described in the main text); panel on the right uses two sessions from the 
-initial round for all fish.
-
-```{r rawdata,fig.cap='(ref:rawdata)'}
+<!-- (ref:rawdata)  -->
+
+```{r rawdata,fig.cap='Relation between the response variable used in this study and the criteria used in previous studies to assess performance in the ephemeral reward task.
+In the x axis, we classified the performance of cleaner fish according to whether they developed a preference for the visitor in the initial round, in the initial and reversal, or none of them.
+In the y axis, we add the choices of two experimental sessions: panel on the left uses one session from the initial round and one from the reversal round when possible (as described in the main text); panel on the right uses two sessions from the initial round for all fish.',out.width='100%',fig.height=5,cache=FALSE}
 plot_grid(initANDRev,init,ncol = 2)
@@
 
-(ref:scaConst) Posterior distributions for scaling constant for the three models 
-("Full model", chaining only" and "penalty only"). We show the kernel 
-density estimates, below the mode (black dot) and the 65% (light blue shade) 
-and 95% (grey shade)  highest posterior density interval. On the top, 
-panel a shows the posterior distribution from the full model; panel b from 
-the model with only chaining; and panel c from a model with only penalty.
-
-```{r scaConst, fig.cap='(ref:scaConst)',fig.pos = 'H', out.extra = "",out.width='95%',fig.height=4}
+<!-- (ref:scaConst) Posterior distributions for scaling constant for the three models -->
+<!-- ("Full model", chaining only" and "penalty only"). We show the kernel -->
+<!-- density estimates, below the mode (black dot) and the 65% (light blue shade) -->
+<!-- and 95% (grey shade)  highest posterior density interval. On the top, -->
+<!-- panel a shows the posterior distribution from the full model; panel b from -->
+<!-- the model with only chaining; and panel c from a model with only penalty. -->
+
+```{r scaConst, fig.cap='Posterior distributions for scaling constant for the three models (Full model, chaining only and penalty only).
+We show the kernel density estimates, below the mode (black dot) and the 65\\% (light blue shade) and 95\\% (grey shade)  highest posterior density interval.
+On the top, panel a shows the posterior distribution from the full model; panel b from the model with only chaining; and panel c from a model with only penalty.',fig.pos = 'H', out.extra = "",out.width='95%',fig.height=5}
 
@@
   theme_classic()+
-  scale_fill_manual(values=c("skyblue","gray85"))
+  scale_fill_manual(values=c("gray85","skyblue","gray85"))
 sca.gam.post<-ggplot(data=MCMCdata2,aes(x=scaleConst)) + 
@@
 
+<!-- (ref:diagnosticsfull) MCMC convergence diagnostics for the full model.  -->
+<!-- On the left trace-plots, on the right changes along the chain of the  -->
+<!-- Gelman and Rubin's shrink factor [@brooks_General_1998]. -->
+
+```{r diagnosticsfull, fig.cap='MCMC convergence diagnostics for the full model.
+On the left trace-plots, on the right changes along the chain of the Gelman and Rubin shrink factor.',out.width='100%',fig.height=5,cache=FALSE,message=FALSE}
+
+longMCMCdata1<-melt(MCMCdata1,id.vars = c("iteration","seed"),
+                    variable.name = "parameter",
+                    measure.vars = c("gamma","negReward","scaleConst"))
+
+parlab<-list(`gamma` =expression(gamma),
+          `negReward`=expression(eta),
+          `scaleConst`="Scaling constant")
+
+traces.full<-ggplot(longMCMCdata1,aes(x=iteration,y=value,colour=as.factor(seed)))+
+  geom_line()+
+  scale_color_manual(values = multDiscrPallet)+
+  labs(color="Chain")+
+  facet_grid(rows=vars(parameter),scales = "free",switch = "y",
+             labeller = function(variable,value){
+  return(parlab[value])})+
+  theme_classic()+
+  theme(legend.position = 'top')
+
+gel.full<-as.data.table(gelman.diag(mcmcList.1)$psrf)
+gel.full[,parameter:=c("gamma","negReward","scalConst")]
+
+pdf(file = NULL)
+gp.dat<-gelman.plot(mcmcList.1)
+rubbish <- dev.off()
+
+gp.dat.frame <- data.table(rbind(as.data.frame(gp.dat[["shrink"]][,,1]), 
+                          as.data.frame(gp.dat[["shrink"]][,,2])), 
+                q=rep(dimnames(gp.dat[["shrink"]])[[3]], each=nrow(gp.dat[["shrink"]][,,1])),
+                last.iter=rep(gp.dat[["last.iter"]], length(gp.dat)))
+
+gelman.full<-ggplot(melt(gp.dat.frame, c("q","last.iter"), value.name="shrink_factor"), 
+       aes(last.iter, shrink_factor, colour=q, linetype=q)) + 
+  geom_hline(yintercept=1, colour="grey30", lwd=0.2) +
+  geom_line() +
+  facet_grid(rows = vars(variable)) +
+  labs(x="Last Iteration in Chain", y="Shrink Factor",
+       colour="Quantile", linetype="Quantile") +
+  scale_linetype_manual(values=c(2,1))+
+  theme_classic()+
+  theme(legend.position = 'top',strip.text.y  = element_blank())
+
+ggarrange(traces.full,gelman.full)
+
+```
+
+<!-- (ref:diagnosticsGam) MCMC convergence diagnostics for the chaining model.  -->
+<!-- On the left trace-plots, on the right changes along the chain of the  -->
+<!-- Gelman and Rubin's shrink factor [@brooks_General_1998] -->
+
+```{r diaggam,fig.cap='MCMC convergence diagnostics for the chaining model.
+On the left trace-plots, on the right changes along the chain of the Gelman and Rubin shrink factor ',echo=FALSE,message=FALSE,out.width='100%',fig.height=5,cache=FALSE,message=FALSE}
+longMCMCdata2<-melt(MCMCdata2,id.vars = c("iteration","seed"),
+                    variable.name = "parameter",
+                    measure.vars = c("gamma","scaleConst"))
+
+parlab<-list(`gamma` =expression(gamma),
+          `scaleConst`="Scaling constant")
+
+traces.gam<-ggplot(longMCMCdata2,aes(x=iteration,y=value,colour=as.factor(seed)))+
+  geom_line()+
+  scale_color_manual(values = multDiscrPallet)+
+  labs(color="Chain")+
+  facet_grid(rows=vars(parameter),scales = "free",switch = "y",
+             labeller = function(variable,value){
+  return(parlab[value])})+
+  theme_classic()+
+  theme(legend.position = 'top')
+
+gel.gam<-as.data.table(gelman.diag(mcmcList.2)$psrf)
+gel.gam[,parameter:=c("gamma","scalConst")]
+
+pdf(file = NULL)
+gp.dat.gam<-gelman.plot(mcmcList.2)
+rubbish <- dev.off()
+
+gp.dat.frame.gam <- data.table(rbind(as.data.frame(gp.dat.gam[["shrink"]][,,1]), 
+                          as.data.frame(gp.dat.gam[["shrink"]][,,2])), 
+                q=rep(dimnames(gp.dat.gam[["shrink"]])[[3]], each=nrow(gp.dat.gam[["shrink"]][,,1])),
+                last.iter=rep(gp.dat.gam[["last.iter"]], length(gp.dat.gam)))
+
+gelman.gam<-ggplot(melt(gp.dat.frame.gam, c("q","last.iter"), value.name="shrink_factor"), 
+       aes(last.iter, shrink_factor, colour=q, linetype=q)) + 
+  geom_hline(yintercept=1, colour="grey30", lwd=0.2) +
+  geom_line() +
+  facet_grid(rows = vars(variable)) +
+  labs(x="Last Iteration in Chain", y="Shrink Factor",
+       colour="Quantile", linetype="Quantile") +
+  scale_linetype_manual(values=c(2,1))+
+  theme_classic()+
+  theme(legend.position = 'top',strip.text.y = element_blank())
+
+ggarrange(traces.gam,gelman.gam)
+```
+
+<!-- (ref:diagNeg) MCMC convergence diagnostics for the penalty model. -->
+<!-- On the left trace-plots, on the right changes along the chain of the -->
+<!-- Gelman and Rubin's shrink factor [@brooks_General_1998] -->
+
+```{r diagNeg,fig.cap='MCMC convergence diagnostics for the penalty model.
+On the left trace-plots, on the right changes along the chain of the Gelman and Rubin shrink factor',out.width='100%',fig.height=5,cache=FALSE,message=FALSE,out.width='100%',fig.height=5,cache=FALSE,message=FALSE}
+longMCMCdata3<-melt(MCMCdata3,id.vars = c("iteration","seed"),
+                    variable.name = "parameter",
+                    measure.vars = c("negReward","scaleConst"))
+
+parlab<-list(`negReward` =expression(eta),
+          `scaleConst`="Scaling constant")
+
+traces.neg<-ggplot(longMCMCdata3,aes(x=iteration,y=value,colour=as.factor(seed)))+
+  geom_line()+
+  scale_color_manual(values = multDiscrPallet)+
+  labs(color="Chain")+
+  facet_grid(rows=vars(parameter),scales = "free",switch = "y",
+             labeller = function(variable,value){
+  return(parlab[value])})+
+  theme_classic()+
+  theme(legend.position = 'top')
+
+pdf(file = NULL)
+gp.dat.neg<-gelman.plot(mcmcList.3)
+rubbish <- dev.off()
+
+gp.dat.frame.neg <- data.table(rbind(as.data.frame(gp.dat.neg[["shrink"]][,,1]),
+                          as.data.frame(gp.dat.neg[["shrink"]][,,2])),
+                q=rep(dimnames(gp.dat.neg[["shrink"]])[[3]], each=nrow(gp.dat.neg[["shrink"]][,,1])),
+                last.iter=rep(gp.dat.neg[["last.iter"]], length(gp.dat.neg)))
+
+gelman.neg<-ggplot(melt(gp.dat.frame.neg, c("q","last.iter"), value.name="shrink_factor"),
+       aes(last.iter, shrink_factor, colour=q, linetype=q)) +
+  geom_hline(yintercept=1, colour="grey30", lwd=0.2) +
+  geom_line() +
+  facet_grid(rows = vars(variable)) +
+  labs(x="Last Iteration in Chain", y="Shrink Factor",
+       colour="Quantile", linetype="Quantile") +
+  scale_linetype_manual(values=c(2,1))+
+  theme_classic()+
+  theme(legend.position = 'top',strip.text.y = element_blank())
+
+ggarrange(traces.neg,gelman.neg)
+```
+
 ```{r param , echo=FALSE,results='asis'}
@@
 ```
-
-(ref:diagnosticsfull) MCMC convergence diagnostics for the full model. 
-On the left trace-plots, on the right changes along the chain of the 
-Gelman and Rubin's shrink factor [@brooks_General_1998].
-
-```{r diagnosticsfull, fig.cap='(ref:diagnosticsfull)',message=FALSE,echo=FALSE,fig.height=5}
-
-longMCMCdata1<-melt(MCMCdata1,id.vars = c("iteration","seed"),
-                    variable.name = "parameter",
-                    measure.vars = c("gamma","negReward","scaleConst"))
-
-parlab<-list(`gamma` =expression(gamma),
-          `negReward`=expression(eta),
-          `scaleConst`="Scaling constant")
-
-traces.full<-ggplot(longMCMCdata1,aes(x=iteration,y=value,colour=as.factor(seed)))+
-  geom_line()+
-  scale_color_manual(values = multDiscrPallet)+
-  labs(color="Chain")+
-  facet_grid(rows=vars(parameter),scales = "free",switch = "y",
-             labeller = function(variable,value){
-  return(parlab[value])})+
-  theme_classic()+
-  theme(legend.position = 'top')
-
-gel.full<-as.data.table(gelman.diag(mcmcList.1)$psrf)
-gel.full[,parameter:=c("gamma","negReward","scalConst")]
-
-pdf(file = NULL)
-gp.dat<-gelman.plot(mcmcList.1)
-rubbish <- dev.off()
-
-gp.dat.frame <- data.table(rbind(as.data.frame(gp.dat[["shrink"]][,,1]), 
-                          as.data.frame(gp.dat[["shrink"]][,,2])), 
-                q=rep(dimnames(gp.dat[["shrink"]])[[3]], each=nrow(gp.dat[["shrink"]][,,1])),
-                last.iter=rep(gp.dat[["last.iter"]], length(gp.dat)))
-
-gelman.full<-ggplot(melt(gp.dat.frame, c("q","last.iter"), value.name="shrink_factor"), 
-       aes(last.iter, shrink_factor, colour=q, linetype=q)) + 
-  geom_hline(yintercept=1, colour="grey30", lwd=0.2) +
-  geom_line() +
-  facet_grid(rows = vars(variable), labeller= labeller(function(var,value){
-  return(parlab[value])})) +
-  labs(x="Last Iteration in Chain", y="Shrink Factor",
-       colour="Quantile", linetype="Quantile") +
-  scale_linetype_manual(values=c(2,1))+
-  theme_classic()+
-  theme(legend.position = 'top')
-
-ggarrange(traces.full,gelman.full)
-
-```
-
-(ref:diagnosticsGam) MCMC convergence diagnostics for the chaining model. 
-On the left trace-plots, on the right changes along the chain of the 
-Gelman and Rubin's shrink factor [@brooks_General_1998]
-
-```{r diaggam,fig.cap='(ref:diagnosticsGam)',echo=FALSE,message=FALSE}
-longMCMCdata2<-melt(MCMCdata2,id.vars = c("iteration","seed"),
-                    variable.name = "parameter",
-                    measure.vars = c("gamma","scaleConst"))
-
-parlab<-list(`gamma` =expression(gamma),
-          `scaleConst`="Scaling constant")
-
-traces.gam<-ggplot(longMCMCdata2,aes(x=iteration,y=value,colour=as.factor(seed)))+
-  geom_line()+
-  scale_color_manual(values = multDiscrPallet)+
-  labs(color="Chain")+
-  facet_grid(rows=vars(parameter),scales = "free",switch = "y",
-             labeller = function(variable,value){
-  return(parlab[value])})+
-  theme_classic()+
-  theme(legend.position = 'top')
-
-gel.gam<-as.data.table(gelman.diag(mcmcList.2)$psrf)
-gel.gam[,parameter:=c("gamma","scalConst")]
-
-pdf(file = NULL)
-gp.dat.gam<-gelman.plot(mcmcList.2)
-rubbish <- dev.off()
-
-gp.dat.frame.gam <- data.table(rbind(as.data.frame(gp.dat.gam[["shrink"]][,,1]), 
-                          as.data.frame(gp.dat.gam[["shrink"]][,,2])), 
-                q=rep(dimnames(gp.dat.gam[["shrink"]])[[3]], each=nrow(gp.dat.gam[["shrink"]][,,1])),
-                last.iter=rep(gp.dat.gam[["last.iter"]], length(gp.dat.gam)))
-
-gelman.gam<-ggplot(melt(gp.dat.frame.gam, c("q","last.iter"), value.name="shrink_factor"), 
-       aes(last.iter, shrink_factor, colour=q, linetype=q)) + 
-  geom_hline(yintercept=1, colour="grey30", lwd=0.2) +
-  geom_line() +
-  facet_grid(rows = vars(variable), labeller= labeller(function(var,value){
-  return(parlab[value])})) +
-  labs(x="Last Iteration in Chain", y="Shrink Factor",
-       colour="Quantile", linetype="Quantile") +
-  scale_linetype_manual(values=c(2,1))+
-  theme_classic()+
-  theme(legend.position = 'top')
-
-ggarrange(traces.gam,gelman.gam)
-```
-
-(ref:diagNeg) MCMC convergence diagnostics for the penalty model.
-On the left trace-plots, on the right changes along the chain of the
-Gelman and Rubin's shrink factor [@brooks_General_1998]
-
-```{r diagNeg,fig.cap='(ref:diagNeg)',message=FALSE}
-longMCMCdata3<-melt(MCMCdata3,id.vars = c("iteration","seed"),
-                    variable.name = "parameter",
-                    measure.vars = c("negReward","scaleConst"))
-
-parlab<-list(`negReward` =expression(eta),
-          `scaleConst`="Scaling constant")
-
-traces.neg<-ggplot(longMCMCdata3,aes(x=iteration,y=value,colour=as.factor(seed)))+
-  geom_line()+
-  scale_color_manual(values = multDiscrPallet)+
-  labs(color="Chain")+
-  facet_grid(rows=vars(parameter),scales = "free",switch = "y",
-             labeller = function(variable,value){
-  return(parlab[value])})+
-  theme_classic()+
-  theme(legend.position = 'top')
-
-pdf(file = NULL)
-gp.dat.neg<-gelman.plot(mcmcList.3)
-rubbish <- dev.off()
-
-gp.dat.frame.neg <- data.table(rbind(as.data.frame(gp.dat.neg[["shrink"]][,,1]),
-                          as.data.frame(gp.dat.neg[["shrink"]][,,2])),
-                q=rep(dimnames(gp.dat.neg[["shrink"]])[[3]], each=nrow(gp.dat.neg[["shrink"]][,,1])),
-                last.iter=rep(gp.dat.neg[["last.iter"]], length(gp.dat.neg)))
-
-gelman.neg<-ggplot(melt(gp.dat.frame.neg, c("q","last.iter"), value.name="shrink_factor"),
-       aes(last.iter, shrink_factor, colour=q, linetype=q)) +
-  geom_hline(yintercept=1, colour="grey30", lwd=0.2) +
-  geom_line() +
-  facet_grid(rows = vars(variable), labeller= labeller(function(var,value){
-  return(parlab[value])})) +
-  labs(x="Last Iteration in Chain", y="Shrink Factor",
-       colour="Quantile", linetype="Quantile") +
-  scale_linetype_manual(values=c(2,1))+
-  theme_classic()+
-  theme(legend.position = 'top')
-
-ggarrange(traces.neg,gelman.neg)
-```

### 2022-03-08 manuscript_PLOS/manuscript_PLOS.Rmd
Updated manuscript tp the PLOS Comp. Biol. Updated figures with new figures.

--- 2022-03-08 manuscript_1.0/manuscript_word.Rmd
@@
 author:
-- Andrés E. Quiñones^[Institute of Biology, University of Neuchâtel, Neuchâtel, Switzerland
-  - andresqp@gmail.com]
-date: "`r format(Sys.time(), '%B %d, %Y')`"
-output:
-  word_document: default
-fig_caption: yes
-fontsize: 12pt
-header-includes:
-- \usepackage{float}
-- \usepackage{setspace}\doublespacing
-- \linespread{2}
-- \usepackage{lineno}
-- \linenumbers
-- \newcommand{\beginsupplement}{ \setcounter{table}{0} \renewcommand{\thetable}{S\arabic{table}}
-  \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}}
-keep_tex: yes
-linespread: 2
-bibliography: Cleanerlearning.bib
-style: M:\Zotero\styles\behavioral-ecology-and-sociobiology.csl
-spacing: double
+  - name: Andrés E. Quiñones 
+    email: andresqp@gmail.com
+    affiliation: Institute of Biology, University of Neuchatel
+    corresponding: andresqp@gmail.com
+  - name: Zegni Triki
+    email: zegni.triki@gmail.com
+    affiliation: Department of Zoology, Stockholm University
+  - name: Redouan Bshary
+    email: redouan.bshary@unine.ch
+    affiliation: Institute of Biology, University of Neuchatel
+address:
+  - code: Institute of Biology, University of Neuchatel
+    address: Institute of Biology, Rue Emile-Argand 11, 2000-CH Neuchatel, Switzerland
+  - code: Department of Zoology, Stockholm University
+    address: Department of Zoology, Svante Arrheniusväg 18 B,  106 91 Stockholm, Sweden,
 abstract: |
@@
 We argue that the combination of computational models with data is a powerful tool to infer the mechanistic underpinnings of cognitive performance.
+
 author_summary: |
@@
 Estimating long term value is a mechanism involved in human foresight.
-keywords: learning, behaviour, cleaners, bayesian statisitics
+
+bibliography: Cleanerlearning.bib
+header-includes: |
+  ```{=latex}
+  \usepackage{float}
+  \usepackage{booktabs}
+  \newcommand{\beginsupplement}{ \setcounter{table}{0}     \renewcommand{\thetable}{S\arabic{table}}\setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}}
+  ```
+output: rticles::plos_article
+# plos.csl can be download and used locally
+csl: http://www.zotero.org/styles/plos
 ---
+
+_Text based on plos sample manuscript, see <https://journals.plos.org/ploscompbiol/s/latex>_
 
@@
 ```
+
+# References {#references .unnumbered}

### 2022-03-08 manuscript_PLOS/manuscript_PLOS.tex
Updated manuscript tp the PLOS Comp. Biol. Updated figures with new figures.

--- 2022-03-08 manuscript_1.0/manuscript_1.0.tex
@@
-%% Author_tex.tex
-%% V1.0
-%% 2012/13/12
-%% developed by Techset
-%%
-%% This file describes the coding for rsproca.cls
-
-\documentclass[]{rsos}%%%%where rsos is the template name
-
-\usepackage{lineno}
-\linenumbers
-
-\usepackage[T1]{fontenc}
-\usepackage[utf8]{inputenc}
+% Template for PLoS
+% Version 3.5 March 2018
+%
+% % % % % % % % % % % % % % % % % % % % % %
+%
+% -- IMPORTANT NOTE
+%
+% This template contains comments intended
+% to minimize problems and delays during our production
+% process. Please follow the template instructions
+% whenever possible.
+%
+% % % % % % % % % % % % % % % % % % % % % % %
+%
+% Once your paper is accepted for publication,
+% PLEASE REMOVE ALL TRACKED CHANGES in this file
+% and leave only the final text of your manuscript.
+% PLOS recommends the use of latexdiff to track changes during review, as this will help to maintain a clean tex file.
+% Visit https://www.ctan.org/pkg/latexdiff?lang=en for info or contact us at latex@plos.org.
+%
+%
+% There are no restrictions on package use within the LaTeX files except that
+% no packages listed in the template may be deleted.
+%
+% Please do not include colors or graphics in the text.
+%
+% The manuscript LaTeX source should be contained within a single file (do not use \input, \externaldocument, or similar commands).
+%
+% % % % % % % % % % % % % % % % % % % % % % %
+%
+% -- FIGURES AND TABLES
+%
+% Please include tables/figure captions directly after the paragraph where they are first cited in the text.
+%
+% DO NOT INCLUDE GRAPHICS IN YOUR MANUSCRIPT
+% - Figures should be uploaded separately from your manuscript file.
+% - Figures generated using LaTeX should be extracted and removed from the PDF before submission.
+% - Figures containing multiple panels/subfigures must be combined into one image file before submission.
+% For figure citations, please use "Fig" instead of "Figure".
+% See http://journals.plos.org/plosone/s/figures for PLOS figure guidelines.
+%
+% Tables should be cell-based and may not contain:
+% - spacing/line breaks within cells to alter layout or alignment
+% - do not nest tabular environments (no tabular environments within tabular environments)
+% - no graphics or colored text (cell background color/shading OK)
+% See http://journals.plos.org/plosone/s/tables for table guidelines.
+%
+% For tables that exceed the width of the text column, use the adjustwidth environment as illustrated in the example table in text below.
+%
+% % % % % % % % % % % % % % % % % % % % % % % %
+%
+% -- EQUATIONS, MATH SYMBOLS, SUBSCRIPTS, AND SUPERSCRIPTS
+%
+% IMPORTANT
+% Below are a few tips to help format your equations and other special characters according to our specifications.
+For more tips to help reduce the possibility of formatting errors during conversion, please see our LaTeX guidelines at http://journals.plos.org/plosone/s/latex
+%
+% For inline equations, please be sure to include all portions of an equation in the math environment.
+%
+% Do not include text that is not math in the math environment.
+%
+% Please add line breaks to long display equations when possible in order to fit size of the column.
+%
+% For inline equations, please do not include punctuation (commas, etc) within the math environment unless this is part of the equation.
+%
+% When adding superscript or subscripts outside of brackets/braces, please group using {}.
+%
+% Do not use \cal for caligraphic font.  Instead, use \mathcal{}
+%
+% % % % % % % % % % % % % % % % % % % % % % % %
+%
+% Please contact latex@plos.org with any questions.
+%
+% % % % % % % % % % % % % % % % % % % % % % % %
+
+\documentclass[10pt,letterpaper]{article}
+\usepackage[top=0.85in,left=2.75in,footskip=0.75in]{geometry}
+
+% amsmath and amssymb packages, useful for mathematical formulas and symbols
+\usepackage{amsmath,amssymb}
+
+% Use adjustwidth environment to exceed column width (see example table in text)
+\usepackage{changepage}
+
+% Use Unicode characters when possible
+\usepackage[utf8x]{inputenc}
+
+% textcomp package and marvosym package for additional characters
+\usepackage{textcomp,marvosym}
+
+% cite package, to clean up citations in the main text. Do not remove.
+% \usepackage{cite}
+
+% Use nameref to cite supporting information files (see Supporting Information section for more info)
+\usepackage{nameref,hyperref}
+
+% line numbers
+\usepackage[right]{lineno}
+
+% ligatures disabled
+\usepackage{microtype}
+\DisableLigatures[f]{encoding = *, family = * }
+
+% color can be used to apply background shading to table cells only
+\usepackage[table]{xcolor}
+
+% array package and thick rules for tables
+\usepackage{array}
+
+% create "+" rule type for thick vertical lines
+\newcolumntype{+}{!{\vrule width 2pt}}
+
+% create \thickcline for thick horizontal lines of variable length
+\newlength\savedwidth
+\newcommand\thickcline[1]{%
+  \noalign{\global\savedwidth\arrayrulewidth\global\arrayrulewidth 2pt}%
+  \cline{#1}%
+  \noalign{\vskip\arrayrulewidth}%
+  \noalign{\global\arrayrulewidth\savedwidth}%
+}
+
+% \thickhline command for thick horizontal lines that span the table
+\newcommand\thickhline{\noalign{\global\savedwidth\arrayrulewidth\global\arrayrulewidth 2pt}%
+\hline
+\noalign{\global\arrayrulewidth\savedwidth}}
+
+% Remove comment for double spacing
+%\usepackage{setspace}
+%\doublespacing
+
+% Text layout
+\raggedright
+\setlength{\parindent}{0.5cm}
+\textwidth 5.25in
+\textheight 8.75in
+
+% Bold the 'Figure #' in the caption and separate it from the title/caption with a period
+% Captions will be left justified
+\usepackage[aboveskip=1pt,labelfont=bf,labelsep=period,justification=raggedright,singlelinecheck=off]{caption}
+\renewcommand{\figurename}{Fig}
+
+% Use the PLoS provided BiBTeX style
+% \bibliographystyle{plos2015}
+
+% Remove brackets from numbering in List of References
+\makeatletter
+\renewcommand{\@biblabel}[1]{\quad#1.}
+\makeatother
+
+% Header and Footer with logo
+\usepackage{lastpage,fancyhdr,graphicx}
+\usepackage{epstopdf}
+%\pagestyle{myheadings}
+\pagestyle{fancy}
+\fancyhf{}
+%\setlength{\headheight}{27.023pt}
+%\lhead{\includegraphics[width=2.0in]{PLOS-submission.eps}}
+\rfoot{\thepage/\pageref{LastPage}}
+\renewcommand{\headrulewidth}{0pt}
+\renewcommand{\footrule}{\hrule height 2pt \vspace{2mm}}
+\fancyheadoffset[L]{2.25in}
+\fancyfootoffset[L]{2.25in}
+\lfoot{\today}
+
+%% Include all macros below
+
+\newcommand{\lorem}{{\bf LOREM}}
+\newcommand{\ipsum}{{\bf IPSUM}}
 
@@
 
+% Pandoc citation processing
+\newlength{\cslhangindent}
+\setlength{\cslhangindent}{1.5em}
+\newlength{\csllabelwidth}
+\setlength{\csllabelwidth}{3em}
+\newlength{\cslentryspacingunit} % times entry-spacing
+\setlength{\cslentryspacingunit}{\parskip}
+% for Pandoc 2.8 to 2.10.1
+\newenvironment{cslreferences}%
+  {}%
+  {\par}
+% For Pandoc 2.11+
+\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
+ {% don't indent paragraphs
+  \setlength{\parindent}{0pt}
+  % turn on hanging indent if param 1 is 1
+  \ifodd #1
+  \let\oldpar\par
+  \def\par{\hangindent=\cslhangindent\oldpar}
+  \fi
+  % set entry spacing
+  \setlength{\parskip}{#2\cslentryspacingunit}
+ }%
+ {}
+\usepackage{calc}
+\newcommand{\CSLBlock}[1]{#1\hfill\break}
+\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
+\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
+\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
+
 \usepackage{float}
@@
 
-%%%% *** Do not adjust lengths that control margins, column widths, etc. ***
-
-%%%%%%%%%%% Defining Enunciations  %%%%%%%%%%%
-\newtheorem{theorem}{\bf Theorem}[section]
-\newtheorem{condition}{\bf Condition}[section]
-\newtheorem{corollary}{\bf Corollary}[section]
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\usepackage{forarray}
+\usepackage{xstring}
+\newcommand{\getIndex}[2]{
+  \ForEach{,}{\IfEq{#1}{\thislevelitem}{\number\thislevelcount\ExitForEach}{}}{#2}
+}
+
+\setcounter{secnumdepth}{0}
+
+\newcommand{\getAff}[1]{
+  \getIndex{#1}{Institute of Biology, University of Neuchatel,Department
+of Zoology, Stockholm University}
+}
 
 \begin{document}
-
-%%%% Article title to be placed here
-\title{Field and experimental data together with computational models reveal how cleaner fish adjust decisions in a biological market}
-
-\author{
-Andrés E. Quiñones$^{1}$,
-Zegni Triki$^{2}$,
-Redouan Bshary$^{1}$}
-
-\address{
-  $^{1}$Institute of Biology, University of Neuchâtel, Neuchâtel, Switzerland\\
-  $^{2}$Department of Zoology, Stockholm University, Stockholm, Sweden}
-%%%% Subject entries to be placed here %%%%
-\subject{
-Behavioural ecology,
-Cognitive ecology,
-Animal behaviour}
-
-%%%% Keyword entries to be placed here %%%%
-\keywords{
-learning,
-cleaners,
-behaviour,
-bayesian statisitics,
-mutualism}
-
-%%%% Insert corresponding author and its email address}
-\corres{
-  AE. Quiñones\\
-  e-mail: \href{mailto:andreseqp@gmail.com}{\nolinkurl{andreseqp@gmail.com}}
+\vspace*{0.2in}
+
+% Title must be 250 characters or less.
+\begin{flushleft}
+{\Large
+\textbf\newline{Field and experimental data together with computational
+models reveal how cleaner fish adjust decisions in a biological
+market} % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
 }
-
-%%%% Abstract text to be placed here %%%%%%%%%%%%
-\begin{abstract}
-While it is generally straightforward to quantify individual performance in cognitive experiments, identifying the underlying cognitive processes remains a major challenge.
-Often, different mechanistic underpinnings yield similar performances, and Lloyd Morgan's cannon warrants acceptance of the simpler explanation.
-Alternatively, when the different mechanisms interact with environmental conditions, variation in performance across environments might allow to statistically infer the mechanism responsible.
-We illustrate this point by fitting computational models to experimental data on performance by wild-caught cleaner fish Labroides dimidiatus in an ephemeral reward task, as well as cleaner and client fish densities from the locations of capture.
-Using Bayesian statistics to fit the model parameters to performance data revealed that cleaner fish most likely estimate future consequences of an action, while it appears unlikely that the removal of the ephemeral reward acts as psychological punishment (negative reinforcement).
-Incorporating future consequences also yields performances that can be considered the result of locally optimal decision-rules, in contrast to the negative reinforcement mechanism.
-We argue that the combination of computational models with data is a powerful tool to infer the mechanistic underpinnings of cognitive performance.
-\end{abstract}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\providecommand{\EndFirstPage}{%
-}
-
-\maketitle
+\newline
+% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
+\\
+Andrés E. Quiñones\textsuperscript{\getAff{Institute of Biology,
+University of Neuchatel}}\textsuperscript{*},
+Zegni Triki\textsuperscript{\getAff{Department of Zoology, Stockholm
+University}},
+Redouan Bshary\textsuperscript{\getAff{Institute of Biology, University
+of Neuchatel}}\\
+\bigskip
+\textbf{\getAff{Institute of Biology, University of Neuchatel}}Institute
+of Biology, Rue Emile-Argand 11, 2000-CH Neuchatel, Switzerland\\
+\textbf{\getAff{Department of Zoology, Stockholm University}}Department
+of Zoology, Svante Arrheniusväg 18 B, 106 91 Stockholm, Sweden,\\
+\bigskip
+* Corresponding author: andresqp@gmail.com\\
+\end{flushleft}
+% Please keep the abstract below 300 words
+\section*{Abstract}
+While it is generally straightforward to quantify individual performance
+in cognitive experiments, identifying the underlying cognitive processes
+remains a major challenge. Often, different mechanistic underpinnings
+yield similar performances, and Lloyd Morgan's cannon warrants
+acceptance of the simpler explanation. Alternatively, when the different
+mechanisms interact with environmental conditions, variation in
+performance across environments might allow to statistically infer the
+mechanism responsible. We illustrate this point by fitting computational
+models to experimental data on performance by wild-caught cleaner fish
+\emph{Labroides dimidiatus} in an ephemeral reward task, as well as
+cleaner and client fish densities from the locations of capture. Using
+Bayesian statistics to fit the model parameters to performance data
+revealed that cleaner fish most likely estimate future consequences of
+an action, while it appears unlikely that the removal of the ephemeral
+reward acts as psychological punishment (negative reinforcement).
+Incorporating future consequences also yields performances that can be
+considered the result of locally optimal decision-rules, in contrast to
+the negative reinforcement mechanism. We argue that the combination of
+computational models with data is a powerful tool to infer the
+mechanistic underpinnings of cognitive performance.
+
+% Please keep the Author Summary between 150 and 200 words
+% Use first person. PLOS ONE authors please skip this step.
+% Author Summary not valid for PLOS ONE submissions.
+\section*{Author summary}
+Performance in behavioural experiments is often used to assess the
+cognitive abilities of animals. However, animals can get to the same
+outcome in alternative ways. Thus, the outcome of the experiments does
+not tell us how animals achieve their performance. In order to overcome
+this limitation, we used a set of computational models, which provide
+predictions on how alternative cognitive mechanisms perform in the face
+of varying environmental conditions, and compare their predictions to
+performance data from individuals that experienced different conditions
+throughout their life. Our study system is the cleaner fish
+\emph{Labroides dimidiatus}, a coral reef fish that feeds off
+ectoparasites and dead tissue from the skin of other reef fishes.
+Cleaner fish often have to choose among alternative clients seeking
+their cleaning service, and the optimal choice is often hard to achieve.
+Our performance experiments mimic the natural choices the cleaner fish
+make. The combination of experiments and computational models points to
+cleaner fish abilities to account for the future effect of their choices
+by estimating the long term expected value of those choices. Estimating
+long term value is a mechanism involved in human foresight.
+
+\linenumbers
+
+% Use "Eq" instead of "Equation" for equation citations.
+\emph{Text based on plos sample manuscript, see
+\url{https://journals.plos.org/ploscompbiol/s/latex}}
 
@@
 
-Often alternative cognitive mechanisms yield similar behaviour and/or cognitive
-performances. This poses a problem for disentangling the mechanistic
-underpinnings of behaviour. This is particularly clear in research aimed at
-discovering between species variation in \emph{higher} cognitive abilities; or
-in other words, research on whether non-human animals show cognitive
-abilities believed to be uniquely human. For instance, when researchers
-try to find \emph{mental time travel-like} behaviour, they usually come up with
-clever experiments to show the behaviour displayed requires inferences made
-through past events\citep{dally_Foodcaching_2006}. However, they often face the
-challenge of alternative scenarios where simpler explanations,
-like classic associative learning, can bring about the
-observed behavioural outcome \citep{suddendorf_Evolution_2007}. Similarly, attempts
-to demonstrate the presence of \emph{theory of mind} in non-human animals
-face objections justified by alternative mechanisms underpinning
-similar behavioural results \citep{heyes_Theory_1998}.
-Such controversies are usually settled by using the principle
-of parsimony and its cognitive version,
-Lloyd Morgan's cannon, which states that the simpler explanation (mechanism)
-should be accepted. Ideally, however, alternative hypotheses should be evaluated
-in light of their explanatory power. One potential dimension that could allow
-the variation necessary among distinct cognitive mechanisms is environmental
-variation. Controlled laboratory conditions often mask between and within
-species variation that arises among different environments. Thus, if
-predictions from the alternative mechanisms depend on environmental
-conditions, it is possible to assess their relative explanatory power
-by performing cognitive test in the context of
-different environmental conditions.
+Often alternative cognitive mechanisms yield similar behaviour and/or
+cognitive performances. This poses a problem for disentangling the
+mechanistic underpinnings of behaviour. This is particularly clear in
+research aimed at discovering between species variation in \emph{higher}
+cognitive abilities; or in other words, research on whether non-human
+animals show cognitive abilities believed to be uniquely human. For
+instance, when researchers try to find \emph{mental time travel-like}
+behaviour, they usually come up with clever experiments to show the
+behaviour displayed requires inferences made through past events{[}1{]}.
+However, they often face the challenge of alternative scenarios where
+simpler explanations, like classic associative learning, can bring about
+the observed behavioural outcome {[}2{]}. Similarly, attempts to
+demonstrate the presence of \emph{theory of mind} in non-human animals
+face objections justified by alternative mechanisms underpinning similar
+behavioural results {[}3{]}. Such controversies are usually settled by
+using the principle of parsimony and its cognitive version, Lloyd
+Morgan's cannon, which states that the simpler explanation (mechanism)
+should be accepted. Ideally, however, alternative hypotheses should be
+evaluated in light of their explanatory power. One potential dimension
+that could allow the variation necessary among distinct cognitive
+mechanisms is environmental variation. Controlled laboratory conditions
+often mask between and within species variation that arises among
+different environments. Thus, if predictions from the alternative
+mechanisms depend on environmental conditions, it is possible to assess
+their relative explanatory power by performing cognitive test in the
+context of different environmental conditions.
 
 From an evolutionary perspective, mechanisms are likely selected because
-of how they allow individuals to respond to environmental variation.
-For example, biological market theory predicts that the exchange rate of goods
-and/or services traded between cooperative partners adjusts to the
-law of supply and demand, when individuals have some degree of partner choice
-\citep{noe_Biological_1995}. Supply and demand conditions, which typically
-depend on the abundance of the species involved, certainly vary in time
-and space. Therefore, natural selection should favour the ability
-to flexibly adjust decisions and behavioural output to
-current market conditions. Indeed, such adjustments have been repeatedly
-documented \citep{axen_Signalling_1996}. In animals, an obvious general candidate
-mechanism for the strategic adjustment is the cognitive machinery. However,
-it is not clear which cognitive mechanisms allow individuals to adjust their
-behaviour to the varying conditions. More specifically the question arises
-to what extent mechanisms beyond basic associative learning may be involved.
+of how they allow individuals to respond to environmental variation. For
+example, biological market theory predicts that the exchange rate of
+goods and/or services traded between cooperative partners adjusts to the
+law of supply and demand, when individuals have some degree of partner
+choice {[}4{]}. Supply and demand conditions, which typically depend on
+the abundance of the species involved, certainly vary in time and space.
+Therefore, natural selection should favour the ability to flexibly
+adjust decisions and behavioural output to current market conditions.
+Indeed, such adjustments have been repeatedly documented {[}5{]}. In
+animals, an obvious general candidate mechanism for the strategic
+adjustment is the cognitive machinery. However, it is not clear which
+cognitive mechanisms allow individuals to adjust their behaviour to the
+varying conditions. More specifically the question arises to what extent
+mechanisms beyond basic associative learning may be involved.
 
 One example of strategic adjustment in a biological market is the marine
-cleaning mutualism involving the cleaner fish \emph{Labroides dimidiatus} and
-`client' fish. Client fish seek cleaner fish services at their territory
-(so-called ``cleaning station'') and offer themselves as food patches
-to get their ectoparasites removed, which provides cleaners
-with food and clients with improved health \citep{waldie_LongTerm_2011, ros_Does_2011, triki_Effects_2016, demaire_Reduced_2020}.
-Given the capacity of some client fish to swim larger distances and
-access multiple cleaning stations while others access the only cleaning
-station in their territory, it is crucial to categorize clients as
-either ``visitors'' or ``residents'', respectively. During cleaning interactions,
-a cleaner fish often face a choice between a visitor and a resident client
-seeking its cleaning services simultaneously. Visitors have the option
-to switch to another cleaner fish if being made to wait, while residents
-must wait for inspection. Indeed,
-visitors have been observed to use their partner choice option in that
-way \citep{bshary_Choosy_2002}, which may explain why cleaners give
-visitors service priority in a field study in the Red Sea
-\citep{bshary_Cleaner_2001}.
-
-When researchers aimed at testing wild-caught cleaner fish, as
-well as individuals from other species, abilities
-to prioritize visitor over resident clients in a lab-based paradigm,
-they used Plexiglas plates of different colours and shapes offering the same
-amount of food as surrogates for visitor and resident clients.
-One plate is made to behave like a resident, i.e.~it remains until
-the cleaner fish has eaten off it. The other plate was made to behave
-like a visitor, i.e.~it is removed if not inspected first.
-This laboratory paradigm originally inspired by the cleaning market
-of cleaner fish is more generally referred as the ephemeral reward task.
-Individuals are assessed in their capacity to develop a preference for the
-ephemeral option, which gives them access to two reward units.
-Cleaners learned to prefer the visitor plate and
-hence obtained the double amount of food \citep{bshary_Asymmetric_2002}.
-Furthermore, adult cleaner fish outperformed various primates as well as rats and
-pigeons in this original version of the ephemeral reward task
-\citep{salwiczek_Adult_2012, zentall_Early_2017}; yet the African grey
-parrots solve this task as well \citep{pepperberg_Can_2014}.
-This between variation in performance, and primates' known cognitive abilities
-\(\color{red}{\text{ref}}\), shows that performance in the task
-cannot be readily explained by classifying species as having high and
-low cognitive abilities. Instead, this between species variation suggests
-that solving the ephemeral reward task requires a set of cognitive
-mechanisms that are not present in all the tested taxa, or were not used
-under the experimental set-up.
+cleaning mutualism involving the cleaner fish \emph{Labroides
+dimidiatus} and `client' fish. Client fish seek cleaner fish services at
+their territory (so-called ``cleaning station'') and offer themselves as
+food patches to get their ectoparasites removed, which provides cleaners
+with food and clients with improved health {[}6--9{]}. Given the
+capacity of some client fish to swim larger distances and access
+multiple cleaning stations while others access the only cleaning station
+in their territory, it is crucial to categorize clients as either
+``visitors'' or ``residents,'' respectively. During cleaning
+interactions, a cleaner fish often face a choice between a visitor and a
+resident client seeking its cleaning services simultaneously. Visitors
+have the option to switch to another cleaner fish if being made to wait,
+while residents must wait for inspection. Indeed, visitors have been
+observed to use their partner choice option in that way {[}10{]}, which
+may explain why cleaners give visitors service priority in a field study
+in the Red Sea {[}11{]}.
+
+When researchers aimed at testing wild-caught cleaner fish, as well as
+individuals from other species, abilities to prioritize visitor over
+resident clients in a lab-based paradigm, they used Plexiglas plates of
+different colours and shapes offering the same amount of food as
+surrogates for visitor and resident clients. One plate is made to behave
+like a resident, i.e.~it remains until the cleaner fish has eaten off
+it. The other plate was made to behave like a visitor, i.e.~it is
+removed if not inspected first. This laboratory paradigm originally
+inspired by the cleaning market of cleaner fish is more generally
+referred as the ephemeral reward task. Individuals are assessed in their
+capacity to develop a preference for the ephemeral option, which gives
+them access to two reward units. Cleaners learned to prefer the visitor
+plate and hence obtained the double amount of food {[}12{]}.
+Furthermore, adult cleaner fish outperformed various primates as well as
+rats and pigeons in this original version of the ephemeral reward task
+{[}13,14{]}; yet the African grey parrots solve this task as well
+{[}15{]}. This between variation in performance, and primates' known
+cognitive abilities \(\color{red}{\text{ref}}\), shows that performance
+in the task cannot be readily explained by classifying species as having
+high and low cognitive abilities. Instead, this between species
+variation suggests that solving the ephemeral reward task requires a set
+of cognitive mechanisms that are not present in all the tested taxa, or
+were not used under the experimental set-up.
 
@@
 reward task has used a broad approach as proposed by Shettleworth
-\citep{shettleworth_Cognition_2009}, who defined cognition as including
-all ways in which animals acquire information
-through the senses, process, retain and decide to act on it.
-Indeed, perception of relevant cues is of major importance
+{[}16{]}, who defined cognition as including all ways in which animals
+acquire information through the senses, process, retain and decide to
+act on it. Indeed, perception of relevant cues is of major importance
 for individual performance. For example, some animals find relevant
-information in the plates \citep{wismer_Cuebased_2019} while others find
-it in the food \citep{pretot_Comparative_2021, pretot_Comparing_2016}.
-However, identifying cues as salient is not the only challenge
-of the ephemeral reward task, as revealed by proximate learning models.
-Such models allow varying the cognitive tool kit and evaluating
-which minimal kit is necessary to solve
-the task at hand (e.g. \citep{dubois_Model_2021}). Applied to the ephemeral
-reward task, learning models showed that basic reinforcement learning does
-not suffice to solve the ephemeral reward task \citep{prat_Modelling_2022, quinones_Reinforcement_2019}.
-This is particularly so when models assume the more complex natural
-situation in which cleaner fish face not only resident-visitor pairs but also
-visitor-visitor and resident-resident pairs, as well a resident alone or
-a visitor alone. To be able to give visitors priority over residents,
-cleaners need to be able to assess a client's value separately for the
-three possible scenarios (alone, paired with a fish with the
-same strategic option, paired with a fish with the alternative strategic option)
-\citep{quinones_Reinforcement_2019}. The ability to distinguish and value
-one stimulus differently alone from compound versions of it has been termed
-configurational learning, chunking,
-or segmentation (see references in \citep{prat_Modelling_2022}).
-
-In addition to configurational learning, cleaners also need to account for
-the future consequences of current decisions. In the model by
-Quiñones \emph{et al.} \citep{quinones_Reinforcement_2019}, this could be achieved in
-two non-mutually exclusive ways: through low temporal discounting of
-future effects, also termed `chaining' \citep{enquist_Power_2016}; and/or
-through perceiving a visitor client leaving as psychological punishment
-(i.e.~as a negative reinforcer). Low temporal discounting is when
-individuals include in their valuation of an action the reward effects
-that this will have in the future. This is done by combining in a single
-valuation the reward obtained in the current time with all the reward that
-comes after, discounting for how far in the future reward
-is accrued. `Chaining' the reward of these different time steps allows
-individuals to take actions that increase the long-term reward at the sacrifice
-of short term considerations \citep{enquist_Power_2016}. Even though, `chaining'
-can be readily implemented computationally in learning models
-\citep{enquist_Power_2016, sutton_Reinforcement_2018}, cognitively it seems to be
-a complex adaptation \citep{suddendorf_Evolution_2007}. On the other hand,
-using client behaviour as a negative reinforcer is, in principle,
-easier to implement. Negative reinforcement is part of the ubiquitous
-learning mechanism termed operant conditioning \citep{thorndike_Animal_1898, skinner_Behavior_1938}. Thus, the standard logic of
-Lloyd Morgan's cannon demands that operant conditioning as the simpler
-explanation is to be accepted by default. Ideally, however, the two
-mechanisms should be evaluated in light of how well
-they explain the available data. Note that different fields interested in
-cognition and decision making use different words to refer to negative
-reinforcers \citep{quinones_Reinforcement_2019, sutton_Reinforcement_2018}.
-Here, for the sake of simplicity and clarity, we will use the word
-`penalty' to refer to this mechanism which includes a negative reinforcer.
-
-Over the last decade, our team tested over a hundred wild-caught
-cleaner fish in the exact same paradigm of the ephemeral reward
-task \citep{salwiczek_Adult_2012, wismer_Variation_2014, triki_Decrease_2018, triki_Biological_2019, triki_Brain_2020}. These fish often come from
-different reef locations around the study field site at Lizard Island,
-Great Barrier Reef in Australia. Further investigation of the local
-eco-sociological conditions revealed that cleaner and client
-fish population densities have a substantial impact on cleaner fish
-performance in the task. Cleaner fish from reef sites with relatively
-low densities were more likely to fail at solving the task \citep{triki_Biological_2019, triki_Decrease_2018, wismer_Variation_2014}. The explanation for this pattern
-is twofold. First, low cleaner fish population densities imply
-low supply and high demand for cleaning services.
-Under such conditions, there are fewer occasions under
-which failing to give priority to a visitor translates to an empty
-cleaning station. Second and also related to the state of the cleaning market,
-visitor clients at low cleaner fish population densities
-are less likely to exert their partner choice options
-and are hence more likely to wait for inspection if not given cleaning
-priority \citep{triki_Brain_2020}. In the absence of partner choice
-cleaner fish should not give priority to visitors any more.
-
-The interplay between the underlying cognitive machinery and
-local ecological conditions apparently generate the documented variable
-performance among individuals of the same species.
-Our approach of fitting the computational model to the empirical data on
-fish densities and cleaner fish censuses and performance
-in the ephemeral reward task aimed at: (i), determining which
-mechanism cleaner fish use to incorporate future consequences of current
-decisions by testing whether chaining, penalty, or a combination
-of both best explains their performance; (ii) determining whether the
-two mechanisms differed with respect to the ecological conditions
-that are likely to cause high versus low performance in the
-ephemeral reward task. Additionally, we assessed which mechanism
-yields optimal performance patterns. Relying on the logic of
-biological market theory, we predicted
-that appropriate performance is to show a low preference for visitors under low
-local cleaner-to-client ratio.
+information in the plates {[}17{]} while others find it in the food
+{[}18,19{]}. However, identifying cues as salient is not the only
+challenge of the ephemeral reward task, as revealed by proximate
+learning models. Such models allow varying the cognitive tool kit and
+evaluating which minimal kit is necessary to solve the task at hand
+(e.g. {[}20{]}). Applied to the ephemeral reward task, learning models
+showed that basic reinforcement learning does not suffice to solve the
+ephemeral reward task {[}21,22{]}. This is particularly so when models
+assume the more complex natural situation in which cleaner fish face not
+only resident-visitor pairs but also visitor-visitor and
+resident-resident pairs, as well a resident alone or a visitor alone. To
+be able to give visitors priority over residents, cleaners need to be
+able to assess a client's value separately for the three possible
+scenarios (alone, paired with a fish with the same strategic option,
+paired with a fish with the alternative strategic option) {[}22{]}. The
+ability to distinguish and value one stimulus differently alone from
+compound versions of it has been termed configurational learning,
+chunking, or segmentation (see references in {[}21{]}).
+
+In addition to configurational learning, cleaners also need to account
+for the future consequences of current decisions. In the model by
+Quiñones \emph{et al.} {[}22{]}, this could be achieved in two
+non-mutually exclusive ways: through low temporal discounting of future
+effects, also termed `chaining' {[}23{]}; and/or through perceiving a
+visitor client leaving as psychological punishment (i.e.~as a negative
+reinforcer). Low temporal discounting is when individuals include in
+their valuation of an action the reward effects that this will have in
+the future. This is done by combining in a single valuation the reward
+obtained in the current time with all the reward that comes after,
+discounting for how far in the future reward is accrued. `Chaining' the
+reward of these different time steps allows individuals to take actions
+that increase the long-term reward at the sacrifice of short term
+considerations {[}23{]}. Even though, `chaining' can be readily
+implemented computationally in learning models {[}23,24{]}, cognitively
+it seems to be a complex adaptation {[}2{]}. On the other hand, using
+client behaviour as a negative reinforcer is, in principle, easier to
+implement. Negative reinforcement is part of the ubiquitous learning
+mechanism termed operant conditioning {[}25,26{]}. Thus, the standard
+logic of Lloyd Morgan's cannon demands that operant conditioning as the
+simpler explanation is to be accepted by default. Ideally, however, the
+two mechanisms should be evaluated in light of how well they explain the
+available data. Note that different fields interested in cognition and
+decision making use different words to refer to negative reinforcers
+{[}22,24{]}. Here, for the sake of simplicity and clarity, we will use
+the word `penalty' to refer to this mechanism which includes a negative
+reinforcer.
+
+Over the last decade, our team tested over a hundred wild-caught cleaner
+fish in the exact same paradigm of the ephemeral reward task
+{[}13,27--30{]}. These fish often come from different reef locations
+around the study field site at Lizard Island, Great Barrier Reef in
+Australia. Further investigation of the local eco-sociological
+conditions revealed that cleaner and client fish population densities
+have a substantial impact on cleaner fish performance in the task.
+Cleaner fish from reef sites with relatively low densities were more
+likely to fail at solving the task {[}27--29{]}. The explanation for
+this pattern is twofold. First, low cleaner fish population densities
+imply low supply and high demand for cleaning services. Under such
+conditions, there are fewer occasions under which failing to give
+priority to a visitor translates to an empty cleaning station. Second
+and also related to the state of the cleaning market, visitor clients at
+low cleaner fish population densities are less likely to exert their
+partner choice options and are hence more likely to wait for inspection
+if not given cleaning priority {[}30{]}. In the absence of partner
+choice cleaner fish should not give priority to visitors any more.
+
+The interplay between the underlying cognitive machinery and local
+ecological conditions apparently generate the documented variable
+performance among individuals of the same species. Our approach of
+fitting the computational model to the empirical data on fish densities
+and cleaner fish censuses and performance in the ephemeral reward task
+aimed at: (i), determining which mechanism cleaner fish use to
+incorporate future consequences of current decisions by testing whether
+chaining, penalty, or a combination of both best explains their
+performance; (ii) determining whether the two mechanisms differed with
+respect to the ecological conditions that are likely to cause high
+versus low performance in the ephemeral reward task. Additionally, we
+assessed which mechanism yields optimal performance patterns. Relying on
+the logic of biological market theory, we predicted that appropriate
+performance is to show a low preference for visitors under low local
+cleaner-to-client ratio.
 
@@
 The model consists of a set of individual-based simulations where
-individuals, representing cleaner fish, face a series of choices
-between two options, which simulate the natural conditions
-of the cleaning market. Individuals experience a series
-of discrete time points in which they face different `states',
-defined by the number and category of client fish (visitor or residents)
-inviting for cleaning services. There are six possible states:
-zero clients, one resident, one visitor,
-resident-resident, visitor-visitor, and resident-visitor.
-The probability of each state is largely determined by the relative
+individuals, representing cleaner fish, face a series of choices between
+two options, which simulate the natural conditions of the cleaning
+market. Individuals experience a series of discrete time points in which
+they face different `states,' defined by the number and category of
+client fish (visitor or residents) inviting for cleaning services. There
+are six possible states: zero clients, one resident, one visitor,
+resident-resident, visitor-visitor, and resident-visitor. The
+probability of each state is largely determined by the relative
 abundance of cleaner fish, residents and visitors, but to some degree by
@@
 This is because residents are willing to queue for cleaning service;
-while visitors leave the queue (with a certain probability) when made to wait.
-Individuals obtain a fixed reward from cleaning a client fish
-regardless of the category. Every time individuals face and make a choice
-they update the probability of making that same choice. The update is
-based on the difference between the expected reward and the obtained
-reward (prediction error) \citep{sutton_Reinforcement_2018, rescorla_Theory_1972}. Given the new information, the update is carried
-in the direction that leads to more reward being obtained, given
-the new information. In the long run, the probability of choosing a visitor
-over a resident converges in the model. To which probability the model
-will converge depends on the relative abundance of cleaners, visitors
-and residents; as well as on the probability of visitors leaving the
-cleaning station when made to wait. Further details of the model
-implementation can be found in Quiñones \emph{et al} \citep{quinones_Reinforcement_2019}.
-
-The model shows that agents need to find a way
-to incorporate future consequences of current choices. In the model,
-this could be achieved with either of two parameters that could
-also work together. First, \(\gamma\) measures how
-much individuals include future rewards in their decision updates.
-If \(\gamma=0\), individuals only use the immediate reward obtained from a
-cleaning interaction. As \(\gamma\) increases, individuals include more the
-reward obtained from the subsequent choices. That amounts to calculating
-and using for decision making the future expected rewards of an action (chaining).
-Second, \(\eta\) measures how much individuals include in their reward the
-fleeing behaviour of visitors as a negative component (penalty). Both of
-these parameters allow individuals to use in their estimates the future
+while visitors leave the queue (with a certain probability) when made to
+wait. Individuals obtain a fixed reward from cleaning a client fish
+regardless of the category. Every time individuals face and make a
+choice they update the probability of making that same choice. The
+update is based on the difference between the expected reward and the
+obtained reward (prediction error) {[}24,31{]}. Given the new
+information, the update is carried in the direction that leads to more
+reward being obtained, given the new information. In the long run, the
+probability of choosing a visitor over a resident converges in the
+model. To which probability the model will converge depends on the
+relative abundance of cleaners, visitors and residents; as well as on
+the probability of visitors leaving the cleaning station when made to
+wait. Further details of the model implementation can be found in
+Quiñones \emph{et al} {[}22{]}.
+
+The model shows that agents need to find a way to incorporate future
+consequences of current choices. In the model, this could be achieved
+with either of two parameters that could also work together. First,
+\(\gamma\) measures how much individuals include future rewards in their
+decision updates. If \(\gamma=0\), individuals only use the immediate
+reward obtained from a cleaning interaction. As \(\gamma\) increases,
+individuals include more the reward obtained from the subsequent
+choices. That amounts to calculating and using for decision making the
+future expected rewards of an action (chaining). Second, \(\eta\)
+measures how much individuals include in their reward the fleeing
+behaviour of visitors as a negative component (penalty). Both of these
+parameters allow individuals to use in their estimates the future
 effects of their choices.
@@
 The empirical data were collected between 2010 and 2019 always during
-the austral winter months June to August from a total of five
-study reef sites (Corner Beach-CB, Horseshoe-HS, Mermaid Cove-MC,
-Northern Horseshoe-NHS, and The Crest-TC) at Lizard Island
+the austral winter months June to August from a total of five study reef
+sites (Corner Beach-CB, Horseshoe-HS, Mermaid Cove-MC, Northern
+Horseshoe-NHS, and The Crest-TC) at Lizard Island
 (\(14.6682^\circ S, 145.4604^\circ E\)), Great Barrier Reef, Australia.
-The data consist of three sets: fish censuses, field
-observations of cleaner-client interactions to quantify the probability
-of visitors leaving if made to wait, and the
-performance of wild-caught cleaner fish in the ephemeral reward test.
-In total, we have twelve site/year data sets for fish censuses and
-corresponding performance in the lab test. Thus, some sites were sampled more
-than once. To estimate the population density of cleaner fish
-and their clients at a given site in
-a given year, Triki \emph{et al.} \citep{triki_Biological_2019} used a series of ten
-transects of \(30m\) each. Observers swam along the transect lines placed on
-the reef and first counted the visible large-bodied adult fish
-(species with total length \(TL \geq 10cm\)) including cleaner fish
-on a width of \(5m\), and then on the
-return individuals of small-bodied fish species (\(TL < 10 cm\))\\
-on a width of \(1 m\)
-(see Triki et al.~2018 for further details on fish censuses data collection).
-We then scaled the counts of cleaner fish, small-bodied,
-and large-bodied clients fish densities per \(100 m^2\).
-From the study by Triki \emph{et al} \citep{triki_Biological_2019}
-cleaner fish and large-bodied client populations densities were
-highly correlated, and only the former
-was hence used in the analyses as representative of both measures.
-
-The field observation data consisted of video recordings/encodings of the
-cleaner-client cleaning interactions. There were videos from eight
-cleaners per site/year of a duration of \(30 min\) each. Triki \emph{et al}
-extracted information from every event wherein a visitor client
-was made to wait in favour of another client (visitor or resident), and noted
-whether or not the visitor left or queued for the cleaning service
-\citep{triki_Biological_2019, triki_Brain_2020}.
-
-The cognitive performance data was from a total of 120 cleaners
-(10 individuals per 12 site/year) tested in the
-ephemeral reward task \citep{triki_Biological_2019, triki_Brain_2020}. Authors
-housed all captured cleaners individually in glass aquaria
-( \(62cm \times 27cm \times 37 cm\) ) and provided them
-with PVC pipes (\(10 cm \times 1 cm\)) as shelters.
-The task consisted of exposing the cleaner fish to substitute
-models of client fish in the form of two \emph{Plexiglas} plates offering the
-same amount of food (one item of mashed prawn). The two plates differed
-in colour and pattern (horizontal green stripes or vertical pink stripes)
-but had equal size (\(10 cm \times 7 cm\)). Importantly, the two plates played
-different roles as either a visitor (ephemeral food source) or
-resident (permanent food source). That is, if a cleaner fish inspected the
+The data consist of three sets: fish censuses, field observations of
+cleaner-client interactions to quantify the probability of visitors
+leaving if made to wait, and the performance of wild-caught cleaner fish
+in the ephemeral reward test. In total, we have twelve site/year data
+sets for fish censuses and corresponding performance in the lab test.
+Thus, some sites were sampled more than once. To estimate the population
+density of cleaner fish and their clients at a given site in a given
+year, Triki \emph{et al.} {[}29{]} used a series of ten transects of
+\(30m\) each. Observers swam along the transect lines placed on the reef
+and first counted the visible large-bodied adult fish (species with
+total length \(TL \geq 10cm\)) including cleaner fish on a width of
+\(5m\), and then on the return individuals of small-bodied fish species
+(\(TL < 10 cm\))\\
+on a width of \(1 m\) (see Triki et al.~2018 for further details on fish
+censuses data collection). We then scaled the counts of cleaner fish,
+small-bodied, and large-bodied clients fish densities per \(100 m^2\).
+From the study by Triki \emph{et al} {[}29{]} cleaner fish and
+large-bodied client populations densities were highly correlated, and
+only the former was hence used in the analyses as representative of both
+measures.
+
+The field observation data consisted of video recordings/encodings of
+the cleaner-client cleaning interactions. There were videos from eight
+cleaners per site/year of a duration of \(30 min\) each. Triki \emph{et
+al} extracted information from every event wherein a visitor client was
+made to wait in favour of another client (visitor or resident), and
+noted whether or not the visitor left or queued for the cleaning service
+{[}29,30{]}.
+
+The cognitive performance data was from a total of 120 cleaners (10
+individuals per 12 site/year) tested in the ephemeral reward task
+{[}29,30{]}. Authors housed all captured cleaners individually in glass
+aquaria ( \(62cm \times 27cm \times 37 cm\) ) and provided them with PVC
+pipes (\(10 cm \times 1 cm\)) as shelters. The task consisted of
+exposing the cleaner fish to substitute models of client fish in the
+form of two \emph{Plexiglas} plates offering the same amount of food
+(one item of mashed prawn). The two plates differed in colour and
+pattern (horizontal green stripes or vertical pink stripes) but had
+equal size (\(10 cm \times 7 cm\)). Importantly, the two plates played
+different roles as either a visitor (ephemeral food source) or resident
+(permanent food source). That is, if a cleaner fish inspected the
 resident plate first, the experimenter withdrew the visitor plate out of
@@
 however, granted access to both plates. The equal size of the plates
-forced cleaner fish to learn to give service priority to the visitor plate
-based solely on the behaviour-cue of the plates rather than size-cue
-\citep{wismer_Cuebased_2019}. Triki \emph{et al.} \citep{triki_Biological_2019, triki_Brain_2020}
-tested the fish for a maximum of 200 trials with 20 trials a day, 10 trials
-in the morning and 10 trials in the afternoon. They randomized and
-counterbalanced the plates' spatial location (i.e.~left or right)
-between trials. Similarly, they counterbalanced the plates' decoration
-(colour and pattern) and the plates' role (visitor or resident) between the
-tested fish. In the original studies, once a fish reach a learning criterion,
-that is, performing significantly above chance level (\(> 50%
-\), \(p-value ≥ 0.05\)),
-they passed to a reversal version of the task where the roles of the
-visitor/resident Plexiglas plates were swapped (see Triki et al.~2019, 2020).
-Here, we used instead a subset of these data in order to have an idea of
-cleaner fish preferences for the visitor plate, even if they do not reach
-the learning criterion within 200 trials. To do so, we first extracted the
-trial-by-trial outcomes from the last two sessions (20 trials) of those who
-never reached the learning criterion for visitor plate
-(\(N = 45\) cleaner fish).
-For those who reached the learning criterion at some point during the
-test and passed to a reversal phase, we extracted the trial-by-trial
-outcomes from the last session (10 trials) before passing to reversal
-and the last 10 trials they were exposed to in the test
-(\(N = 75\) cleaner fish).
-We chose a combination of initial and reversal to quantify preference
-for the visitor client, given that it matches well the criteria chosen
-in previous analysis of the ephemeral reward task experimental set-up
-\citep{triki_Biological_2019, triki_Brain_2020}. In the
-supplementary material (Fig. \ref{fig:rawdata}) we show how our choice maps
-to the previously used criteria. For comparison, we also show a quantification
-of visitor preference based only on the initial phase of the task.
+forced cleaner fish to learn to give service priority to the visitor
+plate based solely on the behaviour-cue of the plates rather than
+size-cue {[}17{]}. Triki \emph{et al.} {[}29,30{]} tested the fish for a
+maximum of 200 trials with 20 trials a day, 10 trials in the morning and
+10 trials in the afternoon. They randomized and counterbalanced the
+plates' spatial location (i.e.~left or right) between trials. Similarly,
+they counterbalanced the plates' decoration (colour and pattern) and the
+plates' role (visitor or resident) between the tested fish. In the
+original studies, once a fish reach a learning criterion, that is,
+performing significantly above chance level (\(> 50%
+\), \(p-value ≥ 0.05\)), they passed to a reversal version of the task
+where the roles of the visitor/resident Plexiglas plates were swapped
+(see Triki et al.~2019, 2020). Here, we used instead a subset of these
+data in order to have an idea of cleaner fish preferences for the
+visitor plate, even if they do not reach the learning criterion within
+200 trials. To do so, we first extracted the trial-by-trial outcomes
+from the last two sessions (20 trials) of those who never reached the
+learning criterion for visitor plate (\(N = 45\) cleaner fish). For
+those who reached the learning criterion at some point during the test
+and passed to a reversal phase, we extracted the trial-by-trial outcomes
+from the last session (10 trials) before passing to reversal and the
+last 10 trials they were exposed to in the test (\(N = 75\) cleaner
+fish). We chose a combination of initial and reversal to quantify
+preference for the visitor client, given that it matches well the
+criteria chosen in previous analysis of the ephemeral reward task
+experimental set-up {[}29,30{]}. In the supplementary material (Fig.
+\ref{fig:rawdata}) we show how our choice maps to the previously used
+criteria. For comparison, we also show a quantification of visitor
+preference based only on the initial phase of the task.
 
@@
 
-The aim of the analyses is to fit the key model parameters
-\(\gamma\) and \(\eta\), to the empirical data from Triki \emph{et al.}
-\citep{triki_Biological_2019, triki_Brain_2020} to test whether each or
-a combination of these effects is a better explanation for the pattern
-seen in the data. We used the ecological variables: cleaners, visitor clients,
-resident clients abundances and visitor clients leaving probability,\\
+The aim of the analyses is to fit the key model parameters \(\gamma\)
+and \(\eta\), to the empirical data from Triki \emph{et al.} {[}29,30{]}
+to test whether each or a combination of these effects is a better
+explanation for the pattern seen in the data. We used the ecological
+variables: cleaners, visitor clients, resident clients abundances and
+visitor clients leaving probability,\\
 as input to the models. As the response variable, we used cleaners'
 preference for visitors over residents in the ephemeral reward task.
-Finally, we used the preference for visitors resulting from the
-model simulations as the prediction for the response variable.
-We kept all other parameter values used for the model simulations constant,
-see Table \ref{tab:param}.
+Finally, we used the preference for visitors resulting from the model
+simulations as the prediction for the response variable. We kept all
+other parameter values used for the model simulations constant, see
+Table \ref{tab:param}.
 
@@
 variables and cleaner fish preferences for visitors, we needed to scale
-the absolute population densities of cleaner fish from the empirical data
-to a measure of relative abundances that captures client visitation patterns.
-This is because, in the model, relative abundances of clients
-define not only the probability of residents and visitors
-but also how often the cleaning station is empty (e.g.~there are no
-clients to be cleaned). The frequency with which clients visit the station
-is another variable, which in nature may vary among different client species
+the absolute population densities of cleaner fish from the empirical
+data to a measure of relative abundances that captures client visitation
+patterns. This is because, in the model, relative abundances of clients
+define not only the probability of residents and visitors but also how
+often the cleaning station is empty (e.g.~there are no clients to be
+cleaned). The frequency with which clients visit the station is another
+variable, which in nature may vary among different client species
 depending on their ectoparasite loads. We do not have field estimates
-for species-specific parasite loads, especially not as a function of the site.
-In order to control for these aspects, we computed a measure of relative
-cleaner fish abundance for each reef site relative to
-absolute abundances and multiplied it
-by a scaling constant that changes the range of the variable. This scaling
-constant is hence meant to capture variation in the market conditions driven
-partly by cleaner fish abundance. We fitted the value of the scaling constant as
-part of the statistical inference. As for the visitor and resident
-abundances, we computed a relative measure with respect to the
-total client abundance, and weighted that by the rescaled relative absence
-of cleaners (\(1-\text{relative cleaner abundance}\)). Thus, all three measures
-of relative abundance sum up to 1, and can be used in the model as a proxy
+for species-specific parasite loads, especially not as a function of the
+site. In order to control for these aspects, we computed a measure of
+relative cleaner fish abundance for each reef site relative to absolute
+abundances and multiplied it by a scaling constant that changes the
+range of the variable. This scaling constant is hence meant to capture
+variation in the market conditions driven partly by cleaner fish
+abundance. We fitted the value of the scaling constant as part of the
+statistical inference. As for the visitor and resident abundances, we
+computed a relative measure with respect to the total client abundance,
+and weighted that by the rescaled relative absence of cleaners
+(\(1-\text{relative cleaner abundance}\)). Thus, all three measures of
+relative abundance sum up to 1, and can be used in the model as a proxy
 for the probability of having different options in the cleaning station.
-Note that we introduced the scaling constant to control for variation that
-is not captured by the model; its parameter distribution does not offer
-biological insights.
+Note that we introduced the scaling constant to control for variation
+that is not captured by the model; its parameter distribution does not
+offer biological insights.
 
 Once we calculated the relative abundances, we obtained predictions from
-the model for each one of the locations and ran the Markov Chain. We started the
-chain with random values for the parameters of interest, then ran the
-computational model once for every reef site using as input the ecological
-explanatory variables. The model outputs the probability of choosing the visitor
-for each location \(p_i\), where \(i\) is the index for the 12 locations. Assuming a
-binomial distribution, the probability that each of the cleaner fish 20 choices
-in the ephemeral reward task was generated by the model
-is given by \(\binom{n}{k_ij}p^{k_{ij}}_i (1-p_i)^{n-k_{ij}}\);
-where \(k_{ij}\) is the number of times that cleaner fish \(j\) in reef site \(i\)
-chose the visitor over the resident; and \(n=20\) (due to our choice of using 20
-choices per cleaner fish). By taking the natural logarithm and summing over all
-the cleaner fish and reef sites, we obtained the log-likelihood of the data
-given the model and parameters. We then proposed a new set of parameters drawn
-from a uniform distribution centred around the old parameter set. The amplitude
-of the uniform distribution used for each parameter can be found in Table
-\ref{tab:param}. Subsequently, we ran the model and calculated the likelihood
-with the new parameter set. We then used the ratio of the two likelihoods to
-choose which parameter set to keep. New parameter sets with a higher likelihood
-than the old set replaced old ones, and those with a lower likelihood replaced
-current ones with a probability equal to the log-likelihood ratio.
-Given that we only used the likelihoods in the decision, we used an
-uninformative prior. Once we decided whether the new parameter set
-would replace the old one, we ran the model again to sample the likelihood
-distribution of the parameter set. We then started
-the cycle again by proposing a new set of parameters and repeated
-the process for \(1e^5\) steps. We ran 5 independent chains,
-discarded the first \(1000\) samples of each chain as burn in,
-and after that, we kept 1 in every 100 samples to avoid autocorrelation.
-The collection of parameters sets kept in
-all chains approximates the posterior distribution. We coded the model
-as well as the fitting algorithm in \emph{c++}, the diagnostics and visualization
-in R \citep{rcoreteam_Language_2021}. All codes are accessible at
+the model for each one of the locations and ran the Markov Chain. We
+started the chain with random values for the parameters of interest,
+then ran the computational model once for every reef site using as input
+the ecological explanatory variables. The model outputs the probability
+of choosing the visitor for each location \(p_i\), where \(i\) is the
+index for the 12 locations. Assuming a binomial distribution, the
+probability that each of the cleaner fish 20 choices in the ephemeral
+reward task was generated by the model is given by
+\(\binom{n}{k_ij}p^{k_{ij}}_i (1-p_i)^{n-k_{ij}}\); where \(k_{ij}\) is
+the number of times that cleaner fish \(j\) in reef site \(i\) chose the
+visitor over the resident; and \(n=20\) (due to our choice of using 20
+choices per cleaner fish). By taking the natural logarithm and summing
+over all the cleaner fish and reef sites, we obtained the log-likelihood
+of the data given the model and parameters. We then proposed a new set
+of parameters drawn from a uniform distribution centred around the old
+parameter set. The amplitude of the uniform distribution used for each
+parameter can be found in Table \ref{tab:param}. Subsequently, we ran
+the model and calculated the likelihood with the new parameter set. We
+then used the ratio of the two likelihoods to choose which parameter set
+to keep. New parameter sets with a higher likelihood than the old set
+replaced old ones, and those with a lower likelihood replaced current
+ones with a probability equal to the log-likelihood ratio. Given that we
+only used the likelihoods in the decision, we used an uninformative
+prior. Once we decided whether the new parameter set would replace the
+old one, we ran the model again to sample the likelihood distribution of
+the parameter set. We then started the cycle again by proposing a new
+set of parameters and repeated the process for \(1e^5\) steps. We ran 5
+independent chains, discarded the first \(1000\) samples of each chain
+as burn in, and after that, we kept 1 in every 100 samples to avoid
+autocorrelation. The collection of parameters sets kept in all chains
+approximates the posterior distribution. We coded the model as well as
+the fitting algorithm in \emph{c++}, the diagnostics and visualization
+in R {[}32{]}. All codes are accessible at
 \(\color{red}{\text{include citation}}\)
@@
 To compare the fit of the three alternative models, we used the
-distribution of pseudo \(R^2\) proposed by Mcfadden \citep{mcfadden_Conditional_1974}.
-Mcfadden's pseudo \(R^2\) is a standard measure of fit for logistic regression.
-In that context, \(pseudo-R^2\) uses the log-likelihood of the data given
-the model, relative to the log-likelihood of the data given a
-model without covariates, as a measure of fit. Our
-model is not a logistic regression, therefore we measured the \(pseudo-R^2\) in
-relation to the log-likelihood of a model
-with parameters \(\gamma\) and \(\eta\) set to zero. This, in practice,
-amounts to a model that has a neutral preference between the two options.
-We computed the pseudo \(R^2\) for all the samples of the posterior from
-the MCMC. Thus, we used these distributions of pseudo \(R^2\)'s as a measure of
-fit.
+distribution of pseudo \(R^2\) proposed by Mcfadden {[}33{]}. Mcfadden's
+pseudo \(R^2\) is a standard measure of fit for logistic regression. In
+that context, \(pseudo-R^2\) uses the log-likelihood of the data given
+the model, relative to the log-likelihood of the data given a model
+without covariates, as a measure of fit. Our model is not a logistic
+regression, therefore we measured the \(pseudo-R^2\) in relation to the
+log-likelihood of a model with parameters \(\gamma\) and \(\eta\) set to
+zero. This, in practice, amounts to a model that has a neutral
+preference between the two options. We computed the pseudo \(R^2\) for
+all the samples of the posterior from the MCMC. Thus, we used these
+distributions of pseudo \(R^2\)'s as a measure of fit.
 
@@
 \begin{figure}
-
-{\centering \includegraphics[width=1\linewidth]{manuscript_1.0_files/figure-latex/post-1}
-
-}
-
-\caption{Posterior distributions for parameter values \(\gamma\) and \(\eta\) for
-the three models (``Full model'', ``chaining only'' and ``penalty only''). We show
-the kernel density estimates, below the mode (black dot) and the 65\%
-(light blue shade) and 95\% (grey shade) highest posterior density interval
-for the two parameters. On the top, panels a and b show posterior
-distributions for a full model, including chaining (\(\gamma\)) and penalty
-(\(\eta\)). Panel c, shows the \(\gamma\) estimate from model with only chaining.
-Panel d shows the \(\\eta\) estimate from a model with only penalty. Panel e,
-shows a measure of fit for all models, namely the distribution of pseudo-\(R^2\)
-obtained from sampling the posterior distribution of parameter values.}\label{fig:post}
+\includegraphics[width=1\linewidth]{manuscript_PLOS_files/figure-latex/post-1} \caption{Posterior distributions for parameter values $\gamma$ and $\eta$ for the three models (Full model, chaining only and penalty only).
+We show the kernel density estimates, below the mode (black dot) and the 65 (light blue shade) and 95\% (grey shade)  highest posterior density interval for the two parameters.
+On the top, panels a and b show posterior distributions for a full model, including chaining ($\gamma$) and penalty ($\eta$).
+Panel c, shows the $\gamma$ estimate from model with only chaining.
+Panel d shows the $\eta$ estimate from a model with only penalty.
+Panel e, shows a measure of fit for all models, namely the distribution of pseudo-$R^2$ obtained from sampling the posterior distribution of parameter values.}\label{fig:post}
 \end{figure}
@@
 Estimation of parameter values for the three models (full model,
-chaining and penalty), support chaining as the only mechanism
-cleaners use to account for the future effects of their actions;
-and thus to solve the ephemeral reward task. In the estimation of the
-parameter values of the full model, which includes both chaining and
-penalty, the bulk of the marginal posterior distribution of \(\eta\) which
-controls the strength of penalty is around 0 (Fig. \ref{fig:post}).
-As for \(\gamma\), controlling chaining, the 95\% confidence
-intervals also includes zero, but the mode of the posterior
-is around 0.5 (Fig. \ref{fig:post}, a). In the chaining model,
-where \(\eta\) is set to zero, the distribution of \(\gamma\) shifted
-to higher values, zero is no longer part of the 95\% credible interval
-of the parameter (Fig. \ref{fig:post}, c). In contrast, when we
-look at the model with only penalty, the posterior distribution
-of \(\eta\) is still centred around zero (Fig. \ref{fig:post}, d).
-Thus, the analysis of the estimates of individual parameter
-values in the three models only supports a strong
+chaining and penalty), support chaining as the only mechanism cleaners
+use to account for the future effects of their actions; and thus to
+solve the ephemeral reward task. In the estimation of the parameter
+values of the full model, which includes both chaining and penalty, the
+bulk of the marginal posterior distribution of \(\eta\) which controls
+the strength of penalty is around 0 (Fig. \ref{fig:post}). As for
+\(\gamma\), controlling chaining, the 95\% confidence intervals also
+includes zero, but the mode of the posterior is around 0.5 (Fig.
+\ref{fig:post}, a). In the chaining model, where \(\eta\) is set to
+zero, the distribution of \(\gamma\) shifted to higher values, zero is
+no longer part of the 95\% credible interval of the parameter (Fig.
+\ref{fig:post}, c). In contrast, when we look at the model with only
+penalty, the posterior distribution of \(\eta\) is still centred around
+zero (Fig. \ref{fig:post}, d). Thus, the analysis of the estimates of
+individual parameter values in the three models only supports a strong
 effect of chaining. Furthermore, the comparison of the models` fit
-favours the chaining model. In panel e of figure \ref{fig:post}
-we show the distribution of \(pseudo-R^2\) calculated using
-samples from the posterior distributions shown before.
-Note, \(pseudo-R^2\) can have negative values, which is when
-the log-likelihood of the model is lower than that of a model that
-triggers neutral preferences. Even though the peak of the three
-\(pseudo-R^2\) distributions were not very different, the model with only
-chaining produced a distribution of \(pseudo-R^2\) where more values
-were positive (to the right of the black line in Fig. \ref{fig:post} f). This
-shows that accounting for variation in the parameter estimates the
-model with chaining gives a better fit to the data, despite
-having one parameter less than the full model. We have not shown
-here the marginal posterior distributions of the scaling constant,
-given that they do not bring biological insight.
-Their visualizations can be found in the supplementary
-material (Fig. \ref{fig:scaConst}), as well as the diagnostics of the MCMCs
-(Figs. \ref{fig:diagnosticsfull},\ref{fig:diaggam},\ref{fig:diagNeg}).
+favours the chaining model. In panel e of figure \ref{fig:post} we show
+the distribution of \(pseudo-R^2\) calculated using samples from the
+posterior distributions shown before. Note, \(pseudo-R^2\) can have
+negative values, which is when the log-likelihood of the model is lower
+than that of a model that triggers neutral preferences. Even though the
+peak of the three \(pseudo-R^2\) distributions were not very different,
+the model with only chaining produced a distribution of \(pseudo-R^2\)
+where more values were positive (to the right of the black line in Fig.
+\ref{fig:post} f). This shows that accounting for variation in the
+parameter estimates the model with chaining gives a better fit to the
+data, despite having one parameter less than the full model. We have not
+shown here the marginal posterior distributions of the scaling constant,
+given that they do not bring biological insight. Their visualizations
+can be found in the supplementary material (Fig. \ref{fig:scaConst}), as
+well as the diagnostics of the MCMCs (Figs.
+\ref{fig:diagnosticsfull},\ref{fig:diaggam},\ref{fig:diagNeg}).
 
 \begin{figure}
-
-{\centering \includegraphics[width=1\linewidth]{manuscript_1.0_files/figure-latex/pred-1}
-
-}
-
-\caption{Observed and predicted probability of choosing a visitor.
-Left-hand side panel: colour contour shows the prediction from the
-learning model using the mode of the posterior distributions of parameters
-recovered by the statistical analysis. Dots show the frequency of visitor
-choices for the 12 reef sites, as well as the corresponding relative
-cleaner fish abundance (x axis) and frequency of visitors clients leaving
-the cleaning station (y axis). Right-hand side panels: Variation of the
-predicted probabilities of choosing a visitor over a resident and their
-observed values for 12 locations. Circles show the mean prediction for
-each location from 100 samples taken from the posterior distribution.
-Thick and thin bars show the 66 and 95\% credible interval, respectively,
-taken from those posterior samples. Squares show the predictions used for the
-panel on the right-hand side. Colour coding denotes different reef site/year
-of the data collection (see Empirical data section). The black line corresponds
-to a perfect match between observed and predicted probabilities. Upper
-panels (a and b) show predictions from a model including chaining and
-penalty; middle panels (c and d) from a model with only chaining; lower
-panels (e and f) from a model with penalty only.}\label{fig:pred}
+\includegraphics[width=1\linewidth]{manuscript_PLOS_files/figure-latex/pred-1} \caption{Observed and predicted probability of choosing a visitor.
+Left-hand side panel: colour contour shows the prediction from the learning model using the mode of the posterior distributions of parameters recovered by the statistical analysis.
+Dots show the frequency of visitor choices for the 12 reef sites, as well as the corresponding relative cleaner fish abundance (x axis) and frequency of visitors clients leaving the cleaning station (y axis).
+Right-hand side panels: Variation of the predicted probabilities  of choosing a visitor over a resident and their observed values for 12 locations.
+Circles show the mean prediction for each location from 100 samples taken from the posterior distribution.
+Thick and thin bars show the 66 and 95\% credible interval, respectively, taken from those posterior samples.
+Squares show the predictions used for the panel on the right-hand side.
+Colour coding denotes different reef site/year of the data collection (see Empirical data section).
+The black line corresponds to a perfect match between observed and predicted probabilities.
+Upper panels (a and b) show predictions from a model including chaining and penalty; middle panels (c and d) from a  model with only chaining; lower panels (e and f) from a model with penalty only.}\label{fig:pred}
 \end{figure}
 
-The main reason for chaining and penalty to give different
-predictions is the way that cleaner fish relative abundance influences the
+The main reason for chaining and penalty to give different predictions
+is the way that cleaner fish relative abundance influences the
 preference for the visitor clients. Visitor leaving probability has a
 similar positive effect on the probability of choosing the visitor
-clients on all three models, they all predict an increase preference
-for visitors as the visitor probability increases (Fig. \ref{fig:pred}).
-In contrast, cleaner fish relative abundance has a different effect in the
-model with only chaining, compared to the other two models,
-full model and penalty. In the model with only chaining, only intermediate
-cleaner fish abundance triggers a preference for the visitor
-clients (Fig. \ref{fig:pred} c). In both models with penalty,
-both intermediate and low cleaner abundance triggered a preference
-for the visitor (Fig. \ref{fig:pred} a,e). Note, however, we calculated
-preferences shown in figure \ref{fig:pred} left panels by using only the mode
-of the posterior distributions, and by holding constant the balance between
+clients on all three models, they all predict an increase preference for
+visitors as the visitor probability increases (Fig. \ref{fig:pred}). In
+contrast, cleaner fish relative abundance has a different effect in the
+model with only chaining, compared to the other two models, full model
+and penalty. In the model with only chaining, only intermediate cleaner
+fish abundance triggers a preference for the visitor clients (Fig.
+\ref{fig:pred} c). In both models with penalty, both intermediate and
+low cleaner abundance triggered a preference for the visitor (Fig.
+\ref{fig:pred} a,e). Note, however, we calculated preferences shown in
+figure \ref{fig:pred} left panels by using only the mode of the
+posterior distributions, and by holding constant the balance between
 resident and visitors´ abundances. Panels on the right, show how close
@@
 In this study, our main aim was to unravel which of two potential
-cognitive mechanisms, chaining of events, penalty,
-or their combination, best explains wild-caught cleaner fish
-performance in the ephemeral reward task, while accounting for their
-ecological conditions. To evaluate the merits of each of these two mechanisms
-separately and combined, we considered cleaner fish performance
-in the lab test to have its origin from the rule these fish applied
-in their natural environment. That is, individuals that
-solved the task already had a preference for
-visitors clients and generalized this rule to the lab conditions
-once being familiar with the task.
-
-While all three models captured well the positive relationship between visitor
-leaving behaviour and cleaner fish performance in
-the market task \citep{triki_Biological_2019}, only the chaining mechanism
-predicted that cleaner fish performance in the task should be low in
-habitats with low cleaner-to-client ratios, regardless of the
-visitor leaving probability. In contrast, models including
-negative reward predicted the highest performance in the ephemeral
-reward task when relative cleaner fish abundance is low, particularly
-together with a high probability of visitor leaving (Fig. \ref{fig:pred}).
-Low relative cleaner fish abundances mean the market has an excess of demand for
-cleaning services. In the models, this translates to a cleaning station
-that is frequently full. Thus, when a visitor leaves, it is likely that the
-cleaner fish will have access to another client in the next step. Therefore,
-there will not be much difference in future reward between choosing
-a visitor and a resident, and cleaners will not develop a preference for the
-visitor in these conditions. On the other hand, the effect of negative reward
-on cleaner fish preference is the opposite, as in a busy cleaning station, to
-that of chaining. cleaner fish will get more often the resident-visitor
-state and will develop a preference for the visitor faster.
-At high cleaner fish abundances, the resident-visitor state
-becomes so rare that neither mechanism is very efficient
-at generating a preference for visitors. When facing the
-resident-visitor choice, it is still best to choose the visitor; however,
-the learning machinery will not be able to develop this preference
-efficiently. Overall, the models suggest that chaining is the cognitive
-mechanism that allows cleaner fish to adaptively adjust to their
-biological market ecological conditions.
+cognitive mechanisms, chaining of events, penalty, or their combination,
+best explains wild-caught cleaner fish performance in the ephemeral
+reward task, while accounting for their ecological conditions. To
+evaluate the merits of each of these two mechanisms separately and
+combined, we considered cleaner fish performance in the lab test to have
+its origin from the rule these fish applied in their natural
+environment. That is, individuals that solved the task already had a
+preference for visitors clients and generalized this rule to the lab
+conditions once being familiar with the task.
+
+While all three models captured well the positive relationship between
+visitor leaving behaviour and cleaner fish performance in the market
+task {[}29{]}, only the chaining mechanism predicted that cleaner fish
+performance in the task should be low in habitats with low
+cleaner-to-client ratios, regardless of the visitor leaving probability.
+In contrast, models including negative reward predicted the highest
+performance in the ephemeral reward task when relative cleaner fish
+abundance is low, particularly together with a high probability of
+visitor leaving (Fig. \ref{fig:pred}). Low relative cleaner fish
+abundances mean the market has an excess of demand for cleaning
+services. In the models, this translates to a cleaning station that is
+frequently full. Thus, when a visitor leaves, it is likely that the
+cleaner fish will have access to another client in the next step.
+Therefore, there will not be much difference in future reward between
+choosing a visitor and a resident, and cleaners will not develop a
+preference for the visitor in these conditions. On the other hand, the
+effect of negative reward on cleaner fish preference is the opposite, as
+in a busy cleaning station, to that of chaining. cleaner fish will get
+more often the resident-visitor state and will develop a preference for
+the visitor faster. At high cleaner fish abundances, the
+resident-visitor state becomes so rare that neither mechanism is very
+efficient at generating a preference for visitors. When facing the
+resident-visitor choice, it is still best to choose the visitor;
+however, the learning machinery will not be able to develop this
+preference efficiently. Overall, the models suggest that chaining is the
+cognitive mechanism that allows cleaner fish to adaptively adjust to
+their biological market ecological conditions.
 
@@
 densities and giving service priority to the visitor plate in the
-ephemeral reward task, as well as cleaner fish living at low
-densities but denying service priority to the visitor plate possess
-larger forebrains; a key teleost brain region associated with
-behavioural flexibility and social intelligence. Those failing to
-show optimized decision-rules given their local ecological
-conditions had relatively smaller forebrains \citep{triki_Brain_2020}.
-Triki \emph{et al.} refer to the former as socially competent cleaner fish,
-while the second group as socially incompetent cleaner fish.
-Social competence is the ability to optimise social behaviour
-to the available social information \citep{taborsky_Social_2012, bshary_Cooperation_2015, varela_Correlated_2020}. Our analyses yielded no
-evidence that the difference in social competence with respect to the local
-ecological conditions and associated brain morphology,
-found by Triki \emph{et al} \citep{triki_Brain_2020}, is due to the mechanism
-used to incorporate future consequences. It is conceivable that
-high performing individuals from low population densities reef sites
-use negative reinforcement instead of chaining, but in that
-case, negative reinforcement should have explained at least
-part of the data. Configurational learning or
-chunking \citep{sutherland_Configural_1989, miller_Magical_1956},
-the second component necessary to solve the ephemeral
-reward task \citep{quinones_Reinforcement_2019}, was
-not varied in the models we analysed here. However, while chunking tendencies
-should vary to allow individuals to adapt to their local conditions
-\citep{prat_Modelling_2022, kolodny_Evolution_2014}, systematic differences
-in individual chunking tendencies would not explain how socially
-competent decisions vary as a function of relative abundance.
-Therefore, it remains currently unclear what cell-demanding
-mechanisms may cause variation in social competence that
-translates into site-specific variation in performance in the
-ephemeral reward task.
+ephemeral reward task, as well as cleaner fish living at low densities
+but denying service priority to the visitor plate possess larger
+forebrains; a key teleost brain region associated with behavioural
+flexibility and social intelligence. Those failing to show optimized
+decision-rules given their local ecological conditions had relatively
+smaller forebrains {[}30{]}. Triki \emph{et al.} refer to the former as
+socially competent cleaner fish, while the second group as socially
+incompetent cleaner fish. Social competence is the ability to optimise
+social behaviour to the available social information {[}34--36{]}. Our
+analyses yielded no evidence that the difference in social competence
+with respect to the local ecological conditions and associated brain
+morphology, found by Triki \emph{et al} {[}30{]}, is due to the
+mechanism used to incorporate future consequences. It is conceivable
+that high performing individuals from low population densities reef
+sites use negative reinforcement instead of chaining, but in that case,
+negative reinforcement should have explained at least part of the data.
+Configurational learning or chunking {[}37,38{]}, the second component
+necessary to solve the ephemeral reward task {[}22{]}, was not varied in
+the models we analysed here. However, while chunking tendencies should
+vary to allow individuals to adapt to their local conditions
+{[}21,39{]}, systematic differences in individual chunking tendencies
+would not explain how socially competent decisions vary as a function of
+relative abundance. Therefore, it remains currently unclear what
+cell-demanding mechanisms may cause variation in social competence that
+translates into site-specific variation in performance in the ephemeral
+reward task.
 
@@
 ignores alternative channels of information that could be relevant in
-market-like situations. For example, the model does not investigate whether
-cleaner fish actually assess the frequency of client visits or a mean frequency
-of visitors leaving. The updating learning mechanism for the development
-of preferences works on a trial-by-trial basis. In the model, cleaner fish
-do not need to assess the actual state of the market, \emph{i.e.} their abundance,
-the abundance of residents and visitors, and client visitation rate as an
-indicator of demand. They only need to assess the short-term
-consequences of their own decisions on food intake and chain them.
-Also, for the sake of simplicity, the model ignores
-the process by which cleaner fish discriminate
-residents and visitor clients. A model that accounts for this discrimination
-probably would involve the development of preferences for morphological or
-behavioural features that are statistically associated with visitors
-or residents. For example, visitors are on average larger
-than residents in body size \citep{bshary_Cleaner_2001}, and contrary to
-residents, they are less likely to chase a cleaner fish that fails to cooperate
-and instead cheats its client by taking a bite of mucus
-\citep{bshary_Asymmetric_2002}. Given these associations, chaining might
-produce the decision-rule ``choose the larger client and/or the less aggressive
-client'', which is not a useful rule in the standard ephemeral reward task.
-
-In conclusion, our study shows that variation in cognitive performance as
-a function of the local ecological conditions may set the stage for the use of
-mechanistic modelling to identify the cognitive processes underlying
-learning in animals. The combination overcomes the limitations
-of the general philosophy in animal cognition to apply the logic of
-Lloyd Morgen's canon (Occam's razor). Cognitive experiments with the
-aim of excluding basic reinforcement learning as a potential
-explanation (operant and/or classical conditioning) of performance
-often employ one trial experiments requiring animals to solve the
-task on the first possible occasion.
-For example, any theory of mind task needs to be solved in the first
-trial in order to exclude fast conditioning \citep{heyes_Theory_1998}.
-Similarly, subjects need to solve a social learning task on the first
-trial to accept imitation as a mechanism over stimulus/local
+market-like situations. For example, the model does not investigate
+whether cleaner fish actually assess the frequency of client visits or a
+mean frequency of visitors leaving. The updating learning mechanism for
+the development of preferences works on a trial-by-trial basis. In the
+model, cleaner fish do not need to assess the actual state of the
+market, \emph{i.e.} their abundance, the abundance of residents and
+visitors, and client visitation rate as an indicator of demand. They
+only need to assess the short-term consequences of their own decisions
+on food intake and chain them. Also, for the sake of simplicity, the
+model ignores the process by which cleaner fish discriminate residents
+and visitor clients. A model that accounts for this discrimination
+probably would involve the development of preferences for morphological
+or behavioural features that are statistically associated with visitors
+or residents. For example, visitors are on average larger than residents
+in body size {[}11{]}, and contrary to residents, they are less likely
+to chase a cleaner fish that fails to cooperate and instead cheats its
+client by taking a bite of mucus {[}12{]}. Given these associations,
+chaining might produce the decision-rule ``choose the larger client
+and/or the less aggressive client,'' which is not a useful rule in the
+standard ephemeral reward task.
+
+In conclusion, our study shows that variation in cognitive performance
+as a function of the local ecological conditions may set the stage for
+the use of mechanistic modelling to identify the cognitive processes
+underlying learning in animals. The combination overcomes the
+limitations of the general philosophy in animal cognition to apply the
+logic of Lloyd Morgen's canon (Occam's razor). Cognitive experiments
+with the aim of excluding basic reinforcement learning as a potential
+explanation (operant and/or classical conditioning) of performance often
+employ one trial experiments requiring animals to solve the task on the
+first possible occasion. For example, any theory of mind task needs to
+be solved in the first trial in order to exclude fast conditioning
+{[}3{]}. Similarly, subjects need to solve a social learning task on the
+first trial to accept imitation as a mechanism over stimulus/local
 enhancement. Such strict conditions are virtually never met. For
 example, potato washing by Japanese macaques, an iconic example of
-social learning, took several years to spread within the group
-\citep{kawamura_Process_1959}, meaning that any learner had been repeatedly
-exposed to demonstrations before acquisition. Importantly, Galef
-\citep{galef_Question_1992} refuted imitation as a mechanism not simply because
-of the repeated exposure but because a (rather qualitative) analysis of
-the spread of potato washing across individuals did not follow the
-prediction based on imitation learning (see also
-\citep{hirata_SweetPotato_2001}). In our case, the number of trials it took
-cleaners to learn the solution to the ephemeral rewards task
-would never allow excluding an important role of
-penalty based on the data
-alone. However, fitting model predictions to our comprehensive empirical
-data set revealed that a more complex mechanism, estimation of future reward,
+social learning, took several years to spread within the group {[}40{]},
+meaning that any learner had been repeatedly exposed to demonstrations
+before acquisition. Importantly, Galef {[}41{]} refuted imitation as a
+mechanism not simply because of the repeated exposure but because a
+(rather qualitative) analysis of the spread of potato washing across
+individuals did not follow the prediction based on imitation learning
+(see also {[}42{]}). In our case, the number of trials it took cleaners
+to learn the solution to the ephemeral rewards task would never allow
+excluding an important role of penalty based on the data alone. However,
+fitting model predictions to our comprehensive empirical data set
+revealed that a more complex mechanism, estimation of future reward,
 fits the data better.
@@
 \begin{figure}
-
-{\centering \includegraphics{manuscript_1.0_files/figure-latex/rawdata-1}
-
-}
-
-\caption{Relation between the response variable used in this study and the
-criteria used in previous studies to assess performance in the ephemeral reward
-task. In the x axis, we classified the performance of cleaner fish according to
-whether they developed a preference for the visitor in the initial round,
-in the initial and reversal, or none of them. In the y axis, we add the choices
-of two experimental sessions: panel on the left uses one session from the initial
-round and one from the reversal round when possible
-(as described in the main text); panel on the right uses two sessions from the
-initial round for all fish.}\label{fig:rawdata}
+\includegraphics[width=1\linewidth]{manuscript_PLOS_files/figure-latex/rawdata-1} \caption{Relation between the response variable used in this study and the criteria used in previous studies to assess performance in the ephemeral reward task.
+In the x axis, we classified the performance of cleaner fish according to whether they developed a preference for the visitor in the initial round, in the initial and reversal, or none of them.
+In the y axis, we add the choices of two experimental sessions: panel on the left uses one session from the initial round and one from the reversal round when possible (as described in the main text); panel on the right uses two sessions from the initial round for all fish.}\label{fig:rawdata}
 \end{figure}
@@
 \begin{figure}[H]
-
-{\centering \includegraphics[width=0.95\linewidth,]{manuscript_1.0_files/figure-latex/scaConst-1}
-
-}
-
-\caption{Posterior distributions for scaling constant for the three models
-(``Full model'', chaining only'' and ``penalty only''). We show the kernel
-density estimates, below the mode (black dot) and the 65\% (light blue shade)
-and 95\% (grey shade) highest posterior density interval. On the top,
-panel a shows the posterior distribution from the full model; panel b from
-the model with only chaining; and panel c from a model with only penalty.}\label{fig:scaConst}
+\includegraphics[width=0.95\linewidth,]{manuscript_PLOS_files/figure-latex/scaConst-1} \caption{Posterior distributions for scaling constant for the three models (Full model, chaining only and penalty only).
+We show the kernel density estimates, below the mode (black dot) and the 65\% (light blue shade) and 95\% (grey shade)  highest posterior density interval.
+On the top, panel a shows the posterior distribution from the full model; panel b from the model with only chaining; and panel c from a model with only penalty.}\label{fig:scaConst}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=1\linewidth]{manuscript_PLOS_files/figure-latex/diagnosticsfull-1} \caption{MCMC convergence diagnostics for the full model.
+On the left trace-plots, on the right changes along the chain of the Gelman and Rubin shrink factor.}\label{fig:diagnosticsfull}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=1\linewidth]{manuscript_PLOS_files/figure-latex/diaggam-1} \caption{MCMC convergence diagnostics for the chaining model.
+On the left trace-plots, on the right changes along the chain of the Gelman and Rubin shrink factor }\label{fig:diaggam}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=1\linewidth]{manuscript_PLOS_files/figure-latex/diagNeg-1} \caption{MCMC convergence diagnostics for the penalty model.
+On the left trace-plots, on the right changes along the chain of the Gelman and Rubin shrink factor}\label{fig:diagNeg}
 \end{figure}
@@
 \caption{\label{tab:param} Parameter values with which the model was run
-in the MCMC.
-\(\sigma\) refers to the amplitude of the perturbation kernel with the subscript indicating the associated parameter.
-New values were taken from a uniform distribution.
-\(\alpha\) refers to the learning rate.}\tabularnewline
+in the MCMC. \(\sigma\) refers to the amplitude of the perturbation
+kernel with the subscript indicating the associated parameter. New
+values were taken from a uniform distribution. \(\alpha\) refers to the
+learning rate.}\tabularnewline
 \toprule
@@
 
-\begin{figure}
-
-{\centering \includegraphics{manuscript_1.0_files/figure-latex/diagnosticsfull-1}
-
-}
-
-\caption{MCMC convergence diagnostics for the full model.
-On the left trace-plots, on the right changes along the chain of the
-Gelman and Rubin's shrink factor \citep{brooks_General_1998}.}\label{fig:diagnosticsfull}
-\end{figure}
-
-\begin{figure}
-
-{\centering \includegraphics{manuscript_1.0_files/figure-latex/diaggam-1}
-
-}
-
-\caption{MCMC convergence diagnostics for the chaining model.
-On the left trace-plots, on the right changes along the chain of the
-Gelman and Rubin's shrink factor \citep{brooks_General_1998}}\label{fig:diaggam}
-\end{figure}
-
-\begin{figure}
-
-{\centering \includegraphics{manuscript_1.0_files/figure-latex/diagNeg-1}
-
-}
-
-\caption{MCMC convergence diagnostics for the penalty model.
-On the left trace-plots, on the right changes along the chain of the
-Gelman and Rubin's shrink factor \citep{brooks_General_1998}}\label{fig:diagNeg}
-\end{figure}
-
-\ethics{The Animal Ethics Committee of the Queensland government (DAFF)
-approved the project (CA 2016/05/970 and CA 2017/05/1063).}
-
-\dataccess{Please provide details on the data availability.}
-
-\aucontribute{AQ and RB designed the study. ZT collected the data. AQ developed the model and
-fitted the model parameters to the data. AQ, RB and ZT wrote the manuscript.}
-
-\competing{The authors declate no conflict of interests.}
-
-\funding{This work was supported by the Swiss National Science Foundation (grants
-number: 31003A\_153067/1 and 310030B\_173334/1 to R.B.).}
-
-\ack{ZT and RB kindly thank the staff of Lizard Island Research Station, Dominique
-Roche, Sharon Wismer, Olivia Rey,Sandra Ann Binning, Elena Levorato and William McNeely for their
-field support. AQ thanks Florian Hartig for statistical advice.}
-
-\bibliographystyle{RS}
-\bibliography{Cleanerlearning.bib}
+\hypertarget{references}{%
+\section*{References}\label{references}}
+\addcontentsline{toc}{section}{References}
+
+\hypertarget{refs}{}
+\begin{CSLReferences}{0}{0}
+\leavevmode\vadjust pre{\hypertarget{ref-dally_Foodcaching_2006}{}}%
+\CSLLeftMargin{1. }
+\CSLRightInline{Dally JM, Emery NJ, Clayton NS. Food-caching western
+scrub-jays keep track of who was watching when. Science (New York, NY).
+2006;312: 1662--1665.
+doi:\href{https://doi.org/10.1126/science.1126539}{10.1126/science.1126539}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-suddendorf_Evolution_2007}{}}%
+\CSLLeftMargin{2. }
+\CSLRightInline{Suddendorf T, Corballis MC. The evolution of foresight:
+{What} is mental time travel, and is it unique to humans? The Behavioral
+and Brain Sciences. 2007;30: 299-313; discussion 313-351.
+doi:\href{https://doi.org/10.1017/S0140525X07001975}{10.1017/S0140525X07001975}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-heyes_Theory_1998}{}}%
+\CSLLeftMargin{3. }
+\CSLRightInline{Heyes CM. Theory of mind in nonhuman primates.
+Behavioral and Brain Sciences. 1998;21: 101--114.
+doi:\href{https://doi.org/10.1017/S0140525X98000703}{10.1017/S0140525X98000703}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-noe_Biological_1995}{}}%
+\CSLLeftMargin{4. }
+\CSLRightInline{Noë R, Hammerstein P. Biological markets. Trends in
+Ecology \& Evolution. 1995;10: 336--339.
+doi:\href{https://doi.org/10.1016/S0169-5347(00)89123-5}{10.1016/S0169-5347(00)89123-5}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-axen_Signalling_1996}{}}%
+\CSLLeftMargin{5. }
+\CSLRightInline{Axén AH, Leimar O, Hoffman V. Signalling in a
+mutualistic interaction. Animal Behaviour. 1996;52: 321--333.
+doi:\href{https://doi.org/10.1006/anbe.1996.0178}{10.1006/anbe.1996.0178}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-waldie_LongTerm_2011}{}}%
+\CSLLeftMargin{6. }
+\CSLRightInline{Waldie PA, Blomberg SP, Cheney KL, Goldizen AW, Grutter
+AS. Long-{Term} {Effects} of the {Cleaner} {Fish} {Labroides} dimidiatus
+on {Coral} {Reef} {Fish} {Communities}. PLOS ONE. 2011;6: e21201.
+doi:\href{https://doi.org/10.1371/journal.pone.0021201}{10.1371/journal.pone.0021201}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-ros_Does_2011}{}}%
+\CSLLeftMargin{7. }
+\CSLRightInline{Ros AFH, Lusa J, Meyer M, Soares M, Oliveira RF,
+Brossard M, et al. Does access to the bluestreak cleaner wrasse
+{Labroides} dimidiatus affect indicators of stress and health in
+resident reef fishes in the {Red} {Sea}? Hormones and Behavior. 2011;59:
+151--158.
+doi:\href{https://doi.org/10.1016/j.yhbeh.2010.11.006}{10.1016/j.yhbeh.2010.11.006}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-triki_Effects_2016}{}}%
+\CSLLeftMargin{8. }
+\CSLRightInline{Triki Z, Grutter AS, Bshary R, Ros AFH. Effects of
+short-term exposure to ectoparasites on fish cortisol and hematocrit
+levels. Marine Biology. 2016;163: 187.
+doi:\href{https://doi.org/10.1007/s00227-016-2959-y}{10.1007/s00227-016-2959-y}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-demaire_Reduced_2020}{}}%
+\CSLLeftMargin{9. }
+\CSLRightInline{Demairé C, Triki Z, Binning SA, Glauser G, Roche DG,
+Bshary R. Reduced access to cleaner fish negatively impacts the
+physiological state of two resident reef fishes. Marine Biology.
+2020;167: 48.
+doi:\href{https://doi.org/10.1007/s00227-020-3658-2}{10.1007/s00227-020-3658-2}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-bshary_Choosy_2002}{}}%
+\CSLLeftMargin{10. }
+\CSLRightInline{Bshary R, Schäffer D. Choosy reef fish select cleaner
+fish that provide high-quality service. Animal Behaviour. 2002;63:
+557--564.
+doi:\href{https://doi.org/10.1006/anbe.2001.1923}{10.1006/anbe.2001.1923}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-bshary_Cleaner_2001}{}}%
+\CSLLeftMargin{11. }
+\CSLRightInline{Bshary R. The cleaner fish market. In: Van Hooff JARAM,
+Hammerstein P, Noë R, editors. Economics in {Nature}: {Social}
+{Dilemmas}, {Mate} {Choice} and {Biological} {Markets}. Cambridge:
+Cambridge University Press; 2001. pp. 146--172.
+doi:\href{https://doi.org/10.1017/CBO9780511752421.010}{10.1017/CBO9780511752421.010}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-bshary_Asymmetric_2002}{}}%
+\CSLLeftMargin{12. }
+\CSLRightInline{Bshary R, Grutter AS. Asymmetric cheating opportunities
+and partner control in a cleaner fish mutualism. Animal Behaviour.
+2002;63: 547--555.
+doi:\href{https://doi.org/10.1006/anbe.2001.1937}{10.1006/anbe.2001.1937}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-salwiczek_Adult_2012}{}}%
+\CSLLeftMargin{13. }
+\CSLRightInline{Salwiczek LH, Prétôt L, Demarta L, Proctor D, Essler J,
+Pinto AI, et al. Adult {Cleaner} {Wrasse} {Outperform} {Capuchin}
+{Monkeys}, {Chimpanzees} and {Orang}-utans in a {Complex} {Foraging}
+{Task} {Derived} from {Cleaner} -- {Client} {Reef} {Fish} {Cooperation}.
+PLOS ONE. 2012;7: e49068.
+doi:\href{https://doi.org/10.1371/journal.pone.0049068}{10.1371/journal.pone.0049068}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-zentall_Early_2017}{}}%
+\CSLLeftMargin{14. }
+\CSLRightInline{Zentall TR, Case JP, Berry JR. Early commitment
+facilitates optimal choice by pigeons. Psychonomic Bulletin \& Review.
+2017;24: 957--963.
+doi:\href{https://doi.org/10.3758/s13423-016-1173-8}{10.3758/s13423-016-1173-8}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-pepperberg_Can_2014}{}}%
+\CSLLeftMargin{15. }
+\CSLRightInline{Pepperberg IM, Hartsfield LA. Can grey parrots
+({Psittacus} erithacus) succeed on a "complex" foraging task failed by
+nonhuman primates ({Pan} troglodytes, {Pongo} abelii, {Sapajus} apella)
+but solved by wrasse fish ({Labroides} dimidiatus)? Journal of
+Comparative Psychology (Washington, DC: 1983). 2014;128: 298--306.
+doi:\href{https://doi.org/10.1037/a0036205}{10.1037/a0036205}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-shettleworth_Cognition_2009}{}}%
+\CSLLeftMargin{16. }
+\CSLRightInline{Shettleworth SJ. Cognition, {Evolution}, and {Behavior}.
+2 edition. Oxford ; New York: Oxford University Press; 2009. }
+
+\leavevmode\vadjust pre{\hypertarget{ref-wismer_Cuebased_2019}{}}%
+\CSLLeftMargin{17. }
+\CSLRightInline{Wismer S, Pinto AI, Triki Z, Grutter AS, Roche DG,
+Bshary R. Cue-based decision rules of cleaner fish in a biological
+market task. Animal Behaviour. 2019 {[}cited 30 Oct 2019{]}.
+doi:\href{https://doi.org/10.1016/j.anbehav.2019.09.013}{10.1016/j.anbehav.2019.09.013}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-pretot_Comparative_2021}{}}%
+\CSLLeftMargin{18. }
+\CSLRightInline{Prétôt L, Mickelberg J, Carrigan J, Stoinski T, Bshary
+R, Brosnan SF. Comparative performance of orangutans ({Pongo} spp.),
+Gorillas ({Gorilla} gorilla gorilla), and drills ({Mandrillus}
+leucophaeus), in an ephemeral foraging task. American Journal of
+Primatology. 2021;83: e23212.
+doi:\href{https://doi.org/10.1002/ajp.23212}{10.1002/ajp.23212}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-pretot_Comparing_2016}{}}%
+\CSLLeftMargin{19. }
+\CSLRightInline{Prétôt L, Bshary R, Brosnan SF. Comparing species
+decisions in a dichotomous choice task: Adjusting task parameters
+improves performance in monkeys. Animal Cognition. 2016;19: 819--834.
+doi:\href{https://doi.org/10.1007/s10071-016-0981-6}{10.1007/s10071-016-0981-6}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-dubois_Model_2021}{}}%
+\CSLLeftMargin{20. }
+\CSLRightInline{Dubois T, Pasquaretta C, Barron AB, Gautrais J, Lihoreau
+M. A model of resource partitioning between foraging bees based on
+learning. PLOS Computational Biology. 2021;17: e1009260.
+doi:\href{https://doi.org/10.1371/journal.pcbi.1009260}{10.1371/journal.pcbi.1009260}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-prat_Modelling_2022}{}}%
+\CSLLeftMargin{21. }
+\CSLRightInline{Prat Y, Bshary R, Lotem A. Modelling how cleaner fish
+approach an ephemeral reward task demonstrates a role for ecologically
+tuned chunking in the evolution of advanced cognition. PLOS Biology.
+2022;20: e3001519.
+doi:\href{https://doi.org/10.1371/journal.pbio.3001519}{10.1371/journal.pbio.3001519}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-quinones_Reinforcement_2019}{}}%
+\CSLLeftMargin{22. }
+\CSLRightInline{Quiñones AE, Leimar O, Lotem A, Bshary R. Reinforcement
+{Learning} {Theory} {Reveals} the {Cognitive} {Requirements} for
+{Solving} the {Cleaner} {Fish} {Market} {Task}. The American Naturalist.
+2019; 000--000.
+doi:\href{https://doi.org/10.1086/707519}{10.1086/707519}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-enquist_Power_2016}{}}%
+\CSLLeftMargin{23. }
+\CSLRightInline{Enquist M, Lind J, Ghirlanda S. The power of associative
+learning and the ontogeny of optimal behaviour. Royal Society Open
+Science. 2016;3: 160734.
+doi:\href{https://doi.org/10.1098/rsos.160734}{10.1098/rsos.160734}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-sutton_Reinforcement_2018}{}}%
+\CSLLeftMargin{24. }
+\CSLRightInline{Sutton RS, Barto AG. Reinforcement {Learning}: {An}
+{Introduction}. second edition edition. Bach F, editor. Cambridge, MA: A
+Bradford Book; 2018. }
+
+\leavevmode\vadjust pre{\hypertarget{ref-thorndike_Animal_1898}{}}%
+\CSLLeftMargin{25. }
+\CSLRightInline{Thorndike EL. Animal intelligence: {An} experimental
+study of the associative processes in animals. The Psychological Review:
+Monograph Supplements. 1898;2: i--109.
+doi:\href{https://doi.org/10.1037/h0092987}{10.1037/h0092987}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-skinner_Behavior_1938}{}}%
+\CSLLeftMargin{26. }
+\CSLRightInline{Skinner BF. The behavior of organisms;: {An}
+experimental analysis,. 1938. }
+
+\leavevmode\vadjust pre{\hypertarget{ref-wismer_Variation_2014}{}}%
+\CSLLeftMargin{27. }
+\CSLRightInline{Wismer S, Pinto AI, Vail AL, Grutter AS, Bshary R.
+Variation in {Cleaner} {Wrasse} {Cooperation} and {Cognition}:
+{Influence} of the {Developmental} {Environment}? Ethology. 2014;120:
+519--531.
+doi:\href{https://doi.org/10.1111/eth.12223}{10.1111/eth.12223}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-triki_Decrease_2018}{}}%
+\CSLLeftMargin{28. }
+\CSLRightInline{Triki Z, Wismer S, Levorato E, Bshary R. A decrease in
+the abundance and strategic sophistication of cleaner fish after
+environmental perturbations. Global Change Biology. 2018;24: 481--489.
+doi:\href{https://doi.org/10.1111/gcb.13943}{10.1111/gcb.13943}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-triki_Biological_2019}{}}%
+\CSLLeftMargin{29. }
+\CSLRightInline{Triki Z, Wismer S, Rey O, Ann Binning S, Levorato E,
+Bshary R. Biological market effects predict cleaner fish strategic
+sophistication. Behavioral Ecology. 2019;30: 1548--1557.
+doi:\href{https://doi.org/10.1093/beheco/arz111}{10.1093/beheco/arz111}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-triki_Brain_2020}{}}%
+\CSLLeftMargin{30. }
+\CSLRightInline{Triki Z, Emery Y, Teles MC, Oliveira RF, Bshary R. Brain
+morphology predicts social intelligence in wild cleaner fish. Nature
+Communications. 2020;11: 6423.
+doi:\href{https://doi.org/10.1038/s41467-020-20130-2}{10.1038/s41467-020-20130-2}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-rescorla_Theory_1972}{}}%
+\CSLLeftMargin{31. }
+\CSLRightInline{Rescorla RA, Wagner ARA. A theory of {Pavlovian}
+conditioning: Variations in the effectiveness of reinforcement and
+non-reinforcement. In: Black AH, Prokasy WF, editors. Classical
+conditioning {II}: Current research and theory. New York:
+Appleton-Century-Crofts; 1972. }
+
+\leavevmode\vadjust pre{\hypertarget{ref-rcoreteam_Language_2021}{}}%
+\CSLLeftMargin{32. }
+\CSLRightInline{R Core Team. R: {A} language and environment for
+statistical computing. Vienna, Austria; 2021. Available:
+\url{https://www.R-project.org/}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-mcfadden_Conditional_1974}{}}%
+\CSLLeftMargin{33. }
+\CSLRightInline{McFadden D. Conditional logit analysis of qualitative
+choice behavior. Frontiers in econometrics. 1974. }
+
+\leavevmode\vadjust pre{\hypertarget{ref-taborsky_Social_2012}{}}%
+\CSLLeftMargin{34. }
+\CSLRightInline{Taborsky B, Oliveira RF. Social competence: An
+evolutionary approach. Trends in Ecology \& Evolution. 2012;27:
+679--688.
+doi:\href{https://doi.org/10.1016/j.tree.2012.09.003}{10.1016/j.tree.2012.09.003}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-bshary_Cooperation_2015}{}}%
+\CSLLeftMargin{35. }
+\CSLRightInline{Bshary R, Oliveira RF. Cooperation in animals: Toward a
+game theory within the framework of social competence. Current Opinion
+in Behavioral Sciences. 2015;3: 31--37.
+doi:\href{https://doi.org/10.1016/j.cobeha.2015.01.008}{10.1016/j.cobeha.2015.01.008}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-varela_Correlated_2020}{}}%
+\CSLLeftMargin{36. }
+\CSLRightInline{Varela SAM, Teles MC, Oliveira RF. The correlated
+evolution of social competence and social cognition. Functional Ecology.
+2020;34: 332--343.
+doi:\href{https://doi.org/10.1111/1365-2435.13416}{10.1111/1365-2435.13416}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-sutherland_Configural_1989}{}}%
+\CSLLeftMargin{37. }
+\CSLRightInline{Sutherland RJ, Rudy JW. Configural association theory:
+{The} role of the hippocampal formation in learning, memory, and
+amnesia. Psychobiology. 1989;17: 129--144.
+doi:\href{https://doi.org/10.3758/BF03337828}{10.3758/BF03337828}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-miller_Magical_1956}{}}%
+\CSLLeftMargin{38. }
+\CSLRightInline{Miller GA. The magical number seven, plus or minus two:
+{Some} limits on our capacity for processing information. Psychological
+review. 1956;63: 81. }
+
+\leavevmode\vadjust pre{\hypertarget{ref-kolodny_Evolution_2014}{}}%
+\CSLLeftMargin{39. }
+\CSLRightInline{Kolodny O, Edelman S, Lotem A. The evolution of
+continuous learning of the structure of the environment. Journal of The
+Royal Society Interface. 2014;11: 20131091--20131091.
+doi:\href{https://doi.org/10.1098/rsif.2013.1091}{10.1098/rsif.2013.1091}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-kawamura_Process_1959}{}}%
+\CSLLeftMargin{40. }
+\CSLRightInline{Kawamura S. The process of sub-culture propagation among
+{Japanese} macaques. Primates. 1959;2: 43--60.
+doi:\href{https://doi.org/10.1007/BF01666110}{10.1007/BF01666110}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-galef_Question_1992}{}}%
+\CSLLeftMargin{41. }
+\CSLRightInline{Galef BG. The question of animal culture. Human Nature.
+1992;3: 157--178.
+doi:\href{https://doi.org/10.1007/BF02692251}{10.1007/BF02692251}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-hirata_SweetPotato_2001}{}}%
+\CSLLeftMargin{42. }
+\CSLRightInline{Hirata S, Watanabe K, Masao K. {``{Sweet}-{Potato}
+{Washing}''} {Revisited}. In: Matsuzawa T, editor. Primate {Origins} of
+{Human} {Cognition} and {Behavior}. Tokyo: Springer Japan; 2001. pp.
+487--508.
+doi:\href{https://doi.org/10.1007/978-4-431-09423-4_24}{10.1007/978-4-431-09423-4\_24}}
+
+\end{CSLReferences}
+
+\nolinenumbers
 

### 2022-03-08 ActCritMCMC.cpp

@@ -6,7 +6,7 @@ ActCrit.cpp
 
 Main file of a project to use data to fit parameter values in a learning model.
 The fit is done using a Markov Chain Monte Carlo. Address of the data file
-and parameter values for the MCMC arer provided to the executable file through 
+and parameter values for the MCMC are provided to the executable file through 
 a JSON file. The output of the executable is either the MCMC data or a data file 
 including predictions from the computational model. 
 
@@ -706,29 +706,6 @@ void abs2rel_abund(vector<cleaner_point> & emp_data, model_param param) {
 	}
 }
 
-//vector<data_point> read_Data(ifstream &marketData) {
-//	// open file
-//	if (!marketData.is_open()) {
-//		std::cerr << "error: unable to open data file\n";
-//		wait_for_return();
-//		exit(EXIT_FAILURE);
-//	}
-//	string header;
-//	getline(marketData,header); // skip header
-//	vector<data_point> data_set; 
-//	data_point input;
-//	for (;;) { // read data
-//		marketData >> input.rel_abund_clean;
-//		marketData >> input.rel_abund_visitors;
-//		marketData >> input.rel_abund_resid;
-//		marketData >> input.prob_Vis_Leav;
-//		marketData >> input.market_exp_success;
-//		data_set.emplace_back(input);
-//		// if end of file
-//		if (marketData.eof()) 	break;
-//	}
-//	return(data_set);
-//}
 
 void initializeChainFile(ofstream &chainOutput,nlohmann::json param){
 	std::string namedir = param["folder"];
@@ -747,15 +724,15 @@ void initializeRoundFile(ofstream& RoundOutput, nlohmann::json param,
 	std::string namedir = param["folder"];
 	namedir.append("round_");
 	namedir.append("gamma_");
-	namedir.append(douts(std::ceil(focals.gamma[0]*100)/100));
+	namedir.append(douts(std::ceil(focals.gamma[0]*1000)/1000));
 	namedir.append("regRew_");
-	namedir.append(douts(std::ceil(focals.negReward[0] * 100) / 100)); 
+	namedir.append(douts(std::ceil(focals.negReward[0] * 1000) / 1000)); 
[…]

### 2022-03-08 analysisMCMC.R

@@ -2,8 +2,7 @@
 ##### parameters in the AC models using data from experiments and the field
 
 ## Libraries
-require(here)
-require(data.table)
+library(data.table)
 library(coda)
 library(ggplot2)
 library(cowplot)
@@ -14,13 +13,18 @@ source(here("loadData.R"))
 library("jsonlite")
 
 # Name of the folders containing the MCMC runs
-scen1<-"MCMCclean_gam_nRew_sca_"
+# scen1<-"MCMCclean_gam_nRew_sca_"
+# scen2<-"MCMCclean_gam_sca_"
+# scen3<-"MCMCclean_Nrew_sca_"
+
+scen1<-"MCMCclean_gam_Nrew_sca_"
 scen2<-"MCMCclean_gam_sca_"
 scen3<-"MCMCclean_Nrew_sca_"
 
+
 # NLables names for the three scenarios
 labels.Scen<-c("both","gam","Nrew")
-labelsPlot.Scen<-c("Full model","Chaining","Penalty")
+labelsPlot.Scen<-c("Full Model","Chaining","Penalty")
 
 ## Load files --------------------------------------------------------------
 
@@ -43,122 +47,16 @@ mcmcList.1<-mcmc.list(do.call(list,lapply(unique(MCMCdata1$seed), function(repli
 
 mcmcList.2<-mcmc.list(do.call(list,lapply(unique(MCMCdata2$seed), function(repli){
   rundata<-MCMCdata2[seed==repli]
-  mcmcRun<-mcmc(rundata[,.(gamma,scaleConst)],thin = thinning)#
+  mcmcRun<-mcmc(rundata[,.(gamma,scaleConst)],thin = thinning)
   return(mcmcRun)
 })))
-
 
 
 mcmcList.3<-mcmc.list(do.call(list,lapply(unique(MCMCdata3$seed), function(repli){
   rundata<-MCMCdata3[seed==repli]
-  mcmcRun<-mcmc(rundata[,.(negReward,scaleConst)],thin =thinning)#
+  mcmcRun<-mcmc(rundata[,.(negReward,scaleConst)],thin = thinning)#
   return(mcmcRun)
 })))
-
-
-
-## Base R plots -----------------------------------------------------------------
-
-
-
-ABC.gamma.time.short<-dcast(MCMCdata1,iteration~seed,value.var = c("gamma"))
[…]

### 2022-03-08 parTOjson.R

@@ -10,12 +10,12 @@ clusterHome<-"/home/ubuntu"
 
 fileName<-"parameters.json"
 
-
-# MCMC fit - Generate json parameter files for -------------------------------------
-
 # name of the scenario for which parameter files will be produces
 # format used for the name: MCMCclean_*parameter1_paramerter2_parameter3.....
-scenario<-"MCMCclean_gam_nRew_sca2"
+scenario<-"MCMCclean_gam_sca"
+
+
+# MCMC fit - Generate json parameter files for -------------------------------------
 
 # for MCMC
 param_mcmc<-list(totRounds=10000, # Number of rounds in the learning model
@@ -33,10 +33,9 @@ param_mcmc<-list(totRounds=10000, # Number of rounds in the learning model
                  chain_length=100000, # Chain length
                  init=c(0.05,0.05,0,0,30), # Initial values for each of the parameters
                  # alphaA,AlphaC, Gamma, NegRew, scalConst
-                 pertScen = c(FALSE,FALSE,TRUE,TRUE,TRUE), # boolean controlling which
+                 pertScen = c(FALSE,FALSE,FALSE,TRUE,TRUE), # boolean controlling which
                  # parameter is perturbed
                  MCMC =1, # run chain=1, run prediction for one parameter set = 0
-                 data="clean", # use all cleaner data = 1, use data by reef sites
                  nRep=1, # number of replicate simulations
                  Group = FALSE, # grouped data according to social competence
                  # from triki et al. 2020
@@ -102,7 +101,7 @@ for(seed in 1:5){
 
 ## Using the mode of the marginal posterior distributions
 
-scenario<-"MCMCclean_Nrew_sca"
+scenario<-"MCMCclean_nRew_sca"
 
 
 # Load MCMC data
@@ -124,46 +123,61 @@ names(modeNegrew)<-c("NR")
 densScal<-density(MCMCdata$scaleConst)
 modescal<-densScal$x[densScal$y==max(densScal$y)]
 
-# parameter files 
+# parameter file 
 param_pred<-list(totRounds=10000,ResReward=1,VisReward=1,
             ResProbLeav=0,scenario=0, inbr=0,outbr=0,forRat=0.0,
[…]

### 2022-03-08 predictions.R

@@ -16,9 +16,9 @@ source(here("aesth_par.R"))
 source(here("../R_files/posPlots.R"))
 
 # Folder where the three models are
-# scen1<-"MCMCclean_gam_Nrew_sca"
-# scen2<-"MCMCclean_gam_sca"
-# scen3<-"MCMCclean_Nrew_sca"
+# scen1<-"MCMCclean_gam_Nrew_sca_"
+# scen2<-"MCMCclean_gam_sca_"
+# scen3<-"MCMCclean_Nrew_sca_"
 
 # Get file with the predictions using the mode of the posterior
 predfileMode.both<-grep(".txt",grep("round",list.files(here("Simulations",
@@ -232,19 +232,7 @@ scatter.obs.pred.both<-ggplot(data=fieldatabyLocSamps.both,
   guides(colour=guide_legend(ncol=3,title="",override.aes = list(size=1)))
 
   
-  # ggplot(data = fieldatabyLoc.both,aes(y=market_binomial_data,x=probvisitor.pred))+
-  # geom_point(data = fieldatabyLocSamps.both,aes(x=probvisitor.pred,y=probVisi.data),
-  #            color='grey')+
-  # geom_point(size=4)+ylim(0.4,0.9)+xlim(0.4,0.9)+
-  # geom_abline(slope=1)+ylab("Observed")+xlab("Predicted")+
-  # ggtitle("")+
-  # theme_classic()+
-  # theme(plot.title = element_text(hjust = 0.5),
-  #     axis.title.x = element_text(size=axisSize),axis.title.y = element_text(size=axislabSize),
-  #     axis.text = element_text(size=14))+
-  # geom_text(x = 0.8, y = 0.85, label = expression(y==x), parse = TRUE,size=3)+
-  # geom_text(x = 0.8, y = 0.5, label = deparse(bquote(R^2==.(round(rsqr.both.McFadden,4)))), 
-  #           parse = TRUE,size=3)
+  
 
 # Panel future reward contour
 cont.obs.pred.gam<- ggplot(data = FIAinterpData.gam,aes(x=rel.abund.cleaners,y=prob.Vis.Leav,
@@ -252,7 +240,7 @@ cont.obs.pred.gam<- ggplot(data = FIAinterpData.gam,aes(x=rel.abund.cleaners,y=p
   geom_raster(interpolate = TRUE) +  
   scale_fill_gradientn(limits=c(0.3,1),colours= myPalette(100))+theme_classic()+
[…]

### 2022-03-08 manuscript_PLOS/manuscript_PLOS.Rmd
Add last referece and URL of th repo in the manuscript

@@
     email: andresqp@gmail.com
-    affiliation: Institute of Biology, University of Neuchatel
+    affiliation: a
     corresponding: andresqp@gmail.com
@@
     email: zegni.triki@gmail.com
-    affiliation: Department of Zoology, Stockholm University
+    affiliation: b
   - name: Redouan Bshary
@@
 address:
-  - code: Institute of Biology, University of Neuchatel
-    address: Institute of Biology, Rue Emile-Argand 11, 2000-CH Neuchatel, Switzerland
-  - code: Department of Zoology, Stockholm University
-    address: Department of Zoology, Svante Arrheniusväg 18 B,  106 91 Stockholm, Sweden,
+  - code: a
+    address: Institute of Biology, University of Neuchatel, Rue Emile-Argand 11, 2000-CH Neuchatel, Switzerland
+  - code: b
+    address: Department of Zoology, Stockholm University, Svante Arrheniusväg 18 B,  106 91 Stockholm, Sweden,
 abstract: |
@@
 This between variation in performance, and primates' known cognitive abilities
-$\color{red}{\text{ref}}$, shows that performance in the task
+[@reader_Evolution_2001], shows that performance in the task
 cannot be readily explained by classifying species as having high and 
@@
 in R [@rcoreteam_Language_2021]. All codes are accessible at 
-$\color{red}{\text{include citation}}$
+<https://github.com/andreseqp/learnDatamodel>
 

### 2022-03-08 manuscript_PLOS/manuscript_PLOS.tex
Add last referece and URL of th repo in the manuscript

@@
 \newcommand{\getAff}[1]{
-  \getIndex{#1}{Institute of Biology, University of Neuchatel,Department
-of Zoology, Stockholm University}
+  \getIndex{#1}{a,b}
 }
@@
 \\
-Andrés E. Quiñones\textsuperscript{\getAff{Institute of Biology,
-University of Neuchatel}}\textsuperscript{*},
-Zegni Triki\textsuperscript{\getAff{Department of Zoology, Stockholm
-University}},
+Andrés E. Quiñones\textsuperscript{\getAff{a}}\textsuperscript{*},
+Zegni Triki\textsuperscript{\getAff{b}},
 Redouan Bshary\textsuperscript{\getAff{Institute of Biology, University
@@
 \bigskip
-\textbf{\getAff{Institute of Biology, University of Neuchatel}}Institute
-of Biology, Rue Emile-Argand 11, 2000-CH Neuchatel, Switzerland\\
-\textbf{\getAff{Department of Zoology, Stockholm University}}Department
-of Zoology, Svante Arrheniusväg 18 B, 106 91 Stockholm, Sweden,\\
+\textbf{\getAff{a}}Institute of Biology,University of Neuchatel ,Rue
+Emile-Argand 11, 2000-CH Neuchatel, Switzerland\\
+\textbf{\getAff{b}}Department of Zoology, Stockholm University, Svante
+Arrheniusväg 18 B, 106 91 Stockholm, Sweden,\\
 \bigskip
@@
 {[}15{]}. This between variation in performance, and primates' known
-cognitive abilities \(\color{red}{\text{ref}}\), shows that performance
-in the task cannot be readily explained by classifying species as having
-high and low cognitive abilities. Instead, this between species
-variation suggests that solving the ephemeral reward task requires a set
-of cognitive mechanisms that are not present in all the tested taxa, or
-were not used under the experimental set-up.
+cognitive abilities {[}\textbf{reader\_Evolution\_2001?}{]}, shows that
+performance in the task cannot be readily explained by classifying
+species as having high and low cognitive abilities. Instead, this
+between species variation suggests that solving the ephemeral reward
+task requires a set of cognitive mechanisms that are not present in all
+the tested taxa, or were not used under the experimental set-up.
 
@@
 in R {[}32{]}. All codes are accessible at
-\(\color{red}{\text{include citation}}\)
+\url{https://github.com/andreseqp/learnDatamodel}
 

### 2022-03-08 parTOjson.R

@@ -64,36 +64,19 @@ for(seed in 1:5){
   param_mcmc$init<-c(0.05,0.05,runif(1,max = 0.6),runif(1,max = 2,min = 0),
                      runif(1,max = 300,min = 5))
   param_mcmc$init[3:4]<-param_mcmc$init[3:4]*param_mcmc$pertScen[3:4]
-  ##runif(1,max = 50,min = 5))
   param_mcmc$seed <- seed
   fileName<-paste("parametersMCMC_",seed,".json",sep="")
   outParam<-toJSON(param_mcmc,auto_unbox = TRUE,pretty = TRUE)
   if(file.exists(paste(param_mcmc$folderL,fileName,sep = ''))){
     currFile<-fromJSON(paste(param_mcmc$folderL,fileName,sep = ''))
     if(sum(unlist(currFile)!=unlist(param_mcmc))>0){
-      # warning("You are erasing old files!! n\ Check first!!!",immediate. = TRUE)
-      # print("OLD value")
-      # print(unlist(currFile)[unlist(currFile)!=unlist(param)])
-      # print("NEW value")
-      # print(unlist(param)[unlist(currFile)!=unlist(param)])
-      # ans<-readline("Want to continue?")
-      # if(substr(ans, 1, 1) == "y"){
       write(outParam,paste(param_mcmc$folderL,fileName,sep = "/"))
-      # jobfile(param$folderL,listfolders[i],jobid = j)
-      # }
-      # else{
-      #   jobfile(param$folderL,listfolders[i])
-      # }
+      
     }
   }else{
     write(outParam,paste(param_mcmc$folderL,fileName,sep = ""))
-    # jobfile(param$folderL,listfolders[i],jobid = j)
   }
 }
-# Uncomment for running simulations directly through R:
-# system(paste(exedir,
-#   gsub("\\","/",paste(param$folder,fileName,sep="\\"),fixed=TRUE)
-#   ,sep = " "))
 
 # Predicted values -------------------------------------------------------------
 
@@ -153,7 +136,7 @@ param_pred_samp$folder<-param_pred_samp$folderL
 
 ## Use modes for predictions
 param_pred$init[c(3,4,5)]<- c(modeGamma$gamma,modeNegrew$NR,modescal)
-                              # modeNegrew$NR,modescal)
+                            
 
 nsamples<-100
 
@@ -178,23 +161,10 @@ for(i in 1:nsamples){
[…]

### 2022-07-20 manuscript_BE/Title_page.Rmd
New version of the manuscript

---
title: | 
 \large \textbf{Title:} Computational models reveal how cleaner fish adjust decisions in a biological market
subtitle: |
  \normalsize \textbf{Short title:} Cleaner fish cognitive mechanisms in a biological market
author: 
  - name: Andrés E. Quiñones 
    email: andresqp@gmail.com
    affiliation: a
    corresponding: andresqp@gmail.com 
    fulladress: Rue Emile-Argand 11, CH-2000, Neuchatel, Switzerland, tel. +41325586486
  - name: Zegni Triki
    affiliation: 
      - a
      - b
  - name: Redouan Bshary
    affiliation: a
address:
  - code: a
    address: Institute of Biology, University of Neuchatel, Neuchatel, Switzerland
  - code: b
    address: Department of Zoology, Stockholm University, Stockholm, Sweden
output:    
  pdf_document:
    keep_tex: true
    latex_engine: xelatex
    template: template.latex
---

## Funding
This work was supported by the Swiss National Science Foundation grants
(grants number: 31003A_153067/1, 310030B_173334/1) to R.B.

## Acknowledgements
ZT and RB kindly thank the staff of Lizard Island Research Station, 
Dominique Roche, Sharon Wismer, Olivia Rey,Sandra Ann Binning, 
Elena Levorato and William McNeely for their field support. 
AQ thanks Florian Hartig for statistical advice, and the cluster of the 
Institute of Computer Science of the University of Neuchâtel (IIUN) for the
computing resources provided.

### 2022-07-20 manuscript_BE/Title_page.tex
New version of the manuscript

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={ Computational models reveal how cleaner fish adjust decisions in a biological market},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\title{\large \textbf{Title:} Computational models reveal how cleaner
fish adjust decisions in a biological market}
\usepackage{etoolbox}
\makeatletter
\providecommand{\subtitle}[1]{% add subtitle to \maketitle
  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
}
\makeatother
\subtitle{\normalsize \textbf{Short title:} Cleaner fish cognitive
mechanisms in a biological market}
\date{}

\usepackage{forarray}
\usepackage{xstring}
\newcommand{\getIndex}[2]{
  \ForEach{,}{\IfEq{#1}{\thislevelitem}{\number\thislevelcount\ExitForEach}{}}{#2}
}

\newcommand{\getAff}[1]{
  \getIndex{#1}{a,b}
}

\begin{document}
\maketitle
\begin{flushleft}

Andrés E. Quiñones\textsuperscript{\getAff{a}}\textsuperscript{*},
Zegni Triki\textsuperscript{\getAff{a}, \getAff{b}},
Redouan Bshary\textsuperscript{\getAff{a}}\\
\bigskip
\textbf{\getAff{a}}Institute of Biology, University of Neuchatel,
Neuchatel, Switzerland\\
\textbf{\getAff{b}}Department of Zoology, Stockholm University,
Stockholm, Sweden\\
\bigskip
* Corresponding author: \href{mailto:andresqp@gmail.com}{\nolinkurl{andresqp@gmail.com}}, Rue
Emile-Argand 11, CH-2000, Neuchatel, Switzerland, tel. +41325586486\\
\end{flushleft}

\hypertarget{funding}{%
\subsection{Funding}\label{funding}}

This work was supported by the Swiss National Science Foundation grants
(grants number: 31003A\_153067/1, 310030B\_173334/1) to R.B.

\hypertarget{acknowledgements}{%
\subsection{Acknowledgements}\label{acknowledgements}}

ZT and RB kindly thank the staff of Lizard Island Research Station,
Dominique Roche, Sharon Wismer, Olivia Rey,Sandra Ann Binning, Elena
Levorato and William McNeely for their field support. AQ thanks Florian
Hartig for statistical advice, and the cluster of the Institute of
Computer Science of the University of Neuchâtel (IIUN) for the computing
resources provided.

\end{document}

### 2022-07-20 manuscript_BE/manuscript_BE.Rmd
New version of the manuscript

--- 2022-03-08 manuscript_1.0/manuscript_word.Rmd
@@
 ---
-title: Field and experimental data together with computational 
-  models reveal how cleaner fish adjust decisions  in a biological market
-author:
-- Andrés E. Quiñones^[Institute of Biology, University of Neuchâtel, Neuchâtel, Switzerland
-  - andresqp@gmail.com]
-date: "`r format(Sys.time(), '%B %d, %Y')`"
+title: | 
+  \large \textbf{Title:} Computational models reveal how cleaner fish adjust decisions in a biological market
+subtitle: |
+  \normalsize \textbf{Abbreviated title:} Cleaner fish cognitive mechanisms in a biological market
+# date: "`r format(Sys.time(), '%B %d, %Y')`"
+# author: 
+#   - name: Andrés E. Quiñones 
+#     email: andresqp@gmail.com
+#     affiliation: a
+#     corresponding: andresqp@gmail.com 
+#     #, Rue Emile-Argand 11, CH-2000, Neuchatel, Switzerland. +41 32 718 31 24
+#   - name: Zegni Triki
+#     affiliation: a
+#     affiliation: b
+#   - name: Redouan Bshary
+#     affiliation: a
+# address:
+#   - code: a
+#     address: Institute of Biology, University of Neuchatel, Neuchatel, Switzerland
+#   - code: b
+#     address: Department of Zoology, Stockholm University, Stockholm, Sweden
 output:
-  word_document: default
+   pdf_document:
+    keep_tex: true
+    latex_engine: xelatex
+    template: template.latex
 fig_caption: yes
 fontsize: 12pt
-header-includes:
-- \usepackage{float}
-- \usepackage{setspace}\doublespacing
-- \linespread{2}
-- \usepackage{lineno}
-- \linenumbers
-- \newcommand{\beginsupplement}{ \setcounter{table}{0} \renewcommand{\thetable}{S\arabic{table}}
-  \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}}
 keep_tex: yes
-linespread: 2
 bibliography: Cleanerlearning.bib
-style: M:\Zotero\styles\behavioral-ecology-and-sociobiology.csl
+style: M:\Zotero\styles\behavioral-ecology.csl
 spacing: double
@@
 We argue that the combination of computational models with data is a powerful tool to infer the mechanistic underpinnings of cognitive performance.
-author_summary: |
-  Performance in behavioural experiments is often used to assess the cognitive abilities of animals.
-However, animals can get to the same outcome in alternative ways.
-Thus, the outcome of the experiments does not tell us how animals achieve their performance.
-In order to overcome this limitation, we used a set of computational models, which provide predictions on how alternative cognitive mechanisms perform in the face of varying environmental conditions, and compare their predictions to performance data from individuals that experienced different conditions throughout their life.
-Our study system is the cleaner fish *Labroides dimidiatus*, a coral reef fish that feeds off ectoparasites and dead tissue from the skin of other reef fishes.
-Cleaner fish often have to choose among alternative clients seeking their cleaning service, and the optimal choice is often hard to achieve.
-Our performance experiments mimic the natural choices the cleaner fish make.
-The combination of experiments and computational models points to cleaner fish abilities to account for the future effect of their choices by estimating the long term expected value of those choices.
-Estimating long term value is a mechanism involved in human foresight.
-keywords: learning, behaviour, cleaners, bayesian statisitics
+lay_summary: |
+  Cleaner fish eat ectoparasites off other fishes, so-called clients.
+It regularly happens that two clients seek a cleaner's service simulatenously.
+Cleaners benefit from prioritising clients unwilling to wait, so they can feed on those willing to wait.
+To make the right choice, cleaners must somehow “look” into the future to anticipate consequences of current choices.
+By combining a learning model with data, we show that cleaners estimate the long-term value of their actions rather than using simpler heuristics.
+Estimating long-term value is a mechanism involved in human foresight.
+header-includes: |
+  ```{=latex}
+  \usepackage{float}
+  \usepackage{graphicx}
+  \usepackage{booktabs}
+  \linespread{2}
+  \usepackage{lineno}
+  \linenumbers
+  \usepackage{setspace}\doublespacing
+  \newcommand{\beginsupplement}{ \setcounter{table}{0}     \renewcommand{\thetable}{S\arabic{table}}\setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}}
+  \providecommand{\keywords}[1]{\textbf{\textit{Keywords---}} #1}
+  ```
+editor_options:
+  markdown:
+    wrap: 80
 ---
+
+```{=latex}
+\keywords{learning, behavior, cleaners, bayesian statisitics, behavioral mechanisms}
+```
+
+\newpage
 
@@
 
-Often alternative cognitive mechanisms yield similar behaviour and/or cognitive
+Often alternative cognitive mechanisms yield similar behavior and/or cognitive
 performances. This poses a problem for disentangling the mechanistic 
-underpinnings of behaviour. This is particularly clear in research aimed at
+underpinnings of behavior. This is particularly clear in research aimed at
 discovering between species variation in *higher* cognitive abilities; or 
@@
 abilities believed to be uniquely human. For instance, when researchers 
-try to find *mental time travel-like* behaviour, they usually come up with 
-clever experiments to show the behaviour displayed requires inferences made 
-through past events[@dally_Foodcaching_2006]. However, they often face the
+try to find *mental time travel-like* behavior, they usually come up with 
+experiments to show the behavior displayed requires inferences made 
+through past events [@dally_Foodcaching_2006]. However, they often face the
 challenge of alternative scenarios where simpler explanations, 
 like classic associative learning, can bring about the 
-observed behavioural outcome [@suddendorf_Evolution_2007]. Similarly, attempts 
+observed behavioral outcome [@suddendorf_Evolution_2007]. Similarly, attempts 
 to demonstrate the presence of *theory of mind* in non-human animals 
 face objections justified by alternative mechanisms underpinning 
-similar behavioural results [@heyes_Theory_1998]. 
+similar behavioral results [@heyes_Theory_1998]. 
 Such controversies are usually settled by using the principle 
@@
 Lloyd Morgan’s cannon, which states that the simpler explanation (mechanism)
-should be accepted. Ideally, however, alternative hypotheses should be evaluated 
-in light of their explanatory power. One potential dimension that could allow
-the variation necessary among distinct cognitive mechanisms is environmental
-variation. Controlled laboratory conditions often mask between and within 
-species variation that arises among different environments. Thus, if 
-predictions from the alternative mechanisms depend on environmental 
-conditions, it is possible to assess their relative explanatory power 
-by performing cognitive test in the context of
-different environmental conditions.
+should be accepted. Ideally, alternative hypotheses should be evaluated 
+in light of their explanatory power.
+
+<!-- If alternative mechanisms predict different  -->
+<!-- outcomes when exposed to different contexts, the variation arising from -->
+<!-- varying the context could open up a way to infer which mechanism is used.  -->
+<!-- Controlled laboratory conditions often mask between and within  -->
+<!-- species variation that arises among different environmental contexts. Thus, if  -->
+<!-- predictions from the alternative mechanisms depend on environmental  -->
+<!-- conditions, it is possible to assess their relative explanatory power  -->
+<!-- by performing cognitive tests in the context of different  -->
+<!-- environmental conditions.  -->
+
+Learning is a key overarching cognitive mechanism that allows 
+individuals to associate rewards with environmental stimuli 
+and thus behave adaptively [@staddon_Adaptive_2016;@shettleworth_Cognition_2009]. 
+Associative learning, in particular, exists in all major vertebrate taxa, 
+and in many invertebrates as well [@heyes_Simple_2012;@macphail_Brain_1982; 
+@staddon_Adaptive_2016; @behrens_Associative_2008]. 
+Associative learning is not homogeneous throughout its taxonomic distribution, 
+rather there are differences across and within species 
+[@shettleworth_Cognition_2009;@sih_Linking_2012]. So presumably, 
+the mechanistic underpinnings of learning have been modified by 
+natural selection [@marler_Species_1989].
+
+One way to formalize the alternative mechanistic underpinnings of 
+associative learning is to develop quantitative models of learning 
+processes. This approach, which started within experimental psychology 
+[@staddon_Adaptive_2016;@brandon_Computational_2002], has been very fruitful 
+in disentangling the mechanistic structure of cognitive systems. 
+More recently, the development of reinforcement learning theory 
+[@sutton_Reinforcement_2018], has allowed to 
+evaluate the empirical support for alternative mechanistic hypotheses by
+providing quantitative predictions which are amenable to statistical tests
+[@farashahi_Learning_2020;@farashahi_Featurebased_2017]. Interestingly, these 
+learning models not only have received support from behavioral data, but also 
+are consistent with the current view on reward processing in the brain 
+[@schultz_Neuronal_2015].
 
@@
 law of supply and demand, when individuals have some degree of partner choice
-[@noe_Biological_1995]. Supply and demand conditions, which typically 
+[@noe_Biological_1995a]. Supply and demand conditions, which typically 
 depend on the abundance of the species involved, certainly vary in time 
-and space. Therefore, natural selection should favour the ability 
-to flexibly adjust decisions and behavioural output to 
-current market conditions. Indeed, such adjustments have been repeatedly 
-documented [@axen_Signalling_1996]. In animals, an obvious general candidate 
-mechanism for the strategic adjustment is the cognitive machinery. However, 
-it is not clear which cognitive mechanisms allow individuals to adjust their 
-behaviour to the varying conditions. More specifically the question arises 
-to what extent mechanisms beyond basic associative learning may be involved.
-
-One example of strategic adjustment in a biological market is the marine
+and space. Therefore, natural selection should favor the ability 
+to flexibly adjust decisions and behavioral output to 
+current market conditions. Indeed, such adjustments have been 
+documented [@axen_Signalling_1996]. One example of strategic 
+adjustment in a biological market is the marine
 cleaning mutualism involving the cleaner fish *Labroides dimidiatus* and
-'client' fish. Client fish seek cleaner fish services at their territory 
+'client' fishes. Client fishes seek cleaner fish services at their territory 
 (so-called “cleaning station”) and offer themselves as food patches 
@@
 either “visitors” or “residents”, respectively. During cleaning interactions, 
-a cleaner fish often face a choice between a visitor and a resident client 
+a cleaner fish often faces a choice between a visitor and a resident client 
 seeking its cleaning services simultaneously. Visitors have the option 
@@
 visitors service priority in a field study in the Red Sea
-[@bshary_Cleaner_2001].
+[@bshary_Cleaner_2001a]. Furthermore, in a lab based paradigm, design 
+to mimic the resident-visitor choice (ephemeral reward task), cleaners learned 
+to prefer the cue associated with the epheral food source (visitor) and
+hence accessed both food sources, obtaining 
+double the amount of food [@bshary_Asymmetric_2002].
+However, further exploration revealed that not all cleaner fish 
+manage to develop a preference for the ephemeral option 
+in the lab [@triki_Decrease_2018]. Over the last decade, over a hundred 
+wild-caught cleaner fish have been tested
+in the exact same paradigm of the ephemeral reward 
+task [@salwiczek_Adult_2012;@wismer_Variation_2014;@triki_Decrease_2018;
+@triki_Biological_2019;@triki_Brain_2020]. These fish often come from 
+different reef locations. Investigation of the local 
+eco-sociological conditions revealed that cleaner and client 
+fish population densities have a substantial impact on cleaner fish 
+performance in the task. Cleaner fish from reef sites with relatively 
+low densities were more likely to fail at solving the task 
+[@triki_Biological_2019;
+@triki_Decrease_2018; @wismer_Variation_2014]. This intra-specific variation
+is unlikely due to local genetic adaptation, because cleaner
+fish are open water spawners and the environmental conditions can vary within 
+the lifespan of a fish.
 
-When researchers aimed at testing wild-caught cleaner fish, as 
-well as individuals from other species, abilities 
-to prioritize visitor over resident clients in a lab-based paradigm, 
-they used Plexiglas plates of different colours and shapes offering the same 
-amount of food as surrogates for visitor and resident clients.
-One plate is made to behave like a resident, i.e. it remains until 
-the cleaner fish has eaten off it. The other plate was made to behave 
-like a visitor, i.e. it is removed if not inspected first. 
-This laboratory paradigm originally inspired by the cleaning market 
-of cleaner fish is more generally referred as the ephemeral reward task. 
-Individuals are assessed in their capacity to develop a preference for the 
-ephemeral option, which gives them access to two reward units.
-Cleaners learned to prefer the visitor plate and
-hence obtained the double amount of food [@bshary_Asymmetric_2002].
-Furthermore, adult cleaner fish outperformed various primates as well as rats and
-pigeons in this original version of the ephemeral reward task
-[@salwiczek_Adult_2012; @zentall_Early_2017]; yet the African grey
-parrots solve this task as well [@pepperberg_Can_2014]. 
-This between variation in performance, and primates' known cognitive abilities
-$\color{red}{\text{ref}}$, shows that performance in the task
-cannot be readily explained by classifying species as having high and 
-low cognitive abilities. Instead, this between species variation suggests
-that solving the ephemeral reward task requires a set of cognitive 
-mechanisms that are not present in all the tested taxa, or were not used 
-under the experimental set-up.
-
-Recent research on the cognitive abilities needed to solve the ephemeral 
-reward task has used a broad approach as proposed by Shettleworth 
-[@shettleworth_Cognition_2009], who defined cognition as including 
-all ways in which animals acquire information 
-through the senses, process, retain and decide to act on it. 
-Indeed, perception of relevant cues is of major importance 
-for individual performance. For example, some animals find relevant 
-information in the plates  [@wismer_Cuebased_2019] while others find 
-it in the food [@pretot_Comparative_2021; @pretot_Comparing_2016]. 
-However, identifying cues as salient is not the only challenge 
-of the ephemeral reward task, as revealed by proximate learning models. 
-Such models allow varying the cognitive tool kit and evaluating 
-which minimal kit is necessary to solve 
-the task at hand (e.g. [@dubois_Model_2021]). Applied to the ephemeral 
-reward task, learning models showed that basic reinforcement learning does 
-not suffice to solve the ephemeral reward task [@prat_Modelling_2022;
-@quinones_Reinforcement_2019]. 
-This is particularly so when models assume the more complex natural 
-situation in which cleaner fish face not only resident-visitor pairs but also 
-visitor-visitor and resident-resident pairs, as well a resident alone or 
-a visitor alone. To be able to give visitors priority over residents, 
+Mechanistic models explicitly designed to mimic the ephemeral reward task 
+have shown that the simplest form of associative learning 
+(operant conditioning) cannot account for a solution to 
+the ephemeral reward task [@prat_Modelling_2022;
+@quinones_Reinforcement_2019]. Operant conditioning is 
+a form of associative learning where individuals use short term 
+reward to associate and choose actions. Such models allow varying 
+the cognitive tool kit and evaluating which minimal kit is necessary 
+to solve the task at hand (e.g. @dubois_Model_2021). 
+To be able to give visitors priority over residents, 
 cleaners need to be able to assess a client’s value separately for the 
@@
 one stimulus differently alone from compound versions of it has been termed 
-configurational learning, chunking, 
-or segmentation (see references in [@prat_Modelling_2022]).
-
+configurational learning, chunking, or 
+segmentation (see references in @prat_Modelling_2022). 
 In addition to configurational learning, cleaners also need to account for 
 the future consequences of current decisions. In the model by 
-Quiñones *et al.* [@quinones_Reinforcement_2019], this could be achieved in 
+@quinones_Reinforcement_2019, this could be achieved in 
 two non-mutually exclusive ways: through low temporal discounting of 
@@
 through perceiving a visitor client leaving as psychological punishment 
-(i.e. as a negative reinforcer). Low temporal discounting is when 
+(i.e. as a negative reinforcer). Chaining is when 
 individuals include in their valuation of an action the reward effects 
@@
 a complex adaptation [@suddendorf_Evolution_2007]. On the other hand,
-using client behaviour as a negative reinforcer is, in principle, 
-easier to implement. Negative reinforcement is part of the ubiquitous 
-learning mechanism termed operant conditioning [@thorndike_Animal_1898; 
-@skinner_Behavior_1938]. Thus, the standard logic of 
+using client behavior as a negative reinforcer is, in principle, 
+easier to implement. Thus, the standard logic of 
 Lloyd Morgan’s cannon demands that operant conditioning as the simpler 
@@
 
-Over the last decade, our team tested over a hundred wild-caught 
-cleaner fish in the exact same paradigm of the ephemeral reward 
-task [@salwiczek_Adult_2012;@wismer_Variation_2014;@triki_Decrease_2018;
-@triki_Biological_2019;@triki_Brain_2020]. These fish often come from 
-different reef locations around the study field site at Lizard Island, 
-Great Barrier Reef in Australia. Further investigation of the local 
-eco-sociological conditions revealed that cleaner and client 
-fish population densities have a substantial impact on cleaner fish 
-performance in the task. Cleaner fish from reef sites with relatively 
-low densities were more likely to fail at solving the task [@triki_Biological_2019;
-@triki_Decrease_2018; @wismer_Variation_2014]. The explanation for this pattern
-is twofold. First, low cleaner fish population densities imply 
-low supply and high demand for cleaning services. 
-Under such conditions, there are fewer occasions under 
-which failing to give priority to a visitor translates to an empty 
-cleaning station. Second and also related to the state of the cleaning market,
-visitor clients at low cleaner fish population densities 
-are less likely to exert their partner choice options 
-and are hence more likely to wait for inspection if not given cleaning 
-priority [@triki_Brain_2020]. In the absence of partner choice 
-cleaner fish should not give priority to visitors any more.
-
-The interplay between the underlying cognitive machinery and 
-local ecological conditions apparently generate the documented variable 
-performance among individuals of the same species. 
-Our approach of fitting the computational model to the empirical data on 
-fish densities and cleaner fish censuses and performance
-in the ephemeral reward task aimed at: (i), determining which 
+In here we used the field and experimental data to fit the parameters of 
+a reinforcement learning model to infer  the 
+cognitive mechanism that cleaners use in their interaction with clients. 
+Specifically, our approach of fitting the computational model 
+to the empirical data aimed at: (i), determining which 
 mechanism cleaner fish use to incorporate future consequences of current 
@@
 yields optimal performance patterns. Relying on the logic of 
-biological market theory, we predicted 
-that appropriate performance is to show a low preference for visitors under low
+biological market theory, we predicted that appropriate performance 
+is to show a high preference for visitors only under high
 local cleaner-to-client ratio.
@@
 they update the probability of making that same choice. The update is
-based on the difference between the expected reward and the obtained
-reward (prediction error) [@sutton_Reinforcement_2018; 
-@rescorla_Theory_1972]. Given the new information, the update is carried
-in the direction that leads to more reward being obtained, given
+based on the difference between the expected value and the obtained
+reward - the prediction error ($\delta_t$) - [@sutton_Reinforcement_2018; 
+@rescorla_Theory_1972]. Formally, the prediction error is given by
+
+\begin{equation}
+\label{eq:delta}
+\delta_t = R_t -  V_t(S_t) + \gamma V_t(S_{t+1}) ,
+\end{equation}
+
+where $R_t$ is the sum different reward sources at time $t$; 
+$V_t(S_t)$ is the estimated value at time $t$ of the the state faced by the agent 
+at time $t$; similarly $V_t(S_{t+1})$ is the estimated value of the state
+to come in the following time-step, $\gamma$ is the discount factor for
+future rewards. When the estimated value of the current state ($V_t(S_t)$) 
+is equal to the sum of short-term ($R_t$) and future discounted reward 
+($\gamma V_t(S_{t+1})$) learning stops for that state. If $\gamma = 0$ 
+the estimates made by the agent only capture short-term reward. We assume 
+short-term reward to two components: positive reward determined by the 
+amount of food obtained from cleaning a client; and negative reward triggered
+when by a client leaving the station without being cleaned. Formally, 
+we let total reward be given by $R_t=P_t - \eta_t$. Where $\eta$ is a parameter
+of the model that determines the the size of the negative reward triggered by
+unattended clients leaving the station.
+
+The prediction error (Eq. \ref{eq:delta}) is used to update the value of each one
+of the states the agent faces, as well as the preference for the 
+resident and visitor options. The value update is simple the product of the 
+prediction error and the parameter for the speed of learning 
+($\Delta V(S_t)=\alpha \delta_t$). The change in preference between the resident 
+and visitor is given by $\Delta (\theta_v-\theta_r)_t=\alpha\delta_t2(1-\pi_v)$,
+where $\theta_i$ represent the preference for one of two options and the 
+difference captures the total change relative to one another; 
+$\pi_v$ corresponds to the current probability of choosing the visitor. 
+$p_i$ is determined by applying the logistic function to the difference in
+preferences between the two mutually exclusive options 
+($\pi_v=\frac{1}{1+e^{-(\theta_v-\theta_r)}}$). This amounts
+to a preference update that is carried in the direction that 
+leads to more reward being obtained, given
 the new information. In the long run, the probability of choosing a visitor 
@@
 cleaning station when made to wait. Further details of the model 
-implementation can be found in Quiñones *et al* [@quinones_Reinforcement_2019].
+implementation can be found in @quinones_Reinforcement_2019.
 
@@
 cleaning interaction. As $\gamma$ increases, individuals include more the
-reward obtained from the subsequent choices. That amounts to calculating
+reward obtained from the subsequent choices. That amounts to estimating
 and using for decision making the future expected rewards of an action (chaining).
 Second, $\eta$ measures how much individuals include in their reward the
-fleeing behaviour of visitors as a negative component (penalty). Both of
+fleeing behavior of visitors as a negative component (penalty). Both of
 these parameters allow individuals to use in their estimates the future
@@
 and their clients at a given site in 
-a given year, Triki *et al.* [@triki_Biological_2019] used a series of ten 
+a given year, @triki_Biological_2019 used a series of ten 
 transects of $30m$ each. Observers swam along the transect lines placed on 
@@
 on a width of $5m$, and then on the 
-return individuals of small-bodied fish species ($TL < 10 cm$) \
+return individuals of small-bodied fish species ($TL < 10 cm$)
 on a width of $1 m$
-(see Triki et al. 2018 for further details on fish censuses data collection). 
+(see @triki_Decrease_2018 for further details on fish censuses data collection). 
 We then scaled the counts of cleaner fish, small-bodied, 
 and  large-bodied  clients fish densities per $100 m^2$. 
-From the study by Triki *et al* [@triki_Biological_2019] 
+From the study by @triki_Biological_2019 
 cleaner fish and large-bodied client populations densities were 
@@
 cleaner-client cleaning interactions. There were videos from eight 
-cleaners per site/year of a duration of $30 min$ each. Triki *et al* 
+cleaners per site/year of a duration of $30 min$ each. Triki et al. 
 extracted information from every event wherein a visitor client 
@@
 housed all captured cleaners individually in glass aquaria 
-( $62cm \times 27cm \times 37 cm$ ) and provided them 
+($62cm \times 27cm \times 37 cm$) and provided them 
 with PVC pipes ($10 cm \times 1 cm$) as shelters. 
@@
 forced cleaner fish to learn to give service priority to the visitor plate 
-based solely on the behaviour-cue of the plates rather than size-cue 
-[@wismer_Cuebased_2019]. Triki *et al.* [@triki_Biological_2019;@triki_Brain_2020] 
+based solely on the behavior-cue of the plates rather than size-cue 
+[@wismer_Cuebased_2019]. Triki et al. [-@triki_Biological_2019;@triki_Brain_2020] 
 tested the fish for a maximum of 200 trials with 20 trials a day, 10 trials 
@@
 they passed to a reversal version of the task where the roles of the 
-visitor/resident Plexiglas plates were swapped (see Triki et al. 2019, 2020). 
+visitor/resident Plexiglas plates were swapped 
+(see Triki et al.[-@triki_Biological_2019;@triki_Brain_2020]). 
 Here, we used instead a subset of these data in order to have an idea of 
@@
 The aim of the analyses is to fit the key model parameters 
-$\gamma$ and $\eta$, to the empirical data from Triki *et al.* 
-[@triki_Biological_2019;@triki_Brain_2020] to test whether each or 
+$\gamma$ and $\eta$, to the empirical data from Triki et al. 
+[-@triki_Biological_2019;@triki_Brain_2020] to test whether each or 
 a combination of these effects is a better explanation for the pattern 
@@
 clients to be cleaned). The frequency with which clients visit the station 
-is another variable, which in nature may vary among different client species 
+is another variable influencing the station occupancy, which in nature 
+may vary among different client species 
 depending on their ectoparasite loads. We do not have field estimates 
@@
 in R [@rcoreteam_Language_2021]. All codes are accessible at 
-$\color{red}{\text{include citation}}$
+<DOI: 10.5281/zenodo.6338073>
 
@@
 We computed the pseudo $R^2$ for all the samples of the posterior from
-the MCMC. Thus, we used these distributions of pseudo $R^2$'s as a measure of
+the MCMC. We used these distributions of pseudo $R^2$'s as a measure of
 fit.
@@
 ```{r post, fig.cap='Posterior distributions for parameter values $\\gamma$ and $\\eta$ for the three models (Full model, chaining only and penalty only).
-We show the kernel density estimates, below the mode (black dot) and the 65 (light blue shade) and 95\\% (grey shade)  highest posterior density interval for the two parameters.
+We show the kernel density estimates, below the mode (black dot) and the 66 (light blue shade) and 95\\% (grey shade)  highest posterior density interval for the two parameters.
 On the top, panels a and b show posterior distributions for a full model, including chaining ($\\gamma$) and penalty ($\\eta$).
@@
 chaining produced a distribution of $pseudo-R^2$ where more values
-were positive (to the right of the black line in Fig. \ref{fig:post} f). This
+were positive (to the right of the black line in Fig. \ref{fig:post} e). This
 shows that accounting for variation in the parameter estimates the
@@
  source(here("predictions.R"))
- ggarrange(cont.obs.pred.both,scatter.obs.pred.both,
- cont.obs.pred.gam,scatter.obs.pred.gam,
- cont.obs.pred.Nrew,scatter.obs.pred.Nrew,
-           labels=c('a','b','c','d','e','f'),common.legend = F,
-   heights=c(1.4,1,1),nrow = 3,ncol = 2)
-
+first_col<-plot_grid(nrow=3,align = "v",byrow = TRUE,
+          cont.obs.pred.both,cont.obs.pred.gam,cont.obs.pred.Nrew,
+          labels=c('a','c','e'),rel_heights = c(1.4,1,1))
+second_col<-plot_grid(nrow=3,align = "v",byrow = TRUE,
+          scatter.obs.pred.both,scatter.obs.pred.gam,scatter.obs.pred.Nrew,
+          labels=c('b','d','f'))
+plot_grid(first_col,second_col,rows = 1)
 ```
@@
 solved the task already had a preference for 
-visitors clients and generalized this rule to the lab conditions 
+visitor clients and generalized this rule to the lab conditions 
 once being familiar with the task.
@@
 While all three models captured well the positive relationship between visitor 
-leaving behaviour and cleaner fish performance in
+leaving behavior and cleaner fish performance in
 the market task [@triki_Biological_2019], only the chaining mechanism 
@@
 on cleaner fish preference is the opposite, as in a busy cleaning station, to
-that of chaining. cleaner fish will get more often the resident-visitor
+that of chaining. Cleaner fish will get more often the resident-visitor
 state and will develop a preference for the visitor faster. 
@@
 conditions had relatively smaller forebrains  [@triki_Brain_2020]. 
-Triki *et al.*  refer to the former as socially competent cleaner fish,
+Triki et al.  refer to the former as socially competent cleaner fish,
 while the second group as socially incompetent cleaner fish. 
-Social competence is the ability to optimise social behaviour 
-to the available social information [@taborsky_Social_2012;
+Social competence is the ability to optimise social behavior 
+to the available social information [@taborsky_Social_2012a;
 @bshary_Cooperation_2015;@varela_Correlated_2020]. Our analyses yielded no 
@@
 ecological conditions and associated brain morphology, 
-found by Triki *et al* [@triki_Brain_2020], is due to the mechanism 
+found by @triki_Brain_2020, is due to the mechanism 
 used to incorporate future consequences. It is conceivable that 
@@
 or residents. For example, visitors are on average larger 
-than residents in body size [@bshary_Cleaner_2001], and contrary to 
+than residents in body size [@bshary_Cleaner_2001a], and contrary to 
 residents, they are less likely to chase a cleaner fish that fails to cooperate
@@
 [@kawamura_Process_1959], meaning that any learner had been repeatedly
-exposed to demonstrations before acquisition. Importantly, Galef
-[@galef_Question_1992] refuted imitation as a mechanism not simply because
+exposed to demonstrations before acquisition. 
+Importantly, @galef_Question_1992 refuted imitation as a mechanism not simply because
 of the repeated exposure but because a (rather qualitative) analysis of
@@
 prediction based on imitation learning (see also
-[@hirata_SweetPotato_2001]). In our case, the number of trials it took
+@hirata_SweetPotato_2001). In our case, the number of trials it took
 cleaners to learn the solution to the ephemeral rewards task 

### 2022-07-20 manuscript_BE/manuscript_BE.tex
New version of the manuscript

--- 2022-03-08 manuscript_1.0/manuscript_1.0.tex
@@
-%% Author_tex.tex
-%% V1.0
-%% 2012/13/12
-%% developed by Techset
-%%
-%% This file describes the coding for rsproca.cls
-
-\documentclass[]{rsos}%%%%where rsos is the template name
-
-\usepackage{lineno}
-\linenumbers
-
+% Options for packages loaded elsewhere
+\PassOptionsToPackage{unicode}{hyperref}
+\PassOptionsToPackage{hyphens}{url}
+%
+\documentclass[
+  12pt,
+]{article}
+\usepackage{amsmath,amssymb}
+\usepackage{lmodern}
+\usepackage{iftex}
+\ifPDFTeX
   \usepackage[T1]{fontenc}
   \usepackage[utf8]{inputenc}
-
-% tightlist command for lists without linebreak
-\providecommand{\tightlist}{%
-  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
-
-% From pandoc table feature
+  \usepackage{textcomp} % provide euro and other symbols
+\else % if luatex or xetex
+  \usepackage{unicode-math}
+  \defaultfontfeatures{Scale=MatchLowercase}
+  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
+\fi
+% Use upquote if available, for straight quotes in verbatim environments
+\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
+\IfFileExists{microtype.sty}{% use microtype if available
+  \usepackage[]{microtype}
+  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
+}{}
+\makeatletter
+\@ifundefined{KOMAClassName}{% if non-KOMA class
+  \IfFileExists{parskip.sty}{%
+    \usepackage{parskip}
+  }{% else
+    \setlength{\parindent}{0pt}
+    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
+}{% if KOMA class
+  \KOMAoptions{parskip=half}}
+\makeatother
+\usepackage{xcolor}
 \usepackage{longtable,booktabs,array}
@@
 \makesavenoteenv{longtable}
+\setlength{\emergencystretch}{3em} % prevent overfull lines
+\providecommand{\tightlist}{%
+  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
+\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
+\newlength{\cslhangindent}
+\setlength{\cslhangindent}{1.5em}
+\newlength{\csllabelwidth}
+\setlength{\csllabelwidth}{3em}
+\newlength{\cslentryspacingunit} % times entry-spacing
+\setlength{\cslentryspacingunit}{\parskip}
+\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
+ {% don't indent paragraphs
+  \setlength{\parindent}{0pt}
+  % turn on hanging indent if param 1 is 1
+  \ifodd #1
+  \let\oldpar\par
+  \def\par{\hangindent=\cslhangindent\oldpar}
+  \fi
+  % set entry spacing
+  \setlength{\parskip}{#2\cslentryspacingunit}
+ }%
+ {}
+\usepackage{calc}
+\newcommand{\CSLBlock}[1]{#1\hfill\break}
+\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
+\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
+\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
+\usepackage{float}
+\usepackage{graphicx}
+\usepackage{booktabs}
+\linespread{2}
+\usepackage{lineno}
+\linenumbers
+\usepackage{setspace}\doublespacing
+\newcommand{\beginsupplement}{ \setcounter{table}{0}     \renewcommand{\thetable}{S\arabic{table}}\setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}}
+\providecommand{\keywords}[1]{\textbf{\textit{Keywords---}} #1}
 
-\usepackage{float}
-\usepackage{booktabs}
-\newcommand{\beginsupplement}{ \setcounter{table}{0}     \renewcommand{\thetable}{S\arabic{table}}\setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}}
+\ifLuaTeX
+  \usepackage{selnolig}  % disable illegal ligatures
+\fi
+\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
+\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
+\urlstyle{same} % disable monospaced font for URLs
+\hypersetup{
+  pdftitle={ Computational models reveal how cleaner fish adjust decisions in a biological market},
+  hidelinks,
+  pdfcreator={LaTeX via pandoc}}
 
-%%%% *** Do not adjust lengths that control margins, column widths, etc. ***
+\title{\large \textbf{Title:} Computational models reveal how cleaner
+fish adjust decisions in a biological market}
+\usepackage{etoolbox}
+\makeatletter
+\providecommand{\subtitle}[1]{% add subtitle to \maketitle
+  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
+}
+\makeatother
+\subtitle{\normalsize \textbf{Abbreviated title:} Cleaner fish cognitive
+mechanisms in a biological market}
+\date{}
 
-%%%%%%%%%%% Defining Enunciations  %%%%%%%%%%%
-\newtheorem{theorem}{\bf Theorem}[section]
-\newtheorem{condition}{\bf Condition}[section]
-\newtheorem{corollary}{\bf Corollary}[section]
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\usepackage{forarray}
+\usepackage{xstring}
+\newcommand{\getIndex}[2]{
+  \ForEach{,}{\IfEq{#1}{\thislevelitem}{\number\thislevelcount\ExitForEach}{}}{#2}
+}
+
+\newcommand{\getAff}[1]{
+  \getIndex{#1}{}
+}
 
 \begin{document}
+\maketitle
+\begin{flushleft}
+\end{flushleft}
+\begin{abstract}
+While it is generally straightforward to quantify individual performance
+in cognitive experiments, identifying the underlying cognitive processes
+remains a major challenge. Often, different mechanistic underpinnings
+yield similar performances, and Lloyd Morgan's cannon warrants
+acceptance of the simpler explanation. Alternatively, when the different
+mechanisms interact with environmental conditions, variation in
+performance across environments might allow to statistically infer the
+mechanism responsible. We illustrate this point by fitting computational
+models to experimental data on performance by wild-caught cleaner fish
+\emph{Labroides dimidiatus} in an ephemeral reward task, as well as
+cleaner and client fish densities from the locations of capture. Using
+Bayesian statistics to fit the model parameters to performance data
+revealed that cleaner fish most likely estimate future consequences of
+an action, while it appears unlikely that the removal of the ephemeral
+reward acts as psychological punishment (negative reinforcement).
+Incorporating future consequences also yields performances that can be
+considered the result of locally optimal decision-rules, in contrast to
+the negative reinforcement mechanism. We argue that the combination of
+computational models with data is a powerful tool to infer the
+mechanistic underpinnings of cognitive performance.
+\end{abstract}
+\subsection*{Lay summary}
+Cleaner fish eat ectoparasites off other fishes, so-called clients. It
+regularly happens that two clients seek a cleaner's service
+simulatenously. Cleaners benefit from prioritising clients unwilling to
+wait, so they can feed on those willing to wait. To make the right
+choice, cleaners must somehow ``look'' into the future to anticipate
+consequences of current choices. By combining a learning model with
+data, we show that cleaners estimate the long-term value of their
+actions rather than using simpler heuristics. Estimating long-term value
+is a mechanism involved in human foresight.
 
-%%%% Article title to be placed here
-\title{Field and experimental data together with computational models reveal how cleaner fish adjust decisions in a biological market}
+\keywords{learning, behavior, cleaners, bayesian statisitics, behavioral mechanisms}
 
-\author{
-Andrés E. Quiñones$^{1}$,
-Zegni Triki$^{2}$,
-Redouan Bshary$^{1}$}
-
-\address{
-  $^{1}$Institute of Biology, University of Neuchâtel, Neuchâtel, Switzerland\\
-  $^{2}$Department of Zoology, Stockholm University, Stockholm, Sweden}
-%%%% Subject entries to be placed here %%%%
-\subject{
-Behavioural ecology,
-Cognitive ecology,
-Animal behaviour}
-
-%%%% Keyword entries to be placed here %%%%
-\keywords{
-learning,
-cleaners,
-behaviour,
-bayesian statisitics,
-mutualism}
-
-%%%% Insert corresponding author and its email address}
-\corres{
-  AE. Quiñones\\
-  e-mail: \href{mailto:andreseqp@gmail.com}{\nolinkurl{andreseqp@gmail.com}}
-}
-
-%%%% Abstract text to be placed here %%%%%%%%%%%%
-\begin{abstract}
-While it is generally straightforward to quantify individual performance in cognitive experiments, identifying the underlying cognitive processes remains a major challenge.
-Often, different mechanistic underpinnings yield similar performances, and Lloyd Morgan's cannon warrants acceptance of the simpler explanation.
-Alternatively, when the different mechanisms interact with environmental conditions, variation in performance across environments might allow to statistically infer the mechanism responsible.
-We illustrate this point by fitting computational models to experimental data on performance by wild-caught cleaner fish Labroides dimidiatus in an ephemeral reward task, as well as cleaner and client fish densities from the locations of capture.
-Using Bayesian statistics to fit the model parameters to performance data revealed that cleaner fish most likely estimate future consequences of an action, while it appears unlikely that the removal of the ephemeral reward acts as psychological punishment (negative reinforcement).
-Incorporating future consequences also yields performances that can be considered the result of locally optimal decision-rules, in contrast to the negative reinforcement mechanism.
-We argue that the combination of computational models with data is a powerful tool to infer the mechanistic underpinnings of cognitive performance.
-\end{abstract}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\providecommand{\EndFirstPage}{%
-}
-
-\maketitle
+\newpage
 
@@
 
-Often alternative cognitive mechanisms yield similar behaviour and/or cognitive
-performances. This poses a problem for disentangling the mechanistic
-underpinnings of behaviour. This is particularly clear in research aimed at
-discovering between species variation in \emph{higher} cognitive abilities; or
-in other words, research on whether non-human animals show cognitive
-abilities believed to be uniquely human. For instance, when researchers
-try to find \emph{mental time travel-like} behaviour, they usually come up with
-clever experiments to show the behaviour displayed requires inferences made
-through past events\citep{dally_Foodcaching_2006}. However, they often face the
-challenge of alternative scenarios where simpler explanations,
-like classic associative learning, can bring about the
-observed behavioural outcome \citep{suddendorf_Evolution_2007}. Similarly, attempts
-to demonstrate the presence of \emph{theory of mind} in non-human animals
-face objections justified by alternative mechanisms underpinning
-similar behavioural results \citep{heyes_Theory_1998}.
-Such controversies are usually settled by using the principle
-of parsimony and its cognitive version,
-Lloyd Morgan's cannon, which states that the simpler explanation (mechanism)
-should be accepted. Ideally, however, alternative hypotheses should be evaluated
-in light of their explanatory power. One potential dimension that could allow
-the variation necessary among distinct cognitive mechanisms is environmental
-variation. Controlled laboratory conditions often mask between and within
-species variation that arises among different environments. Thus, if
-predictions from the alternative mechanisms depend on environmental
-conditions, it is possible to assess their relative explanatory power
-by performing cognitive test in the context of
-different environmental conditions.
+Often alternative cognitive mechanisms yield similar behavior and/or
+cognitive performances. This poses a problem for disentangling the
+mechanistic underpinnings of behavior. This is particularly clear in
+research aimed at discovering between species variation in \emph{higher}
+cognitive abilities; or in other words, research on whether non-human
+animals show cognitive abilities believed to be uniquely human. For
+instance, when researchers try to find \emph{mental time travel-like}
+behavior, they usually come up with experiments to show the behavior
+displayed requires inferences made through past events (Dally, Emery,
+and Clayton 2006). However, they often face the challenge of alternative
+scenarios where simpler explanations, like classic associative learning,
+can bring about the observed behavioral outcome (Suddendorf and
+Corballis 2007). Similarly, attempts to demonstrate the presence of
+\emph{theory of mind} in non-human animals face objections justified by
+alternative mechanisms underpinning similar behavioral results (C. M.
+Heyes 1998). Such controversies are usually settled by using the
+principle of parsimony and its cognitive version, Lloyd Morgan's cannon,
+which states that the simpler explanation (mechanism) should be
+accepted. Ideally, alternative hypotheses should be evaluated in light
+of their explanatory power.
+
+Learning is a key overarching cognitive mechanism that allows
+individuals to associate rewards with environmental stimuli and thus
+behave adaptively (Staddon 2016; Shettleworth 2009). Associative
+learning, in particular, exists in all major vertebrate taxa, and in
+many invertebrates as well (C. Heyes 2012; Macphail 1982; Staddon 2016;
+Behrens et al. 2008). Associative learning is not homogeneous throughout
+its taxonomic distribution, rather there are differences across and
+within species (Shettleworth 2009; Sih and Giudice 2012). So presumably,
+the mechanistic underpinnings of learning have been modified by natural
+selection (Marler and Peters 1989).
+
+One way to formalize the alternative mechanistic underpinnings of
+associative learning is to develop quantitative models of learning
+processes. This approach, which started within experimental psychology
+(Staddon 2016; Brandon, Vogel, and Wagner 2002), has been very fruitful
+in disentangling the mechanistic structure of cognitive systems. More
+recently, the development of reinforcement learning theory (Sutton and
+Barto 2018), has allowed to evaluate the empirical support for
+alternative mechanistic hypotheses by providing quantitative predictions
+which are amenable to statistical tests (Farashahi et al. 2020, 2017).
+Interestingly, these learning models not only have received support from
+behavioral data, but also are consistent with the current view on reward
+processing in the brain (Schultz 2015).
 
 From an evolutionary perspective, mechanisms are likely selected because
-of how they allow individuals to respond to environmental variation.
-For example, biological market theory predicts that the exchange rate of goods
-and/or services traded between cooperative partners adjusts to the
-law of supply and demand, when individuals have some degree of partner choice
-\citep{noe_Biological_1995}. Supply and demand conditions, which typically
-depend on the abundance of the species involved, certainly vary in time
-and space. Therefore, natural selection should favour the ability
-to flexibly adjust decisions and behavioural output to
-current market conditions. Indeed, such adjustments have been repeatedly
-documented \citep{axen_Signalling_1996}. In animals, an obvious general candidate
-mechanism for the strategic adjustment is the cognitive machinery. However,
-it is not clear which cognitive mechanisms allow individuals to adjust their
-behaviour to the varying conditions. More specifically the question arises
-to what extent mechanisms beyond basic associative learning may be involved.
+of how they allow individuals to respond to environmental variation. For
+example, biological market theory predicts that the exchange rate of
+goods and/or services traded between cooperative partners adjusts to the
+law of supply and demand, when individuals have some degree of partner
+choice (Noë and Hammerstein 1995). Supply and demand conditions, which
+typically depend on the abundance of the species involved, certainly
+vary in time and space. Therefore, natural selection should favor the
+ability to flexibly adjust decisions and behavioral output to current
+market conditions. Indeed, such adjustments have been documented (Axén,
+Leimar, and Hoffman 1996). One example of strategic adjustment in a
+biological market is the marine cleaning mutualism involving the cleaner
+fish \emph{Labroides dimidiatus} and `client' fishes. Client fishes seek
+cleaner fish services at their territory (so-called ``cleaning
+station'') and offer themselves as food patches to get their
+ectoparasites removed, which provides cleaners with food and clients
+with improved health (Waldie et al. 2011; Ros et al. 2011; Triki et al.
+2016; Demairé et al. 2020). Given the capacity of some client fish to
+swim larger distances and access multiple cleaning stations while others
+access the only cleaning station in their territory, it is crucial to
+categorize clients as either ``visitors'' or ``residents'',
+respectively. During cleaning interactions, a cleaner fish often faces a
+choice between a visitor and a resident client seeking its cleaning
+services simultaneously. Visitors have the option to switch to another
+cleaner fish if being made to wait, while residents must wait for
+inspection. Indeed, visitors have been observed to use their partner
+choice option in that way (Bshary and Schäffer 2002), which may explain
+why cleaners give visitors service priority in a field study in the Red
+Sea (Bshary 2001). Furthermore, in a lab based paradigm, design to mimic
+the resident-visitor choice (ephemeral reward task), cleaners learned to
+prefer the cue associated with the epheral food source (visitor) and
+hence accessed both food sources, obtaining double the amount of food
+(Bshary and Grutter 2002). However, further exploration revealed that
+not all cleaner fish manage to develop a preference for the ephemeral
+option in the lab (Triki et al. 2018). Over the last decade, over a
+hundred wild-caught cleaner fish have been tested in the exact same
+paradigm of the ephemeral reward task (Salwiczek et al. 2012; Wismer et
+al. 2014; Triki et al. 2018, 2019, 2020). These fish often come from
+different reef locations. Investigation of the local eco-sociological
+conditions revealed that cleaner and client fish population densities
+have a substantial impact on cleaner fish performance in the task.
+Cleaner fish from reef sites with relatively low densities were more
+likely to fail at solving the task (Triki et al. 2019, 2018; Wismer et
+al. 2014). This intra-specific variation is unlikely due to local
+genetic adaptation, because cleaner fish are open water spawners and the
+environmental conditions can vary within the lifespan of a fish.
 
-One example of strategic adjustment in a biological market is the marine
-cleaning mutualism involving the cleaner fish \emph{Labroides dimidiatus} and
-`client' fish. Client fish seek cleaner fish services at their territory
-(so-called ``cleaning station'') and offer themselves as food patches
-to get their ectoparasites removed, which provides cleaners
-with food and clients with improved health \citep{waldie_LongTerm_2011, ros_Does_2011, triki_Effects_2016, demaire_Reduced_2020}.
-Given the capacity of some client fish to swim larger distances and
-access multiple cleaning stations while others access the only cleaning
-station in their territory, it is crucial to categorize clients as
-either ``visitors'' or ``residents'', respectively. During cleaning interactions,
-a cleaner fish often face a choice between a visitor and a resident client
-seeking its cleaning services simultaneously. Visitors have the option
-to switch to another cleaner fish if being made to wait, while residents
-must wait for inspection. Indeed,
-visitors have been observed to use their partner choice option in that
-way \citep{bshary_Choosy_2002}, which may explain why cleaners give
-visitors service priority in a field study in the Red Sea
-\citep{bshary_Cleaner_2001}.
+Mechanistic models explicitly designed to mimic the ephemeral reward
+task have shown that the simplest form of associative learning (operant
+conditioning) cannot account for a solution to the ephemeral reward task
+(Prat, Bshary, and Lotem 2022; Quiñones et al. 2019). Operant
+conditioning is a form of associative learning where individuals use
+short term reward to associate and choose actions. Such models allow
+varying the cognitive tool kit and evaluating which minimal kit is
+necessary to solve the task at hand (e.g. Dubois et al. (2021)). To be
+able to give visitors priority over residents, cleaners need to be able
+to assess a client's value separately for the three possible scenarios
+(alone, paired with a fish with the same strategic option, paired with a
+fish with the alternative strategic option) (Quiñones et al. 2019). The
+ability to distinguish and value one stimulus differently alone from
+compound versions of it has been termed configurational learning,
+chunking, or segmentation (see references in Prat, Bshary, and Lotem
+(2022)). In addition to configurational learning, cleaners also need to
+account for the future consequences of current decisions. In the model
+by Quiñones et al. (2019), this could be achieved in two non-mutually
+exclusive ways: through low temporal discounting of future effects, also
+termed `chaining' (Enquist, Lind, and Ghirlanda 2016); and/or through
+perceiving a visitor client leaving as psychological punishment (i.e.~as
+a negative reinforcer). Chaining is when individuals include in their
+valuation of an action the reward effects that this will have in the
+future. This is done by combining in a single valuation the reward
+obtained in the current time with all the reward that comes after,
+discounting for how far in the future reward is accrued. `Chaining' the
+reward of these different time steps allows individuals to take actions
+that increase the long-term reward at the sacrifice of short term
+considerations (Enquist, Lind, and Ghirlanda 2016). Even though,
+`chaining' can be readily implemented computationally in learning models
+(Enquist, Lind, and Ghirlanda 2016; Sutton and Barto 2018), cognitively
+it seems to be a complex adaptation (Suddendorf and Corballis 2007). On
+the other hand, using client behavior as a negative reinforcer is, in
+principle, easier to implement. Thus, the standard logic of Lloyd
+Morgan's cannon demands that operant conditioning as the simpler
+explanation is to be accepted by default. Ideally, however, the two
+mechanisms should be evaluated in light of how well they explain the
+available data. Note that different fields interested in cognition and
+decision making use different words to refer to negative reinforcers
+(Quiñones et al. 2019; Sutton and Barto 2018). Here, for the sake of
+simplicity and clarity, we will use the word `penalty' to refer to this
+mechanism which includes a negative reinforcer.
 
-When researchers aimed at testing wild-caught cleaner fish, as
-well as individuals from other species, abilities
-to prioritize visitor over resident clients in a lab-based paradigm,
-they used Plexiglas plates of different colours and shapes offering the same
-amount of food as surrogates for visitor and resident clients.
-One plate is made to behave like a resident, i.e.~it remains until
-the cleaner fish has eaten off it. The other plate was made to behave
-like a visitor, i.e.~it is removed if not inspected first.
-This laboratory paradigm originally inspired by the cleaning market
-of cleaner fish is more generally referred as the ephemeral reward task.
-Individuals are assessed in their capacity to develop a preference for the
-ephemeral option, which gives them access to two reward units.
-Cleaners learned to prefer the visitor plate and
-hence obtained the double amount of food \citep{bshary_Asymmetric_2002}.
-Furthermore, adult cleaner fish outperformed various primates as well as rats and
-pigeons in this original version of the ephemeral reward task
-\citep{salwiczek_Adult_2012, zentall_Early_2017}; yet the African grey
-parrots solve this task as well \citep{pepperberg_Can_2014}.
-This between variation in performance, and primates' known cognitive abilities
-\(\color{red}{\text{ref}}\), shows that performance in the task
-cannot be readily explained by classifying species as having high and
-low cognitive abilities. Instead, this between species variation suggests
-that solving the ephemeral reward task requires a set of cognitive
-mechanisms that are not present in all the tested taxa, or were not used
-under the experimental set-up.
-
-Recent research on the cognitive abilities needed to solve the ephemeral
-reward task has used a broad approach as proposed by Shettleworth
-\citep{shettleworth_Cognition_2009}, who defined cognition as including
-all ways in which animals acquire information
-through the senses, process, retain and decide to act on it.
-Indeed, perception of relevant cues is of major importance
-for individual performance. For example, some animals find relevant
-information in the plates \citep{wismer_Cuebased_2019} while others find
-it in the food \citep{pretot_Comparative_2021, pretot_Comparing_2016}.
-However, identifying cues as salient is not the only challenge
-of the ephemeral reward task, as revealed by proximate learning models.
-Such models allow varying the cognitive tool kit and evaluating
-which minimal kit is necessary to solve
-the task at hand (e.g. \citep{dubois_Model_2021}). Applied to the ephemeral
-reward task, learning models showed that basic reinforcement learning does
-not suffice to solve the ephemeral reward task \citep{prat_Modelling_2022, quinones_Reinforcement_2019}.
-This is particularly so when models assume the more complex natural
-situation in which cleaner fish face not only resident-visitor pairs but also
-visitor-visitor and resident-resident pairs, as well a resident alone or
-a visitor alone. To be able to give visitors priority over residents,
-cleaners need to be able to assess a client's value separately for the
-three possible scenarios (alone, paired with a fish with the
-same strategic option, paired with a fish with the alternative strategic option)
-\citep{quinones_Reinforcement_2019}. The ability to distinguish and value
-one stimulus differently alone from compound versions of it has been termed
-configurational learning, chunking,
-or segmentation (see references in \citep{prat_Modelling_2022}).
-
-In addition to configurational learning, cleaners also need to account for
-the future consequences of current decisions. In the model by
-Quiñones \emph{et al.} \citep{quinones_Reinforcement_2019}, this could be achieved in
-two non-mutually exclusive ways: through low temporal discounting of
-future effects, also termed `chaining' \citep{enquist_Power_2016}; and/or
-through perceiving a visitor client leaving as psychological punishment
-(i.e.~as a negative reinforcer). Low temporal discounting is when
-individuals include in their valuation of an action the reward effects
-that this will have in the future. This is done by combining in a single
-valuation the reward obtained in the current time with all the reward that
-comes after, discounting for how far in the future reward
-is accrued. `Chaining' the reward of these different time steps allows
-individuals to take actions that increase the long-term reward at the sacrifice
-of short term considerations \citep{enquist_Power_2016}. Even though, `chaining'
-can be readily implemented computationally in learning models
-\citep{enquist_Power_2016, sutton_Reinforcement_2018}, cognitively it seems to be
-a complex adaptation \citep{suddendorf_Evolution_2007}. On the other hand,
-using client behaviour as a negative reinforcer is, in principle,
-easier to implement. Negative reinforcement is part of the ubiquitous
-learning mechanism termed operant conditioning \citep{thorndike_Animal_1898, skinner_Behavior_1938}. Thus, the standard logic of
-Lloyd Morgan's cannon demands that operant conditioning as the simpler
-explanation is to be accepted by default. Ideally, however, the two
-mechanisms should be evaluated in light of how well
-they explain the available data. Note that different fields interested in
-cognition and decision making use different words to refer to negative
-reinforcers \citep{quinones_Reinforcement_2019, sutton_Reinforcement_2018}.
-Here, for the sake of simplicity and clarity, we will use the word
-`penalty' to refer to this mechanism which includes a negative reinforcer.
-
-Over the last decade, our team tested over a hundred wild-caught
-cleaner fish in the exact same paradigm of the ephemeral reward
-task \citep{salwiczek_Adult_2012, wismer_Variation_2014, triki_Decrease_2018, triki_Biological_2019, triki_Brain_2020}. These fish often come from
-different reef locations around the study field site at Lizard Island,
-Great Barrier Reef in Australia. Further investigation of the local
-eco-sociological conditions revealed that cleaner and client
-fish population densities have a substantial impact on cleaner fish
-performance in the task. Cleaner fish from reef sites with relatively
-low densities were more likely to fail at solving the task \citep{triki_Biological_2019, triki_Decrease_2018, wismer_Variation_2014}. The explanation for this pattern
-is twofold. First, low cleaner fish population densities imply
-low supply and high demand for cleaning services.
-Under such conditions, there are fewer occasions under
-which failing to give priority to a visitor translates to an empty
-cleaning station. Second and also related to the state of the cleaning market,
-visitor clients at low cleaner fish population densities
-are less likely to exert their partner choice options
-and are hence more likely to wait for inspection if not given cleaning
-priority \citep{triki_Brain_2020}. In the absence of partner choice
-cleaner fish should not give priority to visitors any more.
-
-The interplay between the underlying cognitive machinery and
-local ecological conditions apparently generate the documented variable
-performance among individuals of the same species.
-Our approach of fitting the computational model to the empirical data on
-fish densities and cleaner fish censuses and performance
-in the ephemeral reward task aimed at: (i), determining which
-mechanism cleaner fish use to incorporate future consequences of current
-decisions by testing whether chaining, penalty, or a combination
-of both best explains their performance; (ii) determining whether the
-two mechanisms differed with respect to the ecological conditions
-that are likely to cause high versus low performance in the
-ephemeral reward task. Additionally, we assessed which mechanism
-yields optimal performance patterns. Relying on the logic of
-biological market theory, we predicted
-that appropriate performance is to show a low preference for visitors under low
+In here we used the field and experimental data to fit the parameters of
+a reinforcement learning model to infer the cognitive mechanism that
+cleaners use in their interaction with clients. Specifically, our
+approach of fitting the computational model to the empirical data aimed
+at: (i), determining which mechanism cleaner fish use to incorporate
+future consequences of current decisions by testing whether chaining,
+penalty, or a combination of both best explains their performance; (ii)
+determining whether the two mechanisms differed with respect to the
+ecological conditions that are likely to cause high versus low
+performance in the ephemeral reward task. Additionally, we assessed
+which mechanism yields optimal performance patterns. Relying on the
+logic of biological market theory, we predicted that appropriate
+performance is to show a high preference for visitors only under high
 local cleaner-to-client ratio.
@@
 The model consists of a set of individual-based simulations where
-individuals, representing cleaner fish, face a series of choices
-between two options, which simulate the natural conditions
-of the cleaning market. Individuals experience a series
-of discrete time points in which they face different `states',
-defined by the number and category of client fish (visitor or residents)
-inviting for cleaning services. There are six possible states:
-zero clients, one resident, one visitor,
-resident-resident, visitor-visitor, and resident-visitor.
-The probability of each state is largely determined by the relative
+individuals, representing cleaner fish, face a series of choices between
+two options, which simulate the natural conditions of the cleaning
+market. Individuals experience a series of discrete time points in which
+they face different `states', defined by the number and category of
+client fish (visitor or residents) inviting for cleaning services. There
+are six possible states: zero clients, one resident, one visitor,
+resident-resident, visitor-visitor, and resident-visitor. The
+probability of each state is largely determined by the relative
 abundance of cleaner fish, residents and visitors, but to some degree by
@@
 This is because residents are willing to queue for cleaning service;
-while visitors leave the queue (with a certain probability) when made to wait.
-Individuals obtain a fixed reward from cleaning a client fish
-regardless of the category. Every time individuals face and make a choice
-they update the probability of making that same choice. The update is
-based on the difference between the expected reward and the obtained
-reward (prediction error) \citep{sutton_Reinforcement_2018, rescorla_Theory_1972}. Given the new information, the update is carried
-in the direction that leads to more reward being obtained, given
-the new information. In the long run, the probability of choosing a visitor
-over a resident converges in the model. To which probability the model
-will converge depends on the relative abundance of cleaners, visitors
-and residents; as well as on the probability of visitors leaving the
-cleaning station when made to wait. Further details of the model
-implementation can be found in Quiñones \emph{et al} \citep{quinones_Reinforcement_2019}.
+while visitors leave the queue (with a certain probability) when made to
+wait. Individuals obtain a fixed reward from cleaning a client fish
+regardless of the category. Every time individuals face and make a
+choice they update the probability of making that same choice. The
+update is based on the difference between the expected value and the
+obtained reward - the prediction error (\(\delta_t\)) - (Sutton and
+Barto 2018; Rescorla and Wagner 1972). Formally, the prediction error is
+given by
 
-The model shows that agents need to find a way
-to incorporate future consequences of current choices. In the model,
-this could be achieved with either of two parameters that could
-also work together. First, \(\gamma\) measures how
-much individuals include future rewards in their decision updates.
-If \(\gamma=0\), individuals only use the immediate reward obtained from a
-cleaning interaction. As \(\gamma\) increases, individuals include more the
-reward obtained from the subsequent choices. That amounts to calculating
-and using for decision making the future expected rewards of an action (chaining).
-Second, \(\eta\) measures how much individuals include in their reward the
-fleeing behaviour of visitors as a negative component (penalty). Both of
-these parameters allow individuals to use in their estimates the future
+\begin{equation}
+\label{eq:delta}
+\delta_t = R_t -  V_t(S_t) + \gamma V_t(S_{t+1}) ,
+\end{equation}
+
+where \(R_t\) is the sum different reward sources at time \(t\);
+\(V_t(S_t)\) is the estimated value at time \(t\) of the the state faced
+by the agent at time \(t\); similarly \(V_t(S_{t+1})\) is the estimated
+value of the state to come in the following time-step, \(\gamma\) is the
+discount factor for future rewards. When the estimated value of the
+current state (\(V_t(S_t)\)) is equal to the sum of short-term (\(R_t\))
+and future discounted reward (\(\gamma V_t(S_{t+1})\)) learning stops
+for that state. If \(\gamma = 0\) the estimates made by the agent only
+capture short-term reward. We assume short-term reward to two
+components: positive reward determined by the amount of food obtained
+from cleaning a client; and negative reward triggered when by a client
+leaving the station without being cleaned. Formally, we let total reward
+be given by \(R_t=P_t - \eta_t\). Where \(\eta\) is a parameter of the
+model that determines the the size of the negative reward triggered by
+unattended clients leaving the station.
+
+The prediction error (Eq. \ref{eq:delta}) is used to update the value of
+each one of the states the agent faces, as well as the preference for
+the resident and visitor options. The value update is simple the product
+of the prediction error and the parameter for the speed of learning
+(\(\Delta V(S_t)=\alpha \delta_t\)). The change in preference between
+the resident and visitor is given by
+\(\Delta (\theta_v-\theta_r)_t=\alpha\delta_t2(1-\pi_v)\), where
+\(\theta_i\) represent the preference for one of two options and the
+difference captures the total change relative to one another; \(\pi_v\)
+corresponds to the current probability of choosing the visitor. \(p_i\)
+is determined by applying the logistic function to the diffence in
+preferences between the two mutually exclusive options
+(\(\pi_v=\frac{1}{1+e^{-(\theta_v-\theta_r)}}\)). This amounts to a
+preference update that is carried in the direction that leads to more
+reward being obtained, given the new information. In the long run, the
+probability of choosing a visitor over a resident converges in the
+model. To which probability the model will converge depends on the
+relative abundance of cleaners, visitors and residents; as well as on
+the probability of visitors leaving the cleaning station when made to
+wait. Further details of the model implementation can be found in
+Quiñones et al. (2019).
+
+The model shows that agents need to find a way to incorporate future
+consequences of current choices. In the model, this could be achieved
+with either of two parameters that could also work together. First,
+\(\gamma\) measures how much individuals include future rewards in their
+decision updates. If \(\gamma=0\), individuals only use the immediate
+reward obtained from a cleaning interaction. As \(\gamma\) increases,
+individuals include more the reward obtained from the subsequent
+choices. That amounts to estimating and using for decision making the
+future expected rewards of an action (chaining). Second, \(\eta\)
+measures how much individuals include in their reward the fleeing
+behavior of visitors as a negative component (penalty). Both of these
+parameters allow individuals to use in their estimates the future
 effects of their choices.
@@
 The empirical data were collected between 2010 and 2019 always during
-the austral winter months June to August from a total of five
-study reef sites (Corner Beach-CB, Horseshoe-HS, Mermaid Cove-MC,
-Northern Horseshoe-NHS, and The Crest-TC) at Lizard Island
+the austral winter months June to August from a total of five study reef
+sites (Corner Beach-CB, Horseshoe-HS, Mermaid Cove-MC, Northern
+Horseshoe-NHS, and The Crest-TC) at Lizard Island
 (\(14.6682^\circ S, 145.4604^\circ E\)), Great Barrier Reef, Australia.
-The data consist of three sets: fish censuses, field
-observations of cleaner-client interactions to quantify the probability
-of visitors leaving if made to wait, and the
-performance of wild-caught cleaner fish in the ephemeral reward test.
-In total, we have twelve site/year data sets for fish censuses and
-corresponding performance in the lab test. Thus, some sites were sampled more
-than once. To estimate the population density of cleaner fish
-and their clients at a given site in
-a given year, Triki \emph{et al.} \citep{triki_Biological_2019} used a series of ten
-transects of \(30m\) each. Observers swam along the transect lines placed on
-the reef and first counted the visible large-bodied adult fish
-(species with total length \(TL \geq 10cm\)) including cleaner fish
-on a width of \(5m\), and then on the
-return individuals of small-bodied fish species (\(TL < 10 cm\))\\
-on a width of \(1 m\)
-(see Triki et al.~2018 for further details on fish censuses data collection).
-We then scaled the counts of cleaner fish, small-bodied,
-and large-bodied clients fish densities per \(100 m^2\).
-From the study by Triki \emph{et al} \citep{triki_Biological_2019}
-cleaner fish and large-bodied client populations densities were
-highly correlated, and only the former
-was hence used in the analyses as representative of both measures.
+The data consist of three sets: fish censuses, field observations of
+cleaner-client interactions to quantify the probability of visitors
+leaving if made to wait, and the performance of wild-caught cleaner fish
+in the ephemeral reward test. In total, we have twelve site/year data
+sets for fish censuses and corresponding performance in the lab test.
+Thus, some sites were sampled more than once. To estimate the population
+density of cleaner fish and their clients at a given site in a given
+year, Triki et al. (2019) used a series of ten transects of \(30m\)
+each. Observers swam along the transect lines placed on the reef and
+first counted the visible large-bodied adult fish (species with total
+length \(TL \geq 10cm\)) including cleaner fish on a width of \(5m\),
+and then on the return individuals of small-bodied fish species
+(\(TL < 10 cm\)) on a width of \(1 m\) (see Triki et al. (2018) for
+further details on fish censuses data collection). We then scaled the
+counts of cleaner fish, small-bodied, and large-bodied clients fish
+densities per \(100 m^2\). From the study by Triki et al. (2019) cleaner
+fish and large-bodied client populations densities were highly
+correlated, and only the former was hence used in the analyses as
+representative of both measures.
 
-The field observation data consisted of video recordings/encodings of the
-cleaner-client cleaning interactions. There were videos from eight
-cleaners per site/year of a duration of \(30 min\) each. Triki \emph{et al}
-extracted information from every event wherein a visitor client
-was made to wait in favour of another client (visitor or resident), and noted
+The field observation data consisted of video recordings/encodings of
+the cleaner-client cleaning interactions. There were videos from eight
+cleaners per site/year of a duration of \(30 min\) each. Triki et al.~
+extracted information from every event wherein a visitor client was made
+to wait in favour of another client (visitor or resident), and noted
 whether or not the visitor left or queued for the cleaning service
-\citep{triki_Biological_2019, triki_Brain_2020}.
+(Triki et al. 2019, 2020).
 
-The cognitive performance data was from a total of 120 cleaners
-(10 individuals per 12 site/year) tested in the
-ephemeral reward task \citep{triki_Biological_2019, triki_Brain_2020}. Authors
-housed all captured cleaners individually in glass aquaria
-( \(62cm \times 27cm \times 37 cm\) ) and provided them
-with PVC pipes (\(10 cm \times 1 cm\)) as shelters.
-The task consisted of exposing the cleaner fish to substitute
-models of client fish in the form of two \emph{Plexiglas} plates offering the
-same amount of food (one item of mashed prawn). The two plates differed
-in colour and pattern (horizontal green stripes or vertical pink stripes)
-but had equal size (\(10 cm \times 7 cm\)). Importantly, the two plates played
-different roles as either a visitor (ephemeral food source) or
-resident (permanent food source). That is, if a cleaner fish inspected the
+The cognitive performance data was from a total of 120 cleaners (10
+individuals per 12 site/year) tested in the ephemeral reward task (Triki
+et al. 2019, 2020). Authors housed all captured cleaners individually in
+glass aquaria (\(62cm \times 27cm \times 37 cm\)) and provided them with
+PVC pipes (\(10 cm \times 1 cm\)) as shelters. The task consisted of
+exposing the cleaner fish to substitute models of client fish in the
+form of two \emph{Plexiglas} plates offering the same amount of food
+(one item of mashed prawn). The two plates differed in colour and
+pattern (horizontal green stripes or vertical pink stripes) but had
+equal size (\(10 cm \times 7 cm\)). Importantly, the two plates played
+different roles as either a visitor (ephemeral food source) or resident
+(permanent food source). That is, if a cleaner fish inspected the
 resident plate first, the experimenter withdrew the visitor plate out of
@@
 however, granted access to both plates. The equal size of the plates
-forced cleaner fish to learn to give service priority to the visitor plate
-based solely on the behaviour-cue of the plates rather than size-cue
-\citep{wismer_Cuebased_2019}. Triki \emph{et al.} \citep{triki_Biological_2019, triki_Brain_2020}
-tested the fish for a maximum of 200 trials with 20 trials a day, 10 trials
-in the morning and 10 trials in the afternoon. They randomized and
+forced cleaner fish to learn to give service priority to the visitor
+plate based solely on the behavior-cue of the plates rather than
+size-cue (Wismer et al. 2019). Triki et al. (2019, 2020) tested the fish
+for a maximum of 200 trials with 20 trials a day, 10 trials in the
+morning and 10 trials in the afternoon. They randomized and
 counterbalanced the plates' spatial location (i.e.~left or right)
 between trials. Similarly, they counterbalanced the plates' decoration
-(colour and pattern) and the plates' role (visitor or resident) between the
-tested fish. In the original studies, once a fish reach a learning criterion,
-that is, performing significantly above chance level (\(> 50%
-\), \(p-value ≥ 0.05\)),
-they passed to a reversal version of the task where the roles of the
-visitor/resident Plexiglas plates were swapped (see Triki et al.~2019, 2020).
-Here, we used instead a subset of these data in order to have an idea of
-cleaner fish preferences for the visitor plate, even if they do not reach
-the learning criterion within 200 trials. To do so, we first extracted the
-trial-by-trial outcomes from the last two sessions (20 trials) of those who
-never reached the learning criterion for visitor plate
-(\(N = 45\) cleaner fish).
-For those who reached the learning criterion at some point during the
-test and passed to a reversal phase, we extracted the trial-by-trial
-outcomes from the last session (10 trials) before passing to reversal
-and the last 10 trials they were exposed to in the test
-(\(N = 75\) cleaner fish).
-We chose a combination of initial and reversal to quantify preference
-for the visitor client, given that it matches well the criteria chosen
-in previous analysis of the ephemeral reward task experimental set-up
-\citep{triki_Biological_2019, triki_Brain_2020}. In the
-supplementary material (Fig. \ref{fig:rawdata}) we show how our choice maps
-to the previously used criteria. For comparison, we also show a quantification
+(colour and pattern) and the plates' role (visitor or resident) between
+the tested fish. In the original studies, once a fish reach a learning
+criterion, that is, performing significantly above chance level (\(> 50%
+\), \(p-value ≥ 0.05\)), they passed to a reversal version of the task
+where the roles of the visitor/resident Plexiglas plates were swapped
+(see Triki et al.(2019, 2020)). Here, we used instead a subset of these
+data in order to have an idea of cleaner fish preferences for the
+visitor plate, even if they do not reach the learning criterion within
+200 trials. To do so, we first extracted the trial-by-trial outcomes
+from the last two sessions (20 trials) of those who never reached the
+learning criterion for visitor plate (\(N = 45\) cleaner fish). For
+those who reached the learning criterion at some point during the test
+and passed to a reversal phase, we extracted the trial-by-trial outcomes
+from the last session (10 trials) before passing to reversal and the
+last 10 trials they were exposed to in the test (\(N = 75\) cleaner
+fish). We chose a combination of initial and reversal to quantify
+preference for the visitor client, given that it matches well the
+criteria chosen in previous analysis of the ephemeral reward task
+experimental set-up (Triki et al. 2019, 2020). In the supplementary
+material (Fig. \ref{fig:rawdata}) we show how our choice maps to the
+previously used criteria. For comparison, we also show a quantification
 of visitor preference based only on the initial phase of the task.
@@
 
-The aim of the analyses is to fit the key model parameters
-\(\gamma\) and \(\eta\), to the empirical data from Triki \emph{et al.}
-\citep{triki_Biological_2019, triki_Brain_2020} to test whether each or
-a combination of these effects is a better explanation for the pattern
-seen in the data. We used the ecological variables: cleaners, visitor clients,
-resident clients abundances and visitor clients leaving probability,\\
+The aim of the analyses is to fit the key model parameters \(\gamma\)
+and \(\eta\), to the empirical data from Triki et al.~ (2019, 2020) to
+test whether each or a combination of these effects is a better
+explanation for the pattern seen in the data. We used the ecological
+variables: cleaners, visitor clients, resident clients abundances and
+visitor clients leaving probability,\\
 as input to the models. As the response variable, we used cleaners'
 preference for visitors over residents in the ephemeral reward task.
-Finally, we used the preference for visitors resulting from the
-model simulations as the prediction for the response variable.
-We kept all other parameter values used for the model simulations constant,
-see Table \ref{tab:param}.
+Finally, we used the preference for visitors resulting from the model
+simulations as the prediction for the response variable. We kept all
+other parameter values used for the model simulations constant, see
+Table \ref{tab:param}.
 
@@
 variables and cleaner fish preferences for visitors, we needed to scale
-the absolute population densities of cleaner fish from the empirical data
-to a measure of relative abundances that captures client visitation patterns.
-This is because, in the model, relative abundances of clients
-define not only the probability of residents and visitors
-but also how often the cleaning station is empty (e.g.~there are no
-clients to be cleaned). The frequency with which clients visit the station
-is another variable, which in nature may vary among different client species
-depending on their ectoparasite loads. We do not have field estimates
-for species-specific parasite loads, especially not as a function of the site.
-In order to control for these aspects, we computed a measure of relative
-cleaner fish abundance for each reef site relative to
-absolute abundances and multiplied it
-by a scaling constant that changes the range of the variable. This scaling
-constant is hence meant to capture variation in the market conditions driven
-partly by cleaner fish abundance. We fitted the value of the scaling constant as
-part of the statistical inference. As for the visitor and resident
-abundances, we computed a relative measure with respect to the
-total client abundance, and weighted that by the rescaled relative absence
-of cleaners (\(1-\text{relative cleaner abundance}\)). Thus, all three measures
-of relative abundance sum up to 1, and can be used in the model as a proxy
-for the probability of having different options in the cleaning station.
-Note that we introduced the scaling constant to control for variation that
-is not captured by the model; its parameter distribution does not offer
-biological insights.
+the absolute population densities of cleaner fish from the empirical
+data to a measure of relative abundances that captures client visitation
+patterns. This is because, in the model, relative abundances of clients
+define not only the probability of residents and visitors but also how
+often the cleaning station is empty (e.g.~there are no clients to be
+cleaned). The frequency with which clients visit the station is another
+variable influencing the station occupancy, which in nature may vary
+among different client species depending on their ectoparasite loads. We
+do not have field estimates for species-specific parasite loads,
+especially not as a function of the site. In order to control for these
+aspects, we computed a measure of relative cleaner fish abundance for
+each reef site relative to absolute abundances and multiplied it by a
+scaling constant that changes the range of the variable. This scaling
+constant is hence meant to capture variation in the market conditions
+driven partly by cleaner fish abundance. We fitted the value of the
+scaling constant as part of the statistical inference. As for the
+visitor and resident abundances, we computed a relative measure with
+respect to the total client abundance, and weighted that by the rescaled
+relative absence of cleaners (\(1-\text{relative cleaner abundance}\)).
+Thus, all three measures of relative abundance sum up to 1, and can be
+used in the model as a proxy for the probability of having different
+options in the cleaning station. Note that we introduced the scaling
+constant to control for variation that is not captured by the model; its
+parameter distribution does not offer biological insights.
 
 Once we calculated the relative abundances, we obtained predictions from
-the model for each one of the locations and ran the Markov Chain. We started the
-chain with random values for the parameters of interest, then ran the
-computational model once for every reef site using as input the ecological
-explanatory variables. The model outputs the probability of choosing the visitor
-for each location \(p_i\), where \(i\) is the index for the 12 locations. Assuming a
-binomial distribution, the probability that each of the cleaner fish 20 choices
-in the ephemeral reward task was generated by the model
-is given by \(\binom{n}{k_ij}p^{k_{ij}}_i (1-p_i)^{n-k_{ij}}\);
-where \(k_{ij}\) is the number of times that cleaner fish \(j\) in reef site \(i\)
-chose the visitor over the resident; and \(n=20\) (due to our choice of using 20
-choices per cleaner fish). By taking the natural logarithm and summing over all
-the cleaner fish and reef sites, we obtained the log-likelihood of the data
-given the model and parameters. We then proposed a new set of parameters drawn
-from a uniform distribution centred around the old parameter set. The amplitude
-of the uniform distribution used for each parameter can be found in Table
-\ref{tab:param}. Subsequently, we ran the model and calculated the likelihood
-with the new parameter set. We then used the ratio of the two likelihoods to
-choose which parameter set to keep. New parameter sets with a higher likelihood
-than the old set replaced old ones, and those with a lower likelihood replaced
-current ones with a probability equal to the log-likelihood ratio.
-Given that we only used the likelihoods in the decision, we used an
-uninformative prior. Once we decided whether the new parameter set
-would replace the old one, we ran the model again to sample the likelihood
-distribution of the parameter set. We then started
-the cycle again by proposing a new set of parameters and repeated
-the process for \(1e^5\) steps. We ran 5 independent chains,
-discarded the first \(1000\) samples of each chain as burn in,
-and after that, we kept 1 in every 100 samples to avoid autocorrelation.
-The collection of parameters sets kept in
-all chains approximates the posterior distribution. We coded the model
-as well as the fitting algorithm in \emph{c++}, the diagnostics and visualization
-in R \citep{rcoreteam_Language_2021}. All codes are accessible at
-\(\color{red}{\text{include citation}}\)
+the model for each one of the locations and ran the Markov Chain. We
+started the chain with random values for the parameters of interest,
+then ran the computational model once for every reef site using as input
+the ecological explanatory variables. The model outputs the probability
+of choosing the visitor for each location \(p_i\), where \(i\) is the
+index for the 12 locations. Assuming a binomial distribution, the
+probability that each of the cleaner fish 20 choices in the ephemeral
+reward task was generated by the model is given by
+\(\binom{n}{k_ij}p^{k_{ij}}_i (1-p_i)^{n-k_{ij}}\); where \(k_{ij}\) is
+the number of times that cleaner fish \(j\) in reef site \(i\) chose the
+visitor over the resident; and \(n=20\) (due to our choice of using 20
+choices per cleaner fish). By taking the natural logarithm and summing
+over all the cleaner fish and reef sites, we obtained the log-likelihood
+of the data given the model and parameters. We then proposed a new set
+of parameters drawn from a uniform distribution centred around the old
+parameter set. The amplitude of the uniform distribution used for each
+parameter can be found in Table \ref{tab:param}. Subsequently, we ran
+the model and calculated the likelihood with the new parameter set. We
+then used the ratio of the two likelihoods to choose which parameter set
+to keep. New parameter sets with a higher likelihood than the old set
+replaced old ones, and those with a lower likelihood replaced current
+ones with a probability equal to the log-likelihood ratio. Given that we
+only used the likelihoods in the decision, we used an uninformative
+prior. Once we decided whether the new parameter set would replace the
+old one, we ran the model again to sample the likelihood distribution of
+the parameter set. We then started the cycle again by proposing a new
+set of parameters and repeated the process for \(1e^5\) steps. We ran 5
+independent chains, discarded the first \(1000\) samples of each chain
+as burn in, and after that, we kept 1 in every 100 samples to avoid
+autocorrelation. The collection of parameters sets kept in all chains
+approximates the posterior distribution. We coded the model as well as
+the fitting algorithm in \emph{c++}, the diagnostics and visualization
+in R (R Core Team 2021). All codes are accessible at \textless DOI:
+10.5281/zenodo.6338073\textgreater{}
 
 To compare the fit of the three alternative models, we used the
-distribution of pseudo \(R^2\) proposed by Mcfadden \citep{mcfadden_Conditional_1974}.
-Mcfadden's pseudo \(R^2\) is a standard measure of fit for logistic regression.
-In that context, \(pseudo-R^2\) uses the log-likelihood of the data given
-the model, relative to the log-likelihood of the data given a
-model without covariates, as a measure of fit. Our
-model is not a logistic regression, therefore we measured the \(pseudo-R^2\) in
-relation to the log-likelihood of a model
-with parameters \(\gamma\) and \(\eta\) set to zero. This, in practice,
-amounts to a model that has a neutral preference between the two options.
-We computed the pseudo \(R^2\) for all the samples of the posterior from
-the MCMC. Thus, we used these distributions of pseudo \(R^2\)'s as a measure of
-fit.
+distribution of pseudo \(R^2\) proposed by Mcfadden (McFadden 1974).
+Mcfadden's pseudo \(R^2\) is a standard measure of fit for logistic
+regression. In that context, \(pseudo-R^2\) uses the log-likelihood of
+the data given the model, relative to the log-likelihood of the data
+given a model without covariates, as a measure of fit. Our model is not
+a logistic regression, therefore we measured the \(pseudo-R^2\) in
+relation to the log-likelihood of a model with parameters \(\gamma\) and
+\(\eta\) set to zero. This, in practice, amounts to a model that has a
+neutral preference between the two options. We computed the pseudo
+\(R^2\) for all the samples of the posterior from the MCMC. We used
+these distributions of pseudo \(R^2\)'s as a measure of fit.
 
@@
 \begin{figure}
-
-{\centering \includegraphics[width=1\linewidth]{manuscript_1.0_files/figure-latex/post-1}
-
-}
-
-\caption{Posterior distributions for parameter values \(\gamma\) and \(\eta\) for
-the three models (``Full model'', ``chaining only'' and ``penalty only''). We show
-the kernel density estimates, below the mode (black dot) and the 65\%
-(light blue shade) and 95\% (grey shade) highest posterior density interval
-for the two parameters. On the top, panels a and b show posterior
-distributions for a full model, including chaining (\(\gamma\)) and penalty
-(\(\eta\)). Panel c, shows the \(\gamma\) estimate from model with only chaining.
-Panel d shows the \(\\eta\) estimate from a model with only penalty. Panel e,
-shows a measure of fit for all models, namely the distribution of pseudo-\(R^2\)
-obtained from sampling the posterior distribution of parameter values.}\label{fig:post}
+\includegraphics[width=1\linewidth]{manuscript_BE_files/figure-latex/post-1} \caption{Posterior distributions for parameter values $\gamma$ and $\eta$ for the three models (Full model, chaining only and penalty only).
+We show the kernel density estimates, below the mode (black dot) and the 66 (light blue shade) and 95\% (grey shade)  highest posterior density interval for the two parameters.
+On the top, panels a and b show posterior distributions for a full model, including chaining ($\gamma$) and penalty ($\eta$).
+Panel c, shows the $\gamma$ estimate from model with only chaining.
+Panel d shows the $\eta$ estimate from a model with only penalty.
+Panel e, shows a measure of fit for all models, namely the distribution of pseudo-$R^2$ obtained from sampling the posterior distribution of parameter values.}\label{fig:post}
 \end{figure}
@@
 Estimation of parameter values for the three models (full model,
-chaining and penalty), support chaining as the only mechanism
-cleaners use to account for the future effects of their actions;
-and thus to solve the ephemeral reward task. In the estimation of the
-parameter values of the full model, which includes both chaining and
-penalty, the bulk of the marginal posterior distribution of \(\eta\) which
-controls the strength of penalty is around 0 (Fig. \ref{fig:post}).
-As for \(\gamma\), controlling chaining, the 95\% confidence
-intervals also includes zero, but the mode of the posterior
-is around 0.5 (Fig. \ref{fig:post}, a). In the chaining model,
-where \(\eta\) is set to zero, the distribution of \(\gamma\) shifted
-to higher values, zero is no longer part of the 95\% credible interval
-of the parameter (Fig. \ref{fig:post}, c). In contrast, when we
-look at the model with only penalty, the posterior distribution
-of \(\eta\) is still centred around zero (Fig. \ref{fig:post}, d).
-Thus, the analysis of the estimates of individual parameter
-values in the three models only supports a strong
+chaining and penalty), support chaining as the only mechanism cleaners
+use to account for the future effects of their actions; and thus to
+solve the ephemeral reward task. In the estimation of the parameter
+values of the full model, which includes both chaining and penalty, the
+bulk of the marginal posterior distribution of \(\eta\) which controls
+the strength of penalty is around 0 (Fig. \ref{fig:post}). As for
+\(\gamma\), controlling chaining, the 95\% confidence intervals also
+includes zero, but the mode of the posterior is around 0.5 (Fig.
+\ref{fig:post}, a). In the chaining model, where \(\eta\) is set to
+zero, the distribution of \(\gamma\) shifted to higher values, zero is
+no longer part of the 95\% credible interval of the parameter (Fig.
+\ref{fig:post}, c). In contrast, when we look at the model with only
+penalty, the posterior distribution of \(\eta\) is still centred around
+zero (Fig. \ref{fig:post}, d). Thus, the analysis of the estimates of
+individual parameter values in the three models only supports a strong
 effect of chaining. Furthermore, the comparison of the models` fit
-favours the chaining model. In panel e of figure \ref{fig:post}
-we show the distribution of \(pseudo-R^2\) calculated using
-samples from the posterior distributions shown before.
-Note, \(pseudo-R^2\) can have negative values, which is when
-the log-likelihood of the model is lower than that of a model that
-triggers neutral preferences. Even though the peak of the three
-\(pseudo-R^2\) distributions were not very different, the model with only
-chaining produced a distribution of \(pseudo-R^2\) where more values
-were positive (to the right of the black line in Fig. \ref{fig:post} f). This
-shows that accounting for variation in the parameter estimates the
-model with chaining gives a better fit to the data, despite
-having one parameter less than the full model. We have not shown
-here the marginal posterior distributions of the scaling constant,
-given that they do not bring biological insight.
-Their visualizations can be found in the supplementary
-material (Fig. \ref{fig:scaConst}), as well as the diagnostics of the MCMCs
-(Figs. \ref{fig:diagnosticsfull},\ref{fig:diaggam},\ref{fig:diagNeg}).
+favours the chaining model. In panel e of figure \ref{fig:post} we show
+the distribution of \(pseudo-R^2\) calculated using samples from the
+posterior distributions shown before. Note, \(pseudo-R^2\) can have
+negative values, which is when the log-likelihood of the model is lower
+than that of a model that triggers neutral preferences. Even though the
+peak of the three \(pseudo-R^2\) distributions were not very different,
+the model with only chaining produced a distribution of \(pseudo-R^2\)
+where more values were positive (to the right of the black line in Fig.
+\ref{fig:post} e). This shows that accounting for variation in the
+parameter estimates the model with chaining gives a better fit to the
+data, despite having one parameter less than the full model. We have not
+shown here the marginal posterior distributions of the scaling constant,
+given that they do not bring biological insight. Their visualizations
+can be found in the supplementary material (Fig. \ref{fig:scaConst}), as
+well as the diagnostics of the MCMCs (Figs.
+\ref{fig:diagnosticsfull},\ref{fig:diaggam},\ref{fig:diagNeg}).
 
 \begin{figure}
-
-{\centering \includegraphics[width=1\linewidth]{manuscript_1.0_files/figure-latex/pred-1}
-
-}
-
-\caption{Observed and predicted probability of choosing a visitor.
-Left-hand side panel: colour contour shows the prediction from the
-learning model using the mode of the posterior distributions of parameters
-recovered by the statistical analysis. Dots show the frequency of visitor
-choices for the 12 reef sites, as well as the corresponding relative
-cleaner fish abundance (x axis) and frequency of visitors clients leaving
-the cleaning station (y axis). Right-hand side panels: Variation of the
-predicted probabilities of choosing a visitor over a resident and their
-observed values for 12 locations. Circles show the mean prediction for
-each location from 100 samples taken from the posterior distribution.
-Thick and thin bars show the 66 and 95\% credible interval, respectively,
-taken from those posterior samples. Squares show the predictions used for the
-panel on the right-hand side. Colour coding denotes different reef site/year
-of the data collection (see Empirical data section). The black line corresponds
-to a perfect match between observed and predicted probabilities. Upper
-panels (a and b) show predictions from a model including chaining and
-penalty; middle panels (c and d) from a model with only chaining; lower
-panels (e and f) from a model with penalty only.}\label{fig:pred}
+\includegraphics[width=1\linewidth]{manuscript_BE_files/figure-latex/pred-1} \caption{Observed and predicted probability of choosing a visitor.
+Left-hand side panel: colour contour shows the prediction from the learning model using the mode of the posterior distributions of parameters recovered by the statistical analysis.
+Dots show the frequency of visitor choices for the 12 reef sites, as well as the corresponding relative cleaner fish abundance (x axis) and frequency of visitors clients leaving the cleaning station (y axis).
+Right-hand side panels: Variation of the predicted probabilities  of choosing a visitor over a resident and their observed values for 12 locations.
+Circles show the mean prediction for each location from 100 samples taken from the posterior distribution.
+Thick and thin bars show the 66 and 95\% credible interval, respectively, taken from those posterior samples.
+Squares show the predictions used for the panel on the right-hand side.
+Colour coding denotes different reef site/year of the data collection (see Empirical data section).
+The black line corresponds to a perfect match between observed and predicted probabilities.
+Upper panels (a and b) show predictions from a model including chaining and penalty; middle panels (c and d) from a  model with only chaining; lower panels (e and f) from a model with penalty only.}\label{fig:pred}
 \end{figure}
 
-The main reason for chaining and penalty to give different
-predictions is the way that cleaner fish relative abundance influences the
+The main reason for chaining and penalty to give different predictions
+is the way that cleaner fish relative abundance influences the
 preference for the visitor clients. Visitor leaving probability has a
 similar positive effect on the probability of choosing the visitor
-clients on all three models, they all predict an increase preference
-for visitors as the visitor probability increases (Fig. \ref{fig:pred}).
-In contrast, cleaner fish relative abundance has a different effect in the
-model with only chaining, compared to the other two models,
-full model and penalty. In the model with only chaining, only intermediate
-cleaner fish abundance triggers a preference for the visitor
-clients (Fig. \ref{fig:pred} c). In both models with penalty,
-both intermediate and low cleaner abundance triggered a preference
-for the visitor (Fig. \ref{fig:pred} a,e). Note, however, we calculated
-preferences shown in figure \ref{fig:pred} left panels by using only the mode
-of the posterior distributions, and by holding constant the balance between
+clients on all three models, they all predict an increase preference for
+visitors as the visitor probability increases (Fig. \ref{fig:pred}). In
+contrast, cleaner fish relative abundance has a different effect in the
+model with only chaining, compared to the other two models, full model
+and penalty. In the model with only chaining, only intermediate cleaner
+fish abundance triggers a preference for the visitor clients (Fig.
+\ref{fig:pred} c). In both models with penalty, both intermediate and
+low cleaner abundance triggered a preference for the visitor (Fig.
+\ref{fig:pred} a,e). Note, however, we calculated preferences shown in
+figure \ref{fig:pred} left panels by using only the mode of the
+posterior distributions, and by holding constant the balance between
 resident and visitors´ abundances. Panels on the right, show how close
@@
 In this study, our main aim was to unravel which of two potential
-cognitive mechanisms, chaining of events, penalty,
-or their combination, best explains wild-caught cleaner fish
-performance in the ephemeral reward task, while accounting for their
-ecological conditions. To evaluate the merits of each of these two mechanisms
-separately and combined, we considered cleaner fish performance
-in the lab test to have its origin from the rule these fish applied
-in their natural environment. That is, individuals that
-solved the task already had a preference for
-visitors clients and generalized this rule to the lab conditions
-once being familiar with the task.
+cognitive mechanisms, chaining of events, penalty, or their combination,
+best explains wild-caught cleaner fish performance in the ephemeral
+reward task, while accounting for their ecological conditions. To
+evaluate the merits of each of these two mechanisms separately and
+combined, we considered cleaner fish performance in the lab test to have
+its origin from the rule these fish applied in their natural
+environment. That is, individuals that solved the task already had a
+preference for visitor clients and generalized this rule to the lab
+conditions once being familiar with the task.
 
-While all three models captured well the positive relationship between visitor
-leaving behaviour and cleaner fish performance in
-the market task \citep{triki_Biological_2019}, only the chaining mechanism
-predicted that cleaner fish performance in the task should be low in
-habitats with low cleaner-to-client ratios, regardless of the
-visitor leaving probability. In contrast, models including
-negative reward predicted the highest performance in the ephemeral
-reward task when relative cleaner fish abundance is low, particularly
-together with a high probability of visitor leaving (Fig. \ref{fig:pred}).
-Low relative cleaner fish abundances mean the market has an excess of demand for
-cleaning services. In the models, this translates to a cleaning station
-that is frequently full. Thus, when a visitor leaves, it is likely that the
-cleaner fish will have access to another client in the next step. Therefore,
-there will not be much difference in future reward between choosing
-a visitor and a resident, and cleaners will not develop a preference for the
-visitor in these conditions. On the other hand, the effect of negative reward
-on cleaner fish preference is the opposite, as in a busy cleaning station, to
-that of chaining. cleaner fish will get more often the resident-visitor
-state and will develop a preference for the visitor faster.
-At high cleaner fish abundances, the resident-visitor state
-becomes so rare that neither mechanism is very efficient
-at generating a preference for visitors. When facing the
-resident-visitor choice, it is still best to choose the visitor; however,
-the learning machinery will not be able to develop this preference
-efficiently. Overall, the models suggest that chaining is the cognitive
-mechanism that allows cleaner fish to adaptively adjust to their
-biological market ecological conditions.
+While all three models captured well the positive relationship between
+visitor leaving behavior and cleaner fish performance in the market task
+(Triki et al. 2019), only the chaining mechanism predicted that cleaner
+fish performance in the task should be low in habitats with low
+cleaner-to-client ratios, regardless of the visitor leaving probability.
+In contrast, models including negative reward predicted the highest
+performance in the ephemeral reward task when relative cleaner fish
+abundance is low, particularly together with a high probability of
+visitor leaving (Fig. \ref{fig:pred}). Low relative cleaner fish
+abundances mean the market has an excess of demand for cleaning
+services. In the models, this translates to a cleaning station that is
+frequently full. Thus, when a visitor leaves, it is likely that the
+cleaner fish will have access to another client in the next step.
+Therefore, there will not be much difference in future reward between
+choosing a visitor and a resident, and cleaners will not develop a
+preference for the visitor in these conditions. On the other hand, the
+effect of negative reward on cleaner fish preference is the opposite, as
+in a busy cleaning station, to that of chaining. Cleaner fish will get
+more often the resident-visitor state and will develop a preference for
+the visitor faster. At high cleaner fish abundances, the
+resident-visitor state becomes so rare that neither mechanism is very
+efficient at generating a preference for visitors. When facing the
+resident-visitor choice, it is still best to choose the visitor;
+however, the learning machinery will not be able to develop this
+preference efficiently. Overall, the models suggest that chaining is the
+cognitive mechanism that allows cleaner fish to adaptively adjust to
+their biological market ecological conditions.
 
@@
 densities and giving service priority to the visitor plate in the
-ephemeral reward task, as well as cleaner fish living at low
-densities but denying service priority to the visitor plate possess
-larger forebrains; a key teleost brain region associated with
-behavioural flexibility and social intelligence. Those failing to
-show optimized decision-rules given their local ecological
-conditions had relatively smaller forebrains \citep{triki_Brain_2020}.
-Triki \emph{et al.} refer to the former as socially competent cleaner fish,
-while the second group as socially incompetent cleaner fish.
-Social competence is the ability to optimise social behaviour
-to the available social information \citep{taborsky_Social_2012, bshary_Cooperation_2015, varela_Correlated_2020}. Our analyses yielded no
-evidence that the difference in social competence with respect to the local
-ecological conditions and associated brain morphology,
-found by Triki \emph{et al} \citep{triki_Brain_2020}, is due to the mechanism
-used to incorporate future consequences. It is conceivable that
-high performing individuals from low population densities reef sites
-use negative reinforcement instead of chaining, but in that
-case, negative reinforcement should have explained at least
-part of the data. Configurational learning or
-chunking \citep{sutherland_Configural_1989, miller_Magical_1956},
-the second component necessary to solve the ephemeral
-reward task \citep{quinones_Reinforcement_2019}, was
-not varied in the models we analysed here. However, while chunking tendencies
-should vary to allow individuals to adapt to their local conditions
-\citep{prat_Modelling_2022, kolodny_Evolution_2014}, systematic differences
-in individual chunking tendencies would not explain how socially
-competent decisions vary as a function of relative abundance.
-Therefore, it remains currently unclear what cell-demanding
-mechanisms may cause variation in social competence that
-translates into site-specific variation in performance in the
+ephemeral reward task, as well as cleaner fish living at low densities
+but denying service priority to the visitor plate possess larger
+forebrains; a key teleost brain region associated with behavioural
+flexibility and social intelligence. Those failing to show optimized
+decision-rules given their local ecological conditions had relatively
+smaller forebrains (Triki et al. 2020). Triki et al.~refer to the former
+as socially competent cleaner fish, while the second group as socially
+incompetent cleaner fish. Social competence is the ability to optimise
+social behavior to the available social information (Taborsky and
+Oliveira 2012; Bshary and Oliveira 2015; Varela, Teles, and Oliveira
+2020). Our analyses yielded no evidence that the difference in social
+competence with respect to the local ecological conditions and
+associated brain morphology, found by Triki et al. (2020), is due to the
+mechanism used to incorporate future consequences. It is conceivable
+that high performing individuals from low population densities reef
+sites use negative reinforcement instead of chaining, but in that case,
+negative reinforcement should have explained at least part of the data.
+Configurational learning or chunking (Sutherland and Rudy 1989; Miller
+1956), the second component necessary to solve the ephemeral reward task
+(Quiñones et al. 2019), was not varied in the models we analysed here.
+However, while chunking tendencies should vary to allow individuals to
+adapt to their local conditions (Prat, Bshary, and Lotem 2022; Kolodny,
+Edelman, and Lotem 2014), systematic differences in individual chunking
+tendencies would not explain how socially competent decisions vary as a
+function of relative abundance. Therefore, it remains currently unclear
+what cell-demanding mechanisms may cause variation in social competence
+that translates into site-specific variation in performance in the
 ephemeral reward task.
@@
 ignores alternative channels of information that could be relevant in
-market-like situations. For example, the model does not investigate whether
-cleaner fish actually assess the frequency of client visits or a mean frequency
-of visitors leaving. The updating learning mechanism for the development
-of preferences works on a trial-by-trial basis. In the model, cleaner fish
-do not need to assess the actual state of the market, \emph{i.e.} their abundance,
-the abundance of residents and visitors, and client visitation rate as an
-indicator of demand. They only need to assess the short-term
-consequences of their own decisions on food intake and chain them.
-Also, for the sake of simplicity, the model ignores
-the process by which cleaner fish discriminate
-residents and visitor clients. A model that accounts for this discrimination
-probably would involve the development of preferences for morphological or
-behavioural features that are statistically associated with visitors
-or residents. For example, visitors are on average larger
-than residents in body size \citep{bshary_Cleaner_2001}, and contrary to
-residents, they are less likely to chase a cleaner fish that fails to cooperate
-and instead cheats its client by taking a bite of mucus
-\citep{bshary_Asymmetric_2002}. Given these associations, chaining might
-produce the decision-rule ``choose the larger client and/or the less aggressive
-client'', which is not a useful rule in the standard ephemeral reward task.
+market-like situations. For example, the model does not investigate
+whether cleaner fish actually assess the frequency of client visits or a
+mean frequency of visitors leaving. The updating learning mechanism for
+the development of preferences works on a trial-by-trial basis. In the
+model, cleaner fish do not need to assess the actual state of the
+market, \emph{i.e.} their abundance, the abundance of residents and
+visitors, and client visitation rate as an indicator of demand. They
+only need to assess the short-term consequences of their own decisions
+on food intake and chain them. Also, for the sake of simplicity, the
+model ignores the process by which cleaner fish discriminate residents
+and visitor clients. A model that accounts for this discrimination
+probably would involve the development of preferences for morphological
+or behavioural features that are statistically associated with visitors
+or residents. For example, visitors are on average larger than residents
+in body size (Bshary 2001), and contrary to residents, they are less
+likely to chase a cleaner fish that fails to cooperate and instead
+cheats its client by taking a bite of mucus (Bshary and Grutter 2002).
+Given these associations, chaining might produce the decision-rule
+``choose the larger client and/or the less aggressive client'', which is
+not a useful rule in the standard ephemeral reward task.
 
-In conclusion, our study shows that variation in cognitive performance as
-a function of the local ecological conditions may set the stage for the use of
-mechanistic modelling to identify the cognitive processes underlying
-learning in animals. The combination overcomes the limitations
-of the general philosophy in animal cognition to apply the logic of
-Lloyd Morgen's canon (Occam's razor). Cognitive experiments with the
-aim of excluding basic reinforcement learning as a potential
-explanation (operant and/or classical conditioning) of performance
-often employ one trial experiments requiring animals to solve the
-task on the first possible occasion.
-For example, any theory of mind task needs to be solved in the first
-trial in order to exclude fast conditioning \citep{heyes_Theory_1998}.
-Similarly, subjects need to solve a social learning task on the first
-trial to accept imitation as a mechanism over stimulus/local
-enhancement. Such strict conditions are virtually never met. For
-example, potato washing by Japanese macaques, an iconic example of
-social learning, took several years to spread within the group
-\citep{kawamura_Process_1959}, meaning that any learner had been repeatedly
-exposed to demonstrations before acquisition. Importantly, Galef
-\citep{galef_Question_1992} refuted imitation as a mechanism not simply because
-of the repeated exposure but because a (rather qualitative) analysis of
-the spread of potato washing across individuals did not follow the
-prediction based on imitation learning (see also
-\citep{hirata_SweetPotato_2001}). In our case, the number of trials it took
-cleaners to learn the solution to the ephemeral rewards task
-would never allow excluding an important role of
-penalty based on the data
-alone. However, fitting model predictions to our comprehensive empirical
-data set revealed that a more complex mechanism, estimation of future reward,
-fits the data better.
+In conclusion, our study shows that variation in cognitive performance
+as a function of the local ecological conditions may set the stage for
+the use of mechanistic modelling to identify the cognitive processes
+underlying learning in animals. The combination overcomes the
+limitations of the general philosophy in animal cognition to apply the
+logic of Lloyd Morgen's canon (Occam's razor). Cognitive experiments
+with the aim of excluding basic reinforcement learning as a potential
+explanation (operant and/or classical conditioning) of performance often
+employ one trial experiments requiring animals to solve the task on the
+first possible occasion. For example, any theory of mind task needs to
+be solved in the first trial in order to exclude fast conditioning (C.
+M. Heyes 1998). Similarly, subjects need to solve a social learning task
+on the first trial to accept imitation as a mechanism over
+stimulus/local enhancement. Such strict conditions are virtually never
+met. For example, potato washing by Japanese macaques, an iconic example
+of social learning, took several years to spread within the group
+(Kawamura 1959), meaning that any learner had been repeatedly exposed to
+demonstrations before acquisition. Importantly, Galef (1992) refuted
+imitation as a mechanism not simply because of the repeated exposure but
+because a (rather qualitative) analysis of the spread of potato washing
+across individuals did not follow the prediction based on imitation
+learning (see also Hirata, Watanabe, and Masao (2001)). In our case, the
+number of trials it took cleaners to learn the solution to the ephemeral
+rewards task would never allow excluding an important role of penalty
+based on the data alone. However, fitting model predictions to our
+comprehensive empirical data set revealed that a more complex mechanism,
+estimation of future reward, fits the data better.
 
@@
 \begin{figure}
-
-{\centering \includegraphics{manuscript_1.0_files/figure-latex/rawdata-1}
-
-}
-
-\caption{Relation between the response variable used in this study and the
-criteria used in previous studies to assess performance in the ephemeral reward
-task. In the x axis, we classified the performance of cleaner fish according to
-whether they developed a preference for the visitor in the initial round,
-in the initial and reversal, or none of them. In the y axis, we add the choices
-of two experimental sessions: panel on the left uses one session from the initial
-round and one from the reversal round when possible
-(as described in the main text); panel on the right uses two sessions from the
-initial round for all fish.}\label{fig:rawdata}
+\includegraphics[width=1\linewidth]{manuscript_BE_files/figure-latex/rawdata-1} \caption{Relation between the response variable used in this study and the criteria used in previous studies to assess performance in the ephemeral reward task.
+In the x axis, we classified the performance of cleaner fish according to whether they developed a preference for the visitor in the initial round, in the initial and reversal, or none of them.
+In the y axis, we add the choices of two experimental sessions: panel on the left uses one session from the initial round and one from the reversal round when possible (as described in the main text); panel on the right uses two sessions from the initial round for all fish.}\label{fig:rawdata}
 \end{figure}
@@
 \begin{figure}[H]
+\includegraphics[width=0.95\linewidth,]{manuscript_BE_files/figure-latex/scaConst-1} \caption{Posterior distributions for scaling constant for the three models (Full model, chaining only and penalty only).
+We show the kernel density estimates, below the mode (black dot) and the 65\% (light blue shade) and 95\% (grey shade)  highest posterior density interval.
+On the top, panel a shows the posterior distribution from the full model; panel b from the model with only chaining; and panel c from a model with only penalty.}\label{fig:scaConst}
+\end{figure}
 
-{\centering \includegraphics[width=0.95\linewidth,]{manuscript_1.0_files/figure-latex/scaConst-1}
+\begin{figure}
+\includegraphics[width=1\linewidth]{manuscript_BE_files/figure-latex/diagnosticsfull-1} \caption{MCMC convergence diagnostics for the full model.
+On the left trace-plots, on the right changes along the chain of the Gelman and Rubin shrink factor.}\label{fig:diagnosticsfull}
+\end{figure}
 
-}
+\begin{figure}
+\includegraphics[width=1\linewidth]{manuscript_BE_files/figure-latex/diaggam-1} \caption{MCMC convergence diagnostics for the chaining model.
+On the left trace-plots, on the right changes along the chain of the Gelman and Rubin shrink factor }\label{fig:diaggam}
+\end{figure}
 
-\caption{Posterior distributions for scaling constant for the three models
-(``Full model'', chaining only'' and ``penalty only''). We show the kernel
-density estimates, below the mode (black dot) and the 65\% (light blue shade)
-and 95\% (grey shade) highest posterior density interval. On the top,
-panel a shows the posterior distribution from the full model; panel b from
-the model with only chaining; and panel c from a model with only penalty.}\label{fig:scaConst}
+\begin{figure}
+\includegraphics[width=1\linewidth]{manuscript_BE_files/figure-latex/diagNeg-1} \caption{MCMC convergence diagnostics for the penalty model.
+On the left trace-plots, on the right changes along the chain of the Gelman and Rubin shrink factor}\label{fig:diagNeg}
 \end{figure}
@@
 
-\begin{figure}
+\hypertarget{references}{%
+\section*{References}\label{references}}
+\addcontentsline{toc}{section}{References}
 
-{\centering \includegraphics{manuscript_1.0_files/figure-latex/diagnosticsfull-1}
+\hypertarget{refs}{}
+\begin{CSLReferences}{1}{0}
+\leavevmode\vadjust pre{\hypertarget{ref-axen_Signalling_1996}{}}%
+Axén, Annkristin H., Olof Leimar, and Veronika Hoffman. 1996.
+{``Signalling in a Mutualistic Interaction.''} \emph{Animal Behaviour}
+52 (2): 321--33. \url{https://doi.org/10.1006/anbe.1996.0178}.
 
-}
+\leavevmode\vadjust pre{\hypertarget{ref-behrens_Associative_2008}{}}%
+Behrens, Timothy E. J., Laurence T. Hunt, Mark W. Woolrich, and Matthew
+F. S. Rushworth. 2008. {``Associative Learning of Social Value.''}
+\emph{Nature} 456 (7219): 245--49.
+\url{https://doi.org/10.1038/nature07538}.
 
-\caption{MCMC convergence diagnostics for the full model.
-On the left trace-plots, on the right changes along the chain of the
-Gelman and Rubin's shrink factor \citep{brooks_General_1998}.}\label{fig:diagnosticsfull}
-\end{figure}
+\leavevmode\vadjust pre{\hypertarget{ref-brandon_Computational_2002}{}}%
+Brandon, Susan E., Edgar H. Vogel, and Allan R. Wagner. 2002.
+{``Computational {Theories} of {Classical} {Conditioning}.''} In \emph{A
+{Neuroscientist}'s {Guide} to {Classical} {Conditioning}}, edited by
+John W. Moore, 232--310. New York, NY: Springer.
+\url{https://doi.org/10.1007/978-1-4419-8558-3_7}.
 
-\begin{figure}
+\leavevmode\vadjust pre{\hypertarget{ref-bshary_Cleaner_2001a}{}}%
+Bshary, Redouan. 2001. {``The Cleaner Fish Market.''} In \emph{Economics
+in {Nature}: {Social} {Dilemmas}, {Mate} {Choice} and {Biological}
+{Markets}}, edited by Jan A. R. A. M. Van Hooff, Peter Hammerstein, and
+Ronald Noë, 146--72. Cambridge: Cambridge University Press.
+\url{https://doi.org/10.1017/CBO9780511752421.010}.
 
-{\centering \includegraphics{manuscript_1.0_files/figure-latex/diaggam-1}
+\leavevmode\vadjust pre{\hypertarget{ref-bshary_Asymmetric_2002}{}}%
+Bshary, Redouan, and Alexandra S Grutter. 2002. {``Asymmetric Cheating
+Opportunities and Partner Control in a Cleaner Fish Mutualism.''}
+\emph{Animal Behaviour} 63 (3): 547--55.
+\url{https://doi.org/10.1006/anbe.2001.1937}.
 
-}
+\leavevmode\vadjust pre{\hypertarget{ref-bshary_Cooperation_2015}{}}%
+Bshary, Redouan, and Rui F Oliveira. 2015. {``Cooperation in Animals:
+Toward a Game Theory Within the Framework of Social Competence.''}
+\emph{Current Opinion in Behavioral Sciences}, Social behavior, 3
+(June): 31--37. \url{https://doi.org/10.1016/j.cobeha.2015.01.008}.
 
-\caption{MCMC convergence diagnostics for the chaining model.
-On the left trace-plots, on the right changes along the chain of the
-Gelman and Rubin's shrink factor \citep{brooks_General_1998}}\label{fig:diaggam}
-\end{figure}
+\leavevmode\vadjust pre{\hypertarget{ref-bshary_Choosy_2002}{}}%
+Bshary, Redouan, and Daniel Schäffer. 2002. {``Choosy Reef Fish Select
+Cleaner Fish That Provide High-Quality Service.''} \emph{Animal
+Behaviour} 63 (3): 557--64.
+\url{https://doi.org/10.1006/anbe.2001.1923}.
 
-\begin{figure}
+\leavevmode\vadjust pre{\hypertarget{ref-dally_Foodcaching_2006}{}}%
+Dally, Joanna M., Nathan J. Emery, and Nicola S. Clayton. 2006.
+{``Food-Caching Western Scrub-Jays Keep Track of Who Was Watching
+When.''} \emph{Science (New York, N.Y.)} 312 (5780): 1662--65.
+\url{https://doi.org/10.1126/science.1126539}.
 
-{\centering \includegraphics{manuscript_1.0_files/figure-latex/diagNeg-1}
+\leavevmode\vadjust pre{\hypertarget{ref-demaire_Reduced_2020}{}}%
+Demairé, Camille, Zegni Triki, Sandra A. Binning, Gaëtan Glauser,
+Dominique G. Roche, and Redouan Bshary. 2020. {``Reduced Access to
+Cleaner Fish Negatively Impacts the Physiological State of Two Resident
+Reef Fishes.''} \emph{Marine Biology} 167 (4): 48.
+\url{https://doi.org/10.1007/s00227-020-3658-2}.
 
-}
+\leavevmode\vadjust pre{\hypertarget{ref-dubois_Model_2021}{}}%
+Dubois, Thibault, Cristian Pasquaretta, Andrew B. Barron, Jacques
+Gautrais, and Mathieu Lihoreau. 2021. {``A Model of Resource
+Partitioning Between Foraging Bees Based on Learning.''} \emph{PLOS
+Computational Biology} 17 (7): e1009260.
+\url{https://doi.org/10.1371/journal.pcbi.1009260}.
 
-\caption{MCMC convergence diagnostics for the penalty model.
-On the left trace-plots, on the right changes along the chain of the
-Gelman and Rubin's shrink factor \citep{brooks_General_1998}}\label{fig:diagNeg}
-\end{figure}
+\leavevmode\vadjust pre{\hypertarget{ref-enquist_Power_2016}{}}%
+Enquist, Magnus, Johan Lind, and Stefano Ghirlanda. 2016. {``The Power
+of Associative Learning and the Ontogeny of Optimal Behaviour.''}
+\emph{Royal Society Open Science} 3 (11): 160734.
+\url{https://doi.org/10.1098/rsos.160734}.
 
-\ethics{The Animal Ethics Committee of the Queensland government (DAFF)
-approved the project (CA 2016/05/970 and CA 2017/05/1063).}
+\leavevmode\vadjust pre{\hypertarget{ref-farashahi_Featurebased_2017}{}}%
+Farashahi, Shiva, Katherine Rowe, Zohra Aslami, Daeyeol Lee, and Alireza
+Soltani. 2017. {``Feature-Based Learning Improves Adaptability Without
+Compromising Precision.''} \emph{Nature Communications} 8 (1): 1768.
+\url{https://doi.org/10.1038/s41467-017-01874-w}.
 
-\dataccess{Please provide details on the data availability.}
+\leavevmode\vadjust pre{\hypertarget{ref-farashahi_Learning_2020}{}}%
+Farashahi, Shiva, Jane Xu, Shih-Wei Wu, and Alireza Soltani. 2020.
+{``Learning Arbitrary Stimulus-Reward Associations for Naturalistic
+Stimuli Involves Transition from Learning about Features to Learning
+about Objects.''} \emph{Cognition} 205 (December): 104425.
+\url{https://doi.org/10.1016/j.cognition.2020.104425}.
 
-\aucontribute{AQ and RB designed the study. ZT collected the data. AQ developed the model and
-fitted the model parameters to the data. AQ, RB and ZT wrote the manuscript.}
+\leavevmode\vadjust pre{\hypertarget{ref-galef_Question_1992}{}}%
+Galef, Bennett G. 1992. {``The Question of Animal Culture.''}
+\emph{Human Nature} 3 (2): 157--78.
+\url{https://doi.org/10.1007/BF02692251}.
 
-\competing{The authors declate no conflict of interests.}
+\leavevmode\vadjust pre{\hypertarget{ref-heyes_Theory_1998}{}}%
+Heyes, C. M. 1998. {``Theory of Mind in Nonhuman Primates.''}
+\emph{Behavioral and Brain Sciences} 21 (1): 101--14.
+\url{https://doi.org/10.1017/S0140525X98000703}.
 
-\funding{This work was supported by the Swiss National Science Foundation (grants
-number: 31003A\_153067/1 and 310030B\_173334/1 to R.B.).}
+\leavevmode\vadjust pre{\hypertarget{ref-heyes_Simple_2012}{}}%
+Heyes, Cecilia. 2012. {``Simple Minds: A Qualified Defence of
+Associative Learning.''} \emph{Philosophical Transactions of the Royal
+Society B: Biological Sciences} 367 (1603): 2695--2703.
+\url{https://doi.org/10.1098/rstb.2012.0217}.
 
-\ack{ZT and RB kindly thank the staff of Lizard Island Research Station, Dominique
-Roche, Sharon Wismer, Olivia Rey,Sandra Ann Binning, Elena Levorato and William McNeely for their
-field support. AQ thanks Florian Hartig for statistical advice.}
+\leavevmode\vadjust pre{\hypertarget{ref-hirata_SweetPotato_2001}{}}%
+Hirata, Satoshi, Kunio Watanabe, and Kawai Masao. 2001.
+{``{`{Sweet}-{Potato} {Washing}'} {Revisited}.''} In \emph{Primate
+{Origins} of {Human} {Cognition} and {Behavior}}, edited by Tetsuro
+Matsuzawa, 487--508. Tokyo: Springer Japan.
+\url{https://doi.org/10.1007/978-4-431-09423-4_24}.
 
-\bibliographystyle{RS}
-\bibliography{Cleanerlearning.bib}
+\leavevmode\vadjust pre{\hypertarget{ref-kawamura_Process_1959}{}}%
+Kawamura, Syunzo. 1959. {``The Process of Sub-Culture Propagation Among
+{Japanese} Macaques.''} \emph{Primates} 2 (1): 43--60.
+\url{https://doi.org/10.1007/BF01666110}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-kolodny_Evolution_2014}{}}%
+Kolodny, O., S. Edelman, and A. Lotem. 2014. {``The Evolution of
+Continuous Learning of the Structure of the Environment.''}
+\emph{Journal of The Royal Society Interface} 11 (92): 20131091--91.
+\url{https://doi.org/10.1098/rsif.2013.1091}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-macphail_Brain_1982}{}}%
+Macphail, Euan M. 1982. \emph{Brain and {Intelligence} in
+{Vertebrates}}. Clarendon Press.
+
+\leavevmode\vadjust pre{\hypertarget{ref-marler_Species_1989}{}}%
+Marler, Peter, and Susan Peters. 1989. {``Species Differences in
+Auditory Responsiveness in Early Vocal Learning.''} In \emph{The
+Comparative Psychology of Audition: {Perceiving} Complex Sounds},
+243--73. Hillsdale, NJ, US: Lawrence Erlbaum Associates, Inc.
+
+\leavevmode\vadjust pre{\hypertarget{ref-mcfadden_Conditional_1974}{}}%
+McFadden, Daniel. 1974. {``Conditional Logit Analysis of Qualitative
+Choice Behavior.''} \emph{Frontiers in Econometrics}, Frontiers in
+econometrics. - {New} {York} {[}u.a.{]} : {Academic} {Press}, {ISBN}
+0-12-776150-0. - 1974, p. 105-142,.
+
+\leavevmode\vadjust pre{\hypertarget{ref-miller_Magical_1956}{}}%
+Miller, George A. 1956. {``The Magical Number Seven, Plus or Minus Two:
+{Some} Limits on Our Capacity for Processing Information.''}
+\emph{Psychological Review} 63 (2): 81.
+
+\leavevmode\vadjust pre{\hypertarget{ref-noe_Biological_1995a}{}}%
+Noë, Ronald, and Peter Hammerstein. 1995. {``Biological Markets.''}
+\emph{Trends in Ecology \& Evolution} 10 (8): 336--39.
+\url{https://doi.org/10.1016/S0169-5347(00)89123-5}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-prat_Modelling_2022}{}}%
+Prat, Yosef, Redouan Bshary, and Arnon Lotem. 2022. {``Modelling How
+Cleaner Fish Approach an Ephemeral Reward Task Demonstrates a Role for
+Ecologically Tuned Chunking in the Evolution of Advanced Cognition.''}
+\emph{PLOS Biology} 20 (1): e3001519.
+\url{https://doi.org/10.1371/journal.pbio.3001519}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-quinones_Reinforcement_2019}{}}%
+Quiñones, Andrés E., Olof Leimar, Arnon Lotem, and Redouan Bshary. 2019.
+{``Reinforcement {Learning} {Theory} {Reveals} the {Cognitive}
+{Requirements} for {Solving} the {Cleaner} {Fish} {Market} {Task}.''}
+\emph{The American Naturalist}, December, 000--000.
+\url{https://doi.org/10.1086/707519}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-rcoreteam_Language_2021}{}}%
+R Core Team. 2021. {``R: {A} Language and Environment for Statistical
+Computing.''} Manual. Vienna, Austria. \url{https://www.R-project.org/}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-rescorla_Theory_1972}{}}%
+Rescorla, R. A., and A. R. A. Wagner. 1972. {``A Theory of {Pavlovian}
+Conditioning: Variations in the Effectiveness of Reinforcement and
+Non-Reinforcement.''} In \emph{Classical Conditioning {II}: Current
+Research and Theory}, edited by Abraham H. Black and William Frederick
+Prokasy. New York: Appleton-Century-Crofts.
+
+\leavevmode\vadjust pre{\hypertarget{ref-ros_Does_2011}{}}%
+Ros, Albert F. H., Jeanne Lusa, Meghann Meyer, Marta Soares, Rui F.
+Oliveira, Michel Brossard, and Redouan Bshary. 2011. {``Does Access to
+the Bluestreak Cleaner Wrasse {Labroides} Dimidiatus Affect Indicators
+of Stress and Health in Resident Reef Fishes in the {Red} {Sea}?''}
+\emph{Hormones and Behavior} 59 (1): 151--58.
+\url{https://doi.org/10.1016/j.yhbeh.2010.11.006}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-salwiczek_Adult_2012}{}}%
+Salwiczek, Lucie H., Laurent Prétôt, Lanila Demarta, Darby Proctor,
+Jennifer Essler, Ana I. Pinto, Sharon Wismer, Tara Stoinski, Sarah F.
+Brosnan, and Redouan Bshary. 2012. {``Adult {Cleaner} {Wrasse}
+{Outperform} {Capuchin} {Monkeys}, {Chimpanzees} and {Orang}-Utans in a
+{Complex} {Foraging} {Task} {Derived} from {Cleaner} -- {Client} {Reef}
+{Fish} {Cooperation}.''} \emph{PLOS ONE} 7 (11): e49068.
+\url{https://doi.org/10.1371/journal.pone.0049068}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-schultz_Neuronal_2015}{}}%
+Schultz, Wolfram. 2015. {``Neuronal {Reward} and {Decision} {Signals}:
+{From} {Theories} to {Data}.''} \emph{Physiological Reviews} 95 (3):
+853--951. \url{https://doi.org/10.1152/physrev.00023.2014}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-shettleworth_Cognition_2009}{}}%
+Shettleworth, Sara J. 2009. \emph{Cognition, {Evolution}, and
+{Behavior}}. 2 edition. Oxford ; New York: Oxford University Press.
+
+\leavevmode\vadjust pre{\hypertarget{ref-sih_Linking_2012}{}}%
+Sih, Andrew, and Marco Del Giudice. 2012. {``Linking Behavioural
+Syndromes and Cognition: A Behavioural Ecology Perspective.''}
+\emph{Philosophical Transactions of the Royal Society of London B:
+Biological Sciences} 367 (1603): 2762--72.
+\url{https://doi.org/10.1098/rstb.2012.0216}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-staddon_Adaptive_2016}{}}%
+Staddon, J. E. R. 2016. \emph{Adaptive {Behavior} and {Learning}}. 2
+edition. Cambridge: Cambridge University Press.
+
+\leavevmode\vadjust pre{\hypertarget{ref-suddendorf_Evolution_2007}{}}%
+Suddendorf, Thomas, and Michael C. Corballis. 2007. {``The Evolution of
+Foresight: {What} Is Mental Time Travel, and Is It Unique to Humans?''}
+\emph{The Behavioral and Brain Sciences} 30 (3): 299-313; discussion
+313-351. \url{https://doi.org/10.1017/S0140525X07001975}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-sutherland_Configural_1989}{}}%
+Sutherland, R. J., and J. W. Rudy. 1989. {``Configural Association
+Theory: {The} Role of the Hippocampal Formation in Learning, Memory, and
+Amnesia.''} \emph{Psychobiology} 17 (2): 129--44.
+\url{https://doi.org/10.3758/BF03337828}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-sutton_Reinforcement_2018}{}}%
+Sutton, Richard S., and Andrew G. Barto. 2018. \emph{Reinforcement
+{Learning}: {An} {Introduction}}. Edited by Francis Bach. Second edition
+edition. Cambridge, MA: A Bradford Book.
+
+\leavevmode\vadjust pre{\hypertarget{ref-taborsky_Social_2012a}{}}%
+Taborsky, Barbara, and Rui F. Oliveira. 2012. {``Social Competence: An
+Evolutionary Approach.''} \emph{Trends in Ecology \& Evolution} 27 (12):
+679--88. \url{https://doi.org/10.1016/j.tree.2012.09.003}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-triki_Brain_2020}{}}%
+Triki, Zegni, Yasmin Emery, Magda C. Teles, Rui F. Oliveira, and Redouan
+Bshary. 2020. {``Brain Morphology Predicts Social Intelligence in Wild
+Cleaner Fish.''} \emph{Nature Communications} 11 (1): 6423.
+\url{https://doi.org/10.1038/s41467-020-20130-2}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-triki_Effects_2016}{}}%
+Triki, Zegni, Alexandra S. Grutter, Redouan Bshary, and Albert F. H.
+Ros. 2016. {``Effects of Short-Term Exposure to Ectoparasites on Fish
+Cortisol and Hematocrit Levels.''} \emph{Marine Biology} 163 (9): 187.
+\url{https://doi.org/10.1007/s00227-016-2959-y}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-triki_Decrease_2018}{}}%
+Triki, Zegni, Sharon Wismer, Elena Levorato, and Redouan Bshary. 2018.
+{``A Decrease in the Abundance and Strategic Sophistication of Cleaner
+Fish After Environmental Perturbations.''} \emph{Global Change Biology}
+24 (1): 481--89. \url{https://doi.org/10.1111/gcb.13943}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-triki_Biological_2019}{}}%
+Triki, Zegni, Sharon Wismer, Olivia Rey, Sandra Ann Binning, Elena
+Levorato, and Redouan Bshary. 2019. {``Biological Market Effects Predict
+Cleaner Fish Strategic Sophistication.''} \emph{Behavioral Ecology} 30
+(6): 1548--57. \url{https://doi.org/10.1093/beheco/arz111}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-varela_Correlated_2020}{}}%
+Varela, Susana A. M., Magda C. Teles, and Rui F. Oliveira. 2020. {``The
+Correlated Evolution of Social Competence and Social Cognition.''}
+\emph{Functional Ecology} 34 (2): 332--43.
+\url{https://doi.org/10.1111/1365-2435.13416}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-waldie_LongTerm_2011}{}}%
+Waldie, Peter A., Simon P. Blomberg, Karen L. Cheney, Anne W. Goldizen,
+and Alexandra S. Grutter. 2011. {``Long-{Term} {Effects} of the
+{Cleaner} {Fish} {Labroides} Dimidiatus on {Coral} {Reef} {Fish}
+{Communities}.''} \emph{PLOS ONE} 6 (6): e21201.
+\url{https://doi.org/10.1371/journal.pone.0021201}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-wismer_Cuebased_2019}{}}%
+Wismer, Sharon, Ana I. Pinto, Zegni Triki, Alexandra S. Grutter,
+Dominique G. Roche, and Redouan Bshary. 2019. {``Cue-Based Decision
+Rules of Cleaner Fish in a Biological Market Task.''} \emph{Animal
+Behaviour}, October.
+\url{https://doi.org/10.1016/j.anbehav.2019.09.013}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-wismer_Variation_2014}{}}%
+Wismer, Sharon, Ana I. Pinto, Alex L. Vail, Alexandra S. Grutter, and
+Redouan Bshary. 2014. {``Variation in {Cleaner} {Wrasse} {Cooperation}
+and {Cognition}: {Influence} of the {Developmental} {Environment}?''}
+\emph{Ethology} 120 (6): 519--31.
+\url{https://doi.org/10.1111/eth.12223}.
+
+\end{CSLReferences}
 

### 2022-07-20 manuscript_BE/manuscript_BE_word.Rmd
New version of the manuscript

--- 2022-03-08 manuscript_1.0/manuscript_word.Rmd
@@
 ---
-title: Field and experimental data together with computational 
-  models reveal how cleaner fish adjust decisions  in a biological market
-author:
-- Andrés E. Quiñones^[Institute of Biology, University of Neuchâtel, Neuchâtel, Switzerland
-  - andresqp@gmail.com]
-date: "`r format(Sys.time(), '%B %d, %Y')`"
+title: | 
+  Title: Field and experimental data together with computational models reveal how cleaner fish adjust decisions  in a biological market
+# author:
+# - Andrés E. Quiñones^[Institute of Biology, University of Neuchâtel, Neuchâtel, Switzerland - andresqp@gmail.com]
+# - Zegni Triki^[Department of Zoology, Stockholm University, Stockholm, Sweden]
+# - Redouan Bshary^[Institute of Biology, University of Neuchâtel, Neuchâtel, Switzerland]
+subtitle: |
+  Abbreviated title: Cleaner fish cognitive mechanisms in a biological market
+# date: "`r format(Sys.time(), '%B %d, %Y')`"
 output:
-  word_document: default
+  word_document
+   # pdf_document:
+    # latex_engine: xelatex
+    # template: template.latex
 fig_caption: yes
 fontsize: 12pt
-header-includes:
-- \usepackage{float}
-- \usepackage{setspace}\doublespacing
-- \linespread{2}
-- \usepackage{lineno}
-- \linenumbers
-- \newcommand{\beginsupplement}{ \setcounter{table}{0} \renewcommand{\thetable}{S\arabic{table}}
-  \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}}
 keep_tex: yes
-linespread: 2
 bibliography: Cleanerlearning.bib
-style: M:\Zotero\styles\behavioral-ecology-and-sociobiology.csl
+style: M:\Zotero\styles\behavioral-ecology.csl
 spacing: double
@@
 We argue that the combination of computational models with data is a powerful tool to infer the mechanistic underpinnings of cognitive performance.
-author_summary: |
-  Performance in behavioural experiments is often used to assess the cognitive abilities of animals.
-However, animals can get to the same outcome in alternative ways.
-Thus, the outcome of the experiments does not tell us how animals achieve their performance.
-In order to overcome this limitation, we used a set of computational models, which provide predictions on how alternative cognitive mechanisms perform in the face of varying environmental conditions, and compare their predictions to performance data from individuals that experienced different conditions throughout their life.
-Our study system is the cleaner fish *Labroides dimidiatus*, a coral reef fish that feeds off ectoparasites and dead tissue from the skin of other reef fishes.
-Cleaner fish often have to choose among alternative clients seeking their cleaning service, and the optimal choice is often hard to achieve.
-Our performance experiments mimic the natural choices the cleaner fish make.
-The combination of experiments and computational models points to cleaner fish abilities to account for the future effect of their choices by estimating the long term expected value of those choices.
-Estimating long term value is a mechanism involved in human foresight.
-keywords: learning, behaviour, cleaners, bayesian statisitics
+
+header-includes: |
+  ```{=latex}
+  \usepackage{float}
+  \usepackage{graphicx}
+  \usepackage{booktabs}
+  \linespread{2}
+  \usepackage{lineno}
+  \linenumbers
+  \usepackage{setspace}\doublespacing
+  \newcommand{\beginsupplement}{ \setcounter{table}{0}     \renewcommand{\thetable}{S\arabic{table}}\setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}}
+  \providecommand{\keywords}[1]{\textbf{\textit{Keywords---}} #1}
+  ```
+editor_options:
+  markdown:
+    wrap: 80
 ---
+
+## Lay summary
+
+  Cleaner fish, reef fish that feed of ectoparasites of other fishes, often choose among alternative clients.
+For the cleaner fish is better to choose certain clients, a choice that favours obtaining food in the future.
+Thus, cleaners must "look" into the future to make the right choice.
+By combining a learning model with data, we show that cleaners estimate the long-term value of their actions rather than using simpler heuristics.
+Estimating long-term value is a mechanism involved in human foresight.
+
+**keywords:** learning, behavior, cleaners, bayesian statisitics, behavioral mechanisms
+
+\newpage
 
@@
 abilities believed to be uniquely human. For instance, when researchers 
-try to find *mental time travel-like* behaviour, they usually come up with 
-clever experiments to show the behaviour displayed requires inferences made 
-through past events[@dally_Foodcaching_2006]. However, they often face the
+try to find *mental time travel-like* behavior, they usually come up with 
+clever experiments to show the behavior displayed requires inferences made 
+through past events [@dally_Foodcaching_2006]. However, they often face the
 challenge of alternative scenarios where simpler explanations, 
@@
 conditions, it is possible to assess their relative explanatory power 
-by performing cognitive test in the context of
+by performing cognitive tests in the context of
 different environmental conditions.
@@
 law of supply and demand, when individuals have some degree of partner choice
-[@noe_Biological_1995]. Supply and demand conditions, which typically 
+[@noe_Biological_1995a]. Supply and demand conditions, which typically 
 depend on the abundance of the species involved, certainly vary in time 
@@
 it is not clear which cognitive mechanisms allow individuals to adjust their 
-behaviour to the varying conditions. More specifically the question arises 
+behaviors to the varying conditions. More specifically the question arises 
 to what extent mechanisms beyond basic associative learning may be involved.
@@
 visitors service priority in a field study in the Red Sea
-[@bshary_Cleaner_2001].
+[@bshary_Cleaner_2001a].
 
@@
 This between variation in performance, and primates' known cognitive abilities
-$\color{red}{\text{ref}}$, shows that performance in the task
+[@reader_Evolution_2011], shows that performance in the task
 cannot be readily explained by classifying species as having high and 
@@
 Recent research on the cognitive abilities needed to solve the ephemeral 
-reward task has used a broad approach as proposed by Shettleworth 
-[@shettleworth_Cognition_2009], who defined cognition as including 
+reward task has used a broad approach as proposed by
+@shettleworth_Cognition_2009, who defined cognition as including 
 all ways in which animals acquire information 
@@
 which minimal kit is necessary to solve 
-the task at hand (e.g. [@dubois_Model_2021]). Applied to the ephemeral 
+the task at hand (e.g. @dubois_Model_2021). Applied to the ephemeral 
 reward task, learning models showed that basic reinforcement learning does 
@@
 configurational learning, chunking, 
-or segmentation (see references in [@prat_Modelling_2022]).
+or segmentation (see references in @prat_Modelling_2022).
 
@@
 the future consequences of current decisions. In the model by 
-Quiñones *et al.* [@quinones_Reinforcement_2019], this could be achieved in 
+@quinones_Reinforcement_2019, this could be achieved in 
 two non-mutually exclusive ways: through low temporal discounting of 
@@
 a complex adaptation [@suddendorf_Evolution_2007]. On the other hand,
-using client behaviour as a negative reinforcer is, in principle, 
+using client behavior as a negative reinforcer is, in principle, 
 easier to implement. Negative reinforcement is part of the ubiquitous 
@@
 
-Over the last decade, our team tested over a hundred wild-caught 
-cleaner fish in the exact same paradigm of the ephemeral reward 
+Over the last decade, over a hundred wild-caught cleaner fish have been tested
+in the exact same paradigm of the ephemeral reward 
 task [@salwiczek_Adult_2012;@wismer_Variation_2014;@triki_Decrease_2018;
@@
 based on the difference between the expected reward and the obtained
-reward (prediction error) [@sutton_Reinforcement_2018; 
+reward - the prediction error- [@sutton_Reinforcement_2018; 
 @rescorla_Theory_1972]. Given the new information, the update is carried

### 2022-07-20 manuscript_PLOS/manuscript_PLOS.tex
New version of the manuscript

@@
 Zegni Triki\textsuperscript{\getAff{b}},
-Redouan Bshary\textsuperscript{\getAff{Institute of Biology, University
-of Neuchatel}}\\
+Redouan Bshary\textsuperscript{\getAff{a}}\\
 \bigskip
-\textbf{\getAff{a}}Institute of Biology,University of Neuchatel ,Rue
-Emile-Argand 11, 2000-CH Neuchatel, Switzerland\\
-\textbf{\getAff{b}}Department of Zoology, Stockholm University, Svante
-Arrheniusväg 18 B, 106 91 Stockholm, Sweden,\\
+\textbf{\getAff{a}}Institute of Biology, University of Neuchatel,
+Neuchatel, Switzerland\\
+\textbf{\getAff{b}}Department of Zoology, Stockholm University,
+Stockholm, Sweden\\
 \bigskip
@@
 {[}15{]}. This between variation in performance, and primates' known
-cognitive abilities {[}\textbf{reader\_Evolution\_2001?}{]}, shows that
-performance in the task cannot be readily explained by classifying
-species as having high and low cognitive abilities. Instead, this
-between species variation suggests that solving the ephemeral reward
-task requires a set of cognitive mechanisms that are not present in all
-the tested taxa, or were not used under the experimental set-up.
+cognitive abilities {[}16{]}, shows that performance in the task cannot
+be readily explained by classifying species as having high and low
+cognitive abilities. Instead, this between species variation suggests
+that solving the ephemeral reward task requires a set of cognitive
+mechanisms that are not present in all the tested taxa, or were not used
+under the experimental set-up.
 
@@
 reward task has used a broad approach as proposed by Shettleworth
-{[}16{]}, who defined cognition as including all ways in which animals
+{[}17{]}, who defined cognition as including all ways in which animals
 acquire information through the senses, process, retain and decide to
@@
 for individual performance. For example, some animals find relevant
-information in the plates {[}17{]} while others find it in the food
-{[}18,19{]}. However, identifying cues as salient is not the only
+information in the plates {[}18{]} while others find it in the food
+{[}19,20{]}. However, identifying cues as salient is not the only
 challenge of the ephemeral reward task, as revealed by proximate
@@
 evaluating which minimal kit is necessary to solve the task at hand
-(e.g. {[}20{]}). Applied to the ephemeral reward task, learning models
+(e.g. {[}21{]}). Applied to the ephemeral reward task, learning models
 showed that basic reinforcement learning does not suffice to solve the
-ephemeral reward task {[}21,22{]}. This is particularly so when models
+ephemeral reward task {[}22,23{]}. This is particularly so when models
 assume the more complex natural situation in which cleaner fish face not
@@
 scenarios (alone, paired with a fish with the same strategic option,
-paired with a fish with the alternative strategic option) {[}22{]}. The
+paired with a fish with the alternative strategic option) {[}23{]}. The
 ability to distinguish and value one stimulus differently alone from
 compound versions of it has been termed configurational learning,
-chunking, or segmentation (see references in {[}21{]}).
+chunking, or segmentation (see references in {[}22{]}).
 
@@
 for the future consequences of current decisions. In the model by
-Quiñones \emph{et al.} {[}22{]}, this could be achieved in two
+Quiñones \emph{et al.} {[}23{]}, this could be achieved in two
 non-mutually exclusive ways: through low temporal discounting of future
-effects, also termed `chaining' {[}23{]}; and/or through perceiving a
+effects, also termed `chaining' {[}24{]}; and/or through perceiving a
 visitor client leaving as psychological punishment (i.e.~as a negative
@@
 that increase the long-term reward at the sacrifice of short term
-considerations {[}23{]}. Even though, `chaining' can be readily
-implemented computationally in learning models {[}23,24{]}, cognitively
+considerations {[}24{]}. Even though, `chaining' can be readily
+implemented computationally in learning models {[}24,25{]}, cognitively
 it seems to be a complex adaptation {[}2{]}. On the other hand, using
@@
 implement. Negative reinforcement is part of the ubiquitous learning
-mechanism termed operant conditioning {[}25,26{]}. Thus, the standard
+mechanism termed operant conditioning {[}26,27{]}. Thus, the standard
 logic of Lloyd Morgan's cannon demands that operant conditioning as the
@@
 decision making use different words to refer to negative reinforcers
-{[}22,24{]}. Here, for the sake of simplicity and clarity, we will use
+{[}23,25{]}. Here, for the sake of simplicity and clarity, we will use
 the word `penalty' to refer to this mechanism which includes a negative
@@
 fish in the exact same paradigm of the ephemeral reward task
-{[}13,27--30{]}. These fish often come from different reef locations
+{[}13,28--31{]}. These fish often come from different reef locations
 around the study field site at Lizard Island, Great Barrier Reef in
@@
 Cleaner fish from reef sites with relatively low densities were more
-likely to fail at solving the task {[}27--29{]}. The explanation for
+likely to fail at solving the task {[}28--30{]}. The explanation for
 this pattern is twofold. First, low cleaner fish population densities
@@
 partner choice options and are hence more likely to wait for inspection
-if not given cleaning priority {[}30{]}. In the absence of partner
+if not given cleaning priority {[}31{]}. In the absence of partner
 choice cleaner fish should not give priority to visitors any more.
@@
 update is based on the difference between the expected reward and the
-obtained reward (prediction error) {[}24,31{]}. Given the new
+obtained reward (prediction error) {[}25,32{]}. Given the new
 information, the update is carried in the direction that leads to more
@@
 wait. Further details of the model implementation can be found in
-Quiñones \emph{et al} {[}22{]}.
+Quiñones \emph{et al} {[}23{]}.
 
@@
 density of cleaner fish and their clients at a given site in a given
-year, Triki \emph{et al.} {[}29{]} used a series of ten transects of
+year, Triki \emph{et al.} {[}30{]} used a series of ten transects of
 \(30m\) each. Observers swam along the transect lines placed on the reef
@@
 \(5m\), and then on the return individuals of small-bodied fish species
-(\(TL < 10 cm\))\\
-on a width of \(1 m\) (see Triki et al.~2018 for further details on fish
-censuses data collection). We then scaled the counts of cleaner fish,
-small-bodied, and large-bodied clients fish densities per \(100 m^2\).
-From the study by Triki \emph{et al} {[}29{]} cleaner fish and
-large-bodied client populations densities were highly correlated, and
-only the former was hence used in the analyses as representative of both
-measures.
+(\(TL < 10 cm\)) on a width of \(1 m\) (see Triki et al.~2018 for
+further details on fish censuses data collection). We then scaled the
+counts of cleaner fish, small-bodied, and large-bodied clients fish
+densities per \(100 m^2\). From the study by Triki \emph{et al} {[}30{]}
+cleaner fish and large-bodied client populations densities were highly
+correlated, and only the former was hence used in the analyses as
+representative of both measures.
 
@@
 noted whether or not the visitor left or queued for the cleaning service
-{[}29,30{]}.
+{[}30,31{]}.
 
@@
 individuals per 12 site/year) tested in the ephemeral reward task
-{[}29,30{]}. Authors housed all captured cleaners individually in glass
+{[}30,31{]}. Authors housed all captured cleaners individually in glass
 aquaria ( \(62cm \times 27cm \times 37 cm\) ) and provided them with PVC
@@
 plate based solely on the behaviour-cue of the plates rather than
-size-cue {[}17{]}. Triki \emph{et al.} {[}29,30{]} tested the fish for a
+size-cue {[}18{]}. Triki \emph{et al.} {[}30,31{]} tested the fish for a
 maximum of 200 trials with 20 trials a day, 10 trials in the morning and
@@
 criteria chosen in previous analysis of the ephemeral reward task
-experimental set-up {[}29,30{]}. In the supplementary material (Fig.
+experimental set-up {[}30,31{]}. In the supplementary material (Fig.
 \ref{fig:rawdata}) we show how our choice maps to the previously used
@@
 
+\hypertarget{ethics-statement}{%
+\subsubsection{Ethics statement}\label{ethics-statement}}
+
+The Animal Ethics Committee of the Queensland government (DAFF) approved
+the project (CA 2016/05/970 and CA 2017/05/1063)
+
 \hypertarget{statistical-analysis}{%
@@
 The aim of the analyses is to fit the key model parameters \(\gamma\)
-and \(\eta\), to the empirical data from Triki \emph{et al.} {[}29,30{]}
+and \(\eta\), to the empirical data from Triki \emph{et al.} {[}30,31{]}
 to test whether each or a combination of these effects is a better
@@
 the fitting algorithm in \emph{c++}, the diagnostics and visualization
-in R {[}32{]}. All codes are accessible at
-\url{https://github.com/andreseqp/learnDatamodel}
+in R {[}33{]}. All codes are accessible at \textless DOI:
+10.5281/zenodo.6338073\textgreater{}
 
 To compare the fit of the three alternative models, we used the
-distribution of pseudo \(R^2\) proposed by Mcfadden {[}33{]}. Mcfadden's
+distribution of pseudo \(R^2\) proposed by Mcfadden {[}34{]}. Mcfadden's
 pseudo \(R^2\) is a standard measure of fit for logistic regression. In
@@
 visitor leaving behaviour and cleaner fish performance in the market
-task {[}29{]}, only the chaining mechanism predicted that cleaner fish
+task {[}30{]}, only the chaining mechanism predicted that cleaner fish
 performance in the task should be low in habitats with low
@@
 decision-rules given their local ecological conditions had relatively
-smaller forebrains {[}30{]}. Triki \emph{et al.} refer to the former as
+smaller forebrains {[}31{]}. Triki \emph{et al.} refer to the former as
 socially competent cleaner fish, while the second group as socially
 incompetent cleaner fish. Social competence is the ability to optimise
-social behaviour to the available social information {[}34--36{]}. Our
+social behaviour to the available social information {[}35--37{]}. Our
 analyses yielded no evidence that the difference in social competence
 with respect to the local ecological conditions and associated brain
-morphology, found by Triki \emph{et al} {[}30{]}, is due to the
+morphology, found by Triki \emph{et al} {[}31{]}, is due to the
 mechanism used to incorporate future consequences. It is conceivable
@@
 negative reinforcement should have explained at least part of the data.
-Configurational learning or chunking {[}37,38{]}, the second component
-necessary to solve the ephemeral reward task {[}22{]}, was not varied in
+Configurational learning or chunking {[}38,39{]}, the second component
+necessary to solve the ephemeral reward task {[}23{]}, was not varied in
 the models we analysed here. However, while chunking tendencies should
 vary to allow individuals to adapt to their local conditions
-{[}21,39{]}, systematic differences in individual chunking tendencies
+{[}22,40{]}, systematic differences in individual chunking tendencies
 would not explain how socially competent decisions vary as a function of
@@
 example, potato washing by Japanese macaques, an iconic example of
-social learning, took several years to spread within the group {[}40{]},
+social learning, took several years to spread within the group {[}41{]},
 meaning that any learner had been repeatedly exposed to demonstrations
-before acquisition. Importantly, Galef {[}41{]} refuted imitation as a
+before acquisition. Importantly, Galef {[}42{]} refuted imitation as a
 mechanism not simply because of the repeated exposure but because a
@@
 individuals did not follow the prediction based on imitation learning
-(see also {[}42{]}). In our case, the number of trials it took cleaners
+(see also {[}43{]}). In our case, the number of trials it took cleaners
 to learn the solution to the ephemeral rewards task would never allow
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-noe_Biological_1995}{}}%
+\leavevmode\vadjust pre{\hypertarget{ref-noe_Biological_1995a}{}}%
 \CSLLeftMargin{4. }
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-bshary_Cleaner_2001}{}}%
+\leavevmode\vadjust pre{\hypertarget{ref-bshary_Cleaner_2001a}{}}%
 \CSLLeftMargin{11. }
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-reader_Evolution_2011}{}}%
+\CSLLeftMargin{16. }
+\CSLRightInline{Reader SM, Hager Y, Laland KN. The evolution of primate
+general and cultural intelligence. Philosophical Transactions of the
+Royal Society B: Biological Sciences. 2011;366: 1017--1027.
+doi:\href{https://doi.org/10.1098/rstb.2010.0342}{10.1098/rstb.2010.0342}}
+
 \leavevmode\vadjust pre{\hypertarget{ref-shettleworth_Cognition_2009}{}}%
-\CSLLeftMargin{16. }
+\CSLLeftMargin{17. }
 \CSLRightInline{Shettleworth SJ. Cognition, {Evolution}, and {Behavior}.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-wismer_Cuebased_2019}{}}%
-\CSLLeftMargin{17. }
+\CSLLeftMargin{18. }
 \CSLRightInline{Wismer S, Pinto AI, Triki Z, Grutter AS, Roche DG,
@@
 \leavevmode\vadjust pre{\hypertarget{ref-pretot_Comparative_2021}{}}%
-\CSLLeftMargin{18. }
+\CSLLeftMargin{19. }
 \CSLRightInline{Prétôt L, Mickelberg J, Carrigan J, Stoinski T, Bshary
@@
 \leavevmode\vadjust pre{\hypertarget{ref-pretot_Comparing_2016}{}}%
-\CSLLeftMargin{19. }
+\CSLLeftMargin{20. }
 \CSLRightInline{Prétôt L, Bshary R, Brosnan SF. Comparing species
@@
 \leavevmode\vadjust pre{\hypertarget{ref-dubois_Model_2021}{}}%
-\CSLLeftMargin{20. }
+\CSLLeftMargin{21. }
 \CSLRightInline{Dubois T, Pasquaretta C, Barron AB, Gautrais J, Lihoreau
@@
 \leavevmode\vadjust pre{\hypertarget{ref-prat_Modelling_2022}{}}%
-\CSLLeftMargin{21. }
+\CSLLeftMargin{22. }
 \CSLRightInline{Prat Y, Bshary R, Lotem A. Modelling how cleaner fish
@@
 \leavevmode\vadjust pre{\hypertarget{ref-quinones_Reinforcement_2019}{}}%
-\CSLLeftMargin{22. }
+\CSLLeftMargin{23. }
 \CSLRightInline{Quiñones AE, Leimar O, Lotem A, Bshary R. Reinforcement
@@
 \leavevmode\vadjust pre{\hypertarget{ref-enquist_Power_2016}{}}%
-\CSLLeftMargin{23. }
+\CSLLeftMargin{24. }
 \CSLRightInline{Enquist M, Lind J, Ghirlanda S. The power of associative
@@
 \leavevmode\vadjust pre{\hypertarget{ref-sutton_Reinforcement_2018}{}}%
-\CSLLeftMargin{24. }
+\CSLLeftMargin{25. }
 \CSLRightInline{Sutton RS, Barto AG. Reinforcement {Learning}: {An}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-thorndike_Animal_1898}{}}%
-\CSLLeftMargin{25. }
+\CSLLeftMargin{26. }
 \CSLRightInline{Thorndike EL. Animal intelligence: {An} experimental
@@
 \leavevmode\vadjust pre{\hypertarget{ref-skinner_Behavior_1938}{}}%
-\CSLLeftMargin{26. }
+\CSLLeftMargin{27. }
 \CSLRightInline{Skinner BF. The behavior of organisms;: {An}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-wismer_Variation_2014}{}}%
-\CSLLeftMargin{27. }
+\CSLLeftMargin{28. }
 \CSLRightInline{Wismer S, Pinto AI, Vail AL, Grutter AS, Bshary R.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-triki_Decrease_2018}{}}%
-\CSLLeftMargin{28. }
+\CSLLeftMargin{29. }
 \CSLRightInline{Triki Z, Wismer S, Levorato E, Bshary R. A decrease in
@@
 \leavevmode\vadjust pre{\hypertarget{ref-triki_Biological_2019}{}}%
-\CSLLeftMargin{29. }
+\CSLLeftMargin{30. }
 \CSLRightInline{Triki Z, Wismer S, Rey O, Ann Binning S, Levorato E,
@@
 \leavevmode\vadjust pre{\hypertarget{ref-triki_Brain_2020}{}}%
-\CSLLeftMargin{30. }
+\CSLLeftMargin{31. }
 \CSLRightInline{Triki Z, Emery Y, Teles MC, Oliveira RF, Bshary R. Brain
@@
 \leavevmode\vadjust pre{\hypertarget{ref-rescorla_Theory_1972}{}}%
-\CSLLeftMargin{31. }
+\CSLLeftMargin{32. }
 \CSLRightInline{Rescorla RA, Wagner ARA. A theory of {Pavlovian}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-rcoreteam_Language_2021}{}}%
-\CSLLeftMargin{32. }
+\CSLLeftMargin{33. }
 \CSLRightInline{R Core Team. R: {A} language and environment for
@@
 \leavevmode\vadjust pre{\hypertarget{ref-mcfadden_Conditional_1974}{}}%
-\CSLLeftMargin{33. }
+\CSLLeftMargin{34. }
 \CSLRightInline{McFadden D. Conditional logit analysis of qualitative
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-taborsky_Social_2012}{}}%
-\CSLLeftMargin{34. }
+\leavevmode\vadjust pre{\hypertarget{ref-taborsky_Social_2012a}{}}%
+\CSLLeftMargin{35. }
 \CSLRightInline{Taborsky B, Oliveira RF. Social competence: An
@@
 \leavevmode\vadjust pre{\hypertarget{ref-bshary_Cooperation_2015}{}}%
-\CSLLeftMargin{35. }
+\CSLLeftMargin{36. }
 \CSLRightInline{Bshary R, Oliveira RF. Cooperation in animals: Toward a
@@
 \leavevmode\vadjust pre{\hypertarget{ref-varela_Correlated_2020}{}}%
-\CSLLeftMargin{36. }
+\CSLLeftMargin{37. }
 \CSLRightInline{Varela SAM, Teles MC, Oliveira RF. The correlated
@@
 \leavevmode\vadjust pre{\hypertarget{ref-sutherland_Configural_1989}{}}%
-\CSLLeftMargin{37. }
+\CSLLeftMargin{38. }
 \CSLRightInline{Sutherland RJ, Rudy JW. Configural association theory:
@@
 \leavevmode\vadjust pre{\hypertarget{ref-miller_Magical_1956}{}}%
-\CSLLeftMargin{38. }
+\CSLLeftMargin{39. }
 \CSLRightInline{Miller GA. The magical number seven, plus or minus two:
@@
 \leavevmode\vadjust pre{\hypertarget{ref-kolodny_Evolution_2014}{}}%
-\CSLLeftMargin{39. }
+\CSLLeftMargin{40. }
 \CSLRightInline{Kolodny O, Edelman S, Lotem A. The evolution of
@@
 \leavevmode\vadjust pre{\hypertarget{ref-kawamura_Process_1959}{}}%
-\CSLLeftMargin{40. }
+\CSLLeftMargin{41. }
 \CSLRightInline{Kawamura S. The process of sub-culture propagation among
@@
 \leavevmode\vadjust pre{\hypertarget{ref-galef_Question_1992}{}}%
-\CSLLeftMargin{41. }
+\CSLLeftMargin{42. }
 \CSLRightInline{Galef BG. The question of animal culture. Human Nature.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-hirata_SweetPotato_2001}{}}%
-\CSLLeftMargin{42. }
+\CSLLeftMargin{43. }
 \CSLRightInline{Hirata S, Watanabe K, Masao K. {``{Sweet}-{Potato}

### 2022-07-20 analysisMCMC.R

@@ -151,5 +151,5 @@ nrew.nrew.post<-ggplot(data=MCMCdata3,aes(x=negReward)) +
                show.legend=FALSE) +
   scale_fill_manual(values=c("gray85","skyblue","gray85"))+
   labs(title=labelsPlot.Scen[3],
-       subtitle = expression(gamma),x="",y="")+
+       subtitle = expression(eta),x="",y="")+
   theme_classic()+xlim(-2,2)

### 2022-07-20 predictions.R

@@ -216,7 +216,8 @@ cont.obs.pred.both<- ggplot(data = FIAinterpData.both,aes(x=rel.abund.cleaners,y
 # Panel full model scatter
 scatter.obs.pred.both<-ggplot(data=fieldatabyLocSamps.both,
                               aes(y=probVisi.data,colour=site_year,x=probvisitor.pred))+
-  stat_gradientinterval(aes(slab_alpha=F),point_interval = mode_hdi,point_size=2)+
+  stat_gradientinterval(aes(slab_alpha=F),point_interval = mode_hdi,point_size=2,
+                        fill_type = "segments")+
   geom_abline(slope=1)+ylab("Observed")+xlab("")+
   geom_point(data = fieldatabyLoc.both,aes(y=market_binomial_data,x=probvisitor.pred),
              shape=15,size=2)+
@@ -251,7 +252,8 @@ cont.obs.pred.gam<- ggplot(data = FIAinterpData.gam,aes(x=rel.abund.cleaners,y=p
 # Panel future reward scatter
 scatter.obs.pred.gam<-ggplot(data=fieldatabyLocSamps.gam,
                              aes(y=probVisi.data,colour=site_year,x=probvisitor.pred))+
-  stat_gradientinterval(aes(slab_alpha=F),point_interval = mode_hdi,point_size=2)+
+  stat_gradientinterval(aes(slab_alpha=F),point_interval = mode_hdi,point_size=2,
+                        fill_type = "segments")+
   geom_abline(slope=1)+ylab("Observed")+xlab("Predicted")+
   geom_point(data = fieldatabyLoc.gam,aes(y=market_binomial_data,x=probvisitor.pred),
              shape=15,size=2)+
@@ -285,7 +287,8 @@ cont.obs.pred.Nrew<- ggplot(data = FIAinterpData.Nrew,aes(x=rel.abund.cleaners,y
 
 scatter.obs.pred.Nrew<-ggplot(data=fieldatabyLocSamps.Nrew,
                               aes(y=probVisi.data,colour=site_year,x=probvisitor.pred))+
-  stat_gradientinterval(aes(slab_alpha=F),point_interval = mode_hdi,point_size=2)+
+  stat_gradientinterval(aes(slab_alpha=F),point_interval = mode_hdi,point_size=2,
+                        fill_type = "segments")+
   geom_abline(slope=1)+ylab("Observed")+xlab("Predicted")+
[…]

### 2022-07-25 manuscript_BE/manuscript_BE.Rmd
Further changes to the manuscript

@@
 If $\gamma=0$, individuals only use the immediate reward obtained from a
-cleaning interaction. As $\gamma$ increases, individuals include more the
+cleaning interaction. As $\gamma$ increases, individuals include more of the
 reward obtained from the subsequent choices. That amounts to estimating
@@
 (see @triki_Decrease_2018 for further details on fish censuses data collection). 
+Total length estimates were done by the observer. 
 We then scaled the counts of cleaner fish, small-bodied, 
 and  large-bodied  clients fish densities per $100 m^2$.
-From the study by @triki_Biological_2019 
-cleaner fish and large-bodied client populations densities were 
-highly correlated, and only the former 
-was hence used in the analyses as representative of both measures.
 
@@
 extracted information from every event wherein a visitor client 
-was made to wait in favour of another client (visitor or resident), and noted 
+was made to wait in favor of another client (visitor or resident), and noted 
 whether or not the visitor left or queued for the cleaning service
@@
 however, granted access to both plates. The equal size of the plates 
-forced cleaner fish to learn to give service priority to the visitor plate 
-based solely on the behavior-cue of the plates rather than size-cue 
-[@wismer_Cuebased_2019]. Triki et al. [-@triki_Biological_2019;@triki_Brain_2020] 
+forced cleaner fish to decide based solely on the association between 
+the behaviour and the collor/pattern cue [@wismer_Cuebased_2019]. 
+Triki et al. [-@triki_Biological_2019;@triki_Brain_2020] 
 tested the fish for a maximum of 200 trials with 20 trials a day, 10 trials 
@@
 (colour and pattern) and the plates’ role (visitor or resident) between the 
-tested fish. In the original studies, once a fish reach a learning criterion, 
-that is, performing significantly above chance level ($> 50%$, $p-value ≥ 0.05$),
+tested fish. In the original studies, once a fish reached a learning criterion, 
+that is, performing significantly above chance level in a binomial test 
+($p-value 	\leq 0.05$, ),
 they passed to a reversal version of the task where the roles of the 
-visitor/resident Plexiglas plates were swapped 
-(see Triki et al.[-@triki_Biological_2019;@triki_Brain_2020]). 
-Here, we used instead a subset of these data in order to have an idea of 
+visitor/resident Plexiglas plates were swapped. The reversal phased 
+stopped when the fish performed significatly above chance, or the fish
+completed the 200 trial together with the initial;
+see Triki et al.[-@triki_Biological_2019;@triki_Brain_2020]. 
+Here, we are interested in explaining the total frequency of visitor choices
+using the model, rather than just the achievement of the criterion. 
+Total frequency of visitor choices naturally comes out of the model, 
+and allows us to use all the variation among cleaners, instead of reducing 
+that to a binomial variable.
+Thus, we used instead a subset of these data to estimate the final 
 cleaner fish preferences for the visitor plate, even if they do not reach 
@@
 ($N = `r fieldData.cleaner.filt.sum[V1>2,length(V1)]`$ cleaner fish).
+
 We chose a combination of initial and reversal to quantify preference 
-for the visitor client, given that it matches well the criteria chosen 
-in previous analysis of the ephemeral reward task experimental set-up
-[@triki_Biological_2019;@triki_Brain_2020]. In the 
-supplementary material (Fig. \ref{fig:rawdata}) we show how our choice maps
-to the previously used criteria. For comparison, we also show a quantification 
-of visitor preference based only on the initial phase of the task.
+for the visitor client. However, it could be argued that using only the initial
+phase gives a better estimation of the cleaner fish preference for the visitor. 
+In the supplementary material (Fig. \ref{fig:rawdata}) we show how using 
+initial and reversal (a), and only initial (b) maps
+to the previously used criteria. The initial and reversal match better
+the criteria chosen in previous analysis of the ephemeral 
+reward task experimental set-up
+[@triki_Biological_2019;@triki_Brain_2020].
 
@@
 resident clients abundances and visitor clients leaving probability,  
-as input to the models. As the response variable, we used cleaners' 
-preference for visitors over residents in the ephemeral reward task. 
-Finally, we used the preference for visitors resulting from the 
-model simulations as the prediction for the response variable. 
-We kept all other parameter values used for the model simulations constant, 
-see Table \ref{tab:param}.
+as input to the models. As the response variable, we used the frequency with 
+which cleaners chose the visitor option in the ephemeral reward task. 
+Finally, we used the probability with which agents in the model
+simulations choose the visitor in resident-visitor options
+as the prediction for the response variable. 
+We kept all other parameter values used for 
+the model simulations constant, see Table \ref{tab:param}.
 
@@
 in R [@rcoreteam_Language_2021]. All codes are accessible at 
-<DOI: 10.5281/zenodo.6338073>
+[![DOI](https://zenodo.org/badge/440585701.svg)](https://zenodo.org/badge/latestdoi/440585701).
 
@@
 ```{r rawdata,fig.cap='Relation between the response variable used in this study and the criteria used in previous studies to assess performance in the ephemeral reward task.
-In the x axis, we classified the performance of cleaner fish according to whether they developed a preference for the visitor in the initial round, in the initial and reversal, or none of them.
-In the y axis, we add the choices of two experimental sessions: panel on the left uses one session from the initial round and one from the reversal round when possible (as described in the main text); panel on the right uses two sessions from the initial round for all fish.',out.width='100%',fig.height=5,cache=FALSE}
-plot_grid(initANDRev,init,ncol = 2)
+In the x axis, we classified the performance of cleaner fish according to whether they developed a preference for the visitor in the initial round (initial only), in the initial and reversal (both), or none of them (none).
+In the y axis, we add the choices of two experimental sessions: in panel \\textbf{a} we use one session from the initial round and one from the reversal round when possible (as described in the main text); in panel \\textbf{b} we use two sessions from the initial round for all fish.',out.width='100%',fig.height=5,cache=FALSE}
+plot_grid(initANDRev,init,ncol = 2,labels = c("a","b"),label_x = 0.15)
 

### 2022-07-25 manuscript_BE/manuscript_BE.tex
Further changes to the manuscript

@@
 \makesavenoteenv{longtable}
+\usepackage{graphicx}
+\makeatletter
+\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
+\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
+\makeatother
+% Scale images if necessary, so that they will not overflow the page
+% margins by default, and it is still possible to overwrite the defaults
+% using explicit options in \includegraphics[width, height, ...]{}
+\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
+% Set default figure placement to htbp
+\makeatletter
+\def\fps@figure{htbp}
+\makeatother
 \setlength{\emergencystretch}{3em} % prevent overfull lines
@@
 corresponds to the current probability of choosing the visitor. \(p_i\)
-is determined by applying the logistic function to the diffence in
+is determined by applying the logistic function to the difference in
 preferences between the two mutually exclusive options
@@
 reward obtained from a cleaning interaction. As \(\gamma\) increases,
-individuals include more the reward obtained from the subsequent
+individuals include more of the reward obtained from the subsequent
 choices. That amounts to estimating and using for decision making the
@@
 (\(TL < 10 cm\)) on a width of \(1 m\) (see Triki et al. (2018) for
-further details on fish censuses data collection). We then scaled the
-counts of cleaner fish, small-bodied, and large-bodied clients fish
-densities per \(100 m^2\). From the study by Triki et al. (2019) cleaner
-fish and large-bodied client populations densities were highly
-correlated, and only the former was hence used in the analyses as
-representative of both measures.
+further details on fish censuses data collection). Total length
+estimates were done by the observer. We then scaled the counts of
+cleaner fish, small-bodied, and large-bodied clients fish densities per
+\(100 m^2\).
 
@@
 extracted information from every event wherein a visitor client was made
-to wait in favour of another client (visitor or resident), and noted
+to wait in favor of another client (visitor or resident), and noted
 whether or not the visitor left or queued for the cleaning service
@@
 however, granted access to both plates. The equal size of the plates
-forced cleaner fish to learn to give service priority to the visitor
-plate based solely on the behavior-cue of the plates rather than
-size-cue (Wismer et al. 2019). Triki et al. (2019, 2020) tested the fish
-for a maximum of 200 trials with 20 trials a day, 10 trials in the
-morning and 10 trials in the afternoon. They randomized and
-counterbalanced the plates' spatial location (i.e.~left or right)
-between trials. Similarly, they counterbalanced the plates' decoration
-(colour and pattern) and the plates' role (visitor or resident) between
-the tested fish. In the original studies, once a fish reach a learning
-criterion, that is, performing significantly above chance level (\(> 50%
-\), \(p-value ≥ 0.05\)), they passed to a reversal version of the task
-where the roles of the visitor/resident Plexiglas plates were swapped
-(see Triki et al.(2019, 2020)). Here, we used instead a subset of these
-data in order to have an idea of cleaner fish preferences for the
-visitor plate, even if they do not reach the learning criterion within
-200 trials. To do so, we first extracted the trial-by-trial outcomes
-from the last two sessions (20 trials) of those who never reached the
-learning criterion for visitor plate (\(N = 45\) cleaner fish). For
-those who reached the learning criterion at some point during the test
-and passed to a reversal phase, we extracted the trial-by-trial outcomes
-from the last session (10 trials) before passing to reversal and the
-last 10 trials they were exposed to in the test (\(N = 75\) cleaner
-fish). We chose a combination of initial and reversal to quantify
-preference for the visitor client, given that it matches well the
+forced cleaner fish to decide based solely on the association between
+the behaviour and the collor/pattern cue (Wismer et al. 2019). Triki et
+al. (2019, 2020) tested the fish for a maximum of 200 trials with 20
+trials a day, 10 trials in the morning and 10 trials in the afternoon.
+They randomized and counterbalanced the plates' spatial location
+(i.e.~left or right) between trials. Similarly, they counterbalanced the
+plates' decoration (colour and pattern) and the plates' role (visitor or
+resident) between the tested fish. In the original studies, once a fish
+reached a learning criterion, that is, performing significantly above
+chance level in a binomial test (\(p-value \leq 0.05\), ), they passed
+to a reversal version of the task where the roles of the
+visitor/resident Plexiglas plates were swapped. The reversal phased
+stopped when the fish performed significatly above chance, or the fish
+completed the 200 trial together with the initial; see Triki et
+al.(2019, 2020). Here, we are interested in explaining the total
+frequency of visitor choices using the model, rather than just the
+achievement of the criterion. Total frequency of visitor choices
+naturally comes out of the model, and allows us to use all the variation
+among cleaners, instead of reducing that to a binomial variable. Thus,
+we used instead a subset of these data to estimate the final cleaner
+fish preferences for the visitor plate, even if they do not reach the
+learning criterion within 200 trials. To do so, we first extracted the
+trial-by-trial outcomes from the last two sessions (20 trials) of those
+who never reached the learning criterion for visitor plate (\(N = 45\)
+cleaner fish). For those who reached the learning criterion at some
+point during the test and passed to a reversal phase, we extracted the
+trial-by-trial outcomes from the last session (10 trials) before passing
+to reversal and the last 10 trials they were exposed to in the test
+(\(N = 75\) cleaner fish).
+
+We chose a combination of initial and reversal to quantify preference
+for the visitor client. However, it could be argued that using only the
+initial phase gives a better estimation of the cleaner fish preference
+for the visitor. In the supplementary material (Fig. \ref{fig:rawdata})
+we show how using initial and reversal (a), and only initial (b) maps to
+the previously used criteria. The initial and reversal match better the
 criteria chosen in previous analysis of the ephemeral reward task
-experimental set-up (Triki et al. 2019, 2020). In the supplementary
-material (Fig. \ref{fig:rawdata}) we show how our choice maps to the
-previously used criteria. For comparison, we also show a quantification
-of visitor preference based only on the initial phase of the task.
+experimental set-up (Triki et al. 2019, 2020).
 
@@
 visitor clients leaving probability,\\
-as input to the models. As the response variable, we used cleaners'
-preference for visitors over residents in the ephemeral reward task.
-Finally, we used the preference for visitors resulting from the model
-simulations as the prediction for the response variable. We kept all
-other parameter values used for the model simulations constant, see
-Table \ref{tab:param}.
+as input to the models. As the response variable, we used the frequency
+with which cleaners chose the visitor option in the ephemeral reward
+task. Finally, we used the probability with which agents in the model
+simulations choose the visitor in resident-visitor options as the
+prediction for the response variable. We kept all other parameter values
+used for the model simulations constant, see Table \ref{tab:param}.
 
@@
 the fitting algorithm in \emph{c++}, the diagnostics and visualization
-in R (R Core Team 2021). All codes are accessible at \textless DOI:
-10.5281/zenodo.6338073\textgreater{}
+in R (R Core Team 2021). All codes are accessible at
+\href{https://zenodo.org/badge/latestdoi/440585701}{\includegraphics{https://zenodo.org/badge/440585701.svg}}.
 
@@
 \includegraphics[width=1\linewidth]{manuscript_BE_files/figure-latex/rawdata-1} \caption{Relation between the response variable used in this study and the criteria used in previous studies to assess performance in the ephemeral reward task.
-In the x axis, we classified the performance of cleaner fish according to whether they developed a preference for the visitor in the initial round, in the initial and reversal, or none of them.
-In the y axis, we add the choices of two experimental sessions: panel on the left uses one session from the initial round and one from the reversal round when possible (as described in the main text); panel on the right uses two sessions from the initial round for all fish.}\label{fig:rawdata}
+In the x axis, we classified the performance of cleaner fish according to whether they developed a preference for the visitor in the initial round (initial only), in the initial and reversal (both), or none of them (none).
+In the y axis, we add the choices of two experimental sessions: in panel \textbf{a} we use one session from the initial round and one from the reversal round when possible (as described in the main text); in panel \textbf{b} we use two sessions from the initial round for all fish.}\label{fig:rawdata}
 \end{figure}

### 2022-07-25 loadFieldData.R

@@ -205,21 +205,23 @@ ggplot(field.merged.2,aes(x=score_visitor.init,y=score_visitor,
 
 initANDRev<-ggplot(field.merged.2,aes(y=score_visitor,x=as.factor(class.perform)))+
   geom_beeswarm()+theme_classic()+labs(title = "Initial and reversal")+
-  scale_x_discrete(name ="Performance",labels=c("0"="Nothing","1"="initial only",
+  scale_x_discrete(name ="Performance",labels=c("0"="None","1"="initial only",
                                                   "2"="both"))+ylim(0,20)+
   stat_summary(fun.data = function(x){return(c(y=20,
                label=length(x)))},
-               geom = "text")+ylab("# of visitor chosen")
+               geom = "text")+ylab("# of visitor chosen")+
+  theme(plot.title = element_text(hjust = 1)) 
 
 
 init<-ggplot(field.merged.2,aes(y=score_visitor.init,x=as.factor(class.perform)))+
   geom_beeswarm()+theme_classic()+labs(title = "Initial")+
-  scale_x_discrete(name ="Performance",labels=c("0"="Nothing",
+  scale_x_discrete(name ="Performance",labels=c("0"="None",
                                                 "1"="initial only",
                                                 "2"="both"))+ylim(0,20)+
   stat_summary(fun.data = function(x){return(c(y=20,
                           label=length(x)))},
-               geom = "text")+ylab("")
+               geom = "text")+ylab("")+
+  theme(plot.title = element_text(hjust = 1)) 
 
 
 

### 2022-08-08 manuscript_BE/manuscript_BE.Rmd
Edits in the source code to fit parameters using PAA

@@
 \begin{equation}
+\delta_t = R_t -  V_t(S_t) + \gamma V_t(S_{t+1}) ,
 \label{eq:delta}
-\delta_t = R_t -  V_t(S_t) + \gamma V_t(S_{t+1}) ,
 \end{equation}
@@
 absolute abundances and multiplied it
-by a scaling constant that changes the range of the variable. This scaling 
-constant is hence meant to capture variation in the market conditions driven 
-partly by cleaner fish abundance. We fitted the value of the scaling constant as 
-part of the statistical inference. As for the visitor and resident 
-abundances, we computed a relative measure with respect to the 
-total client abundance, and weighted that by the rescaled relative absence 
+by a scaling constant that changes the range of the variable. Specifically,
+cleaner fish relative abundance is equal 
+to $\frac{\epsilon C_{abs}}{\epsilon C_{abs}+R_{abs}+V_{abs}}$. 
+Where $\epsilon$ is the scaling constant; $C_{abs}$ 
+is the cleaner fish absolute density; $R_{abs}$ is the residents absolute 
+density and $V_{abs}$ is the visitor client absolute density. This scaling 
+constant is meant to capture variation in the market conditions driven 
+partly by cleaner fish abundance. We fitted the value of the scaling constant
+($\epsilon$) as part of the statistical inference. 
+As for the visitor and resident abundances, we computed a 
+relative measure with respect to the 
+total client abundance, and weighted that by the re-scaled relative absence 
 of cleaners ($1-\text{relative cleaner abundance}$). Thus, all three measures 
@@
 given the model and parameters. We then proposed a new set of parameters drawn 
-from a uniform distribution centred around the old parameter set. The amplitude 
+from a uniform distribution centered around the old parameter set. The amplitude 
 of the uniform distribution used for each parameter can be found in Table 
@@
 in R [@rcoreteam_Language_2021]. All codes are accessible at 
-[![DOI](https://zenodo.org/badge/440585701.svg)](https://zenodo.org/badge/latestdoi/440585701).
+\url{https://zenodo.org/badge/latestdoi/440585701}
+<!-- [![zenodo.6338073.svg)](https://zenodo.org/badge/latestdoi/440585701). -->
 
@@
 look at the model with only penalty, the posterior distribution 
-of $\eta$ is still centred around zero (Fig. \ref{fig:post}, d). 
+of $\eta$ is still centered around zero (Fig. \ref{fig:post}, d). 
 Thus, the analysis of the estimates of individual parameter 
 values in the three models only supports a strong 
-effect of chaining. Furthermore, the comparison of the models` fit 
-favours the chaining model. In panel e of figure \ref{fig:post} 
+effect of chaining. Furthermore, the comparison of the models' fit 
+favors the chaining model. In panel e of figure \ref{fig:post} 
 we show the distribution of $pseudo-R^2$ calculated using 
@@
 
-The main reason for chaining and penalty to give different
-predictions is the way that cleaner fish relative abundance influences the
-preference for the visitor clients. Visitor leaving probability has a
-similar positive effect on the probability of choosing the visitor
-clients on all three models, they all predict an increase preference 
-for visitors as the visitor probability increases  (Fig. \ref{fig:pred}).
-In contrast, cleaner fish relative abundance has a different effect in the
-model with only chaining, compared to the other two models,
-full model and penalty. In the model with only chaining, only intermediate 
-cleaner fish abundance triggers a preference for the visitor 
-clients (Fig. \ref{fig:pred} c). In both models with penalty, 
-both intermediate and low cleaner abundance triggered a preference 
-for the visitor (Fig. \ref{fig:pred} a,e). Note, however, we calculated 
-preferences shown in figure \ref{fig:pred} left panels by using only the mode 
+Low cleaner fish relative abundance yields different predictions 
+from a model with only chaining and with penalty.
+The model with only chaining predicts a low preference fpr the visitor when
+cleaner fish relative abundance is low (Fig. \ref{fig:pred} c). In contrast,
+the models including penalty (with and without chaining) predict high 
+preference for the visitor option (Fig. \ref{fig:pred} a and e).
+For intermediate and high cleaner relative abundances the predictions 
+are similar for all three models. Intermediate relative abundance 
+trigger a high preference for the visitor; while low abundances trigger
+low preference for the visitor (Fig. \ref{fig:pred}a,b,e). 
+Note, however, we calculated 
+preferences shown in figure \ref{fig:pred} left panels by using only the model 
 of the posterior distributions, and by holding constant the balance between 
-resident and visitors´ abundances. Panels on the right, show how close 
+resident and visitors' abundances. Panels on the right, show how close 
 predictions are from the observed data, allowing the balance between 
@@
 distribution.
+
+Visitor leaving probability has an overall 
+positive effect on the probability of choosing the visitor
+clients on all three models. All three models predict an increase preference 
+for visitors as the visitor probability increases  (Fig. \ref{fig:pred}).
 

### 2022-08-08 manuscript_BE/manuscript_BE.tex
Edits in the source code to fit parameters using PAA

@@
 \makesavenoteenv{longtable}
-\usepackage{graphicx}
-\makeatletter
-\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
-\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
-\makeatother
-% Scale images if necessary, so that they will not overflow the page
-% margins by default, and it is still possible to overwrite the defaults
-% using explicit options in \includegraphics[width, height, ...]{}
-\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
-% Set default figure placement to htbp
-\makeatletter
-\def\fps@figure{htbp}
-\makeatother
 \setlength{\emergencystretch}{3em} % prevent overfull lines
@@
 each reef site relative to absolute abundances and multiplied it by a
-scaling constant that changes the range of the variable. This scaling
-constant is hence meant to capture variation in the market conditions
-driven partly by cleaner fish abundance. We fitted the value of the
-scaling constant as part of the statistical inference. As for the
+scaling constant that changes the range of the variable. Specifically,
+cleaner fish relative abundance is equal to
+\(\frac{\epsilon C_{abs}}{\epsilon C_{abs}+R_{abs}+V_{abs}}\). Where
+\(\epsilon\) is the scaling constant; \(C_{abs}\) is the cleaner fish
+absolute density; \(R_{abs}\) is the residents absolute density and
+\(V_{abs}\) is the visitor client absolute density. This scaling
+constant is meant to capture variation in the market conditions driven
+partly by cleaner fish abundance. We fitted the value of the scaling
+constant (\(\epsilon\)) as part of the statistical inference. As for the
 visitor and resident abundances, we computed a relative measure with
-respect to the total client abundance, and weighted that by the rescaled
-relative absence of cleaners (\(1-\text{relative cleaner abundance}\)).
-Thus, all three measures of relative abundance sum up to 1, and can be
-used in the model as a proxy for the probability of having different
-options in the cleaning station. Note that we introduced the scaling
-constant to control for variation that is not captured by the model; its
-parameter distribution does not offer biological insights.
+respect to the total client abundance, and weighted that by the
+re-scaled relative absence of cleaners
+(\(1-\text{relative cleaner abundance}\)). Thus, all three measures of
+relative abundance sum up to 1, and can be used in the model as a proxy
+for the probability of having different options in the cleaning station.
+Note that we introduced the scaling constant to control for variation
+that is not captured by the model; its parameter distribution does not
+offer biological insights.
 
@@
 of the data given the model and parameters. We then proposed a new set
-of parameters drawn from a uniform distribution centred around the old
+of parameters drawn from a uniform distribution centered around the old
 parameter set. The amplitude of the uniform distribution used for each
@@
 in R (R Core Team 2021). All codes are accessible at
-\href{https://zenodo.org/badge/latestdoi/440585701}{\includegraphics{https://zenodo.org/badge/440585701.svg}}.
+\url{https://zenodo.org/badge/latestdoi/440585701}
 
@@
 \ref{fig:post}, c). In contrast, when we look at the model with only
-penalty, the posterior distribution of \(\eta\) is still centred around
+penalty, the posterior distribution of \(\eta\) is still centered around
 zero (Fig. \ref{fig:post}, d). Thus, the analysis of the estimates of
 individual parameter values in the three models only supports a strong
-effect of chaining. Furthermore, the comparison of the models` fit
-favours the chaining model. In panel e of figure \ref{fig:post} we show
+effect of chaining. Furthermore, the comparison of the models' fit
+favors the chaining model. In panel e of figure \ref{fig:post} we show
 the distribution of \(pseudo-R^2\) calculated using samples from the
@@
 
-The main reason for chaining and penalty to give different predictions
-is the way that cleaner fish relative abundance influences the
-preference for the visitor clients. Visitor leaving probability has a
-similar positive effect on the probability of choosing the visitor
-clients on all three models, they all predict an increase preference for
-visitors as the visitor probability increases (Fig. \ref{fig:pred}). In
-contrast, cleaner fish relative abundance has a different effect in the
-model with only chaining, compared to the other two models, full model
-and penalty. In the model with only chaining, only intermediate cleaner
-fish abundance triggers a preference for the visitor clients (Fig.
-\ref{fig:pred} c). In both models with penalty, both intermediate and
-low cleaner abundance triggered a preference for the visitor (Fig.
-\ref{fig:pred} a,e). Note, however, we calculated preferences shown in
-figure \ref{fig:pred} left panels by using only the mode of the
-posterior distributions, and by holding constant the balance between
-resident and visitors´ abundances. Panels on the right, show how close
-predictions are from the observed data, allowing the balance between
-client types to vary and using a set of samples from the posterior
-distribution.
+Low cleaner fish relative abundance yields different predictions from a
+model with only chaining and with penalty. The model with only chaining
+predicts a low preference fpr the visitor when cleaner fish relative
+abundance is low (Fig. \ref{fig:pred} c). In contrast, the models
+including penalty (with and without chaining) predict high preference
+for the visitor option (Fig. \ref{fig:pred} a and e). For intermediate
+and high cleaner relative abundances the predictions are similar for all
+three models. Intermediate relative abundance trigger a high preference
+for the visitor; while low abundances trigger low preference for the
+visitor (Fig. \ref{fig:pred}a,b,e). Note, however, we calculated
+preferences shown in figure \ref{fig:pred} left panels by using only the
+model of the posterior distributions, and by holding constant the
+balance between resident and visitors' abundances. Panels on the right,
+show how close predictions are from the observed data, allowing the
+balance between client types to vary and using a set of samples from the
+posterior distribution.
+
+Visitor leaving probability has an overall positive effect on the
+probability of choosing the visitor clients on all three models. All
+three models predict an increase preference for visitors as the visitor
+probability increases (Fig. \ref{fig:pred}).
 
@@
 learning rate.}\tabularnewline
-\toprule
+\toprule()
 Parameter & Value \\
-\midrule
+\midrule()
 \endfirsthead
-\toprule
+\toprule()
 Parameter & Value \\
-\midrule
+\midrule()
 \endhead
@@
 Chain length & \(1^5\) \\
-\bottomrule
+\bottomrule()
 \end{longtable}

### 2022-08-08 ActCritMCMC.cpp

@@ -32,8 +32,8 @@ Start date:
 #include <iostream>
 #include <fstream>
 #include <omp.h>
-#include "random.h"
-#include "json.hpp"       
+#include "../Cpp/Routines/C++/RandomNumbers/random.h"
+#include "../Cpp/json.hpp"       
 // Header for reading and using JSON files see https://github.com/nlohmann/json
 
 
@@ -887,11 +887,20 @@ void do_simulation(//del focal_model,
 	client *clientSet;
 	clientSet = new client[int(sim_param["totRounds"]) * 2];
 	int idClientSet;
-	FAATyp1 *cleaners[2];
-	cleaners[0] = new FAATyp1(focal_comb.alphaC, focal_comb.gamma[0],
-		focal_comb.negReward[0], focal_comb.alphaA);
-	if(sim_param["Group"]) cleaners[1] = new FAATyp1(focal_comb.alphaC, focal_comb.gamma[1],
-		focal_comb.negReward[1], focal_comb.alphaA);
+	agent* cleaners[2];
+	if (sim_param["agent"] == "FAA") {
+		cleaners[0] = new FAATyp1(focal_comb.alphaC, focal_comb.gamma[0],
+			focal_comb.negReward[0], focal_comb.alphaA);
+		if (sim_param["Group"]) cleaners[1] = new FAATyp1(focal_comb.alphaC,
+			focal_comb.gamma[1], focal_comb.negReward[1], focal_comb.alphaA);
+	}
+	else {
+		cleaners[0] = new PAATyp1(focal_comb.alphaC, focal_comb.gamma[0],
+			focal_comb.negReward[0], focal_comb.alphaA, 1.0, 0.0);
+		if (sim_param["Group"]) cleaners[1] = new PAATyp1(focal_comb.alphaC,
+			focal_comb.gamma[1],
+			focal_comb.negReward[1], focal_comb.alphaA, 1.0, 0.0);
+	}	
 	double VisPref, init;
 	int countRVopt;
 	abs2rel_abund(emp_data, focal_comb);
@@ -958,38 +967,39 @@ int main(int argc, char* argv[]){
 	// Only for debugging 
 	// input parameters provided by a JSON file with the following
 	// structure:
-	// json sim_param;
-	// sim_param["totRounds"]    = 5000;
-	// sim_param["ResReward"]    = 1;
-	// sim_param["VisReward"]    = 1;
[…]

### 2022-08-08 parTOjson.R

@@ -12,23 +12,34 @@ fileName<-"parameters.json"
 
 # name of the scenario for which parameter files will be produces
 # format used for the name: MCMCclean_*parameter1_paramerter2_parameter3.....
-scenario<-"MCMCclean_gam_sca"
+scenario<- "test"#"MCMCclean_PAA_gam_Nre_sca"
 
 
 # MCMC fit - Generate json parameter files for -------------------------------------
 
 # for MCMC
-param_mcmc<-list(totRounds=10000, # Number of rounds in the learning model
-                 ResReward=1,VisReward=1, # Magnitude of reward for resdents and visitors
-                 ResProbLeav=0, # Prob. of resindet leaving the station if unattended
-                 scenario=0, # scenario of how the clients reach the station
+param_mcmc<-list(totRounds=10000, 
+                 # Number of rounds in the learning model
+                 ResReward=1,VisReward=1, 
+                 # Magnitude of reward for residents and visitors
+                 ResProbLeav=0, 
+                 # Prob. of resident leaving the station if unattended
+                 scenario=0, 
+                 # scenario of how the clients reach the station
                  #nature 0, experiment 1, marketExperiment 2, ExtendedMarket 3
-                 inbr=0,outbr=0, # probability of clients seeking similar/ different,
+                 inbr=0,outbr=0, 
+                 # probability of clients seeking similar/ different,
                  # clients, respectively, in the station
-                 forRat=0.0, # Rate at which cleaners forget what they have learned
-                 seed=1,  # Seed for the random number generator
-                 propfullPrint = 0.7, #Proportion of rounds used to calculate predictions
-                 sdPert=c(0.05,0.05,0.3,4,300), # Width of the perturbation kernel for each parameter
+                 forRat=0.0, 
+                 # Rate at which cleaners forget what they have learned
+                 seed=1,  
+                 # Seed for the random number generator
+                 agent="PAA", 
+                 # Type of agent FAA (chuncking), PAA (not chuncking)
+                 propfullPrint = 0.7, 
+                 #Proportion of final rounds used to calculate predictions
+                 sdPert=c(0.05,0.05,0.3,4,300), 
+                 # Width of the perturbation kernel for each parameter
                  # alphaA,AlphaC, Gamma, NegRew, scalConst
                  chain_length=100000, # Chain length
[…]

### 2022-08-15 manuscript_BE/manuscript_BE.Rmd
Further changes to include PAA in the analysis. Dealing with convergence problems

@@
   \normalsize \textbf{Abbreviated title:} Cleaner fish cognitive mechanisms in a biological market
-# date: "`r format(Sys.time(), '%B %d, %Y')`"
-# author: 
-#   - name: Andrés E. Quiñones 
-#     email: andresqp@gmail.com
-#     affiliation: a
-#     corresponding: andresqp@gmail.com 
-#     #, Rue Emile-Argand 11, CH-2000, Neuchatel, Switzerland. +41 32 718 31 24
-#   - name: Zegni Triki
-#     affiliation: a
-#     affiliation: b
-#   - name: Redouan Bshary
-#     affiliation: a
-# address:
-#   - code: a
-#     address: Institute of Biology, University of Neuchatel, Neuchatel, Switzerland
-#   - code: b
-#     address: Department of Zoology, Stockholm University, Stockholm, Sweden
 output:
   pdf_document:
-    keep_tex: true
+    keep_tex: yes
     latex_engine: xelatex
     template: template.latex
+  word_document: default
 fig_caption: yes
@@
 bibliography: Cleanerlearning.bib
-style: M:\Zotero\styles\behavioral-ecology.csl
+style: "M:\\Zotero\\styles\\behavioral-ecology.csl"
 spacing: double
 abstract: |
-  While it is generally straightforward to quantify individual performance in cognitive experiments, identifying the underlying cognitive processes remains a major challenge.
-Often, different mechanistic underpinnings yield similar performances, and Lloyd Morgan’s cannon warrants acceptance of the simpler explanation.
-Alternatively, when the different mechanisms interact with environmental conditions, variation in performance across environments might allow to statistically infer the mechanism responsible.
-We illustrate this point by fitting computational models to experimental data on performance by wild-caught cleaner fish *Labroides dimidiatus* in an ephemeral reward task, as well as cleaner and client fish densities from the locations of capture.
-Using Bayesian statistics to fit the model parameters to performance data revealed that cleaner fish most likely estimate future consequences of an action, while it appears unlikely that the removal of the ephemeral reward acts as psychological punishment (negative reinforcement).
-Incorporating future consequences also yields performances that can be considered the result of locally optimal decision-rules, in contrast to the negative reinforcement mechanism.
-We argue that the combination of computational models with data is a powerful tool to infer the mechanistic underpinnings of cognitive performance.
+  While it is generally straightforward to quantify individual performance
+  in cognitive experiments, identifying the underlying cognitive processes remains
+  a major challenge. Often, different mechanistic underpinnings yield similar performances,
+  and Lloyd Morgan’s cannon warrants acceptance of the simpler explanation. Alternatively,
+  when the different mechanisms interact with environmental conditions, variation
+  in performance across environments might allow to statistically infer the mechanism
+  responsible. We illustrate this point by fitting computational models to experimental
+  data on performance by wild-caught cleaner fish *Labroides dimidiatus* in an ephemeral
+  reward task, as well as cleaner and client fish densities from the locations of
+  capture. Using Bayesian statistics to fit the model parameters to performance data
+  revealed that cleaner fish most likely estimate future consequences of an action,
+  while it appears unlikely that the removal of the ephemeral reward acts as psychological
+  punishment (negative reinforcement). Incorporating future consequences also yields
+  performances that can be considered the result of locally optimal decision-rules,
+  in contrast to the negative reinforcement mechanism. We argue that the combination
+  of computational models with data is a powerful tool to infer the mechanistic underpinnings
+  of cognitive performance.
 lay_summary:  |
   Cleaner fish eat ectoparasites off other fishes, so-called clients.
-It regularly happens that two clients seek a cleaner's service simulatenously.
-Cleaners benefit from prioritising clients unwilling to wait, so they can feed on those willing to wait.
-To make the right choice, cleaners must somehow “look” into the future to anticipate consequences of current choices.
-By combining a learning model with data, we show that cleaners estimate the long-term value of their actions rather than using simpler heuristics.
-Estimating long-term value is a mechanism involved in human foresight.
+  It regularly happens that two clients seek a cleaner's service simulatenously. Cleaners
+  benefit from prioritising clients unwilling to wait, so they can feed on those willing
+  to wait. To make the right choice, cleaners must somehow “look” into the future
+  to anticipate consequences of current choices. By combining a learning model with
+  data, we show that cleaners estimate the long-term value of their actions rather
+  than using simpler heuristics. Estimating long-term value is a mechanism involved
+  in human foresight.
 header-includes: |
@@
     \usepackage{float}
-  \usepackage{graphicx}
     \usepackage{booktabs}
-  \linespread{2}
-  \usepackage{lineno}
-  \linenumbers
-  \usepackage{setspace}\doublespacing
     \newcommand{\beginsupplement}{ \setcounter{table}{0}             \renewcommand{\thetable}{S\arabic{table}}\setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}}
-  \providecommand{\keywords}[1]{\textbf{\textit{Keywords---}} #1}
   ```
@@
 source(here("analysisMCMC.R"))
-first.col<-plot_grid(nrow=3,align = "v",byrow = TRUE,
-          gam.both.post,gam.gam.post,nrew.nrew.post,
-          labels=c('a','c','d'))
-second.col<-plot_grid(nrow = 2,align = "v",byrow = TRUE,
-          nrew.both.post,panel.rsqr.all,rel_heights = c(1,2),
-          labels = c('b','e'))
-plot_grid(ncol = 2,first.col,second.col)
+
+ggarrange(allGammapost.plot,alletapost.plot,common.legend = TRUE)
+# first.col<-plot_grid(nrow=3,align = "v",byrow = TRUE,
+#           gam.both.post.FAA,gam.gam.post.FAA,nrew.nrew.post.FAA,
+#           labels=c('a','c','d'))
+# second.col<-plot_grid(nrow = 2,align = "v",byrow = TRUE,
+#           nrew.both.post.FAA,panel.rsqr.all,rel_heights = c(1,2),
+#           labels = c('b','e'))
+# plot_grid(ncol = 2,first.col,second.col)
 
@@
 
-```{r scaConst, fig.cap='Posterior distributions for scaling constant for the three models (Full model, chaining only and penalty only).
+```{r scaConstFAA, fig.cap='Posterior distributions for scaling constant for the three models (Full model, chaining only and penalty only).
 We show the kernel density estimates, below the mode (black dot) and the 65\\% (light blue shade) and 95\\% (grey shade)  highest posterior density interval.
@@
 
+```{r scaConstPAA, fig.cap='Posterior distributions for scaling constant for the three models (Full model, chaining only and penalty only).
+We show the kernel density estimates, below the mode (black dot) and the 65\\% (light blue shade) and 95\\% (grey shade)  highest posterior density interval.
+On the top, panel a shows the posterior distribution from the full model; panel b from the model with only chaining; and panel c from a model with only penalty.',fig.pos = 'H', out.extra = "",out.width='95%',fig.height=5}
+
+sca.both.post.PAA<-ggplot(data=MCMCdata4,aes(x=scaleConst)) + 
+  stat_halfeye(aes(fill=stat(cut(x,breaks = cuts.4$scaleConst))),
+               point_interval = mode_hdi, .width = c(.66, .95),
+               point_size=3,show.legend=FALSE) + 
+  labs(title=labelsPlot.Scen[1],x="",y="")+
+  theme_classic()+
+  scale_fill_manual(values=c("gray85","skyblue","gray85"))
+sca.gam.post.PAA<-ggplot(data=MCMCdata5,aes(x=scaleConst)) + 
+  stat_halfeye(aes(fill=stat(cut(x,breaks = cuts.5$scaleConst))),
+               point_interval = mode_hdi, 
+               .width = c(.66, .95),point_size=3,
+               show.legend=FALSE)+theme_classic()+
+  scale_fill_manual(values=c("gray85","skyblue","gray85"))+
+  labs(title=labelsPlot.Scen[2],x="",y="")
+sca.nRew.post.PAA<-ggplot(data=MCMCdata6,aes(x=scaleConst)) +
+  stat_halfeye(aes(fill=stat(cut(x,breaks = cuts.6$scaleConst))),
+               point_interval = mode_hdi, .width = c(.66, .95),
+               point_size=3,
+               show.legend=FALSE) +
+  scale_fill_manual(values=c("skyblue","gray85"))+
+  labs(title=labelsPlot.Scen[3],x="",y="")+
+  theme_classic()
+ggarrange(sca.both.post.PAA,sca.gam.post.PAA,
+          sca.nRew.post.PAA,
+          labels=c('a','b','c'),common.legend = F)
+
+```
+
 <!-- (ref:diagnosticsfull) MCMC convergence diagnostics for the full model.  -->
@@
 
-```{r diagnosticsfull, fig.cap='MCMC convergence diagnostics for the full model.
+```{r diagnosticsfullFAA, fig.cap='MCMC convergence diagnostics for the full model.
 On the left trace-plots, on the right changes along the chain of the Gelman and Rubin shrink factor.',out.width='100%',fig.height=5,cache=FALSE,message=FALSE}
@@
 
-```{r diaggam,fig.cap='MCMC convergence diagnostics for the chaining model.
+```{r diaggamFAA,fig.cap='MCMC convergence diagnostics for the chaining model.
 On the left trace-plots, on the right changes along the chain of the Gelman and Rubin shrink factor ',echo=FALSE,message=FALSE,out.width='100%',fig.height=5,cache=FALSE,message=FALSE}
@@
 
-parlab<-list(`gamma` =expression(gamma),
-          `scaleConst`="Scaling constant")
+longMCMCdata2[,parameter:=factor(parameter,labels=c("gamma","'Scaling constant'"))]
 
@@
   facet_grid(rows=vars(parameter),scales = "free",switch = "y",
-             labeller = function(variable,value){
-  return(parlab[value])})+
+             labeller = label_parsed)+
   theme_classic()+
@@
 
-```{r diagNeg,fig.cap='MCMC convergence diagnostics for the penalty model.
+```{r diagNegFAA,fig.cap='MCMC convergence diagnostics for the penalty model.
 On the left trace-plots, on the right changes along the chain of the Gelman and Rubin shrink factor',out.width='100%',fig.height=5,cache=FALSE,message=FALSE,out.width='100%',fig.height=5,cache=FALSE,message=FALSE}
@@
 
-parlab<-list(`negReward` =expression(eta),
-          `scaleConst`="Scaling constant")
+longMCMCdata3[,parameter:=factor(parameter,labels=c("eta","'Scaling constant'"))]
 
@@
 ggarrange(traces.neg,gelman.neg)
+```
+
+<!-- (ref:diagnosticsfull) MCMC convergence diagnostics for the full model. -->
+<!-- On the left trace-plots, on the right changes along the chain of the -->
+<!-- Gelman and Rubin's shrink factor [@brooks_General_1998]. -->
+
+```{r diagnosticsfullPAA, fig.cap='MCMC convergence diagnostics for the full model.
+On the left trace-plots, fig.height=5, message=FALSE, cache=FALSE, on the right changes along the chain of the Gelman and Rubin shrink factor.',out.width='100%'}
+
+longMCMCdata4<-melt(MCMCdata4,id.vars = c("iteration","seed"),
+                    variable.name = "parameter",
+                    measure.vars = c("gamma","negReward","scaleConst"))
+
+parlab<-list(`gamma` =expression(gamma),
+          `negReward`=expression(eta),
+          `scaleConst`="Scaling constant")
+
+traces.full.PAA<-ggplot(longMCMCdata4,aes(x=iteration,y=value,colour=as.factor(seed)))+
+  geom_line()+
+  scale_color_manual(values = multDiscrPallet)+
+  labs(color="Chain")+
+  facet_grid(rows=vars(parameter),scales = "free",switch = "y",
+             labeller = function(variable,value){
+  return(parlab[value])})+
+  theme_classic()+
+  theme(legend.position = 'top')
+
+gel.full<-as.data.table(gelman.diag(mcmcList.4)$psrf)
+gel.full[,parameter:=c("gamma","negReward","scalConst")]
+
+pdf(file = NULL)
+gp.dat<-gelman.plot(mcmcList.4)
+rubbish <- dev.off()
+
+gp.dat.frame.PAA <- data.table(rbind(as.data.frame(gp.dat[["shrink"]][,,1]),
+                          as.data.frame(gp.dat[["shrink"]][,,2])),
+                q=rep(dimnames(gp.dat[["shrink"]])[[3]], each=nrow(gp.dat[["shrink"]][,,1])),
+                last.iter=rep(gp.dat[["last.iter"]], length(gp.dat)))
+
+gelman.full.PAA<-ggplot(melt(gp.dat.frame.PAA, c("q","last.iter"), value.name="shrink_factor"),
+       aes(last.iter, shrink_factor, colour=q, linetype=q)) +
+  geom_hline(yintercept=1, colour="grey30", lwd=0.2) +
+  geom_line() +
+  facet_grid(rows = vars(variable)) +
+  labs(x="Last Iteration in Chain", y="Shrink Factor",
+       colour="Quantile", linetype="Quantile") +
+  scale_linetype_manual(values=c(2,1))+
+  theme_classic()+
+  theme(legend.position = 'top',strip.text.y  = element_blank())
+
+ggarrange(traces.full.PAA,gelman.full.PAA)
+
+```
+
+<!-- (ref:diagnosticsGam) MCMC convergence diagnostics for the chaining model.  -->
+<!-- On the left trace-plots, on the right changes along the chain of the  -->
+<!-- Gelman and Rubin's shrink factor [@brooks_General_1998] -->
+
+```{r diaggamPAA,fig.cap='MCMC convergence diagnostics for the chaining model.
+On the left trace-plots, on the right changes along the chain of the Gelman and Rubin shrink factor ',echo=FALSE,message=FALSE,out.width='100%',fig.height=5,cache=FALSE,message=FALSE}
+longMCMCdata5<-melt(MCMCdata5,id.vars = c("iteration","seed"),
+                    variable.name = "parameter",
+                    measure.vars = c("gamma","scaleConst"))
+
+longMCMCdata5[,parameter:=factor(parameter,labels = c("gamma","'Scaling constant'"))]
+
+traces.gam.PAA<-ggplot(longMCMCdata5,aes(x=iteration,y=value,colour=as.factor(seed)))+
+  geom_line()+
+  scale_color_manual(values = multDiscrPallet)+
+  labs(color="Chain")+
+  facet_grid(rows=vars(parameter),scales = "free",switch = "y",
+             labeller = label_parsed)+
+  theme_classic()+
+  theme(legend.position = 'top')
+
+gel.gam<-as.data.table(gelman.diag(mcmcList.5)$psrf)
+gel.gam[,parameter:=c("gamma","scalConst")]
+
+pdf(file = NULL)
+gp.dat.gam<-gelman.plot(mcmcList.5)
+rubbish <- dev.off()
+
+gp.dat.frame.gam.PAA <- data.table(rbind(as.data.frame(gp.dat.gam[["shrink"]][,,1]),
+                          as.data.frame(gp.dat.gam[["shrink"]][,,2])),
+                q=rep(dimnames(gp.dat.gam[["shrink"]])[[3]], each=nrow(gp.dat.gam[["shrink"]][,,1])),
+                last.iter=rep(gp.dat.gam[["last.iter"]], length(gp.dat.gam)))
+
+gelman.gam.PAA<-ggplot(melt(gp.dat.frame.gam.PAA, c("q","last.iter"), value.name="shrink_factor"),
+       aes(last.iter, shrink_factor, colour=q, linetype=q)) +
+  geom_hline(yintercept=1, colour="grey30", lwd=0.2) +
+  geom_line() +
+  facet_grid(rows = vars(variable)) +
+  labs(x="Last Iteration in Chain", y="Shrink Factor",
+       colour="Quantile", linetype="Quantile") +
+  scale_linetype_manual(values=c(2,1))+
+  theme_classic()+
+  theme(legend.position = 'top',strip.text.y = element_blank())
+
+ggarrange(traces.gam.PAA,gelman.gam.PAA)
+```
+
+<!-- (ref:diagNeg) MCMC convergence diagnostics for the penalty model. -->
+<!-- On the left trace-plots, on the right changes along the chain of the -->
+<!-- Gelman and Rubin's shrink factor [@brooks_General_1998] -->
+
+```{r diagNegPAA,fig.cap='MCMC convergence diagnostics for the penalty model.
+On the left trace-plots, on the right changes along the chain of the Gelman and Rubin shrink factor',out.width='100%',fig.height=5,cache=FALSE,message=FALSE,out.width='100%',fig.height=5,cache=FALSE,message=FALSE}
+longMCMCdata6<-melt(MCMCdata6,id.vars = c("iteration","seed"),
+                    variable.name = "parameter",
+                    measure.vars = c("negReward","scaleConst"))
+
+longMCMCdata6[,parameter:=factor(parameter,labels = c("eta","'Scaling constant'"))]
+
+traces.neg.PAA<-ggplot(longMCMCdata6,aes(x=iteration,y=value,colour=as.factor(seed)))+
+  geom_line()+
+  scale_color_manual(values = multDiscrPallet)+
+  labs(color="Chain")+
+  facet_grid(rows=vars(parameter),scales = "free",switch = "y",
+             labeller = label_parsed)+
+  theme_classic()+
+  theme(legend.position = 'top')
+
+pdf(file = NULL)
+gp.dat.neg<-gelman.plot(mcmcList.6)
+rubbish <- dev.off()
+
+gp.dat.frame.neg.PAA <- data.table(rbind(as.data.frame(gp.dat.neg[["shrink"]][,,1]),
+                          as.data.frame(gp.dat.neg[["shrink"]][,,2])),
+                q=rep(dimnames(gp.dat.neg[["shrink"]])[[3]], each=nrow(gp.dat.neg[["shrink"]][,,1])),
+                last.iter=rep(gp.dat.neg[["last.iter"]], length(gp.dat.neg)))
+
+gelman.neg.PAA<-ggplot(melt(gp.dat.frame.neg.PAA, c("q","last.iter"), value.name="shrink_factor"),
+       aes(last.iter, shrink_factor, colour=q, linetype=q)) +
+  geom_hline(yintercept=1, colour="grey30", lwd=0.2) +
+  geom_line() +
+  facet_grid(rows = vars(variable)) +
+  labs(x="Last Iteration in Chain", y="Shrink Factor",
+       colour="Quantile", linetype="Quantile") +
+  scale_linetype_manual(values=c(2,1))+
+  theme_classic()+
+  theme(legend.position = 'top',strip.text.y = element_blank())
+
+ggarrange(traces.neg.PAA,gelman.neg.PAA)
 ```

### 2022-08-15 manuscript_BE/manuscript_BE.tex
Further changes to include PAA in the analysis. Dealing with convergence problems

@@
   \usepackage{float}
-\usepackage{graphicx}
   \usepackage{booktabs}
-\linespread{2}
-\usepackage{lineno}
-\linenumbers
-\usepackage{setspace}\doublespacing
   \newcommand{\beginsupplement}{ \setcounter{table}{0}             \renewcommand{\thetable}{S\arabic{table}}\setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}}
-\providecommand{\keywords}[1]{\textbf{\textit{Keywords---}} #1}
 
@@
 \begin{figure}
-\includegraphics[width=1\linewidth]{manuscript_BE_files/figure-latex/diagnosticsfull-1} \caption{MCMC convergence diagnostics for the full model.
-On the left trace-plots, on the right changes along the chain of the Gelman and Rubin shrink factor.}\label{fig:diagnosticsfull}
+\includegraphics[width=1\linewidth]{manuscript_BE_files/figure-latex/diagnosticsfullFAA-1} \caption{MCMC convergence diagnostics for the full model.
+On the left trace-plots, on the right changes along the chain of the Gelman and Rubin shrink factor.}\label{fig:diagnosticsfullFAA}
 \end{figure}
@@
 \begin{figure}
-\includegraphics[width=1\linewidth]{manuscript_BE_files/figure-latex/diaggam-1} \caption{MCMC convergence diagnostics for the chaining model.
-On the left trace-plots, on the right changes along the chain of the Gelman and Rubin shrink factor }\label{fig:diaggam}
+\includegraphics[width=1\linewidth]{manuscript_BE_files/figure-latex/diaggamFAA-1} \caption{MCMC convergence diagnostics for the chaining model.
+On the left trace-plots, on the right changes along the chain of the Gelman and Rubin shrink factor }\label{fig:diaggamFAA}
 \end{figure}
@@
 \begin{figure}
-\includegraphics[width=1\linewidth]{manuscript_BE_files/figure-latex/diagNeg-1} \caption{MCMC convergence diagnostics for the penalty model.
-On the left trace-plots, on the right changes along the chain of the Gelman and Rubin shrink factor}\label{fig:diagNeg}
+\includegraphics[width=1\linewidth]{manuscript_BE_files/figure-latex/diagNegFAA-1} \caption{MCMC convergence diagnostics for the penalty model.
+On the left trace-plots, on the right changes along the chain of the Gelman and Rubin shrink factor}\label{fig:diagNegFAA}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=1\linewidth]{manuscript_BE_files/figure-latex/diagnosticsfullPAA-1} \caption{MCMC convergence diagnostics for the full model.
+On the left trace-plots, on the right changes along the chain of the Gelman and Rubin shrink factor.}\label{fig:diagnosticsfullPAA}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=1\linewidth]{manuscript_BE_files/figure-latex/diaggamPAA-1} \caption{MCMC convergence diagnostics for the chaining model.
+On the left trace-plots, on the right changes along the chain of the Gelman and Rubin shrink factor }\label{fig:diaggamPAA}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=1\linewidth]{manuscript_BE_files/figure-latex/diagNegPAA-1} \caption{MCMC convergence diagnostics for the penalty model.
+On the left trace-plots, on the right changes along the chain of the Gelman and Rubin shrink factor}\label{fig:diagNegPAA}
 \end{figure}

### 2022-08-15 manuscript_BE/manuscript_BE_word.Rmd
Further changes to include PAA in the analysis. Dealing with convergence problems

@@
 abstract: |
-  While it is generally straightforward to quantify individual performance in cognitive experiments, identifying the underlying cognitive processes remains a major challenge.
-Often, different mechanistic underpinnings yield similar performances, and Lloyd Morgan’s cannon warrants acceptance of the simpler explanation.
-Alternatively, when the different mechanisms interact with environmental conditions, variation in performance across environments might allow to statistically infer the mechanism responsible.
-We illustrate this point by fitting computational models to experimental data on performance by wild-caught cleaner fish *Labroides dimidiatus* in an ephemeral reward task, as well as cleaner and client fish densities from the locations of capture.
-Using Bayesian statistics to fit the model parameters to performance data revealed that cleaner fish most likely estimate future consequences of an action, while it appears unlikely that the removal of the ephemeral reward acts as psychological punishment (negative reinforcement).
-Incorporating future consequences also yields performances that can be considered the result of locally optimal decision-rules, in contrast to the negative reinforcement mechanism.
-We argue that the combination of computational models with data is a powerful tool to infer the mechanistic underpinnings of cognitive performance.
+  While it is generally straightforward to quantify individual performance
+  in cognitive experiments, identifying the underlying cognitive processes remains
+  a major challenge. Often, different mechanistic underpinnings yield similar performances,
+  and Lloyd Morgan’s cannon warrants acceptance of the simpler explanation. Alternatively,
+  when the different mechanisms interact with environmental conditions, variation
+  in performance across environments might allow to statistically infer the mechanism
+  responsible. We illustrate this point by fitting computational models to experimental
+  data on performance by wild-caught cleaner fish *Labroides dimidiatus* in an ephemeral
+  reward task, as well as cleaner and client fish densities from the locations of
+  capture. Using Bayesian statistics to fit the model parameters to performance data
+  revealed that cleaner fish most likely estimate future consequences of an action,
+  while it appears unlikely that the removal of the ephemeral reward acts as psychological
+  punishment (negative reinforcement). Incorporating future consequences also yields
+  performances that can be considered the result of locally optimal decision-rules,
+  in contrast to the negative reinforcement mechanism. We argue that the combination
+  of computational models with data is a powerful tool to infer the mechanistic underpinnings
+  of cognitive performance. "
 
@@
 
-  Cleaner fish, reef fish that feed of ectoparasites of other fishes, often choose among alternative clients.
-For the cleaner fish is better to choose certain clients, a choice that favours obtaining food in the future.
-Thus, cleaners must "look" into the future to make the right choice.
-By combining a learning model with data, we show that cleaners estimate the long-term value of their actions rather than using simpler heuristics.
-Estimating long-term value is a mechanism involved in human foresight.
+Cleaner fish eat ectoparasites off other fishes, so-called clients.
+It regularly happens that two clients seek a cleaner's service simultaneously. Cleaners
+benefit from prioritizing clients unwilling to wait, so they can feed on those willing
+to wait. To make the right choice, cleaners must somehow “look” into the future
+to anticipate consequences of current choices. By combining a learning model with
+data, we show that cleaners estimate the long-term value of their actions rather
+than using simpler heuristics. Estimating long-term value is a mechanism involved
+in human foresight.
 
@@
 try to find *mental time travel-like* behavior, they usually come up with 
-clever experiments to show the behavior displayed requires inferences made 
+experiments to show the behavior displayed requires inferences made 
 through past events [@dally_Foodcaching_2006]. However, they often face the
@@
 like classic associative learning, can bring about the 
-observed behavioural outcome [@suddendorf_Evolution_2007]. Similarly, attempts 
+observed behavioral outcome [@suddendorf_Evolution_2007]. Similarly, attempts 
 to demonstrate the presence of *theory of mind* in non-human animals 
 face objections justified by alternative mechanisms underpinning 
-similar behavioural results [@heyes_Theory_1998]. 
+similar behavioral results [@heyes_Theory_1998]. 
 Such controversies are usually settled by using the principle 
@@
 Lloyd Morgan’s cannon, which states that the simpler explanation (mechanism)
-should be accepted. Ideally, however, alternative hypotheses should be evaluated 
-in light of their explanatory power. One potential dimension that could allow
-the variation necessary among distinct cognitive mechanisms is environmental
-variation. Controlled laboratory conditions often mask between and within 
-species variation that arises among different environments. Thus, if 
-predictions from the alternative mechanisms depend on environmental 
-conditions, it is possible to assess their relative explanatory power 
-by performing cognitive tests in the context of
-different environmental conditions.
+should be accepted. Ideally, alternative hypotheses should be evaluated 
+in light of their explanatory power.
+
+<!-- If alternative mechanisms predict different  -->
+<!-- outcomes when exposed to different contexts, the variation arising from -->
+<!-- varying the context could open up a way to infer which mechanism is used.  -->
+<!-- Controlled laboratory conditions often mask between and within  -->
+<!-- species variation that arises among different environmental contexts. Thus, if  -->
+<!-- predictions from the alternative mechanisms depend on environmental  -->
+<!-- conditions, it is possible to assess their relative explanatory power  -->
+<!-- by performing cognitive tests in the context of different  -->
+<!-- environmental conditions.  -->
+
+Learning is a key overarching cognitive mechanism that allows 
+individuals to associate rewards with environmental stimuli 
+and thus behave adaptively [@staddon_Adaptive_2016;@shettleworth_Cognition_2009]. 
+Associative learning, in particular, exists in all major vertebrate taxa, 
+and in many invertebrates as well [@heyes_Simple_2012;@macphail_Brain_1982; 
+@staddon_Adaptive_2016; @behrens_Associative_2008]. 
+Associative learning is not homogeneous throughout its taxonomic distribution, 
+rather there are differences across and within species 
+[@shettleworth_Cognition_2009;@sih_Linking_2012]. So presumably, 
+the mechanistic underpinnings of learning have been modified by 
+natural selection [@marler_Species_1989].
+
+One way to formalize the alternative mechanistic underpinnings of 
+associative learning is to develop quantitative models of learning 
+processes. This approach, which started within experimental psychology 
+[@staddon_Adaptive_2016;@brandon_Computational_2002], has been very fruitful 
+in disentangling the mechanistic structure of cognitive systems. 
+More recently, the development of reinforcement learning theory 
+[@sutton_Reinforcement_2018], has allowed to 
+evaluate the empirical support for alternative mechanistic hypotheses by
+providing quantitative predictions which are amenable to statistical tests
+[@farashahi_Learning_2020;@farashahi_Featurebased_2017]. Interestingly, these 
+learning models not only have received support from behavioral data, but also 
+are consistent with the current view on reward processing in the brain 
+[@schultz_Neuronal_2015].
 
@@
 depend on the abundance of the species involved, certainly vary in time 
-and space. Therefore, natural selection should favour the ability 
-to flexibly adjust decisions and behavioural output to 
-current market conditions. Indeed, such adjustments have been repeatedly 
-documented [@axen_Signalling_1996]. In animals, an obvious general candidate 
-mechanism for the strategic adjustment is the cognitive machinery. However, 
-it is not clear which cognitive mechanisms allow individuals to adjust their 
-behaviors to the varying conditions. More specifically the question arises 
-to what extent mechanisms beyond basic associative learning may be involved.
-
-One example of strategic adjustment in a biological market is the marine
+and space. Therefore, natural selection should favor the ability 
+to flexibly adjust decisions and behavioral output to 
+current market conditions. Indeed, such adjustments have been 
+documented [@axen_Signalling_1996]. One example of strategic 
+adjustment in a biological market is the marine
 cleaning mutualism involving the cleaner fish *Labroides dimidiatus* and
-'client' fish. Client fish seek cleaner fish services at their territory 
+'client' fishes. Client fishes seek cleaner fish services at their territory 
 (so-called “cleaning station”) and offer themselves as food patches 
@@
 visitors service priority in a field study in the Red Sea
-[@bshary_Cleaner_2001a].
-
-When researchers aimed at testing wild-caught cleaner fish, as 
-well as individuals from other species, abilities 
-to prioritize visitor over resident clients in a lab-based paradigm, 
-they used Plexiglas plates of different colours and shapes offering the same 
-amount of food as surrogates for visitor and resident clients.
-One plate is made to behave like a resident, i.e. it remains until 
-the cleaner fish has eaten off it. The other plate was made to behave 
-like a visitor, i.e. it is removed if not inspected first. 
-This laboratory paradigm originally inspired by the cleaning market 
-of cleaner fish is more generally referred as the ephemeral reward task. 
-Individuals are assessed in their capacity to develop a preference for the 
-ephemeral option, which gives them access to two reward units.
-Cleaners learned to prefer the visitor plate and
-hence obtained the double amount of food [@bshary_Asymmetric_2002].
-Furthermore, adult cleaner fish outperformed various primates as well as rats and
-pigeons in this original version of the ephemeral reward task
-[@salwiczek_Adult_2012; @zentall_Early_2017]; yet the African grey
-parrots solve this task as well [@pepperberg_Can_2014]. 
-This between variation in performance, and primates' known cognitive abilities
-[@reader_Evolution_2011], shows that performance in the task
-cannot be readily explained by classifying species as having high and 
-low cognitive abilities. Instead, this between species variation suggests
-that solving the ephemeral reward task requires a set of cognitive 
-mechanisms that are not present in all the tested taxa, or were not used 
-under the experimental set-up.
-
-Recent research on the cognitive abilities needed to solve the ephemeral 
-reward task has used a broad approach as proposed by
-@shettleworth_Cognition_2009, who defined cognition as including 
-all ways in which animals acquire information 
-through the senses, process, retain and decide to act on it. 
-Indeed, perception of relevant cues is of major importance 
-for individual performance. For example, some animals find relevant 
-information in the plates  [@wismer_Cuebased_2019] while others find 
-it in the food [@pretot_Comparative_2021; @pretot_Comparing_2016]. 
-However, identifying cues as salient is not the only challenge 
-of the ephemeral reward task, as revealed by proximate learning models. 
-Such models allow varying the cognitive tool kit and evaluating 
-which minimal kit is necessary to solve 
-the task at hand (e.g. @dubois_Model_2021). Applied to the ephemeral 
-reward task, learning models showed that basic reinforcement learning does 
-not suffice to solve the ephemeral reward task [@prat_Modelling_2022;
-@quinones_Reinforcement_2019]. 
-This is particularly so when models assume the more complex natural 
-situation in which cleaner fish face not only resident-visitor pairs but also 
-visitor-visitor and resident-resident pairs, as well a resident alone or 
-a visitor alone. To be able to give visitors priority over residents, 
+[@bshary_Cleaner_2001a]. Furthermore, in a lab based paradigm, design 
+to mimic the resident-visitor choice (ephemeral reward task), cleaners learned 
+to prefer the cue associated with the epheral food source (visitor) and
+hence accessed both food sources, obtaining 
+double the amount of food [@bshary_Asymmetric_2002].
+However, further exploration revealed that not all cleaner fish 
+manage to develop a preference for the ephemeral option 
+in the lab [@triki_Decrease_2018]. Over the last decade, over a hundred 
+wild-caught cleaner fish have been tested
+in the exact same paradigm of the ephemeral reward 
+task [@salwiczek_Adult_2012;@wismer_Variation_2014;@triki_Decrease_2018;
+@triki_Biological_2019;@triki_Brain_2020]. These fish often come from 
+different reef locations. Investigation of the local 
+eco-sociological conditions revealed that cleaner and client 
+fish population densities have a substantial impact on cleaner fish 
+performance in the task. Cleaner fish from reef sites with relatively 
+low densities were more likely to fail at solving the task 
+[@triki_Biological_2019;
+@triki_Decrease_2018; @wismer_Variation_2014]. This intra-specific variation
+is unlikely due to local genetic adaptation, because cleaner
+fish are open water spawners and the environmental conditions can vary within 
+the lifespan of a fish.
+
+Mechanistic models explicitly designed to mimic the ephemeral reward task 
+have shown that the simplest form of associative learning 
+(operant conditioning) cannot account for a solution to 
+the ephemeral reward task [@prat_Modelling_2022;
+@quinones_Reinforcement_2019]. Operant conditioning is 
+a form of associative learning where individuals use short term 
+reward to associate and choose actions. Such models allow varying 
+the cognitive tool kit and evaluating which minimal kit is necessary 
+to solve the task at hand (e.g. @dubois_Model_2021). 
+To be able to give visitors priority over residents, 
 cleaners need to be able to assess a client’s value separately for the 
@@
 one stimulus differently alone from compound versions of it has been termed 
-configurational learning, chunking, 
-or segmentation (see references in @prat_Modelling_2022).
-
+configurational learning, chunking, or 
+segmentation (see references in @prat_Modelling_2022). 
 In addition to configurational learning, cleaners also need to account for 
@@
 using client behavior as a negative reinforcer is, in principle, 
-easier to implement. Negative reinforcement is part of the ubiquitous 
-learning mechanism termed operant conditioning [@thorndike_Animal_1898; 
-@skinner_Behavior_1938]. Thus, the standard logic of 
+easier to implement. Thus, the standard logic of 
 Lloyd Morgan’s cannon demands that operant conditioning as the simpler 
@@
 
-Over the last decade, over a hundred wild-caught cleaner fish have been tested
-in the exact same paradigm of the ephemeral reward 
-task [@salwiczek_Adult_2012;@wismer_Variation_2014;@triki_Decrease_2018;
-@triki_Biological_2019;@triki_Brain_2020]. These fish often come from 
-different reef locations around the study field site at Lizard Island, 
-Great Barrier Reef in Australia. Further investigation of the local 
-eco-sociological conditions revealed that cleaner and client 
-fish population densities have a substantial impact on cleaner fish 
-performance in the task. Cleaner fish from reef sites with relatively 
-low densities were more likely to fail at solving the task [@triki_Biological_2019;
-@triki_Decrease_2018; @wismer_Variation_2014]. The explanation for this pattern
-is twofold. First, low cleaner fish population densities imply 
-low supply and high demand for cleaning services. 
-Under such conditions, there are fewer occasions under 
-which failing to give priority to a visitor translates to an empty 
-cleaning station. Second and also related to the state of the cleaning market,
-visitor clients at low cleaner fish population densities 
-are less likely to exert their partner choice options 
-and are hence more likely to wait for inspection if not given cleaning 
-priority [@triki_Brain_2020]. In the absence of partner choice 
-cleaner fish should not give priority to visitors any more.
-
-The interplay between the underlying cognitive machinery and 
-local ecological conditions apparently generate the documented variable 
-performance among individuals of the same species. 
-Our approach of fitting the computational model to the empirical data on 
-fish densities and cleaner fish censuses and performance
-in the ephemeral reward task aimed at: (i), determining which 
+In here we used the field and experimental data to fit the parameters of 
+a reinforcement learning model to infer  the 
+cognitive mechanism that cleaners use in their interaction with clients. 
+Specifically, our approach of fitting the computational model 
+to the empirical data aimed at: (i), determining which 
 mechanism cleaner fish use to incorporate future consequences of current 
@@
 they update the probability of making that same choice. The update is
-based on the difference between the expected reward and the obtained
-reward - the prediction error- [@sutton_Reinforcement_2018; 
-@rescorla_Theory_1972]. Given the new information, the update is carried
-in the direction that leads to more reward being obtained, given
+based on the difference between the expected value and the obtained
+reward - the prediction error ($\delta_t$) - [@sutton_Reinforcement_2018; 
+@rescorla_Theory_1972]. Formally, the prediction error is given by
+
+\begin{equation}
+\delta_t = R_t -  V_t(S_t) + \gamma V_t(S_{t+1}) ,
+\label{eq:delta}
+\end{equation}
+
+where $R_t$ is the sum different reward sources at time $t$; 
+$V_t(S_t)$ is the estimated value at time $t$ of the the state faced by the agent 
+at time $t$; similarly $V_t(S_{t+1})$ is the estimated value of the state
+to come in the following time-step, $\gamma$ is the discount factor for
+future rewards. When the estimated value of the current state ($V_t(S_t)$) 
+is equal to the sum of short-term ($R_t$) and future discounted reward 
+($\gamma V_t(S_{t+1})$) learning stops for that state. If $\gamma = 0$ 
+the estimates made by the agent only capture short-term reward. We assume 
+short-term reward to two components: positive reward determined by the 
+amount of food obtained from cleaning a client; and negative reward triggered
+when by a client leaving the station without being cleaned. Formally, 
+we let total reward be given by $R_t=P_t - \eta_t$. Where $\eta$ is a parameter
+of the model that determines the the size of the negative reward triggered by
+unattended clients leaving the station.
+
+The prediction error (Eq. \ref{eq:delta}) is used to update the value of each one
+of the states the agent faces, as well as the preference for the 
+resident and visitor options. The value update is simple the product of the 
+prediction error and the parameter for the speed of learning 
+($\Delta V(S_t)=\alpha \delta_t$). The change in preference between the resident 
+and visitor is given by $\Delta (\theta_v-\theta_r)_t=\alpha\delta_t2(1-\pi_v)$,
+where $\theta_i$ represent the preference for one of two options and the 
+difference captures the total change relative to one another; 
+$\pi_v$ corresponds to the current probability of choosing the visitor. 
+$p_i$ is determined by applying the logistic function to the difference in
+preferences between the two mutually exclusive options 
+($\pi_v=\frac{1}{1+e^{-(\theta_v-\theta_r)}}$). This amounts
+to a preference update that is carried in the direction that 
+leads to more reward being obtained, given
 the new information. In the long run, the probability of choosing a visitor 
@@
 in R [@rcoreteam_Language_2021]. All codes are accessible at 
-<DOI: 10.5281/zenodo.6338073>
+\url{https://zenodo.org/badge/latestdoi/440585701}
+<!-- [![zenodo.6338073.svg)](https://zenodo.org/badge/latestdoi/440585701). -->
 
@@
  source(here("predictions.R"))
- ggarrange(cont.obs.pred.both,scatter.obs.pred.both,
- cont.obs.pred.gam,scatter.obs.pred.gam,
- cont.obs.pred.Nrew,scatter.obs.pred.Nrew,
-           labels=c('a','b','c','d','e','f'),common.legend = F,
-   heights=c(1.4,1,1),nrow = 3,ncol = 2)
-
-```
-
-The main reason for chaining and penalty to give different
-predictions is the way that cleaner fish relative abundance influences the
-preference for the visitor clients. Visitor leaving probability has a
-similar positive effect on the probability of choosing the visitor
-clients on all three models, they all predict an increase preference 
-for visitors as the visitor probability increases  (Fig. \ref{fig:pred}).
-In contrast, cleaner fish relative abundance has a different effect in the
-model with only chaining, compared to the other two models,
-full model and penalty. In the model with only chaining, only intermediate 
-cleaner fish abundance triggers a preference for the visitor 
-clients (Fig. \ref{fig:pred} c). In both models with penalty, 
-both intermediate and low cleaner abundance triggered a preference 
-for the visitor (Fig. \ref{fig:pred} a,e). Note, however, we calculated 
-preferences shown in figure \ref{fig:pred} left panels by using only the mode 
+first_col<-plot_grid(nrow=3,align = "v",byrow = TRUE,
+          cont.obs.pred.both,cont.obs.pred.gam,cont.obs.pred.Nrew,
+          labels=c('a','c','e'),rel_heights = c(1.4,1,1))
+second_col<-plot_grid(nrow=3,align = "v",byrow = TRUE,
+          scatter.obs.pred.both,scatter.obs.pred.gam,scatter.obs.pred.Nrew,
+          labels=c('b','d','f'))
+plot_grid(first_col,second_col,rows = 1)
+```
+
+Low cleaner fish relative abundance yields different predictions 
+from a model with only chaining and with penalty.
+The model with only chaining predicts a low preference fpr the visitor when
+cleaner fish relative abundance is low (Fig. \ref{fig:pred} c). In contrast,
+the models including penalty (with and without chaining) predict high 
+preference for the visitor option (Fig. \ref{fig:pred} a and e).
+For intermediate and high cleaner relative abundances the predictions 
+are similar for all three models. Intermediate relative abundance 
+trigger a high preference for the visitor; while low abundances trigger
+low preference for the visitor (Fig. \ref{fig:pred}a,b,e). 
+Note, however, we calculated 
+preferences shown in figure \ref{fig:pred} left panels by using only the model 
 of the posterior distributions, and by holding constant the balance between 
-resident and visitors´ abundances. Panels on the right, show how close 
+resident and visitors' abundances. Panels on the right, show how close 
 predictions are from the observed data, allowing the balance between 
@@
 ggarrange(traces.neg,gelman.neg)
+```
+
+<!-- (ref:diagnosticsfull) MCMC convergence diagnostics for the full model. -->
+<!-- On the left trace-plots, on the right changes along the chain of the -->
+<!-- Gelman and Rubin's shrink factor [@brooks_General_1998]. -->
+
+```{r diagnosticsfullPAA, fig.cap='MCMC convergence diagnostics for the full model.
+On the left trace-plots, on the right changes along the chain of the Gelman and Rubin shrink factor.',out.width='100%',fig.height=5,cache=FALSE,message=FALSE}
+
+longMCMCdata4<-melt(MCMCdata4,id.vars = c("iteration","seed"),
+                    variable.name = "parameter",
+                    measure.vars = c("gamma","negReward","scaleConst"))
+
+parlab<-list(`gamma` =expression(gamma),
+          `negReward`=expression(eta),
+          `scaleConst`="Scaling constant")
+
+traces.full.PAA<-ggplot(longMCMCdata4,aes(x=iteration,y=value,colour=as.factor(seed)))+
+  geom_line()+
+  scale_color_manual(values = multDiscrPallet)+
+  labs(color="Chain")+
+  facet_grid(rows=vars(parameter),scales = "free",switch = "y",
+             labeller = function(variable,value){
+  return(parlab[value])})+
+  theme_classic()+
+  theme(legend.position = 'top')
+
+gel.full<-as.data.table(gelman.diag(mcmcList.4)$psrf)
+gel.full[,parameter:=c("gamma","negReward","scalConst")]
+
+pdf(file = NULL)
+gp.dat<-gelman.plot(mcmcList.4)
+rubbish <- dev.off()
+
+gp.dat.frame.PAA <- data.table(rbind(as.data.frame(gp.dat[["shrink"]][,,1]),
+                          as.data.frame(gp.dat[["shrink"]][,,2])),
+                q=rep(dimnames(gp.dat[["shrink"]])[[3]], each=nrow(gp.dat[["shrink"]][,,1])),
+                last.iter=rep(gp.dat[["last.iter"]], length(gp.dat)))
+
+gelman.full.PAA<-ggplot(melt(gp.dat.frame.PAA, c("q","last.iter"), value.name="shrink_factor"),
+       aes(last.iter, shrink_factor, colour=q, linetype=q)) +
+  geom_hline(yintercept=1, colour="grey30", lwd=0.2) +
+  geom_line() +
+  facet_grid(rows = vars(variable)) +
+  labs(x="Last Iteration in Chain", y="Shrink Factor",
+       colour="Quantile", linetype="Quantile") +
+  scale_linetype_manual(values=c(2,1))+
+  theme_classic()+
+  theme(legend.position = 'top',strip.text.y  = element_blank())
+
+ggarrange(traces.full.PAA,gelman.full.PAA)
+
+```
+
+<!-- (ref:diagnosticsGam) MCMC convergence diagnostics for the chaining model.  -->
+<!-- On the left trace-plots, on the right changes along the chain of the  -->
+<!-- Gelman and Rubin's shrink factor [@brooks_General_1998] -->
+
+```{r diaggamPAA,fig.cap='MCMC convergence diagnostics for the chaining model.
+On the left trace-plots, on the right changes along the chain of the Gelman and Rubin shrink factor ',echo=FALSE,message=FALSE,out.width='100%',fig.height=5,cache=FALSE,message=FALSE}
+longMCMCdata5<-melt(MCMCdata5,id.vars = c("iteration","seed"),
+                    variable.name = "parameter",
+                    measure.vars = c("gamma","scaleConst"))
+
+longMCMCdata5[,parameter:=factor(parameter,labels = c("gamma","'Scaling constant'"))]
+
+traces.gam.PAA<-ggplot(longMCMCdata5,aes(x=iteration,y=value,colour=as.factor(seed)))+
+  geom_line()+
+  scale_color_manual(values = multDiscrPallet)+
+  labs(color="Chain")+
+  facet_grid(rows=vars(parameter),scales = "free",switch = "y",
+             labeller = label_parsed)+
+  theme_classic()+
+  theme(legend.position = 'top')
+
+gel.gam<-as.data.table(gelman.diag(mcmcList.5)$psrf)
+gel.gam[,parameter:=c("gamma","scalConst")]
+
+pdf(file = NULL)
+gp.dat.gam<-gelman.plot(mcmcList.5)
+rubbish <- dev.off()
+
+gp.dat.frame.gam.PAA <- data.table(rbind(as.data.frame(gp.dat.gam[["shrink"]][,,1]),
+                          as.data.frame(gp.dat.gam[["shrink"]][,,2])),
+                q=rep(dimnames(gp.dat.gam[["shrink"]])[[3]], each=nrow(gp.dat.gam[["shrink"]][,,1])),
+                last.iter=rep(gp.dat.gam[["last.iter"]], length(gp.dat.gam)))
+
+gelman.gam.PAA<-ggplot(melt(gp.dat.frame.gam.PAA, c("q","last.iter"), value.name="shrink_factor"),
+       aes(last.iter, shrink_factor, colour=q, linetype=q)) +
+  geom_hline(yintercept=1, colour="grey30", lwd=0.2) +
+  geom_line() +
+  facet_grid(rows = vars(variable)) +
+  labs(x="Last Iteration in Chain", y="Shrink Factor",
+       colour="Quantile", linetype="Quantile") +
+  scale_linetype_manual(values=c(2,1))+
+  theme_classic()+
+  theme(legend.position = 'top',strip.text.y = element_blank())
+
+ggarrange(traces.gam.PAA,gelman.gam.PAA)
+```
+
+<!-- (ref:diagNeg) MCMC convergence diagnostics for the penalty model. -->
+<!-- On the left trace-plots, on the right changes along the chain of the -->
+<!-- Gelman and Rubin's shrink factor [@brooks_General_1998] -->
+
+```{r diagNegPAA,fig.cap='MCMC convergence diagnostics for the penalty model.
+On the left trace-plots, on the right changes along the chain of the Gelman and Rubin shrink factor',out.width='100%',fig.height=5,cache=FALSE,message=FALSE,out.width='100%',fig.height=5,cache=FALSE,message=FALSE}
+longMCMCdata6<-melt(MCMCdata6,id.vars = c("iteration","seed"),
+                    variable.name = "parameter",
+                    measure.vars = c("negReward","scaleConst"))
+
+longMCMCdata6[,parameter:=factor(parameter,labels = c("eta","'Scaling constant'"))]
+
+traces.neg.PAA<-ggplot(longMCMCdata6,aes(x=iteration,y=value,colour=as.factor(seed)))+
+  geom_line()+
+  scale_color_manual(values = multDiscrPallet)+
+  labs(color="Chain")+
+  facet_grid(rows=vars(parameter),scales = "free",switch = "y",
+             labeller = label_parsed)+
+  theme_classic()+
+  theme(legend.position = 'top')
+
+pdf(file = NULL)
+gp.dat.neg<-gelman.plot(mcmcList.6)
+rubbish <- dev.off()
+
+gp.dat.frame.neg.PAA <- data.table(rbind(as.data.frame(gp.dat.neg[["shrink"]][,,1]),
+                          as.data.frame(gp.dat.neg[["shrink"]][,,2])),
+                q=rep(dimnames(gp.dat.neg[["shrink"]])[[3]], each=nrow(gp.dat.neg[["shrink"]][,,1])),
+                last.iter=rep(gp.dat.neg[["last.iter"]], length(gp.dat.neg)))
+
+gelman.neg.PAA<-ggplot(melt(gp.dat.frame.neg.PAA, c("q","last.iter"), value.name="shrink_factor"),
+       aes(last.iter, shrink_factor, colour=q, linetype=q)) +
+  geom_hline(yintercept=1, colour="grey30", lwd=0.2) +
+  geom_line() +
+  facet_grid(rows = vars(variable)) +
+  labs(x="Last Iteration in Chain", y="Shrink Factor",
+       colour="Quantile", linetype="Quantile") +
+  scale_linetype_manual(values=c(2,1))+
+  theme_classic()+
+  theme(legend.position = 'top',strip.text.y = element_blank())
+
+ggarrange(traces.neg.PAA,gelman.neg.PAA)
 ```

### 2022-08-15 manuscript_PLOS/manuscript_PLOS.Rmd
update DOI
Further changes to include PAA in the analysis. Dealing with convergence problems

@@
     email: redouan.bshary@unine.ch
-    affiliation: Institute of Biology, University of Neuchatel
+    affiliation: a
 address:
   - code: a
-    address: Institute of Biology, University of Neuchatel, Rue Emile-Argand 11, 2000-CH Neuchatel, Switzerland
+    address: Institute of Biology, University of Neuchatel, Neuchatel, Switzerland
   - code: b
-    address: Department of Zoology, Stockholm University, Svante Arrheniusväg 18 B,  106 91 Stockholm, Sweden,
+    address: Department of Zoology, Stockholm University, Stockholm, Sweden
 abstract: |
@@
 This between variation in performance, and primates' known cognitive abilities
-[@reader_Evolution_2001], shows that performance in the task
+[@reader_Evolution_2011], shows that performance in the task
 cannot be readily explained by classifying species as having high and 
@@
 on a width of $5m$, and then on the 
-return individuals of small-bodied fish species ($TL < 10 cm$) \
+return individuals of small-bodied fish species ($TL < 10 cm$)
 on a width of $1 m$
@@
 
+### Ethics statement
+The Animal Ethics Committee of the Queensland government (DAFF)
+  approved the project (CA 2016/05/970 and CA 2017/05/1063)
+
 ### Statistical analysis
@@
 in R [@rcoreteam_Language_2021]. All codes are accessible at 
-<https://github.com/andreseqp/learnDatamodel>
+<DOI: 10.5281/zenodo.6338073>
 
@@
 Social competence is the ability to optimise social behaviour 
-to the available social information [@taborsky_Social_2012;
+to the available social information [@taborsky_Social_2012a;
 @bshary_Cooperation_2015;@varela_Correlated_2020]. Our analyses yielded no 
@@
 
+```{r diagnosticsfullPAA, fig.cap='MCMC convergence diagnostics for the full model.
+On the left trace-plots, on the right changes along the chain of the Gelman and Rubin shrink factor.',out.width='100%',fig.height=5,cache=FALSE,message=FALSE}
+
+longMCMCdata4<-melt(MCMCdata4,id.vars = c("iteration","seed"),
+                    variable.name = "parameter",
+                    measure.vars = c("gamma","negReward","scaleConst"))
+
+parlab<-list(`gamma` =expression(gamma),
+          `negReward`=expression(eta),
+          `scaleConst`="Scaling constant")
+
+traces.full.PAA<-ggplot(longMCMCdata4,aes(x=iteration,y=value,colour=as.factor(seed)))+
+  geom_line()+
+  scale_color_manual(values = multDiscrPallet)+
+  labs(color="Chain")+
+  facet_grid(rows=vars(parameter),scales = "free",switch = "y",
+             labeller = function(variable,value){
+  return(parlab[value])})+
+  theme_classic()+
+  theme(legend.position = 'top')
+
+gel.full<-as.data.table(gelman.diag(mcmcList.4)$psrf)
+gel.full[,parameter:=c("gamma","negReward","scalConst")]
+
+pdf(file = NULL)
+gp.dat<-gelman.plot(mcmcList.4)
+rubbish <- dev.off()
+
+gp.dat.frame <- data.table(rbind(as.data.frame(gp.dat[["shrink"]][,,1]), 
+                          as.data.frame(gp.dat[["shrink"]][,,2])), 
+                q=rep(dimnames(gp.dat[["shrink"]])[[3]], each=nrow(gp.dat[["shrink"]][,,1])),
+                last.iter=rep(gp.dat[["last.iter"]], length(gp.dat)))
+
+gelman.full.PAA<-ggplot(melt(gp.dat.frame, c("q","last.iter"), value.name="shrink_factor"), 
+       aes(last.iter, shrink_factor, colour=q, linetype=q)) + 
+  geom_hline(yintercept=1, colour="grey30", lwd=0.2) +
+  geom_line() +
+  facet_grid(rows = vars(variable)) +
+  labs(x="Last Iteration in Chain", y="Shrink Factor",
+       colour="Quantile", linetype="Quantile") +
+  scale_linetype_manual(values=c(2,1))+
+  theme_classic()+
+  theme(legend.position = 'top',strip.text.y  = element_blank())
+
+ggarrange(traces.full.PAA,gelman.full.PAA)
+
+```
+
 <!-- (ref:diagnosticsGam) MCMC convergence diagnostics for the chaining model.  -->
@@
 
+<!-- (ref:diagnosticsGam) MCMC convergence diagnostics for the chaining model.  -->
+<!-- On the left trace-plots, on the right changes along the chain of the  -->
+<!-- Gelman and Rubin's shrink factor [@brooks_General_1998] -->
+
+```{r diaggamPAA,fig.cap='MCMC convergence diagnostics for the chaining model.
+On the left trace-plots, on the right changes along the chain of the Gelman and Rubin shrink factor ',echo=FALSE,message=FALSE,out.width='100%',fig.height=5,cache=FALSE,message=FALSE}
+longMCMCdata5<-melt(MCMCdata5,id.vars = c("iteration","seed"),
+                    variable.name = "parameter",
+                    measure.vars = c("gamma","scaleConst"))
+
+parlab<-list(`gamma` =expression(gamma),
+          `scaleConst`="Scaling constant")
+
+traces.gam.PAA<-ggplot(longMCMCdata5,aes(x=iteration,y=value,colour=as.factor(seed)))+
+  geom_line()+
+  scale_color_manual(values = multDiscrPallet)+
+  labs(color="Chain")+
+  facet_grid(rows=vars(parameter),scales = "free",switch = "y",
+             labeller = function(variable,value){
+  return(parlab[value])})+
+  theme_classic()+
+  theme(legend.position = 'top')
+
+gel.gam<-as.data.table(gelman.diag(mcmcList.5)$psrf)
+gel.gam[,parameter:=c("gamma","scalConst")]
+
+pdf(file = NULL)
+gp.dat.gam<-gelman.plot(mcmcList.5)
+rubbish <- dev.off()
+
+gp.dat.frame.gam.PAA <- data.table(rbind(as.data.frame(gp.dat.gam[["shrink"]][,,1]), 
+                          as.data.frame(gp.dat.gam[["shrink"]][,,2])), 
+                q=rep(dimnames(gp.dat.gam[["shrink"]])[[3]], each=nrow(gp.dat.gam[["shrink"]][,,1])),
+                last.iter=rep(gp.dat.gam[["last.iter"]], length(gp.dat.gam)))
+
+gelman.gam.PAA<-ggplot(melt(gp.dat.frame.gam.PAA, c("q","last.iter"), value.name="shrink_factor"), 
+       aes(last.iter, shrink_factor, colour=q, linetype=q)) + 
+  geom_hline(yintercept=1, colour="grey30", lwd=0.2) +
+  geom_line() +
+  facet_grid(rows = vars(variable)) +
+  labs(x="Last Iteration in Chain", y="Shrink Factor",
+       colour="Quantile", linetype="Quantile") +
+  scale_linetype_manual(values=c(2,1))+
+  theme_classic()+
+  theme(legend.position = 'top',strip.text.y = element_blank())
+
+ggarrange(traces.gam.PAA,gelman.gam.PAA)
+```
+
 <!-- (ref:diagNeg) MCMC convergence diagnostics for the penalty model. -->
@@
 ggarrange(traces.neg,gelman.neg)
+```
+<!-- (ref:diagNeg) MCMC convergence diagnostics for the penalty model. -->
+<!-- On the left trace-plots, on the right changes along the chain of the -->
+<!-- Gelman and Rubin's shrink factor [@brooks_General_1998] -->
+
+```{r diagNeg,fig.cap='MCMC convergence diagnostics for the penalty model.
+On the left trace-plots, on the right changes along the chain of the Gelman and Rubin shrink factor',out.width='100%',fig.height=5,cache=FALSE,message=FALSE,out.width='100%',fig.height=5,cache=FALSE,message=FALSE}
+longMCMCdata6<-melt(MCMCdata6,id.vars = c("iteration","seed"),
+                    variable.name = "parameter",
+                    measure.vars = c("negReward","scaleConst"))
+
+parlab<-list(`negReward` =expression(eta),
+          `scaleConst`="Scaling constant")
+
+traces.neg.PAA<-ggplot(longMCMCdata6,aes(x=iteration,y=value,colour=as.factor(seed)))+
+  geom_line()+
+  scale_color_manual(values = multDiscrPallet)+
+  labs(color="Chain")+
+  facet_grid(rows=vars(parameter),scales = "free",switch = "y",
+             labeller = function(variable,value){
+  return(parlab[value])})+
+  theme_classic()+
+  theme(legend.position = 'top')
+
+pdf(file = NULL)
+gp.dat.neg<-gelman.plot(mcmcList.6)
+rubbish <- dev.off()
+
+gp.dat.frame.neg.PAA <- data.table(rbind(as.data.frame(gp.dat.neg[["shrink"]][,,1]),
+                          as.data.frame(gp.dat.neg[["shrink"]][,,2])),
+                q=rep(dimnames(gp.dat.neg[["shrink"]])[[3]], each=nrow(gp.dat.neg[["shrink"]][,,1])),
+                last.iter=rep(gp.dat.neg[["last.iter"]], length(gp.dat.neg)))
+
+gelman.neg.PAA<-ggplot(melt(gp.dat.frame.neg, c("q","last.iter"), value.name="shrink_factor"),
+       aes(last.iter, shrink_factor, colour=q, linetype=q)) +
+  geom_hline(yintercept=1, colour="grey30", lwd=0.2) +
+  geom_line() +
+  facet_grid(rows = vars(variable)) +
+  labs(x="Last Iteration in Chain", y="Shrink Factor",
+       colour="Quantile", linetype="Quantile") +
+  scale_linetype_manual(values=c(2,1))+
+  theme_classic()+
+  theme(legend.position = 'top',strip.text.y = element_blank())
+
+ggarrange(traces.neg.PAA,gelman.neg.PAA)
 ```

### 2022-08-15 ActCritMCMC.cpp

@@ -113,6 +113,9 @@ public:
 	virtual int mapOptions(client options[], int &choice)=0;
 	// function that maps state action pairs to indexes in the array 'values' 
 	//where values are stored
+	bool isRVoption(int time);
+	// Function to know if there is an RV option in the 
+	// current t=0 or future t=1 option
 	virtual void updateThet(int curState) = 0;
 	// function to update the policy parameter Theta
 	int numEst;
@@ -489,6 +492,15 @@ void agent::choice() {
 	else {
 		// if the clients are the same - choose randomly
 		choiceT1 = rnd::bernoulli();
+	}
+}
+
+bool agent::isRVoption(int time) {
+	if (time == 0) {
+		return(cleanOptionsT[0] + cleanOptionsT[1] == 1);
+	}
+	else {
+		return(cleanOptionsT1[0] + cleanOptionsT1[1] == 1);
 	}
 }
 
@@ -933,7 +945,7 @@ void do_simulation(//del focal_model,
 					learnScenario(sim_param["scenario"]));
 			cleaners[emp_data[id_data_point].group]->update();
 				if (trial > int(sim_param["totRounds"]) * float(sim_param["propfullPrint"])) {
-					if (cleaners[emp_data[id_data_point].group]->getstate(0) == 0) {
+					if (cleaners[emp_data[id_data_point].group]->isRVoption(0)) {
 						++countRVopt;
 						if (cleaners[emp_data[id_data_point].group]->
 							cleanOptionsT[cleaners[emp_data[id_data_point].group]->getChoice(0)] == visitor) 
@@ -967,39 +979,39 @@ int main(int argc, char* argv[]){
 	// Only for debugging 
 	// input parameters provided by a JSON file with the following
 	// structure:
-	 json sim_param;
-	 sim_param["totRounds"]    = 5000;
-	 sim_param["ResReward"]    = 1;
-	 sim_param["VisReward"]    = 1;
-	 sim_param["ResProbLeav"]  = 0;
-	 sim_param["scenario"]  = 0;
-	 sim_param["inbr"]         = 0;
-	 sim_param["outbr"]        = 0;
-	 sim_param["seed"]         = 3;
-	 sim_param["forRat"]       = 0.0;
[…]

### 2022-08-15 analysisMCMC.R

@@ -8,6 +8,7 @@ library(ggplot2)
 library(cowplot)
 library(ggdist)
 library(ggpubr)
+library(here)
 source(here("../R_files/posPlots.R"))
 source(here("loadData.R"))
 library("jsonlite")
@@ -20,12 +21,15 @@ library("jsonlite")
 scen1<-"MCMCclean_gam_Nrew_sca_"
 scen2<-"MCMCclean_gam_sca_"
 scen3<-"MCMCclean_Nrew_sca_"
+scen4<-"MCMCclean_PAA2_gam_Nrew_sca_"
+scen5<-"MCMCclean_PAA_gam_sca_"
+scen6<-"MCMCclean_PAA_Nrew_sca_"
 
 
 # NLables names for the three scenarios
 labels.Scen<-c("both","gam","Nrew")
 labelsPlot.Scen<-c("Full Model","Chaining","Penalty")
-
+labels.agente<-c("FAA","PAA")
 ## Load files --------------------------------------------------------------
 
 # Defaults for MCMC analysis
@@ -36,6 +40,9 @@ thinning<-100
 MCMCdata1<-loadMCMCrun(scen1,thinning = thinning,burn.in = burn.in)
 MCMCdata2<-loadMCMCrun(scen2,thinning = thinning,burn.in = burn.in)
 MCMCdata3<-loadMCMCrun(scen3,thinning = thinning,burn.in = burn.in)
+MCMCdata4<-loadMCMCrun(scen4,thinning = thinning,burn.in = burn.in)
+MCMCdata5<-loadMCMCrun(scen5,thinning = thinning,burn.in = burn.in)
+MCMCdata6<-loadMCMCrun(scen6,thinning = thinning,burn.in = burn.in)
 
 
 # Create list with the data, convenient to use CODA for diagnostics
@@ -54,6 +61,25 @@ mcmcList.2<-mcmc.list(do.call(list,lapply(unique(MCMCdata2$seed), function(repli
 
 mcmcList.3<-mcmc.list(do.call(list,lapply(unique(MCMCdata3$seed), function(repli){
   rundata<-MCMCdata3[seed==repli]
+  mcmcRun<-mcmc(rundata[,.(negReward,scaleConst)],thin = thinning)#
+  return(mcmcRun)
+})))
+
+mcmcList.4<-mcmc.list(do.call(list,lapply(unique(MCMCdata4$seed), function(repli){
[…]

### 2022-08-15 parTOjson.R

@@ -6,13 +6,13 @@ source(here("loadData.R"))
 
 simsDir<-"Simulations"
 
-clusterHome<-"/home/ubuntu"
+clusterHome<-"/home/ubuntu/learnData"
 
 fileName<-"parameters.json"
 
 # name of the scenario for which parameter files will be produces
 # format used for the name: MCMCclean_*parameter1_paramerter2_parameter3.....
-scenario<- "test"#"MCMCclean_PAA_gam_Nre_sca"
+scenario<- "MCMCclean_PAA2_gam_Nrew_sca"#""
 
 
 # MCMC fit - Generate json parameter files for -------------------------------------
@@ -38,22 +38,22 @@ param_mcmc<-list(totRounds=10000,
                  # Type of agent FAA (chuncking), PAA (not chuncking)
                  propfullPrint = 0.7, 
                  #Proportion of final rounds used to calculate predictions
-                 sdPert=c(0.05,0.05,0.3,4,300), 
+                 sdPert=c(0.05,0.05,0.2,5,200), 
                  # Width of the perturbation kernel for each parameter
                  # alphaA,AlphaC, Gamma, NegRew, scalConst
                  chain_length=100000, # Chain length
                  init=c(0.05,0.05,0,0,30), # Initial values for each of the parameters
                  # alphaA,AlphaC, Gamma, NegRew, scalConst
-                 pertScen = c(FALSE,FALSE,FALSE,TRUE,TRUE), # boolean controlling which
+                 pertScen = c(FALSE,FALSE,TRUE,TRUE,TRUE), # boolean controlling which
                  # parameter is perturbed
                  MCMC =1, # run chain=1, run prediction for one parameter set = 0
                  nRep=1, # number of replicate simulations
                  Group = FALSE, # grouped data according to social competence
                  # from triki et al. 2020
                  dataFile =
-                 # paste(clusterHome,"Data","data_cleaner_abs_threa1.5.txt",
-                 #                  sep="/"),
-                   here("Data","data_cleaner_abs_threa1.5.txt"),
+                 paste(clusterHome,"Data","data_cleaner_abs_threa1.5.txt",
+                                  sep="/"),
+                   # here("Data","data_cleaner_abs_threa1.5.txt"),
                  # location of the data file
[…]

### 2022-08-16 manuscript_BE/manuscript_BE.Rmd
Edits in the source code to be able to sit some fish with FAA and others with PAA

@@
 
-```{r post, fig.cap='Posterior distributions for parameter values $\\gamma$ and $\\eta$ for the three models (Full model, chaining only and penalty only).
-We show the kernel density estimates, below the mode (black dot) and the 66 (light blue shade) and 95\\% (grey shade)  highest posterior density interval for the two parameters.
+```{r post, fig.cap='Posterior distributions for parameter values $\\gamma$ and $\\eta$ for the six models, three for each type of agent (Agents: FAA and PAA; models: Full model, chaining only and penalty only).
+We show the kernel density estimates, below the mode (black dot) and the 66 (light color shade) and 95\\% (grey shade)  highest posterior density interval for the two parameters.
+Colors blue and red denote agents FAA and PAA respectively.
 On the top, panels a and b show posterior distributions for a full model, including chaining ($\\gamma$) and penalty ($\\eta$).

### 2022-08-16 ActCritMCMC.cpp

@@ -626,14 +626,17 @@ struct model_param {
 	//model_param(model_param const &obj);
 	double alphaC, alphaA, scaleConst;
 	double gamma[2], negReward[2];
+	double probFAA[2];
 	model_param &operator= (model_param const &rhs) {
 		alphaA = rhs.alphaA;
 		alphaC = rhs.alphaC;
 		scaleConst = rhs.scaleConst;
 		gamma[0] = rhs.gamma[0];
 		negReward[0] = rhs.negReward[0];
+		probFAA[0] = rhs.probFAA[0];
 		gamma[1] = rhs.gamma[1];
 		negReward[1] = rhs.negReward[1];
+		probFAA[1] = rhs.probFAA[1];
 		return *this;
 	}
 };
@@ -724,9 +727,10 @@ void initializeChainFile(ofstream &chainOutput,nlohmann::json param){
 	string IndFile = create_filename(namedir, param);
 	chainOutput.open(IndFile.c_str());
 	chainOutput << "iteration	" << "alpha_actor	" << "alpha_critic	" <<
-		 "gamma	" << "negReward	";
+		 "gamma	" << "negReward	" << "probFAA	";
 	if (bool(param["Group"]))
-		chainOutput	<< "gamma.1	" << "negReward.1	";
+		chainOutput	<< "gamma.1	" << "negReward.1	" << 
+		"probFAA.1";
 	chainOutput  << "scaleConst	" << "fit	" << "ratio" << endl;
 }
 
@@ -875,6 +879,10 @@ model_param perturb_parameters_uniform(model_param focal_param, json &sim_param)
 		boundedParUnifPert(focal_param.negReward[0],
 			sim_param["sdPert"][3], -INFINITY, INFINITY) +
 			(!bool(sim_param["pertScen"][3]))*focal_param.negReward[0];
+	new_param.probFAA[0] = bool(sim_param["pertScen"][5]) *
+		boundedParUnifPert(focal_param.probFAA[0],
+			sim_param["sdPert"][5], 0, 1) +
+			(!bool(sim_param["pertScen"][5])) * focal_param.probFAA[0];
 	if (sim_param["Group"]) {
 		new_param.gamma[1] = bool(sim_param["pertScen"][2]) *
 			boundedParUnifPert(focal_param.gamma[1],
[…]

### 2022-08-16 analysisMCMC.R

@@ -22,8 +22,8 @@ scen1<-"MCMCclean_gam_Nrew_sca_"
 scen2<-"MCMCclean_gam_sca_"
 scen3<-"MCMCclean_Nrew_sca_"
 scen4<-"MCMCclean_PAA2_gam_Nrew_sca_"
-scen5<-"MCMCclean_PAA_gam_sca_"
-scen6<-"MCMCclean_PAA_Nrew_sca_"
+scen5<-"MCMCclean_PAA2_gam_sca_"
+scen6<-"MCMCclean_PAA2_Nrew_sca_"
 
 
 # NLables names for the three scenarios
@@ -65,11 +65,15 @@ mcmcList.3<-mcmc.list(do.call(list,lapply(unique(MCMCdata3$seed), function(repli
   return(mcmcRun)
 })))
 
+MCMCdata4<-MCMCdata4[iteration<66800]
+
 mcmcList.4<-mcmc.list(do.call(list,lapply(unique(MCMCdata4$seed), function(repli){
   rundata<-MCMCdata4[seed==repli]
   mcmcRun<-mcmc(rundata[,.(gamma,negReward,scaleConst)],thin = thinning)#
   return(mcmcRun)
 })))
+
+MCMCdata5<-MCMCdata5[iteration<MCMCdata5[,max(iteration),by=seed][,min(V1)]]
 
 mcmcList.5<-mcmc.list(do.call(list,lapply(unique(MCMCdata5$seed), function(repli){
   rundata<-MCMCdata5[seed==repli]
@@ -77,7 +81,7 @@ mcmcList.5<-mcmc.list(do.call(list,lapply(unique(MCMCdata5$seed), function(repli
   return(mcmcRun)
 })))
 
-
+MCMCdata6<-MCMCdata6[iteration<MCMCdata6[,max(iteration),by=seed][,min(V1)]]
 mcmcList.6<-mcmc.list(do.call(list,lapply(unique(MCMCdata6$seed), function(repli){
   rundata<-MCMCdata6[seed==repli]
   mcmcRun<-mcmc(rundata[,.(negReward,scaleConst)],thin = thinning)#

### 2022-08-16 parTOjson.R

@@ -12,13 +12,13 @@ fileName<-"parameters.json"
 
 # name of the scenario for which parameter files will be produces
 # format used for the name: MCMCclean_*parameter1_paramerter2_parameter3.....
-scenario<- "MCMCclean_PAA2_gam_Nrew_sca"#""
+scenario<- "test"#""
 
 
 # MCMC fit - Generate json parameter files for -------------------------------------
 
 # for MCMC
-param_mcmc<-list(totRounds=10000, 
+param_mcmc<-list(totRounds=100, 
                  # Number of rounds in the learning model
                  ResReward=1,VisReward=1, 
                  # Magnitude of reward for residents and visitors
@@ -34,26 +34,26 @@ param_mcmc<-list(totRounds=10000,
                  # Rate at which cleaners forget what they have learned
                  seed=1,  
                  # Seed for the random number generator
-                 agent="PAA", 
+                 # agent="PAA", 
                  # Type of agent FAA (chuncking), PAA (not chuncking)
                  propfullPrint = 0.7, 
                  #Proportion of final rounds used to calculate predictions
-                 sdPert=c(0.05,0.05,0.2,5,200), 
+                 sdPert=c(0.05,0.05,0.3,6,100,0.2), 
                  # Width of the perturbation kernel for each parameter
-                 # alphaA,AlphaC, Gamma, NegRew, scalConst
+                 # alphaA,AlphaC, Gamma, NegRew, scalConst,probFAA
                  chain_length=100000, # Chain length
-                 init=c(0.05,0.05,0,0,30), # Initial values for each of the parameters
-                 # alphaA,AlphaC, Gamma, NegRew, scalConst
-                 pertScen = c(FALSE,FALSE,TRUE,TRUE,TRUE), # boolean controlling which
+                 init=c(0.05,0.05,0,0,30,1), # Initial values for each of the parameters
+                 # alphaA,AlphaC, Gamma, NegRew, scalConst,probFAA
+                 pertScen = c(FALSE,FALSE,FALSE,TRUE,TRUE,TRUE), # boolean controlling which
                  # parameter is perturbed
                  MCMC =1, # run chain=1, run prediction for one parameter set = 0
                  nRep=1, # number of replicate simulations
                  Group = FALSE, # grouped data according to social competence
                  # from triki et al. 2020
[…]

### 2022-08-22 manuscript_BE/manuscript_BE.Rmd
Implementation of a probability for choosing the agent type is successfully implemented. However, the new model does not add a lot of explanatory power

@@
 
-```{=latex}
-\keywords{learning, behavior, cleaners, bayesian statisitics, behavioral mechanisms}
-```
+<!-- ```{=latex} -->
+<!-- \keywords{learning, behavior, cleaners, bayesian statisitics, behavioral mechanisms} -->
+<!-- ``` -->
 
@@
 forced cleaner fish to decide based solely on the association between 
-the behaviour and the collor/pattern cue [@wismer_Cuebased_2019]. 
+the behaviour and the color/pattern cue [@wismer_Cuebased_2019]. 
 Triki et al. [-@triki_Biological_2019;@triki_Brain_2020] 
@@
 
+scen1<-"MCMCclean_gam_Nrew_sca_"
+scen2<-"MCMCclean_gam_sca_"
+scen3<-"MCMCclean_Nrew_sca_"
+scen4<-"MCMCclean_PAA_gam_Nrew_sca_"
+scen5<-"MCMCclean_PAA_gam_sca_"
+scen6<-"MCMCclean_PAA_Nrew_sca_"
+
 source(here("analysisMCMC.R"))
-
 ggarrange(allGammapost.plot,alletapost.plot,common.legend = TRUE)
@@
 
+```
+
+```{r fitAllModels}
+panel.rsqr.all
 ```
@@
 Their visualizations can be found in the supplementary 
-material (Fig. \ref{fig:scaConst}), as well as the diagnostics of the MCMCs
-(Figs. \ref{fig:diagnosticsfull},\ref{fig:diaggam},\ref{fig:diagNeg}).
+material (Fig. \ref{fig:scaConstFAA} and \ref{fig:scaConstPAA}), as well as the diagnostics of the MCMCs
+(Figs. \ref{fig:diagnosticsfullFAA},\ref{fig:diaggamFAA},\ref{fig:diagNegFAA},
+\ref{fig:diagnosticsfullPAA},\ref{fig:diaggamPAA},\ref{fig:diagNegPAA}).
 
@@
 
-```{r pred, fig.cap='Observed and predicted probability of choosing a visitor.
+```{r predFAA, fig.cap='Observed and predicted probability of choosing a visitor.
 Left-hand side panel: colour contour shows the prediction from the learning model using the mode of the posterior distributions of parameters recovered by the statistical analysis.
@@
 
+scen1<-"MCMCclean_gam_Nrew_sca_"
+scen2<-"MCMCclean_gam_sca_"
+scen3<-"MCMCclean_Nrew_sca_"
  source(here("predictions.R"))
@@
 second_col<-plot_grid(nrow=3,align = "v",byrow = TRUE,
+          scatter.obs.pred.both,scatter.obs.pred.gam,scatter.obs.pred.Nrew,
+           rel_heights = c(1.4,1,1),
+          labels=c('b','d','f'))
+plot_grid(first_col,second_col,rows = 1)
+```
+
+```{r predPAA, fig.cap='Observed and predicted probability of choosing a visitor.
+Left-hand side panel: colour contour shows the prediction from the learning model using the mode of the posterior distributions of parameters recovered by the statistical analysis.
+Dots show the frequency of visitor choices for the 12 reef sites, as well as the corresponding relative cleaner fish abundance (x axis) and frequency of visitors clients leaving the cleaning station (y axis).
+Right-hand side panels: Variation of the predicted probabilities  of choosing a visitor over a resident and their observed values for 12 locations.
+Circles show the mean prediction for each location from 100 samples taken from the posterior distribution.
+Thick and thin bars show the 66 and 95\\% credible interval, respectively, taken from those posterior samples.
+Squares show the predictions used for the panel on the right-hand side.
+Colour coding denotes different reef site/year of the data collection (see Empirical data section).
+The black line corresponds to a perfect match between observed and predicted probabilities.
+Upper panels (a and b) show predictions from a model including chaining and penalty; middle panels (c and d) from a  model with only chaining; lower panels (e and f) from a model with penalty only.',out.width='100%',fig.height=5,cache=FALSE}
+
+scen1<-"MCMCclean_PAA2_gam_Nrew_sca_"
+scen2<-"MCMCclean_PAA2_gam_sca_"
+scen3<-"MCMCclean_PAA2_Nrew_sca_"
+
+source(here("predictions.R"))
+first_col<-plot_grid(nrow=3,align = "v",byrow = TRUE,
+          cont.obs.pred.both,cont.obs.pred.gam,cont.obs.pred.Nrew,
+          labels=c('a','c','e'),rel_heights = c(1.4,1,1))
+second_col<-plot_grid(nrow=3,align = "v",byrow = TRUE,
+                      rel_heights = c(1.4,1,1),
           scatter.obs.pred.both,scatter.obs.pred.gam,scatter.obs.pred.Nrew,
@@
 sca.both.post.PAA<-ggplot(data=MCMCdata4,aes(x=scaleConst)) + 
-  stat_halfeye(aes(fill=stat(cut(x,breaks = cuts.4$scaleConst))),
+  stat_halfeye(aes(fill=stat(level)),
                point_interval = mode_hdi, .width = c(.66, .95),
@@
 sca.gam.post.PAA<-ggplot(data=MCMCdata5,aes(x=scaleConst)) + 
-  stat_halfeye(aes(fill=stat(cut(x,breaks = cuts.5$scaleConst))),
+  stat_halfeye(aes(fill=stat(level)),
                point_interval = mode_hdi, 
@@
 sca.nRew.post.PAA<-ggplot(data=MCMCdata6,aes(x=scaleConst)) +
-  stat_halfeye(aes(fill=stat(cut(x,breaks = cuts.6$scaleConst))),
+  stat_halfeye(aes(fill=stat(level)),
                point_interval = mode_hdi, .width = c(.66, .95),
@@
                show.legend=FALSE) +
-  scale_fill_manual(values=c("skyblue","gray85"))+
+  scale_fill_manual(values=c("gray85","skyblue","gray85"))+
   labs(title=labelsPlot.Scen[3],x="",y="")+
@@
 ggarrange(traces.neg.PAA,gelman.neg.PAA)
+```
+```{r diagbothGroup,fig.cap='MCMC convergence diagnostics for the penalty model.
+On the left trace-plots, on the right changes along the chain of the Gelman and Rubin shrink factor',out.width='100%',fig.height=5,cache=FALSE,message=FALSE,out.width='100%',fig.height=5,cache=FALSE,message=FALSE}
+longMCMCdata7<-melt(MCMCdata7,id.vars = c("iteration","seed"),
+                    variable.name = "parameter",
+                    measure.vars = c("gamma","probFAA","probFAA.1","scaleConst"))
+
+longMCMCdata7[,parameter:=factor(parameter,labels = c("gamma","p[FAA]","p[FAA_1]","'Scaling constant'"))]
+
+traces.both.group<-ggplot(longMCMCdata7,aes(x=iteration,y=value,colour=as.factor(seed)))+
+  geom_line()+
+  scale_color_manual(values = multDiscrPallet)+
+  labs(color="Chain")+
+  facet_grid(rows=vars(parameter),scales = "free",switch = "y",
+             labeller = label_parsed)+
+  theme_classic()+
+  theme(legend.position = 'top')
+
+pdf(file = NULL)
+gp.dat.both.group<-gelman.plot(mcmcList.7)
+rubbish <- dev.off()
+
+gp.dat.frame.both.group <- data.table(rbind(as.data.frame(gp.dat.both.group[["shrink"]][,,1]),
+                          as.data.frame(gp.dat.both.group[["shrink"]][,,2])),
+                q=rep(dimnames(gp.dat.both.group[["shrink"]])[[3]], each=nrow(gp.dat.neg[["shrink"]][,,1])),
+                last.iter=rep(gp.dat.both.group[["last.iter"]], length(gp.dat.both.group)))
+
+gelman.both.group<-ggplot(melt(gp.dat.frame.both.group, c("q","last.iter"), value.name="shrink_factor"),
+       aes(last.iter, shrink_factor, colour=q, linetype=q)) +
+  geom_hline(yintercept=1, colour="grey30", lwd=0.2) +
+  geom_line() +
+  facet_grid(rows = vars(variable)) +
+  labs(x="Last Iteration in Chain", y="Shrink Factor",
+       colour="Quantile", linetype="Quantile") +
+  scale_linetype_manual(values=c(2,1))+
+  theme_classic()+
+  theme(legend.position = 'top',strip.text.y = element_blank())
+
+ggarrange(traces.both.group,gelman.both.group)
 ```

### 2022-08-22 manuscript_BE/manuscript_BE.tex
Implementation of a probability for choosing the agent type is successfully implemented. However, the new model does not add a lot of explanatory power

@@
 is a mechanism involved in human foresight.
-
-\keywords{learning, behavior, cleaners, bayesian statisitics, behavioral mechanisms}
 
@@
 forced cleaner fish to decide based solely on the association between
-the behaviour and the collor/pattern cue (Wismer et al. 2019). Triki et
+the behaviour and the color/pattern cue (Wismer et al. 2019). Triki et
 al. (2019, 2020) tested the fish for a maximum of 200 trials with 20
@@
 \begin{figure}
-\includegraphics[width=1\linewidth]{manuscript_BE_files/figure-latex/post-1} \caption{Posterior distributions for parameter values $\gamma$ and $\eta$ for the three models (Full model, chaining only and penalty only).
-We show the kernel density estimates, below the mode (black dot) and the 66 (light blue shade) and 95\% (grey shade)  highest posterior density interval for the two parameters.
+\includegraphics[width=1\linewidth]{manuscript_BE_files/figure-latex/post-1} \caption{Posterior distributions for parameter values $\gamma$ and $\eta$ for the six models, three for each type of agent (Agents: FAA and PAA; models: Full model, chaining only and penalty only).
+We show the kernel density estimates, below the mode (black dot) and the 66 (light color shade) and 95\% (grey shade)  highest posterior density interval for the two parameters.
+Colors blue and red denote agents FAA and PAA respectively.
 On the top, panels a and b show posterior distributions for a full model, including chaining ($\gamma$) and penalty ($\eta$).
@@
 \end{figure}
+
+\includegraphics{manuscript_BE_files/figure-latex/fitAllModels-1.pdf}
 
@@
 given that they do not bring biological insight. Their visualizations
-can be found in the supplementary material (Fig. \ref{fig:scaConst}), as
-well as the diagnostics of the MCMCs (Figs.
-\ref{fig:diagnosticsfull},\ref{fig:diaggam},\ref{fig:diagNeg}).
+can be found in the supplementary material (Fig. \ref{fig:scaConstFAA}
+and \ref{fig:scaConstPAA}), as well as the diagnostics of the MCMCs
+(Figs.
+\ref{fig:diagnosticsfullFAA},\ref{fig:diaggamFAA},\ref{fig:diagNegFAA},
+\ref{fig:diagnosticsfullPAA},\ref{fig:diaggamPAA},\ref{fig:diagNegPAA}).
 
 \begin{figure}
-\includegraphics[width=1\linewidth]{manuscript_BE_files/figure-latex/pred-1} \caption{Observed and predicted probability of choosing a visitor.
+\includegraphics[width=1\linewidth]{manuscript_BE_files/figure-latex/predFAA-1} \caption{Observed and predicted probability of choosing a visitor.
 Left-hand side panel: colour contour shows the prediction from the learning model using the mode of the posterior distributions of parameters recovered by the statistical analysis.
@@
 The black line corresponds to a perfect match between observed and predicted probabilities.
-Upper panels (a and b) show predictions from a model including chaining and penalty; middle panels (c and d) from a  model with only chaining; lower panels (e and f) from a model with penalty only.}\label{fig:pred}
+Upper panels (a and b) show predictions from a model including chaining and penalty; middle panels (c and d) from a  model with only chaining; lower panels (e and f) from a model with penalty only.}\label{fig:predFAA}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=1\linewidth]{manuscript_BE_files/figure-latex/predPAA-1} \caption{Observed and predicted probability of choosing a visitor.
+Left-hand side panel: colour contour shows the prediction from the learning model using the mode of the posterior distributions of parameters recovered by the statistical analysis.
+Dots show the frequency of visitor choices for the 12 reef sites, as well as the corresponding relative cleaner fish abundance (x axis) and frequency of visitors clients leaving the cleaning station (y axis).
+Right-hand side panels: Variation of the predicted probabilities  of choosing a visitor over a resident and their observed values for 12 locations.
+Circles show the mean prediction for each location from 100 samples taken from the posterior distribution.
+Thick and thin bars show the 66 and 95\% credible interval, respectively, taken from those posterior samples.
+Squares show the predictions used for the panel on the right-hand side.
+Colour coding denotes different reef site/year of the data collection (see Empirical data section).
+The black line corresponds to a perfect match between observed and predicted probabilities.
+Upper panels (a and b) show predictions from a model including chaining and penalty; middle panels (c and d) from a  model with only chaining; lower panels (e and f) from a model with penalty only.}\label{fig:predPAA}
 \end{figure}
@@
 \begin{figure}[H]
-\includegraphics[width=0.95\linewidth,]{manuscript_BE_files/figure-latex/scaConst-1} \caption{Posterior distributions for scaling constant for the three models (Full model, chaining only and penalty only).
+\includegraphics[width=0.95\linewidth,]{manuscript_BE_files/figure-latex/scaConstFAA-1} \caption{Posterior distributions for scaling constant for the three models (Full model, chaining only and penalty only).
 We show the kernel density estimates, below the mode (black dot) and the 65\% (light blue shade) and 95\% (grey shade)  highest posterior density interval.
-On the top, panel a shows the posterior distribution from the full model; panel b from the model with only chaining; and panel c from a model with only penalty.}\label{fig:scaConst}
+On the top, panel a shows the posterior distribution from the full model; panel b from the model with only chaining; and panel c from a model with only penalty.}\label{fig:scaConstFAA}
+\end{figure}
+
+\begin{figure}[H]
+\includegraphics[width=0.95\linewidth,]{manuscript_BE_files/figure-latex/scaConstPAA-1} \caption{Posterior distributions for scaling constant for the three models (Full model, chaining only and penalty only).
+We show the kernel density estimates, below the mode (black dot) and the 65\% (light blue shade) and 95\% (grey shade)  highest posterior density interval.
+On the top, panel a shows the posterior distribution from the full model; panel b from the model with only chaining; and panel c from a model with only penalty.}\label{fig:scaConstPAA}
 \end{figure}
@@
 \includegraphics[width=1\linewidth]{manuscript_BE_files/figure-latex/diagnosticsfullPAA-1} \caption{MCMC convergence diagnostics for the full model.
-On the left trace-plots, on the right changes along the chain of the Gelman and Rubin shrink factor.}\label{fig:diagnosticsfullPAA}
+On the left trace-plots, fig.height=5, message=FALSE, cache=FALSE, on the right changes along the chain of the Gelman and Rubin shrink factor.}\label{fig:diagnosticsfullPAA}
 \end{figure}

### 2022-08-22 ActCrit.cpp

@@ -681,7 +681,7 @@ int main(int argc, char* argv[]){
 	double outbr = param["outbr"];
 	int trainingRep = param["trainingRep"];
 	double alphaT = param["alphaT"];
-	int numlearn = param["numlearn"];
+	int learn = param["learn"];
 	int printGen = param["printGen"];
 	double propfullPrint = param["propfullPrint"];
 	int seed = param["seed"];
@@ -717,15 +717,16 @@ int main(int argc, char* argv[]){
 								double init = tmpGam*(1 - pow(1 - tmpRes - tmpVis, 2)) / (1 - tmpGam);
 
 							   // Initialize agents
-								learners[1] = new PAATyp1(alphaT, *itg, *itn,
+								learners[0] = new PAATyp1(alphaT, *itg, *itn,
 									*italTh, init, alphaThNch);
-								learners[0] = new FAATyp1(alphaT, *itg, *itn, 
+								learners[1] = new FAATyp1(alphaT, *itg, *itn, 
 									*italTh, init);
 								// output of learning trials
 								ofstream printTest;
 // Loop through types of agents
-for (int k = 0; k < numlearn; ++k) {
-    initializeIndFile(printTest, *learners[k],
+// for (int k = 0; k < numlearn; ++k) {
+  int k = param["learn"];
+  initializeIndFile(printTest, *learners[k],
 	param, *itVisProb, *itResProb);
     // Loop through the number of replicates
 	for (int i = 0; i < trainingRep; i++) {
@@ -754,7 +755,7 @@ for (int k = 0; k < numlearn; ++k) {
 
 	printTest.close();
 	delete learners[k];
-}
+// }
 							
 						}
 					}

### 2022-08-22 ActCritMCMC.cpp

@@ -730,7 +730,7 @@ void initializeChainFile(ofstream &chainOutput,nlohmann::json param){
 		 "gamma	" << "negReward	" << "probFAA	";
 	if (bool(param["Group"]))
 		chainOutput	<< "gamma.1	" << "negReward.1	" << 
-		"probFAA.1";
+		"probFAA.1	";
 	chainOutput  << "scaleConst	" << "fit	" << "ratio" << endl;
 }
 
@@ -884,18 +884,24 @@ model_param perturb_parameters_uniform(model_param focal_param, json &sim_param)
 			sim_param["sdPert"][5], 0, 1) +
 			(!bool(sim_param["pertScen"][5])) * focal_param.probFAA[0];
 	if (sim_param["Group"]) {
-		new_param.gamma[1] = bool(sim_param["pertScen"][2]) *
+		new_param.gamma[1] = bool(sim_param["groupPars"][2])*(
+			bool(sim_param["pertScen"][2]) *
 			boundedParUnifPert(focal_param.gamma[1],
 				sim_param["sdPert"][2], -1, 1) +
-				(!bool(sim_param["pertScen"][2]))*focal_param.gamma[1];
-		new_param.negReward[1] = bool(sim_param["pertScen"][3])*
+				(!bool(sim_param["pertScen"][2]))*focal_param.gamma[1])+
+			(!bool(sim_param["groupPars"][2])*new_param.gamma[0]);
+		new_param.negReward[1] = bool(sim_param["groupPars"][3])*(
+			bool(sim_param["pertScen"][3])*
 			boundedParUnifPert(focal_param.negReward[1],
 				sim_param["sdPert"][3], -INFINITY, INFINITY) +
-				(!bool(sim_param["pertScen"][3]))*focal_param.negReward[1];
-		new_param.probFAA[1] = bool(sim_param["pertScen"][5]) *
+				(!bool(sim_param["pertScen"][3]))*focal_param.negReward[1]) +
+			(!bool(sim_param["groupPars"][3]) * new_param.negReward[0]);
+		new_param.probFAA[1] = bool(sim_param["groupPars"][5])*(
+			bool(sim_param["pertScen"][5]) *
 			boundedParUnifPert(focal_param.probFAA[1],
 				sim_param["sdPert"][5], 0, 1) +
-				(!bool(sim_param["pertScen"][5])) * focal_param.probFAA[1];
[…]

### 2022-08-22 analysisMCMC.R

@@ -18,18 +18,18 @@ library("jsonlite")
 # scen2<-"MCMCclean_gam_sca_"
 # scen3<-"MCMCclean_Nrew_sca_"
 
-scen1<-"MCMCclean_gam_Nrew_sca_"
-scen2<-"MCMCclean_gam_sca_"
-scen3<-"MCMCclean_Nrew_sca_"
-scen4<-"MCMCclean_PAA2_gam_Nrew_sca_"
-scen5<-"MCMCclean_PAA2_gam_sca_"
-scen6<-"MCMCclean_PAA2_Nrew_sca_"
-
+# scen1<-"MCMCclean_gam_Nrew_sca_"
+# scen2<-"MCMCclean_gam_sca_"
+# scen3<-"MCMCclean_Nrew_sca_"
+# scen4<-"MCMCclean_PAA_gam_Nrew_sca_"
+# scen5<-"MCMCclean_PAA_gam_sca_"
+# scen6<-"MCMCclean_PAA_Nrew_sca_"
+scen7<-"MCMCclean_both_gam_Nrew_sca_group_"
 
 # NLables names for the three scenarios
 labels.Scen<-c("both","gam","Nrew")
 labelsPlot.Scen<-c("Full Model","Chaining","Penalty")
-labels.agente<-c("FAA","PAA")
+labels.agente<-c("FAA","PAA","both")
 ## Load files --------------------------------------------------------------
 
 # Defaults for MCMC analysis
@@ -43,7 +43,7 @@ MCMCdata3<-loadMCMCrun(scen3,thinning = thinning,burn.in = burn.in)
 MCMCdata4<-loadMCMCrun(scen4,thinning = thinning,burn.in = burn.in)
 MCMCdata5<-loadMCMCrun(scen5,thinning = thinning,burn.in = burn.in)
 MCMCdata6<-loadMCMCrun(scen6,thinning = thinning,burn.in = burn.in)
-
+MCMCdata7<-loadMCMCrun(scen7,thinning = thinning,burn.in = burn.in)
 
 # Create list with the data, convenient to use CODA for diagnostics
 mcmcList.1<-mcmc.list(do.call(list,lapply(unique(MCMCdata1$seed), function(repli){
@@ -65,7 +65,7 @@ mcmcList.3<-mcmc.list(do.call(list,lapply(unique(MCMCdata3$seed), function(repli
   return(mcmcRun)
 })))
 
[…]

### 2022-08-22 parTOjson.R

@@ -12,13 +12,13 @@ fileName<-"parameters.json"
 
 # name of the scenario for which parameter files will be produces
 # format used for the name: MCMCclean_*parameter1_paramerter2_parameter3.....
-scenario<- "test"#""
+scenario<- "MCMCclean_PAA_Nrew_sca"
 
 
 # MCMC fit - Generate json parameter files for -------------------------------------
 
 # for MCMC
-param_mcmc<-list(totRounds=100, 
+param_mcmc<-list(totRounds=10000, 
                  # Number of rounds in the learning model
                  ResReward=1,VisReward=1, 
                  # Magnitude of reward for residents and visitors
@@ -34,26 +34,27 @@ param_mcmc<-list(totRounds=100,
                  # Rate at which cleaners forget what they have learned
                  seed=1,  
                  # Seed for the random number generator
-                 # agent="PAA", 
+                 agent="PAA",
                  # Type of agent FAA (chuncking), PAA (not chuncking)
                  propfullPrint = 0.7, 
                  #Proportion of final rounds used to calculate predictions
-                 sdPert=c(0.05,0.05,0.3,6,100,0.2), 
+                 sdPert=c(0.05,0.05,0.25,6.5,100,0.2), 
                  # Width of the perturbation kernel for each parameter
                  # alphaA,AlphaC, Gamma, NegRew, scalConst,probFAA
                  chain_length=100000, # Chain length
-                 init=c(0.05,0.05,0,0,30,1), # Initial values for each of the parameters
+                 init=c(0.05,0.05,0,0,30,0), # Initial values for each of the parameters
                  # alphaA,AlphaC, Gamma, NegRew, scalConst,probFAA
-                 pertScen = c(FALSE,FALSE,FALSE,TRUE,TRUE,TRUE), # boolean controlling which
+                 pertScen = c(FALSE,FALSE,FALSE,TRUE,TRUE,FALSE), # boolean controlling which
                  # parameter is perturbed
                  MCMC =1, # run chain=1, run prediction for one parameter set = 0
[…]

### 2022-08-22 predictions.R

@@ -7,6 +7,7 @@ library("RColorBrewer")
 library("patchwork") 
 library(ggpubr)
 library(ggdist)
+library(ggforce)
 library(here)
 library(cowplot)
 source(here("loadData.R"))
@@ -14,6 +15,7 @@ source(here("data2interp.R"))
 require('akima')
 source(here("aesth_par.R"))
 source(here("../R_files/posPlots.R"))
+
 
 # Folder where the three models are
 # scen1<-"MCMCclean_gam_Nrew_sca_"
@@ -49,13 +51,13 @@ predictDataMode.Nrew<-fread(here("Simulations",scen3,
 
 # Load predictions with the samples from the posterior
 predictDataSamps.both<-do.call(rbind,lapply(predfileSamples.both,fread))
-predictDataSamps.both[,id_samp:=rep(1:100,each=120)]
+predictDataSamps.both[,id_samp:=rep(1:length(predfileSamples.both),each=120)]
 
 predictDataSamps.gam<-do.call(rbind,lapply(predfileSamples.gam,fread))
-predictDataSamps.gam[,id_samp:=rep(1:100,each=120)]
+predictDataSamps.gam[,id_samp:=rep(1:length(predfileSamples.gam),each=120)]
 
-predictDataSamps.Nrew<-do.call(rbind,lapply(predfileSamples.gam,fread))
-predictDataSamps.Nrew[,id_samp:=rep(1:100,each=120)]
+predictDataSamps.Nrew<-do.call(rbind,lapply(predfileSamples.Nrew,fread))
+predictDataSamps.Nrew[,id_samp:=rep(1:length(predfileSamples.Nrew),each=120)]
 
 
 
@@ -94,10 +96,12 @@ fieldatabyLocSamps.Nrew<-predictDataSamps.Nrew[,.(probVisi.data=mean(visitorChoi
                                              by=.(site_year,id_samp)]
 
 myPalette <- colorRampPalette(rev(brewer.pal(11, "Spectral")))
-sc <- scale_colour_gradientn(colours = myPalette(100), limits=c(0,0.8))
+sc <- scale_colour_gradientn(colours = myPalette(100), limits=c(0,1))
 
 
 ## Load data for the contour plot using the mode of the posterior --------------
+
+pointInt<-200
 
 # Full model
 simsDir.both<-here("Simulations",scen1)
@@ -115,8 +119,6 @@ FIA.stats<-FIAlastQuarData[,.(meanProb=mean(Prob.RV.V),
[…]

### 2022-10-05 manuscript_BE/manuscript_BE.Rmd
Edits to include PAA in the analysis. As well as first attempt to use BayesianTools in the MCMC

@@
 scen3<-"MCMCclean_Nrew_sca_"
-scen4<-"MCMCclean_PAA_gam_Nrew_sca_"
-scen5<-"MCMCclean_PAA_gam_sca_"
-scen6<-"MCMCclean_PAA_Nrew_sca_"
+scen4<-"MCMCclean_PAA2_gam_Nrew_sca_"
+scen5<-"MCMCclean_PAA2_gam_sca_"
+scen6<-"MCMCclean_PAA2_Nrew_sca_"
 
@@
  source(here("predictions.R"))
-first_col<-plot_grid(nrow=3,align = "v",byrow = TRUE,
-          cont.obs.pred.both,cont.obs.pred.gam,cont.obs.pred.Nrew,
-          labels=c('a','c','e'),rel_heights = c(1.4,1,1))
-second_col<-plot_grid(nrow=3,align = "v",byrow = TRUE,
-          scatter.obs.pred.both,scatter.obs.pred.gam,scatter.obs.pred.Nrew,
-           rel_heights = c(1.4,1,1),
-          labels=c('b','d','f'))
-plot_grid(first_col,second_col,rows = 1)
+first_col<-plot_grid(nrow=2,align = "v",byrow = TRUE,
+          cont.obs.pred.both,cont.obs.pred.gam,
+          labels=c('a','c'),rel_heights = c(1.4,1))
+second_col<-plot_grid(nrow=2,align = "v",byrow = TRUE,
+          cont.obs.pred.Nrew,scatter.all.plot,
+           rel_heights = c(1,1.4),
+          labels=c('b','d'))
+plot_grid(first_col,second_col)
 ```
@@
 source(here("predictions.R"))
-first_col<-plot_grid(nrow=3,align = "v",byrow = TRUE,
-          cont.obs.pred.both,cont.obs.pred.gam,cont.obs.pred.Nrew,
-          labels=c('a','c','e'),rel_heights = c(1.4,1,1))
-second_col<-plot_grid(nrow=3,align = "v",byrow = TRUE,
-                      rel_heights = c(1.4,1,1),
-          scatter.obs.pred.both,scatter.obs.pred.gam,scatter.obs.pred.Nrew,
-          labels=c('b','d','f'))
-plot_grid(first_col,second_col,rows = 1)
+
+first_col<-plot_grid(nrow=2,align = "v",byrow = TRUE,
+          cont.obs.pred.both,cont.obs.pred.gam,
+          labels=c('a','c'),rel_heights = c(1.4,1))
+second_col<-plot_grid(nrow=2,align = "v",byrow = TRUE,
+          cont.obs.pred.Nrew,scatter.all.plot,
+           rel_heights = c(1,1.4),
+          labels=c('b','d'))
+plot_grid(first_col,second_col)
 ```

### 2022-10-05 ActCritMCMC.cpp

@@ -599,7 +599,25 @@ filename.append(".txt");
 return(filename);
 }
 
-
+struct model_param {
+	//model_param(model_param const &obj);
+	double alphaC, alphaA, scaleConst;
+	double gamma[2], negReward[2];
+	double probFAA[2];
+	double interpReg, slopRegRelAC, slopRegPVL;
+	model_param &operator= (model_param const &rhs) {
+		alphaA = rhs.alphaA;
+		alphaC = rhs.alphaC;
+		scaleConst = rhs.scaleConst;
+		gamma[0] = rhs.gamma[0];
+		negReward[0] = rhs.negReward[0];
+		probFAA[0] = rhs.probFAA[0];
+		gamma[1] = rhs.gamma[1];
+		negReward[1] = rhs.negReward[1];
+		probFAA[1] = rhs.probFAA[1];
+		return *this;
+	}
+};
 
 struct locat_point {
 	double rel_abund_clean, rel_abund_visitors, rel_abund_resid, prob_Vis_Leav;
@@ -618,28 +636,26 @@ struct cleaner_point {
 	float market_exp_success;
 	double marketPred;
 	int group=0;
-};
-
-
-
-struct model_param {
-	//model_param(model_param const &obj);
-	double alphaC, alphaA, scaleConst;
-	double gamma[2], negReward[2];
-	double probFAA[2];
-	model_param &operator= (model_param const &rhs) {
-		alphaA = rhs.alphaA;
-		alphaC = rhs.alphaC;
-		scaleConst = rhs.scaleConst;
-		gamma[0] = rhs.gamma[0];
-		negReward[0] = rhs.negReward[0];
-		probFAA[0] = rhs.probFAA[0];
-		gamma[1] = rhs.gamma[1];
-		negReward[1] = rhs.negReward[1];
-		probFAA[1] = rhs.probFAA[1];
-		return *this;
+	bool agent; // Agent to be used in the simulation of the model
+	void setAgent(model_param currPars, json sim_param) {
+		double prob_F;
+		switch (int(sim_param["agentScen"])){
+		case 0:
+			prob_F = currPars.probFAA[group];
+			break;
+		case 1:
+			prob_F = 1 / (1 + exp(-(currPars.interpReg
+				+ currPars.slopRegRelAC*rel_abund_clean
+				+ currPars.slopRegPVL*prob_Vis_Leav)));
+		default:
+			prob_F =currPars.probFAA[group];
+			break;
+		}
[…]

### 2022-10-05 ActCrit_R.cpp

@@ -1,0 +1,741 @@
+#include <Rcpp.h>
+#include <stdio.h>
+#include <cstdlib>
+#include <math.h>
+#include <iostream>
+#include <fstream>
+#include <omp.h>
+#include "../Cpp/Routines/C++/RandomNumbers/random.h"
+#include "../Cpp/json.hpp"  
+using namespace Rcpp;
+using namespace std;
+using json = nlohmann::json;
+
+// [[Rcpp::depends(RcppJson)]]
+// [[Rcpp::plugins("cpp11")]]
+
+
+#define GET_VARIABLE_NAME(Variable) (#Variable)
+
+enum client { resident, visitor, absence };																		
+// clients can be resident, visitors, or be absent
+enum learPar { alphaPar, gammaPar, netaPar , alphathPar};
+
+enum learnScenario {nature, experiment, marketExperiment, ExtendedMarket};
+
+class agent													// Learning agent
+{
+public:
+  agent(double alphaI, double gammaI, double negRewardI, 
+        double alphathI, double initVal);
+  // constructor providing values for the learning parameters
+  ~agent();																
+  // destructor not really necessary
+  void update();
+  // function that updates the value of state-action pairs according to 
+  //current reward and estimates of future values
+  void act(client newOptions[], int &idNewOptions, double &VisProbLeav, 
+           double ResProbLeav, double VisReward, double ResReward, double inbr, 
+           double outbr,  learnScenario scenario);
+  // function where the agent takes the action, gets reward, see new 
+  //state and chooses future action
+  void printIndData(ofstream &learnSeries, int &seed, double &outbr, 
+                    double pV, double pR);
+  // prints individual data from the learning process
+  double getLearnPar(learPar parameter);
+  // function to access the learning parameters
+  void checkChoice();
+  // Check that the choice taken is among one of the options, 
+  //otherwise trigger an error
+  void rebirth(double initVal);		
+  int getstate(bool time) {
+    if (!time) return currState;
+    else return nextState;
+  }
+  bool getChoice(bool time) {
+    if (!time) return choiceT;
+    else return choiceT1;
+  }
+  // Function to reset private variables in an individual
+  void getNewOptions(client newOptions[], int &idNewOptions, 
[…]

### 2022-10-05 predictions.R

@@ -8,6 +8,8 @@ library("patchwork")
 library(ggpubr)
 library(ggdist)
 library(ggforce)
+library(concaveman)
+library(ggalt)
 library(here)
 library(cowplot)
 source(here("loadData.R"))
@@ -65,17 +67,22 @@ predictDataSamps.Nrew[,id_samp:=rep(1:length(predfileSamples.Nrew),each=120)]
 fieldatabyLoc.both<-predictDataMode.both[,.(probVisi.data=mean(visitorChoices)/20,
                               probvisitor.pred=max(visitorChoices_pred),
                               re.abund.clean=max(rel.abund.cleaners),
-                            prob.Vis.leave=max(prob.Vis.Leav)),by=site_year]
+                              prob.Vis.leave=max(prob.Vis.Leav),
+                              model="both"),by=site_year]
 
 fieldatabyLoc.gam<-predictDataMode.gam[,.(probVisi.data=mean(visitorChoices)/20,
                                    probvisitor.pred=max(visitorChoices_pred),
                                    re.abund.clean=max(rel.abund.cleaners),
-                                   prob.Vis.leave=max(prob.Vis.Leav)),by=site_year]
+                                   prob.Vis.leave=max(prob.Vis.Leav),
+                                   model="gamma"
+                                   ),by=site_year]
 
 fieldatabyLoc.Nrew<-predictDataMode.Nrew[,.(probVisi.data=mean(visitorChoices)/20,
                                           probvisitor.pred=max(visitorChoices_pred),
                                           re.abund.clean=max(rel.abund.cleaners),
-                                          prob.Vis.leave=max(prob.Vis.Leav)),by=site_year]
+                                          prob.Vis.leave=max(prob.Vis.Leav),
+                                          model="eta"
+                                          ),by=site_year]
 
 fieldatabyLocSamps.both<-predictDataSamps.both[,.(probVisi.data=mean(visitorChoices)/20,
                                         probvisitor.pred=max(visitorChoices_pred),
@@ -201,6 +208,7 @@ rsqr.Nrew.McFadden<-1-predictDataMode.Nrew[,sum(log.like)]/
 
 axislabSize<-8
 axisSize<-12
+margPlots<-unit(c(0,0,0,0),"cm")
 # Panel full model contour
[…]

### 2022-10-05 test.cpp

@@ -1,0 +1,138 @@
+#include <Rcpp.h>
+using namespace Rcpp;
+
+// This is a simple example of exporting a C++ function to R. You can
+// source this function into an R session using the Rcpp::sourceCpp 
+// function (or via the Source button on the editor toolbar). Learn
+// more about Rcpp at:
+//
+//   http://www.rcpp.org/
+//   http://adv-r.had.co.nz/Rcpp.html
+//   http://gallery.rcpp.org/
+//
+
+
+NumericVector timesTwo(NumericVector x) {
+  return x * 2;
+}
+
+std::string hello() {
+  return "hello";
+}
+void bla() {
+  Rprintf("hello\\n");
+}
+void bla2( int x, double y) {
+  Rprintf("hello (x = %d, y = %5.2f)\\n", x, y);
+}
+class World {
+public:
+  World() : msg("hello") {}
+  void set(std::string msg) { this->msg = msg; }
+  std::string greet() { return msg; }
+private:
+  std::string msg;
+};
+
+RCPP_MODULE(yada){
+  using namespace Rcpp;
+  function("hello" , &hello);
+  function("bla" , &bla);
+  function("bla2" , &bla2);
+  class_<World>("World")
+    .constructor()
+    .method("greet", &World::greet)
+    .method("set", &World::set)
+  ;
+}
+
+// struct model_param {
+//   model_param()=default;
+//   double logist() {
+//     return (1 / (1 + exp(-(alphaA-alphaC))));
+//   }
+//   void set(double alphaC_,double alphaA_){
+//     this->alphaA = alphaA_;
+//     this->alphaC = alphaC_;
+//   }
+//   void copy(Rcpp::XPtr<model_param> mp_ptr){
+//     this->alphaA = mp_ptr->alphaA;
+//     this->alphaC = mp_ptr->alphaC;
+//   }
+//   Rcpp::XPtr<model_param>get_ptr(){
+//     Rcpp::XPtr<model_param> p(this,true);
+//     return p;
+//   }
+//   double alphaC, alphaA;
+// };
+// 
+// 
+// RCPP_MODULE(cleaner){
+//   using namespace Rcpp;
+//   function("timesTwo", &timesTwo);
+// 
+//   class_<model_param>("model_param")
+//     .constructor()
+//     .method("set_gamma", &model_param::set)
[…]

### 2022-10-05 testRcpp.R

@@ -1,0 +1,41 @@
+library(Rcpp)
+library(here)
+library("BayesianTools")
+
+sourceCpp("test.cpp")
+
+timesTwo(3)
+
+?VSEM
+
+focal<-new(model_param)
+focal$set_gamma(0.5,0.5)
+focal$logist()
+new_param<-new(model_param)
+new_param$set_gamma(1,10)
+new_param$logist()
+
+focal$copy(new_param$get_ptr())
+
+focal$logist()
+
+
+focal$set_gamma(1,1)
+focal$logist()
+focal$set_gamma(0.5,0.6)
+focal$logist()
+
+hello()
+bla()
+bla2(42, 0.42)
+
+w <- new(World)
+w$greet()
+w$set("hohoho")
+w$greet()
+
+muUnif<-new(Uniform,0,2)
+
+muUnif$draw(5)
+
+sourceCpp("ActCrit_R.cpp")

### 2023-10-03 manuscript_BE/manuscript_BE.Rmd
BayesianTools was not getting a reasonable response from the LH function. Now it seems to be fixed. Ready for new sims

@@
 The model with only chaining predicts a low preference fpr the visitor when
-cleaner fish relative abundance is low (Fig. \ref{fig:pred} c). In contrast,
+cleaner fish relative abundance is low (Fig. \ref{fig:predPAA} c). In contrast,
 the models including penalty (with and without chaining) predict high 
-preference for the visitor option (Fig. \ref{fig:pred} a and e).
+preference for the visitor option (Fig. \ref{fig:predFAA} a and e).
 For intermediate and high cleaner relative abundances the predictions 
@@
 trigger a high preference for the visitor; while low abundances trigger
-low preference for the visitor (Fig. \ref{fig:pred}a,b,e). 
+low preference for the visitor (Fig. \ref{fig:predFAA}a,b,e). 
 Note, however, we calculated 
-preferences shown in figure \ref{fig:pred} left panels by using only the model 
+preferences shown in figure \ref{fig:predFAA} left panels by using only the model 
 of the posterior distributions, and by holding constant the balance between 
@@
 clients on all three models. All three models predict an increase preference 
-for visitors as the visitor probability increases  (Fig. \ref{fig:pred}).
+for visitors as the visitor probability increases  (Fig. \ref{fig:predFAA}).
 
@@
 reward task when relative cleaner fish abundance is low, particularly 
-together with a high probability of visitor leaving (Fig. \ref{fig:pred}).
+together with a high probability of visitor leaving (Fig. \ref{fig:predFAA}).
 Low relative cleaner fish abundances mean the market has an excess of demand for

### 2023-10-03 bayes_analysis.R

@@ -12,10 +12,10 @@ sourceCpp(here("ActCrit_R.cpp"))
 source(here("bayes_funcs.R"))
 
 defaultPars<-foc.param
-scenarios_select<-list(BT_FAA_gam_Nrew_sca=
+scenarios_select<-list(BTSfake_FAA_gam_Nrew_sca=
                          c("scaleConst", "gamma0","negReward0"),
-                       BT_FAA_gam_sca=c("scaleConst", "gamma0"),
-                       BT_FAA_Nrew_sca=c("scaleConst", "negReward0"))
+                       BTSfake_FAA_gam_sca=c("scaleConst", "gamma0"),
+                       BTSfake_FAA_Nrew_sca=c("scaleConst", "negReward0"))
 fieldData<-fread(here("Data","data_cleaner_abs_threa1.5.txt"))
 names(fieldData)[4:8]<-c("abund_clean","abund_visitors","abund_resid",
                          "prob_Vis_Leav","group")
@@ -46,7 +46,7 @@ param_mcmc<-list(
 
 # FAA --------------------------------------------------------------------------
 
-scenario <-"BT_FAA_gam_sca"
+scenario <-"BTSfake_FAA_gam_Nrew_sca"
 parSel <- scenarios_select[[scenario]]
 # Load MCMC chains
 MCMC.FAA.loaded <- readRDS(file = here(paste0(scenario,"_"),
@@ -97,7 +97,7 @@ sum(dbinom(fieldData$score_visitor,20,
            fieldData$score_visitor/20,log = TRUE))
 
 sourceCpp(here("ActCrit_R.cpp"))
-
+source("bayes_funcs.R")
 
 parSel<- names(test.param)
 
@@ -111,12 +111,18 @@ test.param.0<-test.param
 test.param.0$gamma0<-0.3
 test.param.0$probFAA<-0
 
+foc.param[parSel]
+
+as.numeric(test.param.0)
+
 FAA_gam_0 <- do_simulation(fieldData,test.param.0,param_mcmc.1)
+
+LogLihood(pars = as.numeric(test.param.0)[match(parSel,names(test.param.0))])
+
 mean(FAA_gam_0[,"marketPred"])
 hist.0<-ggplot(FAA_gam_0,aes(x=marketPred))+geom_histogram()+
   ggtitle(paste0("Log-likelihood_0: ",LogLihood(pars = test.param.0)))+
   xlim(0,1)
-
[…]

### 2023-10-03 bayes_funcs.R

@@ -2,19 +2,20 @@
 
 ## Likelihood
 
-LogLihood<-function(pars){
+LogLihood<-function(pars,sum=TRUE){
   # set parameters that are not calibrated on default values 
   x = defaultPars
-  x[parSel] = pars[parSel]
+  loc_pars = match(parSel,names(defaultPars))
+  x[loc_pars] = pars
   if(is.null(parSel))  warning(call. = TRUE)
-  predicted <- do_simulation(emp_data = fieldData,
+    predicted <- do_simulation(emp_data = fieldData,
                              focal_param = x,
                              sim_param =   param_mcmc)    # run simulations
-  logliHood<-sum(dbinom(predicted[,"score_visitor"],20,
-                        predicted[,"marketPred"],log = TRUE)) # 
+  logliHood<-dbinom(predicted[,"score_visitor"],20,
+                        predicted[,"marketPred"],log = TRUE)
   # Log likelihood calculated using the number of visitor choices, 
   # the total number of trials (20) and the model prediction
-  return(logliHood)
+  return(if (sum == TRUE) sum(logliHood) else logliHood)
 }
 
 # Default parameters

### 2023-10-03 fitFakeData.R

@@ -48,23 +48,52 @@ pars2reco<-foc.param
 pars2reco$scaleConst <-350
 pars2reco$gamma0 <- 0.5
 
+t(fieldData[,lapply(.SD,fivenum),.SDcols = c('abund_clean','abund_visitors',
+                                           'abund_visitors','prob_Vis_Leav')])
+fieldData[,unique(interaction(site.year,cleaner_ID))]
+fieldData[,unique(cleaner_ID)]
 
-fakedata <- do_simulation(fieldData,focal_param = pars2reco,
+
+str(fieldData)
+
+totN<-240
+SuperFakeData <- data.table(
+  site.year=rep(1:24,each=10),
+  cleaner_ID=rep(1:10,24),
+  abund_clean=rep(runif(24,range(fieldData[,abund_clean])[1],
+                    range(fieldData[,abund_clean])[2]),
+                  each=10),
+  abund_visitors=rep(runif(24,range(fieldData[,abund_visitors])[1],
+                           range(fieldData[,abund_visitors])[2]),
+                     each=10),
+  abund_resid=rep(runif(24,range(fieldData[,abund_resid])[1],
+                           range(fieldData[,abund_resid])[2]),
+                     each=10),
+  prob_Vis_Leav=rep(runif(24,range(fieldData[,prob_Vis_Leav])[1],
+                        range(fieldData[,prob_Vis_Leav])[2]),
+                  each=10),
+  score_visitor=rep(-1,240),
+  group=rep(0,240)
+)
+
+simfakedata <- do_simulation(SuperFakeData,focal_param = pars2reco,
                           sim_param = param_mcmc)
 
-fakedata<-data.table(fakedata)
+simfakedata <- data.table(simfakedata)
+str(simfakedata)
 
-fakedata[,fake_score_vis:=sapply(marketPred,FUN = rbinom,n=1,size = 20)]
+dim(simfakedata)
 
-fakeFieldData <- fieldData
-
-fakeFieldData[,score_visitor:=fakedata[,fake_score_vis]]
-
-fieldData <- as.data.frame(fakeFieldData)
+simfakedata[,fake_score_vis:=
+              sapply(marketPred,FUN = rbinom,n=1,size = 20)]
 
 
+SuperFakeData[,score_visitor:=simfakedata[,fake_score_vis]]
 
-nIter<-1000
+fieldData <- as.data.frame(SuperFakeData)
+
+
[…]
